### 2024-02-27 _manuscript/_tex/index.tex
render 1

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Pierre Gernez; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Discriminating Seagrass From Green Macroalgae in European
Intertidal areas using high resolution multispectral drone imagery}
\author[1]{Simon Oiry%
\corref{cor1}%
}
 \ead{oirysimon@gmail.com} 
\author[1]{Bede Ffinian Rowe Davies%
%
}

\author[1]{Pierre Gernez%
%
}

\author[2]{Ana I. Sousa%
%
}

\author[1]{Philippe Rosa%
%
}

\author[3]{Maria Laura Zoffoli%
%
}

\author[4]{Guillaume Brunier%
%
}

\author[1]{Laurent Barillé%
%
}

\affiliation[1]{organization={Nantes University},,postcodesep={}}
\affiliation[2]{organization={Aveiro University},,postcodesep={}}
\affiliation[3]{organization={CNR ISMAR},,postcodesep={}}
\affiliation[4]{organization={JeSaisPas},,postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
In September 2021, a significant jump in seismic activity on the island
of La Palma (Canary Islands, Spain) signaled the start of a volcanic
crisis that still continues at the time of writing. Earthquake data is
continually collected and published by the Instituto Geográphico
Nacional (IGN). \ldots{}
\end{abstract}

\begin{keyword}
    Drone \sep 
    Remote Sensing
\end{keyword}
\end{frontmatter}

\section{Introduction}\label{introduction}

Coastal areas are vital hotshots for marine biodiversity, with
intertidal seagrass meadows playing a crucial role at the interface
between land and ocean \citep{unsworth2022}. These meadows offer a
myriad of ecosystem services to humanity, including limitation of
coastline erosion, reducing the risk of eutrophication, carbon
sequestration, and oxygen production. They serve as vital habitats for a
diverse array of marine and terrestrial species, providing living,
breeding, and feeding grounds \citetext{\citealp[
]{gardner2018}; \citealp[ ]{Zoffoli2022}; \citealp{jankowska2019}}. Due
to their proximity to human activities, seagrass meadows are directly
exposed to and impacted by anthropogenic pressures. Global regression
and fragmentation are currently observed due to diseases, disasters,
coastal urbanization, sea reclamation, as well as fishing activities,
dredging, sea level rise, coastal erosion, competition with alien
species, and reduction in water quality \citetext{\citealp[
]{nguyen2021}; \citealp[ ]{soissons2018}; \citealp[
]{orth2006}; \citealp[ ]{lin2018}; \citealp{duffy2019}}. While
improvements in water quality have been recently reported in European
sites, allowing an overall recovery of seagrass ecosystems at the local
scale, many other coastal waters worldwide are still subjected to strong
eutrophication processes \citetext{\citealp[
]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal eutrophication has been
associated to anomalous accumulation of green macroalgae, the so-called
green tides. Green tides produce shade and suffication over seagrass
individuals, thus threatening the health of seagrass ecosystems
\citetext{\citealp[ ]{Duarte2002}; \citealp{wang2022}}.

The importance of seagrass meadows and the variety of ecosystem services
they provide have led to the enhancement of global and regional
monitoring programs for systematically surveying different Essential
Oceanic Variable \citep{Miloslavich2018} as seagrass coverage and
composition; as well as Essential Biodiversity Variable
\citep{Pereira2013} such as seagrass taxonomic diversity; species
distribution, population abundance, and phenology. Monitoring programs
also prioritize the identification of threats to these ecosystems,
particularly during early stages, to facilitate effective mitigation
actions. Traditionally, these ecological parameters have been quantified
through in situ measurements, although this approach faces several
constraints over intertidal zones. Intertidal meadows are only partially
exposed during low tide and can be situated in difficult-to-reach
mudflats, potentially leading to inaccurate and limited estimations with
conventional sampling techniques \citep{nijland2019}. However, satellite
data have been proven effective in complenmenting in situ surveys,
allowing for the rapid and consitent retrieval of EOV's over extensive
seagrass meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
]{xu2021}; \citealp[ ]{Traganos2018}; \citealp{coffer2023}}

Satellite remote sensing offers the advantage of acquiring large-scale
data in real-time but presents its inherent challenges. Free access
satellite data (e.g., Sentinel-2 and Landsat8/9) provide relatively low
spatial resolution data (10 - 30 m) across a limited number of spectral
bands. These characteristics can be a limitation to accurately
discriminating seagrass from others co-existing macrophytes over the
meadow. Chlorophyceae (Green Algae) and marine Magnoliopsida (Seagrass)
share the same pigment composition \citetext{\citealp[
]{ralph2002}; \citealp{Douay2022}}. As a result, their respective
spectral signatures can be considered similar by a non-expert observer
\citetext{\citealp[ ]{Davies2023}; \citealp{bannari2022}}. Recently,
using a hyperspectral library, \citep{Davies2023} demonstrated that the
spectral resolution of Sentinel-2, might be enough for the
discrimination between Magnoliopsida and Chlorophyceae. However, green
tide events occur at small spatial scales that are not observable using
satellite imagery \citep{tuya2013}, especially during the initial stage
of the event.

Remote sensing drone acquisitions are presented as a tool that can
potentially fill gaps left by satellite and in situ data. Drone can
cover large expanses while recording imagery at significantly higher
spatial resolutions than satellite (pixel size from cm to mm) and still
capturing data at multi-spectral resolution \citetext{\citealp[
]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
allows for their application across a diverse thematic range , from
coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
]{casella2020}; \citealp{angnuureng2022}} to mapping the spatial
distribution of species \citetext{\citealp[ ]{joyce2023}; \citealp[
]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[
]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
to coastal habitat mapping, many studies showcase their findings with
study case limited to a single flight, restricting the generalizability
of their application to other sites \citetext{\citealp[
]{Roman2021}; \citealp[ ]{collin2019improving}; \citealp[
]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. This study aimed
to analyze the potential of a drone equipped with a multispectral sensor
for maping intertidal macrophytes, with a particular focus on
discriminating Magnoliopsida and Chlorophyceae. Ten drone flights were
performed over soft-bottom intertidal areas along two European countries
(France and Portugal), covering a wide range of habitats, from
monospecific seagrass meadows to meadows mixed with green or red algae.
A deep learning algorithm was trained and validated for macrophyte
discrimination, emphasizing applicability across diverse sites without a
loss of accuracy in predictions.

  \bibliography{library.bib}

\end{document}

### 2024-02-27 _manuscript/_tex/index.tex
test2

@@
 \hypersetup{
-  pdftitle={Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery},
+  pdftitle={Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Pierre Gernez; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Laurent Barillé},
@@
 \title{Discriminating Seagrass From Green Macroalgae in European
-Intertidal areas using high resolution multispectral drone imagery}
+Intertidal areas using high resolution multispectral drone imagery.}
 \author[1]{Simon Oiry%

### 2024-02-27 index.qmd
test2

---
title: Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
author:
  - name: Simon Oiry
    orcid: 0000-0001-7161-5246
    corresponding: true
    email: oirysimon@gmail.com
    roles:
      - Investigation
      - Writing
      - Data acquisition
    affiliations:
      - Nantes University
  - name: Bede Ffinian Rowe Davies
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Pierre Gernez
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Ana I. Sousa
    corresponding: false
    roles:
      - Data acquisition
      - Revision
    affiliations:
      - Aveiro University
  - name: Philippe Rosa
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Maria Laura Zoffoli
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - CNR ISMAR
  - name: Guillaume Brunier
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - JeSaisPas
  - name: Laurent Barillé
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
keywords:
  - Drone
  - Remote Sensing
abstract: |
  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing. Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN). ...
plain-language-summary: |
  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
key-points:
  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
date: last-modified
citation:
  container-title: Earth and Space Science
number-sections: true
---

# Introduction

Coastal areas are vital hotshots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022]. These meadows offer a myriad of ecosystem services to humanity, including limitation of coastline erosion, reducing the risk of eutrophication, carbon sequestration, and oxygen production. They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019]. Due to their proximity to human activities, seagrass meadows are directly exposed to and impacted by anthropogenic pressures. Global regression and fragmentation are currently observed due to diseases, disasters, coastal urbanization, sea reclamation, as well as fishing activities, dredging, sea level rise, coastal erosion, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019]. While improvements in water quality have been recently reported in European sites, allowing an overall recovery of seagrass ecosystems at the local scale, many other coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021]. Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides. Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@Duarte2002 ; @wang2022].

The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of global and regional monitoring programs for systematically surveying different Essential Oceanic Variable [@Miloslavich2018] as seagrass coverage and composition; as well as Essential Biodiversity Variable [@Pereira2013] such as seagrass taxonomic diversity; species distribution, population abundance, and phenology. Monitoring programs also prioritize the identification of threats to these ecosystems, particularly during early stages, to facilitate effective mitigation actions. Traditionally, these ecological parameters have been quantified through in situ measurements, although this approach faces several constraints over intertidal zones. Intertidal meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019]. However, satellite data have been proven effective in complenmenting in situ surveys, allowing for the rapid and consitent retrieval of EOV's over extensive seagrass meadows. [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023]

Satellite remote sensing offers the advantage of acquiring large-scale data in real-time but presents its inherent challenges. Free access satellite data (e.g., Sentinel-2 and Landsat8/9) provide relatively low spatial resolution data (10 - 30 m) across a limited number of spectral bands. These characteristics can be a limitation to accurately discriminating seagrass from others co-existing macrophytes over the meadow. Chlorophyceae (Green Algae) and marine Magnoliopsida (Seagrass) share the same pigment composition [@ralph2002 ; @Douay2022]. As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022]. Recently, using a hyperspectral library, @Davies2023 demonstrated that the spectral resolution of Sentinel-2, might be enough for the discrimination between Magnoliopsida and Chlorophyceae. However, green tide events occur at small spatial scales that are not observable using satellite imagery [@tuya2013], especially during the initial stage of the event.

Remote sensing drone acquisitions are presented as a tool that can potentially fill gaps left by satellite and in situ data. Drone can cover large expanses while recording imagery at significantly higher spatial resolutions than satellite (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use]. The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping the spatial distribution of species [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic]. However, when applied to coastal habitat mapping, many studies showcase their findings with study case limited to a single flight, restricting the generalizability of their application to other sites [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic]. This study aimed to analyze the potential of a drone equipped with a multispectral sensor for maping intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae. Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae. A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of accuracy in predictions.

### 2024-02-27 _manuscript/_tex/index.tex
test3

--- 2024-02-27 _manuscript/_tex/index.tex
@@
 \hypersetup{
-  pdftitle={Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery},
+  pdftitle={Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Pierre Gernez; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Laurent Barillé},
@@
 \begin{frontmatter}
-\title{Discriminating Seagrass From Green Macroalgae in European
-Intertidal areas using high resolution multispectral drone imagery}
+\title{Discriminating Seagrasses From Green Macroalgae in European
+Intertidal areas using high resolution multispectral drone imagery.}
 \author[1]{Simon Oiry%

### 2024-02-27 index.qmd
test3
test push

@@
 ---
-title: Discriminating Seagrass From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
+title: Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
 author:
@@
 
+```{r library}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: true
+
+library(flextable)
+library(tidyverse)
+library(tidyterra)
+library(tidymodels)
+library(Utilities.Package) 
+library(patchwork)
+library(sf) 
+library(rnaturalearth) 
+library(rnaturalearthdata) 
+library(rnaturalearthhires)
+library(ggforce) 
+library(patchwork)
+library(terra)
+library(gt)
+library(scales)
+library(magick)
+library(grid)
+library(ggforce)
+library(statebins)
+library(ggridges)
+library(ggspatial)
+library(terrainr)
+# library(ggpmisc)
+library(broom)
+library(stars)
+library(gmodels)
+library(caret)
+
+options(scipen = 100000000)
+```
+
+```{r}
+#| cache: false
+#| echo: false
+#| warning: false
+
+my_comma<-scales::label_comma(accuracy = NULL, big.mark = ",",decimal.mark = ".")
+```
+
 # Introduction
@@
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of accuracy in predictions.
+
+# Material & Methods
+
+## Study sites
+
+Seven study sites distributed between France and Portugal were selected for their relatively extensive intertidal seagrass beds.
+Two sites are located in Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
+This gulf covers an area of 115 km² and is only connect to the sea through a 900m wide channel.
+A total of 53 small islands are scattered across the gulf leading to 250 km of shorelines.
+Patchy seagrass meadows can be found on a lot of these islands.
+Within the Gulf of Morbihan we have chosen two sites : One is located in one of these island (Arz island).
+The other one is located in the sourthern part of the Gulf (Duer).
+Two others sites are located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
+This bay is a semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
+With up to 6m in tidal range during spring tide, a 6 km² seagrass meadow can uncover at low tide.
+The sites we surveyed (L'Epine and Barbatre, @fig-map B) are located in the southernmost part of the bay, along the Noirmoutier Island, and host a monospecific *Zostera noltei* seagrass bed with very little mixing with other macrophytes.
+Three sites have been survey in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
+The extent of this lagoon is about 80 km² with many narrow channels, large salt marshes and many mudflats that uncovers at low tide.
+It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
+The southernmost site (Gafanha) is a mudflat located in an affluent of the lagoon whereas the two other sites are situated in the middle of the lagoon and are only accessible by boat (@fig-map C).
+These Portuguese sites were characterized by a more diverse intertidal area, where the seagrass meadow could intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae), or green algae (Chlorophyceae).
+
+```{r Figure1 Overall Map}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+world_map <- sovereignty10 %>% 
+  st_as_sf() %>% 
+  dplyr::filter(SOVEREIGNT%in%c("Spain","France","Portugal",
+                                "Italy","Andorra",
+                                "United Kingdom",
+                                "Switzerland","Belgium",
+                                "Germany","Luxembourg") )
+
+bbox_europe <- st_bbox(c(xmin = -20, ymin = 34,
+                         xmax = 20, ymax = 55) ,
+                       crs = st_crs(world_map) )
+
+world_map<-st_make_valid(world_map)
+
+european_union_map_cropped <- st_crop(world_map, bbox_europe)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+UnitedKingdom<-sovereignty10 %>% 
+  st_as_sf() %>% 
+  dplyr::filter(SOVEREIGNT%in%c("United Kingdom") ) %>% 
+  st_cast("POLYGON")
+
+bbox_UK <- st_bbox(c(xmin = -20, ymin = 45,
+                         xmax = 20, ymax = 55) ,
+                       crs = st_crs(UnitedKingdom) )
+
+UnitedKingdom<-st_make_valid(UnitedKingdom)
+
+UK_map_cropped <- st_crop(UnitedKingdom, bbox_UK)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+Europe_sf<-european_union_map_cropped %>% 
+  dplyr::bind_rows(UK_map_cropped)
+
+Projects<-data.frame(
+  Name=c(
+  "Portugal - Aveiro Lagoon Flights\nLower-Resolution: 4\nHigher-Resolution: 1",
+  "France - Morbihan Gulf Flights\nLower-Resolution: 3\nHigher-Resolution: 3",
+  "France - Bourgneuf Bay Flights\nLower-Resolution: 4\nHigher-Resolution: 0"
+  ) ,
+  Long=c(-8.745730,
+         -2.840592, 
+         -2.111868) ,
+  Lat=c(40.617610, 
+        47.578736,
+        47.024719) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+Projects_df<-Projects %>%
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)  %>% 
+  separate(Name, into=c("Country","Bay") ,sep=" - ")  %>% 
+  dplyr::mutate(Country=as.factor(Country) ,
+                Bay=as.factor(Bay) )
+
+Miniworld_map <- sovereignty10 %>% 
+  st_as_sf()
+
+sf_use_s2(FALSE)
+
+bbox_EU <- st_bbox(c(xmin = -30, ymin = 20,
+                         xmax = 50, ymax = 70) ,
+                       crs = st_crs(Miniworld_map) )
+
+  MiniEU_map<-st_crop(Miniworld_map, bbox_EU)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+  df_P1<-Projects_df %>% 
+    mutate(ID = c(1:nrow(.))) %>% 
+    mutate(Site = case_when(ID == 1 ~ "Aveiro Lagoon",
+                            ID == 2 ~ "Morbihan Gulf",
+                            ID == 3 ~ "Bourgneuf Bay",
+                            TRUE ~ "NA"),
+           ID = case_when(ID == 1 ~ "C",
+                          ID == 2 ~ "A",
+                          TRUE ~ "B")) %>% 
+    dplyr::select(c(lon,lat,ID,Site))
+
+    scaleFUN <- function(x) paste0(sprintf("%.2f", x),"°N")
+
+p1  <-
+  ggplot(MiniEU_map) +
+  geom_sf(linewidth=0.5,alpha=0.93,
+          fill="#CFCFCF",colour="grey30")+
+    ggforce::geom_mark_ellipse(data=df_P1,
+                 aes(x=lon,
+                     y=lat,
+                     label = ID,
+                     description=Site) ,
+                 linewidth=0.3,
+                 fill="goldenrod",
+                 show.legend=F,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 con.colour = "goldenrod4",
+                 label.fontsize = c(25,20),
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") , 
+  label.buffer = unit(5, "mm") ,
+  label.fill = "grey90")+
+  coord_sf(xlim=c(2600000,4100000) ,
+          ylim=c(1600000,3100000))+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  scale_y_continuous(labels=scaleFUN)+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20) )
+
+ggsave("Figures/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)
+
+```
+
+```{r Figure1 Aveiro}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Gafanha",
+  "Mataducos",
+  "Marinha Lanzarote"
+  ) ,
+  Description = c("12m and 120m Flights",
+                  "120m Flight",
+                  "120m Flight"),
+  Long=c(-8.742485,
+         -8.646980, 
+         -8.690677) ,
+  Lat=c(40.597599, 
+        40.666634,
+        40.665120) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+aveiro_plot <-
+ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#CFCFCF"))+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 25,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.70, -8.60, by = 0.10))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))
+
+ggsave("Figures/Figure1/Map_Aveiro.png",aveiro_plot,width= 10, height=10)
+
+```
+
+```{r Figure1 Bourgneuf Bay}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_BB <- filelist[str_detect(filelist,"mask_land_intertidal_BB")] %>% 
+  read_sf()
+
+Flight_BB<-data.frame(
+  Name=c(
+  "Barbâtre",
+  "L'Epine"
+  ) ,
+  Description = c("120m Flight",
+                  "120m Flight"),
+  Long=c(-2.166313,
+         -2.228239) ,
+  Lat=c(46.956420, 
+        46.989515) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_BB))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+BB_plot <- ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#CFCFCF"))+
+  geom_sf(data = mask_BB, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
+      coord_sf(xlim=c(550609,579539) ,
+          ylim=c(5189447,5218377) )+
+  ggforce::geom_mark_ellipse(data=Flight_BB,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 con.size = 2,
+                 label.fontsize = 25,
+                 label.hjust = 0.5,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = c(0.95,0.2),
+        legend.key.size =  unit(1, "cm"),
+        legend.text = element_text(size = 20),
+        legend.title=element_blank(),
+        legend.background = element_rect(linewidth = 0.5, 
+                                         fill = "white",
+                                         linetype="solid", 
+                                  colour ="black"),
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))
+
+ggsave("Figures/Figure1/Map_BB.png",width= 10, height=10)
+
+```
+
+```{r Figure1 Morbihan Bay}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_Morb <- filelist[str_detect(filelist,"mask_land_intertidal_Morbihan")] %>% 
+  read_sf()
+
+Flight_Morbihan<-data.frame(
+  Name=c(
+  "Arz",
+  "Duer"
+  ) ,
+  Description = c("12m Flight",
+                  "12m and 120m Flight"),
+  Long=c(-2.795961,
+         -2.746186) ,
+  Lat=c(47.603260, 
+        47.543877) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_Morb))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+Morbihan_plot<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
+                    values = c("#7DC27D", "#CFCFCF"))+
+  geom_sf(data = mask_Morb, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
+      coord_sf(xlim=c(503019,526177) ,
+          ylim=c(5257824,5280982))+
+  ggforce::geom_mark_ellipse(data=Flight_Morbihan,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 con.size = 2,
+                 label.hjust = 0.5,
+                 label.fontsize = 25,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  geom_label(aes(x = 505000, y = 5280982-1981, label = "A"), size = 20)+
+  scale_x_continuous(breaks = seq(-3, -2.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))
+
+  ggsave("Figures/Figure1/Map_Morbihan.png",width= 10, height=10)
+
+```
+
+```{r Figure1 saving}
+#| cache: false
+#| echo: false
+#| eval: false
+#| warning: false
+
+layout <- c(
+  patchwork::area(t = 1, l = 1, b = 10, r = 10),
+  patchwork::area(t = 1, l = 11, b = 10, r = 20),
+  patchwork::area(t = 11, l = 1, b = 20, r = 10),
+  patchwork::area(t = 11, l = 11, b = 20, r = 20)
+)
+# plot(layout)
+
+Tot <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Drone_Sites.png"), interpolate = T)
+BB <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_BB.png"), interpolate = T)
+Mor <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Morbihan.png"), interpolate = T)
+Av <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Aveiro.png"), interpolate = T)
+
+a<-Tot+Mor+BB+Av+patchwork::plot_layout(design=layout)
+
+ggsave("./Figures/Fig1_Map_Drone_Sites.png",a, width= 10, height=10, dpi = 800)
+
+```
+
+```{r Figure1}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: >
+#|   Sites where the different drone flights were made.
+A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon.
+Light green represent terrestrial areas whereas darkgreen represent intertidal areas.
+#| label: fig-map
+#| fig-width: 9
+#| fig-height: 9
+
+knitr::include_graphics("./Figures/Fig1_Map_Drone_Sites.png")
+```
+
+## Drone Data
+
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from blue (444 nm) to near infrared (840 nm).
+An angle of 90° has been maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
+A side overlap of 70% and a front overlap of 80% between each image has been set.
+Images have been calibrated in reflectance using a calibration panel reflective at \~50% provided by the camera's manufaturer and a Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance data during the flight.
+A Structure-from-Motion photogrammetry software (Agisoft Metashape) has been used to process images to obtain multispectral orthomosaics of each flight.
+The workflow for orthomosaicking has remained consistent for every flight.
+First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
+This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
+A dense point cloud has been then produced using a structure from motion algorithm.
+A surface interpolation of this dense point cloud has been made to obtain a Digital Surface Model (DSM), used to reconstruct the multispectral ortho-image.
+Across all the sites, flights were made at two different altitudes : 12 m or/and 120 m.
+Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it simple to visually distinguish between the various types of vegetation.
+High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (Table 1).
+
+```{r Table1}
+#| echo: false
+#| warning: false
+#| tbl-cap: List of drone Flight, summarising the date, the altitude and the purpose of each flight.
+#| cache: true
+
+df<-data.frame(
+  Country = c(
+    rep("France",5),
+    rep("Portugal",4)
+  ),
+  Site = c(
+    rep("Morbihan",3),
+    rep("Bourgneuf Bay",2),
+    rep("Aveiro Lagoon",4)
+  ),
+  Name = c(
+    "Arz Island",
+    "Duer",
+    "Duer",
+    "Barbâtre",
+    "L'Epine",
+    "Inner Lagoon",
+    "Mataducos",
+    "Gafanha",
+    "Gafanha"
+  ),
+  Altitude = c(
+    "12m",
+    "12m",
+    "120m",
+    "120m",
+    "120m",
+    "120m",
+    "120m",
+    "120m",
+    "12m"
+  ),
+  Utility = c(
+    "Training",
+    "Training",
+    "Validation",
+    "Validation",
+    "Validation",
+    "Validation",
+    "Validation",
+    "Validation",
+    "Training"
+  )
+)
+
+brdr1 <- fp_border_default(color = "black", width = 1.5)
+brdr2 <- fp_border_default(color = "grey", width = 1.5)
+brdr3 <- fp_border_default(color = "grey40", width = 1.5)
+
+flextable(df)  %>%
+  merge_v(j = 1) %>%
+  merge_v(j = 2) %>%
+    border_remove() %>%
+    hline_top(border=brdr1) %>%
+    hline(i=5, border=brdr1) %>%
+    hline(i=1,j = 3:5, border=brdr2) %>%
+    hline(i=2, border=brdr2) %>%
+    hline(i=3, j = 2:5, border=brdr3) %>%
+    hline(i=4, j = 3:5, border=brdr2) %>%
+    hline(i=6, border=brdr2) %>%
+    hline(i=6, j = 1:2, border=brdr1) %>%
+    hline(i=7, border=brdr2) %>%
+    hline(i=8, border=brdr2) %>%
+    hline(i=9, border=brdr1) %>%
+    vline(j=2, border = brdr1) %>%
+    flextable::align(align = "center",part = "all") %>%
+    flextable::align(align = "center",part = "header") %>%
+  # set_caption(caption = "Table 1 List of drone Flight, summarising the date, the altitude and the purpose of each flight.") %>%
+  set_table_properties(layout = "autofit")
+
+```
+
+## Field sampling
+
+Before each flight, targets used as Ground Control Points (GCPs) were dispersed and georeferenced with a Trimble © Geo XH 6000 differential GPS (dGPS).
+GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
+dGPS was also used to georeference quardrats of 0.25cm² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (Brown algae), Magnoliopsida (Seagrass), Chlorophyceae (Green algae) and Rhodophyceae (Red algae) (@fig-vegetation).
+Picture of each quadrat were taken and uploaded on the online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif].
+Each photograph was also processed to estimate the percent cover of each type of vegetation.
+Georeferenced hyperspectral reflectance signatures of each vegetation class were also sampled using an ASD FieldSpec HandHeld 2 spectroradiomete, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
+The methodological scheme followed in this study is presented in @fig-workflow.
+
+```{r Figure2 Spectra Pictures}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+micasense<-list.files(pattern = "Wavelength_Micasense_DualMX.csv",recursive = T) %>% 
+  read.delim(sep = ";")
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "Arz") ~ "Arz",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          str_detect(path, "Pred") ~ "Pred",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".xml"),
+                !str_detect(path,".enp"))
+
+gaf_low_multi<- imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "FALSE",
+         folder == "Input") %>%
+  slice(1) %>% 
+  pull(path) %>%
+  rast() 
+ names(gaf_low_multi)<-c(paste0("B",c(1:10)))
+
+ Gafanha_low_pred<-"./Data/image/prediction/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
+     rast()
+ names(Gafanha_low_pred)<-"pred"
+
+# arz_multi<- imglist %>% 
+#   filter(site == "Arz", 
+#          type == "ortho") %>% 
+#   slice(1) %>% 
+#   pull(path) %>% 
+#   rast()
+#  names(arz_multi)<-c(paste0("B",c(1:10)))
+# 
+# arz_pred<- imglist %>% 
+#   filter(site == "Arz", 
+#          type == "Pred",
+#          str_detect(path, "7by7")) %>% 
+#   slice(1) %>% 
+#   pull(path) %>% 
+#   rast()
+#  names(arz_pred)<-"pred"
+
+gaf<-rast(list(gaf_low_multi,Gafanha_low_pred)) %>% 
+  as.data.frame(xy = F) %>% 
+  dtplyr::lazy_dt() %>% 
+  dplyr::filter(B1 != 65535,
+                pred != 0) %>%
+  as_tibble() %>% 
+  rename(Class = "pred") %>%
+  mutate(pxl_ID = c(1:nrow(.))) %>% 
+  pivot_longer(-c(Class,pxl_ID), names_to = "band",values_to = "value") %>% 
+  left_join(micasense, by = c("band" = "Band_ID")) %>% 
+  group_by(Class, Wavelength) %>% 
+  dplyr::summarise(mean = mean(value),
+                   sd = sd(value),
+                   max = max(value),
+                   min = min(value),
+                   median = median(value)) %>%  
+  mutate(Class = case_when(Class == 1 ~ "Bare Sediment",
+                              Class == 2 ~ "D - Chloropyceae",
+                              Class == 3 ~ "Bare Sediment",
+                              Class == 4 ~ "A - MagnoliopsidaL",
+                              Class == 5 ~ "E - Microphytobenthos",
+                              Class == 6 ~ "A - Magnoliopsida",
+                              Class == 7 ~ "B - Phaeophyceae",
+                              Class == 8 ~ "C - Rhodophyceae",
+                              Class == 9 ~ "Sun Glint",
+                              Class == 10 ~ "Water",
+                              Class == 11 ~ "Xanthophyceae",
+                              TRUE ~ "NA"))
+
+spectra<-gaf %>% 
+  dplyr::filter(Class != "Bare Sediment",
+                Class != "Sun Glint",
+                Class != "Water",
+                Class != "Xanthophyceae",
+                Class != "A - MagnoliopsidaL") %>% 
+  ggplot(aes(x=Wavelength, y = mean/10000, color = Class))+
+  geom_line(linewidth = 0.5)+
+  scale_color_manual(values=c("#389318", "#873e23", "#b3002d", "#b3ff1a", "#DAA520"))+
+  ylab("Reflectance")+
+  xlab("Wavelength (nm)")+
+  theme_Bede()+
+  theme(axis.text.x = element_text(size = 5),
+        axis.text.y = element_text(size = 5),
+        axis.title.x = element_text(size = 7),
+        axis.title.y = element_text(size = 7),
+        legend.position = c(0.2, 0.7),
+        plot.background = element_rect(fill = rgb(1,1,1, alpha=0), colour = NA),
+        legend.title=element_blank(),
+        legend.text = element_text(size = 5),
+        legend.key.size = unit(0.25, "cm"),
+        legend.text.align = 0,
+        panel.border = element_blank(), 
+        panel.background = element_blank(),
+        axis.line = element_line(color="black"))
+
+ggsave("Figures/Spectral_shapes.png",spectra, bg = "transparent",  height = 2, width = 3, dpi = 2000)
+
+sp <- image_ggplot(magick::image_read("Figures/Spectral_shapes.png"), interpolate = T)
+
+# sp<-ggplot()+
+#   geom_spatraster_rgb(data = rast("Figures/Spectral_shapes.png"),maxcell = 4009008)+
+#   coord_equal()+
+#     theme_void()+
+#   theme(axis.text = element_blank(), 
+#         axis.title = element_blank(), 
+#         axis.ticks = element_blank(),
+#         panel.background = element_rect(fill='transparent'),
+#         plot.background = element_rect(fill='transparent', color=NA),
+#         axis.ticks.length = unit(0, "pt"),
+#         panel.grid.major=element_blank(), 
+#         panel.grid.minor=element_blank(), 
+#         plot.margin = margin(0, 0, 0, 0, "pt"))
+# 
+# 
+# Magno <- magick::image_read("Data/Pictures/Figure2/Magnoliopsida_cropped2.png")%>%
+#   # magick::image_rotate(90)%>%
+#   grid::rasterGrob()
+# 
+# Brown <- magick::image_read("Data/Pictures/Figure2/Phaeophyceae_cropped.png")%>%
+#   grid::rasterGrob()
+# 
+# Red <- magick::image_read("Data/Pictures/Figure2/Rhodophyceae_cropped.png")%>% 
+#   grid::rasterGrob()
+# 
+# green <- magick::image_read("Data/Pictures/Figure2/Chlorophyceae_cropped.png")%>% 
+#   grid::rasterGrob()
+# 
+# MPB <- magick::image_read("Data/Pictures/Figure2/Bacillariophyceae_cropped.png")%>% 
+#   grid::rasterGrob()
+# 
+# Lines<-data.frame(x=c(10,20,10),
+#                   y=c(-0.1,-0.1,10),
+#                   xend=c(10,20,30),
+#                   yend=c(20,20,10))
+# labels<-data.frame(name = c("A","B","C","D","E"),
+#                    x= c(1,11,21,11,21),
+#                    y=c(19,19,19,1,1))
+# 
+# a<-ggplot(expand_grid(x = 0:30,y=0:20),aes(x = x, y = y) ) +
+#   geom_point(alpha=0) +
+#   coord_fixed()+
+#   ggplot2::annotation_custom(Magno, 0,10, 0, 20) +
+#   ggplot2::annotation_custom(green, 10,20, 10, 20)+
+#   ggplot2::annotation_custom(Red, 10,20, 0, 10)+
+#   ggplot2::annotation_custom(Brown, 20,30, 10, 20)+
+#   ggplot2::annotation_custom(MPB, 20,30, 0,10)+
+#   geom_segment(data=Lines,aes(x=x,y=y,xend=xend,yend=yend),
+#                colour="white",linewidth=2)+
+#   ggplot2::annotation_custom(ggplotGrob(spectra), 5,25, 5,15)+
+#   geom_label(data=labels,aes(x=x,y=y,label=name), size = 10)+
+#   theme_void()+
+#   theme(axis.title.x = element_blank(),
+#         axis.title.y = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.text.y = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         axis.ticks.y = element_blank(),
+#         plot.margin = grid::unit(c(0.01,0.01,0.01,0.01), "mm"),
+#         # rect = element_blank(),
+#         panel.margin = grid::unit(c(0.01, 0.01, 0.01, 0.01), "mm"))
+# 
+# Lines1<-data.frame(x=c(0,10,20,30),
+#                   y=c(10,0,0,0),
+#                   xend=c(40.1,10,20,30),
+#                   yend=c(10,10,10,10))
+# 
+# labels1<-data.frame(name = c("A","B","C","D","E"),
+#                    x= c(1,1,11,21,31),
+#                    y=c(29,9,9,9,9))
+# 
+# ggplot(expand_grid(x = 0:40,y=0:30),aes(x = x, y = y) ) +
+#   geom_point(alpha=0) +
+#   coord_fixed()+
+#   ggplot2::annotation_custom(Magno, 0,10, 10, 30) +
+#   ggplot2::annotation_custom(Brown, 0,10, 0, 10)+
+#   ggplot2::annotation_custom(Red, 10,20, 0, 10)+
+#   ggplot2::annotation_custom(green, 20,30, 0, 10)+
+#   ggplot2::annotation_custom(MPB, 30,40, 0,10)+
+#   geom_segment(data=Lines1,aes(x=x,y=y,xend=xend,yend=yend),
+#                colour="white",linewidth=2)+
+#   ggplot2::annotation_custom(ggplotGrob(spectra), 10,40, 10,30)+
+#   geom_label(data=labels1,aes(x=x,y=y,label=name), size = 10)+
+#   theme_void()+
+#   theme(axis.title.x = element_blank(),
+#         axis.title.y = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.text.y = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         axis.ticks.y = element_blank(),
+#         plot.margin = grid::unit(c(0.01,0.01,0.01,0.01), "mm"),
+#         # rect = element_blank(),
+#         panel.margin = grid::unit(c(0.01, 0.01, 0.01, 0.01), "mm"),
+#         legend.text.align = 0)
+
+Magno<-ggplot()+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Magnoliopsida_cropped2.png"))+
+  coord_equal()+
+  geom_label(aes(x = 50,y= 950, label = "A"))+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+Brown<-ggplot()+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Pheophyceae_cropped.png"))+
+  coord_equal()+
+  geom_label(aes(x = 50,y=450, label = "B"))+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+Red <- ggplot()+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Rodophyceae_cropped.png"))+
+  coord_equal()+
+  geom_label(aes(x = 50,y=450, label = "C"))+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+green <- ggplot()+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Chlorophyceae_cropped.png"))+
+  coord_equal()+
+  geom_label(aes(x = 50,y=450, label = "D"))+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+MPB <- ggplot()+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Bacillariophyceae_cropped.png"))+
+  coord_equal()+
+  geom_label(aes(x = 50,y=450, label = "E"))+
+  theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+layout <- c(
+  patchwork::area(t = 10, l = 0, b = 30, r = 10),
+    patchwork::area(t = 0, l = 0, b = 10, r = 10),
+    patchwork::area(t = 0, l = 10, b = 10, r = 20),
+    patchwork::area(t = 0, l = 20, b = 10, r = 30),
+    patchwork::area(t = 0, l = 30, b = 10, r = 40),
+    patchwork::area(t = 10, l = 10, b = 30, r = 40)
+)
+
+layout1 <- c(
+  patchwork::area(t = 1, l = 1, b = 20, r = 10),
+    patchwork::area(t = 20, l = 1, b = 29, r = 10),
+    patchwork::area(t = 20, l = 9, b = 29, r = 18),
+    patchwork::area(t = 20, l = 17, b = 29, r = 26),
+    patchwork::area(t = 20, l = 25, b = 29, r = 34),
+    patchwork::area(t = 1, l = 9, b = 20, r = 34)
+)
+
+# plot(layout1)
+
+plot<-Magno+
+  Brown+
+  Red+
+  green+
+  MPB+
+  sp+
+  patchwork::plot_layout(design=layout1)
+
+ggsave("Figures/Spectral_shapes_total.png",plot, height = 7, width = 10, dpi = 800)
+```
+
+```{r Figure2 Plot}
+#| cache: true
+#| echo: false
+#| warning: false
+#| fig-cap: Class of vegetation used to train the CNN model and their standardised spectral signature
+#| label: fig-vegetation
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("Figures/Spectral_shapes_total.png")
+```
+
+## Intertidal vegetation mapping
+
+```{r Figure3 text opening}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+layout<-"Data/Figure2_Workflow" %>%
+  list.files("V4.txt",full.names = T, recursive = T) %>%
+  read_delim(delim = "\t", escape_double = FALSE,
+    trim_ws = TRUE) %>%
+  dplyr::filter(Evaluate == T)
+
+layout$Text<- gsub("alaligne","\n", layout$Text)
+
+boxes<- layout %>% 
+  dplyr::filter(Type == "Box",
+                shape == "square")
+
+text<- layout %>% 
+  dplyr::filter(Type == "Box")
+
+diamonds<- layout %>% 
+  dplyr::filter(Type == "Box",
+                shape == "diamond")
+diff = 0.1
+for (i in 1:nrow(diamonds)) {
+  diam_a<-diamonds[i,]
+
+df<-data.frame(  
+  x = c(diam_a$xmin - diff, diam_a$xmin + diff, diam_a$xmax + diff, diam_a$xmax - diff),
+  y = c(diam_a$ymin, diam_a$ymax, diam_a$ymax, diam_a$ymin),
+  Type = rep(diam_a$Type,4),
+  Text = rep(diam_a$Text,4),
+  Color = rep(diam_a$color,4),
+  Evaluate = rep(diam_a$Evaluate,4),
+  Resolution =  rep(diam_a$Resolution,4),
+  Evaluate_bigbox = rep(diam_a$Evaluate_bigbox,4),
+  alpha = rep(diam_a$alpha,4),
+  shape =  rep(diam_a$shape,4)
+)
+  if(i == 1){
+    diamond_list<-list(df)
+  }else{
+    diamond_list[[i]]<-df
+  }
+}
+
+Arrows<- layout %>% 
+  dplyr::filter(Type == "Arrow",
+                Evaluate == T)
+
+Group_box<-layout %>% 
+  dplyr::filter(Type == "Box",
+                Evaluate_bigbox == T) %>% 
+  group_by(Group) %>% 
+  dplyr::summarise(xmin = min(xmin)-0.1,
+                   xmax = max(xmax)+0.1,
+                   ymin = min(ymin)-0.1,
+                   ymax = max(ymax)+0.1,
+                   alpha = 0.1,
+                   color = color)
+
+resolution_box<-layout %>% 
+  dplyr::filter(Type == "Box",
+                Resolution != "NA") %>% 
+  group_by(Resolution) %>% 
+  dplyr::summarise(xmin = min(xmin)-0.1,
+                   xmax = max(xmax)+0.1,
+                   ymin = min(ymin)-0.1,
+                   ymax = max(ymax)+0.1,
+                   alpha = 0.1,
+                   color = color)
+
+legend = data.frame(color = unique(layout$color)) %>% 
+  dplyr::filter(!is.na(color)) %>% 
+  mutate(label = case_when(color == "#EA6155" ~ "Input Data",
+                           color == "#DC9614" ~ "Pre-processing",
+                           color == "#52A4DA" ~ "Model Building",
+                           color == "#79DA52" ~ "Validation",
+                           color == "#DA9652" ~ "Output Data",
+                           color == "darkcyan" ~ "Final Product",
+                           color == "#DA5273"  ~ "Prediction",
+                           TRUE ~ "NA")) %>% 
+  arrange
+
+segment<-layout %>% 
+  dplyr::filter(Type == "Segment")
+
+```
+
+```{r Figure3 building}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+building <- F
+
+if(building == T){
+
+text_size = 6 #### 6 to plot it fullscreen in R,  1.8 for exporting with ggsave
+line_size =1 ####arrow_size 0.3 to export  1 to for R plotting
+
+legend_size = 1 #### 0.3 to export, 1 for R ploting
+legend_text = 10 #### 4 to export, 10 for R ploting
+}else{
+
+text_size = 1.85 #### 6 to plot it fullscreen in R,  1.8 for exporting with ggsave
+line_size =0.3 ####arrow_size 0.3 to export  1 to for R plotting
+
+legend_size = 0.3 #### 0.3 to export, 1 for R ploting
+legend_text = 5 #### 5 to export, 10 for R ploting
+
+}
+
+a<-ggplot()+
+
+  statebins:::geom_rrect(data = Group_box,
+            mapping = aes(xmin = xmin,
+                          xmax= xmax,
+                          ymin = ymin,
+                          ymax = ymax),
+            alpha = 0.05,
+            size = 0.2,
+            show.legend = F,
+            fill = Group_box$color,
+            color = "black")+
+
+    statebins:::geom_rrect(data = resolution_box,
+            mapping = aes(xmin = xmin,
+                          xmax= xmax,
+                          ymin = ymin,
+                          ymax = ymax,
+                          alpha = rep(c("Input Data", "Pre-processing", "Model Building", "Prediction", "Validation", "Output Data", "Final Product"),2)),
+            fill = "NA",
+            linetype = 2,
+            size = 0.4,
+            color = "black")+
+
+  scale_alpha_manual(name = "", 
+                     values = c(1,1,1,1,1,1,1),
+                     labels = c("Input Data", "Pre-Processing", "Model Building", "Prediction", "Validation", "Output Data", "Final Product"),
+                     guide = guide_legend(ncol = 1, override.aes = list(fill = c("#f94144", "#f3722c", "#f8961e", "#f9c74f", "#90be6d", "#43aa8b", "#577590"),
+                                                                        shape = c(22),
+                                                                        linetype = c(1),
+                                                                        alpha = c(0.5)
+                                                                        )
+                                          )
+                     )+
+
+  statebins:::geom_rrect(data = boxes,
+            mapping = aes(xmin = xmin,
+                          xmax= xmax,
+                          ymin = ymin,
+                          ymax = ymax
+                          ),
+            size = 0.2,
+            alpha = as.numeric(boxes$alpha),
+            fill = boxes$color,
+            color = "black")
+
+  for(i in 1:length(diamond_list)){
+    poly_i<-diamond_list[[i]]
+    a<-a+
+      geom_polygon(data = poly_i, 
+                   mapping = aes(x = x, 
+                                 y = y
+                                 ),
+                  size = 0.2,
+                   alpha = poly_i$alpha,
+                   fill = poly_i$Color,
+                   color = "black")
+
+  }
+
+if(building == T){
+    a<-a+
+    geom_text(data = text,
+            mapping = aes(x = (xmax+xmin)/2, y = (ymax + ymin)/2, label = (ID)), size = text_size)
+
+}else{
+    a<-a+
+    geom_text(data = text,
+            mapping = aes(x = (xmax+xmin)/2, y = (ymax + ymin)/2, label = (Text)), size = text_size)
+}
+
+  a<-a+
+    geom_segment(data = Arrows, aes( x = xmin, xend = xmax, y = ymin, yend = ymax),
+    size=line_size, linejoin = "mitre", lineend = "butt",
+    arrow = arrow(length = unit(1, "mm"), type= "closed")
+    )+
+    geom_segment(data = segment, aes( x = xmin, xend = xmax, y = ymin, yend = ymax),
+    size=line_size, linejoin = "mitre", lineend = "square"
+    )+
+
+  geom_text(aes(x = -5.4, y = -2, label = "Flight height: 12 m \n Pixel size : 8 mm", angle = 90), size = text_size+1)+
+
+  geom_text(aes(x = -5.4, y = -6.8, label = "Flight height: 120 m \n Pixel size : 80 mm", angle = 90), size = text_size+1)+
+
+  geom_text(aes(x = 4, y = 1.75, label = "Pre Processing"), size = text_size)
+
+  if(building == F){
+  a<- a+ theme_void()
+  }
+
+  a<-a+
+  theme(legend.position = c(0.88,0.3),
+        legend.text = element_text(size = legend_text),
+        legend.key.size = unit(legend_size, 'cm')
+        )+
+  scale_x_continuous(breaks = scales::breaks_width(0.5))+
+  scale_y_continuous(breaks = scales::breaks_width(0.5))
+
+if(building == T){
+a
+}else{
+  ggsave("Figures/Figure3_workflow.png",a, width = 1920, height = 1129, units = "px")
+}
+
+```
+
+```{r Figure3}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: "Schematic representation of the workflow.
+Diamonds represent input or output data, and rectangles represent Python processing algorithms.
+The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights were utilized for training and prediction of the CNN model, whereas low-resolution flights were solely employed for prediction purposes."
+#| label: fig-workflow
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Figure3_workflow.png")
+
+```
+
+The spectral similarities of reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
+To overcome this challenge, a deep learning classification method was developed, trained, validated, and applied to each drone flight (@fig-workflow).
+
+### Neural Network model building
+
+```{r loading df_training}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+df_training<-"Data/training/TrainandValid_NewStanRawMetrics.csv" %>% 
+  read_delim(delim = ";", escape_double = FALSE, trim_ws = TRUE) %>% 
+  dplyr::filter(True_Class != "Xanthophyceae",
+                True_Class != "Deep_Sediment",
+                True_Class != "Water",
+                True_Class != "SunGlint",
+                True_Class != "Bare_Sediment") %>% 
+  mutate(True_Class = case_when(True_Class == "Clorophyta" ~ "Chlorophyceae",
+                               True_Class == "Rhodphyta" ~ "Rhodophyceae",
+                               True_Class == "MPB" ~ "Bacillariophyceae",
+                               True_Class == "Magnoliosida" ~ "Magnoliopsida",
+                               True_Class == "Phaeophyta" ~ "Phaeophyceae",
+                               True_Class == "Low_SPC" ~ "Magnoliopsida",
+                               TRUE ~ "NA"
+                               )) %>% 
+  group_by(True_Class) %>% 
+  summarise(n = n()) %>% 
+  rename(True = "True_Class", 
+         Training_Pixels = "n")
+
+write.csv(df_training,"Data/training/TrainandValid_NewStanRawMetrics_Processed.csv",row.names = F)
+
+```
+
+```{r}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: true
+
+df_training<-read.csv("Data/training/TrainandValid_NewStanRawMetrics_Processed.csv")
+```
+
+```{r Table2 process}
+#| echo: false
+#| warning: false
+#| cache: true
+#| eval: false
+
+df_validation<-"Data/accuracy_assesment_low&high_flights.csv" %>% 
+  read_delim(delim = ",", escape_double = FALSE, trim_ws = TRUE) %>% 
+  dplyr::filter(True != "Sediment",
+                True != "Sun Glint",
+                True != "Water",
+                True != "Xanthophyceae") %>% 
+  mutate(True = case_when(True == "Green Algae" ~ "Chlorophyceae",
+                          True == "Microphytobenthos" ~ "Bacillariophyceae",
+                          True == "Rhodophyceae" ~ "Rhodophyceae",
+                          True == "Pheophyceae" ~ "Phaeophyceae",
+                          TRUE ~ True)) %>% 
+  group_by(True) %>% 
+  summarise(n = n())
+
+write.csv(df_validation,"Data/training/TrainandValid_NewStanRawMetrics_Processed_valid.csv",row.names = F)
+
+```
+
+```{r Table2}
+#| echo: false
+#| warning: false
+#| tbl-cap: Vegetation Classes of the model and the number of pixels used to train and validate each class
+#| cache: true
+
+df_validation<-read.csv("Data/training/TrainandValid_NewStanRawMetrics_Processed_valid.csv")
+
+df_training %>% 
+  left_join(df_validation, by = "True") %>% 
+  rename(`Validation Pixels` = "n",
+         Class = "True",
+         `Training Pixels` = "Training_Pixels") %>% 
+  flextable() %>% 
+  # border_remove() %>%
+  flextable::align(align = "center",part = "all") %>%
+  flextable::align(align = "center",part = "header") %>% 
+  set_table_properties(layout = "autofit")
+
+```
+
+A dataset containing photo-interpreted drone reflectance pixels was built to train a Convolutional Neural Network (CNN) model with 2 hidden layers.
+The training pixels were categorized into 7 different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
+Only low-altitude flights (Table 1) were used for training purposes because of their 8 mm spatial resolution allowing to avoid spectral sub-pixel mixing and to accurately visually differentiate various vegetation classes.
+More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights have been used to train the model (Table 2).
+Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @cao2017) and the NDVI (@eq-ndvi).
+Standardisation of spectral bands is used to eliminate the scaling differences between spectra and to limit the effect of biomass on the shape of the spectra [@Douay2022 ; @Davies2023].
+
+$$
+R_{i}^{*}(\lambda) = \frac{R_{i}(\lambda) - min(R_{i})}{max(R_{i})- min(R_{i})}
+$$ {#eq-std}
+
+where $R_{i}(\lambda)$ is the reflectance at the wavelength $(\lambda)$ of each individual spectra $(i)$, $min(R_{i})$, and $max(R_{i})$ are the minimum and maximum value of the spectra $(i)$
+
+$$
+NDVI = \frac{R(840nm)-R(668nm)}{R(840nm)+R(668nm)}
+$$ {#eq-ndvi}
+
+where $R(840nm)$ is the reflectance at 840 nm and $R(668nm)$ is the reflectance at 668 nm.
+
+### Validation
+
+```{r Validation Pixel Count}
+#| echo: false
+#| warning: false
+#| cache: true
+#| eval: false
+
+df<-"Output/Validation_data" %>% 
+  list.files("ResultsNewNN_NoXanthowithNDVIWithOldandBoat.csv",recursive = T, full.names = T) %>% 
+  read.csv() %>% 
+  as_tibble() %>% 
+  rename(Truth_ID = "Truth") %>% 
+  mutate(Truth =  case_when(Truth_ID == 1 ~ "Bare_Sediment",
+                          Truth_ID == 2 ~ "Chlorophyta",
+                          Truth_ID == 3 ~ "Bare_Sediment",
+                          Truth_ID == 4 ~ "Magnoliosida",
+                          Truth_ID == 5 ~ "Bare_Sediment",
+                          Truth_ID == 6 ~ "Magnoliosida",
+                          Truth_ID == 7 ~ "Phaeophyta",
+                          Truth_ID == 8 ~ "Rhodphyta",
+                          Truth_ID == 9 ~ "SunGlint",
+                          Truth_ID == 10 ~ "Water",
+                          Truth_ID == 11 ~ "Xanthophyceae",
+                          Truth_ID == 12 ~ "Spartina",
+                          Truth_ID == 41 ~ "Bleached seagrasses",
+                          TRUE ~ "NA"),
+         Pred_Class = case_when(Pred_Class == "Clorophyta" ~ "Chlorophyta",
+                                Pred_Class == "Rhodphyta" ~ "Rhodphyta",
+                                Pred_Class == "Deep_Sediment" ~ "Bare_Sediment",
+                                Pred_Class == "MPB" ~ "Bare_Sediment",
+                                (Pred_Class == "Low_SPC" & NDVI > 0.2) ~ "Magnoliosida",
+                                (Pred_Class == "Low_SPC" & NDVI <= 0.2 )~ "Bare_Sediment",
+                          TRUE ~ Pred_Class)) %>% 
+  dplyr::filter(Truth != "Water",
+                Truth  != "Spartina",
+                Truth != "SunGlint",
+                Truth != "Bleached seagrasses",
+                Truth != "Xanthophyceae",
+                # Pred_Class != "Low_SPC",
+                Pred_Class != "Xanthophyceae",
+                 Pred_Class != "Water",
+                 Pred_Class != "SunGlint",
+                !Flight == "Handfisher_1_old",
+                !Flight == "Handfisher_2_old",
+                !Flight == "Handfisher_2") %>%
+  dplyr::select(-NDVI)
+
+count_validation_pixel<-nrow(df)
+write.csv(count_validation_pixel,"Output/count_validation_pixel.csv", row.names = F)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| cache: true
+
+count_validation_pixel<-read.csv("Output/count_validation_pixel.csv") %>% 
+  pull(x)
+```
+
+The CNN model was applied to all the 9 flights at both 12 and 120 m of altitude.
+In situ information on georeferenced class type and percent cover collected during each flight has been used to assess the CNN accuracy.
+These images were used to construct a validation dataset indicating the presence or absence of each class.
+Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.
+A confusion matrix, along with precision metrics such as the global accuracy, the sensitivity, the specificity, and the Kappa coefficient, was generated for each of the study sites.
+Finally each validation matrix has been merge to create a unique matrix of the model.
+A total of `r my_comma(round(count_validation_pixel,-3))` pixels has been used to globally validate the CNN model.
+
+# Results
+
+## Classification
+
+A total of 9 prediction maps corresponding to the 9 drone flights were obtained.
+Each prediction map is associated with a probability map, indicating the probability of the selected class for every pixel.
+The low-altitude flight conducted in Gafanaha, Portugal, represents the site with the highest complexity (@fig-GafLow).
+Among the 5 vegetation classes on which the CNN model was trained, 4 were present on this site.
+On this site, there is a mixture of Chlorophyceae and Rhodophyceae over the seagrass meadow.
+This is also where Bacillariophyceae is most abundant.
+Although the seagrass bed is solely composed of *Zostera noltei*, various colors can be observed: dark green (indicating healthy beds with 100% coverage) and whitish/brown (indicating beds where leaves are dying).
+Regardless of the color, the meadow is predicted as Magnoliopsida by the CNN model.
+
+```{r Figure 4 Gaf Low}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
+  list.files(pattern = ".shp", recursive = T, full.names = T) %>%
+  read_sf() %>%
+  mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
+                        name == "ZOS" ~ 2,
+                        name == "BL" ~ 3,
+                        name == "SED" ~ 4,
+                        name == "GRE" ~ 5,
+                        name == "RED" ~ 6,
+                        name == "Xanthophyceae" ~ 7)) %>% 
+  as("Spatial") %>% 
+  vect()
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
+  pull(path) %>% 
+  read_sf()
+###### Preview ###########
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Gafanha"
+  ) ,
+  Description = c("12m and 120m Flights"),
+  Long=c(-8.742485) ,
+  Lat=c(40.597599) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 18,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+######### RGB #########
+ Gafanha_low_ortho<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() 
+ names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
+
+ values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
+
+ Gafanha_low_ortho_zoomed<-Gafanha_low_ortho %>% 
+   crop(zoom_extent)
+
+ map_extent_full<- st_as_sf(as.polygons(ext(Gafanha_low_ortho)))
+ sf::st_crs(map_extent_full)<-st_crs(Gafanha_low_ortho)
+
+  map_extent_zommed<- st_as_sf(as.polygons(ext(Gafanha_low_ortho_zoomed)))
+ sf::st_crs(map_extent_zommed)<-st_crs(Gafanha_low_ortho_zoomed)
+
+ rgb_Gafanha_low_zoomed<-ggplot()+
+   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed, 
+                                  r = 3,
+                                  g = 2,
+                                  b = 1)+
+   theme_Bede_Map()+
+   geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+   coord_sf(crs = 4326)+
+     theme_void()
+
+ scale_labels<-data.frame(x = c(-8.74368, -8.743565,-8.74342),
+                          y = c(rep(40.59792,3)),
+                          text = c("0","10","20 m"))
+
+  rgb_Gafanha_low<- ggplot()+
+  scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="grey30")+
+   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
+         r = 1,
+         g = 2,
+         b = 3,
+         maxcell = 4010533
+         )+
+    ggspatial::annotation_scale(location = "tl",
+                                text_cex=2)+
+      annotation_custom(ggplotGrob(p1),
+                        xmin = -8.7430,
+                        xmax = -8.742702,
+                        ymin = 40.5970515, 
+                        ymax = 40.5974) +
+   theme_Bede_Map()+
+   geom_sf(data = zoom_extent, 
+           fill = "transparent",
+           colour = "black",
+           linetype = "dashed", 
+           linewidth = 1)+
+   coord_sf(crs = 4326)+
+  annotation_custom(ggplotGrob(rgb_Gafanha_low_zoomed),
+                    xmin = -8.7430,
+                    xmax=-8.7427,
+                    ymin = 40.5977) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
+                              y=c(40.5976275,40.5979,40.5975373,40.59771),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  theme(axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+        axis.text.x = element_text(size = 20, angle = 20, hjust = 1))+
+    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
+    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
+
+ggsave("Figures/Gaf_Low_RGB.png",rgb_Gafanha_low , width = 1920*4, height = 1129*4, units = "px")
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+####### Zoomed map ########
+
+Gafanha_low_pred_zoomed<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "low",
+       type == "Pred",
+       resampled == "FALSE",
+       folder == "Input",
+       new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred_zoomed)<-"layer"
+
+Gafanha_low_pred_zoomed<-Gafanha_low_pred_zoomed %>% 
+  crop(zoom_extent)
+Gafanha_low_pred_zoomed<-as.factor(Gafanha_low_pred_zoomed)
+
+Gafanha_low_pred_map_zoomed<-ggplot()+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer))+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  coord_sf(crs = 4326)+
+  scale_fill_manual(values=c("#70543e", "#b3ff1a","#70543e", "#DAA520", "#389318","#873e23","#b3002d", NA, "#42c9bc"), na.value = NA)+
+  theme_void()+
+  # coord_equal()+
+  theme(axis.text.x = element_blank(),
+      axis.text.y = element_blank(),
+      axis.title = element_blank())+
+  theme(legend.position = "none")
+ # Gafanha_low_pred_map_zoomed
+
+####  Overall map
+Gafanha_low_pred<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "low",
+       type == "Pred",
+       # resampled == "TRUE",
+       new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred)<-"layer"
+
+values(Gafanha_low_pred)[values(Gafanha_low_pred) == 0] = NA
+
+Gafanha_low_pred<-Gafanha_low_pred %>% 
+  as.factor()
+
+####### Pred ######
+
+Gafanha_low_pred_map <-
+  ggplot()+
+  scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="grey30")+
+  # geom_sf(data = background_GafHigh,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=1,
+  #         colour="white")+
+   ggnewscale::new_scale("fill")+
+    tidyterra::geom_spatraster(data = Gafanha_low_pred, 
+                               mapping = aes(fill = layer),
+                               maxcell = 500832*8)+
+  geom_sf(data = zoom_extent, 
+          fill = "transparent", 
+          colour = "black",
+          linetype = "dashed", 
+          linewidth = 1)+
+  coord_sf(crs = 4326)+
+  annotation_custom(ggplotGrob(Gafanha_low_pred_map_zoomed), 
+                    xmin = -8.7430,
+                    xmax=-8.7427, 
+                    ymin = 40.5977) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
+                              y=c(40.5976275,40.5979,40.5975373,40.59771),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  theme_Bede_Map()+
+  # coord_equal()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         # axis.text.y = element_text(size = 20),
+         axis.text.y = element_blank(),
+         axis.title = element_blank(),
+         legend.background = element_blank(),
+         legend.position = c(0.98,0.3),
+         legend.text = element_text(size = 20),
+         legend.key.size = unit(1,"cm"))+
+    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
+    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
+
+ggsave("Figures/Gaf_Low_Pred.png",Gafanha_low_pred_map , width = 1920*4, height = 1129*4, units = "px")
+
+################# PLOT AND SAVING ###########
+
+plot_Gaf_Low<-rgb_Gafanha_low+
+  Gafanha_low_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Gaf_Low_Pred.png",plot_Gaf_Low , width = 1920*4, height = 1009*4, units = "px")
+```
+
+```{r Figure 4 Gaf Low plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanaha, Portugal.
+The total extent of this flight is 3000m² with a resolution of 8 mm per pixel.
+Background colors means intertidal area (Light Green) and land area (Light Grey).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-GafLow
+#| fig-width: 10
+#| fig-height: 8
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_Low_Pred.png")
+
+```
+
+```{r Figure 4 V2}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+imglist<-
+  data.frame("Data",
+             path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path,"AveiroHigh")~"Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+########## ZOOM #############
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+mask_low<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"mask_Gafanha_low")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Gafanha_low_ortho_zoomed<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() %>% 
+  crop(zoom_extent)
+
+names(Gafanha_low_ortho_zoomed)<-c("B1", "B3", "B5","alpha")
+
+ Gafanha_low_pred_zoomed<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "Pred",
+         # resampled == "TRUE",
+         new == "TRUE") %>% 
+  pull(path) %>% 
+  rast() %>% 
+  crop(zoom_extent) %>% 
+  mask(mask_low, inverse = T) %>% 
+   as.factor()
+
+names(Gafanha_low_pred_zoomed)<-"layer"
+
+zoomed_low_map<-ggplot()+
+  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed,
+                                 r = 1,
+                                 g = 2,
+                                 b = 3)+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer), show.legend = F)+
+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
+                    na.value = NA,
+                    name = "", 
+                    labels = c("Sediment", 
+                               "Chlorophyceae", 
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 2)+
+  theme(legend.position = "none")+
+  theme_void()
+
+#############
+
+ Gafanha_low_ortho<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() 
+ names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
+values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
+
+ Gafanha_low_pred<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "Pred",
+         # resampled == "TRUE",
+         new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred)<-"layer"
+
+Gafanha_low_pred_masked<-Gafanha_low_pred %>% 
+  # crop(mask_low) %>% 
+  mask(mask_low, inverse = T)
+
+values(Gafanha_low_pred_masked)[values(Gafanha_low_pred_masked) == 0] = NA
+
+Gafanha_low_pred_masked<-Gafanha_low_pred_masked %>% 
+  as.factor()
+
+rgb_Gafanha_low <- ggplot()+
+  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
+                                 r = 1,
+                                 g = 2,
+                                 b = 3)+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_masked, mapping = aes(fill = layer))+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
+                    na.value = NA,
+                    name = "", 
+                    labels = c("Sediment", 
+                               "Chlorophyceae", 
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggspatial::annotation_scale(location = "bl",text_cex=2)+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+
+  geom_segment(aes(x = -8.7434247325, y=40.5977530006, xend = -8.7430558162, yend = 40.5972152706), linetype ="dashed" ,linewidth=2)+
+  annotation_custom(ggplotGrob(zoomed_low_map), xmin = -8.743725, xmax = -8.7434057328, ymin = 40.5977200450, ymax = 40.59798) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74336194,-8.74371,-8.743243794,-8.7434057328), y=c(40.59762751,40.5977400850,40.59762725,40.5977200450),grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  theme_Bede_Map()+
+  coord_sf(crs = 4326)+
+  theme(axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+        axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+        legend.position=c(0.3, 0.3))+
+  # ggtitle("a ")+
+  scale_x_continuous(breaks=seq(-8.7437, -8.7430, 0.0002))
+rgb_Gafanha_low
+
+ggsave("Figures/Gaf_Low_RGB_Pred_V2.png",rgb_Gafanha_low , width = 890*4, height = 1120*4, units = "px")
+
+```
+
+The high-altitude flight over Gafanha covered nearly 1 km² in total (@fig-GafHigh).
+A channel delineating a small island was present in the flight, but it has been masked in the prediction map due to glinting and misclassification caused by the turbid shallow water.
+Most of the intertidal area has been classified as Magnoliopsida by the model, even though there is discoloration of seagrass blades.
+Only a few pixels have been classified as Chlorophyceae at this scale.
+Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remains mostly classified as such in the high-altitude flight, but some pixels of it are now classified as Magnoliopsida.
+The patches of Rhodophyceae are still well classified.
+*Spartina sp.* was present in the northern part of the flight, near the land, and has been classified either as Magnoliopsida or as Phaeophyceae.
+
+```{r Figure 5 Gaf High}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+#### Preview ####
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Gafanha"
+  ) ,
+  Description = c("12m and 120m Flights"),
+  Long=c(-8.742485) ,
+  Lat=c(40.597599) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 20,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+
+#####
+
+land_mask_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "mask_Gafanha_high1")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+GafHigh_ortho<-imglist %>% 
+  dplyr::filter(site == "Gafanha",
+                type == "ortho",
+                alt=="high",
+                col == "TRUE") %>%
+  pull(path) %>% 
+  rast()
+names(GafHigh_ortho)<-c("B1","B3", "B5", "alpha")
+
+# values(GafHigh_ortho)[values(GafHigh_ortho$B1) == 0] = NA
+
+GafHigh_ortho_masked<-GafHigh_ortho %>% 
+  mask(land_mask_GafHigh, inverse = F) %>% 
+  crop(land_mask_GafHigh)
+
+GafHigh_ortho_masked<-na.omit(GafHigh_ortho_masked, field=NA, geom=FALSE)
+
+###### RGB ########
+zoom_gaf_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_High_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Gaflow_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"GafLow_extent.shp")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+rgb_Gafanha_High_zoomed<-GafHigh_ortho_masked %>% 
+  crop(zoom_gaf_high_sf)
+
+rgb_Gafanha_High_zoomed<-
+  ggplot()+
+  tidyterra::geom_spatraster_rgb(data = rgb_Gafanha_High_zoomed,
+         r = 1,
+         g = 2,
+         b = 3)+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  theme_void()
+
+rgb_Gafanha_High <- ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+   tidyterra::geom_spatraster_rgb(data = GafHigh_ortho_masked,
+         r = 1,
+         g = 2,
+         b = 3,
+         maxcell = 5007120)+
+    ggspatial::annotation_scale(location = "bl",
+                                text_cex=2)+
+    annotation_custom(ggplotGrob(p1), 
+                      xmin = -8.744, 
+                      xmax = -8.7412,
+                      ymin = 40.5923,
+                      ymax = 40.595) +
+    geom_sf(data = zoom_gaf_high_sf,
+            fill = "transparent", 
+            colour = "black",
+            linetype = "dashed", 
+            linewidth = 1)+
+    geom_sf(data = Gaflow_extent,
+            fill = "transparent", 
+            colour = "red",
+            linetype = "dashed", 
+            linewidth = 2)+
+    geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
+                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  annotation_custom(ggplotGrob(rgb_Gafanha_High_zoomed),
+                    xmin = -8.7479, 
+                    xmax = -8.7452, 
+                    ymin = 40.5979,
+                    ymax = 40.603) +
+   theme_Bede_Map()+
+   coord_sf(crs = 4326)+
+   # xlim(c(-8.748, -8.741))+
+  # ylim(c(40.593,40.601))+
+  theme(axis.title = element_blank(),
+         axis.text.x = element_text(size = 20, angle = 20, hjust = 1),
+         axis.text.y = element_text(size = 20))+
+  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
+  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
+# rgb_Gafanha_High
+
+ggsave("Figures/Gaf_High_RGB.png",rgb_Gafanha_High , width = 712*4, height = 1120*4, units = "px")
+
+######### Pred #######
+Gafanha_high_pred<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "high",
+       type == "Pred",
+       new == "TRUE",
+       !str_detect(path, "Probs")) %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_high_pred)<-"layer"
+
+GafHigh_pred_masked<-Gafanha_high_pred %>% 
+  mask(land_mask_GafHigh, inverse = F) %>% 
+  crop(land_mask_GafHigh)
+
+GafHigh_pred_masked<-na.omit(GafHigh_pred_masked, field=NA, geom=FALSE)
+
+values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 0] = NA
+values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 3] = 1
+
+GafHigh_pred_masked<-GafHigh_pred_masked %>% 
+  as.factor()
+
+Gafanha_High_zoomed_pred<-GafHigh_pred_masked %>% 
+  crop(zoom_gaf_high_sf)
+
+Gafanha_High_zoomed_pred<-
+  ggplot()+
+   tidyterra::geom_spatraster(data = Gafanha_High_zoomed_pred, mapping = aes(fill = layer),
+                            show.legend = F,
+                             maxcell = 5007120)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  theme_void()
+
+Gafanha_high_pred_map<-ggplot()+
+  geom_sf(data = background_GafHigh, 
+          mapping = aes(fill = Type),
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+    scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = GafHigh_pred_masked, 
+                             # show.legend = F,
+                             mapping = aes(fill = layer),
+                             maxcell = 5010420)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+       geom_sf(data = zoom_gaf_high_sf, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+    geom_sf(data = Gaflow_extent,
+            fill = "transparent", 
+            colour = "red",
+            linetype = "dashed", 
+            linewidth = 2)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
+                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  annotation_custom(ggplotGrob(Gafanha_High_zoomed_pred), 
+                    xmin = -8.7479, 
+                    xmax = -8.7452, 
+                    ymin = 40.5979,
+                    ymax = 40.603) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         axis.title = element_blank(),
+        # axis.text.y = element_text(size = 20),
+        axis.text.y = element_blank(),
+         legend.background = element_blank(),
+         legend.position = c(0.96,0.23),
+         legend.text = element_text(size = 23),
+         legend.key.size = unit(1.2,"cm"))+
+  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
+  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
+# Gafanha_high_pred_map
+
+ggsave("Figures/Gaf_High_Pred.png",Gafanha_high_pred_map , width = 712*4, height = 1120*4, units = "px")
+
+################# PLOT AND SAVING ###########
+plot_GafHigh<-rgb_Gafanha_High+
+  Gafanha_high_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Gaf_High_Pred.png",plot_GafHigh , width = 2105*4, height = 1363*4, units = "px")
+
+#########
+
+```
+
+```{r Figure 5 Gaf High plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanaha, Portugal.
+The total extent of this flight is about 1 km² with a resolution of 80 mm per pixel.
+Background colors means intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+The red triangle shows the extent of the low altitude flight of Gafanha.
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-GafHigh
+#| fig-width: 10
+#| fig-height: 8
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_High_Pred.png")
+
+```
+
+The High altitude flight made in the inner lagoon of the Ria de Aveiro is the largest of all flights, covering almost 1.5 km² (@fig-Boat).
+On this site, only seagrass and red algae where seen on the field.
+The classification follows the same pattern, with a patchy Magnoliopsida meadow mixed on the eastern part of the flight with Rhodophyceae.
+As shown in the zoom (@fig-Boat), the edges of the meadow can be colonised by Chlorophyceae.
+
+```{r Figure 6 Boat}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+########### PREVIEW #############
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Marinha Lanzarote"
+  ) ,
+  Description = c(
+                  "120m Flight"),
+  Long=c( 
+         -8.690677) ,
+  Lat=c(
+        40.665120) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,show.legend = F,colour="grey30")+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 10,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+##### ZOOM and masking #####
+
+Boat_rgb<-imglist %>% 
+  filter(str_detect(path,"Boat_high_RGB_merged.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat_rgb)<-c("B1","B3","B5")
+values(Boat_rgb)[values(Boat_rgb) == 0] = NA
+
+mask_boat<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "boat")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_Boat<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Boat")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_boat_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_boat_high_sf_2<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_2_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+rgb_Boat_zoomed<-Boat_rgb %>% 
+  crop(zoom_boat_high_sf)
+
+rgb_Boat_zoomed_2<-Boat_rgb %>% 
+  crop(zoom_boat_high_sf_2)
+
+Boat_rgb_mask<-Boat_rgb %>% 
+  mask(mask_boat, inverse = T)
+
+rgb_Boat_zoomed_map<- ggplot()+
+  geom_spatraster_rgb(data = rgb_Boat_zoomed,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      max_col_value = 4000)+
+  geom_sf(data = zoom_boat_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+
+  theme_void()
+
+rgb_Boat_zoomed_map_2
+ggplot()+
+  geom_spatraster_rgb(data = rgb_Boat_zoomed_2,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      interpolate = F,
+                      max_col_value = 4000)+
+  geom_sf(data = zoom_boat_high_sf_2, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+
+  theme_void()
+
+####### RGB ############
+
+RGB_Boat_map<-
+ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_Boat,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Boat,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+  tidyterra::geom_spatraster_rgb(data = Boat_rgb_mask,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      # maxcell = 5000,
+                      maxcell = 500832*8,
+                      max_col_value = 5000)+
+  geom_sf(data = zoom_boat_high_sf,
+          fill = "transparent",
+          colour = "black", 
+          linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf_2,
+          fill = "transparent",
+          colour = "black", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map),
+                    xmin = -8.6975,
+                    xmax = -8.69,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map_2),
+                    xmin = -8.6975+0.007,
+                    xmax = -8.69+0.007,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(p1),
+                    xmin = -8.6795,
+                    xmax = -8.6736,
+                    ymin = 40.6585,
+                    ymax = 40.6625) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
+                              y=c(40.66244282,40.66673,40.66244282,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+    geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
+                              y=c(40.6652874,40.66675,40.6652874,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  ggspatial::annotation_scale(location = "bl",
+                              text_cex=2)+
+  scale_x_continuous(limits = c(-8.6965,-8.675),
+                     breaks =  -8.685)+
+  scale_y_continuous(limits = c(40.659,40.6704),
+                     breaks =  40.664)+
+  theme_Bede_Map()+
+  theme(axis.title = element_blank(),
+        # axis.text.x = element_text(size = 20, angle = 20 , hjust = 1),
+        axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 20))+
+   coord_sf(crs = 4326)
+
+####### Pred ######## 
+Boat1_pred<-imglist %>% 
+  filter(str_detect(path,"AveiroBoat1_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat1_pred)<-"layer"
+
+Boat2_pred<-imglist %>% 
+  filter(str_detect(path,"AveiroBoat2_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat2_pred)<-"layer"
+
+values(Boat1_pred)[values(Boat1_pred) == 0] = NA
+values(Boat2_pred)[values(Boat2_pred) == 0] = NA
+
+B1_overextent<-ext(Boat1_pred)
+B1_overextent[2]<-ext(Boat2_pred)[2]
+B1_overextent[4]<-ext(Boat2_pred)[4]
+B1_overextent <- rast(B1_overextent)
+res(B1_overextent)<-res(Boat1_pred)
+# terra::writeRaster(B1$B1,"B1.tif")
+# terra::writeRaster(B2$B2,"B2.tif")
+
+B2_resampled <- terra::resample(Boat2_pred,B1_overextent, method = "near",threads = T)
+# terra::writeRaster(B2_resampled$B1,"B2_resampled.tif", overwrite = T)
+
+Boat_pred<-merge(Boat1_pred,B2_resampled)
+
+Boat_pred_aggregate<-terra::aggregate(Boat_pred,fact = 6, fun ="modal")
+
+masked_pred<-Boat_pred_aggregate %>% 
+  mask(mask_boat,inverse=TRUE)%>% 
+  as.factor()
+
+Boat_pred_zoom<-Boat1_pred %>% 
+  crop(zoom_boat_high_sf) %>% 
+  as.factor()
+
+Boat_pred_zoom_2<-Boat2_pred %>% 
+  crop(zoom_boat_high_sf_2) %>% 
+  as.factor()
+
+Boat_Pred_zoomed_map<- ggplot()+
+  tidyterra::geom_spatraster(data = Boat_pred_zoom, 
+                             mapping = aes(fill = layer), 
+                             show.legend = F,
+                             maxcell = 5010420)+
+  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorphyceae",
+                               "Magnoliopsida"))+
+  geom_sf(data = zoom_boat_high_sf, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  theme_void()
+
+Boat_Pred_zoomed_map_2<- ggplot()+
+  tidyterra::geom_spatraster(data = Boat_pred_zoom_2, 
+                             mapping = aes(fill = layer), 
+                             show.legend = F,
+                             maxcell = 5010420)+
+  scale_fill_manual(values=c("#70543e","#389318","#873e23","#b3002d"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae"))+
+  geom_sf(data = zoom_boat_high_sf_2, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  theme_void()
+
+Boat_pred_map<-ggplot()+
+  geom_sf(data = background_Boat, 
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Boat,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+    scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = masked_pred, 
+                             mapping = aes(fill = layer),
+                             # show.legend = F,
+                             maxcell = 5010420,
+                             )+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggnewscale::new_scale("fill")+
+  geom_sf(data = zoom_boat_high_sf, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf_2, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
+                              y=c(40.66244282,40.66673,40.66244282,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
+                              y=c(40.6652874,40.66675,40.6652874,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map),
+                    xmin = -8.6975,
+                    xmax = -8.69,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map_2),
+                    xmin = -8.6975+0.007,
+                    xmax = -8.69+0.007,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(
+     # axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+     axis.text.x = element_blank(),
+         axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+         legend.background = element_blank(),
+         legend.position = c(0.98,0.38),
+         legend.text = element_text(size = 18),
+         legend.key.size = unit(0.8,"cm"))+
+  scale_x_continuous(limits = c(-8.6965,-8.675),
+                     breaks =  -8.685)+
+  scale_y_continuous(limits = c(40.659,40.6704),
+                     breaks =  40.664)
+################# PLOT AND SAVING ###########
+plot_Boat<-RGB_Boat_map/
+  Boat_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Boat_Pred.png",plot_Boat , width = 1000*4, height = 1120*4, units = "px")
+
+```
+
+```{r Figure 6 Boat plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
+The total extent of this flight is about 1.5 km² with a resolution of 80 mm per pixel.
+Background colors means intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-Boat
+#| fig-width: 10
+#| fig-height: 4
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Maps Pred/FigX-Boat_Pred.png")
+
+```
+
+The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike crossing the northern part of the flight from west to east.
+Alongside this dike, brown algae attached to rocks and stranded green algae could be found.
+Despite the high mixture between Chlorophyceae and Magnoliopsida in this flight, these two classes are well discriminated by the classifier.
+
+```{r Figure 7 North Dike}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+##### Preview #####
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_BB <- filelist[str_detect(filelist,"mask_land_intertidal_BB")] %>% 
+  read_sf()
+
+Flight_BB<-data.frame(
+  Name=c(
+  "L'Epine"
+  ) ,
+  Description = c(
+                  "120m Flight"),
+  Long=c(
+         -2.228239) ,
+  Lat=c( 
+        46.989515) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_BB))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1 <- ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
+      coord_sf(xlim=c(550609,579539) ,
+          ylim=c(5189447,5218377) )+
+  ggforce::geom_mark_ellipse(data=Flight_BB,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 con.size = 2,
+                 label.fontsize = 10,
+                 label.hjust = 0.5,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+  # theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = c(0.95,0.2),
+        legend.key.size =  unit(1, "cm"),
+        legend.text = element_text(size = 20),
+        legend.title=element_blank(),
+        legend.background = element_rect(linewidth = 0.5, 
+                                         fill = "white",
+                                         linetype="solid", 
+                                  colour ="black"),
+        # panel.background = element_rect(fill = "#FFFFFF90"),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank())+
+  theme_void()
+
+##### RGB ######
+
+Dike_rgb<-imglist %>% 
+  filter(str_detect(path,"NorthDike_high_multi_4326_colored.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Dike_rgb)<-c("B1","B3","B5","alpha")
+values(Dike_rgb)[values(Dike_rgb$alpha) == 0] = NA
+
+mask_Dike<-"Data/shp/Bourgneuf" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "mask_NorthDike")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_Dike<-"Data/shp/Bourgneuf" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_Dike_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Dike_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Dike_rgb_masked<-Dike_rgb %>% 
+  crop(mask_Dike) %>%
+  mask(mask_Dike)
+
+zoom_rgb_dike<-Dike_rgb_masked %>% 
+  crop(zoom_Dike_high_sf)
+
+zoom_rgb_dike_map<-ggplot()+
+  geom_spatraster_rgb(data = zoom_rgb_dike,
+                      r = 3,
+                      g = 2,
+                      b = 1)+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  coord_sf(crs = 32630)+
+  theme_void()
+
+RGB_Dike_map <- ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_Dike,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Dike,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+  tidyterra::geom_spatraster_rgb(data = Dike_rgb_masked,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      # maxcell = 500,
+                      maxcell = 500832*8
+                      )+
+  geom_sf(data = zoom_Dike_high_sf, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(zoom_rgb_dike_map), 
+                    xmin = -2.226, 
+                    ymin = 46.9888,
+                    ymax = 46.9893) +
+  annotation_custom(ggplotGrob(p1),
+                    xmin = -2.226,
+                    ymin = 46.9875) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
+                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  ggspatial::annotation_scale(location = "tl",text_cex=2)+
+  scale_x_continuous(limits = c(-2.2293,-2.2253),
+                     breaks =  -2.228)+
+  scale_y_continuous(limits = c(46.9882,46.98935),
+                     breaks =  46.9890)+
+  theme_Bede_Map()+
+  theme(
+    # axis.text.x =element_text(size = 20, angle = 20, hjust = 1),
+    axis.text.x =element_blank(),
+        axis.title = element_blank(),
+        axis.text.y = element_text(size = 20))+
+   coord_sf(crs = 4326)
+
+##### Pred ######
+
+Dike_Pred<-imglist %>% 
+  filter(str_detect(path,"Noirmoutier_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7_4326.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Dike_Pred)<-c("layer")
+values(Dike_Pred)[values(Dike_Pred) == 0] = NA
+
+Dike_Pred_masked<-Dike_Pred %>% 
+  crop(mask_Dike) %>% 
+  mask(mask_Dike) %>% 
+  as.factor()
+
+zoom_Pred_dike<-Dike_Pred_masked %>% 
+  crop(zoom_Dike_high_sf)
+
+zoom_Pred_dike_map<-ggplot()+
+  tidyterra::geom_spatraster(data = zoom_Pred_dike, mapping = aes(fill = layer), show.legend = F)+
+  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23","#42c9bc"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorphyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Water"))+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  theme_void()
+
+Dike_pred_map<-ggplot()+
+  geom_sf(data = background_Dike, 
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_Dike,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+    scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = Dike_Pred_masked, 
+                             mapping = aes(fill = layer),
+                             maxcell = 5010420,
+                             )+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggnewscale::new_scale("fill")+
+  geom_sf(data = zoom_Dike_high_sf, 
+          fill = "transparent", 
+          colour = "black",
+          linetype = "dashed", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(zoom_Pred_dike_map), 
+                    xmin = -2.226, 
+                    ymin = 46.9888,
+                    ymax = 46.9893) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
+                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  # annotation_custom(ggplotGrob(Boat_Pred_zoomed_map), xmin = -8.697, xmax = -8.692, ymin = 40.667,ymax = 40.6705) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+         legend.background = element_blank(),
+         legend.position = c(1,0.50),
+         legend.text = element_text(size = 18),
+         legend.key.size = unit(0.8,"cm"))+
+  scale_x_continuous(limits = c(-2.2293,-2.2253),
+                     breaks =  -2.228)+
+  scale_y_continuous(limits = c(46.9882,46.98935),
+                     breaks =  46.9890)
+
+################# PLOT AND SAVING ###########
+
+plot_Dike<-RGB_Dike_map/
+  Dike_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Dike_Pred.png",plot_Dike , width = 1200*4, height = 900*4, units = "px")
+
+```
+
+```{r Figure 7 North Dike plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of Northern part of Noirmoutier Island, France.
+The total extent of this flight is about 28 000 m² with a resolution of 80 mm per pixel.
+Background colors means intertidal area (Light Green) and land area (Light Grey).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-Dike
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Maps Pred/FigX-Dike_Pred.png")
+```
+
+## Validation
+
+```{r Global Accuracy assesment}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: true
+
+df<-"Output/Validation_data" %>% 
+  list.files("ResultsNewNN_NoXanthowithNDVIWithOldandBoat.csv",recursive = T, full.names = T) %>% 
+  read.csv() %>% 
+  as_tibble() %>% 
+  rename(Truth_ID = "Truth") %>% 
+  mutate(Truth =  case_when(Truth_ID == 1 ~ "Sediment",
+                          Truth_ID == 2 ~ "Chlorophyceae",
+                          Truth_ID == 3 ~ "Sediment",
+                          Truth_ID == 4 ~ "Magnoliopsida",
+                          Truth_ID == 5 ~ "Bacillariophyceae",
+                          Truth_ID == 6 ~ "Magnoliopsida",
+                          Truth_ID == 7 ~ "Phaeophyceae",
+                          Truth_ID == 8 ~ "Rhodophyceae",
+                          Truth_ID == 9 ~ "SunGlint",
+                          Truth_ID == 10 ~ "Water",
+                          Truth_ID == 11 ~ "Xanthophyceae",
+                          Truth_ID == 12 ~ "Spartina",
+                          Truth_ID == 41 ~ "Bleached seagrasses",
+                          TRUE ~ "NA"),
+         Pred_Class = case_when(Pred_Class == "Clorophyta" ~ "Chlorophyceae",
+                                Pred_Class == "Phaeophyta" ~ "Phaeophyceae",
+                                Pred_Class == "Rhodphyta" ~ "Rhodophyceae",
+                                Pred_Class == "Deep_Sediment" ~ "Sediment",
+                                Pred_Class == "MPB" ~ "Bacillariophyceae",
+                                Pred_Class == "Bare_Sediment" ~ "Sediment",
+                                 Pred_Class == "Magnoliosida" ~ "Magnoliopsida",
+                                (Pred_Class == "Low_SPC" & NDVI > 0.2) ~ "Magnoliopsida",
+                                (Pred_Class == "Low_SPC" & NDVI <= 0.2 )~ "Sediment",
+                          TRUE ~ Pred_Class)) %>% 
+  dplyr::filter(Truth != "Water",
+                Truth  != "Spartina",
+                Truth != "SunGlint",
+                Truth != "Bleached seagrasses",
+                Truth != "Xanthophyceae",
+                # Pred_Class != "Low_SPC",
+                Pred_Class != "Xanthophyceae",
+                 Pred_Class != "Water",
+                 Pred_Class != "SunGlint",
+                !Flight == "Handfisher_1_old",
+                !Flight == "Handfisher_2_old",
+                !Flight == "Handfisher_2") %>%
+  dplyr::select(-NDVI)
+
+a<-as.character(unique(df$Truth))
+b<-as.character(unique(df$Pred_Class))
+ab<-setdiff(a,b)
+ba<-setdiff(b,a)
+
+if (!(length(ab) == 0 & length(ba) == 0)) {
+
+lines_to_add<-data.frame(Pred_Class = c(ab,ba),
+                         Pred_ID = NA,
+                         Flight = NA,
+                         Truth_ID = NA,
+                         Truth = c(ab,ba))
+
+df<-df %>% 
+  rbind(lines_to_add)
+  rm(lines_to_add)
+
+}
+
+  df<- df %>%
+  mutate(Pred_Class = as_factor(Pred_Class),
+         Truth = as_factor(Truth),
+         Truth = fct_relevel(Truth, c("Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae")),
+         Pred_Class = fct_relevel(Pred_Class, c("Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae")),
+         Flight = case_when(str_detect(Flight, "Boat") ~ "Boat",
+                            TRUE ~ Flight))
+
+####### GafanahaLow #######
+df_GafanhaLow<-df %>% 
+  filter(Flight == "GafanhaLow")
+
+validation_metrics_GafanhaLow<-confusionMatrix(df_GafanhaLow$Pred_Class,df_GafanhaLow$Truth)
+
+conf_mat_GafanhaLow<-validation_metrics_GafanhaLow[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_GafanhaLow[6,]<-NA
+conf_mat_GafanhaLow[,6]<-NA
+
+for(i in 1:(nrow(conf_mat_GafanhaLow))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_GafanhaLow[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_GafanhaLow[,i],na.rm = T)
+}
+conf_mat_std_GafanhaLow<-conf_mat_GafanhaLow
+
+for(row in 1:nrow(conf_mat_std_GafanhaLow)){
+  for(col in 1:ncol(conf_mat_std_GafanhaLow)){
+    conf_mat_std_GafanhaLow[row,col]<-conf_mat_std_GafanhaLow[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_GafanhaLow[row,col])
+    }
+}
+
+confmat_rast_GafanhaLow<-conf_mat_std_GafanhaLow %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_GafanhaLow<-subst(confmat_rast_GafanhaLow, NA, -99)
+names(confmat_rast_GafanhaLow)<-"layer"
+ext(confmat_rast_GafanhaLow)<-c(18.1,21.9,8.2,11.8)
+confmat_rast_GafanhaLow_sf<-as.polygons(confmat_rast_GafanhaLow,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_GafanhaLow_centroid<-st_centroid(confmat_rast_GafanhaLow_sf)
+values(confmat_rast_GafanhaLow)[values(confmat_rast_GafanhaLow) == 0] = NA
+values(confmat_rast_GafanhaLow)[values(confmat_rast_GafanhaLow) == -99] = NA
+
+####### GafanhaHigh #######
+
+df_GafanhaHigh<-df %>% 
+  filter(Flight == "GafanhaHigh")
+
+validation_metrics_GafanhaHigh<-confusionMatrix(df_GafanhaHigh$Pred_Class,df_GafanhaHigh$Truth)
+
+conf_mat_GafanhaHigh<-validation_metrics_GafanhaHigh[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_GafanhaHigh[6,]<-NA
+conf_mat_GafanhaHigh[,6]<-NA
+
+for(i in 1:(nrow(conf_mat_GafanhaHigh))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_GafanhaHigh[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_GafanhaHigh[,i],na.rm = T)
+}
+conf_mat_std_GafanhaHigh<-conf_mat_GafanhaHigh
+
+for(row in 1:nrow(conf_mat_std_GafanhaHigh)){
+  for(col in 1:ncol(conf_mat_std_GafanhaHigh)){
+    conf_mat_std_GafanhaHigh[row,col]<-conf_mat_std_GafanhaHigh[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_GafanhaHigh[row,col])
+    }
+}
+
+confmat_rast_GafanhaHigh<-conf_mat_std_GafanhaHigh %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_GafanhaHigh<-subst(confmat_rast_GafanhaHigh, NA, -99)
+names(confmat_rast_GafanhaHigh)<-"layer"
+ext(confmat_rast_GafanhaHigh)<-c(14.1,17.9,8.2,11.8)
+confmat_rast_GafanhaHigh_sf<-as.polygons(confmat_rast_GafanhaHigh,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_GafanhaHigh_centroid<-st_centroid(confmat_rast_GafanhaHigh_sf)
+values(confmat_rast_GafanhaHigh)[values(confmat_rast_GafanhaHigh) == 0] = NA
+values(confmat_rast_GafanhaHigh)[values(confmat_rast_GafanhaHigh) == -99] = NA
+
+# plot_matrix_GafanhaHigh <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_GafanhaHigh),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Gafanha Low")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+# 
+#
+
+####### DuerLow #######
+
+df_DuerLow<-df %>% 
+  filter(Flight == "DuerLow")
+
+validation_metrics_DuerLow<-confusionMatrix(df_DuerLow$Pred_Class,df_DuerLow$Truth)
+
+conf_mat_DuerLow<-validation_metrics_DuerLow[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_DuerLow[5,]<-NA
+conf_mat_DuerLow[,5]<-NA
+
+for(i in 1:(nrow(conf_mat_DuerLow))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_DuerLow[i,], na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_DuerLow[,i], na.rm = T)
+}
+conf_mat_std_DuerLow<-conf_mat_DuerLow
+
+# for(row in 1:nrow(conf_mat_std_DuerLow)){
+#   for(col in 1:ncol(conf_mat_std_DuerLow)){
+#     conf_mat_std_DuerLow[row,col]<-conf_mat_std_DuerLow[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_DuerLow[row,col])
+#     }
+# }
+
+for(row in 1:nrow(conf_mat_std_DuerLow)){
+  for(col in 1:ncol(conf_mat_std_DuerLow)){
+    conf_mat_std_DuerLow[row,col]<-conf_mat_std_DuerLow[row,col]/((df_sum$col[col]))
+    }
+}
+
+confmat_rast_DuerLow<-conf_mat_std_DuerLow %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_DuerLow<-subst(confmat_rast_DuerLow, NA, -99)
+names(confmat_rast_DuerLow)<-"layer"
+ext(confmat_rast_DuerLow)<-c(18.1,21.9,0,3.8)
+confmat_rast_DuerLow_sf<-as.polygons(confmat_rast_DuerLow,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_DuerLow_centroid<-st_centroid(confmat_rast_DuerLow_sf)
+values(confmat_rast_DuerLow)[values(confmat_rast_DuerLow) == 0] = NA
+values(confmat_rast_DuerLow)[values(confmat_rast_DuerLow) == -99] = NA
+
+# plot_matrix_DuerLow <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_DuerLow),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Duer Low")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### Horse_rooster #######
+
+df_Horse_rooster<-df %>% 
+  filter(Flight == "Horse_rooster")
+
+validation_metrics_Horse_rooster<-confusionMatrix(df_Horse_rooster$Pred_Class,df_Horse_rooster$Truth)
+
+conf_mat_Horse_rooster<-validation_metrics_Horse_rooster[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_Horse_rooster[6,]<-NA
+conf_mat_Horse_rooster[,6]<-NA
+conf_mat_Horse_rooster[2,]<-NA
+conf_mat_Horse_rooster[,2]<-NA
+
+for(i in 1:(nrow(conf_mat_Horse_rooster))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_Horse_rooster[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_Horse_rooster[,i],na.rm = T)
+}
+conf_mat_std_Horse_rooster<-conf_mat_Horse_rooster
+
+for(row in 1:nrow(conf_mat_std_Horse_rooster)){
+  for(col in 1:ncol(conf_mat_std_Horse_rooster)){
+    conf_mat_std_Horse_rooster[row,col]<-conf_mat_std_Horse_rooster[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_Horse_rooster[row,col])
+    }
+}
+
+confmat_rast_Horse_rooster<-conf_mat_std_Horse_rooster %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_Horse_rooster<-subst(confmat_rast_Horse_rooster, NA, -99)
+names(confmat_rast_Horse_rooster)<-"layer"
+ext(confmat_rast_Horse_rooster)<-c(14.1,17.9,4.2,7.8)
+confmat_rast_Horse_rooster_sf<-as.polygons(confmat_rast_Horse_rooster,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_Horse_rooster_centroid<-st_centroid(confmat_rast_Horse_rooster_sf)
+values(confmat_rast_Horse_rooster)[values(confmat_rast_Horse_rooster) == 0] = NA
+values(confmat_rast_Horse_rooster)[values(confmat_rast_Horse_rooster) == -99] = NA
+
+# plot_matrix_Horse_rooster <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_Horse_rooster),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed",
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Mataducos")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### Handfisher_1 #######
+
+df_Handfisher_1<-df %>% 
+  filter(Flight == "Handfisher_1")
+
+validation_metrics_Handfisher_1<-confusionMatrix(df_Handfisher_1$Pred_Class,df_Handfisher_1$Truth)
+
+conf_mat_Handfisher_1<-validation_metrics_Handfisher_1[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_Handfisher_1[5,]<-NA
+conf_mat_Handfisher_1[6,]<-NA
+conf_mat_Handfisher_1[2,]<-NA
+conf_mat_Handfisher_1[3,]<-NA
+conf_mat_Handfisher_1[,5]<-NA
+conf_mat_Handfisher_1[,6]<-NA
+conf_mat_Handfisher_1[,2]<-NA
+conf_mat_Handfisher_1[,3]<-NA
+
+for(i in 1:(nrow(conf_mat_Handfisher_1))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_Handfisher_1[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_Handfisher_1[,i],na.rm = T)
+}
+conf_mat_std_Handfisher_1<-conf_mat_Handfisher_1
+
+for(row in 1:nrow(conf_mat_std_Handfisher_1)){
+  for(col in 1:ncol(conf_mat_std_Handfisher_1)){
+    conf_mat_std_Handfisher_1[row,col]<-conf_mat_std_Handfisher_1[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_Handfisher_1[row,col])
+    }
+}
+
+confmat_rast_Handfisher_1<-conf_mat_std_Handfisher_1 %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_Handfisher_1<-subst(confmat_rast_Handfisher_1, NA, -99)
+names(confmat_rast_Handfisher_1)<-"layer"
+ext(confmat_rast_Handfisher_1)<-c(22.1,25.9,4.2,7.8)
+confmat_rast_Handfisher_1_sf<-as.polygons(confmat_rast_Handfisher_1,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_Handfisher_1_centroid<-st_centroid(confmat_rast_Handfisher_1_sf)
+values(confmat_rast_Handfisher_1)[values(confmat_rast_Handfisher_1) == 0] = NA
+values(confmat_rast_Handfisher_1)[values(confmat_rast_Handfisher_1) == -99] = NA
+
+# plot_matrix_Handfisher_1 <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_Handfisher_1),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Barbatre")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### Boat #######
+
+df_Boat<-df %>% 
+  filter(Flight == "Boat")
+
+validation_metrics_Boat<-confusionMatrix(df_Boat$Pred_Class,df_Boat$Truth)
+
+conf_mat_Boat<-validation_metrics_Boat[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+
+conf_mat_Boat[6,]<-NA
+conf_mat_Boat[,6]<-NA
+conf_mat_Boat[2,]<-NA
+conf_mat_Boat[,2]<-NA
+
+for(i in 1:(nrow(conf_mat_Boat))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_Boat[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_Boat[,i],na.rm = T)
+}
+conf_mat_std_Boat<-conf_mat_Boat
+
+for(row in 1:nrow(conf_mat_std_Boat)){
+  for(col in 1:ncol(conf_mat_std_Boat)){
+    conf_mat_std_Boat[row,col]<-conf_mat_std_Boat[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_Boat[row,col])
+    }
+}
+
+confmat_rast_Boat<-conf_mat_std_Boat %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_Boat<-subst(confmat_rast_Boat, NA, -99)
+names(confmat_rast_Boat)<-"layer"
+ext(confmat_rast_Boat)<-c(22.1,25.9,8.2,11.8)
+confmat_rast_Boat_sf<-as.polygons(confmat_rast_Boat,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_Boat_centroid<-st_centroid(confmat_rast_Boat_sf)
+values(confmat_rast_Boat)[values(confmat_rast_Boat) == 0] = NA
+values(confmat_rast_Boat)[values(confmat_rast_Boat) == -99] = NA
+
+# plot_matrix_Boat <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_Boat),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Inner Lagoon")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### Arz #######
+
+df_Arz<-df %>% 
+  filter(Flight == "Arz")
+
+validation_metrics_Arz<-confusionMatrix(df_Arz$Pred_Class,df_Arz$Truth)
+
+conf_mat_Arz<-validation_metrics_Arz[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_Arz[3,]<-NA
+conf_mat_Arz[,3]<-NA
+conf_mat_Arz[2,]<-NA
+conf_mat_Arz[,2]<-NA
+conf_mat_Arz[5,]<-NA
+conf_mat_Arz[,5]<-NA
+
+for(i in 1:(nrow(conf_mat_Arz))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_Arz[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_Arz[,i],na.rm = T)
+}
+conf_mat_std_Arz<-conf_mat_Arz
+
+for(row in 1:nrow(conf_mat_std_Arz)){
+  for(col in 1:ncol(conf_mat_std_Arz)){
+    conf_mat_std_Arz[row,col]<-conf_mat_std_Arz[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_Arz[row,col])
+    }
+}
+
+confmat_rast_Arz<-conf_mat_std_Arz %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_Arz<-subst(confmat_rast_Arz, NA, -99)
+names(confmat_rast_Arz)<-"layer"
+ext(confmat_rast_Arz)<-c(14.1,17.9,0,3.8)
+confmat_rast_Arz_sf<-as.polygons(confmat_rast_Arz,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_Arz_centroid<-st_centroid(confmat_rast_Arz_sf)
+values(confmat_rast_Arz)[values(confmat_rast_Arz) == 0] = NA
+values(confmat_rast_Arz)[values(confmat_rast_Arz) == -99] = NA
+
+# plot_matrix_Arz <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_Arz),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("Arz Island")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### NorthDike #######
+
+df_NorthDike<-df %>% 
+  filter(Flight == "NorthDike")
+
+validation_metrics_NorthDike<-confusionMatrix(df_NorthDike$Pred_Class,df_NorthDike$Truth)
+
+conf_mat_NorthDike<-validation_metrics_NorthDike[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_NorthDike[5,]<-NA
+conf_mat_NorthDike[,5]<-NA
+conf_mat_NorthDike[2,]<-NA
+conf_mat_NorthDike[,2]<-NA
+
+for(i in 1:(nrow(conf_mat_NorthDike))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_NorthDike[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_NorthDike[,i],na.rm = T)
+}
+conf_mat_std_NorthDike<-conf_mat_NorthDike
+
+for(row in 1:nrow(conf_mat_std_NorthDike)){
+  for(col in 1:ncol(conf_mat_std_NorthDike)){
+    conf_mat_std_NorthDike[row,col]<-conf_mat_std_NorthDike[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_NorthDike[row,col])
+    }
+}
+
+confmat_rast_NorthDike<-conf_mat_std_NorthDike %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_NorthDike<-subst(confmat_rast_NorthDike, NA, -99)
+names(confmat_rast_NorthDike)<-"layer"
+ext(confmat_rast_NorthDike)<-c(18.1,21.9,4.2,7.8)
+confmat_rast_NorthDike_sf<-as.polygons(confmat_rast_NorthDike,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_NorthDike_centroid<-st_centroid(confmat_rast_NorthDike_sf)
+values(confmat_rast_NorthDike)[values(confmat_rast_NorthDike) == 0] = NA
+values(confmat_rast_NorthDike)[values(confmat_rast_NorthDike) == -99] = NA
+
+# plot_matrix_NorthDike <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_NorthDike),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("L'Epine")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+
+####### Kerdrean #######
+
+df_Kerdrean<-df %>% 
+  filter(Flight == "Kerdrean")
+
+validation_metrics_Kerdrean<-confusionMatrix(df_Kerdrean$Pred_Class,df_Kerdrean$Truth)
+
+conf_mat_Kerdrean<-validation_metrics_Kerdrean[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+conf_mat_Kerdrean[c(2,3,4,5,6),]<-NA
+conf_mat_Kerdrean[,c(2,3,4,5,6)]<-NA
+
+for(i in 1:(nrow(conf_mat_Kerdrean))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_Kerdrean[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_Kerdrean[,i],na.rm = T)
+}
+conf_mat_std_Kerdrean<-conf_mat_Kerdrean
+
+for(row in 1:nrow(conf_mat_std_Kerdrean)){
+  for(col in 1:ncol(conf_mat_std_Kerdrean)){
+    conf_mat_std_Kerdrean[row,col]<-conf_mat_std_Kerdrean[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_Kerdrean[row,col])
+    }
+}
+
+confmat_rast_Kerdrean<-conf_mat_std_Kerdrean %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_Kerdrean<-subst(confmat_rast_Kerdrean, NA, -99)
+names(confmat_rast_Kerdrean)<-"layer"
+ext(confmat_rast_Kerdrean)<-c(22.1,25.9,0,3.8)
+confmat_rast_Kerdrean_sf<-as.polygons(confmat_rast_Kerdrean,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_Kerdrean_centroid<-st_centroid(confmat_rast_Kerdrean_sf)
+
+values(confmat_rast_Kerdrean)[values(confmat_rast_Kerdrean) == 0] = NA
+values(confmat_rast_Kerdrean)[values(confmat_rast_Kerdrean) == -99] = NA
+
+# plot_matrix_Kerdrean <-
+# ggplot()+
+#   geom_spatraster(data = (confmat_rast_Kerdrean),
+#                   show.legend = F,
+#                   na.rm = TRUE
+#                   )+
+#   scale_fill_Bede("mixed", 
+#                   discrete = F,
+#                   na.value = "white",
+#                   trans = "sqrt",
+#                   labels = c("5","25", "50", "75", "100"),
+#                   breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+#   labs(fill = "Proportion \n of pixels (%)")+
+#   scale_x_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Sediment","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#                      expand = c(0, 0),
+#                      position = "top",
+#                      limits = c(0,10))+
+#   scale_y_continuous(breaks = seq(1,9, by = 2),
+#                      labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Sediment"),
+#                      expand = c(0, 0.1),
+#                      limits = c(0,10))+
+#   geom_path(
+#     data = data.frame(
+#       x = c(0,10,0,10,0,10,0,10,0,10,0,10,0,0,2,2,4,4,6,6,8,8,10,10),
+#       y = c(0,0,2,2,4,4,6,6,8,8,10,10,0,10,0,10,0,10,0,10,0,10,0,10),
+#       group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12)
+#       ),
+#     aes(x,y,group= group),
+#     linewidth = 1
+#     )+
+#   theme_void()+
+#   ggtitle("L'Epine")+
+#   theme(plot.title = element_text(hjust = 0.5),
+#         plot.margin = unit(c(0,30,0,30), "pt"))
+#
+
+confmat_rast_Arz_centroid<-confmat_rast_Arz_centroid %>% 
+  mutate(site = "Arz")
+confmat_rast_Boat_centroid<-confmat_rast_Boat_centroid %>% 
+  mutate(site = "Boat")
+confmat_rast_DuerLow_centroid<-confmat_rast_DuerLow_centroid %>% 
+  mutate(site = "DuerLow")
+confmat_rast_GafanhaHigh_centroid<-confmat_rast_GafanhaHigh_centroid %>% 
+  mutate(site = "Gaf_High")
+confmat_rast_GafanhaLow_centroid<-confmat_rast_GafanhaLow_centroid %>% 
+  mutate(site = "Gaf_Low")
+confmat_rast_Handfisher_1_centroid<-confmat_rast_Handfisher_1_centroid %>% 
+  mutate(site = "Handfisher")
+confmat_rast_Horse_rooster_centroid<-confmat_rast_Horse_rooster_centroid %>% 
+  mutate(site = "Rooster")
+confmat_rast_Kerdrean_centroid<-confmat_rast_Kerdrean_centroid %>% 
+  mutate(site = "kerdrean")
+confmat_rast_NorthDike_centroid<-confmat_rast_NorthDike_centroid %>% 
+  mutate(site = "Dike")
+
+centroid_cells<-rbind(confmat_rast_Arz_centroid,confmat_rast_Boat_centroid,confmat_rast_DuerLow_centroid,confmat_rast_GafanhaHigh_centroid,confmat_rast_GafanhaLow_centroid,confmat_rast_Handfisher_1_centroid,confmat_rast_Horse_rooster_centroid,confmat_rast_Kerdrean_centroid,confmat_rast_NorthDike_centroid) %>%
+  filter(layer == -99)
+
+##### Global #####
+
+validation_metrics<-confusionMatrix(df$Pred_Class,df$Truth)
+
+metrics_by_class<-validation_metrics$byClass %>% 
+    as.data.frame()
+
+conf_mat<-validation_metrics[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 6) %>%
+  as.data.frame()
+
+for(i in 1:(nrow(conf_mat))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat[i,])
+  df_sum[i,2] <- sum(conf_mat[,i])
+}
+
+conf_mat_std<-conf_mat
+for(row in 1:nrow(conf_mat_std)){
+  for(col in 1:ncol(conf_mat_std)){
+    conf_mat_std[row,col]<-conf_mat_std[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std[row,col])
+    }
+
+}
+
+confmat_rast<-conf_mat_std %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+names(confmat_rast)<-"layer"
+ext(confmat_rast)<-c(0,12,0,12)
+# crs(confmat_rast)<-"4326"
+
+ values(confmat_rast)[values(confmat_rast) == 0] = NA
+
+df_summarize<-df %>% 
+  group_by(Flight) %>% 
+  summarize(n = length(Flight)) %>% 
+  ungroup() %>% 
+  mutate(prop = n / sum(n),
+         Site = case_when(Flight == "GafanhaHigh" ~ "Gafanha High",
+                   Flight == "GafanhaLow" ~ "Gafanha Low",
+                   Flight == "Boat" ~ "Marinha Lanzarote",
+                   Flight == "Horse_rooster" ~ "Mataducos",
+                   Flight == "NorthDike" ~ "L'Epine",
+                   Flight == "Handfisher_1" ~ "Barbâtre",
+                   Flight == "Arz" ~ "Arz Island",
+                   Flight == "DuerLow" ~ "Duer",
+                   TRUE ~ Flight))
+
+df_corrected_accuracy<-data.frame(
+      x = c(1,3,5,7,9,11),
+      y = c(11,9,7,5,3,1),
+      lab = c(metrics_by_class[1,11],metrics_by_class[2,11], metrics_by_class[3,11], metrics_by_class[4,11],metrics_by_class[5,11],metrics_by_class[6,11]))
+
+df_Sens_Spec<-data.frame(
+    x = c(1,3,5,7,9, 11, 12.9, 12.9, 12.9, 12.9, 12.9,12.9),
+    y = c(-0.3,-0.3,-0.3,-0.3,-0.3,-0.3,11,9,7,5,3,1),
+    lab = c(metrics_by_class$Recall[c(1:6)],metrics_by_class$Precision[c(1:6)])
+)
+
+df_Label_Sites<-data.frame(
+    x = c(16,20,24,16,20,24,16,20,24),
+    y = c(12,12,12,8,8,8,4,4,4),
+    lab = c(paste0("Gafanha High, ", df_summarize %>% 
+                     filter(Flight == "GafanhaHigh") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Gafanha Low, ",df_summarize %>% 
+                     filter(Flight == "GafanhaLow") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Inner Lagoon, ", df_summarize %>% 
+                     filter(Flight == "Boat") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Mataducos, ", df_summarize %>% 
+                     filter(Flight == "Horse_rooster") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("L'Epine, ", df_summarize %>% 
+                     filter(Flight == "NorthDike") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Barbâtre, ", df_summarize %>% 
+                     filter(Flight == "Handfisher_1") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Arz Island, ", df_summarize %>% 
+                     filter(Flight == "Arz") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Duer, ", df_summarize %>% 
+                     filter(Flight == "DuerLow") %>% 
+                     pull(prop) %>% 
+                     round(2)),
+            paste0("Kerdrean, ", df_summarize %>% 
+                     filter(Flight == "Kerdrean") %>% 
+                     pull(prop) %>% 
+                     round(2)))
+)
+
+x_axis_text<-data.frame(
+    x = c(1,3,5,7,9,11),
+    y = c(12.5,12.5,12.5,12.5,12.5,12.5),
+    lab = c("Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae")
+)
+
+y_axis_text<-data.frame(
+    x = c(-0.4,-0.4,-0.4,-0.4,-0.4,-0.4),
+    y = c(11,9,7,5,3,1),
+    lab = c("Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae")
+)
+
+centroid_cells_df<-data.frame(st_coordinates(st_cast(centroid_cells$geometry,"MULTIPOINT")),centroid_cells$site)
+
+centroid_cells_df$col <-NA
+centroid_cells_df$row <-NA
+
+for(i in 1:length(unique(centroid_cells_df$centroid_cells.site))){
+
+  df_temp<-centroid_cells_df %>% 
+    filter(centroid_cells_df$centroid_cells.site == unique(centroid_cells_df$centroid_cells.site)[i])
+
+  #### Column
+
+  for( ii in 1:length(unique(as.character(df_temp$X)))){
+    if(nrow(df_temp %>% 
+            filter(X == unique(as.character(df_temp$X))[ii])) == 6){
+
+      centroid_cells_df<-centroid_cells_df %>% 
+        mutate(col = case_when(centroid_cells.site == unique(centroid_cells_df$centroid_cells.site)[i] ~
+                         case_when(as.character(X) == unique(as.character(df_temp$X))[ii] ~ 
+                                   paste0("col",ii),
+                                   TRUE ~ col),
+                         TRUE ~ col))
+    }
+  }
+
+  #### ROW
+  for( iii in 1:length(unique(as.character(df_temp$Y)))){
+    if(nrow(df_temp %>% 
+            filter(Y == unique(as.character(df_temp$Y))[iii])) == 6){
+
+      centroid_cells_df<-centroid_cells_df %>% 
+        mutate(row = case_when(centroid_cells.site == unique(centroid_cells_df$centroid_cells.site)[i] ~
+                         case_when(as.character(Y) == unique(as.character(df_temp$Y))[iii] ~ 
+                                   paste0("row",iii),
+                                   TRUE ~ row),
+                         TRUE ~ row))
+    }
+  }
+
+}
+
+# other_table_path<-data.frame(
+#   x = c(1,25,1,25,1,25,1,25,
+#         1,1,5,5,9,9,13,13,17,17,21,21,25,25
+#         ),
+#   y= c(-2,-2,-3,-3,-4,-4,-5,-5,
+#        -2,-5,-2,-5,-2,-5,-2,-5,-2,-5,-2,-5,-2,-5
+#        ),
+#   group=c(1,1,9,9,10,10,11,11,
+#           2,2,3,3,4,4,5,5,6,6,7,7,8,8
+#           )
+# )
+# 
+# other_table_title <- data.frame(
+#   x = c(-1,3,7,11,15,19,23),
+#   y = c(-1.5,-1.5,-1.5,-1.5,-1.5,-1.5,-1.5),
+#   label = c("Metrics","Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+#   group = c(1,2,3,4,5,6,7)
+# )
+# 
+# accuracy_by_class<-validation_metrics$byClass %>% 
+#   as.data.frame()
+# 
+# other_table_values <- data.frame(
+#   x = c(3,7,11,15,19,23,
+#         3,7,11,15,19,23,
+#         3,7,11,15,19,23),
+#   y = c(-2.5,-2.5,-2.5,-2.5,-2.5,-2.5,
+#         -3.5,-3.5,-3.5,-3.5,-3.5,-3.5,
+#         -4.5,-4.5,-4.5,-4.5,-4.5,-4.5),
+#   label = round(c(accuracy_by_class$Sensitivity[c(1:6)],
+#             accuracy_by_class$Specificity[c(1:6)],
+#             accuracy_by_class$`Balanced Accuracy`[c(1:6)]),2)
+# )
+
+other_table_path<-data.frame(
+  x = c(-3,26,-3,26,-3,26,-3,26,-3,26,
+        -3,-3,0,0,3.857,3.857,7.714,7.714,11.571,11.571,15.429,15.429,19.286,19.286,23.142,23.142,26,26
+        ),
+  y= c(-2,-2,-3,-3,-4,-4,-5,-5,-1,-1,
+       -1,-5,-1,-5,-1,-5,-1,-5,-1,-5,-1,-5,-1,-5,-1,-5,-1,-5
+       ),
+  group=c(1,1,9,9,10,10,11,11,12,12,13,13,14,14,
+          2,2,3,3,4,4,5,5,6,6,7,7,8,8
+          )
+)
+
+other_table_title <- data.frame(
+  x = c(-1.529,1.929,5.786,9.643,13.5,17.359,21.215,24.571),
+  y = c(-1.5,-1.5,-1.5,-1.5,-1.5,-1.5,-1.5,-1.5),
+  label = c("Metrics","Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae", "Overall")
+)
+
+other_table_y_axis<-data.frame(
+  x=c(-0.4,-0.4,-0.4),
+  y=c(-2.5,-3.5,-4.5),
+  label = c("Sensitivity","Specificity", "Accuracy")
+)
+
+accuracy_by_class<-validation_metrics$byClass %>% 
+  as.data.frame()
+
+other_table_values <- data.frame(
+  x = c(1.929,5.786,9.643,13.5,17.359,21.215,24.571,
+        1.929,5.786,9.643,13.5,17.359,21.215,24.571,
+        1.929,5.786,9.643,13.5,17.359,21.215),
+  y = c(-2.5,-2.5,-2.5,-2.5,-2.5,-2.5,-2.5,
+        -3.5,-3.5,-3.5,-3.5,-3.5,-3.5,-3.5,
+        -4.5,-4.5,-4.5,-4.5,-4.5,-4.5),
+  label = round(c(accuracy_by_class$Sensitivity[c(1:6)],mean(accuracy_by_class$Sensitivity),
+            accuracy_by_class$Specificity[c(1:6)],mean(accuracy_by_class$Specificity),
+            accuracy_by_class$`Balanced Accuracy`[c(1:6)]),2)
+)
+
+global_accuracy_coord<-data.frame(x = 24.571,
+                                  y = -4.5,
+                                  label = round(as.numeric(validation_metrics$overall[1]),2))
+
+centroid_cells_df_rows<-centroid_cells_df %>% 
+  filter(!is.na(row)) %>% 
+  mutate(Row = paste0(centroid_cells.site,"_",row))
+
+centroid_cells_df_cols<-centroid_cells_df %>% 
+  filter(!is.na(col)) %>% 
+  mutate(cols = paste0(centroid_cells.site,"_",col))
+
+plot_matrix_global <-
+ggplot()+
+  geom_spatraster(data = (confmat_rast),
+                  # show.legend = F,
+                  na.rm = TRUE
+                  )+
+  geom_spatraster(data = confmat_rast_GafanhaLow,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_GafanhaLow_sf,
+          fill = "transparent")+
+  geom_spatraster(data = confmat_rast_GafanhaHigh,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_GafanhaHigh_sf,
+          fill = "transparent")+
+  geom_spatraster(data = confmat_rast_Boat,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_Boat_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_Horse_rooster,
+                  na.rm = TRUE
+                  )+
+    geom_sf(data = confmat_rast_Horse_rooster_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_NorthDike,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_NorthDike_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_Handfisher_1,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_Handfisher_1_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_Arz,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_Arz_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_DuerLow,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_DuerLow_sf,
+          fill = "transparent")+
+    geom_spatraster(data = confmat_rast_Kerdrean,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_Kerdrean_sf,
+          fill = "transparent")+
+  # geom_sf(data = centroid_cells,
+  #         fill = "transparent")+
+
+  geom_path(data = centroid_cells_df_rows, 
+            aes(x = X, y = Y, group = Row),
+            linewidth = 2,
+            linejoin = "round",
+            lineend = "round",
+            colour = "grey")+
+  geom_path(data = centroid_cells_df_cols, 
+            aes(x = X, y = Y, group = cols),
+            linewidth = 2,
+            linejoin = "round",
+            lineend = "round",
+            colour = "grey")+
+  scale_fill_gradientn(
+    # colours = c("black","firebrick4","goldenrod","yellow","chartreuse3"),
+    # colours = c("khaki1","goldenrod","firebrick3","chartreuse4"),
+    colours = c("khaki1","firebrick4","firebrick4","firebrick4","#3e0b0b"),
+    # colours = c("#7d0000","#00b300","#00b300","#00b300","#007d00"),
+    na.value = "white", 
+    trans = "sqrt",
+    labels = c("0.05","0.25", "0.50", "0.75", "1"),
+    breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+  # scale_fill_Bede("mixed", 
+  #                 discrete = F,
+  #                 reverse = TRUE,
+  #                 na.value = "white",
+  #                 trans = "sqrt",
+  #                 labels = c("5","25", "50", "75", "100"),
+  #                 breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+  labs(fill = "Proportion \n of pixels")+
+  scale_x_continuous(breaks = seq(1,11, by = 2),
+                     labels = c("Sediment","Bacillariophyceae","Chlorophyceae","Magnoliopsida","Rhodophyceae","Phaeophyceae"),
+                     expand = c(0, 0),
+                     position = "top",
+                     limits = c(-4.6,29))+
+  scale_y_continuous(breaks = seq(1,11, by = 2),
+                     labels = c("Phaeophyceae","Rhodophyceae","Magnoliopsida","Chlorophyceae","Bacillariophyceae","Sediment"),
+                     expand = c(0, 0.1),
+                     limits = c(-5,15.5))+
+  geom_polygon(aes(x = c(-3,26,26,-3),
+                   y = c(-4,-4,-5,-5)),
+               fill = "lightgrey",
+               color = "transparent")+
+  geom_polygon(aes(x = c(23.142,26,26,23.142),
+                   y = c(-1,-1,-4,-4)),
+               fill = "lightgrey",
+               color = "transparent")+
+  geom_path(
+    data = data.frame(
+      x = c(0,12,0,12,0,12,0,12,0,12,0,12,0,12,0,0,2,2,4,4,6,6,8,8,10,10,12,12),
+      y = c(0,0,2,2,4,4,6,6,8,8,10,10,12,12,0,12,0,12,0,12,0,12,0,12,0,12,0,12),
+      group = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11,12,12,13,13,14,14)
+      ),
+    aes(x,y,group= group),
+    linewidth = 1
+    )+
+  geom_path(data = other_table_path,
+            aes(x = x,
+                y = y,
+                group = group),
+            linewidth = 1)+
+  geom_label(
+    data = df_corrected_accuracy,
+    aes(x = x, y = y, label = paste0(round(lab,3)*100,"%")),
+    fill = "#ffffff99",
+    size = 9
+    )+
+  geom_text(
+    data = df_Sens_Spec,
+    aes(x = x, y = y, label = paste0(round(lab,4)*100,"%")),
+    # fill = "#ffffff99",
+    size = 8
+    )+
+  geom_text(
+    data = other_table_title,
+    aes(x = x, y = y, label = label),
+    # fill = "#ffffff99",
+    size = 8
+    )+
+  geom_text(
+    data = other_table_y_axis,
+    aes(x = x, y = y, label = label),
+    size = 8,
+    hjust = 1,
+    size = 8
+  )+
+  geom_text(
+    data = other_table_values,
+    aes(x = x, y = y, label = label),
+    # fill = "#ffffff99",
+    size = 8
+    )+
+  geom_text(
+    data = global_accuracy_coord,
+    aes(x = x, y = y, label = label),
+    # fill = "#ffffff99",
+    size = 12,
+    color = "firebrick4"
+
+    )+
+  geom_label(
+    data = df_Label_Sites,
+    aes(x = x, y = y, label = lab),
+    fill = "#ffffff99",
+    size = 6.8
+    )+
+  geom_text(
+    data = x_axis_text,
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    # vjust = 1,
+    hjust = 0,
+    size = 9,
+    angle = 40
+    )+
+  geom_text(
+    data = y_axis_text,
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    hjust = 1,
+    size = 9,
+    # angle = 20
+    )+
+
+  # geom_text(
+  #   aes(x = 13.8, y = 12.72, label = "Producer's Accuracy"),
+  #   # fill = "#ffffff99",
+  #   size = 9,
+  #   angle = 20
+  #   )+
+  # geom_text(
+  #   aes(x = 0, y = 0, label = "User's Accuracy"),
+  #   # fill = "#ffffff99",
+  #   size = 9
+  #   )+
+  xlab("References")+
+  ylab("Prediction")+
+  # ggplot2::annotation_custom(ggplotGrob(small_validation_matrices), xmin = 12, ymin = 0)+
+  theme_Bede()+
+  theme(
+  # axis.title.x = element_text(size = 35),
+        # axis.title.y = element_text(size = 35),
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+
+        # axis.text.x = element_text(size = 30),
+        axis.text.x = element_blank(),
+        # axis.text.y = element_text(size = 25),
+         axis.text.y = element_blank(),
+
+        axis.ticks.x = element_blank(),
+        axis.ticks.y = element_blank(), 
+        panel.border = element_blank(),
+        axis.line=element_blank(),
+        # legend.position = "top",
+        legend.position = c(0.73, 0.9),
+        legend.direction="horizontal",
+        legend.key.width = unit(2,"cm"),
+        legend.text = element_text(size = 20),
+        legend.title = element_text(size = 20, vjust = 2),
+        legend.title.align = 0.5,
+        legend.justification = "center")
+
+# plot_matrix_global
+############ Metrics of each sites ###################
+
+Arz_metrics_ByClass<-validation_metrics_Arz$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Arz Island") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+Arz_metrics_overall<-validation_metrics_Arz$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Arz Island",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+Arz_metrics<-rbind(Arz_metrics_ByClass,Arz_metrics_overall)
+
+Boat_metrics_ByClass<-validation_metrics_Boat$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Marinha Lanzarote") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+Boat_metrics_overall<-validation_metrics_Boat$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Marinha Lanzarote",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+Boat_metrics<-rbind(Boat_metrics_ByClass,Boat_metrics_overall)
+
+DuerLow_metrics_ByClass<-validation_metrics_DuerLow$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Duer") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+DuerLow_metrics_overall<-validation_metrics_DuerLow$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Duer",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+DuerLow_metrics<-rbind(DuerLow_metrics_ByClass,DuerLow_metrics_overall)
+
+GafanhaHigh_metrics_ByClass<-validation_metrics_GafanhaHigh$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Gafanha High") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+GafanhaHigh_metrics_overall<-validation_metrics_GafanhaHigh$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Gafanha High",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+GafanhaHigh_metrics<-rbind(GafanhaHigh_metrics_ByClass,GafanhaHigh_metrics_overall)
+
+GafanhaLow_metrics_ByClass<-validation_metrics_GafanhaLow$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Gafanha Low") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+GafanhaLow_metrics_overall<-validation_metrics_GafanhaLow$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Gafanha Low",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+GafanhaLow_metrics<-rbind(GafanhaLow_metrics_ByClass,GafanhaLow_metrics_overall)
+
+Handfisher_1_metrics_ByClass<-validation_metrics_Handfisher_1$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Barbâtre") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+Handfisher_1_metrics_overall<-validation_metrics_Handfisher_1$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Barbâtre",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+Handfisher_1_metrics<-rbind(Handfisher_1_metrics_ByClass,Handfisher_1_metrics_overall)
+
+Horse_rooster_metrics_ByClass<-validation_metrics_Horse_rooster$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Mataducos") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+Horse_rooster_metrics_overall<-validation_metrics_Horse_rooster$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Mataducos",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+Horse_rooster_metrics<-rbind(Horse_rooster_metrics_ByClass,Horse_rooster_metrics_overall)
+
+Kerdrean_metrics_ByClass<-validation_metrics_Kerdrean$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "Kerdrean") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+Kerdrean_metrics_overall<-validation_metrics_Kerdrean$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "Kerdrean",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+Kerdrean_metrics<-rbind(Kerdrean_metrics_ByClass,Kerdrean_metrics_overall)
+
+NorthDike_metrics_ByClass<-validation_metrics_NorthDike$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.),
+         Site = "L'Epine") %>% 
+  pivot_longer(-c(Class,Site),names_to = "metric", values_to = "value")
+
+NorthDike_metrics_overall<-validation_metrics_NorthDike$overall %>% 
+  as.data.frame() %>% 
+  rename(value = ".") %>% 
+  mutate(Class = "All",
+         Site = "L'Epine",
+         metric = rownames(.)) %>% 
+  reframe(Class,Site,metric,value)
+
+NorthDike_metrics<-rbind(NorthDike_metrics_ByClass,NorthDike_metrics_overall)
+
+BySite_Metrics<-rbind(NorthDike_metrics,Kerdrean_metrics,Horse_rooster_metrics,Handfisher_1_metrics,GafanhaLow_metrics,GafanhaHigh_metrics,DuerLow_metrics,Boat_metrics,Arz_metrics)
+
+Overall_metrics_ByClass<-validation_metrics$byClass %>% 
+  as.data.frame() %>% 
+  mutate(Class = rownames(.) %>% 
+           gsub("Class: ","",.)) %>% 
+  pivot_longer(-c(Class),names_to = "metric", values_to = "value")
+################
+
+ggsave("Figures/Validation/ConfusionMatrixGlobal.png",plot_matrix_global , width = 1920*4, height = 1032*4, units = "px")
+
+```
+
+```{r Global Accuracy assesment Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: A global confusion matrix on the left is derived from validation data across each flight, while a mosaic of confusion matrices from individual flights is presented on the right.
+The labels inside the matrices indicate the balanced accuracy for each class.
+The labels at the bottom of the matrices indicate the User's accuracy for each class, and those on the right indicate the Producer's Accuracy.
+The values adjacent to the names of each site represent the proportion of total pixels from that site contributing to the overall matrix.
+Grey lines within the mosaic indicate the absence of validation data for the class at that site.
+The table at the bottom summarizes the Sensitivity, Specificity, and Accuracy for each class and for the overall model.
+#| label: fig-Validation
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Validation/ConfusionMatrixGlobal.png")
+
+```
+
+A total amount of `r my_comma(round(count_validation_pixel,-3))` pixels have been used to validate the Neural Network classifier.
+The site with the least amount of validation data is `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` with a total of `r min(df_summarize$n)` pixels whereas `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` is the site with the most amount of validation data with `r max(df_summarize$n)` pixels.
+The global accuracy of the model is `r round(validation_metrics$overall[[1]]*100,2)`% and a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
+The least performing site is `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` with an accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`% whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` is the site with most accurate prediction, with a global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%.
+Overall Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae are well classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
+`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` is the least performing class with an accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` mainly due to a confusion with Magnoliopsida and Sediment.
+
+## Variable importance
+
+```{r VIP}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
+
+################# SPECTRA ########### 
+SP1<-read.csv("Output/Spectra_VIP.csv") %>% 
+  dplyr::select(-X) %>% 
+  mutate(type = "Min/Max Standardised Spectra") %>% 
+  dplyr::filter(Class != "Bare Sediment",
+                Class != "Sun Glint",
+                Class != "Water",
+                Class != "Xanthophyceae",
+                Class != "A - MagnoliopsidaL") %>% 
+  as_tibble()%>% 
+  rename(value = "STD")
+
+SP2<-read.csv("Output/Spectra_VIP2.csv") %>% 
+  dplyr::select(-X) %>% 
+  mutate(type = "Raw Spectra",
+         mean = mean / 10000)%>% 
+  dplyr::filter(Class != "Bare Sediment",
+                Class != "Sun Glint",
+                Class != "Water",
+                Class != "Xanthophyceae",
+                Class != "A - MagnoliopsidaL") %>% 
+  as_tibble() %>% 
+  dplyr::reframe(Class,Wavelength, mean, type) %>% 
+  rename(value = "mean")
+
+SP<-SP1 %>% 
+  rbind(SP2)
+
+SP_plot<-ggplot(SP, aes( x = Wavelength, y = value, color = Class))+
+  geom_line(linewidth = 1.5, show.legend = F)+
+  facet_wrap(~ type, scale = "free",ncol =1) +
+  scale_color_manual(values=c("#389318", "#873e23", "#b3002d", "#b3ff1a", "#DAA520"))+
+  ylab("Reflectance")+
+  xlab("Wavelength (nm)")+
+  theme_Bede()+
+  theme(axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20),
+        axis.title.x = element_text(size = 25),
+        axis.title.y = element_text(size = 25),
+        strip.text = element_text(size=25),
+        legend.position = c(0.2, 0.7),
+        plot.background = element_rect(fill = rgb(1,1,1, alpha=0), colour = NA),
+        legend.title=element_blank(),
+        legend.text = element_text(size = 5),
+        legend.key.size = unit(0.25, "cm"),
+        legend.text.align = 0,
+        panel.border = element_blank(), 
+        panel.background = element_blank(),
+        axis.line = element_line(color="black"))
+
+############## VIP ##############
+
+filelist<-"Data" %>% 
+  list.files(pattern = "NN_VIP_byClass_NoXanth.csv", recursive = T,full.names = T)
+
+VIP<-filelist[which(str_detect(filelist,"VIP"))] %>% 
+  read.csv() %>% 
+  mutate(Magnoliopsida = (Magnoliosida + Low_SPC)/2) %>% 
+  dplyr::select(-c(Magnoliosida ,Low_SPC))
+
+VIP1<-VIP %>%
+  dplyr::select(-c(Water,
+                   SunGlint,
+                   Deep_Sediment,
+                   Bare_Sediment)) %>%
+  # dplyr::filter(!str_detect(X,"NDVI")) %>% 
+  mutate(isSTD = case_when(str_detect(X,"Stan") ~ "Standardised", 
+                         TRUE ~ "RAW")) %>%
+  pivot_longer(-c(X,isSTD), names_to = "Class",values_to = "value") %>% 
+  dplyr::filter(X != "NDVI",
+                X != "NDVI_Stan") %>% 
+  group_by(Class) %>%
+  mutate(STD = (value-min(value))/(max(value)-min(value))) %>% 
+  ungroup() %>% 
+  mutate(Class = case_when(Class == "Magnoliosida" ~ "Magnoliopsida",
+                           Class == "Low_SPC" ~ "Magnoliopsida",
+                           Class == "Clorophyta" ~ "Chlorophyceae",
+                           Class == "Rhodphyta" ~ "Rhodophyceae",
+                           Class == "MPB" ~ "Bacillariophyceae",
+                           Class == "Phaeophyta" ~ "Phaeophyceae",
+                           TRUE ~ Class),
+         Variable = str_replace_all(str_replace_all(str_replace_all(X,"Reflectance",""),"Stan",""),"_","")) %>% 
+  dplyr::filter(Class != "Total")
+
+VIP_summarised<-VIP1 %>% 
+  group_by(Variable, Class) %>% 
+  dplyr::summarise(sumVIP = sum(STD)) %>% 
+  ungroup() %>% 
+  group_by(Class) %>% 
+  mutate(STD = (sumVIP-min(sumVIP))/(max(sumVIP)-min(sumVIP)))
+
+VIP_subPLOT<-VIP_summarised %>% 
+  ggplot(aes(x = Variable, y = STD, fill = Class)) +
+  geom_col(color = "black",position =  "dodge") +
+  coord_polar()+
+  scale_y_continuous(limits = c(0,1), breaks = c(0.25,0.5,0.75,1))+
+  facet_wrap(~Class)+
+  scale_fill_manual("Class", labels = c("Bacillariophyceae","Chlorophyceae", "Magnoliopsida", "Phaeophyceae","Rhodophyceae"),
+                    values = c("#DAA520","#b3ff1a", "#389318","#873e23","#b3002d"))+
+  theme_Bede()+
+  theme(panel.grid.major.y = element_line(linetype = "dotted",color = c("grey9","grey9","grey9","grey9",NA)))+
+  ylab("Importance")+
+  theme(legend.position="top",
+        strip.text = element_text(size = 25),
+        axis.text.y = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.ticks.y =element_blank(),
+        axis.title.x =element_blank(),
+        axis.title.y =element_text(size = 20),
+        legend.key.size = unit(1, 'cm'),
+        legend.title = element_text(size=20),
+        legend.text = element_text(size=20))+
+  guides(fill = guide_legend(nrow = 1))
+
+VIP_PLOT<-VIP_subPLOT+
+  # geom_text(aes(label = "Standardised Reflectance Spectra"), color = "black", size = 8)+
+  inset_element(SP_plot,left = 0.6341, top = 0.47, bottom = -0.01, right = 0.90,  align_to = "full")
+VIP_PLOT
+ggsave("Figures/VIP/Fig_VIP.png", VIP_PLOT, width = 1920*4, height = 1129*4, units = "px")
+
+################# VIP NDVI ######################
+
+VIP_NDVI<-
+  VIP %>%
+  dplyr::select(-c(Water,
+                   SunGlint,
+                   Deep_Sediment,
+                   Bare_Sediment)) %>%
+  # dplyr::filter(!str_detect(X,"NDVI")) %>% 
+  mutate(isSTD = case_when(str_detect(X,"Stan") ~ "Standardised", 
+                         TRUE ~ "RAW")) %>%
+  pivot_longer(-c(X,isSTD), names_to = "Class",values_to = "value") %>% 
+  dplyr::filter(X == "NDVI") %>% 
+  group_by(Class) %>%
+  mutate(STD = (value-min(value))/(max(value)-min(value))) %>% 
+  ungroup() %>% 
+  mutate(Class = case_when(Class == "Magnoliosida" ~ "Magnoliopsida",
+                           Class == "Low_SPC" ~ "Magnoliopsida",
+                           Class == "Clorophyta" ~ "Chlorophyceae",
+                           Class == "Rhodphyta" ~ "Rhodophyceae",
+                           Class == "MPB" ~ "Bacillariophyceae",
+                           Class == "Phaeophyta" ~ "Phaeophyceae",
+                           TRUE ~ Class),
+         Variable = str_replace_all(str_replace_all(str_replace_all(X,"Reflectance",""),"Stan",""),"_","")) %>% 
+  dplyr::filter(Class != "Total") %>% 
+  group_by(Class) %>% 
+  summarise(sum = sum(value)) %>% 
+  mutate(STD = (sum-min(sum))/(max(sum)-min(sum))) %>% 
+  ggplot(aes(x = Class, y = STD, fill = Class)) +
+  geom_col(color = "black",position =  "dodge") +
+  # coord_polar()+
+  scale_y_continuous(limits = c(0,1), breaks = c(0.25,0.5,0.75,1))+
+  # facet_wrap(~Class)+
+  scale_fill_manual("Class", labels = c("Bacillariophyceae","Chlorophyceae", "Magnoliopsida", "Phaeophyceae","Rhodophyceae"),
+                    values = c("#DAA520","#b3ff1a", "#389318","#873e23","#b3002d"))+  theme_Bede()+
+  theme(panel.grid.major.y = element_line(linetype = "dotted",color = c("grey9","grey9","grey9","grey9",NA)))+
+  ylab("Importance")+
+  theme(legend.position="top",
+        strip.text = element_text(size = 25),
+        axis.text.y = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.ticks.y =element_blank(),
+        axis.title.x =element_blank(),
+        axis.title.y =element_text(size = 20),
+        legend.key.size = unit(1, 'cm'),
+        legend.title = element_text(size=20),
+        legend.text = element_text(size=20))+
+  guides(fill = guide_legend(nrow = 1))
+
+```
+
+```{r VIP Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Variable Importance of the Neural Network Classifier for each vegetation class.
+The bigger the slice, the more important is the variable to predict accuratly this class.
+The bottom right plot shows the drone standardised reflectance spectra of each class.
+#| label: fig-VIP
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("Figures/VIP/Fig_VIP.png")
+
+```
+
+The computation of the importance variable of each class indicate which wavelength is mandatory to accurately predict the class (@fig-VIP).
+Bands at 444 nm, 717 nm and 842 nm of the Micasense camera are important for none of the vegetation classes.
+The band at 531 nm is the only important predictor for the classifier to accuratly predict chlorophyceae.
+In fact, at this wavelength, the Chlorophyceae spectra has the maximum reflectance value of all the classes.
+531 nm and 740 nm are the most important predictors to predict Phaeophyceae, corresponding to the minimum reflectance value among all the classes.
+Bands at 475 and 560 nm are the most important predictors for Bacillariophyceae and Rhodophyceae, respectively.
+4 predictors, ranging from the Green (560 nm) to the RedEdge (705 nm) are important to predict accurately magnoliopsida.
+
+## Effect of the flight height on the prediction
+
+```{r Upscaling}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
+
+if(length(list.files("./Output",pattern = "output_80_filtered_Upscaling.csv")) == 0 ){
+ imglist<-"Output/High_Flights_correction/Low_flight_spatial_resampling/" %>%
+   list.files(".tif",full.names = T) %>%
+   as.data.frame() %>%
+   rename(path = ".") %>%
+   mutate(size = case_when(str_detect(path,"_8_7x7.tif") ~ 8,
+                           str_detect(path,"16.tif") ~ 16,
+                           str_detect(path,"32.tif") ~ 32,
+                           str_detect(path,"48.tif") ~ 48,
+                           str_detect(path,"64.tif") ~ 64,
+                           str_detect(path,"80.tif") ~ 80),
+          type = case_when(str_detect(path, "ortho") ~ "ortho",
+                           str_detect(path, "pred") ~ "Pred",
+                           TRUE ~ "Prob"))
+
+pred_8<-imglist %>%
+   filter(size == 8,
+          type == "Pred") %>%
+   pull(path) %>%
+   terra::rast()
+ names(pred_8)<-"Pred_8"
+
+ pred_80<-imglist %>%
+   filter(size == 80,
+          type == "Pred") %>%
+   pull(path) %>%
+   terra::rast()
+ names(pred_80)<-"Pred_80"
+
+prob_80<-imglist %>%
+   filter(size == 80,
+          type == "Prob") %>%
+   pull(path) %>%
+   terra::rast()
+ names(prob_80)<-"Prob_80"
+
+ model_80<-imglist %>%
+   filter(size == 80,
+          type == "Pred") %>%
+   pull(path) %>%
+   terra::rast()
+ values(model_80)<-c(1:ncell(model_80))
+ names(model_80)<-"ID_80"
+
+ model_80_rs_to_8<-terra::resample(model_80,pred_8,method = "near")
+ names(model_80_rs_to_8)<-"ID_80"
+
+ df_80_8<-terra::rast(list(model_80_rs_to_8,pred_8)) %>%
+   as.data.frame(xy=F) %>%
+   filter(!Pred_8 == 0)
+
+ df_80<-terra::rast(list(model_80,pred_80,prob_80)) %>%
+   as.data.frame(xy=F) %>%
+   filter(!Pred_80 == 0)
+
+#############
+output_80<-df_80 %>% 
+  left_join(df_80_8, by = "ID_80") %>% 
+  filter(!is.na(Pred_8)) %>% 
+  mutate(Class_80 = case_when(Pred_80 == 1 ~ "Bare Sediment",
+                              Pred_80 == 2 ~ "Green Algae",
+                              Pred_80 == 3 ~ "Bare Sediment",
+                              Pred_80 == 4 ~ "Magnoliopsida",
+                              Pred_80 == 5 ~ "Microphytobenthos",
+                              Pred_80 == 6 ~ "Magnoliopsida",
+                              Pred_80 == 7 ~ "Phaeophyceae",
+                              Pred_80 == 8 ~ "Rhodophyceae",
+                              Pred_80 == 9 ~ "Sun Glint",
+                              Pred_80 == 10 ~ "Water",
+                              Pred_80 == 11 ~ "Xanthophyceae",
+                              TRUE ~ as.character(Pred_80)),
+         Class_8 = case_when(Pred_8 == 1 ~ "Bare Sediment",
+                              Pred_8 == 2 ~ "Green Algae",
+                              Pred_8 == 3 ~ "Bare Sediment",
+                              Pred_8 == 4 ~ "Magnoliopsida",
+                              Pred_8 == 5 ~ "Microphytobenthos",
+                              Pred_8 == 6 ~ "Magnoliopsida",
+                              Pred_8 == 7 ~ "Phaeophyceae",
+                              Pred_8 == 8 ~ "Rhodophyceae",
+                              Pred_8 == 9 ~ "Sun Glint",
+                              Pred_8 == 10 ~ "Water",
+                              Pred_8 == 11 ~ "Xanthophyceae",
+                              TRUE ~ as.character(Pred_8))
+         ) %>% 
+   dplyr::filter(Class_80 != "Water",
+                 Class_80 != "Phaeophyceae",
+                 Class_80 != "Sun Glint",
+                 Class_8 != "Water",
+                 Class_8 != "Phaeophyceae",
+                 Class_8 != "Sun Glint") %>% 
+           group_by(ID_80, Prob_80) %>% 
+           summarise(prop_Sed = sum((Pred_8 == 1)|(Pred_8 == 3))/n(),
+                     prop_Green = sum(Pred_8 == 2)/n(),
+                     prop_Magno = sum((Pred_8 == 4)|(Pred_8 == 6))/n(),
+                     prop_MPB = sum(Pred_8 == 5)/n(),
+                     prop_Rodo = sum(Pred_8 == 8)/n(),
+                     prop_Xantho = sum(Pred_8 == 11)/n(),
+                     True = unique(Class_80)) %>%
+  pivot_longer(-c(ID_80,True,Prob_80), names_to = "Class", values_to = "Proportion") %>% 
+  mutate(Class = case_when(Class == "prop_Sed" ~ "Bare Sediment",
+                           Class == "prop_Green" ~ "Green Algae",
+                           Class == "prop_Magno" ~ "Magnoliopsida",
+                           Class == "prop_MPB" ~ "Microphytobenthos",
+                           Class == "prop_Pheo" ~ "Phaeophyceae",
+                           Class == "prop_Rodo" ~ "Rhodophyceae",
+                           Class == "prop_Glint" ~ "Sun Glint",
+                           Class == "prop_Water" ~ "Water",
+                           Class == "prop_Xantho" ~ "Xanthophyceae"),
+         same = case_when(True == Class ~ 1,
+                          TRUE ~ 0)) %>% 
+  dplyr::filter(!Proportion == 0)
+
+  list<-output_80 %>% 
+  dplyr::filter(Proportion == 1,
+                Class == True) %>% 
+  pull(ID_80)
+
+output_80_filtered<-output_80 %>% 
+  dplyr::filter(!ID_80 %in% list )
+
+output_80_filtered_same<-output_80_filtered %>% 
+  dplyr::filter(same == 1)
+
+write.csv(output_80_filtered, "./Output/output_80_filtered_Upscaling.csv")
+write.csv(output_80_filtered_same, "./Output/output_80_filtered_same_Upscaling.csv")
+
+}else{
+
+  output_80_filtered<-read.csv("./Output/output_80_filtered_Upscaling.csv") %>% 
+    dplyr::mutate(Proportion = Proportion *100) %>% 
+    dplyr::select(-X) %>% 
+    as_tibble()
+  output_80_filtered_same<-read.csv("./Output/output_80_filtered_same_Upscaling.csv")%>% 
+    dplyr::mutate(Proportion = Proportion *100) %>% 
+    dplyr::select(-X) %>% 
+    as_tibble()
+}
+
+################# LM ####################
+lm_sediment<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Bare Sediment")
+
+ lm_sediment<- lm(lm_sediment$Prob_80 ~ lm_sediment$Proportion)
+
+ lm_green<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Green Algae") 
+  lm_green<- lm(lm_green$Prob_80 ~ lm_green$Proportion)
+
+ lm_magno<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Magnoliopsida") 
+   lm_magno<- lm(lm_magno$Prob_80 ~ lm_magno$Proportion)
+
+ lm_MPB<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Microphytobenthos")
+    lm_MPB<- lm(lm_MPB$Prob_80 ~ lm_MPB$Proportion)
+
+lm_Rodo<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Rodophyceae")
+    lm_Rodo<- lm(lm_Rodo$Prob_80 ~ lm_Rodo$Proportion)
+
+ ########### ALPHA ###############
+alpha_sed<-data.frame(prop = seq(0,1,  0.01)) %>% 
+  mutate(alpha = lm_sediment$coefficients[[2]]*prop+lm_sediment$coefficients[[1]],
+         ID = c(1:nrow(.)),
+         xmin = seq(0,1,  0.01),
+         xmax = seq(0.01,1.01,0.01),
+         ymin = rep(0,nrow(.)),
+         ymax = rep(1,nrow(.))) %>% 
+  pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+  pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+  mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+  dplyr::select(-c(name_x,name_y)) %>% 
+  mutate(alpha = case_when(alpha > 1 ~ 1,
+                           TRUE ~ alpha),
+         alpha = 1-alpha)%>% 
+  mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+alpha_green<-data.frame(prop = seq(0,1,  0.01)) %>% 
+  mutate(alpha = lm_green$coefficients[[2]]*prop+lm_green$coefficients[[1]],
+         ID = c(1:nrow(.)),
+         xmin = seq(0,1,  0.01),
+         xmax = seq(0.01,1.01,0.01),
+         ymin = rep(0,nrow(.)),
+         ymax = rep(1,nrow(.))) %>% 
+  pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+  pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+  mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+  dplyr::select(-c(name_x,name_y)) %>% 
+  mutate(alpha = case_when(alpha > 1 ~ 1,
+                           TRUE ~ alpha),
+         alpha = 1-alpha)%>% 
+  mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+alpha_magno<-data.frame(prop = seq(0,1,  0.01)) %>% 
+  mutate(alpha = lm_magno$coefficients[[2]]*prop+lm_magno$coefficients[[1]],
+         ID = c(1:nrow(.)),
+         xmin = seq(0,1,  0.01),
+         xmax = seq(0.01,1.01,0.01),
+         ymin = rep(0,nrow(.)),
+         ymax = rep(1,nrow(.))) %>% 
+  pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+  pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+  mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+  dplyr::select(-c(name_x,name_y)) %>% 
+  mutate(alpha = case_when(alpha > 1 ~ 1,
+                           TRUE ~ alpha),
+         alpha = 1-alpha)%>% 
+  mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+alpha_MPB<-data.frame(prop = seq(0,1,  0.01)) %>% 
+  mutate(alpha = lm_MPB$coefficients[[2]]*prop+lm_MPB$coefficients[[1]],
+         ID = c(1:nrow(.)),
+         xmin = seq(0,1,  0.01),
+         xmax = seq(0.01,1.01,0.01),
+         ymin = rep(0,nrow(.)),
+         ymax = rep(1,nrow(.))) %>% 
+  pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+  pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+  mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+  dplyr::select(-c(name_x,name_y)) %>% 
+  mutate(alpha = case_when(alpha > 1 ~ 1,
+                           TRUE ~ alpha),
+         alpha = 1-alpha)%>% 
+  mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+alpha_Rodo<-data.frame(prop = seq(0,1,  0.01)) %>% 
+  mutate(alpha = lm_Rodo$coefficients[[2]]*prop+lm_Rodo$coefficients[[1]],
+         ID = c(1:nrow(.)),
+         xmin = seq(0,1,  0.01),
+         xmax = seq(0.01,1.01,0.01),
+         ymin = rep(0,nrow(.)),
+         ymax = rep(1,nrow(.))) %>% 
+  pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+  pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+  mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+  dplyr::select(-c(name_x,name_y)) %>% 
+  mutate(alpha = case_when(alpha > 1 ~ 1,
+                           TRUE ~ alpha),
+         alpha = 1-alpha)%>% 
+  mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+# alpha_xantho<-data.frame(prop = seq(0,1,  0.01)) %>% 
+#   mutate(alpha = lm_xantho$coefficients[[2]]*prop+lm_xantho$coefficients[[1]],
+#          ID = c(1:nrow(.)),
+#          xmin = seq(0,1,  0.01),
+#          xmax = seq(0.01,1.01,0.01),
+#          ymin = rep(0,nrow(.)),
+#          ymax = rep(1,nrow(.))) %>% 
+#   pivot_longer(c(xmin,xmax),names_to = "name_x", values_to = "x") %>% 
+#   pivot_longer(c(ymax,ymin), names_to = "name_y",values_to = "y") %>% 
+#   mutate(y = rep(c(0,1,1,0),nrow(.)/4)) %>% 
+#   dplyr::select(-c(name_x,name_y)) %>% 
+#   mutate(alpha = case_when(alpha > 1 ~ 1,
+#                            TRUE ~ alpha),
+#          alpha = 1-alpha) %>% 
+#   mutate(alpha = (alpha - min(alpha))/ (max(alpha) - min(alpha)))
+
+#################
+
+sediment<-output_80_filtered %>% 
+  dplyr::filter(True == "Bare Sediment") %>% 
+  mutate(Class = case_when(Class != True ~ "Other",
+                            TRUE ~ Class)) %>% 
+  group_by(ID_80,Class) %>% 
+  reframe(Prob_80 = unique(Prob_80),
+          True = unique(True),
+          Class = unique(Class),
+          Proportion = sum(Proportion)) %>% 
+  mutate(Class = as.factor(Class),
+         Class = forcats::fct_relevel(Class,"Bare Sediment", after = Inf)) %>% 
+  ggplot()+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,show.legend = F,position = "fill",adjust = 3)+
+  # facet_wrap(~ True)+
+  scale_fill_manual(values=c("gray85","#70543e"))+
+  # scale_alpha_manual(values = c(0.5,1))+
+  theme_Bede()+
+  # geom_polygon(data = alpha_sed, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_sed$alpha,color=NA, fill = "white")+
+  geom_vline(xintercept = (lm_sediment$coefficients[[2]]*85+lm_sediment$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
+  ggtitle("Bare Sediment")+
+  # annotate(geom="text",x = lm_sediment$coefficients[[2]]*0.85+lm_sediment$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15)
+        # axis.title.y = element_blank(),
+        # axis.title.x = element_text(size = 20)
+        )
+
+green<-output_80_filtered %>% 
+  dplyr::filter(True == "Green Algae") %>% 
+  mutate(Class = case_when(Class != True ~ "Other",
+                            TRUE ~ Class)) %>% 
+  group_by(ID_80,Class) %>% 
+  reframe(Prob_80 = unique(Prob_80),
+          True = unique(True),
+          Class = unique(Class),
+          Proportion = sum(Proportion)) %>%
+  mutate(Class = as.factor(Class),
+         Class = forcats::fct_relevel(Class,"Green Algae", after = Inf)) %>% 
+  ggplot()+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,show.legend = F,position = "fill",adjust = 3)+
+  # facet_wrap(~ True)+
+  scale_fill_manual(values=c("gray85", "#b3ff1a"))+
+  # scale_alpha_manual(values = c(0.5,1))+
+  theme_Bede()+
+  # geom_polygon(data = alpha_green, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_green$alpha,color=NA, fill = "white")+
+  geom_vline(xintercept = (lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
+  ggtitle("Green Algae")+
+  # annotate(geom="text",x = lm_green$coefficients[[2]]*0.85+lm_green$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15)
+        # axis.title.y = element_blank(),
+        # axis.title.x = element_text(size = 20)
+        )
+
+magno<-output_80_filtered %>% 
+  dplyr::filter(True == "Magnoliopsida") %>% 
+  mutate(Class = case_when(Class != True ~ "Other",
+                            TRUE ~ Class)) %>% 
+  group_by(ID_80,Class) %>% 
+  reframe(Prob_80 = unique(Prob_80),
+          True = unique(True),
+          Class = unique(Class),
+          Proportion = sum(Proportion)) %>%
+  mutate(Class = as.factor(Class),
+         Class = forcats::fct_relevel(Class,"Magnoliopsida", after = Inf)) %>%
+  ggplot()+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,show.legend = F, position = "fill",adjust = 3)+
+  # facet_wrap(~ True)+
+  scale_fill_manual(values=c("gray85","#389350"))+
+  # scale_alpha_manual(values = c(0.5,1))+
+  theme_Bede()+
+  # geom_polygon(data = alpha_magno, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_magno$alpha,color=NA, fill = "white")+
+  geom_vline(xintercept = (lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
+  ggtitle("Magnoliopsida")+
+  # annotate(geom="text",x = lm_magno$coefficients[[2]]*0.85+lm_magno$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15)
+        # axis.title.y = element_blank(),
+        # axis.title.x = element_text(size = 20)
+        )
+
+MPB<-output_80_filtered %>% 
+  dplyr::filter(True == "Microphytobenthos") %>% 
+  mutate(Class = case_when(Class != True ~ "Other",
+                            TRUE ~ Class)) %>% 
+  group_by(ID_80,Class) %>% 
+  reframe(Prob_80 = unique(Prob_80),
+          True = unique(True),
+          Class = unique(Class),
+          Proportion = sum(Proportion)) %>%
+  mutate(Class = as.factor(Class),
+         Class = forcats::fct_relevel(Class,"Microphytobenthos", after = Inf)) %>%
+  ggplot()+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,show.legend = F,position = "fill",adjust = 3)+
+  # facet_wrap(~ True)+
+  scale_fill_manual(values=c("gray85","#DAA520"))+
+  # scale_alpha_manual(values = c(0.5,1))+
+  theme_Bede()+
+  # geom_polygon(data = alpha_MPB, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_MPB$alpha,color=NA, fill = "white")+
+  geom_vline(xintercept = (lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
+  ggtitle("Microphytobenthos")+
+  # annotate(geom="text",x = lm_MPB$coefficients[[2]]*0.85+lm_MPB$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15)
+        # axis.title.y = element_blank(),
+        # axis.title.x = element_text(size = 20)
+        )
+
+rodo<-output_80_filtered %>% 
+  dplyr::filter(True == "Rodophyceae") %>% 
+  mutate(Class = case_when(Class != True ~ "Others Classes",
+                           Class == "Rodophyceae" ~ "Rhodophyceae",
+                            TRUE ~ Class),
+         True = case_when(True == "Rodophyceae" ~ "Rhodophyceae",
+                          TRUE ~ True)) %>% 
+  group_by(ID_80,Class) %>% 
+  reframe(Prob_80 = unique(Prob_80),
+          True = unique(True),
+          Class = unique(Class),
+          Proportion = sum(Proportion)) %>%
+  mutate(Class = factor(Class, c("Others Classes","Rhodophyceae","Bacillariophyceae", "Magnoliopsida","Chlorophyceae","Phaeophyceae"))) %>% 
+         # Class = forcats::fct_relevel(Class,"Rodophyceae", after = Inf)) %>%
+  ggplot()+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,position = "fill",adjust = 3)+
+  # facet_wrap(~ True)+
+  scale_fill_manual("Class",
+                    labels = c("Others Classes","Rhodophyceae","Bacillariophyceae", "Magnoliopsida","Chlorophyceae","Phaeophyceae"),
+                    values=c("gray85","#b3002d","#DAA520","#389350","#b3ff1a","#70543e"),
+                    drop = F)+
+  # scale_alpha_manual(values = c(0.5,1))+
+  theme_Bede()+
+  # geom_polygon(data = alpha_Rodo, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_Rodo$alpha,color=NA, fill = "white")+
+  geom_vline(xintercept = (lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
+  ggtitle("Rhodophyceae")+
+  # annotate(geom="text",x = lm_Rodo$coefficients[[2]]*0.85+lm_Rodo$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        # axis.title.y = element_blank(),
+        # axis.title.x = element_text(size = 20),
+        legend.text = element_text(size = 15),
+        legend.key.size = unit(1,"cm"),
+        legend.title = element_blank())
+
+# xantho<-output_80_filtered %>% 
+#   dplyr::filter(True == "Xanthophyceae") %>% 
+#   ggplot()+
+#   geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),position = "fill",adjust = 3)+
+#   # facet_wrap(~ True)+
+#   scale_fill_manual(values=c("#70543e", "#b3ff1a", "#389350", "#DAA520","#b3002d", "#cccc00"))+
+#   # scale_alpha_manual(values = c(0.5,1))+
+#   theme_Bede()+
+#   geom_polygon(data = alpha_xantho, mapping = aes(x=x, y = y, alpha = alpha, group = ID),alpha = alpha_xantho$alpha,color=NA, fill = "white")+
+#   geom_vline(xintercept = lm_xantho$coefficients[[2]]*0.85+lm_xantho$coefficients[[1]])+
+#   ggtitle("Xanthophyceae")+
+#   annotate(geom="text",x = lm_xantho$coefficients[[2]]*0.85+lm_xantho$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
+#   theme(axis.text.x = element_text(size = 15, angle = 45, hjust = 0.7),
+#         axis.text.y = element_text(size = 15),
+#         axis.title.y = element_blank(),
+#         axis.title.x = element_text(size = 20))
+
+plot<-(sediment + green) /
+(MPB + rodo)+
+magno+
+  patchwork::plot_layout(guides = "collect") &
+  theme(legend.position = "bottom",
+        plot.title = element_text(size=25, hjust = 0.55),
+        axis.text.x = element_text(size = 15, hjust = 0.8),
+        axis.title = element_text(size=20),
+        axis.text.y = element_text(size = 15),
+        panel.grid=element_blank())&
+  scale_x_continuous(breaks = c(25,50,75,100),limits= c(0,100.01),expand = c(0, 0)) &
+  scale_y_continuous(expand = c(0, 0)) &
+  xlab("Percent Cover (%)") & 
+  ylab("Density")
+
+ggsave("Figures/Upscaling/density_vs_Proportion.png",plot , width = 833*4, height = 1118*4, units = "px")
+
+```
+
+```{r Upscaling prob}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: true
+
+output_80_filtered_same<-read.csv("./Output/output_80_filtered_same_Upscaling.csv")%>% 
+    dplyr::mutate(Proportion = Proportion *100) %>% 
+    dplyr::select(-X) %>% 
+    as_tibble()
+
+################# LM ####################
+lm_sediment<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Bare Sediment")
+
+ lm_sediment<- lm(lm_sediment$Prob_80 ~ lm_sediment$Proportion)
+
+ lm_green<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Green Algae") 
+  lm_green<- lm(lm_green$Prob_80 ~ lm_green$Proportion)
+
+ lm_magno<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Magnoliopsida") 
+   lm_magno<- lm(lm_magno$Prob_80 ~ lm_magno$Proportion)
+
+ lm_MPB<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Microphytobenthos")
+    lm_MPB<- lm(lm_MPB$Prob_80 ~ lm_MPB$Proportion)
+
+lm_Rodo<-output_80_filtered_same %>%
+  dplyr::filter(Class == "Rodophyceae")
+    lm_Rodo<- lm(lm_Rodo$Prob_80 ~ lm_Rodo$Proportion)
+
+```
+
+```{r Upscaling Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Kernel density plot showing the proportion of pixel well classified based on the percent cover of the class in high altitude flight pixels of Gafanha, Portugal.
+Each subplot shows all the pixels of the same classes on the hight altitude flight.
+Percent cover of classes is retrieve using the result of the classification of the low altitude flight of Gafanha, Portugal.
+The vertical dashed line shows the 0.85 probability of the model.
+Everything on the right of this line has a probability higher then 0.85 and everuthing on the left of this line has a probability lower.
+#| label: fig-upscaling
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "90%"
+
+knitr::include_graphics("Figures/Upscaling/density_vs_Proportion.png")
+
+```
+
+@fig-upscaling is showing the percent cover of a class required to classify correctly the high altitude flight.
+When the percent cover of the class is 100 %, big pixels are well classified for all the classes excepted for Bare Sediment, where it's well classified 80% of the time.
+A vegetative percent cover of at least 80% is need to have all the big pixels well classified, at the exception of Magnoliopsida that needs an higher percent cover (\>90 %) to be well classified.
+Concerning the probability of each class, a really high Percent cover is needed to confidently predict Bacillariophyceae.
+To predict Chlorophyceae with a confidence of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % is needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
+
+# Discussion
+
+## Seagrass Discrimination
+
+## Spatial and Spectral Resolution impact on the prediction
+
+```{r Table Pigment}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+df_pigment<-
+  data.frame(
+    Classes=c("Magnoliopsida",
+           "Chlorophyceae",
+           "Bacillariophyceae",
+           "Phaeophyceae",
+           "Rhodophyceae"),
+    chlb=c(1,1,0,0,0),
+    chlc=c(0,0,1,1,0),
+    fuco=c(0,0,1,1,0),
+    zea=c(1,1,0,1,0),
+    diad=c(0,0,1,0,0),
+    lutein=c(1,1,0,0,0),
+    Neox=c(1,1,0,0,0),
+    PE=c(0,0,0,0,1),
+    PC=c(0,0,0,0,1))%>%
+  select(-Classes) %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+ext(df_pigment)<-c(0,9,0,5)
+
+y_axis_text_pigment<-data.frame(x = rep(-0.05,5),
+                                y = c(0.5,1.5,2.5,3.5,4.5), 
+                                lab = c("Rhodophyceae",
+                                    "Phaeophyceae",
+                                    "Bacillariophy.",
+                                    "Chlorophyceae",
+                                    "Magnoliopsida")
+                                )
+x_axis_text_pigment<-data.frame(y = rep(5.5,9),
+                                x = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5),
+                                lab = c("Chlb","Chlc","Fuco","Zea","Diad","Lut","Neo","PE","PC")
+                                )
+
+min_x_line = -1.5
+max_y_line = 6
+
+line_grid<-data.frame(xmin=NA,
+                      xmax=NA,
+                      ymin=NA,
+                      ymax=NA,
+                      group=NA)
+
+for(i in 0:max_y_line){
+  line_grid[i+1,1]=min_x_line
+  line_grid[i+1,2]=9
+  line_grid[i+1,3]=i
+  line_grid[i+1,4]=i
+  line_grid[i+1,5]=i+1
+}
+nrowgrid=nrow(line_grid)
+for(i in 0:9){
+  line_grid[i+1+nrowgrid,1]=i
+  line_grid[i+1+nrowgrid,2]=i
+  line_grid[i+1+nrowgrid,3]=0
+  line_grid[i+1+nrowgrid,4]=max_y_line
+  line_grid[i+1+nrowgrid,5]=i+1+nrowgrid
+
+}
+
+ line_grid[nrow(line_grid)+1,1] = min_x_line
+ line_grid[nrow(line_grid),2] = min_x_line
+ line_grid[nrow(line_grid),3] = 0
+ line_grid[nrow(line_grid),4] = max_y_line
+ line_grid[nrow(line_grid),5] = nrow(line_grid)
+
+ line_grid<- line_grid %>% 
+   rbind(c(-1.5,9,-0.6,-0.6,19))%>% 
+   rbind(c(-1.5,-1.5,-0.6,0,20))%>% 
+   rbind(c(0,0,-0.6,0,21))%>% 
+   rbind(c(1,1,-0.6,0,22))%>% 
+   rbind(c(2,2,-0.6,0,23))%>% 
+   rbind(c(3,3,-0.6,0,24))%>% 
+   rbind(c(4,4,-0.6,0,25))%>% 
+   rbind(c(5,5,-0.6,0,26))%>% 
+   rbind(c(6,6,-0.6,0,27))%>% 
+   rbind(c(7,7,-0.6,0,28))%>% 
+   rbind(c(8,8,-0.6,0,29))%>% 
+   rbind(c(9,9,-0.6,0,30))
+
+ Absorption_wv<- data.frame(x = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5),
+                            y = rep(-0.3,9),
+                            lab = c("650","636","550","489","496","490","450","566","615"))
+
+rast_pigment<-ggplot()+
+  geom_spatraster(data = (df_pigment),
+                  # show.legend = F,
+                  na.rm = TRUE
+                  )+
+  coord_fixed(ratio = 0.7)+
+  scale_fill_gradientn(
+    # colours = c("black","firebrick4","goldenrod","yellow","chartreuse3"),
+    # colours = c("khaki1","goldenrod","firebrick3","chartreuse4"),
+    colours = c("firebrick4","orange","#007d00"),
+    # colours = c("#7d0000","#00b300","#00b300","#00b300","#007d00"),
+    na.value = "white",
+    labels = c("Absence","no se","Presence"),
+    breaks = c(0,0.5,1))+
+  geom_text(
+    data = y_axis_text_pigment,
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    hjust = 1,
+    size = 6,
+    # angle = 20
+    )+
+  geom_text(
+    data = data.frame(x = -0.05, y = -0.3, lab = "Absorption (nm)"),
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    hjust = 1,
+    size = 5,
+    # angle = 20
+    )+
+  geom_text(
+    data = Absorption_wv,
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    hjust = 0.5,
+    size = 6,
+    # angle = 20
+    )+
+  geom_text(
+    data = x_axis_text_pigment,
+    aes(x = x, y = y, label = lab),
+    # fill = "#ffffff99",
+    hjust = 0.5,
+    size = 7,
+    # angle = 20
+    )+
+  geom_segment(data = line_grid, 
+               aes(x = xmin, xend = xmax, y = ymin, yend = ymax, group = group),
+               linewidth = 1)+
+  xlim(c(-2,9))+
+  ylim(c(-1,6.1))+
+  theme_Bede()+
+  theme(
+  # axis.title.x = element_text(size = 35),
+        # axis.title.y = element_text(size = 35),
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+
+        # axis.text.x = element_text(size = 30),
+        axis.text.x = element_blank(),
+        # axis.text.y = element_text(size = 25),
+         axis.text.y = element_blank(),
+
+        axis.ticks.x = element_blank(),
+        axis.ticks.y = element_blank(),
+        panel.border = element_blank(),
+        axis.line=element_blank(),
+        # legend.position = "top",
+        legend.position = "none",
+        legend.direction="horizontal",
+        legend.key.width = unit(2,"cm"),
+        legend.text = element_text(size = 20),
+        legend.title = element_text(size = 20, vjust = 2),
+        legend.title.align = 0.5,
+        legend.justification = "center")
+
+# rast_pigment
+
+ggsave("./Figures/Disc_Pigment_Table.png",rast_pigment, width= 1066*4, height=516*4, units = "px")
+
+```
+
+```{r Plot Table Pigment}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: !expr "Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
+Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin."
+#| label: fig-Pigm
+#| fig-width: 10
+#| fig-height: 5
+#| out-width: "100%"
+
+# Pigment composition of the different vegetation classes.
+Green indicate the presence of the pigment in the class while red indicate the abscence.
+Chlb : Chlorophyll-b ; Chlc : Chlorophyll-c ; Fuco : Fucoxanthin ; Zea : Zeaxanthin ; Diad : Diadinoxanthin ; Lut : Lutein ; Neo : Neoxanthin ; PE : Phycoerythrin ; PC : Phycocyanin.
+
+knitr::include_graphics("./Figures/Disc_Pigment_Table.png")
+```
+
+```{r Reflectance_Validation 2 height}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
+  rast()
+
+# low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+#   rast()
+
+low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
+  rast() %>% 
+  resample(high_alt, method = "med")
+
+low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
+  rast()
+
+mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
+  vect()
+
+high_alt_masked<-crop(high_alt,mask)
+high_alt_masked<-mask(high_alt_masked,mask)
+
+low_alt_masked<-crop(low_alt,mask)
+low_alt_masked<-mask(low_alt_masked,mask)
+
+low_alt_pred_masked<-crop(low_alt_pred,mask)
+low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
+
+stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
+  as.data.frame()
+
+names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
+              "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
+              "pred")
+
+stk_long<-stk %>% 
+  mutate(px_ID = c(1:nrow(stk))) %>% 
+  pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
+  mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
+                         str_detect(Bands, "high") ~ "High",
+                         TRUE ~ "NA"),
+         Bands = gsub("_high","",Bands),
+         Bands = gsub("_low","",Bands))
+
+stk_summarized<-stk_long %>% 
+  # group_by(px_ID,alt) %>% 
+  # reframe(Value = mean(Value),
+  #         pred = unique(pred)) %>% 
+  pivot_wider(names_from = "alt", values_from = "Value")
+
+df<-stk_summarized %>% 
+  ungroup() %>% 
+  group_by(Bands) %>% 
+  filter(Low<10000,
+         High < 10000,
+         Low < quantile(Low,probs = 0.99),
+         High < quantile(High,probs = 0.99),
+         Low > quantile(Low,probs = 0.01),
+         High > quantile(High,probs = 0.01),
+         !pred %in% c(7,9,3,10)) %>%
+  ungroup()
+
+plot <- df %>% 
+  group_by(pred) %>% 
+  sample_n(10000) %>% 
+  rearrr::rotate_2d(x_col = "Low", y_col = "High",degrees = 9, origin = c(0,0)) %>% select(Low_rotated,High_rotated) %>% 
+  rename(Low = Low_rotated, High = High_rotated) %>% 
+  mutate(Low = Low /10000, 
+         High = High/10000) %>% 
+  ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(0,6000),
+                               breaks = c(0,2000,4000,6000),
+                               labels = c("1","2000","4000","6000"))+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "red" )+
+  theme_Bede()+
+  ylim(c(0.05,0.6))+
+  xlim(c(0.05,0.6))+
+  ylab("Reflectance of the 120m flight")+
+  xlab("Reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+ggsave("./Figures/Compare_reflectance.png",plot, width= 472*4, height=402*4, units = "px")
+
+```
+
+```{r Plot Reflectance_Validation 2 height}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a 1 to 1 relationship. 
+#| label: fig-CompareRef
+#| fig-width: 5
+#| fig-height: 5
+#| out-width: "50%"
+
+# Pigment composition of the different vegetation classes.
+Green indicate the presence of the pigment in the class while red indicate the abscence.
+Chlb : Chlorophyll-b ; Chlc : Chlorophyll-c ; Fuco : Fucoxanthin ; Zea : Zeaxanthin ; Diad : Diadinoxanthin ; Lut : Lutein ; Neo : Neoxanthin ; PE : Phycoerythrin ; PC : Phycocyanin.
+
+knitr::include_graphics("./Figures/Compare_reflectance.png")
+```
+
+## Big picture
+
+# Conclusion
+
+# Bibliography

### 2024-02-27 _manuscript/_tex/index.tex
add all big files

@@
 
+\usepackage{fontspec}
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{colortbl}
+\usepackage{hhline}
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{wrapfig}
 \makeatletter
@@
 \begin{abstract}
-In September 2021, a significant jump in seismic activity on the island
-of La Palma (Canary Islands, Spain) signaled the start of a volcanic
-crisis that still continues at the time of writing. Earthquake data is
-continually collected and published by the Instituto Geográphico
-Nacional (IGN). \ldots{}
+Coastal areas host seagrass meadows, which offer crucial ecosystem
+services including erosion control and carbon sequestration. However,
+these areas are increasingly impacted by human activities, leading to
+seagrass decline and habitat fragmentation. In situ surveys,
+traditionally performed to monitor these ecosystems face limitations on
+temporal and spatial coverage, particularly in intertidal zones,
+prompting the use of satellite data within monitoring programs. Yet,
+satellite remote sensing struggles with spatial and spectral resolution,
+making it difficult to discriminate seagrass from other macrophytes in
+highly heterogenous meadows. To address these challenges, drone images
+acquired with multi-spectral sensors offer a promising solution. This
+study focuses on using drones acquisitions for mapping intertidal
+macrophytes, effectively discriminating between seagrass and green
+macroalgae. Ten drone flights were conducted at two different altitudes
+(12m and 120m) across diverse European habitats in France and Portugal.
+Low altitude flights were used to train a Deep Learning classifier based
+on Neural Networks to discrimintate among 5 intertidal vegetation
+classes. Drone mapping demonstrated an overall accuracy of 94\% across
+all the sites and images, covering a total area of 467 000 m². The model
+exhibited an accuracy of 96.4\% in identifying seagrass.
 \end{abstract}
@@
 \end{frontmatter}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
 
@@
 
+\section{Material \& Methods}\label{material-methods}
+
+\subsection{Study sites}\label{study-sites}
+
+Seven study sites distributed between France and Portugal were selected
+for their relatively extensive intertidal seagrass beds. Two sites are
+located in Gulf of Morbihan (Figure~\ref{fig-map} A), France (47.5791°N,
+2.8018°W). This gulf covers an area of 115 km² and is only connect to
+the sea through a 900m wide channel. A total of 53 small islands are
+scattered across the gulf leading to 250 km of shorelines. Patchy
+seagrass meadows can be found on a lot of these islands. Within the Gulf
+of Morbihan we have chosen two sites : One is located in one of these
+island (Arz island). The other one is located in the sourthern part of
+the Gulf (Duer). Two others sites are located in Bourgneuf Bay, France
+(46.9849°N, 2.1488°W). This bay is a semi-enclosed macrotidal bay,
+protected from waves by Noirmoutier Island. With up to 6m in tidal range
+during spring tide, a 6 km² seagrass meadow can uncover at low tide. The
+sites we surveyed (L'Epine and Barbatre, Figure~\ref{fig-map} B) are
+located in the southernmost part of the bay, along the Noirmoutier
+Island, and host a monospecific \emph{Zostera noltei} seagrass bed with
+very little mixing with other macrophytes. Three sites have been survey
+in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W). The
+extent of this lagoon is about 80 km² with many narrow channels, large
+salt marshes and many mudflats that uncovers at low tide. It is
+connected to the open sea through a single channel, with a tidal lag
+between the North and the South of the lagoon. The southernmost site
+(Gafanha) is a mudflat located in an affluent of the lagoon whereas the
+two other sites are situated in the middle of the lagoon and are only
+accessible by boat (Figure~\ref{fig-map} C). These Portuguese sites were
+characterized by a more diverse intertidal area, where the seagrass
+meadow could intermingle with red algae (Rhodophyceae), brown algae
+(Phaeophyceae), or green algae (Chlorophyceae).
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-map}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=26.67in,height=\textheight]{./Figures/Fig1_Map_Drone_Sites.png}
+
+}
+
+\caption{\label{fig-map}Sites where the different drone flights were
+made. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon.
+Light green represent terrestrial areas whereas darkgreen represent
+intertidal areas.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\subsection{Drone Data}\label{drone-data}
+
+At each location, a DJI Matrice 200 quadcopter drone equipped with a
+Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
+million pixel reflectance photographs in 10 spectral bands, from blue
+(444 nm) to near infrared (840 nm). An angle of 90° has been maintained
+between the sun and the drone's route to guarantee uniform lighting
+conditions between flight lines. A side overlap of 70\% and a front
+overlap of 80\% between each image has been set. Images have been
+calibrated in reflectance using a calibration panel reflective at
+\textasciitilde50\% provided by the camera's manufaturer and a
+Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance
+data during the flight. A Structure-from-Motion photogrammetry software
+(Agisoft Metashape) has been used to process images to obtain
+multispectral orthomosaics of each flight. The workflow for
+orthomosaicking has remained consistent for every flight. First, tying
+key points were detected inside of each image and between overlapping
+images in order to obtain a sparse point cloud. This cloud was cleaned
+using reprojection accuracy metric in order to remove noisy points. A
+dense point cloud has been then produced using a structure from motion
+algorithm. A surface interpolation of this dense point cloud has been
+made to obtain a Digital Surface Model (DSM), used to reconstruct the
+multispectral ortho-image. Across all the sites, flights were made at
+two different altitudes : 12 m or/and 120 m. Low altitude drone flights
+produce ortho-images with a very high spatial resolution (8 mm per
+pixel), making it simple to visually distinguish between the various
+types of vegetation. High altitude fights on the other hand allow to
+cover large areas and produced images with a pixel size of 80 mm (Table
+1).
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{ccccc}
+\caption{List of drone Flight, summarising the date, the altitude and the purpose
+of each flight.}\tabularnewline
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\
+
+\ascline{1.5pt}{000000}{1-5}\endfirsthead
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\
+
+\ascline{1.5pt}{000000}{1-5}\endhead
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Arz\ Island}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{\multirow[c]{-3}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Morbihan}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{666666}{2-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Barbâtre}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{\multirow[c]{-5}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{France}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-2}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bourgneuf\ Bay}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{L'Epine}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{000000}{1-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Inner\ Lagoon}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Mataducos}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+
+\ascline{1.5pt}{BEBEBE}{3-5}
+
+\multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Portugal}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Aveiro\ Lagoon}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
+
+\ascline{1.5pt}{000000}{1-5}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\subsection{Field sampling}\label{field-sampling}
+
+Before each flight, targets used as Ground Control Points (GCPs) were
+dispersed and georeferenced with a Trimble © Geo XH 6000 differential
+GPS (dGPS). GCPs were used to correct georeferencing imprecision of
+orthomosaics with an horizontal and vertical accuracy of 10cm. dGPS was
+also used to georeference quardrats of 0.25cm² used to assess the
+presence or absence of 5 key classes of vegetation : Bacillariophyceae
+(Diatoms forming large biofilm over the sediment during low tide),
+Phaeophyceae (Brown algae), Magnoliopsida (Seagrass), Chlorophyceae
+(Green algae) and Rhodophyceae (Red algae)
+(Figure~\ref{fig-vegetation}). Picture of each quadrat were taken and
+uploaded on the online on the Global Biodiversity Information Facility
+(GBIF) platform \citep{BedeGbif}. Each photograph was also processed to
+estimate the percent cover of each type of vegetation. Georeferenced
+hyperspectral reflectance signatures of each vegetation class were also
+sampled using an ASD FieldSpec HandHeld 2 spectroradiomete, which
+acquires reflectance between 325 and 1075 nm, with 1 nm of spectral
+resolution. The methodological scheme followed in this study is
+presented in Figure~\ref{fig-workflow}.
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-vegetation}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{Figures/Spectral_shapes_total.png}
+
+}
+
+\caption{\label{fig-vegetation}Class of vegetation used to train the CNN
+model and their standardised spectral signature}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\subsection{Intertidal vegetation
+mapping}\label{intertidal-vegetation-mapping}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-workflow}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Figure3_workflow.png}
+
+}
+
+\caption{\label{fig-workflow}Schematic representation of the workflow.
+Diamonds represent input or output data, and rectangles represent Python
+processing algorithms. The overall workflow of this study is divided
+into two distinct parts based on the spatial resolution of the drone
+flights: high-resolution flights were utilized for training and
+prediction of the CNN model, whereas low-resolution flights were solely
+employed for prediction purposes.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The spectral similarities of reflectance signatures between intertidal
+green macrophytes (Magnoliopsida and Chlorophyceae) make their
+discrimination challenging using simple classification algorithms
+(Figure~\ref{fig-vegetation} F). To overcome this challenge, a deep
+learning classification method was developed, trained, validated, and
+applied to each drone flight (Figure~\ref{fig-workflow}).
+
+\subsubsection{Neural Network model
+building}\label{neural-network-model-building}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{ccc}
+\caption{Vegetation Classes of the model and the number of pixels used to train
+and validate each class}\tabularnewline
+
+\ascline{1.5pt}{666666}{1-3}
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\
+
+\ascline{1.5pt}{666666}{1-3}\endfirsthead
+
+\ascline{1.5pt}{666666}{1-3}
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\
+
+\ascline{1.5pt}{666666}{1-3}\endhead
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bacillariophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4,475}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,371,920}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Chlorophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17,140}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{6,258,737}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Magnoliopsida}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{221,065}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{69,079,189}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Phaeophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{169,936}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{18,481,141}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Rhodophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5,771}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1.5pt}{666666}{1-3}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+A dataset containing photo-interpreted drone reflectance pixels was
+built to train a Convolutional Neural Network (CNN) model with 2 hidden
+layers. The training pixels were categorized into 7 different classes,
+representing the various habitats encountered at the different study
+sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae,
+Phaeophyceae and Rhodophyceae. Only low-altitude flights (Table 1) were
+used for training purposes because of their 8 mm spatial resolution
+allowing to avoid spectral sub-pixel mixing and to accurately visually
+differentiate various vegetation classes. More than 418,000 pixels at 8
+mm resolution from the 3 training flights have been used to train the
+model (Table 2). Twenty one variables were used by the model as
+predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX
+multispectral camera (ranging from 444 nm to 840 nm), the same 10
+spectral bands standardized using a min/max transformation
+(Equation~\ref{eq-std} ; \citep{cao2017}) and the NDVI
+(Equation~\ref{eq-ndvi}). Standardisation of spectral bands is used to
+eliminate the scaling differences between spectra and to limit the
+effect of biomass on the shape of the spectra \citetext{\citealp[
+]{Douay2022}; \citealp{Davies2023}}.
+
+\begin{equation}\phantomsection\label{eq-std}{
+R_{i}^{*}(\lambda) = \frac{R_{i}(\lambda) - min(R_{i})}{max(R_{i})- min(R_{i})}
+}\end{equation}
+
+where \(R_{i}(\lambda)\) is the reflectance at the wavelength
+\((\lambda)\) of each individual spectra \((i)\), \(min(R_{i})\), and
+\(max(R_{i})\) are the minimum and maximum value of the spectra \((i)\)
+
+\begin{equation}\phantomsection\label{eq-ndvi}{
+NDVI = \frac{R(840nm)-R(668nm)}{R(840nm)+R(668nm)}
+}\end{equation}
+
+where \(R(840nm)\) is the reflectance at 840 nm and \(R(668nm)\) is the
+reflectance at 668 nm.
+
+\subsubsection{Validation}\label{validation}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The CNN model was applied to all the 9 flights at both 12 and 120 m of
+altitude. In situ information on georeferenced class type and percent
+cover collected during each flight has been used to assess the CNN
+accuracy. These images were used to construct a validation dataset
+indicating the presence or absence of each class. Additionally to the
+quadrat-based validation dataset, polygons of each class were photo
+interpreted in order to increase the number of pixels of the validation
+dataset. A confusion matrix, along with precision metrics such as the
+global accuracy, the sensitivity, the specificity, and the Kappa
+coefficient, was generated for each of the study sites. Finally each
+validation matrix has been merge to create a unique matrix of the model.
+A total of 536,000 pixels has been used to globally validate the CNN
+model.
+
+\section{Results}\label{results}
+
+\subsection{Classification}\label{classification}
+
+A total of 9 prediction maps corresponding to the 9 drone flights were
+obtained. Each prediction map is associated with a probability map,
+indicating the probability of the selected class for every pixel. The
+low-altitude flight conducted in Gafanaha, Portugal, represents the site
+with the highest complexity (Figure~\ref{fig-GafLow}). Among the 5
+vegetation classes on which the CNN model was trained, 4 were present on
+this site. On this site, there is a mixture of Chlorophyceae and
+Rhodophyceae over the seagrass meadow. This is also where
+Bacillariophyceae is most abundant. Although the seagrass bed is solely
+composed of \emph{Zostera noltei}, various colors can be observed: dark
+green (indicating healthy beds with 100\% coverage) and whitish/brown
+(indicating beds where leaves are dying). Regardless of the color, the
+meadow is predicted as Magnoliopsida by the CNN model.
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-GafLow}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_Low_Pred.png}
+
+}
+
+\caption{\label{fig-GafLow}RGB orthomosaic (Left) and Prediction (Right)
+of the low altitude flight of Gafanaha, Portugal. The total extent of
+this flight is 3000m² with a resolution of 8 mm per pixel. Background
+colors means intertidal area (Light Green) and land area (Light Grey).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The high-altitude flight over Gafanha covered nearly 1 km² in total
+(Figure~\ref{fig-GafHigh}). A channel delineating a small island was
+present in the flight, but it has been masked in the prediction map due
+to glinting and misclassification caused by the turbid shallow water.
+Most of the intertidal area has been classified as Magnoliopsida by the
+model, even though there is discoloration of seagrass blades. Only a few
+pixels have been classified as Chlorophyceae at this scale. Furthermore,
+the area that was classified as Bacillariophyceae in the low-altitude
+flight remains mostly classified as such in the high-altitude flight,
+but some pixels of it are now classified as Magnoliopsida. The patches
+of Rhodophyceae are still well classified. \emph{Spartina sp.} was
+present in the northern part of the flight, near the land, and has been
+classified either as Magnoliopsida or as Phaeophyceae.
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-GafHigh}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_High_Pred.png}
+
+}
+
+\caption{\label{fig-GafHigh}RGB orthomosaic (Left) and Prediction
+(Right) of the high altitude flight of Gafanaha, Portugal. The total
+extent of this flight is about 1 km² with a resolution of 80 mm per
+pixel. Background colors means intertidal area (Light Green), land area
+(Light Grey) and water (Light Blue). The red triangle shows the extent
+of the low altitude flight of Gafanha. The zoom covers an area
+equivalent to a 10-meter Sentinel-2 pixel size.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The High altitude flight made in the inner lagoon of the Ria de Aveiro
+is the largest of all flights, covering almost 1.5 km²
+(Figure~\ref{fig-Boat}). On this site, only seagrass and red algae where
+seen on the field. The classification follows the same pattern, with a
+patchy Magnoliopsida meadow mixed on the eastern part of the flight with
+Rhodophyceae. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of
+the meadow can be colonised by Chlorophyceae.
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-Boat}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Boat_Pred.png}
+
+}
+
+\caption{\label{fig-Boat}RGB orthomosaic (Top) and Prediction (Bottom)
+of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
+The total extent of this flight is about 1.5 km² with a resolution of 80
+mm per pixel. Background colors means intertidal area (Light Green),
+land area (Light Grey) and water (Light Blue). The zoom covers an area
+equivalent to a 10-meter Sentinel-2 pixel size.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The flight over L'Epine in Noirmoutier Island, France
+(Figure~\ref{fig-Dike}) was conducted near a dike crossing the northern
+part of the flight from west to east. Alongside this dike, brown algae
+attached to rocks and stranded green algae could be found. Despite the
+high mixture between Chlorophyceae and Magnoliopsida in this flight,
+these two classes are well discriminated by the classifier.
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-Dike}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Dike_Pred.png}
+
+}
+
+\caption{\label{fig-Dike}RGB orthomosaic (Top) and Prediction (Bottom)
+of Northern part of Noirmoutier Island, France. The total extent of this
+flight is about 28 000 m² with a resolution of 80 mm per pixel.
+Background colors means intertidal area (Light Green) and land area
+(Light Grey). The zoom covers an area equivalent to a 10-meter
+Sentinel-2 pixel size.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\subsection{Validation}\label{validation-1}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-Validation}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGlobal.png}
+
+}
+
+\caption{\label{fig-Validation}A global confusion matrix on the left is
+derived from validation data across each flight, while a mosaic of
+confusion matrices from individual flights is presented on the right.
+The labels inside the matrices indicate the balanced accuracy for each
+class. The labels at the bottom of the matrices indicate the User's
+accuracy for each class, and those on the right indicate the Producer's
+Accuracy. The values adjacent to the names of each site represent the
+proportion of total pixels from that site contributing to the overall
+matrix. Grey lines within the mosaic indicate the absence of validation
+data for the class at that site. The table at the bottom summarizes the
+Sensitivity, Specificity, and Accuracy for each class and for the
+overall model.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+A total amount of 536,000 pixels have been used to validate the Neural
+Network classifier. The site with the least amount of validation data is
+Kerdrean with a total of 5557 pixels whereas Marinha Lanzarote is the
+site with the most amount of validation data with 159713 pixels. The
+global accuracy of the model is 94.26\% and a Kappa coefficient of 0.92
+(Figure~\ref{fig-Validation}). The least performing site is Gafanha High
+with an accuracy of 75.45\% whereas Mataducos is the site with most
+accurate prediction, with a global accuracy of 98.05\%. Overall
+Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae are well
+classified with a balanced accuracy of 1, 0.96, 0.96 and 0.91
+respectively. Bacillariophyceae is the least performing class with an
+accuracy of 0.72 mainly due to a confusion with Magnoliopsida and
+Sediment.
+
+\subsection{Variable importance}\label{variable-importance}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-VIP}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{Figures/VIP/Fig_VIP.png}
+
+}
+
+\caption{\label{fig-VIP}Variable Importance of the Neural Network
+Classifier for each vegetation class. The bigger the slice, the more
+important is the variable to predict accuratly this class. The bottom
+right plot shows the drone standardised reflectance spectra of each
+class.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+The computation of the importance variable of each class indicate which
+wavelength is mandatory to accurately predict the class
+(Figure~\ref{fig-VIP}). Bands at 444 nm, 717 nm and 842 nm of the
+Micasense camera are important for none of the vegetation classes. The
+band at 531 nm is the only important predictor for the classifier to
+accuratly predict chlorophyceae. In fact, at this wavelength, the
+Chlorophyceae spectra has the maximum reflectance value of all the
+classes. 531 nm and 740 nm are the most important predictors to predict
+Phaeophyceae, corresponding to the minimum reflectance value among all
+the classes. Bands at 475 and 560 nm are the most important predictors
+for Bacillariophyceae and Rhodophyceae, respectively. 4 predictors,
+ranging from the Green (560 nm) to the RedEdge (705 nm) are important to
+predict accurately magnoliopsida.
+
+\subsection{Effect of the flight height on the
+prediction}\label{effect-of-the-flight-height-on-the-prediction}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-upscaling}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Upscaling/density_vs_Proportion.png}
+
+}
+
+\caption{\label{fig-upscaling}Kernel density plot showing the proportion
+of pixel well classified based on the percent cover of the class in high
+altitude flight pixels of Gafanha, Portugal. Each subplot shows all the
+pixels of the same classes on the hight altitude flight. Percent cover
+of classes is retrieve using the result of the classification of the low
+altitude flight of Gafanha, Portugal. The vertical dashed line shows the
+0.85 probability of the model. Everything on the right of this line has
+a probability higher then 0.85 and everuthing on the left of this line
+has a probability lower.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+Figure~\ref{fig-upscaling} is showing the percent cover of a class
+required to classify correctly the high altitude flight. When the
+percent cover of the class is 100 \%, big pixels are well classified for
+all the classes excepted for Bare Sediment, where it's well classified
+80\% of the time. A vegetative percent cover of at least 80\% is need to
+have all the big pixels well classified, at the exception of
+Magnoliopsida that needs an higher percent cover (\textgreater90 \%) to
+be well classified. Concerning the probability of each class, a really
+high Percent cover is needed to confidently predict Bacillariophyceae.
+To predict Chlorophyceae with a confidence of 0.85, a percent cover of
+93 \% is needed, 90 \% for magnoliopsida, 92 \% for Rhodophyceae and 97
+\% for Bacillariophyceae.
+
+\section{Discussion}\label{discussion}
+
+\subsection{Seagrass Discrimination}\label{seagrass-discrimination}
+
+\subsection{Spatial and Spectral Resolution impact on the
+prediction}\label{spatial-and-spectral-resolution-impact-on-the-prediction}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-Pigm}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Disc_Pigment_Table.png}
+
+}
+
+\caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
+(Green) or absent (Red) in each taxonomic class present in the Neural
+Network Classifier, along with their absorption wavelength measured with
+spectroradiometer. Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco:
+fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino:
+diadinoxanthin, Neo: neoxanthin.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\phantomsection\label{cell-fig-CompareRef}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Compare_reflectance.png}
+
+}
+
+\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
+both low-altitude and high-altitude flights over a common area. The red
+dashed line represents a 1 to 1 relationship.}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
+Notebook}}
+
+\subsection{Big picture}\label{big-picture}
+
+\section{Conclusion}\label{conclusion}
+
+\renewcommand\refname{Bibliography}
   \bibliography{library.bib}

### 2024-02-27 _manuscript/index.qmd
add all big files

--- 2024-02-27 index.qmd
@@
 abstract: |
-  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing.
-Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN).
-...
+  Coastal areas host seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration.
+However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation.
+In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the use of satellite data within monitoring programs.
+Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
+To address these challenges, drone images acquired with multi-spectral sensors offer a promising solution.
+This study focuses on using drones acquisitions for mapping intertidal macrophytes, effectively discriminating between seagrass and green macroalgae.
+Ten drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal.
+Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among 5 intertidal vegetation classes.
+Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
+The model exhibited an accuracy of 96.4% in identifying seagrass.
 plain-language-summary: |
-  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
+  This study demonstrates the efficacy of using drones equipped with multi-spectral sensors for mapping intertidal macrophytes, particularly seagrass, overcoming limitations of traditional in situ surveys and satellite remote sensing, with a Deep Learning classifier achieving 94% overall accuracy across diverse European habitats, and 96.4% accuracy specifically in identifying seagrass.
+
 key-points:
-  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
-  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
+  - An intertidal vegetation classifier has been built to be used across different study sites without losing classification accuracy. 
+  - Neural Network made to accuratly discriminates intertidal seagrasses from green algae (chlorophyceae)
 date: last-modified
@@
 #| warning: false
-#| fig-cap: !expr "Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
-Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin."
+#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
+Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin.')"
 #| label: fig-Pigm

### 2024-02-27 index.qmd
push all

@@
 abstract: |
-  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing.
-Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN).
-...
+  Coastal areas host seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration.
+However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation.
+In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the use of satellite data within monitoring programs.
+Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
+To address these challenges, drone images acquired with multi-spectral sensors offer a promising solution.
+This study focuses on using drones acquisitions for mapping intertidal macrophytes, effectively discriminating between seagrass and green macroalgae.
+Ten drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal.
+Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among 5 intertidal vegetation classes.
+Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
+The model exhibited an accuracy of 96.4% in identifying seagrass.
 plain-language-summary: |
-  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
+  This study demonstrates the efficacy of using drones equipped with multi-spectral sensors for mapping intertidal macrophytes, particularly seagrass, overcoming limitations of traditional in situ surveys and satellite remote sensing, with a Deep Learning classifier achieving 94% overall accuracy across diverse European habitats, and 96.4% accuracy specifically in identifying seagrass.
+
 key-points:
-  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
-  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
+  - An intertidal vegetation classifier has been built to be used across different study sites without losing classification accuracy. 
+  - Neural Network made to accuratly discriminates intertidal seagrasses from green algae (chlorophyceae)
 date: last-modified
-citation:
-  container-title: Earth and Space Science
 number-sections: true

### 2024-02-27 _manuscript/index.qmd
try to push all

@@
   This study demonstrates the efficacy of using drones equipped with multi-spectral sensors for mapping intertidal macrophytes, particularly seagrass, overcoming limitations of traditional in situ surveys and satellite remote sensing, with a Deep Learning classifier achieving 94% overall accuracy across diverse European habitats, and 96.4% accuracy specifically in identifying seagrass.
-
 key-points:
@@
 date: last-modified
-citation:
-  container-title: Earth and Space Science
 number-sections: true

### 2024-02-27 index.qmd
add all

@@
 
-```{r}
+```{r my_comma}
 #| cache: false
@@
 
-```{r}
+```{r df_training}
 #| cache: true
@@
 
-```{r}
+```{r count_validation_pixel}
 #| echo: false

### 2024-02-28 docs/_tex/index.tex
word and pdf included

--- 2024-02-27 _manuscript/_tex/index.tex
@@
 
-\affiliation[1]{organization={Nantes University},,postcodesep={}}
-\affiliation[2]{organization={Aveiro University},,postcodesep={}}
-\affiliation[3]{organization={CNR ISMAR},,postcodesep={}}
-\affiliation[4]{organization={JeSaisPas},,postcodesep={}}
+\affiliation[1]{organization={Institut des Substances et Organismes de
+la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes,
+France},,postcodesep={}}
+\affiliation[2]{organization={CESAM -- Centre for Environmental and
+Marine Studies, Department of Biology, University of Aveiro, Aveiro,
+Portugal},,postcodesep={}}
+\affiliation[3]{organization={Consiglio Nazionale delle Ricerche,
+Istituto di Scienze Marine (CNR-ISMAR), 00133 Rome,
+Italy},,postcodesep={}}
+\affiliation[4]{organization={BRGM French Geological Survey, Cayenne
+97300, French Guiana},,postcodesep={}}
 
@@
 \end{frontmatter}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \phantomsection\label{cell-fig-map}
@@
 
-\includegraphics[width=26.67in,height=\textheight]{./Figures/Fig1_Map_Drone_Sites.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Fig1_Map_Drone_Sites.png}
 
@@
 \end{figure}%
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \subsection{Field sampling}\label{field-sampling}
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \phantomsection\label{cell-fig-vegetation}
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \subsection{Intertidal vegetation
 mapping}\label{intertidal-vegetation-mapping}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 The spectral similarities of reflectance signatures between intertidal
@@
 building}\label{neural-network-model-building}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 A dataset containing photo-interpreted drone reflectance pixels was
@@
 spectral bands standardized using a min/max transformation
-(Equation~\ref{eq-std} ; \citep{cao2017}) and the NDVI
+(Equation~\ref{eq-std} ; \citep{Cao2017}) and the NDVI
 (Equation~\ref{eq-ndvi}). Standardisation of spectral bands is used to
@@
 \subsubsection{Validation}\label{validation}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \phantomsection\label{cell-fig-GafLow}
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 The high-altitude flight over Gafanha covered nearly 1 km² in total
@@
 classified either as Magnoliopsida or as Phaeophyceae.
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 The High altitude flight made in the inner lagoon of the Ria de Aveiro
@@
 the meadow can be colonised by Chlorophyceae.
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 The flight over L'Epine in Noirmoutier Island, France
@@
 these two classes are well discriminated by the classifier.
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \subsection{Validation}\label{validation-1}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 A total amount of 536,000 pixels have been used to validate the Neural
@@
 \subsection{Variable importance}\label{variable-importance}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 The computation of the importance variable of each class indicate which
@@
 prediction}\label{effect-of-the-flight-height-on-the-prediction}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
 
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 Figure~\ref{fig-upscaling} is showing the percent cover of a class
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \phantomsection\label{cell-fig-Pigm}
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \phantomsection\label{cell-fig-CompareRef}
@@
 
-\textsubscript{Source:
-\href{https://SigOiry.github.io/Drone_Paper_2023/index.qmd.html}{Article
-Notebook}}
-
 \subsection{Big picture}\label{big-picture}

### 2024-02-28 docs/index.qmd
word and pdf included

--- 2024-02-27 index.qmd
@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Bede Ffinian Rowe Davies
@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Pierre Gernez
@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Ana I. Sousa
@@
     affiliations:
-      - Aveiro University
+      - CESAM – Centre for Environmental and Marine Studies, Department of Biology, University of Aveiro, Aveiro, Portugal
   - name: Philippe Rosa
@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Maria Laura Zoffoli
@@
     affiliations:
-      - CNR ISMAR
+      - Consiglio Nazionale delle Ricerche, Istituto di Scienze Marine (CNR-ISMAR), 00133 Rome, Italy
   - name: Guillaume Brunier
@@
     affiliations:
-      - JeSaisPas
+      - BRGM French Geological Survey, Cayenne 97300, French Guiana
   - name: Laurent Barillé
@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
 keywords:
@@
 date: last-modified
+citation:
+  container-title: Earth and Space Science
 number-sections: true
+notebook-links: false
 ---
@@
 #| label: fig-map
-#| fig-width: 9
-#| fig-height: 9
+#| fig-width: 7
+#| fig-height: 7
+#| out-width: "100%"
 
@@
 More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights have been used to train the model (Table 2).
-Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @cao2017) and the NDVI (@eq-ndvi).
+Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the NDVI (@eq-ndvi).
 Standardisation of spectral bands is used to eliminate the scaling differences between spectra and to limit the effect of biomass on the shape of the spectra [@Douay2022 ; @Davies2023].

### 2024-02-28 docs/_tex/index.tex
part of the discuss

@@
   pdftitle={Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
-  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Pierre Gernez; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Laurent Barillé},
+  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
   pdfkeywords={Drone, Remote Sensing},
@@
 
-\author[1]{Pierre Gernez%
-%
-}
-
 \author[2]{Ana I. Sousa%
@@
 \author[4]{Guillaume Brunier%
+%
+}
+
+\author[1]{Pierre Gernez%
 %
@@
 to analyze the potential of a drone equipped with a multispectral sensor
-for maping intertidal macrophytes, with a particular focus on
+for mapping intertidal macrophytes, with a particular focus on
 discriminating Magnoliopsida and Chlorophyceae. Ten drone flights were
@@
 
-\subsection{Seagrass Discrimination}\label{seagrass-discrimination}
+The primary objective of this study was to develop a method for the
+accurate classification of macrophytes on intertidal mudflats,
+specifically focusing on distinguishing between Chlorophyceae (green
+algae) and marine Magnoliopsida (seagrasses) using multispectral drone
+data. The challenge arises from the shared pigment composition between
+these two vegetation classes, complicating their differentiation using
+remote sensing techniques. This challenge has been addressed through the
+utilization of high-resolution drone flights allowing a precise
+photointerpretation of pure pixels of the different vegetation classes
+used as training data, providing a robust foundation for subsequent
+classification analyses. In achieving 94.26 accuracy across all study
+sites, this method demonstrates its efficacy in accurately classifying
+macrophytes, thus offering a reliable approach for vegetation
+classification in intertidal mudflats using remote sensing data.
 
-\subsection{Spatial and Spectral Resolution impact on the
-prediction}\label{spatial-and-spectral-resolution-impact-on-the-prediction}
+\subsection{Green Macrophytes
+Discrimination}\label{green-macrophytes-discrimination}
 
@@
 \end{figure}%
+
+The discrimination of seagrasses from green macroalgae presents
+significant challenges, primarily due to the shared pigment composition
+between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
+frequent spatial mixing of these green macrophytes. This similarity in
+pigment composition, including photosynthetic and carotenoid pigments
+like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
+spectral signatures that are often indistinguishable to non expererences
+This spectral overlap is further complicated by the intermingling of
+seagrasses and green macroalgae in the same spatial locations, posing a
+significant challenge for remote sensing aimed at accurately mapping and
+monitoring coastal ecosystems. Our study addresses these complexities by
+utilizing high-resolution drone imagery with 10 spectral bands.
+\citep{Davies2023} has shown that having at least 8 spectral bands
+ranging between 500 nm to 850 nm with on band at 530 nm and another one
+at 730 nm is crucial to accurately discriminate green macrophytes.
+
+\phantomsection\label{cell-fig-ValidationGreen}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGreen.png}
+
+}
+
+\caption{\label{fig-ValidationGreen}Sample of
+Figure~\ref{fig-Validation} focusing on green macrophytes. The labels
+inside the matrice indicate the number of pixels.}
+
+\end{figure}%
+
+The Micasense RedEdge-MX DUAL camera used in this study meets these two
+criteria, enabling the classifier to achieve 97\% of accuracy between
+these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
+pigment compostion of green macrophytes is similar, differences in the
+spectral shape can still be observed (Figure~\ref{fig-vegetation}).
+Several factors can explain these differences such has different pigment
+concentration en proportion, different cellular organisation and 3D
+disposition of the plant a whole on the intertidal mudflat
+\citep[\citep{kirk1994light},
+\citep{hedley2018influence}]{beach1997vivo}.
+
+The VIP analysis of the Neural Network model (see Fig. VIP) shows that
+the 531 nm band is the most important spectral band for accurately
+identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae
+exhibits the highest reflectance among all other classes, highlighting
+the difference in carotenoid proportion between seagrasses and green
+algae.
+
+\subsection{Spectral and Temporal Resolution impact on the
+prediction}\label{spectral-and-temporal-resolution-impact-on-the-prediction}
 

### 2024-02-28 docs/index.qmd
part of the discuss

@@
   - name: Bede Ffinian Rowe Davies
-    corresponding: false
-    roles: 
-      - Investigation
-      - Data acquisition
-      - Revision
-    affiliations:
-      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
-  - name: Pierre Gernez
     corresponding: false
@@
       - BRGM French Geological Survey, Cayenne 97300, French Guiana
+  - name: Pierre Gernez
+    corresponding: false
+    roles: 
+      - Investigation
+      - Data acquisition
+      - Revision
+    affiliations:
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Laurent Barillé
@@
 notebook-links: false
+editor_options: 
+  chunk_output_type: console
+csl: RSE.csl
 ---
@@
 However, when applied to coastal habitat mapping, many studies showcase their findings with study case limited to a single flight, restricting the generalizability of their application to other sites [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-This study aimed to analyze the potential of a drone equipped with a multispectral sensor for maping intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
+This study aimed to analyze the potential of a drone equipped with a multispectral sensor for mapping intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae.
@@
 
+######### Focus on green macrophytes
+df_green<-df %>% 
+  filter(Pred_Class %in% c("Magnoliopsida", "Chlorophyceae"),
+         Truth %in% c("Magnoliopsida", "Chlorophyceae")) %>% 
+  mutate(Pred_Class = as.factor(as.character(Pred_Class)),
+         Truth = as.factor(as.character(Truth)))
+
+validation_metrics_green<-confusionMatrix(df_green$Pred_Class,df_green$Truth)
+
+conf_mat_green<-validation_metrics_green[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 2) %>%
+  as.data.frame()
+
+for(i in 1:(nrow(conf_mat_green))){
+  if(i == 1 ){
+    df_sum<-data.frame(row = NA,
+                       col = NA)
+  }
+  df_sum[i,1] <- sum(conf_mat_green[i,],na.rm = T)
+  df_sum[i,2] <- sum(conf_mat_green[,i],na.rm = T)
+}
+conf_mat_std_green<-conf_mat_green
+
+for(row in 1:nrow(conf_mat_std_green)){
+  for(col in 1:ncol(conf_mat_std_green)){
+    conf_mat_std_green[row,col]<-conf_mat_std_green[row,col]/((df_sum$row[row] + df_sum$col[col])-conf_mat_std_green[row,col])
+    }
+}
+
+confmat_rast_green<-conf_mat_std_green %>% 
+  as.matrix() %>% 
+  as.array() %>% 
+  rast()
+
+confmat_rast_green<-subst(confmat_rast_green, NA, -99)
+names(confmat_rast_green)<-"layer"
+ext(confmat_rast_green)<-c(0,2,0,2)
+confmat_rast_green_sf<-as.polygons(confmat_rast_green,aggregate=F) %>% 
+  sf::st_as_sf()
+confmat_rast_green_centroid<-st_centroid(confmat_rast_green_sf)
+
+values(confmat_rast_green)[values(confmat_rast_green) == 0] = NA
+values(confmat_rast_green)[values(confmat_rast_green) == -99] = NA
+
+labels_green<-validation_metrics_green[[2]] %>% 
+  as.numeric() %>%
+  base::matrix(ncol = 1) %>%
+  as.data.frame() %>% 
+  rename(label = "V1") %>% 
+  mutate(x = c(0.5,0.5,1.5,1.5),
+         y = c(1.5,0.5,1.5,0.5))
+
+plot_green<-ggplot()+
+geom_spatraster(data = confmat_rast_green,
+                  na.rm = TRUE
+                  )+
+  geom_sf(data = confmat_rast_green_sf,
+          fill = "transparent")+
+  scale_fill_gradientn(
+    # colours = c("black","firebrick4","goldenrod","yellow","chartreuse3"),
+    # colours = c("khaki1","goldenrod","firebrick3","chartreuse4"),
+    colours = c("khaki1","firebrick4","firebrick4","firebrick4","#3e0b0b"),
+    # colours = c("#7d0000","#00b300","#00b300","#00b300","#007d00"),
+    na.value = "white", 
+    trans = "sqrt",
+    limits = c(0,1),
+    labels = c("0.05","0.25", "0.50", "1"),
+    breaks = c(0.05,0.25,0.50,1))+
+  # scale_fill_Bede("mixed", 
+  #                 discrete = F,
+  #                 reverse = TRUE,
+  #                 na.value = "white",
+  #                 trans = "sqrt",
+  #                 labels = c("5","25", "50", "75", "100"),
+  #                 breaks = c(0.05,0.25,0.50,0.75,0.9999))+
+  labs(fill = "Proportion \n of pixels")+
+  scale_x_continuous(breaks = seq(0.5,1.5, by = 1),
+                     labels = c("Chlorophyceae","Magnoliopsida"),
+                     expand = c(0, 0),
+                     position = "top",
+                     limits = c(0,2))+
+  scale_y_continuous(breaks = seq(0.5,1.5, by = 1),
+                     labels = c("Magnoliopsida","Chlorophyceae"),
+                     expand = c(0, 0),
+                     limits = c(0,2))+
+  geom_label(data = labels_green,aes(x = x, y = y, label = label ))+
+  xlab("References")+
+  ylab("Prediction")+
+  # ggplot2::annotation_custom(ggplotGrob(small_validation_matrices), xmin = 12, ymin = 0)+
+  theme_Bede()+
+  theme( 
+        panel.border = element_blank(),
+        axis.line=element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20, angle =90, hjust = 0.5),
+
+        # legend.position = "top",
+        # legend.position = c(0.73, 0.9),
+        # legend.direction="horizontal",
+        # legend.key.width = unit(2,"cm"),
+        legend.text = element_text(size = 20),
+        legend.title = element_text(size = 20, vjust = 2),
+        legend.title.align = 0.5,
+        legend.justification = "center")
+
+ggsave("./Figures/Validation/ConfusionMatrixGreen.png", plot_green, width = 671*4, height = 479*4, units = "px" )
+
 ```
@@
 
-## Seagrass Discrimination
-
-## Spatial and Spectral Resolution impact on the prediction
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The challenge arises from the shared pigment composition between these two vegetation classes, complicating their differentiation using remote sensing techniques.
+This challenge has been addressed through the utilization of high-resolution drone flights allowing a precise photointerpretation of pure pixels of the different vegetation classes used as training data, providing a robust foundation for subsequent classification analyses.
+In achieving `r round(validation_metrics$overall[[1]]*100,2)` accuracy across all study sites, this method demonstrates its efficacy in accurately classifying macrophytes, thus offering a reliable approach for vegetation classification in intertidal mudflats using remote sensing data.
+
+## Green Macrophytes Discrimination
 
@@
 
+The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
+This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non expererences This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
+Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands.
+@Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with on band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
+
+::::: columns
+::: column
+```{r Global Accuracy assesment Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Sample of @fig-Validation focusing on green macrophytes. The labels inside the matrice indicate the number of pixels.
+#| label: fig-ValidationGreen
+#| fig-width: 10
+#| fig-height: 10
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Validation/ConfusionMatrixGreen.png")
+
+```
+:::
+
+::: column
+The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
+Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
+Several factors can explain these differences such has different pigment concentration en proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
+:::
+:::::
+
+The VIP analysis of the Neural Network model (see Fig.
+VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
+In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in carotenoid proportion between seagrasses and green algae.
+
+## Spectral and Temporal Resolution impact on the prediction
+
 ```{r Reflectance_Validation 2 height}

### 2024-03-01 index.qmd
add all

@@
     affiliations:
-      - Nantes University
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
+  - name: Ana I. Sousa
+    corresponding: false
+    roles:
+      - Data acquisition
+      - Revision
+    affiliations:
+      - CESAM – Centre for Environmental and Marine Studies, Department of Biology, University of Aveiro, Aveiro, Portugal
+  - name: Philippe Rosa
+    corresponding: false
+    roles: 
+      - Data acquisition
+      - Revision
+    affiliations:
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
+  - name: Maria Laura Zoffoli
+    corresponding: false
+    roles: 
+      - Data acquisition
+      - Revision
+    affiliations:
+      - Consiglio Nazionale delle Ricerche, Istituto di Scienze Marine (CNR-ISMAR), 00133 Rome, Italy
+  - name: Guillaume Brunier
+    corresponding: false
+    roles: 
+      - Data acquisition
+      - Revision
+    affiliations:
+      - BRGM French Geological Survey, Cayenne 97300, French Guiana
   - name: Pierre Gernez
@@
     affiliations:
-      - Nantes University
-  - name: Ana I. Sousa
-    corresponding: false
-    roles:
-      - Data acquisition
-      - Revision
-    affiliations:
-      - Aveiro University
-  - name: Philippe Rosa
-    corresponding: false
-    roles: 
-      - Data acquisition
-      - Revision
-    affiliations:
-      - Nantes University
-  - name: Maria Laura Zoffoli
-    corresponding: false
-    roles: 
-      - Data acquisition
-      - Revision
-    affiliations:
-      - CNR ISMAR
-  - name: Guillaume Brunier
-    corresponding: false
-    roles: 
-      - Data acquisition
-      - Revision
-    affiliations:
-      - JeSaisPas
+      - Institut des Substances et Organismes de la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes, France
   - name: Laurent Barillé
@@
 date: last-modified
+citation:
+  container-title: Earth and Space Science
 number-sections: true
+notebook-links: false
+editor_options: 
+  chunk_output_type: console
+csl: RSE.csl
 ---
@@
 Coastal areas are vital hotshots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
-These meadows offer a myriad of ecosystem services to humanity, including limitation of coastline erosion, reducing the risk of eutrophication, carbon sequestration, and oxygen production.
+Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production,protection against sea-level rise and coastline erosion, and limitation of eutrophication.
 They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019].
-Due to their proximity to human activities, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation are currently observed due to diseases, disasters, coastal urbanization, sea reclamation, as well as fishing activities, dredging, sea level rise, coastal erosion, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019].
-While improvements in water quality have been recently reported in European sites, allowing an overall recovery of seagrass ecosystems at the local scale, many other coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides.
-Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@Duarte2002 ; @wang2022].
-
-The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of global and regional monitoring programs for systematically surveying different Essential Oceanic Variable [@Miloslavich2018] as seagrass coverage and composition; as well as Essential Biodiversity Variable [@Pereira2013] such as seagrass taxonomic diversity; species distribution, population abundance, and phenology.
-Monitoring programs also prioritize the identification of threats to these ecosystems, particularly during early stages, to facilitate effective mitigation actions.
-Traditionally, these ecological parameters have been quantified through in situ measurements, although this approach faces several constraints over intertidal zones.
-Intertidal meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
-However, satellite data have been proven effective in complenmenting in situ surveys, allowing for the rapid and consitent retrieval of EOV's over extensive seagrass meadows.
+Due to the concentration of human activities in coastal zones, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
+Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019].
+While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
+Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides (@devlin2023nutrients ; @devlin2023nutrients).
+Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
+
+The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, populuation abundance, and phenology [@Pereira2013].
+Seagrass monitoring is all the more important as it makes possible to identify which pressure should be addressed in priority to facilitate effective mitigation actions.
+Traditionally, indicators of seagrass status have been quantified using in situ measurements.
+The acquisition of field data in intertidal zones is however notoriously challenging.
+Intertidal seagrass meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
+Satellite observations have been proven effective in complementing in situ sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
 [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023]
 
-Satellite remote sensing offers the advantage of acquiring large-scale data in real-time but presents its inherent challenges.
-Free access satellite data (e.g., Sentinel-2 and Landsat8/9) provide relatively low spatial resolution data (10 - 30 m) across a limited number of spectral bands.
-These characteristics can be a limitation to accurately discriminating seagrass from others co-existing macrophytes over the meadow.
-Chlorophyceae (Green Algae) and marine Magnoliopsida (Seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
+While satellite remote sensing provides temporally consistent observations over large spatial scales, it is limited by several constraints.
+Satellite missions with a high temporal resolution (e.g.
+daily MODIS observation) are limited by a coarse spatial resolution (\>100m).
+Mission with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
+The limited number of spectral bands is indeed a challenge to accurately discriminate seagrass from others co-existing macrophytes.
+In particular Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
 As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022].
-Recently, using a hyperspectral library, @Davies2023 demonstrated that the spectral resolution of Sentinel-2, might be enough for the discrimination between Magnoliopsida and Chlorophyceae.
-However, green tide events occur at small spatial scales that are not observable using satellite imagery [@tuya2013], especially during the initial stage of the event.
-
-Remote sensing drone acquisitions are presented as a tool that can potentially fill gaps left by satellite and in situ data.
-Drone can cover large expanses while recording imagery at significantly higher spatial resolutions than satellite (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
-The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping the spatial distribution of species [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
-However, when applied to coastal habitat mapping, many studies showcase their findings with study case limited to a single flight, restricting the generalizability of their application to other sites [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-This study aimed to analyze the potential of a drone equipped with a multispectral sensor for maping intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance measurements, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+The application of this approach to satellite remote sensing remains however to be validated.
+Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of the event.
+
+Drone can potentially fill the gaps left by satellite remote sensing and in situ measurments, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
+However, when applied to coastal habitat mapping, most sutdy cases were limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+The present study aimed at analyzing the potential of multispectral drone remote sensing to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae.
-A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of accuracy in predictions.
+A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy
 
@@
 Patchy seagrass meadows can be found on a lot of these islands.
-Within the Gulf of Morbihan we have chosen two sites : One is located in one of these island (Arz island).
-The other one is located in the sourthern part of the Gulf (Duer).
+Within the Gulf of Morbihan we have chosen two sites : one is located in one of these island (Arz island); the other one is located in the sourthern part of the gulf (Duer).
 Two others sites are located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
 This bay is a semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
-With up to 6m in tidal range during spring tide, a 6 km² seagrass meadow can uncover at low tide.
-The sites we surveyed (L'Epine and Barbatre, @fig-map B) are located in the southernmost part of the bay, along the Noirmoutier Island, and host a monospecific *Zostera noltei* seagrass bed with very little mixing with other macrophytes.
-Three sites have been survey in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
+Bougneuf bay hosts a large intertidal seagrass meadow of about 6 km².
+Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contain a monospecific bed of *Zostera noltei* with very little mixing with other macrophytes.
+Three sites have been surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
 The extent of this lagoon is about 80 km² with many narrow channels, large salt marshes and many mudflats that uncovers at low tide.
@@
 The southernmost site (Gafanha) is a mudflat located in an affluent of the lagoon whereas the two other sites are situated in the middle of the lagoon and are only accessible by boat (@fig-map C).
-These Portuguese sites were characterized by a more diverse intertidal area, where the seagrass meadow could intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae), or green algae (Chlorophyceae).
+These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass could intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae), and green algae (Chlorophyceae).
 
@@
 #| fig-cap: >
-#|   Sites where the different drone flights were made.
-A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon.
-Light green represent terrestrial areas whereas darkgreen represent intertidal areas.
+#|   Sites observed by drone. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent terrestrial areas whereas darkgreen represent intertidal areas. 
 #| label: fig-map
-#| fig-width: 9
-#| fig-height: 9
+#| fig-width: 7
+#| fig-height: 7
+#| out-width: "100%"
 
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from blue (444 nm) to near infrared (840 nm).
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
 An angle of 90° has been maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
 A side overlap of 70% and a front overlap of 80% between each image has been set.
-Images have been calibrated in reflectance using a calibration panel reflective at \~50% provided by the camera's manufaturer and a Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance data during the flight.
+for each flight Images have been calibrated in reflectance using a calibration panel reflective at \~50% provided by the camera's manufaturer and a Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance data during the flight.
 A Structure-from-Motion photogrammetry software (Agisoft Metashape) has been used to process images to obtain multispectral orthomosaics of each flight.
@@
 
+The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
+This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non expererences This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
+Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands.
+@Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with on band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
+
+::: columns
+::: column
+```{r Global Accuracy assesment Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Sample of @fig-Validation focusing on green macrophytes. The labels inside the matrice indicate the number of pixels.
+#| label: fig-ValidationGreen
+#| fig-width: 10
+#| fig-height: 10
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Validation/ConfusionMatrixGreen.png")
+
+```
+:::
+
+::: column
+The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
+Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
+Several factors can explain these differences such has different pigment concentration en proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
+:::
+:::
+
+The VIP analysis of the Neural Network model (see Fig.
+VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
+In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).
+
+Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electomagnetic spectra.
+These two key features has been identified by the Neural Network as the two principale predictors to accuratly identify Brown algae (@fig-VIP, )
+
+## Spectral and Temporal Resolution impact on the prediction
+
 ```{r Reflectance_Validation 2 height}

### 2024-03-01 docs/_tex/index.tex
Pierre comments

@@
 intertidal seagrass meadows playing a crucial role at the interface
-between land and ocean \citep{unsworth2022}. These meadows offer a
-myriad of ecosystem services to humanity, including limitation of
-coastline erosion, reducing the risk of eutrophication, carbon
-sequestration, and oxygen production. They serve as vital habitats for a
-diverse array of marine and terrestrial species, providing living,
-breeding, and feeding grounds \citetext{\citealp[
+between land and ocean \citep{unsworth2022}. Seagrass meadows provide a
+myriad of ecosystem services to humanity, including carbon
+sequestration, oxygen production,protection against sea-level rise and
+coastline erosion, and limitation of eutrophication. They serve as vital
+habitats for a diverse array of marine and terrestrial species,
+providing living, breeding, and feeding grounds \citetext{\citealp[
 ]{gardner2018}; \citealp[ ]{Zoffoli2022}; \citealp{jankowska2019}}. Due
-to their proximity to human activities, seagrass meadows are directly
-exposed to and impacted by anthropogenic pressures. Global regression
-and fragmentation are currently observed due to diseases, disasters,
-coastal urbanization, sea reclamation, as well as fishing activities,
-dredging, sea level rise, coastal erosion, competition with alien
-species, and reduction in water quality \citetext{\citealp[
-]{nguyen2021}; \citealp[ ]{soissons2018}; \citealp[
+to the concentration of human activities in coastal zones, seagrass
+meadows are directly exposed to and impacted by anthropogenic pressures.
+Global regression and fragmentation are currently observed due to
+climate change, diseases, urbanization, land reclamation, dredging,
+competition with alien species, and reduction in water quality
+\citetext{\citealp[ ]{nguyen2021}; \citealp[ ]{soissons2018}; \citealp[
 ]{orth2006}; \citealp[ ]{lin2018}; \citealp{duffy2019}}. While
-improvements in water quality have been recently reported in European
-sites, allowing an overall recovery of seagrass ecosystems at the local
-scale, many other coastal waters worldwide are still subjected to strong
-eutrophication processes \citetext{\citealp[
-]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal eutrophication has been
-associated to anomalous accumulation of green macroalgae, the so-called
-green tides. Green tides produce shade and suffication over seagrass
-individuals, thus threatening the health of seagrass ecosystems
-\citetext{\citealp[ ]{Duarte2002}; \citealp{wang2022}}.
+improvements in water quality have been recently reported in Europe,
+allowing an overall recovery of seagrass ecosystems at local scale, many
+coastal waters worldwide are still subjected to strong eutrophication
+processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
+Coastal eutrophication has been associated to anomalous accumulation of
+green macroalgae, the so-called green tides (\citep{devlin2023nutrients}
+; \citep{devlin2023nutrients}). Green tides produce shade and
+suffication over seagrass individuals, thus threatening the health of
+seagrass ecosystems \citep{wang2022}.
 
 The importance of seagrass meadows and the variety of ecosystem services
-they provide have led to the enhancement of global and regional
-monitoring programs for systematically surveying different Essential
-Oceanic Variable \citep{Miloslavich2018} as seagrass coverage and
-composition; as well as Essential Biodiversity Variable
-\citep{Pereira2013} such as seagrass taxonomic diversity; species
-distribution, population abundance, and phenology. Monitoring programs
-also prioritize the identification of threats to these ecosystems,
-particularly during early stages, to facilitate effective mitigation
-actions. Traditionally, these ecological parameters have been quantified
-through in situ measurements, although this approach faces several
-constraints over intertidal zones. Intertidal meadows are only partially
-exposed during low tide and can be situated in difficult-to-reach
-mudflats, potentially leading to inaccurate and limited estimations with
-conventional sampling techniques \citep{nijland2019}. However, satellite
-data have been proven effective in complenmenting in situ surveys,
-allowing for the rapid and consitent retrieval of EOV's over extensive
-seagrass meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
+they provide have led to the enhancement of both global and regional
+programs monitoring Essential Oceanic Variable (EOVs) such as seagrass
+composition \citep{Miloslavich2018}, as well as Essential Biodiversity
+Variable (EBVs) such as seagrass taxonomic diversity, species
+distribution, populuation abundance, and phenology \citep{Pereira2013}.
+Seagrass monitoring is all the more important as it makes possible to
+identify which pressure should be addressed in priority to facilitate
+effective mitigation actions. Traditionally, indicators of seagrass
+status have been quantified using in situ measurements. The acquisition
+of field data in intertidal zones is however notoriously challenging.
+Intertidal seagrass meadows are only partially exposed during low tide
+and can be situated in difficult-to-reach mudflats, potentially leading
+to inaccurate and limited estimations with conventional sampling
+techniques \citep{nijland2019}. Satellite observations have been proven
+effective in complementing in situ sampling, allowing for the near
+real-time and consistent retrieval of seagrass EOVs and EBVs over
+extensive meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
 ]{xu2021}; \citealp[ ]{Traganos2018}; \citealp{coffer2023}}
 
-Satellite remote sensing offers the advantage of acquiring large-scale
-data in real-time but presents its inherent challenges. Free access
-satellite data (e.g., Sentinel-2 and Landsat8/9) provide relatively low
-spatial resolution data (10 - 30 m) across a limited number of spectral
-bands. These characteristics can be a limitation to accurately
-discriminating seagrass from others co-existing macrophytes over the
-meadow. Chlorophyceae (Green Algae) and marine Magnoliopsida (Seagrass)
-share the same pigment composition \citetext{\citealp[
-]{ralph2002}; \citealp{Douay2022}}. As a result, their respective
-spectral signatures can be considered similar by a non-expert observer
-\citetext{\citealp[ ]{Davies2023}; \citealp{bannari2022}}. Recently,
-using a hyperspectral library, \citep{Davies2023} demonstrated that the
-spectral resolution of Sentinel-2, might be enough for the
-discrimination between Magnoliopsida and Chlorophyceae. However, green
-tide events occur at small spatial scales that are not observable using
-satellite imagery \citep{tuya2013}, especially during the initial stage
-of the event.
+While satellite remote sensing provides temporally consistent
+observations over large spatial scales, it is limited by several
+constraints. Satellite missions with a high temporal resolution
+(e.g.~daily MODIS observation) are limited by a coarse spatial
+resolution (\textgreater100m). Mission with a high spatial resolution
+such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low
+spectral resolution. The limited number of spectral bands is indeed a
+challenge to accurately discriminate seagrass from others co-existing
+macrophytes. In particular Chlorophyceae (green algae) and marine
+Magnoliopsida (seagrass) share the same pigment composition
+\citetext{\citealp[ ]{ralph2002}; \citealp{Douay2022}}. As a result,
+their respective spectral signatures can be considered similar by a
+non-expert observer \citetext{\citealp[
+]{Davies2023}; \citealp{bannari2022}}. Recently, using advanced
+machine-learning algorithms trained with a large hyperspectral library
+of more then 300 field reflectance measurements, \citep{Davies2023}
+demonstrated that it was possible to discriminate Magnoliopsida from
+Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral
+resolution. The application of this approach to satellite remote sensing
+remains however to be validated. Moreover patches of green algae can
+develop at small spatial scales that are not observable using
+non-commercial satellite imagery \citep{tuya2013}, especially during the
+initial stage of the event.
 
-Remote sensing drone acquisitions are presented as a tool that can
-potentially fill gaps left by satellite and in situ data. Drone can
-cover large expanses while recording imagery at significantly higher
-spatial resolutions than satellite (pixel size from cm to mm) and still
-capturing data at multi-spectral resolution \citetext{\citealp[
-]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
-allows for their application across a diverse thematic range , from
-coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
-]{casella2020}; \citealp{angnuureng2022}} to mapping the spatial
-distribution of species \citetext{\citealp[ ]{joyce2023}; \citealp[
+Drone can potentially fill the gaps left by satellite remote sensing and
+in situ measurments, due to their ability to provide spatially-explicit
+observations at very high spatial resolutions (pixel size from cm to mm)
+and still capturing data at multi-spectral resolution
+\citetext{\citealp[ ]{fairley2022drone}; \citealp{oh2017use}}. The
+versatility of drones allows for their application across a diverse
+thematic range , from coastal zone management \citetext{\citealp[
+]{adade2021}; \citealp[ ]{casella2020}; \citealp{angnuureng2022}} to
+mapping species distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
 ]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[
 ]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
-to coastal habitat mapping, many studies showcase their findings with
-study case limited to a single flight, restricting the generalizability
-of their application to other sites \citetext{\citealp[
-]{Roman2021}; \citealp[ ]{collin2019improving}; \citealp[
-]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. This study aimed
-to analyze the potential of a drone equipped with a multispectral sensor
-for mapping intertidal macrophytes, with a particular focus on
-discriminating Magnoliopsida and Chlorophyceae. Ten drone flights were
-performed over soft-bottom intertidal areas along two European countries
-(France and Portugal), covering a wide range of habitats, from
-monospecific seagrass meadows to meadows mixed with green or red algae.
-A deep learning algorithm was trained and validated for macrophyte
-discrimination, emphasizing applicability across diverse sites without a
-loss of accuracy in predictions.
+to coastal habitat mapping, most sutdy cases were limited to a single
+flight, restricting the generalizability of their application over wider
+geographical scales \citetext{\citealp[ ]{Roman2021}; \citealp[
+]{collin2019improving}; \citealp[
+]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. The present study
+aimed at analyzing the potential of multispectral drone remote sensing
+to map intertidal macrophytes, with a particular focus on discriminating
+Magnoliopsida and Chlorophyceae. Ten drone flights were performed over
+soft-bottom intertidal areas along two European countries (France and
+Portugal), covering a wide range of habitats, from monospecific seagrass
+meadows to meadows mixed with green or red algae. A deep learning
+algorithm was trained and validated for macrophyte discrimination,
+emphasizing applicability across diverse sites without a loss of
+prediction accuracy.
 
@@
 seagrass meadows can be found on a lot of these islands. Within the Gulf
-of Morbihan we have chosen two sites : One is located in one of these
-island (Arz island). The other one is located in the sourthern part of
-the Gulf (Duer). Two others sites are located in Bourgneuf Bay, France
+of Morbihan we have chosen two sites : one is located in one of these
+island (Arz island); the other one is located in the sourthern part of
+the gulf (Duer). Two others sites are located in Bourgneuf Bay, France
 (46.9849°N, 2.1488°W). This bay is a semi-enclosed macrotidal bay,
-protected from waves by Noirmoutier Island. With up to 6m in tidal range
-during spring tide, a 6 km² seagrass meadow can uncover at low tide. The
-sites we surveyed (L'Epine and Barbatre, Figure~\ref{fig-map} B) are
-located in the southernmost part of the bay, along the Noirmoutier
-Island, and host a monospecific \emph{Zostera noltei} seagrass bed with
-very little mixing with other macrophytes. Three sites have been survey
-in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W). The
-extent of this lagoon is about 80 km² with many narrow channels, large
-salt marshes and many mudflats that uncovers at low tide. It is
-connected to the open sea through a single channel, with a tidal lag
-between the North and the South of the lagoon. The southernmost site
-(Gafanha) is a mudflat located in an affluent of the lagoon whereas the
-two other sites are situated in the middle of the lagoon and are only
-accessible by boat (Figure~\ref{fig-map} C). These Portuguese sites were
-characterized by a more diverse intertidal area, where the seagrass
-meadow could intermingle with red algae (Rhodophyceae), brown algae
-(Phaeophyceae), or green algae (Chlorophyceae).
+protected from waves by Noirmoutier Island. Bougneuf bay hosts a large
+intertidal seagrass meadow of about 6 km². Within this meadow, the sites
+observed by drones (L'Epine and Barbatre, Figure~\ref{fig-map} B)
+contain a monospecific bed of \emph{Zostera noltei} with very little
+mixing with other macrophytes. Three sites have been surveyed in the Ria
+de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of this
+lagoon is about 80 km² with many narrow channels, large salt marshes and
+many mudflats that uncovers at low tide. It is connected to the open sea
+through a single channel, with a tidal lag between the North and the
+South of the lagoon. The southernmost site (Gafanha) is a mudflat
+located in an affluent of the lagoon whereas the two other sites are
+situated in the middle of the lagoon and are only accessible by boat
+(Figure~\ref{fig-map} C). These Portuguese sites are characterized by a
+more diverse intertidal vegetation, where patches of seagrass could
+intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae),
+and green algae (Chlorophyceae).
 
@@
 
-\caption{\label{fig-map}Sites where the different drone flights were
-made. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon.
-Light green represent terrestrial areas whereas darkgreen represent
-intertidal areas.}
+\caption{\label{fig-map}Sites observed by drone. A: Gulf of Morbihan, B:
+Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent
+terrestrial areas whereas darkgreen represent intertidal areas.}
 
@@
 Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
-million pixel reflectance photographs in 10 spectral bands, from blue
-(444 nm) to near infrared (840 nm). An angle of 90° has been maintained
+million pixel reflectance photographs in 10 spectral bands, from 444 nm
+(blue) to 840 nm (near infrared, NIR). An angle of 90° was maintained
 between the sun and the drone's route to guarantee uniform lighting
 conditions between flight lines. A side overlap of 70\% and a front
-overlap of 80\% between each image has been set. Images have been
-calibrated in reflectance using a calibration panel reflective at
-\textasciitilde50\% provided by the camera's manufaturer and a
-Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance
-data during the flight. A Structure-from-Motion photogrammetry software
-(Agisoft Metashape) has been used to process images to obtain
-multispectral orthomosaics of each flight. The workflow for
-orthomosaicking has remained consistent for every flight. First, tying
-key points were detected inside of each image and between overlapping
-images in order to obtain a sparse point cloud. This cloud was cleaned
-using reprojection accuracy metric in order to remove noisy points. A
-dense point cloud has been then produced using a structure from motion
-algorithm. A surface interpolation of this dense point cloud has been
-made to obtain a Digital Surface Model (DSM), used to reconstruct the
-multispectral ortho-image. Across all the sites, flights were made at
-two different altitudes : 12 m or/and 120 m. Low altitude drone flights
-produce ortho-images with a very high spatial resolution (8 mm per
-pixel), making it simple to visually distinguish between the various
-types of vegetation. High altitude fights on the other hand allow to
-cover large areas and produced images with a pixel size of 80 mm (Table
-1).
+overlap of 80\% between each imagewas set for each flight. A downwelling
+light sensor (DLS2) was used to acquire irradiance data concomitantly
+with the camera measurements. Raw data were calibrated in reflectance
+using a calibration panel reflective at \textasciitilde50\% provided by
+the manufacturer. A structure-from-motion photogrammetry software
+(Agisoft Metashape) was used to process images to obtain multispectral
+orthomosaics of each flight. The workflow for orthomosaicking was the
+same for every flight. First, tying key points were detected inside of
+each image and between overlapping images in order to obtain a sparse
+point cloud. This cloud was cleaned using reprojection accuracy metric
+in order to remove noisy points. A dense point cloud was then produced
+using a structure from motion algorithm. A surface interpolation of this
+dense point cloud was made to obtain a digital surface model (DSM), used
+to reconstruct the multispectral ortho-image. Across all sites, flights
+were made at two different altitudes : 12 m or/and 120 m. Low altitude
+drone flights produce ortho-images with a very high spatial resolution
+(8 mm per pixel), making it simple to visually distinguish between the
+various types of vegetation. High altitude fights on the other hand
+allow to cover large areas and produced images with a pixel size of 80
+mm (Table 1).
 
@@
 \begin{longtable}[c]{ccccc}
-\caption{List of drone Flight, summarising the date, the altitude and the purpose
+\caption{List of drone flight, summarising the date, the altitude and the purpose
 of each flight.}\tabularnewline
@@
 Before each flight, targets used as Ground Control Points (GCPs) were
-dispersed and georeferenced with a Trimble © Geo XH 6000 differential
-GPS (dGPS). GCPs were used to correct georeferencing imprecision of
-orthomosaics with an horizontal and vertical accuracy of 10cm. dGPS was
-also used to georeference quardrats of 0.25cm² used to assess the
-presence or absence of 5 key classes of vegetation : Bacillariophyceae
-(Diatoms forming large biofilm over the sediment during low tide),
-Phaeophyceae (Brown algae), Magnoliopsida (Seagrass), Chlorophyceae
-(Green algae) and Rhodophyceae (Red algae)
-(Figure~\ref{fig-vegetation}). Picture of each quadrat were taken and
+distributed over the study site and georeferenced with a Trimble © Geo
+XH 6000 differential GPS (dGPS). GCPs were used to correct
+georeferencing imprecision of orthomosaics with an horizontal and
+vertical accuracy of 10cm. dGPS was also used to georeference quadrats
+of 0.25cm² used to assess the presence or absence of 5 key classes of
+vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm
+over the sediment during low tide), Phaeophyceae (brown algae),
+Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae
+(red algae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
 uploaded on the online on the Global Biodiversity Information Facility
-(GBIF) platform \citep{BedeGbif}. Each photograph was also processed to
-estimate the percent cover of each type of vegetation. Georeferenced
-hyperspectral reflectance signatures of each vegetation class were also
-sampled using an ASD FieldSpec HandHeld 2 spectroradiomete, which
-acquires reflectance between 325 and 1075 nm, with 1 nm of spectral
-resolution. The methodological scheme followed in this study is
-presented in Figure~\ref{fig-workflow}.
+(GBIF) platform \citep{BedeGbif}, a public open portal to store and
+share biodiversity data. Each photograph was also processed to estimate
+the percent cover of each type of vegetation using an image processing
+software (imageJ). For all quadrat, the hyperspectral reflectance
+signatures of each vegetation class was measured using an ASD FieldSpec
+HandHeld 2 spectroradiometer, which acquires reflectance between 325 and
+1075 nm, with 1 nm of spectral resolution. The methodological scheme
+followed in this study is presented in Figure~\ref{fig-workflow}.
 
@@
 
-\caption{\label{fig-vegetation}Class of vegetation used to train the CNN
-model and their standardised spectral signature}
+\caption{\label{fig-vegetation}Class of vegetation used to train the
+Neural Network model and their standardised spectral signature}
 
@@
 flights: high-resolution flights were utilized for training and
-prediction of the CNN model, whereas low-resolution flights were solely
-employed for prediction purposes.}
+prediction of the Neural Network model, whereas low-resolution flights
+were solely employed for prediction purposes.}
 
@@
 
-The spectral similarities of reflectance signatures between intertidal
-green macrophytes (Magnoliopsida and Chlorophyceae) make their
-discrimination challenging using simple classification algorithms
+The spectral similarities of the reflectance signatures between
+intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make
+their discrimination challenging using simple classification algorithms
 (Figure~\ref{fig-vegetation} F). To overcome this challenge, a deep
@@
 A dataset containing photo-interpreted drone reflectance pixels was
-built to train a Convolutional Neural Network (CNN) model with 2 hidden
-layers. The training pixels were categorized into 7 different classes,
-representing the various habitats encountered at the different study
-sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae,
-Phaeophyceae and Rhodophyceae. Only low-altitude flights (Table 1) were
-used for training purposes because of their 8 mm spatial resolution
-allowing to avoid spectral sub-pixel mixing and to accurately visually
-differentiate various vegetation classes. More than 418,000 pixels at 8
-mm resolution from the 3 training flights have been used to train the
-model (Table 2). Twenty one variables were used by the model as
-predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX
-multispectral camera (ranging from 444 nm to 840 nm), the same 10
-spectral bands standardized using a min/max transformation
-(Equation~\ref{eq-std} ; \citep{Cao2017}) and the NDVI
-(Equation~\ref{eq-ndvi}). Standardisation of spectral bands is used to
-eliminate the scaling differences between spectra and to limit the
-effect of biomass on the shape of the spectra \citetext{\citealp[
+built to train a Neural Network model with 2 hidden layers. The training
+pixels were categorized into 7 different classes, representing the
+various habitats encountered at the different study sites: Sediment,
+Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
+Rhodophyceae. Only low-altitude flights (Table 1) were used for training
+purposes because their 8 mm spatial resolution allowied to avoid
+spectral sub-pixel mixing and to accurately differentiate various
+vegetation classes. More than 418,000 pixels at 8 mm resolution from the
+3 training flights were used to train the model (Table 2). Twenty one
+variables were used by the model as predictors: 10 raw spectral bands of
+the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm
+to 840 nm), the same 10 spectral bands standardized using a min/max
+transformation (Equation~\ref{eq-std} ; \citep{Cao2017}) and the
+Normalized difference vegetation index (NDVI, Equation~\ref{eq-ndvi}).
+Standardisation of spectral bands is used to eliminate the scaling
+differences between spectra and to limit the effect of biomass on the
+shape of the spectra \citetext{\citealp[
 ]{Douay2022}; \citealp{Davies2023}}.
@@
 
-The CNN model was applied to all the 9 flights at both 12 and 120 m of
-altitude. In situ information on georeferenced class type and percent
-cover collected during each flight has been used to assess the CNN
-accuracy. These images were used to construct a validation dataset
-indicating the presence or absence of each class. Additionally to the
-quadrat-based validation dataset, polygons of each class were photo
-interpreted in order to increase the number of pixels of the validation
-dataset. A confusion matrix, along with precision metrics such as the
-global accuracy, the sensitivity, the specificity, and the Kappa
-coefficient, was generated for each of the study sites. Finally each
-validation matrix has been merge to create a unique matrix of the model.
-A total of 536,000 pixels has been used to globally validate the CNN
-model.
+The model was applied to all flights at both 12 and 120 m of altitude.
+In situ information on georeferenced class type and percent cover
+collected during each flight was used to assess the model accuracy.
+These images were used to construct a validation dataset indicating the
+presence or absence of each class. Additionally to the quadrat-based
+validation dataset, polygons of each class were photo interpreted in
+order to increase the number of pixels of the validation dataset. A
+confusion matrix, along with precision metrics such as global accuracy,
+sensitivity, specificity, and Kappa coefficient, was generated for each
+sites. All validation matrices were then merged to create a unique
+matrix . Altogether, a total of 536,000 pixels was used to validate the
+model, thus providing a geographically robust validation dataset.
 
@@
 with the highest complexity (Figure~\ref{fig-GafLow}). Among the 5
-vegetation classes on which the CNN model was trained, 4 were present on
+vegetation classes on which the model was trained, 4 were present on
 this site. On this site, there is a mixture of Chlorophyceae and
@@
 (indicating beds where leaves are dying). Regardless of the color, the
-meadow is predicted as Magnoliopsida by the CNN model.
+meadow is predicted as Magnoliopsida by the model.
 
@@
 (Figure~\ref{fig-GafHigh}). A channel delineating a small island was
-present in the flight, but it has been masked in the prediction map due
-to glinting and misclassification caused by the turbid shallow water.
-Most of the intertidal area has been classified as Magnoliopsida by the
-model, even though there is discoloration of seagrass blades. Only a few
-pixels have been classified as Chlorophyceae at this scale. Furthermore,
-the area that was classified as Bacillariophyceae in the low-altitude
-flight remains mostly classified as such in the high-altitude flight,
-but some pixels of it are now classified as Magnoliopsida. The patches
-of Rhodophyceae are still well classified. \emph{Spartina sp.} was
-present in the northern part of the flight, near the land, and has been
-classified either as Magnoliopsida or as Phaeophyceae.
+masked in the prediction map due to sunglint and misclassification
+caused by the turbid shallow water. Most of the intertidal area has been
+classified as Magnoliopsida by the model, even though there is
+discoloration of seagrass blades. Only a few pixels have been classified
+as Chlorophyceae at this scale. Furthermore, the area that was
+classified as Bacillariophyceae in the low-altitude flight remains
+mostly classified as such in the high-altitude flight, though some
+pixels were classified as Magnoliopsida. Patches of Rhodophyceae were
+correctly classified. In the nothern part of the scene, near the land
+limit, patches of \emph{Spartina sp.} were misclassified, either as
+Magnoliopsida or as Phaeophyceae.
 
@@
 
-The High altitude flight made in the inner lagoon of the Ria de Aveiro
-is the largest of all flights, covering almost 1.5 km²
+The high altitude flight acquired over the inner lagoon of the Ria de
+Aveiro is the largest of all flights, covering almost 1.5 km²
 (Figure~\ref{fig-Boat}). On this site, only seagrass and red algae where
-seen on the field. The classification follows the same pattern, with a
-patchy Magnoliopsida meadow mixed on the eastern part of the flight with
-Rhodophyceae. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of
-the meadow can be colonised by Chlorophyceae.
+seen on the field. The classification provided consistent results, with
+a patchy Magnoliopsida meadow mixed with Rhodophyceae on the eastern
+part of the scene. As shown in the zoom (Figure~\ref{fig-Boat}), the
+edges of the meadow can be colonised by Chlorophyceae.
 
@@
 (Figure~\ref{fig-Dike}) was conducted near a dike crossing the northern
-part of the flight from west to east. Alongside this dike, brown algae
+part of the scene from west to east. Alongside this dike, brown algae
 attached to rocks and stranded green algae could be found. Despite the
-high mixture between Chlorophyceae and Magnoliopsida in this flight,
-these two classes are well discriminated by the classifier.
+high mixture between Chlorophyceae and Magnoliopsida these two classes
+were correctly discriminated by the classifier.
 
@@
 
-A total amount of 536,000 pixels have been used to validate the Neural
-Network classifier. The site with the least amount of validation data is
-Kerdrean with a total of 5557 pixels whereas Marinha Lanzarote is the
-site with the most amount of validation data with 159713 pixels. The
-global accuracy of the model is 94.26\% and a Kappa coefficient of 0.92
-(Figure~\ref{fig-Validation}). The least performing site is Gafanha High
-with an accuracy of 75.45\% whereas Mataducos is the site with most
-accurate prediction, with a global accuracy of 98.05\%. Overall
-Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae are well
-classified with a balanced accuracy of 1, 0.96, 0.96 and 0.91
-respectively. Bacillariophyceae is the least performing class with an
-accuracy of 0.72 mainly due to a confusion with Magnoliopsida and
+A total of 536,000 pixels was used to validate the Neural Network
+classifier. The sites with the lowest and highest number of validation
+data were Kerdrean (5557 pixels) and Marinha Lanzarote (159713 pixels),
+respectively. Model global accuracy was 94.26\% with a Kappa coefficient
+of 0.92 (Figure~\ref{fig-Validation}). The least performing site was
+Gafanha High (global accuracy of 75.45\%) whereas Mataducos was the site
+with the most accurate prediction (global accuracy of 98.05\%). Overall,
+the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were
+correctly classified with a balanced accuracy of 1, 0.96, 0.96 and 0.91
+respectively. Bacillariophyceae was the least performing class (accuracy
+of 0.72 ) mainly due to the confusion between Magnoliopsida and
 Sediment.
@@
 
-The computation of the importance variable of each class indicate which
-wavelength is mandatory to accurately predict the class
-(Figure~\ref{fig-VIP}). Bands at 444 nm, 717 nm and 842 nm of the
-Micasense camera are important for none of the vegetation classes. The
-band at 531 nm is the only important predictor for the classifier to
-accuratly predict chlorophyceae. In fact, at this wavelength, the
-Chlorophyceae spectra has the maximum reflectance value of all the
-classes. 531 nm and 740 nm are the most important predictors to predict
-Phaeophyceae, corresponding to the minimum reflectance value among all
-the classes. Bands at 475 and 560 nm are the most important predictors
-for Bacillariophyceae and Rhodophyceae, respectively. 4 predictors,
-ranging from the Green (560 nm) to the RedEdge (705 nm) are important to
-predict accurately magnoliopsida.
+The computation of the variable importance makes it possible to identify
+which wavelengths are the most useful for class prediction
+(Figure~\ref{fig-VIP}). The spectral bands at 444 , 717 and 842 nm of
+the Micasense camera are important for none of the vegetation classes.
+The band at 531 nm is the only important predictor for the classifier to
+accurately predict chlorophyceae. In fact, at this wavelength, the
+Chlorophyceae spectra has the maximum reflectance among of all
+vegetation classes. The bands at 531 and 740 nm are the most important
+predictors for Phaeophyceae, corresponding to the minimum reflectance
+among all classes. Bands at 475 and 560 nm are the most important
+predictors for Bacillariophyceae and Rhodophyceae, respectively. Four
+predictors, ranging from the green (560 nm) to the RedEdge (705 nm)
+bands are important to accurately predict magnoliopsida.
 
@@
 
-Figure~\ref{fig-upscaling} is showing the percent cover of a class
-required to classify correctly the high altitude flight. When the
-percent cover of the class is 100 \%, big pixels are well classified for
-all the classes excepted for Bare Sediment, where it's well classified
-80\% of the time. A vegetative percent cover of at least 80\% is need to
-have all the big pixels well classified, at the exception of
+Using the very high precision low altitude flight, we determined the
+minimal percent cover required to classify correctly classify a given
+class using the high altitude flight (Figure~\ref{fig-upscaling}). When
+the percent cover of the class is 100 \%, big pixels are well classified
+for all the classes excepted for Bare Sediment, where it's well
+classified 80\% of the time. A vegetative percent cover of at least 80\%
+is need to have all the big pixels well classified, at the exception of
 Magnoliopsida that needs an higher percent cover (\textgreater90 \%) to
@@
 exhibits the highest reflectance among all other classes, highlighting
-the difference in carotenoid proportion between seagrasses and green
-algae.
+the difference in accessories carotenoid proportion between seagrasses
+and green algae (\citep{repolho2017seagrass}).
+
+Concerning Phaeophyceae, the thick cell walls of plant of this class
+make it really reflective in the infrared part of the spectra whereas
+the presence of Fucoxanthin and Zeaxanthin result in a low reflectance
+in the visible part of the electomagnetic spectra. These two key
+features has been identified by the Neural Network as the two principale
+predictors to accuratly identify Brown algae (Figure~\ref{fig-VIP}, )
 

### 2024-03-01 docs/index.qmd
Pierre comments

@@
 Coastal areas are vital hotshots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
-These meadows offer a myriad of ecosystem services to humanity, including limitation of coastline erosion, reducing the risk of eutrophication, carbon sequestration, and oxygen production.
+Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production,protection against sea-level rise and coastline erosion, and limitation of eutrophication.
 They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019].
-Due to their proximity to human activities, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation are currently observed due to diseases, disasters, coastal urbanization, sea reclamation, as well as fishing activities, dredging, sea level rise, coastal erosion, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019].
-While improvements in water quality have been recently reported in European sites, allowing an overall recovery of seagrass ecosystems at the local scale, many other coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides.
-Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@Duarte2002 ; @wang2022].
-
-The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of global and regional monitoring programs for systematically surveying different Essential Oceanic Variable [@Miloslavich2018] as seagrass coverage and composition; as well as Essential Biodiversity Variable [@Pereira2013] such as seagrass taxonomic diversity; species distribution, population abundance, and phenology.
-Monitoring programs also prioritize the identification of threats to these ecosystems, particularly during early stages, to facilitate effective mitigation actions.
-Traditionally, these ecological parameters have been quantified through in situ measurements, although this approach faces several constraints over intertidal zones.
-Intertidal meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
-However, satellite data have been proven effective in complenmenting in situ surveys, allowing for the rapid and consitent retrieval of EOV's over extensive seagrass meadows.
+Due to the concentration of human activities in coastal zones, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
+Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019].
+While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
+Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides (@devlin2023nutrients ; @devlin2023nutrients).
+Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
+
+The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, populuation abundance, and phenology [@Pereira2013].
+Seagrass monitoring is all the more important as it makes possible to identify which pressure should be addressed in priority to facilitate effective mitigation actions.
+Traditionally, indicators of seagrass status have been quantified using in situ measurements.
+The acquisition of field data in intertidal zones is however notoriously challenging.
+Intertidal seagrass meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
+Satellite observations have been proven effective in complementing in situ sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
 [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023]
 
-Satellite remote sensing offers the advantage of acquiring large-scale data in real-time but presents its inherent challenges.
-Free access satellite data (e.g., Sentinel-2 and Landsat8/9) provide relatively low spatial resolution data (10 - 30 m) across a limited number of spectral bands.
-These characteristics can be a limitation to accurately discriminating seagrass from others co-existing macrophytes over the meadow.
-Chlorophyceae (Green Algae) and marine Magnoliopsida (Seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
+While satellite remote sensing provides temporally consistent observations over large spatial scales, it is limited by several constraints.
+Satellite missions with a high temporal resolution (e.g.
+daily MODIS observation) are limited by a coarse spatial resolution (\>100m).
+Mission with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
+The limited number of spectral bands is indeed a challenge to accurately discriminate seagrass from others co-existing macrophytes.
+In particular Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
 As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022].
-Recently, using a hyperspectral library, @Davies2023 demonstrated that the spectral resolution of Sentinel-2, might be enough for the discrimination between Magnoliopsida and Chlorophyceae.
-However, green tide events occur at small spatial scales that are not observable using satellite imagery [@tuya2013], especially during the initial stage of the event.
-
-Remote sensing drone acquisitions are presented as a tool that can potentially fill gaps left by satellite and in situ data.
-Drone can cover large expanses while recording imagery at significantly higher spatial resolutions than satellite (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
-The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping the spatial distribution of species [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
-However, when applied to coastal habitat mapping, many studies showcase their findings with study case limited to a single flight, restricting the generalizability of their application to other sites [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-This study aimed to analyze the potential of a drone equipped with a multispectral sensor for mapping intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance measurements, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+The application of this approach to satellite remote sensing remains however to be validated.
+Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of the event.
+
+Drone can potentially fill the gaps left by satellite remote sensing and in situ measurments, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
+However, when applied to coastal habitat mapping, most sutdy cases were limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+The present study aimed at analyzing the potential of multispectral drone remote sensing to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae.
-A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of accuracy in predictions.
+A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
 
@@
 #| fig-cap: >
-#|   Sites where the different drone flights were made.
-A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon.
-Light green represent terrestrial areas whereas darkgreen represent intertidal areas.
+#|   Sites observed by drone. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent terrestrial areas whereas darkgreen represent intertidal areas. 
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from blue (444 nm) to near infrared (840 nm).
-An angle of 90° has been maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
-A side overlap of 70% and a front overlap of 80% between each image has been set.
-Images have been calibrated in reflectance using a calibration panel reflective at \~50% provided by the camera's manufaturer and a Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance data during the flight.
-A Structure-from-Motion photogrammetry software (Agisoft Metashape) has been used to process images to obtain multispectral orthomosaics of each flight.
-The workflow for orthomosaicking has remained consistent for every flight.
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
+An angle of 90° was maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
+A side overlap of 70% and a front overlap of 80% between each imagewas set for each flight.
+A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements.
+Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer.
+A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
+The workflow for orthomosaicking was the same for every flight.
 First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
 This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
-A dense point cloud has been then produced using a structure from motion algorithm.
-A surface interpolation of this dense point cloud has been made to obtain a Digital Surface Model (DSM), used to reconstruct the multispectral ortho-image.
-Across all the sites, flights were made at two different altitudes : 12 m or/and 120 m.
+A dense point cloud was then produced using a structure from motion algorithm.
+A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
+Across all sites, flights were made at two different altitudes : 12 m or/and 120 m.
 Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it simple to visually distinguish between the various types of vegetation.
@@
 #| warning: false
-#| tbl-cap: List of drone Flight, summarising the date, the altitude and the purpose of each flight.
+#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight.
 #| cache: true
@@
 
-Before each flight, targets used as Ground Control Points (GCPs) were dispersed and georeferenced with a Trimble © Geo XH 6000 differential GPS (dGPS).
+Before each flight, targets used as Ground Control Points (GCPs) were distributed over the study site and georeferenced with a Trimble © Geo XH 6000 differential GPS (dGPS).
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quardrats of 0.25cm² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (Brown algae), Magnoliopsida (Seagrass), Chlorophyceae (Green algae) and Rhodophyceae (Red algae) (@fig-vegetation).
-Picture of each quadrat were taken and uploaded on the online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif].
-Each photograph was also processed to estimate the percent cover of each type of vegetation.
-Georeferenced hyperspectral reflectance signatures of each vegetation class were also sampled using an ASD FieldSpec HandHeld 2 spectroradiomete, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
+dGPS was also used to georeference quadrats of 0.25cm² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (brown algae), Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae (red algae) (@fig-vegetation).
+Pictures of each quadrat were uploaded on the online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
+Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software (imageJ).
+For all quadrat, the hyperspectral reflectance signatures of each vegetation class was measured using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
 The methodological scheme followed in this study is presented in @fig-workflow.
@@
 #| warning: false
-#| fig-cap: Class of vegetation used to train the CNN model and their standardised spectral signature
+#| fig-cap: Class of vegetation used to train the Neural Network model and their standardised spectral signature
 #| label: fig-vegetation
@@
 Diamonds represent input or output data, and rectangles represent Python processing algorithms.
-The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights were utilized for training and prediction of the CNN model, whereas low-resolution flights were solely employed for prediction purposes."
+The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights were utilized for training and prediction of the Neural Network model, whereas low-resolution flights were solely employed for prediction purposes."
 #| label: fig-workflow
@@
 
-The spectral similarities of reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
+The spectral similarities of the reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
 To overcome this challenge, a deep learning classification method was developed, trained, validated, and applied to each drone flight (@fig-workflow).
@@
 
-A dataset containing photo-interpreted drone reflectance pixels was built to train a Convolutional Neural Network (CNN) model with 2 hidden layers.
+A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model with 2 hidden layers.
 The training pixels were categorized into 7 different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (Table 1) were used for training purposes because of their 8 mm spatial resolution allowing to avoid spectral sub-pixel mixing and to accurately visually differentiate various vegetation classes.
-More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights have been used to train the model (Table 2).
-Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the NDVI (@eq-ndvi).
+Only low-altitude flights (Table 1) were used for training purposes because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately differentiate various vegetation classes.
+More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (Table 2).
+Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
 Standardisation of spectral bands is used to eliminate the scaling differences between spectra and to limit the effect of biomass on the shape of the spectra [@Douay2022 ; @Davies2023].
@@
 
-The CNN model was applied to all the 9 flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover collected during each flight has been used to assess the CNN accuracy.
+The model was applied to all flights at both 12 and 120 m of altitude.
+In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
 These images were used to construct a validation dataset indicating the presence or absence of each class.
 Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.
-A confusion matrix, along with precision metrics such as the global accuracy, the sensitivity, the specificity, and the Kappa coefficient, was generated for each of the study sites.
-Finally each validation matrix has been merge to create a unique matrix of the model.
-A total of `r my_comma(round(count_validation_pixel,-3))` pixels has been used to globally validate the CNN model.
+A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
+All validation matrices were then merged to create a unique matrix .
+Altogether, a total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the model, thus providing a geographically robust validation dataset.
 
@@
 The low-altitude flight conducted in Gafanaha, Portugal, represents the site with the highest complexity (@fig-GafLow).
-Among the 5 vegetation classes on which the CNN model was trained, 4 were present on this site.
+Among the 5 vegetation classes on which the model was trained, 4 were present on this site.
 On this site, there is a mixture of Chlorophyceae and Rhodophyceae over the seagrass meadow.
@@
 Although the seagrass bed is solely composed of *Zostera noltei*, various colors can be observed: dark green (indicating healthy beds with 100% coverage) and whitish/brown (indicating beds where leaves are dying).
-Regardless of the color, the meadow is predicted as Magnoliopsida by the CNN model.
+Regardless of the color, the meadow is predicted as Magnoliopsida by the model.
 
@@
 The high-altitude flight over Gafanha covered nearly 1 km² in total (@fig-GafHigh).
-A channel delineating a small island was present in the flight, but it has been masked in the prediction map due to glinting and misclassification caused by the turbid shallow water.
+A channel delineating a small island was masked in the prediction map due to sunglint and misclassification caused by the turbid shallow water.
 Most of the intertidal area has been classified as Magnoliopsida by the model, even though there is discoloration of seagrass blades.
 Only a few pixels have been classified as Chlorophyceae at this scale.
-Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remains mostly classified as such in the high-altitude flight, but some pixels of it are now classified as Magnoliopsida.
-The patches of Rhodophyceae are still well classified.
-*Spartina sp.* was present in the northern part of the flight, near the land, and has been classified either as Magnoliopsida or as Phaeophyceae.
+Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remains mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
+Patches of Rhodophyceae were correctly classified.
+In the nothern part of the scene, near the land limit, patches of *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 
-The High altitude flight made in the inner lagoon of the Ria de Aveiro is the largest of all flights, covering almost 1.5 km² (@fig-Boat).
+The high altitude flight acquired over the inner lagoon of the Ria de Aveiro is the largest of all flights, covering almost 1.5 km² (@fig-Boat).
 On this site, only seagrass and red algae where seen on the field.
-The classification follows the same pattern, with a patchy Magnoliopsida meadow mixed on the eastern part of the flight with Rhodophyceae.
+The classification provided consistent results, with a patchy Magnoliopsida meadow mixed with Rhodophyceae on the eastern part of the scene.
 As shown in the zoom (@fig-Boat), the edges of the meadow can be colonised by Chlorophyceae.
@@
 
-The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike crossing the northern part of the flight from west to east.
+The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike crossing the northern part of the scene from west to east.
 Alongside this dike, brown algae attached to rocks and stranded green algae could be found.
-Despite the high mixture between Chlorophyceae and Magnoliopsida in this flight, these two classes are well discriminated by the classifier.
+Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
 
@@
 
-A total amount of `r my_comma(round(count_validation_pixel,-3))` pixels have been used to validate the Neural Network classifier.
-The site with the least amount of validation data is `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` with a total of `r min(df_summarize$n)` pixels whereas `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` is the site with the most amount of validation data with `r max(df_summarize$n)` pixels.
-The global accuracy of the model is `r round(validation_metrics$overall[[1]]*100,2)`% and a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
-The least performing site is `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` with an accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`% whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` is the site with most accurate prediction, with a global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%.
-Overall Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae are well classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
-`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` is the least performing class with an accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` mainly due to a confusion with Magnoliopsida and Sediment.
+A total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the Neural Network classifier.
+The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
+Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
+The least performing site was `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`%) whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` was the site with the most accurate prediction (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%).
+Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were correctly classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
+`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` was the least performing class (accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` ) mainly due to the confusion between Magnoliopsida and Sediment.
 
@@
 
-The computation of the importance variable of each class indicate which wavelength is mandatory to accurately predict the class (@fig-VIP).
-Bands at 444 nm, 717 nm and 842 nm of the Micasense camera are important for none of the vegetation classes.
-The band at 531 nm is the only important predictor for the classifier to accuratly predict chlorophyceae.
-In fact, at this wavelength, the Chlorophyceae spectra has the maximum reflectance value of all the classes.
-531 nm and 740 nm are the most important predictors to predict Phaeophyceae, corresponding to the minimum reflectance value among all the classes.
+The computation of the variable importance makes it possible to identify which wavelengths are the most useful for class prediction (@fig-VIP).
+The spectral bands at 444 , 717 and 842 nm of the Micasense camera are important for none of the vegetation classes.
+The band at 531 nm is the only important predictor for the classifier to accurately predict chlorophyceae.
+In fact, at this wavelength, the Chlorophyceae spectra has the maximum reflectance among of all vegetation classes.
+The bands at 531 and 740 nm are the most important predictors for Phaeophyceae, corresponding to the minimum reflectance among all classes.
 Bands at 475 and 560 nm are the most important predictors for Bacillariophyceae and Rhodophyceae, respectively.
-4 predictors, ranging from the Green (560 nm) to the RedEdge (705 nm) are important to predict accurately magnoliopsida.
+Four predictors, ranging from the green (560 nm) to the RedEdge (705 nm) bands are important to accurately predict magnoliopsida.
 
@@
 
-@fig-upscaling is showing the percent cover of a class required to classify correctly the high altitude flight.
+Using the very high precision low altitude flight, we determined the minimal percent cover required to classify correctly classify a given class using the high altitude flight (@fig-upscaling).
 When the percent cover of the class is 100 %, big pixels are well classified for all the classes excepted for Bare Sediment, where it's well classified 80% of the time.
@@
 
-::::: columns
+::: columns
 ::: column
@@
 :::
-:::::
+:::
 
@@
 VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in carotenoid proportion between seagrasses and green algae.
+In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).
+
+Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electomagnetic spectra.
+These two key features has been identified by the Neural Network as the two principale predictors to accuratly identify Brown algae (@fig-VIP, )
 

### 2024-03-01 index.qmd
Pierre comments

@@
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae.
-A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy
+A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
 
@@
 At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
-An angle of 90° has been maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
-A side overlap of 70% and a front overlap of 80% between each image has been set.
-for each flight Images have been calibrated in reflectance using a calibration panel reflective at \~50% provided by the camera's manufaturer and a Downwelling Light Sensor (DLS2) that was utilized to acquire irradiance data during the flight.
-A Structure-from-Motion photogrammetry software (Agisoft Metashape) has been used to process images to obtain multispectral orthomosaics of each flight.
-The workflow for orthomosaicking has remained consistent for every flight.
+An angle of 90° was maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
+A side overlap of 70% and a front overlap of 80% between each imagewas set for each flight.
+A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements.
+Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer.
+A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
+The workflow for orthomosaicking was the same for every flight.
 First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
 This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
-A dense point cloud has been then produced using a structure from motion algorithm.
-A surface interpolation of this dense point cloud has been made to obtain a Digital Surface Model (DSM), used to reconstruct the multispectral ortho-image.
-Across all the sites, flights were made at two different altitudes : 12 m or/and 120 m.
+A dense point cloud was then produced using a structure from motion algorithm.
+A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
+Across all sites, flights were made at two different altitudes : 12 m or/and 120 m.
 Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it simple to visually distinguish between the various types of vegetation.
@@
   sample_n(10000) %>%
-  rearrr::rotate_2d(x_col = "Low", y_col = "High",degrees = 9, origin = c(0,0)) %>% select(Low_rotated,High_rotated) %>% 
-  rename(Low = Low_rotated, High = High_rotated) %>% 
   mutate(Low = Low /10000, 

### 2024-03-01 docs/_tex/index.tex
Pierre comments

@@
 
-\subsection{Green Macrophytes
-Discrimination}\label{green-macrophytes-discrimination}
+\subsection{Vegetation Discrimination}\label{vegetation-discrimination}
 
@@
 like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
-spectral signatures that are often indistinguishable to non expererences
+spectral signatures that are often indistinguishable to non exper eyes.
 This spectral overlap is further complicated by the intermingling of
@@
 \citep{Davies2023} has shown that having at least 8 spectral bands
-ranging between 500 nm to 850 nm with on band at 530 nm and another one
-at 730 nm is crucial to accurately discriminate green macrophytes.
+ranging between 500 nm to 850 nm with including a band at 530 nm and
+another one at 730 nm is crucial to accurately discriminate green
+macrophytes.
 
@@
 Several factors can explain these differences such has different pigment
-concentration en proportion, different cellular organisation and 3D
+concentration or proportion, different cellular organisation and 3D
 disposition of the plant a whole on the intertidal mudflat
@@
 
-The VIP analysis of the Neural Network model (see Fig. VIP) shows that
-the 531 nm band is the most important spectral band for accurately
-identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae
-exhibits the highest reflectance among all other classes, highlighting
-the difference in accessories carotenoid proportion between seagrasses
-and green algae (\citep{repolho2017seagrass}).
+The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
+shows that the 531 nm band is the most important spectral band for
+accurately identifying Chlorophyceae. In fact, at this wavelength,
+Chlorophyceae exhibits the highest reflectance among all other classes,
+highlighting the difference in accessories carotenoid proportion between
+seagrasses and green algae (\citep{repolho2017seagrass}).
 
@@
 the presence of Fucoxanthin and Zeaxanthin result in a low reflectance
-in the visible part of the electomagnetic spectra. These two key
-features has been identified by the Neural Network as the two principale
-predictors to accuratly identify Brown algae (Figure~\ref{fig-VIP}, )
+in the visible part of the electromagnetic spectra. These two key
+features has been identified by the Neural Network as the two principal
+predictors to accurately identify Brown algae (Figure~\ref{fig-VIP}).
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
+contributes to the lowest reflectance among all classes in the spectral
+range of 560 to 615 nm (Figure~\ref{fig-VIP}). The band at 560 nm has
+been identified as important for accurately identifying this class
+Resolution impact on the prediction. Regarding Bacillariophyceae, the
+VIP analysis (Figure~\ref{fig-VIP}) indicates that 475 nm is the most
+important predictor for this class. This could be attributed to the
+absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in
+the blue part of spectra, resulting in the highest visible reflectance
+among all classes. Furethemore, it is vegetation with the lowest
+concentration of chlorphyll-a, pigment absorbing light both in the blue
+and the red. The transparency of Bacillariophyceae makes the reflectance
+of the sediment part of the overall reflectance of Bacillariophyceae,
+further explaining the high reflectance in the blue.
 
-\subsection{Spectral and Temporal Resolution impact on the
-prediction}\label{spectral-and-temporal-resolution-impact-on-the-prediction}
+\subsection{\texorpdfstring{\textbf{Spectral Spatial Temporal Resolution
+impact on the
+prediction}}{Spectral Spatial Temporal Resolution impact on the prediction}}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}
 

### 2024-03-01 index.qmd
Pierre comments

@@
 
-## Green Macrophytes Discrimination
+## Vegetation Discrimination
 
@@
 The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
-This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non expererences This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
+This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non exper eyes.
+This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
 Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands.
-@Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with on band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
+@Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with including a band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
 
@@
 Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
-Several factors can explain these differences such has different pigment concentration en proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
+Several factors can explain these differences such has different pigment concentration or proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
 :::
@@
 
-The VIP analysis of the Neural Network model (see Fig.
-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
+The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
 In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).
 
-Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electomagnetic spectra.
-These two key features has been identified by the Neural Network as the two principale predictors to accuratly identify Brown algae (@fig-VIP, )
-
-## Spectral and Temporal Resolution impact on the prediction
+Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electromagnetic spectra.
+These two key features has been identified by the Neural Network as the two principal predictors to accurately identify Brown algae (@fig-VIP).
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range of 560 to 615 nm (@fig-VIP).
+The band at 560 nm has been identified as important for accurately identifying this class Resolution impact on the prediction.
+Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicates that 475 nm is the most important predictor for this class.
+This could be attributed to the absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in the blue part of spectra, resulting in the highest visible reflectance among all classes.
+Furethemore, it is vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
+The transparency of Bacillariophyceae makes the reflectance of the sediment part of the overall reflectance of Bacillariophyceae, further explaining the high reflectance in the blue.
+
+## **Spectral Spatial Temporal Resolution impact on the prediction**
 

### 2024-03-01 docs/_tex/index.tex
Pierre comments

@@
 
-\subsection{\texorpdfstring{\textbf{Spectral Spatial Temporal Resolution
-impact on the
-prediction}}{Spectral Spatial Temporal Resolution impact on the prediction}}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}
+\subsection{Spectral Spatial Temporal Resolution impact on the
+prediction}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}
 
@@
 
+In the present study, the main novelty is the usage of two different
+altitude (12m and 120m) in the neural network model building. The
+spatial resolution of the low altitude fights (8mm) allows for an
+accurate selection of pure pixel of the classes used in the neural
+network model
+
 \subsection{Big picture}\label{big-picture}

### 2024-03-01 index.qmd
Pierre comments

@@
 
-## **Spectral Spatial Temporal Resolution impact on the prediction**
+## Spectral Spatial Temporal Resolution impact on the prediction
 
@@
 
+::: columns
+::: column
 ```{r Plot Reflectance_Validation 2 height}
@@
 ```
+:::
+
+::: column
+In the present study, the main novelty is the usage of two different altitude (12m and 120m) in the neural network model building.
+The spatial resolution of the low altitude fights (8mm) allows for an accurate selection of pure pixel of the classes used in the neural network model
+:::
+:::
 

### 2024-03-02 docs/_tex/index.tex
add disc

@@
 highlighting the difference in accessories carotenoid proportion between
-seagrasses and green algae (\citep{repolho2017seagrass}).
+seagrasses and green algae \citep{repolho2017seagrass}.
 
@@
 both low-altitude and high-altitude flights over a common area. The red
-dashed line represents a 1 to 1 relationship.}
-
-\end{figure}%
-
-In the present study, the main novelty is the usage of two different
-altitude (12m and 120m) in the neural network model building. The
-spatial resolution of the low altitude fights (8mm) allows for an
-accurate selection of pure pixel of the classes used in the neural
-network model
+dashed line represents a linear model wheras the black dashed line
+represents a 1 to 1 relationship.}
+
+\end{figure}%
+
+In this study, a key innovation lies in the utilization of two different
+altitudes (12m and 120m) for constructing the neural network model. The
+lower altitude flights (8mm spatial resolution) enable precise selection
+of pure pixels representing the classes used in the neural network
+model. This methodology implies a consistency between the reflectance of
+both altitude.
+
+Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
+from a low-altitude flight and a high-altitude flight conducted over the
+same area. An apparent underestimation of reflectance values is observed
+in the high-altitude flight, particularly for higher values. Since both
+flights were conducted over vegetation areas, the highest reflectance
+values correspond to the infrared part of the spectrum. The disparity in
+infrared reflectance may stem from temporal differences between the
+flights, possibly resulting in a slightly drier intertidal area and
+consequently higher infrared reflectance. This disparity poses an issue
+for the methodology followed in the present study, relying solely on one
+flight height for training. To address this issue, we employed min/max
+standardized reflectance spectra as predictors for the model
+(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
+eliminate differences in the level of reflectance, focusing instead on
+the shape of the spectra. This is a key feature in building a model that
+can reliably predict vegetation across geographical sites and seasons.
+It enables consistent prediction of vegetation classes across variations
+in biomass and variability in light conditions \citetext{\citealp[
+]{fyfe2003spatial}; \citealp[
+]{COSTA2021107018}; \citealp{piaser2023impact}}.
 

### 2024-03-02 index.qmd
add disc

@@
 The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).
+In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae [@repolho2017seagrass].
 
@@
   # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "red" )+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
   theme_Bede()+
@@
         legend.key.width = unit(3,"line"))
-
+plot
 ggsave("./Figures/Compare_reflectance.png",plot, width= 472*4, height=402*4, units = "px")
@@
 #| warning: false
-#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a 1 to 1 relationship. 
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
+The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship.
 #| label: fig-CompareRef
@@
 ::: column
-In the present study, the main novelty is the usage of two different altitude (12m and 120m) in the neural network model building.
-The spatial resolution of the low altitude fights (8mm) allows for an accurate selection of pure pixel of the classes used in the neural network model
+In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
+The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model.
+This methodology implies a consistency between the reflectance of both altitude.
 :::
@@
 
+ @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
+An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values.
+Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
+The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
+This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training.
+To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]).
+This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra.
+This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons.
+It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
+
 ## Big picture

### 2024-03-02 docs/_tex/index.tex
low res figures

@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Fig1_Map_Drone_Sites.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Fig1_Map_Drone_Sites.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{Figures/Spectral_shapes_total.png}
+\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/Spectral_shapes_total.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Figure3_workflow.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Figure3_workflow.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_Low_Pred.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Gaf_High_Pred.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Boat_Pred.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Maps Pred/FigX-Dike_Pred.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGlobal.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGlobal.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{Figures/VIP/Fig_VIP.png}
+\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/VIP/Fig_VIP.png}
 
@@
 
-\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Upscaling/density_vs_Proportion.png}
+\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Low_res/Upscaling/density_vs_Proportion.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Disc_Pigment_Table.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Validation/ConfusionMatrixGreen.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGreen.png}
 
@@
 
-\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Compare_reflectance.png}
+\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}
 

### 2024-03-02 index.qmd
low res figures

@@
 
-knitr::include_graphics("./Figures/Fig1_Map_Drone_Sites.png")
+knitr::include_graphics("./Figures/Low_res/Fig1_Map_Drone_Sites.png")
 ```
@@
 
-knitr::include_graphics("Figures/Spectral_shapes_total.png")
+knitr::include_graphics("Figures/Low_res/Spectral_shapes_total.png")
 ```
@@
 
-knitr::include_graphics("./Figures/Figure3_workflow.png")
+knitr::include_graphics("./Figures/Low_res/Figure3_workflow.png")
 
@@
 
-knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_Low_Pred.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png")
 
@@
 
-knitr::include_graphics("./Figures/Maps Pred/FigX-Gaf_High_Pred.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")
 
@@
 
-knitr::include_graphics("./Figures/Maps Pred/FigX-Boat_Pred.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png")
 
@@
 
-knitr::include_graphics("./Figures/Maps Pred/FigX-Dike_Pred.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png")
 ```
@@
 
-knitr::include_graphics("./Figures/Validation/ConfusionMatrixGlobal.png")
+knitr::include_graphics("./Figures/Low_res/Validation/ConfusionMatrixGlobal.png")
 
@@
 
-knitr::include_graphics("Figures/VIP/Fig_VIP.png")
+knitr::include_graphics("Figures/Low_res/VIP/Fig_VIP.png")
 
@@
 
-knitr::include_graphics("Figures/Upscaling/density_vs_Proportion.png")
+knitr::include_graphics("Figures/Low_res/Upscaling/density_vs_Proportion.png")
 
@@
 
-knitr::include_graphics("./Figures/Disc_Pigment_Table.png")
+knitr::include_graphics("./Figures/Low_res/Disc_Pigment_Table.png")
 ```
@@
 
-knitr::include_graphics("./Figures/Validation/ConfusionMatrixGreen.png")
+knitr::include_graphics("./Figures/Low_res/Validation/ConfusionMatrixGreen.png")
 
@@
 
-knitr::include_graphics("./Figures/Compare_reflectance.png")
+knitr::include_graphics("./Figures/Low_res/Compare_reflectance.png")
 ```

### 2024-03-02 docs/_tex/index.tex
add disc
page layout

@@
 
-\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}
 
@@
 model. This methodology implies a consistency between the reflectance of
-both altitude.
-
-Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
-from a low-altitude flight and a high-altitude flight conducted over the
-same area. An apparent underestimation of reflectance values is observed
-in the high-altitude flight, particularly for higher values. Since both
-flights were conducted over vegetation areas, the highest reflectance
-values correspond to the infrared part of the spectrum. The disparity in
-infrared reflectance may stem from temporal differences between the
-flights, possibly resulting in a slightly drier intertidal area and
-consequently higher infrared reflectance. This disparity poses an issue
-for the methodology followed in the present study, relying solely on one
-flight height for training. To address this issue, we employed min/max
-standardized reflectance spectra as predictors for the model
-(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
-eliminate differences in the level of reflectance, focusing instead on
-the shape of the spectra. This is a key feature in building a model that
-can reliably predict vegetation across geographical sites and seasons.
-It enables consistent prediction of vegetation classes across variations
-in biomass and variability in light conditions \citetext{\citealp[
-]{fyfe2003spatial}; \citealp[
+both altitude. Figure~\ref{fig-CompareRef} depicts the relationship
+between reflectance from a low-altitude flight and a high-altitude
+flight conducted over the same area. An apparent underestimation of
+reflectance values is observed in the high-altitude flight, particularly
+for higher values. Since both flights were conducted over vegetation
+areas, the highest reflectance values correspond to the infrared part of
+the spectrum.
+
+The disparity in infrared reflectance may stem from temporal differences
+between the flights, possibly resulting in a slightly drier intertidal
+area and consequently higher infrared reflectance. This disparity poses
+an issue for the methodology followed in the present study, relying
+solely on one flight height for training. To address this issue, we
+employed min/max standardized reflectance spectra as predictors for the
+model (Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us
+to eliminate differences in the level of reflectance, focusing instead
+on the shape of the spectra. This is a key feature in building a model
+that can reliably predict vegetation across geographical sites and
+seasons. It enables consistent prediction of vegetation classes across
+variations in biomass and variability in light conditions
+\citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
 ]{COSTA2021107018}; \citealp{piaser2023impact}}.
 
+The Figure~\ref{fig-upscaling} demonstrates that a seagrass cover
+percentage of 90 \% is necessary for confident prediction of seagrass
+presence. This highlights a limitation of the methodology used to
+construct the training dataset for the model. The dataset was composed
+exclusively of pure pixels, which has resulted in the model's reduced
+confidence when faced with lower percentages of seagrass cover. This
+implies that outside of the biomass peak of seagrass this model should
+be less accurate. This needs to be futher investigated.
+
 \subsection{Big picture}\label{big-picture}
 
-\section{Conclusion}\label{conclusion}
-
-\renewcommand\refname{Bibliography}
+\renewcommand\refname{Conclusion}
   \bibliography{library.bib}

### 2024-03-02 index.qmd
add disc
page layout

@@
 #| label: fig-CompareRef
-#| fig-width: 5
-#| fig-height: 5
-#| out-width: "50%"
+#| fig-width: 10
+#| fig-height: 10
+#| out-width: "100%"
 
@@
 This methodology implies a consistency between the reflectance of both altitude.
-:::
-:::
-
 @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
@@
 Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
+:::
+:::
+
 The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
@@
 
+The @fig-upscaling demonstrates that a seagrass cover percentage of `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % is necessary for confident prediction of seagrass presence.
+This highlights a limitation of the methodology used to construct the training dataset for the model.
+The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
+This implies that outside of the biomass peak of seagrass this model should be less accurate.
+This needs to be futher investigated.
+
 ## Big picture
@@
 # Conclusion
-
-# Bibliography

### 2024-03-04 docs/_tex/index.tex
maj 0403

--- 2024-03-02 docs/_tex/index.tex
@@
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
-  pdfkeywords={Drone, Remote Sensing},
+  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
+Ecosystems, Neural Network},
   colorlinks=true,
@@
 \begin{keyword}
-    Drone \sep 
-    Remote Sensing
+    Drone \sep Remote Sensing \sep Seagrass \sep Coastal
+Ecosystems \sep 
+    Neural Network
 \end{keyword}
@@
 
-\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}
+\includegraphics[width=1\textwidth,height=\textheight]{index_files/figure-pdf/fig-CompareRef-1.pdf}
 
@@
 dashed line represents a linear model wheras the black dashed line
-represents a 1 to 1 relationship.}
+represents a 1 to 1 relationship. Left (A) plots RAW data and right (B)
+plots standardise data.}
 
@@
 model. This methodology implies a consistency between the reflectance of
-both altitude.
-
-Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
-from a low-altitude flight and a high-altitude flight conducted over the
-same area. An apparent underestimation of reflectance values is observed
-in the high-altitude flight, particularly for higher values. Since both
-flights were conducted over vegetation areas, the highest reflectance
-values correspond to the infrared part of the spectrum. The disparity in
-infrared reflectance may stem from temporal differences between the
-flights, possibly resulting in a slightly drier intertidal area and
-consequently higher infrared reflectance. This disparity poses an issue
-for the methodology followed in the present study, relying solely on one
-flight height for training. To address this issue, we employed min/max
-standardized reflectance spectra as predictors for the model
-(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
-eliminate differences in the level of reflectance, focusing instead on
-the shape of the spectra. This is a key feature in building a model that
-can reliably predict vegetation across geographical sites and seasons.
-It enables consistent prediction of vegetation classes across variations
-in biomass and variability in light conditions \citetext{\citealp[
+both altitude. Figure~\ref{fig-CompareRef} (A) depicts the relationship
+between reflectance from a low-altitude flight and a high-altitude
+flight conducted over the same area. An apparent underestimation of
+reflectance values is observed in the high-altitude flight, particularly
+for higher values. Since both flights were conducted over vegetation
+areas, the highest reflectance values correspond to the infrared part of
+the spectrum.
+
+The disparity in infrared reflectance may stem from temporal differences
+between the flights, possibly resulting in a slightly drier intertidal
+area and consequently higher infrared reflectance. This disparity poses
+an issue for the methodology followed in the present study, relying
+solely on one flight height for training. To address this issue, we
+employed min/max standardized reflectance spectra as predictors for the
+model (Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} (B) ;
+\citep{Cao2017}). This approach allows us to eliminate differences in
+the level of reflectance, focusing instead on the shape of the spectra.
+This is a key feature in building a model that can reliably predict
+vegetation across geographical sites and seasons. It enables consistent
+prediction of vegetation classes across variations in biomass and
+variability in light conditions \citetext{\citealp[
 ]{fyfe2003spatial}; \citealp[
@@
 
+The Figure~\ref{fig-upscaling} demonstrates that a seagrass cover
+percentage of 90 \% is necessary for confident prediction of seagrass
+presence. This highlights a limitation of the methodology used to
+construct the training dataset for the model. The dataset was composed
+exclusively of pure pixels, which has resulted in the model's reduced
+confidence when faced with lower percentages of seagrass cover.
+Intertidal seagrasses exhibit strong phenology, with varying pigment
+composition throughout the year\citetext{\citealp[
+]{bargain2013seasonal}; \citealp{legare2022remote}}. This suggests that
+outside of the biomass peak of seagrasses, this model may be less
+accurate. Further investigation is warranted to explore this aspect.
+
 \subsection{Big picture}\label{big-picture}
 
-\section{Conclusion}\label{conclusion}
-
-\renewcommand\refname{Bibliography}
+Climate change, global warming, alien and invasive species development,
+coastal erosion, sealevel rise, while further impact coastal ecosystems
+in the future \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
+]{holon2018predictive}; \citealp{marquet2024global}}. The demand for
+meaningful and efficient monitoring methods for these habitats has
+therefore never been greater \citetext{\citealp[
+]{muller2018satellite}; \citealp[
+]{villalobos2023remote}; \citealp{oiry2021using}}. Employing traditional
+sampling methods to monitor these ecosystems is time and
+resource-intensive, and the findings are often difficult to scale up.
+Earth observation methods can bridge this gap and meet the needs for
+monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
+The retrieval of Essential Biodiversity Variables (EBVs) and Essential
+Ocean Variables (EOVs) through satellite observations is increasingly
+common, enabling comprehensive monitoring of entire ecosystems over
+extended time periods \citetext{\citealp[
+]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}.
+
+\renewcommand\refname{Conclusion}
   \bibliography{library.bib}

### 2024-03-04 index.qmd
maj 0403

@@
   - Remote Sensing
+  - Seagrass
+  - Coastal Ecosystems
+  - Neural Network 
 abstract: |
@@
 citation:
-  container-title: Earth and Space Science
+  container-title: Remote Sensing of Environment
 number-sections: true
@@
 #| label: fig-map
-#| fig-width: 7
-#| fig-height: 7
+#| fig-width: 10
+#| fig-height: 10
 #| out-width: "100%"
@@
 
-::: columns
-::: column
-```{r Plot Reflectance_Validation 2 height}
+```{r}
 #| cache: false
@@
 The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship.
+Left (A) plots RAW data and right (B) plots standardise data.
 #| label: fig-CompareRef
 #| fig-width: 10
-#| fig-height: 10
+#| fig-height: 5
 #| out-width: "100%"
 
-# Pigment composition of the different vegetation classes.
-Green indicate the presence of the pigment in the class while red indicate the abscence.
-Chlb : Chlorophyll-b ; Chlc : Chlorophyll-c ; Fuco : Fucoxanthin ; Zea : Zeaxanthin ; Diad : Diadinoxanthin ; Lut : Lutein ; Neo : Neoxanthin ; PE : Phycoerythrin ; PC : Phycocyanin.
-
-knitr::include_graphics("./Figures/Low_res/Compare_reflectance.png")
+RAW <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+STD <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance_std.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+RAW+STD
+
 ```
-:::
-
-::: column
+
 In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
@@
 This methodology implies a consistency between the reflectance of both altitude.
-@fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
+@fig-CompareRef (A) depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
 An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values.
 Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
-:::
-:::
 
@@
 This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training.
-To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]).
+To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; @fig-CompareRef (B) ; [@Cao2017]).
 This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra.
@@
 The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
-This implies that outside of the biomass peak of seagrass this model should be less accurate.
-This needs to be futher investigated.
+Intertidal seagrasses exhibit strong phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
+This suggests that outside of the biomass peak of seagrasses, this model may be less accurate.
+Further investigation is warranted to explore this aspect.
 
@@
 
+Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, while further impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
+The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
+Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
+Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems.
+[@papathanasopoulou2019satellite].
+The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
+
 # Conclusion

### 2024-03-04 docs/_tex/index.tex
preprint warning

@@
 \hypersetup{
-  pdftitle={Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
+  pdftitle={PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
@@
 \begin{frontmatter}
-\title{Discriminating Seagrasses From Green Macroalgae in European
-Intertidal areas using high resolution multispectral drone imagery.}
+\title{PREPRINT -- Discriminating Seagrasses From Green Macroalgae in
+European Intertidal areas using high resolution multispectral drone
+imagery -- PREPRINT.}
 \author[1]{Simon Oiry%

### 2024-03-05 docs/_tex/index.tex
'disc

@@
 
-\subsection{Big picture}\label{big-picture}
+\subsection{Application of the model}\label{application-of-the-model}
 
@@
 extended time periods \citetext{\citealp[
-]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}.
+]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
+significance of monitoring waters, particularly in light of the Water
+Framework Directive (WFD ; \citep{directive2000eu}), cannot be
+overstated in environmental management and conservation efforts. The WFD
+mandates the achievement and maintenance of ``good ecological status''
+for all European waters, which necessitates a comprehensive
+understanding and monitoring of aquatic ecosystems, including coastal
+habitats like seagrass \citetext{\citealp[
+]{foden2007angiosperms}; \citealp[
+]{nordlund2024one}; \citealp{Zoffoli2021}}.
+
+Effective and efficient monitoring tools are essential for identifying
+the impacts of human activities and natural changes on these ecosystems.
+Drones, with their capability for high-resolution, multispectral
+imagery, provide a novel and powerful means to rapidly and accurately
+acquire ground truth data. This data is critical for calibrating and
+validating satellite remote sensing applications, thereby enhancing our
+capacity to monitor vast coastal areas systematically under the WFD
+framework. The integration of drone technology facilitates a scalable
+approach to environmental surveillance, offering significant
+advancements in the spatial and temporal resolution of data collection.
+This, in turn, supports the directive's objectives by enabling more
+informed and timely management decisions for the preservation and
+restoration of aquatic ecosystems.
 

### 2024-03-05 index.qmd
preprint warning
save0403
'disc

@@
 ---
-title: Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
+title: PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.
 author:
@@
 csl: RSE.csl
+
 ---
@@
 
-## Big picture
+## Application of the model
 
@@
 The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
+The significance of monitoring waters, particularly in light of the Water Framework Directive (WFD ; @directive2000eu), cannot be overstated in environmental management and conservation efforts.
+The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
+
+Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems.
+Drones, with their capability for high-resolution, multispectral imagery, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
+output of the model used in the present study).
+This data is critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework.
+The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
+This, in turn, supports the directive's objectives by enabling more informed and timely management decisions for the preservation and restoration of aquatic ecosystems.
 

### 2024-03-05 docs/_tex/index.tex
'disc

@@
 significance of monitoring waters, particularly in light of the Water
-Framework Directive (WFD ; \citep{directive2000eu}), cannot be
-overstated in environmental management and conservation efforts. The WFD
-mandates the achievement and maintenance of ``good ecological status''
-for all European waters, which necessitates a comprehensive
-understanding and monitoring of aquatic ecosystems, including coastal
-habitats like seagrass \citetext{\citealp[
-]{foden2007angiosperms}; \citealp[
+Framework Directive (WFD ; \citep{WFD2000}), cannot be overstated in
+environmental management and conservation efforts. The WFD mandates the
+achievement and maintenance of ``good ecological status'' for all
+European waters, which necessitates a comprehensive understanding and
+monitoring of aquatic ecosystems, including coastal habitats like
+seagrass \citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
 ]{nordlund2024one}; \citealp{Zoffoli2021}}.
@@
 imagery, provide a novel and powerful means to rapidly and accurately
-acquire ground truth data. This data is critical for calibrating and
-validating satellite remote sensing applications, thereby enhancing our
-capacity to monitor vast coastal areas systematically under the WFD
-framework. The integration of drone technology facilitates a scalable
-approach to environmental surveillance, offering significant
-advancements in the spatial and temporal resolution of data collection.
-This, in turn, supports the directive's objectives by enabling more
-informed and timely management decisions for the preservation and
-restoration of aquatic ecosystems.
+acquire ground truth data (i.e.~output of the model used in the present
+study). This data is critical for calibrating and validating satellite
+remote sensing applications, thereby enhancing our capacity to monitor
+vast coastal areas systematically under the WFD framework. The
+integration of drone technology facilitates a scalable approach to
+environmental surveillance, offering significant advancements in the
+spatial and temporal resolution of data collection. This, in turn,
+supports the directive's objectives by enabling more informed and timely
+management decisions for the preservation and restoration of aquatic
+ecosystems.
 

### 2024-03-05 index.qmd
'disc

@@
 The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
-The significance of monitoring waters, particularly in light of the Water Framework Directive (WFD ; @directive2000eu), cannot be overstated in environmental management and conservation efforts.
+The significance of monitoring waters, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
 The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].

### 2024-03-05 docs/_tex/index.tex
add conclusion

@@
 
-\renewcommand\refname{Conclusion}
+\section{Conclusion}\label{conclusion}
+
+The utilization of drone-based remote sensing coupled with machine
+learning techniques has proven to be an effective method for the
+discrimination of seagrasses and macroalgae in coastal ecosystems. This
+study has highlighted the potential for these technologies to enhance
+the accuracy and efficiency of habitat monitoring, which is essential
+for environmental management and conservation strategies. Through the
+application of high-resolution multispectral imagery, the research
+contributes to the broader understanding and surveillance of aquatic
+ecosystems, aligning with objectives outlined in policies such as the
+Water Framework Directive. The findings underscore the importance of
+adopting advanced remote sensing tools in ecological studies and
+environmental monitoring, providing a foundation for future research and
+policy implementation aimed at ecosystem preservation and restoration.
+
   \bibliography{library.bib}

### 2024-03-05 index.qmd
add conclusion

@@
 # Conclusion
+
+The utilization of drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses and macroalgae in coastal ecosystems.
+This study has highlighted the potential for these technologies to enhance the accuracy and efficiency of habitat monitoring, which is essential for environmental management and conservation strategies.
+Through the application of high-resolution multispectral imagery, the research contributes to the broader understanding and surveillance of aquatic ecosystems, aligning with objectives outlined in policies such as the Water Framework Directive.
+The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem preservation and restoration.

### 2024-03-06 docs/_tex/index.tex
short disc

@@
 
-The primary objective of this study was to develop a method for the
-accurate classification of macrophytes on intertidal mudflats,
-specifically focusing on distinguishing between Chlorophyceae (green
-algae) and marine Magnoliopsida (seagrasses) using multispectral drone
-data. The challenge arises from the shared pigment composition between
-these two vegetation classes, complicating their differentiation using
-remote sensing techniques. This challenge has been addressed through the
-utilization of high-resolution drone flights allowing a precise
-photointerpretation of pure pixels of the different vegetation classes
-used as training data, providing a robust foundation for subsequent
-classification analyses. In achieving 94.26 accuracy across all study
-sites, this method demonstrates its efficacy in accurately classifying
-macrophytes, thus offering a reliable approach for vegetation
-classification in intertidal mudflats using remote sensing data.
-
 \subsection{Vegetation Discrimination}\label{vegetation-discrimination}
@@
 
-The discrimination of seagrasses from green macroalgae presents
+The primary objective of this study was to develop a method for the
+accurate classification of macrophytes on intertidal mudflats,
+specifically focusing on distinguishing between Chlorophyceae (green
+algae) and marine Magnoliopsida (seagrasses) using multispectral drone
+data. The discrimination of seagrasses from green macroalgae presents
 significant challenges, primarily due to the shared pigment composition

### 2024-03-06 index.qmd
short disc

@@
 # Discussion
-
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The challenge arises from the shared pigment composition between these two vegetation classes, complicating their differentiation using remote sensing techniques.
-This challenge has been addressed through the utilization of high-resolution drone flights allowing a precise photointerpretation of pure pixels of the different vegetation classes used as training data, providing a robust foundation for subsequent classification analyses.
-In achieving `r round(validation_metrics$overall[[1]]*100,2)` accuracy across all study sites, this method demonstrates its efficacy in accurately classifying macrophytes, thus offering a reliable approach for vegetation classification in intertidal mudflats using remote sensing data.
-
 ## Vegetation Discrimination
@@
 
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
 The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.

### 2024-03-06 docs/_tex/index.tex
mistakes correction

@@
 
-Coastal areas are vital hotshots for marine biodiversity, with
+Coastal areas are vital hotspots for marine biodiversity, with
 intertidal seagrass meadows playing a crucial role at the interface
@@
 myriad of ecosystem services to humanity, including carbon
-sequestration, oxygen production,protection against sea-level rise and
+sequestration, oxygen production, protection against sea-level rise and
 coastline erosion, and limitation of eutrophication. They serve as vital
@@
 processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
-Coastal eutrophication has been associated to anomalous accumulation of
-green macroalgae, the so-called green tides (\citep{devlin2023nutrients}
-; \citep{devlin2023nutrients}). Green tides produce shade and
-suffication over seagrass individuals, thus threatening the health of
-seagrass ecosystems \citep{wang2022}.
+Coastal eutrophication has been ass ociated to anomalous accumulation of
+green macroalgae, the so-called green tides
+(\citep{devlin2023nutrients}). Green tides produce shade and suffocation
+over seagrass individuals, thus threatening the health of seagrass
+ecosystems \citep{wang2022}.
 
@@
 Variable (EBVs) such as seagrass taxonomic diversity, species
-distribution, populuation abundance, and phenology \citep{Pereira2013}.
+distribution, population abundance, and phenology \citep{Pereira2013}.
 Seagrass monitoring is all the more important as it makes possible to
@@
 effective mitigation actions. Traditionally, indicators of seagrass
-status have been quantified using in situ measurements. The acquisition
+status have been quantified using in situ measurments. The acquisition
 of field data in intertidal zones is however notoriously challenging.
@@
 machine-learning algorithms trained with a large hyperspectral library
-of more then 300 field reflectance measurements, \citep{Davies2023}
+of more then 300 field reflectance measurments, \citep{Davies2023}
 demonstrated that it was possible to discriminate Magnoliopsida from
@@
 
-Drone can potentially fill the gaps left by satellite remote sensing and
-in situ measurments, due to their ability to provide spatially-explicit
-observations at very high spatial resolutions (pixel size from cm to mm)
-and still capturing data at multi-spectral resolution
-\citetext{\citealp[ ]{fairley2022drone}; \citealp{oh2017use}}. The
-versatility of drones allows for their application across a diverse
-thematic range , from coastal zone management \citetext{\citealp[
-]{adade2021}; \citealp[ ]{casella2020}; \citealp{angnuureng2022}} to
-mapping species distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
+Drones can potentially fill the gaps left by satellite remote sensing
+and in situ measurments, due to their ability to provide
+spatially-explicit observations at very high spatial resolutions (pixel
+size from cm to mm) and still capturing data at multi-spectral
+resolution \citetext{\citealp[
+]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
+allows for their application across a diverse thematic range , from
+coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
+]{casella2020}; \citealp{angnuureng2022}} to mapping species
+distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
 ]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[
 ]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
-to coastal habitat mapping, most sutdy cases were limited to a single
+to coastal habitat mapping, most study cases were limited to a single
 flight, restricting the generalizability of their application over wider
@@
 located in Gulf of Morbihan (Figure~\ref{fig-map} A), France (47.5791°N,
-2.8018°W). This gulf covers an area of 115 km² and is only connect to
+2.8018°W). This gulf covers an area of 115 km² and is only connected to
 the sea through a 900m wide channel. A total of 53 small islands are
@@
 of Morbihan we have chosen two sites : one is located in one of these
-island (Arz island); the other one is located in the sourthern part of
+island (Arz island); the other one is located in the southern part of
 the gulf (Duer). Two others sites are located in Bourgneuf Bay, France
@@
 conditions between flight lines. A side overlap of 70\% and a front
-overlap of 80\% between each imagewas set for each flight. A downwelling
-light sensor (DLS2) was used to acquire irradiance data concomitantly
-with the camera measurements. Raw data were calibrated in reflectance
-using a calibration panel reflective at \textasciitilde50\% provided by
-the manufacturer. A structure-from-motion photogrammetry software
-(Agisoft Metashape) was used to process images to obtain multispectral
-orthomosaics of each flight. The workflow for orthomosaicking was the
-same for every flight. First, tying key points were detected inside of
-each image and between overlapping images in order to obtain a sparse
-point cloud. This cloud was cleaned using reprojection accuracy metric
-in order to remove noisy points. A dense point cloud was then produced
-using a structure from motion algorithm. A surface interpolation of this
-dense point cloud was made to obtain a digital surface model (DSM), used
-to reconstruct the multispectral ortho-image. Across all sites, flights
-were made at two different altitudes : 12 m or/and 120 m. Low altitude
-drone flights produce ortho-images with a very high spatial resolution
-(8 mm per pixel), making it simple to visually distinguish between the
-various types of vegetation. High altitude fights on the other hand
-allow to cover large areas and produced images with a pixel size of 80
-mm (Table 1).
+overlap of 80\% between each image was set for each flight. A
+downwelling light sensor (DLS2) was used to acquire irradiance data
+concomitantly with the camera measurements. Raw data were calibrated in
+reflectance using a calibration panel reflective at \textasciitilde50\%
+provided by the manufacturer. A structure-from-motion photogrammetry
+software (Agisoft Metashape) was used to process images to obtain
+multispectral orthomosaics of each flight. The workflow for
+orthomosaicking was the same for every flight. First, tying key points
+were detected inside of each image and between overlapping images in
+order to obtain a sparse point cloud. This cloud was cleaned using
+reprojection accuracy metric in order to remove noisy points. A dense
+point cloud was then produced using a structure from motion algorithm. A
+surface interpolation of this dense point cloud was made to obtain a
+digital surface model (DSM), used to reconstruct the multispectral
+ortho-image. Across all sites, flights were made at two different
+altitudes : 12 m or/and 120 m. Low altitude drone flights produce
+ortho-images with a very high spatial resolution (8 mm per pixel),
+making it simple to visually distinguish between the various types of
+vegetation. High altitude fights on the other hand allow to cover large
+areas and produced images with a pixel size of 80 mm (Table 1).
 
@@
 vertical accuracy of 10cm. dGPS was also used to georeference quadrats
-of 0.25cm² used to assess the presence or absence of 5 key classes of
+of 0.25 m² used to assess the presence or absence of 5 key classes of
 vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm
@@
 (red algae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
-uploaded on the online on the Global Biodiversity Information Facility
-(GBIF) platform \citep{BedeGbif}, a public open portal to store and
-share biodiversity data. Each photograph was also processed to estimate
-the percent cover of each type of vegetation using an image processing
+uploaded online on the Global Biodiversity Information Facility (GBIF)
+platform \citep{BedeGbif}, a public open portal to store and share
+biodiversity data. Each photograph was also processed to estimate the
+percent cover of each type of vegetation using an image processing
 software (imageJ). For all quadrat, the hyperspectral reflectance
@@
 right plot shows the drone standardised reflectance spectra of each
-class.}
+class. Each slice represent the VIP of both RAW and standardised
+reflectance combined.}
 
@@
 algae) and marine Magnoliopsida (seagrasses) using multispectral drone
-data. The discrimination of seagrasses from green macroalgae presents
-significant challenges, primarily due to the shared pigment composition
-between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
-frequent spatial mixing of these green macrophytes. This similarity in
-pigment composition, including photosynthetic and carotenoid pigments
-like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
-spectral signatures that are often indistinguishable to non exper eyes.
-This spectral overlap is further complicated by the intermingling of
-seagrasses and green macroalgae in the same spatial locations, posing a
-significant challenge for remote sensing aimed at accurately mapping and
-monitoring coastal ecosystems. Our study addresses these complexities by
-utilizing high-resolution drone imagery with 10 spectral bands.
-\citep{Davies2023} has shown that having at least 8 spectral bands
-ranging between 500 nm to 850 nm with including a band at 530 nm and
-another one at 730 nm is crucial to accurately discriminate green
-macrophytes.
+data. The ability to differentiate between various types of vegetation,
+as demonstrated in this study, plays a critical role in ecological
+monitoring and management. By distinguishing between seagrasses and
+macroalgae, our approach facilitates targeted conservation strategies,
+enabling more effective preservation and restoration efforts in coastal
+ecosystems. The discrimination of seagrasses from green macroalgae
+presents significant challenges, primarily due to the shared pigment
+composition between these taxa, as depicted in Figure~\ref{fig-Pigm} but
+also by the frequent spatial mixing of these green macrophytes. This
+similarity in pigment composition, including photosynthetic and
+carotenoid pigments like chlorophyll b and c, fucoxanthin, and
+neoxanthin, results in spectral signatures that are often
+indistinguishable to non exper eyes. This spectral overlap is further
+complicated by the intermingling of seagrasses and green macroalgae in
+the same spatial locations, posing a significant challenge for remote
+sensing aimed at accurately mapping and monitoring coastal ecosystems.
+Our study addresses these complexities by utilizing high-resolution
+drone imagery with 10 spectral bands. \citep{Davies2023} has shown that
+having at least 8 spectral bands ranging between 500 nm to 850 nm with
+including a band at 530 nm and another one at 730 nm is crucial to
+accurately discriminate green macrophytes.
 
@@
 ]{muller2018satellite}; \citealp[
-]{villalobos2023remote}; \citealp{oiry2021using}}. Employing traditional
-sampling methods to monitor these ecosystems is time and
-resource-intensive, and the findings are often difficult to scale up.
-Earth observation methods can bridge this gap and meet the needs for
-monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
-The retrieval of Essential Biodiversity Variables (EBVs) and Essential
-Ocean Variables (EOVs) through satellite observations is increasingly
-common, enabling comprehensive monitoring of entire ecosystems over
-extended time periods \citetext{\citealp[
+]{villalobos2023remote}; \citealp{oiry2021using}}. Our findings,
+particularly the improved discrimination of vegetation types, underscore
+the potential of drone-based remote sensing to support diverse
+applications, from biodiversity conservation to climate change
+adaptation strategies\textbf{.} Employing traditional sampling methods
+to monitor these ecosystems is time and resource-intensive, and the
+findings are often difficult to scale up. Earth observation methods can
+bridge this gap and meet the needs for monitoring coastal ecosystems.
+\citep{papathanasopoulou2019satellite}. The retrieval of Essential
+Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs)
+through satellite observations is increasingly common, enabling
+comprehensive monitoring of entire ecosystems over extended time periods
+\citetext{\citealp[
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The

### 2024-03-06 index.qmd
mistakes correction

@@
 csl: RSE.csl
-
 ---
@@
 
-Coastal areas are vital hotshots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
-Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production,protection against sea-level rise and coastline erosion, and limitation of eutrophication.
+Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
+Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and limitation of eutrophication.
 They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019].
@@
 While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been associated to anomalous accumulation of green macroalgae, the so-called green tides (@devlin2023nutrients ; @devlin2023nutrients).
-Green tides produce shade and suffication over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
-
-The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, populuation abundance, and phenology [@Pereira2013].
+Coastal eutrophication has been ass ociated to anomalous accumulation of green macroalgae, the so-called green tides (@devlin2023nutrients).
+Green tides produce shade and suffocation over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
+
+The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, population abundance, and phenology [@Pereira2013].
 Seagrass monitoring is all the more important as it makes possible to identify which pressure should be addressed in priority to facilitate effective mitigation actions.
-Traditionally, indicators of seagrass status have been quantified using in situ measurements.
+Traditionally, indicators of seagrass status have been quantified using in situ measurments.
 The acquisition of field data in intertidal zones is however notoriously challenging.
@@
 As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022].
-Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance measurements, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance measurments, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
 The application of this approach to satellite remote sensing remains however to be validated.
@@
 
-Drone can potentially fill the gaps left by satellite remote sensing and in situ measurments, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+Drones can potentially fill the gaps left by satellite remote sensing and in situ measurments, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
-However, when applied to coastal habitat mapping, most sutdy cases were limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+However, when applied to coastal habitat mapping, most study cases were limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
 The present study aimed at analyzing the potential of multispectral drone remote sensing to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
@@
 Two sites are located in Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
-This gulf covers an area of 115 km² and is only connect to the sea through a 900m wide channel.
+This gulf covers an area of 115 km² and is only connected to the sea through a 900m wide channel.
 A total of 53 small islands are scattered across the gulf leading to 250 km of shorelines.
 Patchy seagrass meadows can be found on a lot of these islands.
-Within the Gulf of Morbihan we have chosen two sites : one is located in one of these island (Arz island); the other one is located in the sourthern part of the gulf (Duer).
+Within the Gulf of Morbihan we have chosen two sites : one is located in one of these island (Arz island); the other one is located in the southern part of the gulf (Duer).
 Two others sites are located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
@@
 An angle of 90° was maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
-A side overlap of 70% and a front overlap of 80% between each imagewas set for each flight.
+A side overlap of 70% and a front overlap of 80% between each image was set for each flight.
 A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements.
@@
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25cm² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (brown algae), Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae (red algae) (@fig-vegetation).
-Pictures of each quadrat were uploaded on the online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
+dGPS was also used to georeference quadrats of 0.25 m² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (brown algae), Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae (red algae) (@fig-vegetation).
+Pictures of each quadrat were uploaded online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
 Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software (imageJ).
@@
 The bottom right plot shows the drone standardised reflectance spectra of each class.
+Each slice represent the VIP of both RAW and standardised reflectance combined.
 #| label: fig-VIP
@@
 # Discussion
+
 ## Vegetation Discrimination
@@
 The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and management.
+By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
 The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
@@
 The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
+Our findings, particularly the improved discrimination of vegetation types, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies**.** Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
 Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems.

### 2024-03-06 index.qmd
mistakes correction

@@
 #| label: fig-map
-#| fig-width: 10
-#| fig-height: 10
 #| out-width: "100%"
@@
 #| label: fig-vegetation
-#| fig-width: 10
-#| fig-height: 7
 #| out-width: "100%"

### 2024-03-08 docs/_tex/index.tex
first part of Laurent's comments

@@
 making it difficult to discriminate seagrass from other macrophytes in
-highly heterogenous meadows. To address these challenges, drone images
-acquired with multi-spectral sensors offer a promising solution. This
-study focuses on using drones acquisitions for mapping intertidal
-macrophytes, effectively discriminating between seagrass and green
-macroalgae. Ten drone flights were conducted at two different altitudes
-(12m and 120m) across diverse European habitats in France and Portugal.
-Low altitude flights were used to train a Deep Learning classifier based
-on Neural Networks to discrimintate among 5 intertidal vegetation
-classes. Drone mapping demonstrated an overall accuracy of 94\% across
+highly heterogenous meadows. To address these challenges and reduce the
+issue of mlixed pixel, drone images at a very high spatial resolution
+offer a promising solution. This study focuses on using drone
+acquisitions with a ten spectral bands sensor mirroring those of
+Sentinel-2, for mapping intertidal macrophytes and effectively
+discriminating between seagrass and green macroalgae. Nine drone flights
+were conducted at two different altitudes (12m and 120m) across diverse
+European habitats in France and Portugal. Low altitude flights were used
+to train a Deep Learning classifier based on Neural Networks to
+discrimintate among five taxonomic classes of intertidal vegetation:
+Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae
+(Brown algae), Rhodophyceae (Red macroalgae) and Bacillariophyceae
+(Diatoms). Drone mapping demonstrated an overall accuracy of 94\% across
 all the sites and images, covering a total area of 467 000 m². The model
-exhibited an accuracy of 96.4\% in identifying seagrass.
+exhibited an accuracy of 96.4\% in identifying seagrass. This work
+showed that although they share the same pigmentary composition,
+seagrass and green algae can be discriminated using ten bands
+multispectral sensor. The algorithm should now be adapted for Sentinel-2
+to see if this discrimination is still operational at a coarser spatial
+resolution.
 \end{abstract}
@@
 effective mitigation actions. Traditionally, indicators of seagrass
-status have been quantified using in situ measurments. The acquisition
-of field data in intertidal zones is however notoriously challenging.
-Intertidal seagrass meadows are only partially exposed during low tide
-and can be situated in difficult-to-reach mudflats, potentially leading
-to inaccurate and limited estimations with conventional sampling
-techniques \citep{nijland2019}. Satellite observations have been proven
-effective in complementing in situ sampling, allowing for the near
-real-time and consistent retrieval of seagrass EOVs and EBVs over
-extensive meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
-]{xu2021}; \citealp[ ]{Traganos2018}; \citealp{coffer2023}}
+status have been quantified using \emph{in situ} measurements. The
+acquisition of field data in intertidal zones is however notoriously
+challenging. Intertidal seagrass meadows are only partially exposed
+during low tide and can be situated in difficult-to-reach mudflats,
+potentially leading to inaccurate and limited estimations with
+conventional sampling techniques \citep{nijland2019}. Satellite
+observations have been proven effective in complementing in situ
+sampling, allowing for the near real-time and consistent retrieval of
+seagrass EOVs and EBVs over extensive meadows. \citetext{\citealp[
+]{Zoffoli2021}; \citealp[ ]{xu2021}; \citealp[
+]{Traganos2018}; \citealp{coffer2023}}
 
@@
 machine-learning algorithms trained with a large hyperspectral library
-of more then 300 field reflectance measurments, \citep{Davies2023}
+of more then 300 field reflectance spectra, \citep{Davies2023}
 demonstrated that it was possible to discriminate Magnoliopsida from
@@
 Drones can potentially fill the gaps left by satellite remote sensing
-and in situ measurments, due to their ability to provide
+and in situ measurements, due to their ability to provide
 spatially-explicit observations at very high spatial resolutions (pixel
@@
 Portugal), covering a wide range of habitats, from monospecific seagrass
-meadows to meadows mixed with green or red algae. A deep learning
+meadows to meadows mixed with green, or red macroalgae. A deep learning
 algorithm was trained and validated for macrophyte discrimination,
@@
 the gulf (Duer). Two others sites are located in Bourgneuf Bay, France
-(46.9849°N, 2.1488°W). This bay is a semi-enclosed macrotidal bay,
+(46.9849°N, 2.1488°W). This bay is 340 km² semi-enclosed macrotidal bay,
 protected from waves by Noirmoutier Island. Bougneuf bay hosts a large
@@
 more diverse intertidal vegetation, where patches of seagrass could
-intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae),
-and green algae (Chlorophyceae).
+intermingle with red, brown and green macroalgae.
 
@@
 
-\caption{\label{fig-map}Sites observed by drone. A: Gulf of Morbihan, B:
-Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent
-terrestrial areas whereas darkgreen represent intertidal areas.}
+\caption{\label{fig-map}Location of drone flights in France and
+Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
+C: Ria de Aveiro Lagoon (Three sites). Green represent intertidal
+areas.}
 
@@
 Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
-million pixel reflectance photographs in 10 spectral bands, from 444 nm
+million pixel reflectance photographs in ten spectral bands, from 444 nm
 (blue) to 840 nm (near infrared, NIR). An angle of 90° was maintained
@@
 ortho-images with a very high spatial resolution (8 mm per pixel),
-making it simple to visually distinguish between the various types of
+making it efficient to visually distinguish between the various types of
 vegetation. High altitude fights on the other hand allow to cover large
-areas and produced images with a pixel size of 80 mm (Table 1).
+areas and produced images with a pixel size of 80 mm
+(Table~\ref{tbl-flights}).
 
@@
 \begin{longtable}[c]{ccccc}
-\caption{List of drone flight, summarising the date, the altitude and the purpose
-of each flight.}\tabularnewline
+
+\caption{\label{tbl-flights}List of drone flight, summarising the date,
+the altitude and the purpose of each flight. 12 m and 120 m flights have
+a spatial resolution of 8 and 80 mm respectively.}
+
+\tabularnewline
 
@@
 
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{\multirow[c]{-3}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Morbihan}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
+\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{\multirow[c]{-3}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gulf\ of\ Morbihan}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
 
@@
 vertical accuracy of 10cm. dGPS was also used to georeference quadrats
-of 0.25 m² used to assess the presence or absence of 5 key classes of
-vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm
-over the sediment during low tide), Phaeophyceae (brown algae),
-Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae
-(red algae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
-uploaded online on the Global Biodiversity Information Facility (GBIF)
-platform \citep{BedeGbif}, a public open portal to store and share
-biodiversity data. Each photograph was also processed to estimate the
-percent cover of each type of vegetation using an image processing
-software (imageJ). For all quadrat, the hyperspectral reflectance
-signatures of each vegetation class was measured using an ASD FieldSpec
-HandHeld 2 spectroradiometer, which acquires reflectance between 325 and
-1075 nm, with 1 nm of spectral resolution. The methodological scheme
-followed in this study is presented in Figure~\ref{fig-workflow}.
+of 0.25 m² assessing the presence or absence of five key taxonomic
+classes of intertidal vegetation : Bacillariophyceae (Unicellular
+benthic diatoms forming large biofilms at the sediment surface during
+low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass),
+Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae)
+(Figure~\ref{fig-vegetation}). Pictures of each quadrat were uploaded
+online on the Global Biodiversity Information Facility (GBIF) platform
+\citep{BedeGbif}, a public open portal to store and share biodiversity
+data. Each photograph was also processed to estimate the percent cover
+of each type of vegetation using an image processing software (imageJ).
+For all quadrats, the hyperspectral reflectance signatures of each
+vegetation class was measured using an ASD FieldSpec HandHeld 2
+spectroradiometer, which acquires reflectance between 325 and 1075 nm,
+with 1 nm of spectral resolution. Hyperspectral signatures from quadrats
+serve dual purposes: they validate the radiometric calibration of drone
+data and contribute to error reduction in photo interpretation. The
+workflow developped in this study is presented in
+Figure~\ref{fig-workflow}.
 
@@
 
-\caption{\label{fig-vegetation}Class of vegetation used to train the
-Neural Network model and their standardised spectral signature}
+\caption{\label{fig-vegetation}The five taxonomic classes of vegetation
+used to train the Neural Network model and their raw spectral signatures
+at the spectral resolution of the Micasense RedEdge Dual MX.}
 
@@
 into two distinct parts based on the spatial resolution of the drone
-flights: high-resolution flights were utilized for training and
-prediction of the Neural Network model, whereas low-resolution flights
-were solely employed for prediction purposes.}
+flights: high-resolution flights (pixel size: 8 mm) were utilized for
+training and prediction of the Neural Network model, whereas
+lower-resolution flights (pixel size: 80 mm) were solely employed for
+prediction purposes. Validation has been performed on both high and low
+resolution flights.}
 
@@
 \begin{longtable}[c]{ccc}
-\caption{Vegetation Classes of the model and the number of pixels used to train
-and validate each class}\tabularnewline
+
+\caption{\label{tbl-validationPX}Vegetation Classes of the model and the
+number of pixels used to train and validate each class}
+
+\tabularnewline
 
@@
 
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Rhodophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5,771}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Rhodophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5,771}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,515,421}}} \\
 
@@
 built to train a Neural Network model with 2 hidden layers. The training
-pixels were categorized into 7 different classes, representing the
+pixels were categorized into seven different classes, representing the
 various habitats encountered at the different study sites: Sediment,
 Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
-Rhodophyceae. Only low-altitude flights (Table 1) were used for training
-purposes because their 8 mm spatial resolution allowied to avoid
-spectral sub-pixel mixing and to accurately differentiate various
+Rhodophyceae. Only low-altitude flights (Table~\ref{tbl-flights}) were
+used for training because their 8 mm spatial resolution allowied to
+avoid spectral sub-pixel mixing and to accurately differentiate
 vegetation classes. More than 418,000 pixels at 8 mm resolution from the
-3 training flights were used to train the model (Table 2). Twenty one
-variables were used by the model as predictors: 10 raw spectral bands of
-the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm
-to 840 nm), the same 10 spectral bands standardized using a min/max
-transformation (Equation~\ref{eq-std} ; \citep{Cao2017}) and the
-Normalized difference vegetation index (NDVI, Equation~\ref{eq-ndvi}).
-Standardisation of spectral bands is used to eliminate the scaling
-differences between spectra and to limit the effect of biomass on the
-shape of the spectra \citetext{\citealp[
-]{Douay2022}; \citealp{Davies2023}}.
+3 training flights were used to train the model
+(Table~\ref{tbl-validationPX}). Twenty one variables were used by the
+model as predictors: the ten raw spectral bands of the Micasense RedEdge
+Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same
+ten spectral bands standardized using a min/max transformation
+(Equation~\ref{eq-std} ; \citep{Cao2017}) and the Normalized difference
+vegetation index (NDVI, Equation~\ref{eq-ndvi}). Standardisation of
+spectral bands is used to eliminate the scaling differences between
+spectra and to limit the effect of biomass on the shape of the spectra
+\citetext{\citealp[ ]{Douay2022}; \citealp{Davies2023}}.
 
@@
 \subsubsection{Validation}\label{validation}
+
+The workflow of this study revolves around two distinct flight heights
+(12 m and 120 m, Figure~\ref{fig-workflow}) where ensuring consistency
+between reflectances at both heights is crucial. This comparison was
+conducted at sites where low and high altitude flights overlapped. The
+low altitude flights were resampled to the same spatial resolution and
+grid as the high flights using a median resampling method. Reflectance
+values were then extracted, and a scatterplot was generated.
+Subsequently, the slope of the linear model and the coefficient of
+determination (R²) were computed.
 

### 2024-03-08 index.qmd
first part of Laurent's comments

@@
 Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
-To address these challenges, drone images acquired with multi-spectral sensors offer a promising solution.
-This study focuses on using drones acquisitions for mapping intertidal macrophytes, effectively discriminating between seagrass and green macroalgae.
-Ten drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal.
-Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among 5 intertidal vegetation classes.
+To address these challenges and reduce the issue of mlixed pixel, drone images at a very high spatial resolution offer a promising solution.
+This study focuses on using drone acquisitions with a ten spectral bands sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
+Nine drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal.
+Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and Bacillariophyceae (Diatoms).
 Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
 The model exhibited an accuracy of 96.4% in identifying seagrass.
+This work showed that although they share the same pigmentary composition, seagrass and green algae can be discriminated using ten bands multispectral sensor.
+The algorithm should now be adapted for Sentinel-2 to see if this discrimination is still operational at a coarser spatial resolution.
 plain-language-summary: |
@@
 Seagrass monitoring is all the more important as it makes possible to identify which pressure should be addressed in priority to facilitate effective mitigation actions.
-Traditionally, indicators of seagrass status have been quantified using in situ measurments.
+Traditionally, indicators of seagrass status have been quantified using *in situ* measurements.
 The acquisition of field data in intertidal zones is however notoriously challenging.
@@
 As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022].
-Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance measurments, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
 The application of this approach to satellite remote sensing remains however to be validated.
@@
 
-Drones can potentially fill the gaps left by satellite remote sensing and in situ measurments, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+Drones can potentially fill the gaps left by satellite remote sensing and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
@@
 The present study aimed at analyzing the potential of multispectral drone remote sensing to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
-Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green or red algae.
+Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
@@
 Two others sites are located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
-This bay is a semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
+This bay is 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
 Bougneuf bay hosts a large intertidal seagrass meadow of about 6 km².
@@
 The southernmost site (Gafanha) is a mudflat located in an affluent of the lagoon whereas the two other sites are situated in the middle of the lagoon and are only accessible by boat (@fig-map C).
-These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass could intermingle with red algae (Rhodophyceae), brown algae (Phaeophyceae), and green algae (Chlorophyceae).
+These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass could intermingle with red, brown and green macroalgae.
 
@@
 #| fig-cap: >
-#|   Sites observed by drone. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent terrestrial areas whereas darkgreen represent intertidal areas. 
+#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Lagoon (Three sites). Green represent intertidal areas. 
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in 10 spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
 An angle of 90° was maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
@@
 Across all sites, flights were made at two different altitudes : 12 m or/and 120 m.
-Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it simple to visually distinguish between the various types of vegetation.
-High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (Table 1).
+Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
+High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
 
@@
 #| warning: false
-#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight.
+#| label: tbl-flights
+#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
 #| cache: true
@@
   Site = c(
-    rep("Morbihan",3),
+    rep("Gulf of Morbihan",3),
     rep("Bourgneuf Bay",2),
@@
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25 m² used to assess the presence or absence of 5 key classes of vegetation : Bacillariophyceae (Benthic diatoms forming large biofilm over the sediment during low tide), Phaeophyceae (brown algae), Magnoliopsida (seagrass), Chlorophyceae (green algae) and Rhodophyceae (red algae) (@fig-vegetation).
+dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming large biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
 Pictures of each quadrat were uploaded online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
 Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software (imageJ).
-For all quadrat, the hyperspectral reflectance signatures of each vegetation class was measured using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
-The methodological scheme followed in this study is presented in @fig-workflow.
+For all quadrats, the hyperspectral reflectance signatures of each vegetation class was measured using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
+Hyperspectral signatures from quadrats serve dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
+The workflow developped in this study is presented in @fig-workflow.
 
@@
 #| warning: false
-#| fig-cap: Class of vegetation used to train the Neural Network model and their standardised spectral signature
+#| fig-cap: The five taxonomic classes of vegetation used to train the Neural Network model and their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX. 
 #| label: fig-vegetation
@@
 Diamonds represent input or output data, and rectangles represent Python processing algorithms.
-The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights were utilized for training and prediction of the Neural Network model, whereas low-resolution flights were solely employed for prediction purposes."
+The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights (pixel size: 8 mm) were utilized for training and prediction of the Neural Network model, whereas lower-resolution flights (pixel size: 80 mm) were solely employed for prediction purposes.
+Validation has been performed on both high and low resolution flights."
 #| label: fig-workflow
@@
                           True == "Microphytobenthos" ~ "Bacillariophyceae",
-                          True == "Rhodophyceae" ~ "Rhodophyceae",
+                          True == "Rodophyceae" ~ "Rhodophyceae",
                           True == "Pheophyceae" ~ "Phaeophyceae",
@@
 #| tbl-cap: Vegetation Classes of the model and the number of pixels used to train and validate each class
+#| label: tbl-validationPX
 #| cache: true
@@
 A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model with 2 hidden layers.
-The training pixels were categorized into 7 different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (Table 1) were used for training purposes because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately differentiate various vegetation classes.
-More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (Table 2).
-Twenty one variables were used by the model as predictors: 10 raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same 10 spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
+The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
+Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately differentiate vegetation classes.
+More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
+Twenty one variables were used by the model as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
 Standardisation of spectral bands is used to eliminate the scaling differences between spectra and to limit the effect of biomass on the shape of the spectra [@Douay2022 ; @Davies2023].
@@
 ```
+
+The workflow of this study revolves around two distinct flight heights (12 m and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
+This comparison was conducted at sites where low and high altitude flights overlapped.
+The low altitude flights were resampled to the same spatial resolution and grid as the high flights using a median resampling method.
+Reflectance values were then extracted, and a scatterplot was generated.
+Subsequently, the slope of the linear model and the coefficient of determination (R²) were computed.
 

### 2024-03-08 docs/_tex/index.tex
first part of Laurent's comments

@@
 
-\usepackage{fontspec}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\newlength\Oldarrayrulewidth
-\newlength\Oldtabcolsep
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{wrapfig}
 \makeatletter
@@
 
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{0pt}
-
-\renewcommand*{\arraystretch}{1.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[c]{ccccc}
+\begin{table}
 
@@
 
-\tabularnewline
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\
-
-\ascline{1.5pt}{000000}{1-5}\endfirsthead
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\
-
-\ascline{1.5pt}{000000}{1-5}\endhead
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Arz\ Island}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{\multirow[c]{-3}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gulf\ of\ Morbihan}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{666666}{2-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Barbâtre}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{\multirow[c]{-5}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{France}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-2}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bourgneuf\ Bay}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{L'Epine}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{000000}{1-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Inner\ Lagoon}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Mataducos}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\
-
-\ascline{1.5pt}{BEBEBE}{3-5}
-
-\multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Portugal}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Aveiro\ Lagoon}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\
-
-\ascline{1.5pt}{000000}{1-5}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
+\centering{
+
+\includegraphics[width=6.63in,height=\textheight]{Figures/table_flights.png}
+
+}
+
+\end{table}%
 
@@
 
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{0pt}
-
-\renewcommand*{\arraystretch}{1.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[c]{ccc}
+\begin{table}
 
@@
 
-\tabularnewline
-
-\ascline{1.5pt}{666666}{1-3}
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\
-
-\ascline{1.5pt}{666666}{1-3}\endfirsthead
-
-\ascline{1.5pt}{666666}{1-3}
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\
-
-\ascline{1.5pt}{666666}{1-3}\endhead
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bacillariophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4,475}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,371,920}}} \\
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Chlorophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17,140}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{6,258,737}}} \\
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Magnoliopsida}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{221,065}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{69,079,189}}} \\
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Phaeophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{169,936}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{18,481,141}}} \\
-
-\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Rhodophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5,771}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,515,421}}} \\
-
-\ascline{1.5pt}{666666}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
+\centering{
+
+\includegraphics[width=6.63in,height=\textheight]{Figures/table_validation_px.png}
+
+}
+
+\end{table}%
 

### 2024-03-08 index.qmd
first part of Laurent's comments

@@
 
-```{r Table1}
+```{r Table1 building}
+#| cache: false
 #| echo: false
+#| eval: false
 #| warning: false
-#| label: tbl-flights
-#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
-#| cache: true
 
@@
 
-flextable(df)  %>%
+ i = 16.5 # width of the side borders in the word_document output (in centimeters)
+ w = i*0.3937 # width of the side borders in the word_document output (in inches)
+
+flx1<-flextable(df)  %>%
+  flextable::width(width = (w/(ncol(df)))) %>% 
   merge_v(j = 1) %>%
@@
 
+save_as_image(flx1, "Figures/table_flights.png", res = 300)
+```
+
+```{r Table1}
+#| echo: false
+#| warning: false
+#| label: tbl-flights
+#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
+#| cache: true
+
+knitr::include_graphics("Figures/table_flights.png")
 ```
@@
 
+```{r Table2 building}
+#| cache: false
+#| echo: false
+#| eval: false
+#| warning: false
+
+df_validation<-read.csv("Data/training/TrainandValid_NewStanRawMetrics_Processed_valid.csv")
+
+ i = 16.5 # width of the side borders in the word_document output (in centimeters)
+ w = i*0.3937 # width of the side borders in the word_document output (in inches)
+
+df_flx2<-df_training %>% 
+  left_join(df_validation, by = "True") %>% 
+  rename(`Validation Pixels` = "n",
+         Class = "True",
+         `Training Pixels` = "Training_Pixels")
+flx2 <- df_flx2 %>% 
+  flextable() %>% 
+  flextable::width(width = (w/(ncol(df_flx2)))) %>% 
+  # border_remove() %>%
+  flextable::align(align = "center",part = "all") %>%
+  flextable::align(align = "center",part = "header") %>% 
+  set_table_properties(layout = "autofit")
+
+save_as_image(flx2, "Figures/table_validation_px.png", res = 300)
+
+```
+
 ```{r Table2}
@@
 
-df_validation<-read.csv("Data/training/TrainandValid_NewStanRawMetrics_Processed_valid.csv")
-
-df_training %>% 
-  left_join(df_validation, by = "True") %>% 
-  rename(`Validation Pixels` = "n",
-         Class = "True",
-         `Training Pixels` = "Training_Pixels") %>% 
-  flextable() %>% 
-  # border_remove() %>%
-  flextable::align(align = "center",part = "all") %>%
-  flextable::align(align = "center",part = "header") %>% 
-  set_table_properties(layout = "autofit")
-
+knitr::include_graphics("Figures/table_validation_px.png")
 ```

### 2024-03-09 docs/_tex/index.tex
laurent's comments

@@
 
-A total of 9 prediction maps corresponding to the 9 drone flights were
-obtained. Each prediction map is associated with a probability map,
+A total of nine prediction maps corresponding to the nine drone flights
+were obtained. Each prediction map is associated with a probability map,
 indicating the probability of the selected class for every pixel. The
-low-altitude flight conducted in Gafanaha, Portugal, represents the site
-with the highest complexity (Figure~\ref{fig-GafLow}). Among the 5
-vegetation classes on which the model was trained, 4 were present on
-this site. On this site, there is a mixture of Chlorophyceae and
-Rhodophyceae over the seagrass meadow. This is also where
-Bacillariophyceae is most abundant. Although the seagrass bed is solely
-composed of \emph{Zostera noltei}, various colors can be observed: dark
-green (indicating healthy beds with 100\% coverage) and whitish/brown
-(indicating beds where leaves are dying). Regardless of the color, the
-meadow is predicted as Magnoliopsida by the model.
+low-altitude flight conducted in Gafanha, Portugal, represents the site
+with the highest complexity (Figure~\ref{fig-GafLow}). Among the five
+vegetation classes on which the model was trained, four were present on
+this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass
+meadow. There was also Bacillariophyceae forming biofilms on parts of
+sediment surface. Although the seagrass bed was solely composed of
+\emph{Zostera noltei}, various colors of this could be observed from
+dark green (corresponding to healthy leaves) to whitish/brown (when
+leaves were discolored having lost their pigmentation). Regardless of
+color, the meadow was predicted as Magnoliopsida by the model.
 
@@
 \caption{\label{fig-GafLow}RGB orthomosaic (Left) and Prediction (Right)
-of the low altitude flight of Gafanaha, Portugal. The total extent of
+of the low altitude flight of Gafanha, Portugal. The total extent of
 this flight is 3000m² with a resolution of 8 mm per pixel. Background
-colors means intertidal area (Light Green) and land area (Light Grey).
-The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.}
+colors indicate intertidal area (Light Green) and land area (Light
+Grey). The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel
+size.}
 
@@
 masked in the prediction map due to sunglint and misclassification
-caused by the turbid shallow water. Most of the intertidal area has been
-classified as Magnoliopsida by the model, even though there is
-discoloration of seagrass blades. Only a few pixels have been classified
-as Chlorophyceae at this scale. Furthermore, the area that was
-classified as Bacillariophyceae in the low-altitude flight remains
-mostly classified as such in the high-altitude flight, though some
-pixels were classified as Magnoliopsida. Patches of Rhodophyceae were
-correctly classified. In the nothern part of the scene, near the land
-limit, patches of \emph{Spartina sp.} were misclassified, either as
-Magnoliopsida or as Phaeophyceae.
+caused by the turbid shallow water. Most of the intertidal area was
+classified as Magnoliopsida by the model, including seagrass patches
+with discolored leaves. Only a few pixels were classified as
+Chlorophyceae at this scale. Furthermore, the area that was classified
+as Bacillariophyceae in the low-altitude flight remained mostly
+classified as such in the high-altitude flight, though some pixels were
+classified as Magnoliopsida. Patches of Rhodophyceae were correctly
+classified. In the nothern part of the scene, near the land limit,
+patches of the schorre angiosperm \emph{Spartina sp.} were
+misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 \caption{\label{fig-GafHigh}RGB orthomosaic (Left) and Prediction
-(Right) of the high altitude flight of Gafanaha, Portugal. The total
+(Right) of the high altitude flight of Gafanha, Portugal. The total
 extent of this flight is about 1 km² with a resolution of 80 mm per
-pixel. Background colors means intertidal area (Light Green), land area
-(Light Grey) and water (Light Blue). The red triangle shows the extent
-of the low altitude flight of Gafanha. The zoom covers an area
-equivalent to a 10-meter Sentinel-2 pixel size.}
+pixel. Background colors indicate intertidal area (Light Green), land
+area (Light Grey) and water (Light Blue). The red triangle shows the
+extent of the low altitude flight of Gafanha presented in
+Figure~\ref{fig-GafLow}. The zoom covers an area equivalent to a
+10-meter Sentinel-2 pixel size.}
 
@@
 The high altitude flight acquired over the inner lagoon of the Ria de
-Aveiro is the largest of all flights, covering almost 1.5 km²
-(Figure~\ref{fig-Boat}). On this site, only seagrass and red algae where
-seen on the field. The classification provided consistent results, with
-a patchy Magnoliopsida meadow mixed with Rhodophyceae on the eastern
-part of the scene. As shown in the zoom (Figure~\ref{fig-Boat}), the
-edges of the meadow can be colonised by Chlorophyceae.
+Aveiro was the largest of all flights, covering almost 1.5 km²
+(Figure~\ref{fig-Boat}). The site was dominated by seagrass and the red
+macroalgae \emph{Gracilaria vermicullophyla}. The classification
+provided consistent results, with a patchy seagrass meadow mixed with
+red macroalgae on the eastern part of the scene. As shown in the zoom
+(Figure~\ref{fig-Boat}), the edges of the meadow were colonised by green
+macroalgae
 
@@
 The total extent of this flight is about 1.5 km² with a resolution of 80
-mm per pixel. Background colors means intertidal area (Light Green),
-land area (Light Grey) and water (Light Blue). The zoom covers an area
+mm per pixel. Background colors indicates intertidal area (Light Green),
+land area (Light Grey) and water (Light Blue). Each cover an area
 equivalent to a 10-meter Sentinel-2 pixel size.}
@@
 part of the scene from west to east. Alongside this dike, brown algae
-attached to rocks and stranded green algae could be found. Despite the
-high mixture between Chlorophyceae and Magnoliopsida these two classes
-were correctly discriminated by the classifier.
+for the order Fucales (\emph{Fucus spp.}, \emph{Ascophyllum nodosum})
+were attached to sparse rocks and stranded green algae (\emph{ulva
+spp.}) could be observed Despite the high mixture between Chlorophyceae
+and Magnoliopsida these two classes were correctly discriminated by the
+classifier.
 
@@
 \caption{\label{fig-Dike}RGB orthomosaic (Top) and Prediction (Bottom)
-of Northern part of Noirmoutier Island, France. The total extent of this
-flight is about 28 000 m² with a resolution of 80 mm per pixel.
-Background colors means intertidal area (Light Green) and land area
+of the Northern part of Noirmoutier Island, France. The total extent of
+this flight is about 28 000 m² with a resolution of 80 mm per pixel.
+Background colors indicate intertidal area (Light Green) and land area
 (Light Grey). The zoom covers an area equivalent to a 10-meter
@@
 respectively. Bacillariophyceae was the least performing class (accuracy
-of 0.72 ) mainly due to the confusion between Magnoliopsida and
-Sediment.
+of 0.72 ) mainly due to the confusion with Magnoliopsida and Sediment.
 
@@
 \caption{\label{fig-VIP}Variable Importance of the Neural Network
-Classifier for each vegetation class. The bigger the slice, the more
-important is the variable to predict accuratly this class. The bottom
-right plot shows the drone standardised reflectance spectra of each
-class. Each slice represent the VIP of both RAW and standardised
+Classifier for each taxonomic class. The bigger the slice, the more
+important is the variable to predict accurately this class. The right
+plot shows the drone raw and standardised reflectance spectra of each
+class. Each slice represent the VIP of both raw and standardised
 reflectance combined.}
@@
 
-The computation of the variable importance makes it possible to identify
-which wavelengths are the most useful for class prediction
-(Figure~\ref{fig-VIP}). The spectral bands at 444 , 717 and 842 nm of
-the Micasense camera are important for none of the vegetation classes.
-The band at 531 nm is the only important predictor for the classifier to
-accurately predict chlorophyceae. In fact, at this wavelength, the
-Chlorophyceae spectra has the maximum reflectance among of all
-vegetation classes. The bands at 531 and 740 nm are the most important
-predictors for Phaeophyceae, corresponding to the minimum reflectance
-among all classes. Bands at 475 and 560 nm are the most important
-predictors for Bacillariophyceae and Rhodophyceae, respectively. Four
-predictors, ranging from the green (560 nm) to the RedEdge (705 nm)
-bands are important to accurately predict magnoliopsida.
+The computation of the variable importance made it possible to identify
+which wavelengths were the most useful for class prediction
+(Figure~\ref{fig-VIP}). The spectral bands at 444, 717 and 842 nm of the
+Micasense camera did not came out as important for any of the vegetation
+classes. The band at 531 nm was the only important predictor for the
+classifier to accurately predict Chlorophyceae. In fact, at this
+wavelength, the Chlorophyceae spectra have the highest reflectance among
+of all vegetation classes. The bands at 531 and 740 nm were the most
+important predictors for Phaeophyceae, corresponding to the lowest
+reflectance among all classes. Bands at 475 and 560 nm are the most
+important predictors for Bacillariophyceae and Rhodophyceae,
+respectively. Four predictors, ranging from the green (560 nm) to the
+RedEdge (705 nm) bands were important to accurately predict
+Magnoliopsida.
 
@@
 pixels of the same classes on the hight altitude flight. Percent cover
-of classes is retrieve using the result of the classification of the low
-altitude flight of Gafanha, Portugal. The vertical dashed line shows the
-0.85 probability of the model. Everything on the right of this line has
-a probability higher then 0.85 and everuthing on the left of this line
-has a probability lower.}
-
-\end{figure}%
-
-Using the very high precision low altitude flight, we determined the
-minimal percent cover required to classify correctly classify a given
-class using the high altitude flight (Figure~\ref{fig-upscaling}). When
-the percent cover of the class is 100 \%, big pixels are well classified
-for all the classes excepted for Bare Sediment, where it's well
-classified 80\% of the time. A vegetative percent cover of at least 80\%
-is need to have all the big pixels well classified, at the exception of
-Magnoliopsida that needs an higher percent cover (\textgreater90 \%) to
-be well classified. Concerning the probability of each class, a really
-high Percent cover is needed to confidently predict Bacillariophyceae.
-To predict Chlorophyceae with a confidence of 0.85, a percent cover of
-93 \% is needed, 90 \% for magnoliopsida, 92 \% for Rhodophyceae and 97
-\% for Bacillariophyceae.
+of classes was retrieved using the result of the classification of the
+low altitude flight of Gafanha, Portugal. The vertical dashed line shows
+the 0.85 probability of the model. Everything on the right of this line
+has a probability higher then 0.85 and everything on the left of this
+line has a lower probability.}
+
+\end{figure}%
+
+Using the very high resolution low altitude flight, we determined the
+minimal percent cover required to classify correctly a given class using
+the high altitude flight (Figure~\ref{fig-upscaling}). When the percent
+cover of the class was 100 \%, coarser high-flight pixels are well
+classified for all the classes except for Bare Sediment, which was well
+classified 80\% of the time. This phenomenon is likely attributed to the
+time gap between the two flights, allowing for microphytobenthos
+migration, consequently altering the model's classification from bare
+sediment to Bacillariophyceae. A percent cover of at least 80\% was
+needed to have all the low resolution pixels well classified, at the
+exception of Magnoliopsida that needs a higher percent cover
+(\textgreater90 \%) to be well classified. Concerning the probability of
+each class, the highest percent cover was needed to confidently predict
+Bacillariophyceae. To predict Chlorophyceae with a confidence of 0.85, a
+percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
+Rhodophyceae and 97 \% for Bacillariophyceae.
 
@@
 \caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
-(Green) or absent (Red) in each taxonomic class present in the Neural
+(Green) or absent (Red) in each taxonomic class dected by the Neural
 Network Classifier, along with their absorption wavelength measured with
@@
 fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino:
-diadinoxanthin, Neo: neoxanthin.}
+diadinoxanthin, Neo: neoxanthin., PE: phycoerythrin, PC: phycocyanin.}
 
@@
 specifically focusing on distinguishing between Chlorophyceae (green
-algae) and marine Magnoliopsida (seagrasses) using multispectral drone
-data. The ability to differentiate between various types of vegetation,
-as demonstrated in this study, plays a critical role in ecological
-monitoring and management. By distinguishing between seagrasses and
-macroalgae, our approach facilitates targeted conservation strategies,
-enabling more effective preservation and restoration efforts in coastal
-ecosystems. The discrimination of seagrasses from green macroalgae
-presents significant challenges, primarily due to the shared pigment
-composition between these taxa, as depicted in Figure~\ref{fig-Pigm} but
-also by the frequent spatial mixing of these green macrophytes. This
-similarity in pigment composition, including photosynthetic and
-carotenoid pigments like chlorophyll b and c, fucoxanthin, and
-neoxanthin, results in spectral signatures that are often
-indistinguishable to non exper eyes. This spectral overlap is further
-complicated by the intermingling of seagrasses and green macroalgae in
-the same spatial locations, posing a significant challenge for remote
-sensing aimed at accurately mapping and monitoring coastal ecosystems.
-Our study addresses these complexities by utilizing high-resolution
-drone imagery with 10 spectral bands. \citep{Davies2023} has shown that
-having at least 8 spectral bands ranging between 500 nm to 850 nm with
-including a band at 530 nm and another one at 730 nm is crucial to
-accurately discriminate green macrophytes.
+macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
+drone data. The ability to differentiate between various types of
+vegetation, as demonstrated in this study, plays a critical role in
+ecological monitoring and management. By distinguishing between
+seagrasses and macroalgae, our approach facilitates targeted
+conservation strategies, enabling more effective preservation and
+restoration efforts in coastal ecosystems. The discrimination of
+seagrasses from green macroalgae presents significant challenges
+\citetext{\citealp[ ]{oiry2021using}; \citealp{Bannari2022}}, primarily
+due to the shared pigment composition between these taxa
+\citep{mckenzie2020global}, as depicted in Figure~\ref{fig-Pigm} but
+also by the frequent spatial mixing of these green macrophytes. These
+green macrophytes have in common photosynthtic pigmetns, chlorophyll a
+and b, and accessory carotenoid pigments zeaxantin, lutein and
+neoxanthin. As a result the spectral signatures are often
+indistinguishable in the visible wavelength region. This spectral
+overlap is further complicated by the intermingling of seagrasses and
+green macroalgae in the same spatial locations, posing a significant
+challenge for remote sensing aimed at accurately mapping and monitoring
+coastal ecosystems. Our study addresses these complexities by using
+high-resolution drone imagery with 10 spectral bands. \citep{Davies2023}
+have shown that having at least eight spectral bands ranging between 500
+nm to 850 nm including a green band at 530 nm and another one in the
+RedEdge region at 730 nm was crucial to accurately discriminate green
+macrophytes.
 
@@
 these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
-pigment compostion of green macrophytes is similar, differences in the
+pigment composition of green macrophytes is similar, differences in the
 spectral shape can still be observed (Figure~\ref{fig-vegetation}).
 Several factors can explain these differences such has different pigment
-concentration or proportion, different cellular organisation and 3D
-disposition of the plant a whole on the intertidal mudflat
-\citep[\citep{kirk1994light},
-\citep{hedley2018influence}]{beach1997vivo}.
+concentration and/or proportion \citep{bargain2013seasonal}, different
+cellular organisation and the disposition of the plant on the sediment
+surface \citetext{\citealp[ ]{beach1997vivo}; \citealp[
+]{kirk1994light}; \citealp{hedley2018influence}}.
 
 The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
-shows that the 531 nm band is the most important spectral band for
+identified that the 531 nm band as the most important spectral band for
 accurately identifying Chlorophyceae. In fact, at this wavelength,
-Chlorophyceae exhibits the highest reflectance among all other classes,
+Chlorophyceae exhibited the highest reflectance among all other classes,
 highlighting the difference in accessories carotenoid proportion between
-seagrasses and green algae \citep{repolho2017seagrass}.
-
-Concerning Phaeophyceae, the thick cell walls of plant of this class
-make it really reflective in the infrared part of the spectra whereas
-the presence of Fucoxanthin and Zeaxanthin result in a low reflectance
-in the visible part of the electromagnetic spectra. These two key
-features has been identified by the Neural Network as the two principal
-predictors to accurately identify Brown algae (Figure~\ref{fig-VIP}).
-Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
-contributes to the lowest reflectance among all classes in the spectral
-range of 560 to 615 nm (Figure~\ref{fig-VIP}). The band at 560 nm has
-been identified as important for accurately identifying this class
-Resolution impact on the prediction. Regarding Bacillariophyceae, the
-VIP analysis (Figure~\ref{fig-VIP}) indicates that 475 nm is the most
-important predictor for this class. This could be attributed to the
-absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in
-the blue part of spectra, resulting in the highest visible reflectance
-among all classes. Furethemore, it is vegetation with the lowest
-concentration of chlorphyll-a, pigment absorbing light both in the blue
-and the red. The transparency of Bacillariophyceae makes the reflectance
-of the sediment part of the overall reflectance of Bacillariophyceae,
-further explaining the high reflectance in the blue.
+seagrasses and green macroalgae \citep{repolho2017seagrass}.
+
+Concerning Phaeophyceae, the thick cell walls of these macroalgae
+\citep{charrier2021growth} make it more reflective in the infrared part
+of the spectra \citep{Slaton2001} whereas the presence of Fucoxanthin
+and Zeaxanthin result in a low reflectance in the visible part of the
+electromagnetic spectra (Figure~\ref{fig-Pigm} ; Figure~\ref{fig-VIP}).
+These two key features have been identified by the Neural Network as the
+two principal predictors to accurately identify brown algae
+(Figure~\ref{fig-VIP}). Similarly, the presence of phycoerythrin and
+phycocyanin in Rhodophyceae contributes to the lowest reflectance among
+all classes in the spectral range of 560 to 615 nm
+(Figure~\ref{fig-VIP}). The band at 560 nm has been identified as
+important for accurately identifying this class probably in relation to
+the absorption by phycoerythrin (\textbf{REF}). Regarding
+Bacillariophyceae, the VIP analysis (Figure~\ref{fig-VIP}) indicated
+that 475 nm was the most important predictor for this class. classes.
+This is not a usual diagnostic wavelength for Bacillariophyceae which is
+mainly identified by the presence of fucoxanthin and chlorophyll c
+(Table 11), but it correspond to the absorption of diadinoxanthin an
+accessory pigment characteristic of this class
+\citep{meleder2003spectrometric}. Furethemore, it is vegetation with the
+lowest concentration of chlorphyll-a, pigment absorbing light both in
+the blue and the red. The transparency of Bacillariophyceae makes the
+reflectance of the sediment part of the overall reflectance of
+Bacillariophyceae, further explaining the high reflectance in the blue.
 
@@
 both low-altitude and high-altitude flights over a common area. The red
-dashed line represents a linear model wheras the black dashed line
-represents a 1 to 1 relationship. Left (A) plots RAW data and right (B)
-plots standardise data.}
+dashed line represents a linear model whereas the black dashed line
+represents a 1 to 1 relationship. Left (A) plots raw data and right (B)
+plots standardised data.}
 
@@
 altitudes (12m and 120m) for constructing the neural network model. The
-lower altitude flights (8mm spatial resolution) enable precise selection
-of pure pixels representing the classes used in the neural network
-model. This methodology implies a consistency between the reflectance of
-both altitude. Figure~\ref{fig-CompareRef} (A) depicts the relationship
-between reflectance from a low-altitude flight and a high-altitude
-flight conducted over the same area. An apparent underestimation of
-reflectance values is observed in the high-altitude flight, particularly
-for higher values. Since both flights were conducted over vegetation
-areas, the highest reflectance values correspond to the infrared part of
-the spectrum.
+lower altitude flights (8mm spatial resolution) enabled precise
+selection of pure pixels representing the classes used in the neural
+network model. This methodology implies a consistency between the
+reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
+relationship between reflectance from a low-altitude flight and a
+high-altitude flight conducted over the same area. Overall there was a
+good agreement between the two altitudes. There was however a slight
+underestimation for raw reflectance values in the high-altitude flight,
+particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
+both flights were conducted over vegetation areas, the highest
+reflectance values correspond to the infrared part of the spectrum.
 
@@
 employed min/max standardized reflectance spectra as predictors for the
-model (Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} (B) ;
-\citep{Cao2017}). This approach allows us to eliminate differences in
-the level of reflectance, focusing instead on the shape of the spectra.
-This is a key feature in building a model that can reliably predict
-vegetation across geographical sites and seasons. It enables consistent
-prediction of vegetation classes across variations in biomass and
-variability in light conditions \citetext{\citealp[
-]{fyfe2003spatial}; \citealp[
+model (Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allowed
+us to eliminate the slight reflectance difference between the flights
+(Figure~\ref{fig-CompareRef} B) and to focus on the shape of the spectra
+in the visible part of the electromagnetic spectra, where different
+pigmentation are associated to taxonomic dignostic features. This was a
+key feature in building a model that could reliably predict vegetation
+across geographical sites and seasons. It enabled consistent prediction
+of vegetation classes across variations in biomass and variability in
+light conditions \citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
 ]{COSTA2021107018}; \citealp{piaser2023impact}}.
@@
 confidence when faced with lower percentages of seagrass cover.
-Intertidal seagrasses exhibit strong phenology, with varying pigment
+Intertidal seagrasses exhibit marked phenology, with varying pigment
 composition throughout the year\citetext{\citealp[
-]{bargain2013seasonal}; \citealp{legare2022remote}}. This suggests that
-outside of the biomass peak of seagrasses, this model may be less
-accurate. Further investigation is warranted to explore this aspect.
+]{bargain2013seasonal}; \citealp{legare2022remote}}. Since the training
+dataset has been made using well developed seagrass meadows, outside of
+the biomass peak of seagrasses, this model may be less accurate. Further
+investigation is warranted to explore this aspect.
 
@@
 ]{villalobos2023remote}; \citealp{oiry2021using}}. Our findings,
-particularly the improved discrimination of vegetation types, underscore
-the potential of drone-based remote sensing to support diverse
-applications, from biodiversity conservation to climate change
-adaptation strategies\textbf{.} Employing traditional sampling methods
-to monitor these ecosystems is time and resource-intensive, and the
-findings are often difficult to scale up. Earth observation methods can
-bridge this gap and meet the needs for monitoring coastal ecosystems.
+particularly the improved discrimination of seagrass from other
+intertidal vegetation taxonomic classes, underscore the potential of
+drone-based remote sensing to support diverse applications, from
+biodiversity conservation to climate change adaptation strategies.
+Employing traditional sampling methods to monitor these ecosystems is
+time and resource-intensive, and the findings are often difficult to
+scale up. Earth observation methods can bridge this gap and meet the
+needs for monitoring coastal ecosystems.
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
@@
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
-significance of monitoring waters, particularly in light of the Water
-Framework Directive (WFD ; \citep{WFD2000}), cannot be overstated in
-environmental management and conservation efforts. The WFD mandates the
-achievement and maintenance of ``good ecological status'' for all
-European waters, which necessitates a comprehensive understanding and
-monitoring of aquatic ecosystems, including coastal habitats like
-seagrass \citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
+significance of monitoring coastal environment, particularly in light of
+the Water Framework Directive (WFD ; \citep{WFD2000}), cannot be
+overstated in environmental management and conservation efforts. The WFD
+mandates the achievement and maintenance of ``good ecological status''
+for all European waters, which necessitates a comprehensive
+understanding and monitoring of aquatic ecosystems, including coastal
+habitats like seagrass \citetext{\citealp[
+]{foden2007angiosperms}; \citealp[
 ]{nordlund2024one}; \citealp{Zoffoli2021}}.
@@
 Drones, with their capability for high-resolution, multispectral
-imagery, provide a novel and powerful means to rapidly and accurately
-acquire ground truth data (i.e.~output of the model used in the present
-study). This data is critical for calibrating and validating satellite
-remote sensing applications, thereby enhancing our capacity to monitor
-vast coastal areas systematically under the WFD framework. The
+imagery, flight on demand, provide a novel and powerful means to rapidly
+and accurately acquire ground truth data (i.e.~output of the model used
+in the present study). These data are critical for calibrating and
+validating satellite remote sensing applications, thereby enhancing our
+capacity to monitor vast coastal areas systematically under the WFD
+framework. A perspective of this work is to adapt the algorithm for
+Sentinel-2 to see of the discrimination between seagrass and green
+macroalgae is still operational at a coarser spatial resolution. The
 integration of drone technology facilitates a scalable approach to
@@
 
-The utilization of drone-based remote sensing coupled with machine
-learning techniques has proven to be an effective method for the
-discrimination of seagrasses and macroalgae in coastal ecosystems. This
-study has highlighted the potential for these technologies to enhance
-the accuracy and efficiency of habitat monitoring, which is essential
-for environmental management and conservation strategies. Through the
-application of high-resolution multispectral imagery, the research
-contributes to the broader understanding and surveillance of aquatic
-ecosystems, aligning with objectives outlined in policies such as the
-Water Framework Directive. The findings underscore the importance of
-adopting advanced remote sensing tools in ecological studies and
-environmental monitoring, providing a foundation for future research and
-policy implementation aimed at ecosystem preservation and restoration.
+The utilization of very high-resolution drone-based remote sensing
+coupled with machine learning techniques has proven to be an effective
+method for the discrimination of seagrasses from green macroalgae with a
+multispectral resolution sensor. Standardized reflectance were
+incorporated in the Neural Network model allowing for a better
+discrimination of spectral features related to pigment absorption in the
+visible. There was a striking difference for the variable of importance
+to discriminate Magnoliopsida from Chlorophyceae. The latter was
+essentially identify with the 451 nm spectral band while more spetral
+bands were needed to identify the former, notably 650, 560, 668, and 705
+nm. As the spectral bands of the Micasense RedEdge Dual MX are very
+similar to those of Sentinel-2, we suggest that multispectral satellite
+data have the potential to perform this discrimination between green
+macrophytes. The algorithm should now be adapted to Sentinel-2 with all
+the drone data from this study that can be used as training and
+validation data. The findings underscore the importance of adopting
+advanced remote sensing tools in ecological studies and environmental
+monitoring, providing a foundation for future research and policy
+implementation aimed at ecosystem preservation and restoration.
 

### 2024-03-09 index.qmd
laurent's comments

@@
 
-A total of 9 prediction maps corresponding to the 9 drone flights were obtained.
+A total of nine prediction maps corresponding to the nine drone flights were obtained.
 Each prediction map is associated with a probability map, indicating the probability of the selected class for every pixel.
-The low-altitude flight conducted in Gafanaha, Portugal, represents the site with the highest complexity (@fig-GafLow).
-Among the 5 vegetation classes on which the model was trained, 4 were present on this site.
-On this site, there is a mixture of Chlorophyceae and Rhodophyceae over the seagrass meadow.
-This is also where Bacillariophyceae is most abundant.
-Although the seagrass bed is solely composed of *Zostera noltei*, various colors can be observed: dark green (indicating healthy beds with 100% coverage) and whitish/brown (indicating beds where leaves are dying).
-Regardless of the color, the meadow is predicted as Magnoliopsida by the model.
+The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
+Among the five vegetation classes on which the model was trained, four were present on this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass meadow.
+There was also Bacillariophyceae forming biofilms on parts of sediment surface.
+Although the seagrass bed was solely composed of *Zostera noltei*, various colors of this could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
+Regardless of color, the meadow was predicted as Magnoliopsida by the model.
 
@@
 #| warning: false
-#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanaha, Portugal.
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanha, Portugal.
 The total extent of this flight is 3000m² with a resolution of 8 mm per pixel.
-Background colors means intertidal area (Light Green) and land area (Light Grey).
+Background colors indicate intertidal area (Light Green) and land area (Light Grey).
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
 A channel delineating a small island was masked in the prediction map due to sunglint and misclassification caused by the turbid shallow water.
-Most of the intertidal area has been classified as Magnoliopsida by the model, even though there is discoloration of seagrass blades.
-Only a few pixels have been classified as Chlorophyceae at this scale.
-Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remains mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
+Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
+Only a few pixels were classified as Chlorophyceae at this scale.
+Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remained mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
 Patches of Rhodophyceae were correctly classified.
-In the nothern part of the scene, near the land limit, patches of *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+In the nothern part of the scene, near the land limit, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 #| warning: false
-#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanaha, Portugal.
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanha, Portugal.
 The total extent of this flight is about 1 km² with a resolution of 80 mm per pixel.
-Background colors means intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The red triangle shows the extent of the low altitude flight of Gafanha.
+Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+The red triangle shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
 
-The high altitude flight acquired over the inner lagoon of the Ria de Aveiro is the largest of all flights, covering almost 1.5 km² (@fig-Boat).
-On this site, only seagrass and red algae where seen on the field.
-The classification provided consistent results, with a patchy Magnoliopsida meadow mixed with Rhodophyceae on the eastern part of the scene.
-As shown in the zoom (@fig-Boat), the edges of the meadow can be colonised by Chlorophyceae.
+The high altitude flight acquired over the inner lagoon of the Ria de Aveiro was the largest of all flights, covering almost 1.5 km² (@fig-Boat).
+The site was dominated by seagrass and the red macroalgae *Gracilaria vermicullophyla*.
+The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the scene.
+As shown in the zoom (@fig-Boat), the edges of the meadow were colonised by green macroalgae
 
@@
 The total extent of this flight is about 1.5 km² with a resolution of 80 mm per pixel.
-Background colors means intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+Background colors indicates intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+Each cover an area equivalent to a 10-meter Sentinel-2 pixel size.
 #| label: fig-Boat
@@
 The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike crossing the northern part of the scene from west to east.
-Alongside this dike, brown algae attached to rocks and stranded green algae could be found.
-Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
+Alongside this dike, brown algae for the order Fucales (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*ulva spp.*) could be observed Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
 
@@
 #| warning: false
-#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of Northern part of Noirmoutier Island, France.
+#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the Northern part of Noirmoutier Island, France.
 The total extent of this flight is about 28 000 m² with a resolution of 80 mm per pixel.
-Background colors means intertidal area (Light Green) and land area (Light Grey).
+Background colors indicate intertidal area (Light Green) and land area (Light Grey).
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
 Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were correctly classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
-`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` was the least performing class (accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` ) mainly due to the confusion between Magnoliopsida and Sediment.
+`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` was the least performing class (accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` ) mainly due to the confusion with Magnoliopsida and Sediment.
 
@@
 #| warning: false
-#| fig-cap: Variable Importance of the Neural Network Classifier for each vegetation class.
-The bigger the slice, the more important is the variable to predict accuratly this class.
-The bottom right plot shows the drone standardised reflectance spectra of each class.
-Each slice represent the VIP of both RAW and standardised reflectance combined.
+#| fig-cap: Variable Importance of the Neural Network Classifier for each taxonomic class.
+The bigger the slice, the more important is the variable to predict accurately this class.
+The right plot shows the drone raw and standardised reflectance spectra of each class.
+Each slice represent the VIP of both raw and standardised reflectance combined.
 #| label: fig-VIP
@@
 
-The computation of the variable importance makes it possible to identify which wavelengths are the most useful for class prediction (@fig-VIP).
-The spectral bands at 444 , 717 and 842 nm of the Micasense camera are important for none of the vegetation classes.
-The band at 531 nm is the only important predictor for the classifier to accurately predict chlorophyceae.
-In fact, at this wavelength, the Chlorophyceae spectra has the maximum reflectance among of all vegetation classes.
-The bands at 531 and 740 nm are the most important predictors for Phaeophyceae, corresponding to the minimum reflectance among all classes.
+The computation of the variable importance made it possible to identify which wavelengths were the most useful for class prediction (@fig-VIP).
+The spectral bands at 444, 717 and 842 nm of the Micasense camera did not came out as important for any of the vegetation classes.
+The band at 531 nm was the only important predictor for the classifier to accurately predict Chlorophyceae.
+In fact, at this wavelength, the Chlorophyceae spectra have the highest reflectance among of all vegetation classes.
+The bands at 531 and 740 nm were the most important predictors for Phaeophyceae, corresponding to the lowest reflectance among all classes.
 Bands at 475 and 560 nm are the most important predictors for Bacillariophyceae and Rhodophyceae, respectively.
-Four predictors, ranging from the green (560 nm) to the RedEdge (705 nm) bands are important to accurately predict magnoliopsida.
+Four predictors, ranging from the green (560 nm) to the RedEdge (705 nm) bands were important to accurately predict Magnoliopsida.
 
@@
 Each subplot shows all the pixels of the same classes on the hight altitude flight.
-Percent cover of classes is retrieve using the result of the classification of the low altitude flight of Gafanha, Portugal.
+Percent cover of classes was retrieved using the result of the classification of the low altitude flight of Gafanha, Portugal.
 The vertical dashed line shows the 0.85 probability of the model.
-Everything on the right of this line has a probability higher then 0.85 and everuthing on the left of this line has a probability lower.
+Everything on the right of this line has a probability higher then 0.85 and everything on the left of this line has a lower probability.
 #| label: fig-upscaling
@@
 
-Using the very high precision low altitude flight, we determined the minimal percent cover required to classify correctly classify a given class using the high altitude flight (@fig-upscaling).
-When the percent cover of the class is 100 %, big pixels are well classified for all the classes excepted for Bare Sediment, where it's well classified 80% of the time.
-A vegetative percent cover of at least 80% is need to have all the big pixels well classified, at the exception of Magnoliopsida that needs an higher percent cover (\>90 %) to be well classified.
-Concerning the probability of each class, a really high Percent cover is needed to confidently predict Bacillariophyceae.
-To predict Chlorophyceae with a confidence of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % is needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
+Using the very high resolution low altitude flight, we determined the minimal percent cover required to classify correctly a given class using the high altitude flight (@fig-upscaling).
+When the percent cover of the class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was well classified 80% of the time.
+This phenomenon is likely attributed to the time gap between the two flights, allowing for microphytobenthos migration, consequently altering the model's classification from bare sediment to Bacillariophyceae.
+A percent cover of at least 80% was needed to have all the low resolution pixels well classified, at the exception of Magnoliopsida that needs a higher percent cover (\>90 %) to be well classified.
+Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
+To predict Chlorophyceae with a confidence of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
 
@@
 #| warning: false
-#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
-Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin.')"
+#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class dected by the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
+Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin., PE: phycoerythrin, PC: phycocyanin.')"
 #| label: fig-Pigm
@@
 
-# Pigment composition of the different vegetation classes.
-Green indicate the presence of the pigment in the class while red indicate the abscence.
-Chlb : Chlorophyll-b ; Chlc : Chlorophyll-c ; Fuco : Fucoxanthin ; Zea : Zeaxanthin ; Diad : Diadinoxanthin ; Lut : Lutein ; Neo : Neoxanthin ; PE : Phycoerythrin ; PC : Phycocyanin.
-
 knitr::include_graphics("./Figures/Low_res/Disc_Pigment_Table.png")
@@
 
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
 The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and management.
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
-This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non exper eyes.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @Bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
+These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin.
+As a result the spectral signatures are often indistinguishable in the visible wavelength region.
 This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
-Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands.
-@Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with including a band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
+Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands.
+@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate green macrophytes.
 
@@
 The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
-Even if the pigment compostion of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
-Several factors can explain these differences such has different pigment concentration or proportion, different cellular organisation and 3D disposition of the plant a whole on the intertidal mudflat [@beach1997vivo, @kirk1994light, @hedley2018influence].
+Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
+Several factors can explain these differences such has different pigment concentration and/or proportion [@bargain2013seasonal], different cellular organisation and the disposition of the plant on the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 
-The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae [@repolho2017seagrass].
-
-Concerning Phaeophyceae, the thick cell walls of plant of this class make it really reflective in the infrared part of the spectra whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electromagnetic spectra.
-These two key features has been identified by the Neural Network as the two principal predictors to accurately identify Brown algae (@fig-VIP).
+The VIP analysis of the Neural Network model (@fig-VIP) identified that the 531 nm band as the most important spectral band for accurately identifying Chlorophyceae.
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green macroalgae [@repolho2017seagrass].
+
+Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electromagnetic spectra (@fig-Pigm ; @fig-VIP).
+These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
 Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range of 560 to 615 nm (@fig-VIP).
-The band at 560 nm has been identified as important for accurately identifying this class Resolution impact on the prediction.
-Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicates that 475 nm is the most important predictor for this class.
-This could be attributed to the absence of lutein, neoxanthin, and zeaxanthin in diatoms, absorbing in the blue part of spectra, resulting in the highest visible reflectance among all classes.
+The band at 560 nm has been identified as important for accurately identifying this class probably in relation to the absorption by phycoerythrin (**REF**).
+Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
+classes.
+This is not a usual diagnostic wavelength for Bacillariophyceae which is mainly identified by the presence of fucoxanthin and chlorophyll c (Table 11), but it correspond to the absorption of diadinoxanthin an accessory pigment characteristic of this class [@meleder2003spectrometric].
 Furethemore, it is vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
@@
 #| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
-The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship.
-Left (A) plots RAW data and right (B) plots standardise data.
+The red dashed line represents a linear model whereas the black dashed line represents a 1 to 1 relationship.
+Left (A) plots raw data and right (B) plots standardised data.
 #| label: fig-CompareRef
@@
 In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
-The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model.
+The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model.
 This methodology implies a consistency between the reflectance of both altitude.
-@fig-CompareRef (A) depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
-An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values.
+@fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
+Overall there was a good agreement between the two altitudes.
+There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A).
 Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
@@
 This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training.
-To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; @fig-CompareRef (B) ; [@Cao2017]).
-This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra.
-This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons.
-It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
+To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]).
+This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features.
+This was a key feature in building a model that could reliably predict vegetation across geographical sites and seasons.
+It enabled consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
 
@@
 The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
-Intertidal seagrasses exhibit strong phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
-This suggests that outside of the biomass peak of seagrasses, this model may be less accurate.
+Intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
+Since the training dataset has been made using well developed seagrass meadows, outside of the biomass peak of seagrasses, this model may be less accurate.
 Further investigation is warranted to explore this aspect.
@@
 The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of vegetation types, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies**.** Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
+Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation taxonomic classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
+Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
 Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems.
@@
 The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
-The significance of monitoring waters, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
+The significance of monitoring coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
 The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
@@
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral imagery, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
+Drones, with their capability for high-resolution, multispectral imagery, flight on demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
 output of the model used in the present study).
-This data is critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework.
+These data are critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework.
+A perspective of this work is to adapt the algorithm for Sentinel-2 to see of the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
@@
 
-The utilization of drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses and macroalgae in coastal ecosystems.
-This study has highlighted the potential for these technologies to enhance the accuracy and efficiency of habitat monitoring, which is essential for environmental management and conservation strategies.
-Through the application of high-resolution multispectral imagery, the research contributes to the broader understanding and surveillance of aquatic ecosystems, aligning with objectives outlined in policies such as the Water Framework Directive.
+The utilization of very high-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses from green macroalgae with a multispectral resolution sensor.
+Standardized reflectance were incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible.
+There was a striking difference for the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
+The latter was essentially identify with the 451 nm spectral band while more spetral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
+As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green macrophytes.
+The algorithm should now be adapted to Sentinel-2 with all the drone data from this study that can be used as training and validation data.
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem preservation and restoration.

### 2024-03-09 docs/_tex/index.tex
laurent's comments

@@
 seagrasses from green macroalgae presents significant challenges
-\citetext{\citealp[ ]{oiry2021using}; \citealp{Bannari2022}}, primarily
+\citetext{\citealp[ ]{oiry2021using}; \citealp{bannari2022}}, primarily
 due to the shared pigment composition between these taxa
@@
 to discriminate Magnoliopsida from Chlorophyceae. The latter was
-essentially identify with the 451 nm spectral band while more spetral
+essentially identify with the 451 nm spectral band while more spectral
 bands were needed to identify the former, notably 650, 560, 668, and 705

### 2024-03-09 index.qmd
laurent's comments

@@
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @Bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
 These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin.
@@
 There was a striking difference for the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
-The latter was essentially identify with the 451 nm spectral band while more spetral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
+The latter was essentially identify with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
 As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green macrophytes.

### 2024-03-11 docs/_tex/index.tex
Bede's comments

@@
 \begin{abstract}
-Coastal areas host seagrass meadows, which offer crucial ecosystem
+Coastal areas support seagrass meadows, which offer crucial ecosystem
 services including erosion control and carbon sequestration. However,
@@
 offer a promising solution. This study focuses on using drone
-acquisitions with a ten spectral bands sensor mirroring those of
+acquisitions with a ten spectral band sensor mirroring those of
 Sentinel-2, for mapping intertidal macrophytes and effectively
 discriminating between seagrass and green macroalgae. Nine drone flights
-were conducted at two different altitudes (12m and 120m) across diverse
-European habitats in France and Portugal. Low altitude flights were used
-to train a Deep Learning classifier based on Neural Networks to
-discrimintate among five taxonomic classes of intertidal vegetation:
-Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae
-(Brown algae), Rhodophyceae (Red macroalgae) and Bacillariophyceae
-(Diatoms). Drone mapping demonstrated an overall accuracy of 94\% across
-all the sites and images, covering a total area of 467 000 m². The model
-exhibited an accuracy of 96.4\% in identifying seagrass. This work
-showed that although they share the same pigmentary composition,
-seagrass and green algae can be discriminated using ten bands
-multispectral sensor. The algorithm should now be adapted for Sentinel-2
-to see if this discrimination is still operational at a coarser spatial
-resolution.
+were conducted at two different altitudes (12m and 120m) across
+heterogeneous European habitats in France and Portugal. Low altitude
+flights were used to train a Deep Learning classifier based on Neural
+Networks to discrimintate among five taxonomic classes of intertidal
+vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae),
+Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and
+Bacillariophyceae (Diatoms). Classification of drone imagery resulted in
+an overall accuracy of 94\% across all the sites and images, covering a
+total area of 467 000 m². The model exhibited an accuracy of 96.4\% in
+identifying seagrass. This work showed that although they share the same
+pigmentary composition, seagrass and green algae can be discriminated
+using ten bands multispectral sensor. The algorithm should now be
+adapted for Sentinel-2 to see if this discrimination is still
+operational at a coarser spatial resolution.
 \end{abstract}
@@
 intertidal seagrass meadows playing a crucial role at the interface
-between land and ocean \citep{unsworth2022}. Seagrass meadows provide a
-myriad of ecosystem services to humanity, including carbon
+between the land and oceans \citep{unsworth2022}. Seagrass meadows
+provide a myriad of ecosystem services to humanity, including carbon
 sequestration, oxygen production, protection against sea-level rise and
@@
 \citetext{\citealp[ ]{nguyen2021}; \citealp[ ]{soissons2018}; \citealp[
-]{orth2006}; \citealp[ ]{lin2018}; \citealp{duffy2019}}. While
-improvements in water quality have been recently reported in Europe,
-allowing an overall recovery of seagrass ecosystems at local scale, many
-coastal waters worldwide are still subjected to strong eutrophication
-processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
-Coastal eutrophication has been ass ociated to anomalous accumulation of
-green macroalgae, the so-called green tides
-(\citep{devlin2023nutrients}). Green tides produce shade and suffocation
-over seagrass individuals, thus threatening the health of seagrass
-ecosystems \citep{wang2022}.
+]{orth2006}; \citealp[ ]{lin2018}; \citealp[ ]{duffy2019}; \citealp[
+]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. While improvements
+in water quality have been recently reported in Europe, allowing an
+overall recovery of seagrass ecosystems at local scale, many coastal
+waters worldwide are still subjected to strong eutrophication processes
+\citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal
+eutrophication has been ass ociated to excessive accumulation of green
+macroalgae, so-called green tides (\citep{devlin2023nutrients}). Green
+tides produce shade and suffocation over seagrass individuals, thus
+threatening the health of seagrass ecosystems \citep{wang2022}.
 
@@
 distribution, population abundance, and phenology \citep{Pereira2013}.
-Seagrass monitoring is all the more important as it makes possible to
-identify which pressure should be addressed in priority to facilitate
-effective mitigation actions. Traditionally, indicators of seagrass
-status have been quantified using \emph{in situ} measurements. The
-acquisition of field data in intertidal zones is however notoriously
-challenging. Intertidal seagrass meadows are only partially exposed
-during low tide and can be situated in difficult-to-reach mudflats,
-potentially leading to inaccurate and limited estimations with
-conventional sampling techniques \citep{nijland2019}. Satellite
-observations have been proven effective in complementing in situ
-sampling, allowing for the near real-time and consistent retrieval of
-seagrass EOVs and EBVs over extensive meadows. \citetext{\citealp[
-]{Zoffoli2021}; \citealp[ ]{xu2021}; \citealp[
+Traditionally, indicators of seagrass status have been quantified using
+\emph{in situ} measurements. The acquisition of field data in intertidal
+zones is however notoriously challenging. Intertidal seagrass meadows
+are only partially exposed during low tide and can be situated in
+difficult-to-reach mudflats, potentially leading to inaccurate and
+limited estimations with conventional sampling techniques
+\citep{nijland2019}. Satellite observations have been proven effective
+in complementing in situ sampling, allowing for the near real-time and
+consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
+\citetext{\citealp[ ]{Zoffoli2021}; \citealp[ ]{xu2021}; \citealp[
 ]{Traganos2018}; \citealp{coffer2023}}
 
-While satellite remote sensing provides temporally consistent
+While satellite remote sensing (RS) provides temporally consistent
 observations over large spatial scales, it is limited by several
@@
 (e.g.~daily MODIS observation) are limited by a coarse spatial
-resolution (\textgreater100m). Mission with a high spatial resolution
+resolution (\textgreater100m). Missions with a high spatial resolution
 such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low
@@
 Magnoliopsida (seagrass) share the same pigment composition
-\citetext{\citealp[ ]{ralph2002}; \citealp{Douay2022}}. As a result,
-their respective spectral signatures can be considered similar by a
-non-expert observer \citetext{\citealp[
+\citetext{\citealp[ ]{ralph2002}; \citealp{Douay2022}}. Therefore, to
+someone not specialized in the field, their spectral signatures may
+appear to be alike \citetext{\citealp[
 ]{Davies2023}; \citealp{bannari2022}}. Recently, using advanced
@@
 Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral
-resolution. The application of this approach to satellite remote sensing
-remains however to be validated. Moreover patches of green algae can
-develop at small spatial scales that are not observable using
-non-commercial satellite imagery \citep{tuya2013}, especially during the
-initial stage of the event.
-
-Drones can potentially fill the gaps left by satellite remote sensing
-and in situ measurements, due to their ability to provide
-spatially-explicit observations at very high spatial resolutions (pixel
-size from cm to mm) and still capturing data at multi-spectral
-resolution \citetext{\citealp[
+resolution. However the application of this approach to satellite RS
+remains to be validated. Moreover patches of green algae can develop at
+small spatial scales that are not observable using non-commercial
+satellite imagery \citep{tuya2013}, especially during the initial stage
+of th
+
+Drones can potentially fill the gaps left by satellite RS and in situ
+measurements, due to their ability to provide spatially-explicit
+observations at very high spatial resolutions (pixel size from cm to mm)
+while capturing data at multi-spectral resolution \citetext{\citealp[
 ]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
@@
 ]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
-to coastal habitat mapping, most study cases were limited to a single
+to coastal habitat mapping, most case studies are limited to a single
 flight, restricting the generalizability of their application over wider
@@
 ]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. The present study
-aimed at analyzing the potential of multispectral drone remote sensing
-to map intertidal macrophytes, with a particular focus on discriminating
-Magnoliopsida and Chlorophyceae. Ten drone flights were performed over
-soft-bottom intertidal areas along two European countries (France and
-Portugal), covering a wide range of habitats, from monospecific seagrass
-meadows to meadows mixed with green, or red macroalgae. A deep learning
-algorithm was trained and validated for macrophyte discrimination,
-emphasizing applicability across diverse sites without a loss of
-prediction accuracy.
+aimed at analyzing the potential of multispectral drone RS to map
+intertidal macrophytes, with a particular focus on discriminating
+Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
+Ten drone flights were performed over soft-bottom intertidal areas along
+two European countries (France and Portugal), covering a wide range of
+habitats, from monospecific seagrass meadows to meadows mixed with
+green, or red macroalgae. A deep learning algorithm was trained and
+validated for macrophyte discrimination, emphasizing applicability
+across diverse sites without a loss of prediction accuracy.
 
@@
 for their relatively extensive intertidal seagrass beds. Two sites are
-located in Gulf of Morbihan (Figure~\ref{fig-map} A), France (47.5791°N,
-2.8018°W). This gulf covers an area of 115 km² and is only connected to
-the sea through a 900m wide channel. A total of 53 small islands are
-scattered across the gulf leading to 250 km of shorelines. Patchy
-seagrass meadows can be found on a lot of these islands. Within the Gulf
-of Morbihan we have chosen two sites : one is located in one of these
-island (Arz island); the other one is located in the southern part of
-the gulf (Duer). Two others sites are located in Bourgneuf Bay, France
-(46.9849°N, 2.1488°W). This bay is 340 km² semi-enclosed macrotidal bay,
-protected from waves by Noirmoutier Island. Bougneuf bay hosts a large
-intertidal seagrass meadow of about 6 km². Within this meadow, the sites
-observed by drones (L'Epine and Barbatre, Figure~\ref{fig-map} B)
-contain a monospecific bed of \emph{Zostera noltei} with very little
-mixing with other macrophytes. Three sites have been surveyed in the Ria
-de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of this
-lagoon is about 80 km² with many narrow channels, large salt marshes and
-many mudflats that uncovers at low tide. It is connected to the open sea
-through a single channel, with a tidal lag between the North and the
-South of the lagoon. The southernmost site (Gafanha) is a mudflat
-located in an affluent of the lagoon whereas the two other sites are
-situated in the middle of the lagoon and are only accessible by boat
-(Figure~\ref{fig-map} C). These Portuguese sites are characterized by a
-more diverse intertidal vegetation, where patches of seagrass could
-intermingle with red, brown and green macroalgae.
+located in the Gulf of Morbihan (Figure~\ref{fig-map} A), France
+(47.5791°N, 2.8018°W). This gulf covers an area of 115 km² and is only
+connected to the sea through a 900m wide channel. A total of 53 small
+islands are scattered across the gulf leading to 250 km of shorelines.
+Patchy seagrass meadows can be found on a lot of these islands. Within
+the Gulf of Morbihan we chose two sites : one located on one of the
+gulf's islands (Arz island) and the other located in the southern part
+of the gulf (Duer). Two other sites were located in Bourgneuf Bay,
+France (46.9849°N, 2.1488°W). This bay is 340 km² semi-enclosed
+macrotidal bay, protected from waves by Noirmoutier Island. Bougneuf bay
+hosts a large intertidal seagrass meadow of about 6 km². Within this
+meadow, the sites observed by drones (L'Epine and Barbatre,
+Figure~\ref{fig-map} B) contained a monospecific bed of
+\emph{Nanozostera noltei} (dwarf eelgrass) with very little mixing with
+other macrophytes. Three sites were surveyed in the Ria de Aveiro Lagoon
+in Portugal (40.6887°N, 8.6810°W). The extent of this lagoon is about 80
+km² with many narrow channels, large salt marshes and many mudflats that
+uncovers at low tide. It is connected to the open sea through a single
+channel, with a tidal lag between the North and the South of the lagoon.
+The southernmost site (Gafanha) was a mudflat located in a tributary
+river of the lagoon whereas the two other sites were situated in the
+middle of the lagoon and only accessible by boat (Figure~\ref{fig-map}
+C). These Portuguese sites are characterized by a more diverse
+intertidal vegetation, where patches of seagrass intermingle with red,
+brown and green macroalgae.
 
@@
 Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
-C: Ria de Aveiro Lagoon (Three sites). Green represent intertidal
-areas.}
+C: Ria de Aveiro Coastal Lagoon (Three sites). Green represent
+intertidal areas.}
 
@@
 Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
-million pixel reflectance photographs in ten spectral bands, from 444 nm
-(blue) to 840 nm (near infrared, NIR). An angle of 90° was maintained
-between the sun and the drone's route to guarantee uniform lighting
-conditions between flight lines. A side overlap of 70\% and a front
-overlap of 80\% between each image was set for each flight. A
-downwelling light sensor (DLS2) was used to acquire irradiance data
-concomitantly with the camera measurements. Raw data were calibrated in
-reflectance using a calibration panel reflective at \textasciitilde50\%
-provided by the manufacturer. A structure-from-motion photogrammetry
-software (Agisoft Metashape) was used to process images to obtain
-multispectral orthomosaics of each flight. The workflow for
-orthomosaicking was the same for every flight. First, tying key points
-were detected inside of each image and between overlapping images in
-order to obtain a sparse point cloud. This cloud was cleaned using
-reprojection accuracy metric in order to remove noisy points. A dense
-point cloud was then produced using a structure from motion algorithm. A
-surface interpolation of this dense point cloud was made to obtain a
-digital surface model (DSM), used to reconstruct the multispectral
-ortho-image. Across all sites, flights were made at two different
-altitudes : 12 m or/and 120 m. Low altitude drone flights produce
-ortho-images with a very high spatial resolution (8 mm per pixel),
-making it efficient to visually distinguish between the various types of
-vegetation. High altitude fights on the other hand allow to cover large
-areas and produced images with a pixel size of 80 mm
+million pixel reflectance photographs with ten spectral bands, from 444
+nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting
+conditions across flight paths, the drone's trajectory was aligned to
+maintain a solar azimuth angle of 90 degrees. An overlap of 70\% and
+80\% (side and front respectively) between each image was set for each
+flight. A downwelling light sensor (DLS2) was used to acquire irradiance
+data concomitantly with the camera measurements. Raw data were
+calibrated in reflectance using a calibration panel reflective at
+\textasciitilde50\% provided by the manufacturer. A
+structure-from-motion photogrammetry software (Agisoft Metashape) was
+used to process images to obtain multispectral orthomosaics of each
+flight. The workflow for orthomosaicking was the same for every flight.
+First, tying key points were detected inside of each image and between
+overlapping images in order to obtain a sparse point cloud. This cloud
+was cleaned using reprojection accuracy metric in order to remove noisy
+points. A dense point cloud was then produced using a structure from
+motion algorithm. A surface interpolation of this dense point cloud was
+made to obtain a digital surface model (DSM), used to reconstruct the
+multispectral ortho-image. Across all sites, flights were made at two
+different altitudes : 12 m or/and 120 m. Low altitude drone flights
+produce ortho-images with a very high spatial resolution (8 mm per
+pixel), making it efficient to visually distinguish between the various
+types of vegetation. High altitude fights on the other hand allow to
+cover large areas and produced images with a pixel size of 80 mm
 (Table~\ref{tbl-flights}).
@@
 classes of intertidal vegetation : Bacillariophyceae (Unicellular
-benthic diatoms forming large biofilms at the sediment surface during
-low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass),
+benthic diatoms forming biofilms at the sediment surface during low
+tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass),
 Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae)
 (Figure~\ref{fig-vegetation}). Pictures of each quadrat were uploaded
-online on the Global Biodiversity Information Facility (GBIF) platform
+online to the Global Biodiversity Information Facility (GBIF) platform
 \citep{BedeGbif}, a public open portal to store and share biodiversity
@@
 data and contribute to error reduction in photo interpretation. The
-workflow developped in this study is presented in
+workflow developed in this study is presented in
 Figure~\ref{fig-workflow}.
@@
 (Figure~\ref{fig-vegetation} F). To overcome this challenge, a deep
-learning classification method was developed, trained, validated, and
-applied to each drone flight (Figure~\ref{fig-workflow}).
+learning classification method was trained, validated, and applied to
+each drone flight (Figure~\ref{fig-workflow}).
 
@@
 In situ information on georeferenced class type and percent cover
-collected during each flight was used to assess the model accuracy.
-These images were used to construct a validation dataset indicating the
-presence or absence of each class. Additionally to the quadrat-based
-validation dataset, polygons of each class were photo interpreted in
-order to increase the number of pixels of the validation dataset. A
-confusion matrix, along with precision metrics such as global accuracy,
-sensitivity, specificity, and Kappa coefficient, was generated for each
-sites. All validation matrices were then merged to create a unique
-matrix . Altogether, a total of 536,000 pixels was used to validate the
-model, thus providing a geographically robust validation dataset.
+collected during each flight was used to assess the model accuracy,
+including. These images were used to construct a validation dataset
+indicating the presence or absence of each class. Additionally to the
+quadrat-based validation dataset, polygons of each class were photo
+interpreted in order to increase the number of pixels of the validation
+dataset. A confusion matrix, along with precision metrics such as global
+accuracy, sensitivity, specificity, and Kappa coefficient, was generated
+for each sites. All validation matrices were then merged to create a
+unique matrix . Altogether, a total of 536,000 pixels was used to
+validate the model, thus providing a geographically robust validation
+dataset.
+
+\subsection{Variable Importance Plots
+(VIP)}\label{variable-importance-plots-vip}
+
+\subsection{Impact of the percent cover on the
+prediction}\label{impact-of-the-percent-cover-on-the-prediction}
 
@@
 sediment surface. Although the seagrass bed was solely composed of
-\emph{Zostera noltei}, various colors of this could be observed from
+\emph{Nanozostera noltei}, various colors of this could be observed from
 dark green (corresponding to healthy leaves) to whitish/brown (when
 leaves were discolored having lost their pigmentation). Regardless of
-color, the meadow was predicted as Magnoliopsida by the model.
+color, the meadow was accurately predicted as Magnoliopsida by the
+model.
 
@@
 of the low altitude flight of Gafanha, Portugal. The total extent of
-this flight is 3000m² with a resolution of 8 mm per pixel. Background
+this flight was 3000m² with a resolution of 8 mm per pixel. Background
 colors indicate intertidal area (Light Green) and land area (Light
@@
 (Figure~\ref{fig-GafHigh}). A channel delineating a small island was
-masked in the prediction map due to sunglint and misclassification
-caused by the turbid shallow water. Most of the intertidal area was
-classified as Magnoliopsida by the model, including seagrass patches
-with discolored leaves. Only a few pixels were classified as
-Chlorophyceae at this scale. Furthermore, the area that was classified
-as Bacillariophyceae in the low-altitude flight remained mostly
-classified as such in the high-altitude flight, though some pixels were
-classified as Magnoliopsida. Patches of Rhodophyceae were correctly
-classified. In the nothern part of the scene, near the land limit,
-patches of the schorre angiosperm \emph{Spartina sp.} were
-misclassified, either as Magnoliopsida or as Phaeophyceae.
+masked in the prediction map. Most of the intertidal area was classified
+as Magnoliopsida by the model, including seagrass patches with
+discolored leaves. Only a few pixels were classified as Chlorophyceae at
+this scale. Furthermore, the area that was classified as
+Bacillariophyceae in the low-altitude flight remained mostly classified
+as such in the high-altitude flight, though some pixels were classified
+as Magnoliopsida. Patches of Rhodophyceae were correctly classified. In
+the nothern part of the scene, near the land limit, patches of the
+schorre angiosperm \emph{Spartina sp.} were misclassified, either as
+Magnoliopsida or as Phaeophyceae.
 
@@
 (Right) of the high altitude flight of Gafanha, Portugal. The total
-extent of this flight is about 1 km² with a resolution of 80 mm per
+extent of this flight was about 1 km² with a resolution of 80 mm per
 pixel. Background colors indicate intertidal area (Light Green), land
@@
 of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
-The total extent of this flight is about 1.5 km² with a resolution of 80
-mm per pixel. Background colors indicates intertidal area (Light Green),
-land area (Light Grey) and water (Light Blue). Each cover an area
-equivalent to a 10-meter Sentinel-2 pixel size.}
+The total extent of this flight was about 1.5 km² with a resolution of
+80 mm per pixel. Background colors indicates intertidal area (Light
+Green), land area (Light Grey) and water (Light Blue). Each cover an
+area equivalent to a 10-meter Sentinel-2 pixel size.}
 
@@
 of the Northern part of Noirmoutier Island, France. The total extent of
-this flight is about 28 000 m² with a resolution of 80 mm per pixel.
+this flight was about 28 000 m² with a resolution of 80 mm per pixel.
 Background colors indicate intertidal area (Light Green) and land area
@@
 
-A total of 536,000 pixels was used to validate the Neural Network
+A total of 536,000 pixels were used to validate the Neural Network
 classifier. The sites with the lowest and highest number of validation
@@
 respectively. Model global accuracy was 94.26\% with a Kappa coefficient
-of 0.92 (Figure~\ref{fig-Validation}). The least performing site was
+of 0.92 (Figure~\ref{fig-Validation}). The lowest performing site was
 Gafanha High (global accuracy of 75.45\%) whereas Mataducos was the site
@@
 Classifier for each taxonomic class. The bigger the slice, the more
-important is the variable to predict accurately this class. The right
-plot shows the drone raw and standardised reflectance spectra of each
-class. Each slice represent the VIP of both raw and standardised
-reflectance combined.}
+important the variable for prediction of each class. The right plot
+shows the drone raw and standardised reflectance spectra of each class.
+Each slice represents the VIP of both raw and standardised reflectance
+combined.}
 
@@
 The computation of the variable importance made it possible to identify
-which wavelengths were the most useful for class prediction
+which bands were the most useful for class prediction
 (Figure~\ref{fig-VIP}). The spectral bands at 444, 717 and 842 nm of the
@@
 altitude flight pixels of Gafanha, Portugal. Each subplot shows all the
-pixels of the same classes on the hight altitude flight. Percent cover
-of classes was retrieved using the result of the classification of the
-low altitude flight of Gafanha, Portugal. The vertical dashed line shows
-the 0.85 probability of the model. Everything on the right of this line
-has a probability higher then 0.85 and everything on the left of this
-line has a lower probability.}
+pixels of the same classes on the high altitude flight. Percent cover of
+classes was retrieved using the result of the classification of the low
+altitude flight of Gafanha, Portugal. The vertical dashed line shows the
+0.85 probability of the model. Everything on the right of this line has
+a probability higher then 0.85 and everything on the left of this line
+has a lower probability.}
 
@@
 Using the very high resolution low altitude flight, we determined the
-minimal percent cover required to classify correctly a given class using
-the high altitude flight (Figure~\ref{fig-upscaling}). When the percent
-cover of the class was 100 \%, coarser high-flight pixels are well
-classified for all the classes except for Bare Sediment, which was well
-classified 80\% of the time. This phenomenon is likely attributed to the
-time gap between the two flights, allowing for microphytobenthos
-migration, consequently altering the model's classification from bare
-sediment to Bacillariophyceae. A percent cover of at least 80\% was
-needed to have all the low resolution pixels well classified, at the
-exception of Magnoliopsida that needs a higher percent cover
-(\textgreater90 \%) to be well classified. Concerning the probability of
-each class, the highest percent cover was needed to confidently predict
+minimal percent cover required to correctly a given class using the high
+altitude flight (Figure~\ref{fig-upscaling}). When the percent cover of
+the class was 100 \%, coarser high-flight pixels are well classified for
+all the classes except for Bare Sediment, which was only well classified
+80\% of the time. This phenomenon is likely attributed to the time gap
+between the two flights, allowing for microphytobenthos migration,
+consequently altering the model's classification from bare sediment to
+Bacillariophyceae. A percent cover of at least 80\% was needed to have
+all the low resolution pixels well classified, with the exception of
+Magnoliopsida that needed a higher percent cover (\textgreater90 \%) to
+be well classified. Concerning the probability of each class, the
+highest percent cover was needed to confidently predict
 Bacillariophyceae. To predict Chlorophyceae with a confidence of 0.85, a
@@
 seagrasses from green macroalgae presents significant challenges
-\citetext{\citealp[ ]{oiry2021using}; \citealp{bannari2022}}, primarily
-due to the shared pigment composition between these taxa
-\citep{mckenzie2020global}, as depicted in Figure~\ref{fig-Pigm} but
-also by the frequent spatial mixing of these green macrophytes. These
-green macrophytes have in common photosynthtic pigmetns, chlorophyll a
-and b, and accessory carotenoid pigments zeaxantin, lutein and
-neoxanthin. As a result the spectral signatures are often
-indistinguishable in the visible wavelength region. This spectral
-overlap is further complicated by the intermingling of seagrasses and
-green macroalgae in the same spatial locations, posing a significant
-challenge for remote sensing aimed at accurately mapping and monitoring
-coastal ecosystems. Our study addresses these complexities by using
-high-resolution drone imagery with 10 spectral bands. \citep{Davies2023}
-have shown that having at least eight spectral bands ranging between 500
-nm to 850 nm including a green band at 530 nm and another one in the
-RedEdge region at 730 nm was crucial to accurately discriminate green
-macrophytes.
+\citetext{\citealp[ ]{oiry2021using}; \citealp[
+]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
+the shared pigment composition between these taxa
+, Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
+these macrophytes. These green macrophytes have in common photosynthtic
+pigmetns, chlorophyll a and b, and accessory carotenoid pigments
+zeaxantin, lutein and neoxanthin. As a result the spectral signatures
+are often indistinguishable in the visible wavelength region. This
+spectral overlap is further complicated by the intermingling of
+seagrasses and green macroalgae in the same spatial locations, posing a
+significant challenge for remote sensing aimed at accurately mapping and
+monitoring coastal ecosystems. Our study addresses these complexities by
+using high-resolution drone imagery with 10 spectral bands.
+\citep{Davies2023} have shown that having at least eight spectral bands
+ranging between 500 nm to 850 nm including a green band at 530 nm and
+another one in the RedEdge region at 730 nm was crucial to accurately
+discriminate green macrophytes.
 
@@
 Figure~\ref{fig-Validation} focusing on green macrophytes. The labels
-inside the matrice indicate the number of pixels.}
-
-\end{figure}%
-
-The Micasense RedEdge-MX DUAL camera used in this study meets these two
-criteria, enabling the classifier to achieve 97\% of accuracy between
+inside the matrix indicate the number of pixels.}
+
+\end{figure}%
+
+Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in
+this study, enabled the classifier to achieve 97\% of accuracy between
 these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
@@
 accurately identifying Chlorophyceae. In fact, at this wavelength,
-Chlorophyceae exhibited the highest reflectance among all other classes,
-highlighting the difference in accessories carotenoid proportion between
-seagrasses and green macroalgae \citep{repolho2017seagrass}.
+Chlorophyceae exhibited the highest reflectance (raw and standardised)
+among all other classes, highlighting the difference in accessory
+pigments (i.e.~carotenoid) between seagrasses and green macroalgae
+\citep{repolho2017seagrass}.
 
@@
 Climate change, global warming, alien and invasive species development,
-coastal erosion, sealevel rise, while further impact coastal ecosystems
-in the future \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
-]{holon2018predictive}; \citealp{marquet2024global}}. The demand for
-meaningful and efficient monitoring methods for these habitats has
-therefore never been greater \citetext{\citealp[
+coastal erosion, sealevel rise, will continue to impact coastal
+ecosystems in the future
+\citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
+]{holon2018predictive}; \citealp{marquet2024global}}. Therefore the
+demand for meaningful and efficient monitoring methods for these
+habitats has never been greater \citetext{\citealp[
 ]{muller2018satellite}; \citealp[
@@
 time and resource-intensive, and the findings are often difficult to
-scale up. Earth observation methods can bridge this gap and meet the
+up-scale. Earth observation methods can bridge this gap and meet the
 needs for monitoring coastal ecosystems.
@@
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
-significance of monitoring coastal environment, particularly in light of
-the Water Framework Directive (WFD ; \citep{WFD2000}), cannot be
-overstated in environmental management and conservation efforts. The WFD
-mandates the achievement and maintenance of ``good ecological status''
-for all European waters, which necessitates a comprehensive
+significance of monitoring the coastal environment, particularly in
+light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
+be overstated in environmental management and conservation efforts. The
+WFD mandates the achievement and maintenance of ``good ecological
+status'' for all European waters, which necessitates a comprehensive
 understanding and monitoring of aquatic ecosystems, including coastal
@@
 the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral
-imagery, flight on demand, provide a novel and powerful means to rapidly
-and accurately acquire ground truth data (i.e.~output of the model used
-in the present study). These data are critical for calibrating and
+Drones, with their capability for high-resolution, multispectral imagery
+and, flight on demand, provide a novel and powerful means to rapidly and
+accurately acquire ground truth data (i.e.~output of the model used in
+the present study). These data are critical for calibrating and
 validating satellite remote sensing applications, thereby enhancing our
 capacity to monitor vast coastal areas systematically under the WFD
-framework. A perspective of this work is to adapt the algorithm for
-Sentinel-2 to see of the discrimination between seagrass and green
-macroalgae is still operational at a coarser spatial resolution. The
-integration of drone technology facilitates a scalable approach to
-environmental surveillance, offering significant advancements in the
-spatial and temporal resolution of data collection. This, in turn,
-supports the directive's objectives by enabling more informed and timely
-management decisions for the preservation and restoration of aquatic
-ecosystems.
+framework. A perspective of this work could be to aid algorithm applied
+to satellite imagery (e.g.~Sentinel-2) to see of the discrimination
+between seagrass and green macroalgae is still operational at a coarser
+spatial resolution. The integration of drone technology facilitates a
+scalable approach to environmental surveillance, offering significant
+advancements in the spatial and temporal resolution of data collection.
+This, in turn, supports the directive's objectives by enabling more
+informed and timely management decisions for the conservation and
+restoration of aquatic ecosystems.
 
@@
 data have the potential to perform this discrimination between green
-macrophytes. The algorithm should now be adapted to Sentinel-2 with all
-the drone data from this study that can be used as training and
-validation data. The findings underscore the importance of adopting
-advanced remote sensing tools in ecological studies and environmental
-monitoring, providing a foundation for future research and policy
-implementation aimed at ecosystem preservation and restoration.
+macrophytes. The algorithm could be adapted to Sentinel-2 with all the
+drone data from this study that can be used as training and validation
+data. The findings underscore the importance of adopting advanced remote
+sensing tools in ecological studies and environmental monitoring,
+providing a foundation for future research and policy implementation
+aimed at ecosystem conservation and restoration.
 

### 2024-03-11 index.qmd
Bede's comments

@@
 abstract: |
-  Coastal areas host seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration.
+  Coastal areas support seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration.
 However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation.
@@
 To address these challenges and reduce the issue of mlixed pixel, drone images at a very high spatial resolution offer a promising solution.
-This study focuses on using drone acquisitions with a ten spectral bands sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
-Nine drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal.
+This study focuses on using drone acquisitions with a ten spectral band sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
+Nine drone flights were conducted at two different altitudes (12m and 120m) across heterogeneous European habitats in France and Portugal.
 Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and Bacillariophyceae (Diatoms).
-Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
+Classification of drone imagery resulted in an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
 The model exhibited an accuracy of 96.4% in identifying seagrass.
@@
 
-Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
+Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between the land and oceans [@unsworth2022].
 Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and limitation of eutrophication.
@@
 Due to the concentration of human activities in coastal zones, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019].
+Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
 While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been ass ociated to anomalous accumulation of green macroalgae, the so-called green tides (@devlin2023nutrients).
+Coastal eutrophication has been ass ociated to excessive accumulation of green macroalgae, so-called green tides (@devlin2023nutrients).
 Green tides produce shade and suffocation over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
@@
 The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, population abundance, and phenology [@Pereira2013].
-Seagrass monitoring is all the more important as it makes possible to identify which pressure should be addressed in priority to facilitate effective mitigation actions.
 Traditionally, indicators of seagrass status have been quantified using *in situ* measurements.
@@
 
-While satellite remote sensing provides temporally consistent observations over large spatial scales, it is limited by several constraints.
+While satellite remote sensing (RS) provides temporally consistent observations over large spatial scales, it is limited by several constraints.
 Satellite missions with a high temporal resolution (e.g.
 daily MODIS observation) are limited by a coarse spatial resolution (\>100m).
-Mission with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
+Missions with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
 The limited number of spectral bands is indeed a challenge to accurately discriminate seagrass from others co-existing macrophytes.
 In particular Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
-As a result, their respective spectral signatures can be considered similar by a non-expert observer [@Davies2023 ; @bannari2022].
+Therefore, to someone not specialized in the field, their spectral signatures may appear to be alike [@Davies2023 ; @bannari2022].
 Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
-The application of this approach to satellite remote sensing remains however to be validated.
-Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of the event.
-
-Drones can potentially fill the gaps left by satellite remote sensing and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) and still capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+However the application of this approach to satellite RS remains to be validated.
+Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of th
+
+Drones can potentially fill the gaps left by satellite RS and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
-However, when applied to coastal habitat mapping, most study cases were limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-The present study aimed at analyzing the potential of multispectral drone remote sensing to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae.
+However, when applied to coastal habitat mapping, most case studies are limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
@@
 Seven study sites distributed between France and Portugal were selected for their relatively extensive intertidal seagrass beds.
-Two sites are located in Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
+Two sites are located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
 This gulf covers an area of 115 km² and is only connected to the sea through a 900m wide channel.
@@
 Patchy seagrass meadows can be found on a lot of these islands.
-Within the Gulf of Morbihan we have chosen two sites : one is located in one of these island (Arz island); the other one is located in the southern part of the gulf (Duer).
-Two others sites are located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
+Within the Gulf of Morbihan we chose two sites : one located on one of the gulf's islands (Arz island) and the other located in the southern part of the gulf (Duer).
+Two other sites were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
 This bay is 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
 Bougneuf bay hosts a large intertidal seagrass meadow of about 6 km².
-Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contain a monospecific bed of *Zostera noltei* with very little mixing with other macrophytes.
-Three sites have been surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
+Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained a monospecific bed of *Nanozostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
+Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
 The extent of this lagoon is about 80 km² with many narrow channels, large salt marshes and many mudflats that uncovers at low tide.
 It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) is a mudflat located in an affluent of the lagoon whereas the two other sites are situated in the middle of the lagoon and are only accessible by boat (@fig-map C).
-These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass could intermingle with red, brown and green macroalgae.
+The southernmost site (Gafanha) was a mudflat located in a tributary river of the lagoon whereas the two other sites were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
+These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown and green macroalgae.
 
@@
 #| fig-cap: >
-#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Lagoon (Three sites). Green represent intertidal areas. 
+#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represent intertidal areas. 
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs in ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
-An angle of 90° was maintained between the sun and the drone's route to guarantee uniform lighting conditions between flight lines.
-A side overlap of 70% and a front overlap of 80% between each image was set for each flight.
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
+To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees.
+An overlap of 70% and 80% (side and front respectively) between each image was set for each flight.
 A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements.
@@
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming large biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
-Pictures of each quadrat were uploaded online on the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
+dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
 Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software (imageJ).
@@
 Hyperspectral signatures from quadrats serve dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
-The workflow developped in this study is presented in @fig-workflow.
+The workflow developed in this study is presented in @fig-workflow.
 
@@
 The spectral similarities of the reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
-To overcome this challenge, a deep learning classification method was developed, trained, validated, and applied to each drone flight (@fig-workflow).
+To overcome this challenge, a deep learning classification method was trained, validated, and applied to each drone flight (@fig-workflow).
 
@@
 The model was applied to all flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
+In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy, including.
 These images were used to construct a validation dataset indicating the presence or absence of each class.
@@
 
+## Variable Importance Plots (VIP)
+
+## Impact of the percent cover on the prediction
+
 # Results
@@
 There was also Bacillariophyceae forming biofilms on parts of sediment surface.
-Although the seagrass bed was solely composed of *Zostera noltei*, various colors of this could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
-Regardless of color, the meadow was predicted as Magnoliopsida by the model.
+Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
+Regardless of color, the meadow was accurately predicted as Magnoliopsida by the model.
 
@@
 #| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanha, Portugal.
-The total extent of this flight is 3000m² with a resolution of 8 mm per pixel.
+The total extent of this flight was 3000m² with a resolution of 8 mm per pixel.
 Background colors indicate intertidal area (Light Green) and land area (Light Grey).
@@
 The high-altitude flight over Gafanha covered nearly 1 km² in total (@fig-GafHigh).
-A channel delineating a small island was masked in the prediction map due to sunglint and misclassification caused by the turbid shallow water.
+A channel delineating a small island was masked in the prediction map.
 Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
@@
 #| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanha, Portugal.
-The total extent of this flight is about 1 km² with a resolution of 80 mm per pixel.
+The total extent of this flight was about 1 km² with a resolution of 80 mm per pixel.
 Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
@@
 #| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
-The total extent of this flight is about 1.5 km² with a resolution of 80 mm per pixel.
+The total extent of this flight was about 1.5 km² with a resolution of 80 mm per pixel.
 Background colors indicates intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
@@
 #| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the Northern part of Noirmoutier Island, France.
-The total extent of this flight is about 28 000 m² with a resolution of 80 mm per pixel.
+The total extent of this flight was about 28 000 m² with a resolution of 80 mm per pixel.
 Background colors indicate intertidal area (Light Green) and land area (Light Grey).
@@
 
-ggsave("Figures/Validation/ConfusionMatrixGlobal.png",plot_matrix_global , width = 1920*4, height = 1032*4, units = "px")
+ggsave("Figures/High_res/Validation/ConfusionMatrixGlobal.png",plot_matrix_global , width = 1920*4, height = 1032*4, units = "px")
 
@@
                      limits = c(0,2))+
-  geom_label(data = labels_green,aes(x = x, y = y, label = label ))+
+  geom_label(data = labels_green,aes(x = x, y = y, label = label), size = 10)+
   xlab("References")+
@@
 
-ggsave("./Figures/Validation/ConfusionMatrixGreen.png", plot_green, width = 671*4, height = 479*4, units = "px" )
+ggsave("./Figures/High_res/Validation/ConfusionMatrixGreen.png", plot_green, width = 671*4, height = 479*4, units = "px" )
 
@@
 
-A total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the Neural Network classifier.
+A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
 The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
 Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
-The least performing site was `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`%) whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` was the site with the most accurate prediction (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%).
+The lowest performing site was `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`%) whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` was the site with the most accurate prediction (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%).
 Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were correctly classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
@@
 #| fig-cap: Variable Importance of the Neural Network Classifier for each taxonomic class.
-The bigger the slice, the more important is the variable to predict accurately this class.
+The bigger the slice, the more important the variable for prediction of each class.
 The right plot shows the drone raw and standardised reflectance spectra of each class.
-Each slice represent the VIP of both raw and standardised reflectance combined.
+Each slice represents the VIP of both raw and standardised reflectance combined.
 #| label: fig-VIP
@@
 
-The computation of the variable importance made it possible to identify which wavelengths were the most useful for class prediction (@fig-VIP).
+The computation of the variable importance made it possible to identify which bands were the most useful for class prediction (@fig-VIP).
 The spectral bands at 444, 717 and 842 nm of the Micasense camera did not came out as important for any of the vegetation classes.
@@
 #| fig-cap: Kernel density plot showing the proportion of pixel well classified based on the percent cover of the class in high altitude flight pixels of Gafanha, Portugal.
-Each subplot shows all the pixels of the same classes on the hight altitude flight.
+Each subplot shows all the pixels of the same classes on the high altitude flight.
 Percent cover of classes was retrieved using the result of the classification of the low altitude flight of Gafanha, Portugal.
@@
 
-Using the very high resolution low altitude flight, we determined the minimal percent cover required to classify correctly a given class using the high altitude flight (@fig-upscaling).
-When the percent cover of the class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was well classified 80% of the time.
+Using the very high resolution low altitude flight, we determined the minimal percent cover required to correctly a given class using the high altitude flight (@fig-upscaling).
+When the percent cover of the class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
 This phenomenon is likely attributed to the time gap between the two flights, allowing for microphytobenthos migration, consequently altering the model's classification from bare sediment to Bacillariophyceae.
-A percent cover of at least 80% was needed to have all the low resolution pixels well classified, at the exception of Magnoliopsida that needs a higher percent cover (\>90 %) to be well classified.
+A percent cover of at least 80% was needed to have all the low resolution pixels well classified, with the exception of Magnoliopsida that needed a higher percent cover (\>90 %) to be well classified.
 Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
@@
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022], primarily due to the shared pigment composition between these taxa [@mckenzie2020global], as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the shared pigment composition between these taxa [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
 These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin.
@@
 #| warning: false
-#| fig-cap: Sample of @fig-Validation focusing on green macrophytes. The labels inside the matrice indicate the number of pixels.
+#| fig-cap: Sample of @fig-Validation focusing on green macrophytes. The labels inside the matrix indicate the number of pixels.
 #| label: fig-ValidationGreen
@@
 ::: column
-The Micasense RedEdge-MX DUAL camera used in this study meets these two criteria, enabling the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
+Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in this study, enabled the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
 Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
@@
 The VIP analysis of the Neural Network model (@fig-VIP) identified that the 531 nm band as the most important spectral band for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green macroalgae [@repolho2017seagrass].
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the difference in accessory pigments (i.e.
+carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].
 
@@
 
-Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, while further impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
-The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
+Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, will continue to impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
+Therefore the demand for meaningful and efficient monitoring methods for these habitats has never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
 Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation taxonomic classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
-Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up.
+Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale.
 Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems.
@@
 The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
-The significance of monitoring coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
+The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
 The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
@@
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral imagery, flight on demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
+Drones, with their capability for high-resolution, multispectral imagery and, flight on demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
 output of the model used in the present study).
 These data are critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework.
-A perspective of this work is to adapt the algorithm for Sentinel-2 to see of the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
+A perspective of this work could be to aid algorithm applied to satellite imagery (e.g.
+Sentinel-2) to see of the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
-This, in turn, supports the directive's objectives by enabling more informed and timely management decisions for the preservation and restoration of aquatic ecosystems.
+This, in turn, supports the directive's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
 
@@
 As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green macrophytes.
-The algorithm should now be adapted to Sentinel-2 with all the drone data from this study that can be used as training and validation data.
-The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem preservation and restoration.
+The algorithm could be adapted to Sentinel-2 with all the drone data from this study that can be used as training and validation data.
+The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.

### 2024-03-12 docs/_tex/index.tex
fig updated

@@
 pixel. Background colors indicate intertidal area (Light Green), land
-area (Light Grey) and water (Light Blue). The red triangle shows the
+area (Light Grey) and water (Light Blue). The yellow polygon shows the
 extent of the low altitude flight of Gafanha presented in
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{index_files/figure-pdf/fig-CompareRef-1.pdf}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
 
@@
 \caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
-both low-altitude and high-altitude flights over a common area. The red
-dashed line represents a linear model whereas the black dashed line
-represents a 1 to 1 relationship. Left (A) plots raw data and right (B)
-plots standardised data.}
+both low-altitude and high-altitude flights over a common area. The
+black dashed line represents a 1 to 1 relationship. Left (A) plots raw
+data and right (B) plots standardised data.}
 

### 2024-03-12 index.qmd
fig updated

@@
 Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The red triangle shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
+The yellow polygon shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
 
-high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
-  rast()
-
-# low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
 #   rast()
-
-low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
-  rast() %>% 
-  resample(high_alt, method = "med")
-
-low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
-  rast()
-
-mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
-  vect()
-
-high_alt_masked<-crop(high_alt,mask)
-high_alt_masked<-mask(high_alt_masked,mask)
-
-low_alt_masked<-crop(low_alt,mask)
-low_alt_masked<-mask(low_alt_masked,mask)
-
-low_alt_pred_masked<-crop(low_alt_pred,mask)
-low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
-
-stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
-  as.data.frame()
-
-names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
-              "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
-              "pred")
-
-stk_long<-stk %>% 
-  mutate(px_ID = c(1:nrow(stk))) %>% 
-  pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
-  mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
-                         str_detect(Bands, "high") ~ "High",
-                         TRUE ~ "NA"),
-         Bands = gsub("_high","",Bands),
-         Bands = gsub("_low","",Bands))
-
-stk_summarized<-stk_long %>% 
-  # group_by(px_ID,alt) %>% 
-  # reframe(Value = mean(Value),
-  #         pred = unique(pred)) %>% 
-  pivot_wider(names_from = "alt", values_from = "Value")
-
-df<-stk_summarized %>% 
-  ungroup() %>% 
-  group_by(Bands) %>% 
-  filter(Low<10000,
-         High < 10000,
-         Low < quantile(Low,probs = 0.99),
-         High < quantile(High,probs = 0.99),
-         Low > quantile(Low,probs = 0.01),
-         High > quantile(High,probs = 0.01),
-         !pred %in% c(7,9,3,10)) %>%
-  ungroup()
-
-plot <- df %>% 
-  group_by(pred) %>% 
-  sample_n(10000) %>% 
+# 
+# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+# #   rast() 
+# 
+# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
+#   rast() %>% 
+#   resample(high_alt, method = "med")
+# 
+# 
+# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
+#   rast() 
+# 
+# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
+#   vect()
+#   
+# high_alt_masked<-crop(high_alt,mask)
+# high_alt_masked<-mask(high_alt_masked,mask)
+# 
+# low_alt_masked<-crop(low_alt,mask)
+# low_alt_masked<-mask(low_alt_masked,mask)
+# 
+# low_alt_pred_masked<-crop(low_alt_pred,mask)
+# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
+# 
+# 
+# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
+#   as.data.frame()
+# 
+# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
+#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
+#               "pred")
+# 
+# stk_long<-stk %>% 
+#   mutate(px_ID = c(1:nrow(stk))) %>% 
+#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
+#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
+#                          str_detect(Bands, "high") ~ "High",
+#                          TRUE ~ "NA"),
+#          Bands = gsub("_high","",Bands),
+#          Bands = gsub("_low","",Bands))
+# 
+# 
+# stk_summarized<-stk_long %>% 
+#   # group_by(px_ID,alt) %>% 
+#   # reframe(Value = mean(Value),
+#   #         pred = unique(pred)) %>% 
+#   pivot_wider(names_from = "alt", values_from = "Value")
+# 
+# df<-stk_summarized %>% 
+#   ungroup() %>% 
+#   group_by(Bands) %>% 
+#   filter(Low<10000,
+#          High < 10000,
+#          Low < quantile(Low,probs = 0.99),
+#          High < quantile(High,probs = 0.99),
+#          Low > quantile(Low,probs = 0.01),
+#          High > quantile(High,probs = 0.01),
+#          !pred %in% c(7,9,3,10)) %>%
+#   ungroup()
+
+RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
   mutate(Low = Low /10000,
-         High = High/10000) %>% 
+         High = High/10000)
+
+RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
+lm_raw <- lm(RAW$High ~ RAW$Low)
+
+STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
+
+RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
+lm_STD <- lm(STD$High ~ STD$Low)
+
+plot_RAW <- RAW %>%  
   ggplot(aes(x=Low, y=High))+
@@
   geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
   theme_Bede()+
@@
         legend.key.width = unit(3,"line"))
-plot
-ggsave("./Figures/Compare_reflectance.png",plot, width= 472*4, height=402*4, units = "px")
+
+plot_STD <- STD %>%  
+    ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(1,2000),
+                               breaks = c(1,1000,2000),
+                               labels = c("1","1000","2000"))+
+  # scale_color_gradient(na.value = 1)+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,1))+
+  xlim(c(0.05,1))+
+  ylab("Standardised reflectance of the 120m flight")+
+  xlab("Standardised reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
+ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
 
@@
 
-```{r}
-#| cache: false
+```{r ref_compare_building}
+#| cache: true
 #| echo: false
+#| eval: false
 #| warning: false
-#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
-The red dashed line represents a linear model whereas the black dashed line represents a 1 to 1 relationship.
-Left (A) plots raw data and right (B) plots standardised data.
-#| label: fig-CompareRef
-#| fig-width: 10
-#| fig-height: 5
-#| out-width: "100%"
 
 RAW <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance.png"))+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
   coord_equal()+
@@
 STD <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance_std.png"))+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
   coord_equal()+
@@
 
-RAW+STD
+plot <- RAW+STD
+
+ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
+```
+
+```{r RefComapare}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
+The black dashed line represents a 1 to 1 relationship.
+Left (A) plots raw data and right (B) plots standardised data.
+#| label: fig-CompareRef
+#| fig-width: 10
+#| fig-height: 5
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
 

### 2024-03-12 index.qmd
fig updated

@@
 
-## Drone Data
+## Field sampling
+
+### Drone acquisition
 
@@
 Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer.
-A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
-The workflow for orthomosaicking was the same for every flight.
-First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
-This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
-A dense point cloud was then produced using a structure from motion algorithm.
-A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
 Across all sites, flights were made at two different altitudes : 12 m or/and 120 m.
-Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
-High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
+(@tbl-flights).
 
@@
 
-## Field sampling
+### Ground Control Points
 
@@
 
-## Intertidal vegetation mapping
+## Drone Processing
+
+A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
+The workflow for orthomosaicking was the same for every flight.
+First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
+This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
+A dense point cloud was then produced using a structure from motion algorithm.
+A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
+Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
+High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
+
+## General Workflow
 
@@
 
+Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
+This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time.
+The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables.
+The greater the difference between these two benchmark values, the more important the variable is for the model (@WEI2015399).
+
 ## Impact of the percent cover on the prediction
+
+The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm).
+The predictions made on the high-resolution flight can be used to estimate the percent cover of each vegetation class for every pixel of the lower resolution flight.
+Consequently, for each pixel of the high-altitude flights, percent covers of each vegetation class were obtained, and a kernel density plot was generated.
+This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
 

### 2024-03-12 docs/_tex/index.tex
fig updated
Bede's comments done

@@
 
-\subsection{Drone Data}\label{drone-data}
+\subsection{Field sampling}\label{field-sampling}
+
+\subsubsection{Drone acquisition}\label{drone-acquisition}
 
@@
 calibrated in reflectance using a calibration panel reflective at
-\textasciitilde50\% provided by the manufacturer. A
-structure-from-motion photogrammetry software (Agisoft Metashape) was
-used to process images to obtain multispectral orthomosaics of each
-flight. The workflow for orthomosaicking was the same for every flight.
-First, tying key points were detected inside of each image and between
-overlapping images in order to obtain a sparse point cloud. This cloud
-was cleaned using reprojection accuracy metric in order to remove noisy
-points. A dense point cloud was then produced using a structure from
-motion algorithm. A surface interpolation of this dense point cloud was
-made to obtain a digital surface model (DSM), used to reconstruct the
-multispectral ortho-image. Across all sites, flights were made at two
-different altitudes : 12 m or/and 120 m. Low altitude drone flights
-produce ortho-images with a very high spatial resolution (8 mm per
-pixel), making it efficient to visually distinguish between the various
-types of vegetation. High altitude fights on the other hand allow to
-cover large areas and produced images with a pixel size of 80 mm
+\textasciitilde50\% provided by the manufacturer. Across all sites,
+flights were made at two different altitudes : 12 m or/and 120 m.
 (Table~\ref{tbl-flights}).
@@
 
-\subsection{Field sampling}\label{field-sampling}
+\subsubsection{Ground Control Points}\label{ground-control-points}
 
@@
 
-\subsection{Intertidal vegetation
-mapping}\label{intertidal-vegetation-mapping}
+\subsection{Drone Processing}\label{drone-processing}
+
+A structure-from-motion photogrammetry software (Agisoft Metashape) was
+used to process images to obtain multispectral orthomosaics of each
+flight. The workflow for orthomosaicking was the same for every flight.
+First, tying key points were detected inside of each image and between
+overlapping images in order to obtain a sparse point cloud. This cloud
+was cleaned using reprojection accuracy metric in order to remove noisy
+points. A dense point cloud was then produced using a structure from
+motion algorithm. A surface interpolation of this dense point cloud was
+made to obtain a digital surface model (DSM), used to reconstruct the
+multispectral ortho-image. Low altitude drone flights produce
+ortho-images with a very high spatial resolution (8 mm per pixel),
+making it efficient to visually distinguish between the various types of
+vegetation. High altitude fights on the other hand allow to cover large
+areas and produced images with a pixel size of 80 mm
+(Table~\ref{tbl-flights}).
+
+\subsection{General Workflow}\label{general-workflow}
 
@@
 
+Variable Importance Plots (VIP) serve as a method to identify which
+predictors are important for predicting a specific class. This is
+achieved by repeatedly predicting the same dataset while shuffling one
+predictor at a time. The benchmark score obtained after each iteration
+is then compared to the benchmark score obtained without shuffling any
+variables. The greater the difference between these two benchmark
+values, the more important the variable is for the model
+\citep{WEI2015399}.
+
 \subsection{Impact of the percent cover on the
 prediction}\label{impact-of-the-percent-cover-on-the-prediction}
+
+The key aspect of the workflow adopted in the present study is the
+mapping of specific areas at two different altitudes (12m and 120m),
+resulting in two distinct resolutions for the same area (8mm and 80mm).
+The predictions made on the high-resolution flight can be used to
+estimate the percent cover of each vegetation class for every pixel of
+the lower resolution flight. Consequently, for each pixel of the
+high-altitude flights, percent covers of each vegetation class were
+obtained, and a kernel density plot was generated. This plot provides a
+visual representation of the behavior of the model in different
+vegetation percent cover scenarios.
 
@@
 \subsection{Validation}\label{validation-1}
+
+\subsubsection{Reflectance comparison between the two different
+altitudes}\label{reflectance-comparison-between-the-two-different-altitudes}
+
+\phantomsection\label{cell-fig-CompareRef}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
+
+}
+
+\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
+both low-altitude and high-altitude flights over a common area. The
+black dashed line represents a 1 to 1 relationship. Left (A) plots raw
+data and right (B) plots standardized data (Equation~\ref{eq-std}).}
+
+\end{figure}%
+
+In this study, a key innovation lies in the utilization of two different
+altitudes (12m and 120m) for constructing the neural network model. The
+lower altitude flights (8mm spatial resolution) enabled precise
+selection of pure pixels representing the classes used in the neural
+network model. This methodology implies a consistency between the
+reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
+relationship between reflectance from a low-altitude flight and a
+high-altitude flight conducted over the same area. Overall there was a
+good agreement between the two altitudes. There was however a slight
+underestimation for raw reflectance values in the high-altitude flight,
+particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
+both flights were conducted over vegetation areas, the highest
+reflectance values correspond to the infrared part of the spectrum. This
+different is not present anymore when reflectance values of both flights
+have been standardized (Equation~\ref{eq-std} ;
+Figure~\ref{fig-CompareRef} B).
+
+\subsubsection{Neural network classification
+validation}\label{neural-network-classification-validation}
 
@@
 
-\phantomsection\label{cell-fig-CompareRef}
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
-
-}
-
-\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
-both low-altitude and high-altitude flights over a common area. The
-black dashed line represents a 1 to 1 relationship. Left (A) plots raw
-data and right (B) plots standardised data.}
-
-\end{figure}%
-
-In this study, a key innovation lies in the utilization of two different
-altitudes (12m and 120m) for constructing the neural network model. The
-lower altitude flights (8mm spatial resolution) enabled precise
-selection of pure pixels representing the classes used in the neural
-network model. This methodology implies a consistency between the
-reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
-relationship between reflectance from a low-altitude flight and a
-high-altitude flight conducted over the same area. Overall there was a
-good agreement between the two altitudes. There was however a slight
-underestimation for raw reflectance values in the high-altitude flight,
-particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
-both flights were conducted over vegetation areas, the highest
-reflectance values correspond to the infrared part of the spectrum.
-
-The disparity in infrared reflectance may stem from temporal differences
-between the flights, possibly resulting in a slightly drier intertidal
-area and consequently higher infrared reflectance. This disparity poses
-an issue for the methodology followed in the present study, relying
-solely on one flight height for training. To address this issue, we
-employed min/max standardized reflectance spectra as predictors for the
-model (Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allowed
-us to eliminate the slight reflectance difference between the flights
-(Figure~\ref{fig-CompareRef} B) and to focus on the shape of the spectra
-in the visible part of the electromagnetic spectra, where different
-pigmentation are associated to taxonomic dignostic features. This was a
-key feature in building a model that could reliably predict vegetation
-across geographical sites and seasons. It enabled consistent prediction
-of vegetation classes across variations in biomass and variability in
-light conditions \citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
+While comparing the reflectance of both altitudes (12 m and 120 m), it
+was observed Figure~\ref{fig-CompareRef} that there is an
+underestimation of the infrared part of the spectra in the high-altitude
+dataset. The disparity in infrared reflectance may stem from temporal
+differences between the flights, possibly resulting in a slightly drier
+intertidal area and consequently higher infrared reflectance. This
+disparity poses an issue for the methodology followed in the present
+study, relying solely on one flight height for training. To address this
+issue, we employed min/max standardized reflectance spectra as
+predictors for the model (Equation~\ref{eq-std} ; \citep{Cao2017}). This
+approach allowed us to eliminate the slight reflectance difference
+between the flights (Figure~\ref{fig-CompareRef} B) and to focus on the
+shape of the spectra in the visible part of the electromagnetic spectra,
+where different pigmentation are associated to taxonomic dignostic
+features. This was a key feature in building a model that could reliably
+predict vegetation across geographical sites and seasons. It enabled
+consistent prediction of vegetation classes across variations in biomass
+and variability in light conditions \citetext{\citealp[
+]{fyfe2003spatial}; \citealp[
 ]{COSTA2021107018}; \citealp{piaser2023impact}}.

### 2024-03-12 index.qmd
Bede's comments done

@@
 The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables.
-The greater the difference between these two benchmark values, the more important the variable is for the model (@WEI2015399).
+The greater the difference between these two benchmark values, the more important the variable is for the model [@WEI2015399].
 
@@
 ## Validation
+
+### Reflectance comparison between the two different altitudes
+```{r Reflectance_Validation 2 height}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
+#   rast()
+# 
+# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+# #   rast() 
+# 
+# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
+#   rast() %>% 
+#   resample(high_alt, method = "med")
+# 
+# 
+# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
+#   rast() 
+# 
+# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
+#   vect()
+#   
+# high_alt_masked<-crop(high_alt,mask)
+# high_alt_masked<-mask(high_alt_masked,mask)
+# 
+# low_alt_masked<-crop(low_alt,mask)
+# low_alt_masked<-mask(low_alt_masked,mask)
+# 
+# low_alt_pred_masked<-crop(low_alt_pred,mask)
+# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
+# 
+# 
+# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
+#   as.data.frame()
+# 
+# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
+#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
+#               "pred")
+# 
+# stk_long<-stk %>% 
+#   mutate(px_ID = c(1:nrow(stk))) %>% 
+#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
+#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
+#                          str_detect(Bands, "high") ~ "High",
+#                          TRUE ~ "NA"),
+#          Bands = gsub("_high","",Bands),
+#          Bands = gsub("_low","",Bands))
+# 
+# 
+# stk_summarized<-stk_long %>% 
+#   # group_by(px_ID,alt) %>% 
+#   # reframe(Value = mean(Value),
+#   #         pred = unique(pred)) %>% 
+#   pivot_wider(names_from = "alt", values_from = "Value")
+# 
+# df<-stk_summarized %>% 
+#   ungroup() %>% 
+#   group_by(Bands) %>% 
+#   filter(Low<10000,
+#          High < 10000,
+#          Low < quantile(Low,probs = 0.99),
+#          High < quantile(High,probs = 0.99),
+#          Low > quantile(Low,probs = 0.01),
+#          High > quantile(High,probs = 0.01),
+#          !pred %in% c(7,9,3,10)) %>%
+#   ungroup()
+
+RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
+  mutate(Low = Low /10000,
+         High = High/10000)
+
+RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
+lm_raw <- lm(RAW$High ~ RAW$Low)
+
+STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
+
+RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
+lm_STD <- lm(STD$High ~ STD$Low)
+
+plot_RAW <- RAW %>%  
+  ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(0,6000),
+                               breaks = c(0,2000,4000,6000),
+                               labels = c("1","2000","4000","6000"))+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,0.6))+
+  xlim(c(0.05,0.6))+
+  ylab("Reflectance of the 120m flight")+
+  xlab("Reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+plot_STD <- STD %>%  
+    ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(1,2000),
+                               breaks = c(1,1000,2000),
+                               labels = c("1","1000","2000"))+
+  # scale_color_gradient(na.value = 1)+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,1))+
+  xlim(c(0.05,1))+
+  ylab("Standardised reflectance of the 120m flight")+
+  xlab("Standardised reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
+ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
+
+```
+
+```{r ref_compare_building}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+RAW <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+STD <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+plot <- RAW+STD
+
+ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
+```
+
+```{r RefComapare}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
+The black dashed line represents a 1 to 1 relationship.
+Left (A) plots raw data and right (B) plots standardized data (@eq-std).
+#| label: fig-CompareRef
+#| fig-width: 10
+#| fig-height: 5
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
+
+```
+
+In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
+The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model.
+This methodology implies a consistency between the reflectance of both altitude.
+@fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
+Overall there was a good agreement between the two altitudes.
+There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A).
+Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
+This different is not present anymore when reflectance values of both flights have been standardized (@eq-std ; @fig-CompareRef B).
+
+### Neural network classification validation
 
@@
 
-```{r Reflectance_Validation 2 height}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
-#   rast()
-# 
-# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
-# #   rast() 
-# 
-# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
-#   rast() %>% 
-#   resample(high_alt, method = "med")
-# 
-# 
-# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
-#   rast() 
-# 
-# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
-#   vect()
-#   
-# high_alt_masked<-crop(high_alt,mask)
-# high_alt_masked<-mask(high_alt_masked,mask)
-# 
-# low_alt_masked<-crop(low_alt,mask)
-# low_alt_masked<-mask(low_alt_masked,mask)
-# 
-# low_alt_pred_masked<-crop(low_alt_pred,mask)
-# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
-# 
-# 
-# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
-#   as.data.frame()
-# 
-# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
-#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
-#               "pred")
-# 
-# stk_long<-stk %>% 
-#   mutate(px_ID = c(1:nrow(stk))) %>% 
-#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
-#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
-#                          str_detect(Bands, "high") ~ "High",
-#                          TRUE ~ "NA"),
-#          Bands = gsub("_high","",Bands),
-#          Bands = gsub("_low","",Bands))
-# 
-# 
-# stk_summarized<-stk_long %>% 
-#   # group_by(px_ID,alt) %>% 
-#   # reframe(Value = mean(Value),
-#   #         pred = unique(pred)) %>% 
-#   pivot_wider(names_from = "alt", values_from = "Value")
-# 
-# df<-stk_summarized %>% 
-#   ungroup() %>% 
-#   group_by(Bands) %>% 
-#   filter(Low<10000,
-#          High < 10000,
-#          Low < quantile(Low,probs = 0.99),
-#          High < quantile(High,probs = 0.99),
-#          Low > quantile(Low,probs = 0.01),
-#          High > quantile(High,probs = 0.01),
-#          !pred %in% c(7,9,3,10)) %>%
-#   ungroup()
-
-RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
-  mutate(Low = Low /10000,
-         High = High/10000)
-
-RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
-lm_raw <- lm(RAW$High ~ RAW$Low)
-
-STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
-
-RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
-lm_STD <- lm(STD$High ~ STD$Low)
-
-plot_RAW <- RAW %>%  
-  ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(0,6000),
-                               breaks = c(0,2000,4000,6000),
-                               labels = c("1","2000","4000","6000"))+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,0.6))+
-  xlim(c(0.05,0.6))+
-  ylab("Reflectance of the 120m flight")+
-  xlab("Reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-plot_STD <- STD %>%  
-    ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(1,2000),
-                               breaks = c(1,1000,2000),
-                               labels = c("1","1000","2000"))+
-  # scale_color_gradient(na.value = 1)+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,1))+
-  xlim(c(0.05,1))+
-  ylab("Standardised reflectance of the 120m flight")+
-  xlab("Standardised reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
-ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
-
-```
-
-```{r ref_compare_building}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-RAW <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-STD <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-plot <- RAW+STD
-
-ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
-```
-
-```{r RefComapare}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
-The black dashed line represents a 1 to 1 relationship.
-Left (A) plots raw data and right (B) plots standardised data.
-#| label: fig-CompareRef
-#| fig-width: 10
-#| fig-height: 5
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
-
-```
-
-In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
-The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model.
-This methodology implies a consistency between the reflectance of both altitude.
-@fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
-Overall there was a good agreement between the two altitudes.
-There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A).
-Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
-
+While comparing the reflectance of both altitudes (12 m and 120 m), it was observed @fig-CompareRef that there is an underestimation of the infrared part of the spectra in the high-altitude dataset.
 The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.

### 2024-03-12 docs/_tex/index.tex
Laura's comments

@@
 making it difficult to discriminate seagrass from other macrophytes in
-highly heterogenous meadows. To address these challenges and reduce the
-issue of mlixed pixel, drone images at a very high spatial resolution
-offer a promising solution. This study focuses on using drone
-acquisitions with a ten spectral band sensor mirroring those of
-Sentinel-2, for mapping intertidal macrophytes and effectively
+highly heterogenous meadows. Drone images at a very high spatial
+resolution offer a promising solution to address challenges related to
+spatial heterogeneity and intrapixel mixture. This study focuses on
+using drone acquisitions with a ten spectral band sensor mirroring those
+of Sentinel-2, for mapping intertidal macrophytes and effectively
 discriminating between seagrass and green macroalgae. Nine drone flights
 were conducted at two different altitudes (12m and 120m) across
-heterogeneous European habitats in France and Portugal. Low altitude
-flights were used to train a Deep Learning classifier based on Neural
-Networks to discrimintate among five taxonomic classes of intertidal
-vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae),
-Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and
-Bacillariophyceae (Diatoms). Classification of drone imagery resulted in
-an overall accuracy of 94\% across all the sites and images, covering a
-total area of 467 000 m². The model exhibited an accuracy of 96.4\% in
-identifying seagrass. This work showed that although they share the same
-pigmentary composition, seagrass and green algae can be discriminated
-using ten bands multispectral sensor. The algorithm should now be
-adapted for Sentinel-2 to see if this discrimination is still
-operational at a coarser spatial resolution.
+heterogeneous intertidal European habitats in France and Portugal. Low
+altitude flights were used to train a Deep Learning classifier based on
+Neural Networks to discrimintate among five taxonomic classes of
+intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green
+macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae)
+and benthic Bacillariophyceae (Diatoms). Classification of drone imagery
+resulted in an overall accuracy of 94\% across all the sites and images,
+covering a total area of 467 000 m². The model exhibited an accuracy of
+96.4\% in identifying seagrass. This work showed that although they
+share the same pigmentary composition, seagrass and green algae can be
+discriminated using a multispectral sensor with ten spectral bands at
+444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm. The algorithm
+should now be adapted for Sentinel-2 to see if this discrimination is
+still operational at a coarser spatial resolution.
 \end{abstract}
@@
 ]{orth2006}; \citealp[ ]{lin2018}; \citealp[ ]{duffy2019}; \citealp[
-]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. While improvements
-in water quality have been recently reported in Europe, allowing an
-overall recovery of seagrass ecosystems at local scale, many coastal
-waters worldwide are still subjected to strong eutrophication processes
-\citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal
-eutrophication has been ass ociated to excessive accumulation of green
-macroalgae, so-called green tides (\citep{devlin2023nutrients}). Green
-tides produce shade and suffocation over seagrass individuals, thus
-threatening the health of seagrass ecosystems \citep{wang2022}.
+]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. Both habitat
+fragmentation and reduction, in turn, can severely copromise the
+effectiveness of ecosystem services provided by seagrass meadows. While
+improvements in water quality have been recently reported in Europe,
+allowing an overall recovery of seagrass ecosystems at local scale, many
+coastal waters worldwide are still subjected to strong eutrophication
+processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
+Coastal eutrophication has been ass ociated to excessive accumulation of
+green macroalgae, so-called green tides (\citep{devlin2023nutrients}).
+Green tides produce shade and suffocation over seagrass individuals,
+thus threatening the health of seagrass ecosystems \citep{wang2022}.
 
@@
 they provide have led to the enhancement of both global and regional
-programs monitoring Essential Oceanic Variable (EOVs) such as seagrass
+programs to monitor Essential Oceanic Variable (EOVs) such as seagrass
 composition \citep{Miloslavich2018}, as well as Essential Biodiversity
@@
 While satellite remote sensing (RS) provides temporally consistent
-observations over large spatial scales, it is limited by several
-constraints. Satellite missions with a high temporal resolution
-(e.g.~daily MODIS observation) are limited by a coarse spatial
-resolution (\textgreater100m). Missions with a high spatial resolution
-such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low
-spectral resolution. The limited number of spectral bands is indeed a
-challenge to accurately discriminate seagrass from others co-existing
-macrophytes. In particular Chlorophyceae (green algae) and marine
-Magnoliopsida (seagrass) share the same pigment composition
-\citetext{\citealp[ ]{ralph2002}; \citealp{Douay2022}}. Therefore, to
-someone not specialized in the field, their spectral signatures may
-appear to be alike \citetext{\citealp[
-]{Davies2023}; \citealp{bannari2022}}. Recently, using advanced
-machine-learning algorithms trained with a large hyperspectral library
-of more then 300 field reflectance spectra, \citep{Davies2023}
-demonstrated that it was possible to discriminate Magnoliopsida from
-Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral
-resolution. However the application of this approach to satellite RS
-remains to be validated. Moreover patches of green algae can develop at
-small spatial scales that are not observable using non-commercial
-satellite imagery \citep{tuya2013}, especially during the initial stage
-of th
+observations over large spatial scales, its utilization over intertidal
+areas is limited by several constraints. Satellite missions with a high
+temporal resolution (e.g.~daily MODIS observation) are limited by a
+coarse spatial resolution (\textgreater100m) over these restricted
+extension areas. Missions with a high spatial resolution such as
+Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral
+resolution. The limited number of spectral bands is indeed a challenge
+to accurately discriminate seagrass from others co-existing macrophytes.
+In particular Chlorophyceae (green algae) and marine Magnoliopsida
+(seagrass) share the same pigment composition \citetext{\citealp[
+]{ralph2002}; \citealp{Douay2022}}. Therefore, to someone not
+specialized in the field, their spectral signatures may appear to be
+alike \citetext{\citealp[ ]{Davies2023}; \citealp{bannari2022}}.
+Recently, using advanced machine-learning algorithms trained with a
+large hyperspectral library of more than 300 field reflectance spectra,
+\citep{Davies2023} demonstrated that it was possible to discriminate
+Magnoliopsida from Chlorophyceae using radiometric data acquired at
+Sentinel-2 's spectral resolution. However the application of this
+approach to satellite RS remains to be validated. Moreover patches of
+green algae can develop at small spatial scales that are not observable
+using non-commercial satellite imagery \citep{tuya2013}, especially
+during the initial stage of a green tide.
 
@@
 France (46.9849°N, 2.1488°W). This bay is 340 km² semi-enclosed
-macrotidal bay, protected from waves by Noirmoutier Island. Bougneuf bay
-hosts a large intertidal seagrass meadow of about 6 km². Within this
+macrotidal bay, protected from waves by Noirmoutier Island. Bourgneuf
+bay hosts a large intertidal seagrass meadow of about 6 km². Within this
 meadow, the sites observed by drones (L'Epine and Barbatre,
-Figure~\ref{fig-map} B) contained a monospecific bed of
-\emph{Nanozostera noltei} (dwarf eelgrass) with very little mixing with
-other macrophytes. Three sites were surveyed in the Ria de Aveiro Lagoon
-in Portugal (40.6887°N, 8.6810°W). The extent of this lagoon is about 80
-km² with many narrow channels, large salt marshes and many mudflats that
-uncovers at low tide. It is connected to the open sea through a single
-channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) was a mudflat located in a tributary
-river of the lagoon whereas the two other sites were situated in the
-middle of the lagoon and only accessible by boat (Figure~\ref{fig-map}
-C). These Portuguese sites are characterized by a more diverse
-intertidal vegetation, where patches of seagrass intermingle with red,
-brown and green macroalgae.
+Figure~\ref{fig-map} B) contained monospecific beds of \emph{Nanozostera
+noltei} (dwarf eelgrass) with very little mixing with other macrophytes.
+Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal
+(40.6887°N, 8.6810°W). The extent of this lagoon is about 80 km² with
+many narrow channels, large salt marshes and many mudflats that uncovers
+at low tide. It is connected to the open sea through a single channel,
+with a tidal lag between the North and the South of the lagoon. The
+southernmost site (Gafanha) was a mudflat located in a tributary river
+of the lagoon whereas the two other sites (Mataducos and Marinha
+Lanzarote) were situated in the middle of the lagoon and only accessible
+by boat (Figure~\ref{fig-map} C). These Portuguese sites are
+characterized by a more diverse intertidal vegetation, where patches of
+seagrass intermingle with red, brown and green macroalgae.
 
@@
 Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
-C: Ria de Aveiro Coastal Lagoon (Three sites). Green represent
+C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents
 intertidal areas.}
@@
 Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
-million pixel reflectance photographs with ten spectral bands, from 444
-nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting
-conditions across flight paths, the drone's trajectory was aligned to
-maintain a solar azimuth angle of 90 degrees. An overlap of 70\% and
-80\% (side and front respectively) between each image was set for each
-flight. A downwelling light sensor (DLS2) was used to acquire irradiance
-data concomitantly with the camera measurements. Raw data were
-calibrated in reflectance using a calibration panel reflective at
-\textasciitilde50\% provided by the manufacturer. Across all sites,
-flights were made at two different altitudes : 12 m or/and 120 m.
-(Table~\ref{tbl-flights}).
+million pixel reflectance photographs with ten spectral bands ranging
+from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668,
+705, 717, 740 and 840 nm. To ensure consistent lighting conditions
+across flight paths, the drone's trajectory was aligned to maintain a
+solar azimuth angle of 90 degrees. An overlap of 70\% and 80\% (side and
+front respectively) between each image was set for each flight. A
+downwelling light sensor (DLS2) was used to acquire irradiance data
+concomitantly with the camera measurements. Raw data were calibrated in
+reflectance using a calibration panel reflective at \textasciitilde50\%
+provided by the manufacturer. Across all sites, flights were made at two
+different altitudes : 12 m or/and 120 m. (Table~\ref{tbl-flights}).
 
@@
 benthic diatoms forming biofilms at the sediment surface during low
-tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass),
+tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass),
 Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae)
@@
 with 1 nm of spectral resolution. Hyperspectral signatures from quadrats
-serve dual purposes: they validate the radiometric calibration of drone
-data and contribute to error reduction in photo interpretation. The
-workflow developed in this study is presented in
+serve for dual purposes: they validate the radiometric calibration of
+drone data and contribute to error reduction in photo interpretation.
+The workflow developed in this study is presented in
 Figure~\ref{fig-workflow}.
@@
 made to obtain a digital surface model (DSM), used to reconstruct the
-multispectral ortho-image. Low altitude drone flights produce
+multispectral ortho-image. Low altitude drone flights produced
 ortho-images with a very high spatial resolution (8 mm per pixel),
 making it efficient to visually distinguish between the various types of
-vegetation. High altitude fights on the other hand allow to cover large
-areas and produced images with a pixel size of 80 mm
+vegetation. High altitude fights on the other hand allowed to cover
+large areas and produced images with a pixel size of 80 mm
 (Table~\ref{tbl-flights}).
@@
 used for training because their 8 mm spatial resolution allowied to
-avoid spectral sub-pixel mixing and to accurately differentiate
-vegetation classes. More than 418,000 pixels at 8 mm resolution from the
-3 training flights were used to train the model
-(Table~\ref{tbl-validationPX}). Twenty one variables were used by the
-model as predictors: the ten raw spectral bands of the Micasense RedEdge
-Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same
-ten spectral bands standardized using a min/max transformation
-(Equation~\ref{eq-std} ; \citep{Cao2017}) and the Normalized difference
-vegetation index (NDVI, Equation~\ref{eq-ndvi}). Standardisation of
-spectral bands is used to eliminate the scaling differences between
-spectra and to limit the effect of biomass on the shape of the spectra
-\citetext{\citealp[ ]{Douay2022}; \citealp{Davies2023}}.
+avoid spectral sub-pixel mixing and to accurately identify vegetation
+classes. More than 418,000 pixels at 8 mm resolution from the 3 training
+flights were used to train the model (Table~\ref{tbl-validationPX}).
+Twenty one variables were used by the model as predictors: the ten raw
+spectral bands of the Micasense RedEdge Dual MX multispectral camera
+(ranging from 444 nm to 840 nm), the same ten spectral bands
+standardized using a min/max transformation (Equation~\ref{eq-std} ;
+\citep{Cao2017}) and the Normalized difference vegetation index (NDVI,
+Equation~\ref{eq-ndvi}). Standardisation of spectral bands is commonly
+used to eliminate the scaling differences between spectra and to limit
+the effect of biomass on the spectra shape \citetext{\citealp[
+]{Douay2022}; \citealp{Davies2023}}.
 
@@
 In situ information on georeferenced class type and percent cover
-collected during each flight was used to assess the model accuracy,
-including. These images were used to construct a validation dataset
-indicating the presence or absence of each class. Additionally to the
-quadrat-based validation dataset, polygons of each class were photo
-interpreted in order to increase the number of pixels of the validation
-dataset. A confusion matrix, along with precision metrics such as global
-accuracy, sensitivity, specificity, and Kappa coefficient, was generated
-for each sites. All validation matrices were then merged to create a
-unique matrix . Altogether, a total of 536,000 pixels was used to
-validate the model, thus providing a geographically robust validation
-dataset.
+collected during each flight was used to assess the model accuracy.
+These images were used to construct a validation dataset indicating the
+presence or absence of each class. Additionally to the quadrat-based
+validation dataset, polygons of each class were photo interpreted in
+order to increase the number of pixels of the validation dataset. A
+confusion matrix, along with precision metrics such as global accuracy,
+sensitivity, specificity, and Kappa coefficient, was generated for each
+sites. All validation matrices were then aggregated to create a unique
+matrix . Altogether, a total of 536,000 pixels was used to validate the
+model, thus providing a geographically robust validation dataset.
 
@@
 
-A total of nine prediction maps corresponding to the nine drone flights
-were obtained. Each prediction map is associated with a probability map,
-indicating the probability of the selected class for every pixel. The
+The nine drone flights were utilized to produce a total of nine
+prediction maps, each of them associated with a probability map that
+indicates the probability of the selected class for every pixel. The
 low-altitude flight conducted in Gafanha, Portugal, represents the site
@@
 sediment surface. Although the seagrass bed was solely composed of
-\emph{Nanozostera noltei}, various colors of this could be observed from
-dark green (corresponding to healthy leaves) to whitish/brown (when
-leaves were discolored having lost their pigmentation). Regardless of
-color, the meadow was accurately predicted as Magnoliopsida by the
-model.
+\emph{Nanozostera noltei}, various colors of this specie could be
+observed from dark green (corresponding to healthy leaves) to
+whitish/brown (when leaves were discolored having lost their
+pigmentation). Regardless of color, Magnoliopsida pixels were accurately
+predicted by the model.
 
@@
 
-The high-altitude flight over Gafanha covered nearly 1 km² in total
-(Figure~\ref{fig-GafHigh}). A channel delineating a small island was
-masked in the prediction map. Most of the intertidal area was classified
-as Magnoliopsida by the model, including seagrass patches with
-discolored leaves. Only a few pixels were classified as Chlorophyceae at
-this scale. Furthermore, the area that was classified as
-Bacillariophyceae in the low-altitude flight remained mostly classified
-as such in the high-altitude flight, though some pixels were classified
-as Magnoliopsida. Patches of Rhodophyceae were correctly classified. In
-the nothern part of the scene, near the land limit, patches of the
-schorre angiosperm \emph{Spartina sp.} were misclassified, either as
-Magnoliopsida or as Phaeophyceae.
+The high-altitude flight over Gafanha covered a total area of
+approwimately 1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
+small island was masked in the prediction map. Most of the intertidal
+area was classified as Magnoliopsida by the model, including seagrass
+patches with discolored leaves. Only a few pixels were classified as
+Chlorophyceae at this spatial scale. Furthermore, the area that was
+classified as Bacillariophyceae in the low-altitude flight remained
+mostly classified as such in the high-altitude flight, though some
+pixels were classified as Magnoliopsida. Patches of Rhodophyceae were
+correctly classified. In the northern part of the site and near the land
+eadges, patches of the schorre angiosperm \emph{Spartina sp.} were
+misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 
-The high altitude flight acquired over the inner lagoon of the Ria de
-Aveiro was the largest of all flights, covering almost 1.5 km²
-(Figure~\ref{fig-Boat}). The site was dominated by seagrass and the red
+Amoung the high altitude flights, the one acquired over the inner lagoon
+of the Ria de Aveiro covered the largest area with approximately 1.5 km²
+(Figure~\ref{fig-Boat}). This site was dominated by seagrass and the red
 macroalgae \emph{Gracilaria vermicullophyla}. The classification
 provided consistent results, with a patchy seagrass meadow mixed with
-red macroalgae on the eastern part of the scene. As shown in the zoom
+red macroalgae on the eastern part of the site. As shown in the zoom
 (Figure~\ref{fig-Boat}), the edges of the meadow were colonised by green
@@
 The total extent of this flight was about 1.5 km² with a resolution of
-80 mm per pixel. Background colors indicates intertidal area (Light
+80 mm per pixel. Background colors indicate intertidal area (Light
 Green), land area (Light Grey) and water (Light Blue). Each cover an
-area equivalent to a 10-meter Sentinel-2 pixel size.}
+area equivalent to a 10 m Sentinel-2 pixel size.}
 
@@
 The flight over L'Epine in Noirmoutier Island, France
-(Figure~\ref{fig-Dike}) was conducted near a dike crossing the northern
-part of the scene from west to east. Alongside this dike, brown algae
-for the order Fucales (\emph{Fucus spp.}, \emph{Ascophyllum nodosum})
-were attached to sparse rocks and stranded green algae (\emph{ulva
-spp.}) could be observed Despite the high mixture between Chlorophyceae
-and Magnoliopsida these two classes were correctly discriminated by the
-classifier.
+(Figure~\ref{fig-Dike}) was conducted near a dike, which crossed the
+northern part of the site from west to east. Alongside this dike, brown
+algae for the order Fucales (\emph{Fucus spp.}, \emph{Ascophyllum
+nodosum}) were attached to sparse rocks and stranded green algae
+(\emph{Ulva spp.}) could be observed Despite the high mixture between
+Chlorophyceae and Magnoliopsida these two classes were correctly
+discriminated by the classifier.
 
@@
 
-In this study, a key innovation lies in the utilization of two different
-altitudes (12m and 120m) for constructing the neural network model. The
-lower altitude flights (8mm spatial resolution) enabled precise
-selection of pure pixels representing the classes used in the neural
-network model. This methodology implies a consistency between the
-reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
-relationship between reflectance from a low-altitude flight and a
-high-altitude flight conducted over the same area. Overall there was a
-good agreement between the two altitudes. There was however a slight
-underestimation for raw reflectance values in the high-altitude flight,
-particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
-both flights were conducted over vegetation areas, the highest
-reflectance values correspond to the infrared part of the spectrum. This
-different is not present anymore when reflectance values of both flights
-have been standardized (Equation~\ref{eq-std} ;
-Figure~\ref{fig-CompareRef} B).
+In this study, a key innovation lies in the utilization of drone flights
+at two different altitudes (12m and 120m) for constructing the neural
+network model. The lower altitude flights (8mm spatial resolution)
+enabled precise selection of pure pixels to train the neural network
+model. This methodology implies a consistency between the reflectance of
+both altitudes. Figure~\ref{fig-CompareRef} depicts the relationship
+between reflectance from a low and a high-altitude flights conducted
+over the same area. Overall there was a good agreement between the two
+altitudes. There was however a slight underestimation for raw
+reflectance values in the high-altitude flight, particularly for higher
+reflectance values (Figure~\ref{fig-CompareRef} A). Since both flights
+were conducted over vegetation areas, the highest reflectance values
+correspond to the infrared part of the spectrum. This different is not
+present anymore when reflectance values of both flights have been
+standardized (Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} B).
 
@@
 (Figure~\ref{fig-VIP}). The spectral bands at 444, 717 and 842 nm of the
-Micasense camera did not came out as important for any of the vegetation
-classes. The band at 531 nm was the only important predictor for the
-classifier to accurately predict Chlorophyceae. In fact, at this
-wavelength, the Chlorophyceae spectra have the highest reflectance among
-of all vegetation classes. The bands at 531 and 740 nm were the most
-important predictors for Phaeophyceae, corresponding to the lowest
-reflectance among all classes. Bands at 475 and 560 nm are the most
-important predictors for Bacillariophyceae and Rhodophyceae,
-respectively. Four predictors, ranging from the green (560 nm) to the
-RedEdge (705 nm) bands were important to accurately predict
-Magnoliopsida.
+Micasense camera did not provide as important information to
+discriminate any of the vegetation classes. The band at 531 nm was the
+only important predictor for the classifier to accurately predict
+Chlorophyceae. In fact, at this wavelength, the Chlorophyceae spectra
+showed the highest reflectance among of all vegetation classes. The
+bands at 531 and 740 nm were the most important predictors for
+Phaeophyceae, corresponding to the lowest reflectance among all classes.
+Bands at 475 and 560 nm were the most important predictors for
+Bacillariophyceae and Rhodophyceae, respectively. Four predictors,
+ranging from the green (560 nm) to the RedEdge (705 nm) bands were
+important to accurately predict Magnoliopsida.
 
@@
 
-Using the very high resolution low altitude flight, we determined the
-minimal percent cover required to correctly a given class using the high
-altitude flight (Figure~\ref{fig-upscaling}). When the percent cover of
-the class was 100 \%, coarser high-flight pixels are well classified for
-all the classes except for Bare Sediment, which was only well classified
-80\% of the time. This phenomenon is likely attributed to the time gap
-between the two flights, allowing for microphytobenthos migration,
-consequently altering the model's classification from bare sediment to
-Bacillariophyceae. A percent cover of at least 80\% was needed to have
-all the low resolution pixels well classified, with the exception of
-Magnoliopsida that needed a higher percent cover (\textgreater90 \%) to
-be well classified. Concerning the probability of each class, the
-highest percent cover was needed to confidently predict
-Bacillariophyceae. To predict Chlorophyceae with a confidence of 0.85, a
-percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
-Rhodophyceae and 97 \% for Bacillariophyceae.
+Using the very high resolution low altitude flight (8 mm pixels), we
+determined the minimal percent cover required to correctly classify a
+given class within the corresponding high altitude flight
+(Figure~\ref{fig-upscaling}). When the percent cover of a given class
+was 100 \%, coarser high-flight pixels are well classified for all the
+classes except for Bare Sediment, which was only well classified 80\% of
+the time. This phenomenon is likely attributed to the time gap between
+the two flights, allowing for microphytobenthos migration to surface
+during low tide, consequently altering the model's classification from
+bare sediment to Bacillariophyceae. A percent cover of at least 80\% was
+sufficient to have all the pixels of high altitude flights correctly
+classified, with the exception of Magnoliopsida that required a higher
+percent cover (\textgreater90 \%) to be well classified. Concerning the
+probability of each class, the highest percent cover was needed to
+confidently predict Bacillariophyceae. To predict Chlorophyceae with a
+confidence of 0.85, a percent cover of 93 \% was needed, 90 \% for
+Magnoliopsida, 92 \% for Rhodophyceae and 97 \% for Bacillariophyceae.
 
@@
 \caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
-(Green) or absent (Red) in each taxonomic class dected by the Neural
+(Green) or absent (Red) in each taxonomic class present in the Neural
 Network Classifier, along with their absorption wavelength measured with
 spectroradiometer. Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco:
-fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino:
-diadinoxanthin, Neo: neoxanthin., PE: phycoerythrin, PC: phycocyanin.}
+fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
+neoxanthin, PE: phycoerythrin, PC: phycocyanin.}
 
@@
 vegetation, as demonstrated in this study, plays a critical role in
-ecological monitoring and management. By distinguishing between
+ecological monitoring and coastal management. By distinguishing between
 seagrasses and macroalgae, our approach facilitates targeted
@@
 ]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
-the shared pigment composition between these taxa
+the similarities on their spectal signatures in the visible region of
+the eletromagnetic spectra due to shared pigment
 , Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
-these macrophytes. These green macrophytes have in common photosynthtic
-pigmetns, chlorophyll a and b, and accessory carotenoid pigments
-zeaxantin, lutein and neoxanthin. As a result the spectral signatures
-are often indistinguishable in the visible wavelength region. This
-spectral overlap is further complicated by the intermingling of
-seagrasses and green macroalgae in the same spatial locations, posing a
-significant challenge for remote sensing aimed at accurately mapping and
-monitoring coastal ecosystems. Our study addresses these complexities by
-using high-resolution drone imagery with 10 spectral bands.
-\citep{Davies2023} have shown that having at least eight spectral bands
-ranging between 500 nm to 850 nm including a green band at 530 nm and
-another one in the RedEdge region at 730 nm was crucial to accurately
-discriminate green macrophytes.
+these macrophytes. Besides chlorophyll-a that is common to all
+vegetation types, these two green macrophytes have in common other
+photosynthetic pigments such as chlorophyll-b, and accessory carotenoid
+pigments such as zeaxantin, lutein and neoxanthin
+(Figure~\ref{fig-Pigm}). This spectral overlap is further complicated by
+the intermingling of seagrasses and green macroalgae in the same spatial
+locations, posing a significant challenge for remote sensing aimed at
+accurately mapping and monitoring coastal ecosystems. Our study
+addresses these complexities by using high-resolution drone imagery with
+10 spectral bands. \citep{Davies2023} have shown that having at least
+eight spectral bands ranging between 500 nm to 850 nm including a green
+band at 530 nm and another one in the RedEdge region at 730 nm was
+crucial to accurately discriminate amoung green macrophytes.
 
@@
 spectral shape can still be observed (Figure~\ref{fig-vegetation}).
-Several factors can explain these differences such has different pigment
-concentration and/or proportion \citep{bargain2013seasonal}, different
-cellular organisation and the disposition of the plant on the sediment
-surface \citetext{\citealp[ ]{beach1997vivo}; \citealp[
+Several factors can explain these differences such has different
+concentration and/or pigment ratios \citep{bargain2013seasonal},
+different cellular organisation and the disposition of the plant over
+the sediment surface \citetext{\citealp[ ]{beach1997vivo}; \citealp[
 ]{kirk1994light}; \citealp{hedley2018influence}}.
@@
 The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
-identified that the 531 nm band as the most important spectral band for
+identified that the band at 531 nm was the most important one for
 accurately identifying Chlorophyceae. In fact, at this wavelength,
@@
 of the spectra \citep{Slaton2001} whereas the presence of Fucoxanthin
-and Zeaxanthin result in a low reflectance in the visible part of the
-electromagnetic spectra (Figure~\ref{fig-Pigm} ; Figure~\ref{fig-VIP}).
-These two key features have been identified by the Neural Network as the
-two principal predictors to accurately identify brown algae
-(Figure~\ref{fig-VIP}). Similarly, the presence of phycoerythrin and
-phycocyanin in Rhodophyceae contributes to the lowest reflectance among
-all classes in the spectral range of 560 to 615 nm
-(Figure~\ref{fig-VIP}). The band at 560 nm has been identified as
-important for accurately identifying this class probably in relation to
-the absorption by phycoerythrin (\textbf{REF}). Regarding
+and Zeaxanthin result in a low reflectance in the visible region
+(Figure~\ref{fig-Pigm} ; Figure~\ref{fig-VIP}). These two key features
+have been identified by the Neural Network as the two principal
+predictors to accurately identify brown algae (Figure~\ref{fig-VIP}).
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
+contributes to the lowest reflectance among all classes in the spectral
+range of 560 to 615 nm (Figure~\ref{fig-VIP}). Indeed the band at 560 nm
+has been identified as important for identifying this class likely due
+to phycoerythrin absorption at this wavelength (\textbf{REF}). Regarding
 Bacillariophyceae, the VIP analysis (Figure~\ref{fig-VIP}) indicated
-that 475 nm was the most important predictor for this class. classes.
-This is not a usual diagnostic wavelength for Bacillariophyceae which is
-mainly identified by the presence of fucoxanthin and chlorophyll c
-(Table 11), but it correspond to the absorption of diadinoxanthin an
-accessory pigment characteristic of this class
-\citep{meleder2003spectrometric}. Furethemore, it is vegetation with the
-lowest concentration of chlorphyll-a, pigment absorbing light both in
-the blue and the red. The transparency of Bacillariophyceae makes the
+that 475 nm was the most important predictor for this class. This is not
+a usual diagnostic wavelength for Bacillariophyceae which is mainly
+identified by the presence of fucoxanthin and chlorophyll c
+(Figure~\ref{fig-Pigm}), but it correspond to the absorption of
+diadinoxanthin an accessory pigment characteristic of this class
+\citep{meleder2003spectrometric}. Furthermore, it is the vegetation with
+the lowest concentration of chlorphyll-a, pigment absorbing light both
+in the blue and the red. The transparency of Bacillariophyceae makes the
 reflectance of the sediment part of the overall reflectance of
@@
 underestimation of the infrared part of the spectra in the high-altitude
-dataset. The disparity in infrared reflectance may stem from temporal
+dataset. Such disparity in infrared reflectance may stem from temporal
 differences between the flights, possibly resulting in a slightly drier
@@
 
-The Figure~\ref{fig-upscaling} demonstrates that a seagrass cover
-percentage of 90 \% is necessary for confident prediction of seagrass
-presence. This highlights a limitation of the methodology used to
-construct the training dataset for the model. The dataset was composed
-exclusively of pure pixels, which has resulted in the model's reduced
-confidence when faced with lower percentages of seagrass cover.
-Intertidal seagrasses exhibit marked phenology, with varying pigment
-composition throughout the year\citetext{\citealp[
+The Figure~\ref{fig-upscaling} demonstrates that at least 90 \% of
+seagrass cover is necessary for confident prediction of its presence.
+This highlights a limitation of the methodology used to construct the
+training dataset for the model. The dataset used to train our algorithm
+was composed exclusively of pure pixels, which has resulted in the
+model's reduced confidence when faced with lower percentages of seagrass
+cover. Also, intertidal seagrasses exhibit marked phenology, with
+varying pigment composition throughout the year\citetext{\citealp[
 ]{bargain2013seasonal}; \citealp{legare2022remote}}. Since the training
-dataset has been made using well developed seagrass meadows, outside of
-the biomass peak of seagrasses, this model may be less accurate. Further
-investigation is warranted to explore this aspect.
+dataset has been made using well developed seagrass meadows, this model
+may be less accurate outside of the seasonal seagrass peak of biomass.
+Further investigation is required to evaluate the accuracy of the method
+along different periods of the year.
 
@@
 Climate change, global warming, alien and invasive species development,
-coastal erosion, sealevel rise, will continue to impact coastal
-ecosystems in the future
+coastal erosion, and sealevel rise are expected to continue impacting
+coastal ecosystems in the future
 \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
@@
 particularly the improved discrimination of seagrass from other
-intertidal vegetation taxonomic classes, underscore the potential of
-drone-based remote sensing to support diverse applications, from
-biodiversity conservation to climate change adaptation strategies.
-Employing traditional sampling methods to monitor these ecosystems is
-time and resource-intensive, and the findings are often difficult to
-up-scale. Earth observation methods can bridge this gap and meet the
-needs for monitoring coastal ecosystems.
-\citep{papathanasopoulou2019satellite}. The retrieval of Essential
-Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs)
-through satellite observations is increasingly common, enabling
-comprehensive monitoring of entire ecosystems over extended time periods
-\citetext{\citealp[
+intertidal vegetation classes, underscore the potential of drone-based
+remote sensing to support diverse applications, from biodiversity
+conservation to climate change adaptation strategies. Employing
+traditional sampling methods to monitor these ecosystems is time and
+resource-intensive, and the findings are often difficult to up-scale.
+Earth observation methods can bridge this gap and meet the needs for
+monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
+The retrieval of Essential Biodiversity Variables (EBVs) and Essential
+Ocean Variables (EOVs) through satellite observations is increasingly
+common, enabling comprehensive monitoring of entire ecosystems over
+extended time periods \citetext{\citealp[
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
@@
 understanding and monitoring of aquatic ecosystems, including coastal
-habitats like seagrass \citetext{\citealp[
+habitats like seagrass beds \citetext{\citealp[
 ]{foden2007angiosperms}; \citealp[
@@
 Drones, with their capability for high-resolution, multispectral imagery
-and, flight on demand, provide a novel and powerful means to rapidly and
+and, flight on-demand, provide a novel and powerful means to rapidly and
 accurately acquire ground truth data (i.e.~output of the model used in
@@
 validating satellite remote sensing applications, thereby enhancing our
-capacity to monitor vast coastal areas systematically under the WFD
-framework. A perspective of this work could be to aid algorithm applied
-to satellite imagery (e.g.~Sentinel-2) to see of the discrimination
-between seagrass and green macroalgae is still operational at a coarser
-spatial resolution. The integration of drone technology facilitates a
-scalable approach to environmental surveillance, offering significant
+capacity to monitor vast coastal areas systematically under the WFD. A
+perspective of this work could be applying this algorithm to satellite
+imagery (e.g.~Sentinel-2) to evaluate if the discrimination between
+seagrass and green macroalgae is still operational at a coarser spatial
+resolution. The integration of drone technology facilitates a scalable
+approach to environmental surveillance, offering significant
 advancements in the spatial and temporal resolution of data collection.
@@
 method for the discrimination of seagrasses from green macroalgae with a
-multispectral resolution sensor. Standardized reflectance were
+multispectral resolution sensor. Standardized reflectance was
 incorporated in the Neural Network model allowing for a better
@@
 to discriminate Magnoliopsida from Chlorophyceae. The latter was
-essentially identify with the 451 nm spectral band while more spectral
+essentially identified with the 451 nm spectral band while more spectral
 bands were needed to identify the former, notably 650, 560, 668, and 705
@@
 data have the potential to perform this discrimination between green
-macrophytes. The algorithm could be adapted to Sentinel-2 with all the
-drone data from this study that can be used as training and validation
-data. The findings underscore the importance of adopting advanced remote
-sensing tools in ecological studies and environmental monitoring,
-providing a foundation for future research and policy implementation
-aimed at ecosystem conservation and restoration.
+macrophytes. A sentinel-2 algorithm could be developed, using the output
+of this current workflow as training and validation data. The findings
+underscore the importance of adopting advanced remote sensing tools in
+ecological studies and environmental monitoring, providing a foundation
+for future research and policy implementation aimed at ecosystem
+conservation and restoration.
 

### 2024-03-12 index.qmd
Laura's comments

@@
 Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
-To address these challenges and reduce the issue of mlixed pixel, drone images at a very high spatial resolution offer a promising solution.
+Drone images at a very high spatial resolution offer a promising solution to address challenges related to spatial heterogeneity and intrapixel mixture.
 This study focuses on using drone acquisitions with a ten spectral band sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
-Nine drone flights were conducted at two different altitudes (12m and 120m) across heterogeneous European habitats in France and Portugal.
-Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and Bacillariophyceae (Diatoms).
+Nine drone flights were conducted at two different altitudes (12m and 120m) across heterogeneous intertidal European habitats in France and Portugal.
+Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
 Classification of drone imagery resulted in an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
 The model exhibited an accuracy of 96.4% in identifying seagrass.
-This work showed that although they share the same pigmentary composition, seagrass and green algae can be discriminated using ten bands multispectral sensor.
+This work showed that although they share the same pigmentary composition, seagrass and green algae can be discriminated using a multispectral sensor with ten spectral bands at 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
 The algorithm should now be adapted for Sentinel-2 to see if this discrimination is still operational at a coarser spatial resolution.
@@
 Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
+Both habitat fragmentation and reduction, in turn, can severely copromise the effectiveness of ecosystem services provided by seagrass meadows.
 While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
@@
 
-The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs monitoring Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, population abundance, and phenology [@Pereira2013].
+The importance of seagrass meadows and the variety of ecosystem services they provide have led to the enhancement of both global and regional programs to monitor Essential Oceanic Variable (EOVs) such as seagrass composition [@Miloslavich2018], as well as Essential Biodiversity Variable (EBVs) such as seagrass taxonomic diversity, species distribution, population abundance, and phenology [@Pereira2013].
 Traditionally, indicators of seagrass status have been quantified using *in situ* measurements.
@@
 
-While satellite remote sensing (RS) provides temporally consistent observations over large spatial scales, it is limited by several constraints.
+While satellite remote sensing (RS) provides temporally consistent observations over large spatial scales, its utilization over intertidal areas is limited by several constraints.
 Satellite missions with a high temporal resolution (e.g.
-daily MODIS observation) are limited by a coarse spatial resolution (\>100m).
+daily MODIS observation) are limited by a coarse spatial resolution (\>100m) over these restricted extension areas.
 Missions with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
@@
 Therefore, to someone not specialized in the field, their spectral signatures may appear to be alike [@Davies2023 ; @bannari2022].
-Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more then 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more than 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
 However the application of this approach to satellite RS remains to be validated.
-Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of th
+Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of a green tide.
 
@@
 This bay is 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
-Bougneuf bay hosts a large intertidal seagrass meadow of about 6 km².
-Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained a monospecific bed of *Nanozostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
+Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km².
+Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
 Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
@@
 It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) was a mudflat located in a tributary river of the lagoon whereas the two other sites were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
+The southernmost site (Gafanha) was a mudflat located in a tributary river of the lagoon whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
 These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown and green macroalgae.
@@
 #| fig-cap: >
-#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represent intertidal areas. 
+#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents intertidal areas. 
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR).
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands ranging from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
 To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees.
@@
     "L'Epine",
-    "Inner Lagoon",
+    "Marinha Lanzarote",
     "Mataducos",
@@
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
@@
 For all quadrats, the hyperspectral reflectance signatures of each vegetation class was measured using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
-Hyperspectral signatures from quadrats serve dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
+Hyperspectral signatures from quadrats serve for dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
 The workflow developed in this study is presented in @fig-workflow.
@@
 A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
-Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
-High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
+Low altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
+High altitude fights on the other hand allowed to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
 
@@
 The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately differentiate vegetation classes.
+Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
 More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
 Twenty one variables were used by the model as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
-Standardisation of spectral bands is used to eliminate the scaling differences between spectra and to limit the effect of biomass on the shape of the spectra [@Douay2022 ; @Davies2023].
+Standardisation of spectral bands is commonly used to eliminate the scaling differences between spectra and to limit the effect of biomass on the spectra shape [@Douay2022 ; @Davies2023].
 
@@
 The model was applied to all flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy, including.
+In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
 These images were used to construct a validation dataset indicating the presence or absence of each class.
@@
 A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
-All validation matrices were then merged to create a unique matrix .
+All validation matrices were then aggregated to create a unique matrix .
 Altogether, a total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the model, thus providing a geographically robust validation dataset.
@@
 
-A total of nine prediction maps corresponding to the nine drone flights were obtained.
-Each prediction map is associated with a probability map, indicating the probability of the selected class for every pixel.
+The nine drone flights were utilized to produce a total of nine prediction maps, each of them associated with a probability map that indicates the probability of the selected class for every pixel.
 The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
@@
 There was also Bacillariophyceae forming biofilms on parts of sediment surface.
-Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
-Regardless of color, the meadow was accurately predicted as Magnoliopsida by the model.
+Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
+Regardless of color, Magnoliopsida pixels were accurately predicted by the model.
 
@@
 
-The high-altitude flight over Gafanha covered nearly 1 km² in total (@fig-GafHigh).
-A channel delineating a small island was masked in the prediction map.
+The high-altitude flight over Gafanha covered a total area of approwimately 1 km² (@fig-GafHigh).
+A channel contouring a small island was masked in the prediction map.
 Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
-Only a few pixels were classified as Chlorophyceae at this scale.
+Only a few pixels were classified as Chlorophyceae at this spatial scale.
 Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remained mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
 Patches of Rhodophyceae were correctly classified.
-In the nothern part of the scene, near the land limit, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 
-The high altitude flight acquired over the inner lagoon of the Ria de Aveiro was the largest of all flights, covering almost 1.5 km² (@fig-Boat).
-The site was dominated by seagrass and the red macroalgae *Gracilaria vermicullophyla*.
-The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the scene.
+Amoung the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
+This site was dominated by seagrass and the red macroalgae *Gracilaria vermicullophyla*.
+The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
 As shown in the zoom (@fig-Boat), the edges of the meadow were colonised by green macroalgae
@@
 The total extent of this flight was about 1.5 km² with a resolution of 80 mm per pixel.
-Background colors indicates intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-Each cover an area equivalent to a 10-meter Sentinel-2 pixel size.
+Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+Each cover an area equivalent to a 10 m Sentinel-2 pixel size.
 #| label: fig-Boat
@@
 
-The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike crossing the northern part of the scene from west to east.
-Alongside this dike, brown algae for the order Fucales (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*ulva spp.*) could be observed Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
+The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike, which crossed the northern part of the site from west to east.
+Alongside this dike, brown algae for the order Fucales (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
 
@@
 
-In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model.
-The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model.
-This methodology implies a consistency between the reflectance of both altitude.
-@fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area.
+In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
+The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels to train the neural network model.
+This methodology implies a consistency between the reflectance of both altitudes.
+@fig-CompareRef depicts the relationship between reflectance from a low and a high-altitude flights conducted over the same area.
 Overall there was a good agreement between the two altitudes.
-There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A).
+There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
 Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
@@
 The computation of the variable importance made it possible to identify which bands were the most useful for class prediction (@fig-VIP).
-The spectral bands at 444, 717 and 842 nm of the Micasense camera did not came out as important for any of the vegetation classes.
+The spectral bands at 444, 717 and 842 nm of the Micasense camera did not provide as important information to discriminate any of the vegetation classes.
 The band at 531 nm was the only important predictor for the classifier to accurately predict Chlorophyceae.
-In fact, at this wavelength, the Chlorophyceae spectra have the highest reflectance among of all vegetation classes.
+In fact, at this wavelength, the Chlorophyceae spectra showed the highest reflectance among of all vegetation classes.
 The bands at 531 and 740 nm were the most important predictors for Phaeophyceae, corresponding to the lowest reflectance among all classes.
-Bands at 475 and 560 nm are the most important predictors for Bacillariophyceae and Rhodophyceae, respectively.
+Bands at 475 and 560 nm were the most important predictors for Bacillariophyceae and Rhodophyceae, respectively.
 Four predictors, ranging from the green (560 nm) to the RedEdge (705 nm) bands were important to accurately predict Magnoliopsida.
@@
 
-Using the very high resolution low altitude flight, we determined the minimal percent cover required to correctly a given class using the high altitude flight (@fig-upscaling).
-When the percent cover of the class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
-This phenomenon is likely attributed to the time gap between the two flights, allowing for microphytobenthos migration, consequently altering the model's classification from bare sediment to Bacillariophyceae.
-A percent cover of at least 80% was needed to have all the low resolution pixels well classified, with the exception of Magnoliopsida that needed a higher percent cover (\>90 %) to be well classified.
+Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (@fig-upscaling).
+When the percent cover of a given class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
+This phenomenon is likely attributed to the time gap between the two flights, allowing for microphytobenthos migration to surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
+A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher percent cover (\>90 %) to be well classified.
 Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
@@
 #| warning: false
-#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class dected by the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
-Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diato: diatoxanthin, Diadino: diadinoxanthin, Neo: neoxanthin., PE: phycoerythrin, PC: phycocyanin.')"
+#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
+Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin.')"
 #| label: fig-Pigm
@@
 The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and management.
+The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management.
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the shared pigment composition between these taxa [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
-These green macrophytes have in common photosynthtic pigmetns, chlorophyll a and b, and accessory carotenoid pigments zeaxantin, lutein and neoxanthin.
-As a result the spectral signatures are often indistinguishable in the visible wavelength region.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
+Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).
 This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
 Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands.
-@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate green macrophytes.
+@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate amoung green macrophytes.
 
@@
 Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
-Several factors can explain these differences such has different pigment concentration and/or proportion [@bargain2013seasonal], different cellular organisation and the disposition of the plant on the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
+Several factors can explain these differences such has different concentration and/or pigment ratios [@bargain2013seasonal], different cellular organisation and the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 
-The VIP analysis of the Neural Network model (@fig-VIP) identified that the 531 nm band as the most important spectral band for accurately identifying Chlorophyceae.
+The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae.
 In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the difference in accessory pigments (i.e.
@@
 
-Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible part of the electromagnetic spectra (@fig-Pigm ; @fig-VIP).
+Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible region (@fig-Pigm ; @fig-VIP).
 These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
 Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range of 560 to 615 nm (@fig-VIP).
-The band at 560 nm has been identified as important for accurately identifying this class probably in relation to the absorption by phycoerythrin (**REF**).
+Indeed the band at 560 nm has been identified as important for identifying this class likely due to phycoerythrin absorption at this wavelength (**REF**).
 Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
-classes.
-This is not a usual diagnostic wavelength for Bacillariophyceae which is mainly identified by the presence of fucoxanthin and chlorophyll c (Table 11), but it correspond to the absorption of diadinoxanthin an accessory pigment characteristic of this class [@meleder2003spectrometric].
-Furethemore, it is vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
+This is not a usual diagnostic wavelength for Bacillariophyceae which is mainly identified by the presence of fucoxanthin and chlorophyll c (@fig-Pigm), but it correspond to the absorption of diadinoxanthin an accessory pigment characteristic of this class [@meleder2003spectrometric].
+Furthermore, it is the vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
 The transparency of Bacillariophyceae makes the reflectance of the sediment part of the overall reflectance of Bacillariophyceae, further explaining the high reflectance in the blue.
@@
 While comparing the reflectance of both altitudes (12 m and 120 m), it was observed @fig-CompareRef that there is an underestimation of the infrared part of the spectra in the high-altitude dataset.
-The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
+Such disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
 This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training.
@@
 
-The @fig-upscaling demonstrates that a seagrass cover percentage of `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % is necessary for confident prediction of seagrass presence.
+The @fig-upscaling demonstrates that at least `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % of seagrass cover is necessary for confident prediction of its presence.
 This highlights a limitation of the methodology used to construct the training dataset for the model.
-The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
-Intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
-Since the training dataset has been made using well developed seagrass meadows, outside of the biomass peak of seagrasses, this model may be less accurate.
-Further investigation is warranted to explore this aspect.
+The dataset used to train our algorithm was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
+Also, intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
+Since the training dataset has been made using well developed seagrass meadows, this model may be less accurate outside of the seasonal seagrass peak of biomass.
+Further investigation is required to evaluate the accuracy of the method along different periods of the year.
 
@@
 
-Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, will continue to impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
+Climate change, global warming, alien and invasive species development, coastal erosion, and sealevel rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
 Therefore the demand for meaningful and efficient monitoring methods for these habitats has never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation taxonomic classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
+Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
 Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale.
@@
 The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
-The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
+The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
 
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral imagery and, flight on demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
+Drones, with their capability for high-resolution, multispectral imagery and, flight on-demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
 output of the model used in the present study).
-These data are critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework.
-A perspective of this work could be to aid algorithm applied to satellite imagery (e.g.
-Sentinel-2) to see of the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
+These data are critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD.
+A perspective of this work could be applying this algorithm to satellite imagery (e.g.
+Sentinel-2) to evaluate if the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
@@
 The utilization of very high-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses from green macroalgae with a multispectral resolution sensor.
-Standardized reflectance were incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible.
+Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible.
 There was a striking difference for the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
-The latter was essentially identify with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
+The latter was essentially identified with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
 As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green macrophytes.
-The algorithm could be adapted to Sentinel-2 with all the drone data from this study that can be used as training and validation data.
+A sentinel-2 algorithm could be developed, using the output of this current workflow as training and validation data.
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.

### 2024-03-14 docs/_tex/index.tex
final touch

@@
 remote sensing to support diverse applications, from biodiversity
-conservation to climate change adaptation strategies. Employing
-traditional sampling methods to monitor these ecosystems is time and
-resource-intensive, and the findings are often difficult to up-scale.
-Earth observation methods can bridge this gap and meet the needs for
-monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
-The retrieval of Essential Biodiversity Variables (EBVs) and Essential
-Ocean Variables (EOVs) through satellite observations is increasingly
-common, enabling comprehensive monitoring of entire ecosystems over
-extended time periods \citetext{\citealp[
+conservation to climate change adaptation strategies.
+
+With the increase in nutrient concentrations in coastal waters,
+macroalgal blooms are becoming increasingly common in many regions
+around the world \citetext{\citealp[
+]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
+negative impacts on local economic activities, including human health,
+fishing and aquaculture, tourism, and recreational activities
+\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
+first green tide events (i.e.~bloom of green macroalgae of the genus
+\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
+have since been a concern for local policies and economic activities
+\citep{menesguen2018marees}. Some regions of the world have
+louime2017sargassumrecently witnessed an increase in brown macroalgae
+blooms, predominantly involving algae of the genus \emph{Sargassum}
+\citep{louime2017sargassum}. Satellite remote sensing has proven to be a
+valuable tool for mapping the spatial and temporal extent of macroalgal
+blooms worldwide. However, due to its limitations in spatial resolution,
+it can only effectively map well-developed blooms \citetext{\citealp[
+]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
+drone imagery, coupled with an accurate classification algorithm, could
+be utilized to map the early stages of macroalgal blooms in areas known
+to have regular blooms or in new sites. Indeed, this approach could
+provide early warning alerts to local policymakers.
+
+Employing traditional sampling methods to monitor these ecosystems is
+time and resource-intensive, and the findings are often difficult to
+up-scale. Earth observation methods can bridge this gap and meet the
+needs for monitoring coastal ecosystems.
+\citep{papathanasopoulou2019satellite}. The retrieval of Essential
+Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs)
+through satellite observations is increasingly common, enabling
+comprehensive monitoring of entire ecosystems over extended time periods
+\citetext{\citealp[
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The

### 2024-03-14 index.qmd
final touch

@@
 Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
+
+With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green].
+These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green].
+The first green tide events (i.e.
+bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees].
+Some regions of the world have louime2017sargassumrecently witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum].
+Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide.
+However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote].
+High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
+Indeed, this approach could provide early warning alerts to local policymakers.
+
 Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale.

### 2024-03-14 index.qmd
adding data1

@@
 
-ggsave("Figures/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)
+ggsave("Figures/High_res/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)
 
@@
 
-ggsave("Figures/Figure1/Map_Aveiro.png",aveiro_plot,width= 10, height=10)
+ggsave("Figures/High_res/Figure1/Map_Aveiro.png",aveiro_plot,width= 10, height=10)
 
@@
 
-ggsave("Figures/Figure1/Map_BB.png",width= 10, height=10)
+ggsave("Figures/High_res/Figure1/Map_BB.png",width= 10, height=10)
 
@@
 
-  ggsave("Figures/Figure1/Map_Morbihan.png",width= 10, height=10)
+  ggsave("Figures/High_res/Figure1/Map_Morbihan.png",width= 10, height=10)
 
@@
 
-Tot <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Drone_Sites.png"), interpolate = T)
-BB <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_BB.png"), interpolate = T)
-Mor <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Morbihan.png"), interpolate = T)
-Av <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Aveiro.png"), interpolate = T)
+Tot <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Drone_Sites.png"), interpolate = T)
+BB <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_BB.png"), interpolate = T)
+Mor <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Morbihan.png"), interpolate = T)
+Av <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Aveiro.png"), interpolate = T)
 
@@
 
-ggsave("./Figures/Fig1_Map_Drone_Sites.png",a, width= 10, height=10, dpi = 800)
-
+ggsave("./Figures/High_res/Figure1/Fig1_Map_Drone_Sites.png",a, width= 10, height=10, dpi = 800)
 ```
@@
 
-save_as_image(flx1, "Figures/table_flights.png", res = 300)
+save_as_image(flx1, "Figures/High_res/Table1/table_flights.png", res = 300)
 ```
@@
 
-knitr::include_graphics("Figures/table_flights.png")
+knitr::include_graphics("Figures/High_res/Table1/table_flights.png")
 ```
@@
 
-imglist<-
-  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         str_detect(path, "High") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          str_detect(path, "Arz") ~ "Arz",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          str_detect(path, "Pred") ~ "Pred",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".xml"),
-                !str_detect(path,".enp"))
-
-gaf_low_multi<- imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "ortho",
-         resampled == "FALSE",
-         folder == "Input") %>%
-  slice(1) %>% 
-  pull(path) %>%
+gaf_low_multi<- "./Data/BiCOME_Flights/Aveiro/Aveiro_MULTI_12m_ortho_1801.tif" %>% 
   rast()
+
 names(gaf_low_multi)<-c(paste0("B",c(1:10)))
 
- Gafanha_low_pred<-"./Data/image/prediction/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
+ Gafanha_low_pred<-"./Data/image/prediction/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
      rast()
@@
 
-ggsave("Figures/Spectral_shapes.png",spectra, bg = "transparent",  height = 2, width = 3, dpi = 2000)
-
-sp <- image_ggplot(magick::image_read("Figures/Spectral_shapes.png"), interpolate = T)
+ggsave("Figures/High_res/Figure2/Spectral_shapes.png",spectra, bg = "transparent",  height = 2, width = 3, dpi = 2000)
+
+sp <- image_ggplot(magick::image_read("Figures/High_res/Figure2/Spectral_shapes.png"), interpolate = T)
 
@@
 
-ggsave("Figures/Spectral_shapes_total.png",plot, height = 7, width = 10, dpi = 800)
+ggsave("Figures/High_res/Figure2/Spectral_shapes_total.png",plot, height = 7, width = 10, dpi = 800)
 ```

### 2024-03-15 docs/_tex/index.tex
final push

@@
 
-\includegraphics[width=6.63in,height=\textheight]{Figures/table_flights.png}
+\includegraphics[width=6.63in,height=\textheight]{Figures/High_res/Table1/table_flights.png}
 
@@
 classifier. The sites with the lowest and highest number of validation
-data were Kerdrean (5557 pixels) and Marinha Lanzarote (159713 pixels),
-respectively. Model global accuracy was 94.26\% with a Kappa coefficient
-of 0.92 (Figure~\ref{fig-Validation}). The lowest performing site was
-Gafanha High (global accuracy of 75.45\%) whereas Mataducos was the site
-with the most accurate prediction (global accuracy of 98.05\%). Overall,
-the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were
-correctly classified with a balanced accuracy of 1, 0.96, 0.96 and 0.91
-respectively. Bacillariophyceae was the least performing class (accuracy
-of 0.72 ) mainly due to the confusion with Magnoliopsida and Sediment.
+data were Gafanha Low (17316 pixels) and Marinha Lanzarote (159713
+pixels), respectively. Model global accuracy was 94.26\% with a Kappa
+coefficient of 0.92 (Figure~\ref{fig-Validation}). The lowest performing
+site was Gafanha High (global accuracy of 75.45\%) whereas Mataducos was
+the site with the most accurate prediction (global accuracy of 98.05\%).
+Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and
+Rhodophyceae were correctly classified with a balanced accuracy of 1,
+0.96, 0.96 and 0.91 respectively. Bacillariophyceae was the least
+performing class (accuracy of 0.72 ) mainly due to the confusion with
+Magnoliopsida and Sediment.
 

### 2024-03-15 index.qmd
final push

@@
 
-centroid_cells<-rbind(confmat_rast_Arz_centroid,confmat_rast_Boat_centroid,confmat_rast_DuerLow_centroid,confmat_rast_GafanhaHigh_centroid,confmat_rast_GafanhaLow_centroid,confmat_rast_Handfisher_1_centroid,confmat_rast_Horse_rooster_centroid,confmat_rast_Kerdrean_centroid,confmat_rast_NorthDike_centroid) %>%
+centroid_cells<-rbind(confmat_rast_Arz_centroid,confmat_rast_Boat_centroid,confmat_rast_DuerLow_centroid,confmat_rast_GafanhaHigh_centroid,confmat_rast_GafanhaLow_centroid,confmat_rast_Handfisher_1_centroid,confmat_rast_Horse_rooster_centroid,confmat_rast_NorthDike_centroid) %>%
   filter(layer == -99)
@@
                    Flight == "DuerLow" ~ "Duer",
-                   TRUE ~ Flight))
+                   TRUE ~ Flight)) %>% 
+  dplyr::filter(Flight != "Kerdrean")
 
@@
 df_Label_Sites<-data.frame(
-    x = c(16,20,24,16,20,24,16,20,24),
-    y = c(12,12,12,8,8,8,4,4,4),
+    x = c(16,20,24,16,20,24,16,20),
+    y = c(12,12,12,8,8,8,4,4),
     lab = c(paste0("Gafanha High, ", df_summarize %>% 
@@
                      filter(Flight == "DuerLow") %>% 
-                     pull(prop) %>% 
-                     round(2)),
-            paste0("Kerdrean, ", df_summarize %>% 
-                     filter(Flight == "Kerdrean") %>% 
                      pull(prop) %>% 
@@
           fill = "transparent")+
-    geom_spatraster(data = confmat_rast_Kerdrean,
-                  na.rm = TRUE
-                  )+
-  geom_sf(data = confmat_rast_Kerdrean_sf,
-          fill = "transparent")+
+    # geom_spatraster(data = confmat_rast_Kerdrean,
+    #               na.rm = TRUE
+    #               )+
+  # geom_sf(data = confmat_rast_Kerdrean_sf,
+  #         fill = "transparent")+
   # geom_sf(data = centroid_cells,
@@
                      position = "top",
-                     limits = c(-4.6,29))+
+                     limits = c(-7,29))+
   scale_y_continuous(breaks = seq(1,11, by = 2),
@@
                      expand = c(0, 0.1),
-                     limits = c(-5,15.5))+
+                     limits = c(-5,17.5))+
   geom_polygon(aes(x = c(-3,26,26,-3),
@@
         # legend.position = "top",
-        legend.position = c(0.73, 0.9),
+        legend.position = c(0.73, 0.8),
         legend.direction="horizontal",
@@
         legend.title.align = 0.5,
-        legend.justification = "center")
+        legend.justification = "center")+
+  geom_text(aes(x = 7, y = 16, label = "Truth"), size = 14)+
+  geom_text(aes(x = -5, y = 6, label = "Prediction"), angle = 90, size = 14)
 

### 2024-03-15 docs/_tex/index.tex
minor revisions

@@
 have since been a concern for local policies and economic activities
-\citep{menesguen2018marees}. Some regions of the world have
-louime2017sargassumrecently witnessed an increase in brown macroalgae
-blooms, predominantly involving algae of the genus \emph{Sargassum}
-\citep{louime2017sargassum}. Satellite remote sensing has proven to be a
-valuable tool for mapping the spatial and temporal extent of macroalgal
-blooms worldwide. However, due to its limitations in spatial resolution,
-it can only effectively map well-developed blooms \citetext{\citealp[
+\citep{menesguen2018marees}. Some regions of the world have witnessed an
+increase in brown macroalgae blooms, predominantly involving algae of
+the genus \emph{Sargassum} \citep{louime2017sargassum}. Satellite remote
+sensing has proven to be a valuable tool for mapping the spatial and
+temporal extent of macroalgal blooms worldwide. However, due to its
+limitations in spatial resolution, it can only effectively map
+well-developed blooms \citetext{\citealp[
 ]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
@@
 up-scale. Earth observation methods can bridge this gap and meet the
-needs for monitoring coastal ecosystems.
+needs for monitoring coastal ecosystems
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
-Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs)
-through satellite observations is increasingly common, enabling
-comprehensive monitoring of entire ecosystems over extended time periods
-\citetext{\citealp[
+Biodiversity Variables and Essential Ocean Variables through satellite
+observations is increasingly common, enabling comprehensive monitoring
+of entire ecosystems over extended time periods \citetext{\citealp[
 ]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The

### 2024-03-15 index.qmd
minor revisions

@@
 bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees].
-Some regions of the world have louime2017sargassumrecently witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum].
+Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum].
 Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide.
@@
 Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale.
-Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems.
-[@papathanasopoulou2019satellite].
-The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
+Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems [@papathanasopoulou2019satellite].
+The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
 The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.

### 2024-03-22 docs/_tex/index.tex
pierre's comments

@@
 \hypersetup{
-  pdftitle={PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.},
+  pdftitle={DRAFT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- DRAFT},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
@@
 \begin{frontmatter}
-\title{PREPRINT -- Discriminating Seagrasses From Green Macroalgae in
+\title{DRAFT -- Discriminating Seagrasses From Green Macroalgae in
 European Intertidal areas using high resolution multispectral drone
-imagery -- PREPRINT.}
+imagery -- DRAFT}
 \author[1]{Simon Oiry%
@@
 
-\includegraphics[width=6.63in,height=\textheight]{Figures/table_validation_px.png}
+\includegraphics[width=6.63in,height=\textheight]{Figures/High_res/table_validation_px.png}
 
@@
 \subsection{Vegetation Discrimination}\label{vegetation-discrimination}
-
-\phantomsection\label{cell-fig-Pigm}
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}
-
-}
-
-\caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
-(Green) or absent (Red) in each taxonomic class present in the Neural
-Network Classifier, along with their absorption wavelength measured with
-spectroradiometer. Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco:
-fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
-neoxanthin, PE: phycoerythrin, PC: phycocyanin.}
-
-\end{figure}%
 
@@
 pigments such as zeaxantin, lutein and neoxanthin
-(Figure~\ref{fig-Pigm}). This spectral overlap is further complicated by
-the intermingling of seagrasses and green macroalgae in the same spatial
-locations, posing a significant challenge for remote sensing aimed at
-accurately mapping and monitoring coastal ecosystems. Our study
-addresses these complexities by using high-resolution drone imagery with
-10 spectral bands. \citep{Davies2023} have shown that having at least
-eight spectral bands ranging between 500 nm to 850 nm including a green
-band at 530 nm and another one in the RedEdge region at 730 nm was
-crucial to accurately discriminate amoung green macrophytes.
+(Figure~\ref{fig-Pigm}).
+
+\phantomsection\label{cell-fig-Pigm}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}
+
+}
+
+\caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
+(Green) or absent (Red) in each taxonomic class present in the Neural
+Network Classifier, along with their absorption wavelength measured with
+spectroradiometer. Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco:
+fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
+neoxanthin, PE: phycoerythrin, PC: phycocyanin.}
+
+\end{figure}%
+
+This spectral overlap is further complicated by the intermingling of
+seagrasses and green macroalgae in the same spatial locations, posing a
+significant challenge for remote sensing aimed at accurately mapping and
+monitoring coastal ecosystems. Our study addresses these complexities by
+using high-resolution drone imagery with 10 spectral bands.
+\citep{Davies2023} have shown that having at least eight spectral bands
+ranging between 500 nm to 850 nm including a green band at 530 nm and
+another one in the RedEdge region at 730 nm was crucial to accurately
+discriminate amoung green macrophytes.
 
@@
 Chlorophyceae exhibited the highest reflectance (raw and standardised)
-among all other classes, highlighting the difference in accessory
-pigments (i.e.~carotenoid) between seagrasses and green macroalgae
-\citep{repolho2017seagrass}.
+among all other classes, highlighting the potential differences in
+accessory pigment ratios (i.e.~carotenoid) between seagrasses and green
+macroalgae \citep{repolho2017seagrass}.
 
@@
 
-\subsection{Spectral Spatial Temporal Resolution impact on the
-prediction}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}
+\subsection{Impact of Spectral, Spatial, and Temporal Resolution on
+Predictive
+Accuracy}\label{impact-of-spectral-spatial-and-temporal-resolution-on-predictive-accuracy}
 
@@
 limitations in spatial resolution, it can only effectively map
-well-developed blooms \citetext{\citealp[
-]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
+well-developed blooms \citetext{\citealp[ ]{rs13081408}; \citealp[
+]{klemas2012remote}; \citealp{HARO2023103451}}. High spatial resolution
 drone imagery, coupled with an accurate classification algorithm, could
@@
 of entire ecosystems over extended time periods \citetext{\citealp[
-]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
-significance of monitoring the coastal environment, particularly in
-light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
-be overstated in environmental management and conservation efforts. The
-WFD mandates the achievement and maintenance of ``good ecological
-status'' for all European waters, which necessitates a comprehensive
-understanding and monitoring of aquatic ecosystems, including coastal
-habitats like seagrass beds \citetext{\citealp[
-]{foden2007angiosperms}; \citealp[
+]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The Water
+Framework Directive \citep[WFD :][]{WFD2000} mandates the achievement
+and maintenance of ``good ecological status'' for all European waters,
+which necessitates a comprehensive understanding and monitoring of
+aquatic ecosystems, including coastal habitats like seagrass beds
+\citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
 ]{nordlund2024one}; \citealp{Zoffoli2021}}.

### 2024-03-22 index.qmd
pierre's comments

@@
 ---
-title: PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.
+title: DRAFT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- DRAFT
 author:
@@
   mutate(Class = case_when(Class == 1 ~ "Bare Sediment",
-                              Class == 2 ~ "D - Chloropyceae",
+                              Class == 2 ~ "D - Chlorophyceae",
                               Class == 3 ~ "Bare Sediment",
@@
 
-save_as_image(flx2, "Figures/table_validation_px.png", res = 300)
+save_as_image(flx2, "Figures/High_res/table_validation_px.png", res = 300)
 
@@
 
-knitr::include_graphics("Figures/table_validation_px.png")
+knitr::include_graphics("Figures/High_res/table_validation_px.png")
 ```
@@
 
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management.
+By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
+Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).
+
 ```{r Table Pigment}
@@
                                 x = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5),
-                                lab = c("Chlb","Chlc","Fuco","Zea","Diad","Lut","Neo","PE","PC")
+                                lab = c("Chl-b","Chl-c","Fuco","Zea","Diad","Lut","Neo","PE","PC")
                                 )
@@
 
-ggsave("./Figures/Disc_Pigment_Table.png",rast_pigment, width= 1066*4, height=516*4, units = "px")
+ggsave("./Figures/High_res/Disc_Pigment_Table.png",rast_pigment, width= 1066*4, height=516*4, units = "px")
 
@@
 
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management.
-By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
-Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).
 This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
@@
 The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the difference in accessory pigments (i.e.
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the potential differences in accessory pigment ratios (i.e.
 carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].
@@
 
-## Spectral Spatial Temporal Resolution impact on the prediction
+## Impact of Spectral, Spatial, and Temporal Resolution on Predictive Accuracy
 
@@
 Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide.
-However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote].
+However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote ; @HARO2023103451].
 High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
@@
 The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
-The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
-The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
+The Water Framework Directive [WFD : @WFD2000] mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
 

### 2024-03-22 docs/_tex/index.tex
pierre's comments

@@
 altitude flights were used to train a Deep Learning classifier based on
-Neural Networks to discrimintate among five taxonomic classes of
+Neural Networks to discriminate among five taxonomic classes of
 intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green
@@
 ]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. Both habitat
-fragmentation and reduction, in turn, can severely copromise the
+fragmentation and reduction, in turn, can severely compromise the
 effectiveness of ecosystem services provided by seagrass meadows. While
@@
 processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
-Coastal eutrophication has been ass ociated to excessive accumulation of
+Coastal eutrophication has been associated to excessive accumulation of
 green macroalgae, so-called green tides (\citep{devlin2023nutrients}).
@@
 Magnoliopsida from Chlorophyceae using radiometric data acquired at
-Sentinel-2 's spectral resolution. However the application of this
-approach to satellite RS remains to be validated. Moreover patches of
+Sentinel-2 's spectral resolution. However, the application of this
+approach to satellite RS remains to be validated. Moreover, patches of
 green algae can develop at small spatial scales that are not observable
@@
 ]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
-allows for their application across a diverse thematic range , from
+allows for their application across a diverse thematic range, from
 coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
@@
 \caption{\label{fig-map}Location of drone flights in France and
-Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
+Portugal. A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites),
 C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents
@@
 At each location, a DJI Matrice 200 quadcopter drone equipped with a
-Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
-million pixel reflectance photographs with ten spectral bands ranging
-from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668,
-705, 717, 740 and 840 nm. To ensure consistent lighting conditions
-across flight paths, the drone's trajectory was aligned to maintain a
-solar azimuth angle of 90 degrees. An overlap of 70\% and 80\% (side and
-front respectively) between each image was set for each flight. A
-downwelling light sensor (DLS2) was used to acquire irradiance data
-concomitantly with the camera measurements. Raw data were calibrated in
-reflectance using a calibration panel reflective at \textasciitilde50\%
-provided by the manufacturer. Across all sites, flights were made at two
-different altitudes : 12 m or/and 120 m. (Table~\ref{tbl-flights}).
+Micasense RedEdge Dual MX multispectral camera was flown to take
+1.2-million-pixel reflectance photographs with ten spectral bands
+ranging from the blue to the near infrared (NIR): 444, 475, 531, 560,
+650, 668, 705, 717, 740 and 840 nm. To ensure consistent lighting
+conditions across flight paths, the drone's trajectory was aligned to
+maintain a solar azimuth angle of 90 degrees. An overlap of 70\% and
+80\% (side and front respectively) between each image was set for each
+flight. A downwelling light sensor (DLS2) was used to acquire irradiance
+data concomitantly with the camera measurements. Raw data were
+calibrated in reflectance using a calibration panel reflective at
+\textasciitilde50\% provided by the manufacturer. Across all sites,
+flights were made at two different altitudes : 12 m or/and 120 m.
+(Table~\ref{tbl-flights}).
 
@@
 
-\caption{\label{tbl-flights}List of drone flight, summarising the date,
+\caption{\label{tbl-flights}List of drone flight, summarizing the date,
 the altitude and the purpose of each flight. 12 m and 120 m flights have
@@
 georeferencing imprecision of orthomosaics with an horizontal and
-vertical accuracy of 10cm. dGPS was also used to georeference quadrats
+vertical accuracy of 10cm. dGPS was also used to georeferenced quadrats
 of 0.25 m² assessing the presence or absence of five key taxonomic
@@
 \caption{\label{tbl-validationPX}Vegetation Classes of the model and the
-number of pixels used to train and validate each class}
+number of pixels used to train and validate each class.}
 
@@
 Rhodophyceae. Only low-altitude flights (Table~\ref{tbl-flights}) were
-used for training because their 8 mm spatial resolution allowied to
-avoid spectral sub-pixel mixing and to accurately identify vegetation
-classes. More than 418,000 pixels at 8 mm resolution from the 3 training
-flights were used to train the model (Table~\ref{tbl-validationPX}).
-Twenty one variables were used by the model as predictors: the ten raw
-spectral bands of the Micasense RedEdge Dual MX multispectral camera
-(ranging from 444 nm to 840 nm), the same ten spectral bands
-standardized using a min/max transformation (Equation~\ref{eq-std} ;
-\citep{Cao2017}) and the Normalized difference vegetation index (NDVI,
-Equation~\ref{eq-ndvi}). Standardisation of spectral bands is commonly
-used to eliminate the scaling differences between spectra and to limit
-the effect of biomass on the spectra shape \citetext{\citealp[
+used for training because their 8 mm spatial resolution allowed to avoid
+spectral sub-pixel mixing and to accurately identify vegetation classes.
+More than 418,000 pixels at 8 mm resolution from the 3 training flights
+were used to train the model (Table~\ref{tbl-validationPX}). Twenty one
+variables were used by the model as predictors: the ten raw spectral
+bands of the Micasense RedEdge Dual MX multispectral camera (ranging
+from 444 nm to 840 nm), the same ten spectral bands standardized using a
+min/max transformation (Equation~\ref{eq-std} ; \citep{Cao2017}) and the
+Normalized difference vegetation index (NDVI, Equation~\ref{eq-ndvi}).
+Standardization of spectral bands is commonly used to eliminate the
+scaling differences between spectra and to limit the effect of biomass
+on the spectra shape \citetext{\citealp[
 ]{Douay2022}; \citealp{Davies2023}}.
@@
 sensitivity, specificity, and Kappa coefficient, was generated for each
-sites. All validation matrices were then aggregated to create a unique
-matrix . Altogether, a total of 536,000 pixels was used to validate the
+site. All validation matrices were then aggregated to create a unique
+matrix. Altogether, a total of 536,000 pixels was used to validate the
 model, thus providing a geographically robust validation dataset.
@@
 The high-altitude flight over Gafanha covered a total area of
-approwimately 1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
+approximately 1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
 small island was masked in the prediction map. Most of the intertidal
@@
 correctly classified. In the northern part of the site and near the land
-eadges, patches of the schorre angiosperm \emph{Spartina sp.} were
+edges, patches of the schorre angiosperm \emph{Spartina sp.} were
 misclassified, either as Magnoliopsida or as Phaeophyceae.
@@
 
-Amoung the high altitude flights, the one acquired over the inner lagoon
+Among the high altitude flights, the one acquired over the inner lagoon
 of the Ria de Aveiro covered the largest area with approximately 1.5 km²
@@
 red macroalgae on the eastern part of the site. As shown in the zoom
-(Figure~\ref{fig-Boat}), the edges of the meadow were colonised by green
+(Figure~\ref{fig-Boat}), the edges of the meadow were colonized by green
 macroalgae
@@
 important the variable for prediction of each class. The right plot
-shows the drone raw and standardised reflectance spectra of each class.
-Each slice represents the VIP of both raw and standardised reflectance
+shows the drone raw and standardized reflectance spectra of each class.
+Each slice represents the VIP of both raw and standardized reflectance
 combined.}
@@
 0.85 probability of the model. Everything on the right of this line has
-a probability higher then 0.85 and everything on the left of this line
+a probability higher than 0.85 and everything on the left of this line
 has a lower probability.}
@@
 ]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
-the similarities on their spectal signatures in the visible region of
-the eletromagnetic spectra due to shared pigment
+the similarities on their spectral signatures in the visible region of
+the electromagnetic spectra due to shared pigment
 , Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
@@
 another one in the RedEdge region at 730 nm was crucial to accurately
-discriminate amoung green macrophytes.
+discriminate among green macrophytes.
 
@@
 concentration and/or pigment ratios \citep{bargain2013seasonal},
-different cellular organisation and the disposition of the plant over
+different cellular organization and the disposition of the plant over
 the sediment surface \citetext{\citealp[ ]{beach1997vivo}; \citealp[
@@
 accurately identifying Chlorophyceae. In fact, at this wavelength,
-Chlorophyceae exhibited the highest reflectance (raw and standardised)
+Chlorophyceae exhibited the highest reflectance (raw and standardized)
 among all other classes, highlighting the potential differences in
@@
 \citep{meleder2003spectrometric}. Furthermore, it is the vegetation with
-the lowest concentration of chlorphyll-a, pigment absorbing light both
+the lowest concentration of chlorophyll-a, pigment absorbing light both
 in the blue and the red. The transparency of Bacillariophyceae makes the
@@
 shape of the spectra in the visible part of the electromagnetic spectra,
-where different pigmentation are associated to taxonomic dignostic
+where different pigmentation are associated to taxonomic diagnostic
 features. This was a key feature in building a model that could reliably

### 2024-03-22 index.qmd
pierre's comments

@@
 Nine drone flights were conducted at two different altitudes (12m and 120m) across heterogeneous intertidal European habitats in France and Portugal.
-Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
+Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discriminate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
 Classification of drone imagery resulted in an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
@@
 Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
-Both habitat fragmentation and reduction, in turn, can severely copromise the effectiveness of ecosystem services provided by seagrass meadows.
+Both habitat fragmentation and reduction, in turn, can severely compromise the effectiveness of ecosystem services provided by seagrass meadows.
 While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been ass ociated to excessive accumulation of green macroalgae, so-called green tides (@devlin2023nutrients).
+Coastal eutrophication has been associated to excessive accumulation of green macroalgae, so-called green tides (@devlin2023nutrients).
 Green tides produce shade and suffocation over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
@@
 Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more than 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
-However the application of this approach to satellite RS remains to be validated.
-Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of a green tide.
+However, the application of this approach to satellite RS remains to be validated.
+Moreover, patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of a green tide.
 
 Drones can potentially fill the gaps left by satellite RS and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
-The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
+The versatility of drones allows for their application across a diverse thematic range, from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
 However, when applied to coastal habitat mapping, most case studies are limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
@@
 #| fig-cap: >
-#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents intertidal areas. 
+#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents intertidal areas. 
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands ranging from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2-million-pixel reflectance photographs with ten spectral bands ranging from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
 To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees.
@@
 #| label: tbl-flights
-#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
+#| tbl-cap: List of drone flight, summarizing the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
 #| cache: true
@@
 GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+dGPS was also used to georeferenced quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
@@
 #| warning: false
-#| tbl-cap: Vegetation Classes of the model and the number of pixels used to train and validate each class
+#| tbl-cap: Vegetation Classes of the model and the number of pixels used to train and validate each class.
 #| label: tbl-validationPX
@@
 The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
+Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
 More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
 Twenty one variables were used by the model as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
-Standardisation of spectral bands is commonly used to eliminate the scaling differences between spectra and to limit the effect of biomass on the spectra shape [@Douay2022 ; @Davies2023].
+Standardization of spectral bands is commonly used to eliminate the scaling differences between spectra and to limit the effect of biomass on the spectra shape [@Douay2022 ; @Davies2023].
 
@@
 Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.
-A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
-All validation matrices were then aggregated to create a unique matrix .
+A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each site.
+All validation matrices were then aggregated to create a unique matrix.
 Altogether, a total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the model, thus providing a geographically robust validation dataset.
@@
 
-The high-altitude flight over Gafanha covered a total area of approwimately 1 km² (@fig-GafHigh).
+The high-altitude flight over Gafanha covered a total area of approximately 1 km² (@fig-GafHigh).
 A channel contouring a small island was masked in the prediction map.
@@
 Patches of Rhodophyceae were correctly classified.
-In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+In the northern part of the site and near the land edges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 
-Amoung the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
+Among the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
 This site was dominated by seagrass and the red macroalgae *Gracilaria vermicullophyla*.
 The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
-As shown in the zoom (@fig-Boat), the edges of the meadow were colonised by green macroalgae
+As shown in the zoom (@fig-Boat), the edges of the meadow were colonized by green macroalgae
 
@@
 The bigger the slice, the more important the variable for prediction of each class.
-The right plot shows the drone raw and standardised reflectance spectra of each class.
-Each slice represents the VIP of both raw and standardised reflectance combined.
+The right plot shows the drone raw and standardized reflectance spectra of each class.
+Each slice represents the VIP of both raw and standardized reflectance combined.
 #| label: fig-VIP
@@
 The vertical dashed line shows the 0.85 probability of the model.
-Everything on the right of this line has a probability higher then 0.85 and everything on the left of this line has a lower probability.
+Everything on the right of this line has a probability higher than 0.85 and everything on the left of this line has a lower probability.
 #| label: fig-upscaling
@@
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
+The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectral signatures in the visible region of the electromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
 Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).
@@
 Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands.
-@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate amoung green macrophytes.
+@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate among green macrophytes.
 
@@
 Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
-Several factors can explain these differences such has different concentration and/or pigment ratios [@bargain2013seasonal], different cellular organisation and the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
+Several factors can explain these differences such has different concentration and/or pigment ratios [@bargain2013seasonal], different cellular organization and the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the potential differences in accessory pigment ratios (i.e.
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardized) among all other classes, highlighting the potential differences in accessory pigment ratios (i.e.
 carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].
@@
 This is not a usual diagnostic wavelength for Bacillariophyceae which is mainly identified by the presence of fucoxanthin and chlorophyll c (@fig-Pigm), but it correspond to the absorption of diadinoxanthin an accessory pigment characteristic of this class [@meleder2003spectrometric].
-Furthermore, it is the vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
+Furthermore, it is the vegetation with the lowest concentration of chlorophyll-a, pigment absorbing light both in the blue and the red.
 The transparency of Bacillariophyceae makes the reflectance of the sediment part of the overall reflectance of Bacillariophyceae, further explaining the high reflectance in the blue.
@@
 To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]).
-This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features.
+This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic diagnostic features.
 This was a key feature in building a model that could reliably predict vegetation across geographical sites and seasons.

### 2024-04-29 docs/_tex/index.tex
pierre's comments
add pierre's comment

--- 2024-03-15 docs/_tex/index.tex
@@
 covering a total area of 467 000 m². The model exhibited an accuracy of
-96.4\% in identifying seagrass. This work showed that although they
-share the same pigmentary composition, seagrass and green algae can be
-discriminated using a multispectral sensor with ten spectral bands at
-444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm. The algorithm
-should now be adapted for Sentinel-2 to see if this discrimination is
-still operational at a coarser spatial resolution.
+96.4\% in identifying seagrass. Importantly, seagrass and green algae
+can be discriminated, although they share the same pigment composition.
+As the algorithm was developed for a multispectral camera with ten
+spectral bands in the visible and near-infrared, it could be adapted to
+the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering
+promising perspectives for satellite remote sensing of intertidal
+biodiversity over lager scales.
 \end{abstract}
@@
 areas is limited by several constraints. Satellite missions with a high
-temporal resolution (e.g.~daily MODIS observation) are limited by a
-coarse spatial resolution (\textgreater100m) over these restricted
-extension areas. Missions with a high spatial resolution such as
+temporal resolution (e.g.~daily MODIS observation) are limited by a too
+coarse spatial resolution (\textgreater100m) to accurately map patchy
+seagrass meadows. Missions with a high spatial resolution such as
 Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral
@@
 measurements, due to their ability to provide spatially-explicit
-observations at very high spatial resolutions (pixel size from cm to mm)
+observations at very high spatial resolutions (pixel size from mm to cm)
 while capturing data at multi-spectral resolution \citetext{\citealp[
@@
 ]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
-to coastal habitat mapping, most case studies are limited to a single
-flight, restricting the generalizability of their application over wider
-geographical scales \citetext{\citealp[ ]{Roman2021}; \citealp[
-]{collin2019improving}; \citealp[
+to coastal habitat mapping, most case studies were previously limited to
+a single flight, restricting the generalizability of their application
+over wider geographical scales \citetext{\citealp[
+]{Roman2021}; \citealp[ ]{collin2019improving}; \citealp[
 ]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. The present study
 aimed at analyzing the potential of multispectral drone RS to map
-intertidal macrophytes, with a particular focus on discriminating
-Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
-Ten drone flights were performed over soft-bottom intertidal areas along
-two European countries (France and Portugal), covering a wide range of
-habitats, from monospecific seagrass meadows to meadows mixed with
-green, or red macroalgae. A deep learning algorithm was trained and
-validated for macrophyte discrimination, emphasizing applicability
-across diverse sites without a loss of prediction accuracy.
+intertidal macrophytes over a diverse biogeographical range, with a
+particular focus on discriminating Magnoliopsida and Chlorophyceae
+(Seagrass and Green Algae respectively). Ten drone flights were
+performed over soft-bottom intertidal areas along two European countries
+(France and Portugal), covering a wide range of habitats, from
+monospecific seagrass meadows to meadows mixed with green, or red
+macroalgae. A deep learning algorithm was trained and validated for
+macrophyte discrimination, emphasizing applicability across diverse
+sites without a loss of prediction accuracy.
 
@@
 Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
-C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents
-intertidal areas.}
+C: Ria de Aveiro Coastal Lagoon (Three sites). Green areas represents
+the intertidal zone.}
 
@@
 
-The nine drone flights were utilized to produce a total of nine
-prediction maps, each of them associated with a probability map that
-indicates the probability of the selected class for every pixel. The
-low-altitude flight conducted in Gafanha, Portugal, represents the site
-with the highest complexity (Figure~\ref{fig-GafLow}). Among the five
-vegetation classes on which the model was trained, four were present on
-this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass
-meadow. There was also Bacillariophyceae forming biofilms on parts of
-sediment surface. Although the seagrass bed was solely composed of
-\emph{Nanozostera noltei}, various colors of this specie could be
-observed from dark green (corresponding to healthy leaves) to
-whitish/brown (when leaves were discolored having lost their
-pigmentation). Regardless of color, Magnoliopsida pixels were accurately
-predicted by the model.
+Each drone flight was used to produce a prediction map, as well as a
+probability map that indicates the likelihood of the selected class for
+every pixel. The low-altitude flight conducted in Gafanha, Portugal,
+represents the site with the highest complexity
+(Figure~\ref{fig-GafLow}). Among the five vegetation classes on which
+the model was trained, four were present on this site, with
+Chlorophyceae and Rhodophyceae mixed with the seagrass meadow. There was
+also Bacillariophyceae forming biofilms on parts of sediment surface.
+Although the seagrass bed was solely composed of \emph{Nanozostera
+noltei}, various colors of this specie could be observed from dark green
+(corresponding to healthy leaves) to whitish/brown (when leaves were
+discolored having lost their pigmentation). Regardless of color,
+Magnoliopsida pixels were accurately predicted by the model.
 
@@
 The high-altitude flight over Gafanha covered a total area of
-approwimately 1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
+\textasciitilde1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
 small island was masked in the prediction map. Most of the intertidal
@@
 
+In this study, a key innovation lies in the utilization of drone flights
+at two different altitudes (12m and 120m) for constructing the neural
+network model. The lower altitude flights (8mm spatial resolution)
+enabled precise selection of pure pixels to train the neural network
+model. This methodology implies a consistency between the reflectance
+measured from both altitudes. Figure~\ref{fig-CompareRef} depicts the
+relationship between reflectance from a low and a high-altitude flights
+conducted over the same area.
+
 \phantomsection\label{cell-fig-CompareRef}
@@
 
-In this study, a key innovation lies in the utilization of drone flights
-at two different altitudes (12m and 120m) for constructing the neural
-network model. The lower altitude flights (8mm spatial resolution)
-enabled precise selection of pure pixels to train the neural network
-model. This methodology implies a consistency between the reflectance of
-both altitudes. Figure~\ref{fig-CompareRef} depicts the relationship
-between reflectance from a low and a high-altitude flights conducted
-over the same area. Overall there was a good agreement between the two
-altitudes. There was however a slight underestimation for raw
-reflectance values in the high-altitude flight, particularly for higher
-reflectance values (Figure~\ref{fig-CompareRef} A). Since both flights
-were conducted over vegetation areas, the highest reflectance values
-correspond to the infrared part of the spectrum. This different is not
-present anymore when reflectance values of both flights have been
-standardized (Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} B).
+Overall there was a good agreement between the two altitudes. There was
+however a slight underestimation for raw reflectance values in the
+high-altitude flight, particularly for higher reflectance values
+(Figure~\ref{fig-CompareRef} A). Since both flights were conducted over
+vegetation areas, the highest reflectance values correspond to the
+infrared part of the spectrum. This different is not present anymore
+when reflectance values of both flights have been standardized
+(Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} B).
 
@@
 validation}\label{neural-network-classification-validation}
+
+A total of 536,000 pixels were used to validate the Neural Network
+classifier. The sites with the lowest and highest number of validation
+data were Gafanha Low (17316 pixels) and Marinha Lanzarote (159713
+pixels), respectively. Model global accuracy was 94.26\% with a Kappa
+coefficient of 0.92 (Figure~\ref{fig-Validation}).
 
@@
 
-A total of 536,000 pixels were used to validate the Neural Network
-classifier. The sites with the lowest and highest number of validation
-data were Gafanha Low (17316 pixels) and Marinha Lanzarote (159713
-pixels), respectively. Model global accuracy was 94.26\% with a Kappa
-coefficient of 0.92 (Figure~\ref{fig-Validation}). The lowest performing
-site was Gafanha High (global accuracy of 75.45\%) whereas Mataducos was
-the site with the most accurate prediction (global accuracy of 98.05\%).
-Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and
-Rhodophyceae were correctly classified with a balanced accuracy of 1,
-0.96, 0.96 and 0.91 respectively. Bacillariophyceae was the least
-performing class (accuracy of 0.72 ) mainly due to the confusion with
-Magnoliopsida and Sediment.
+The lowest performing site was Gafanha High (global accuracy of 75.45\%)
+whereas Mataducos was the site with the most accurate prediction (global
+accuracy of 98.05\%). Overall, the classes Phaeophyceae, Magnoliopsida,
+Sediment and Rhodophyceae were correctly classified with a balanced
+accuracy of 1, 0.96, 0.96 and 0.91 respectively. Bacillariophyceae was
+the least performing class (accuracy of 0.72 ) mainly due to the
+confusion with Magnoliopsida and Sediment.
 
 \subsection{Variable importance}\label{variable-importance}
+
+The computation of the variable importance made it possible to identify
+which bands were the most useful for class prediction
+(Figure~\ref{fig-VIP}).
 
@@
 
-The computation of the variable importance made it possible to identify
-which bands were the most useful for class prediction
-(Figure~\ref{fig-VIP}). The spectral bands at 444, 717 and 842 nm of the
-Micasense camera did not provide as important information to
-discriminate any of the vegetation classes. The band at 531 nm was the
-only important predictor for the classifier to accurately predict
-Chlorophyceae. In fact, at this wavelength, the Chlorophyceae spectra
-showed the highest reflectance among of all vegetation classes. The
-bands at 531 and 740 nm were the most important predictors for
-Phaeophyceae, corresponding to the lowest reflectance among all classes.
-Bands at 475 and 560 nm were the most important predictors for
-Bacillariophyceae and Rhodophyceae, respectively. Four predictors,
-ranging from the green (560 nm) to the RedEdge (705 nm) bands were
-important to accurately predict Magnoliopsida.
-
-\subsection{Effect of the flight height on the
-prediction}\label{effect-of-the-flight-height-on-the-prediction}
+The spectral bands at 444, 717 and 842 nm of the Micasense camera did
+not provide as important information to discriminate any of the
+vegetation classes. The band at 531 nm was the only important predictor
+for the classifier to accurately predict Chlorophyceae. In fact, at this
+wavelength, the Chlorophyceae spectra showed the highest reflectance
+among of all vegetation classes. The bands at 531 and 740 nm were the
+most important predictors for Phaeophyceae, corresponding to the lowest
+reflectance among all classes. Bands at 475 and 560 nm were the most
+important predictors for Bacillariophyceae and Rhodophyceae,
+respectively. Four predictors, ranging from the green (560 nm) to the
+RedEdge (705 nm) bands were important to accurately predict
+Magnoliopsida.
+
+\subsection{Effect of the percent cover on the
+prediction}\label{effect-of-the-percent-cover-on-the-prediction}
+
+Using the very high resolution low altitude flight (8 mm pixels), we
+determined the minimal percent cover required to correctly classify a
+given class within the corresponding high altitude flight
+(Figure~\ref{fig-upscaling}).
 
@@
 
-Using the very high resolution low altitude flight (8 mm pixels), we
-determined the minimal percent cover required to correctly classify a
-given class within the corresponding high altitude flight
-(Figure~\ref{fig-upscaling}). When the percent cover of a given class
-was 100 \%, coarser high-flight pixels are well classified for all the
-classes except for Bare Sediment, which was only well classified 80\% of
-the time. This phenomenon is likely attributed to the time gap between
-the two flights, allowing for microphytobenthos migration to surface
-during low tide, consequently altering the model's classification from
-bare sediment to Bacillariophyceae. A percent cover of at least 80\% was
-sufficient to have all the pixels of high altitude flights correctly
-classified, with the exception of Magnoliopsida that required a higher
-percent cover (\textgreater90 \%) to be well classified. Concerning the
-probability of each class, the highest percent cover was needed to
-confidently predict Bacillariophyceae. To predict Chlorophyceae with a
-confidence of 0.85, a percent cover of 93 \% was needed, 90 \% for
-Magnoliopsida, 92 \% for Rhodophyceae and 97 \% for Bacillariophyceae.
+When the percent cover of a given class was 100 \%, coarser high-flight
+pixels are well classified for all the classes except for Bare Sediment,
+which was only well classified 80\% of the time. This phenomenon is
+likely attributed to the time gap between the two flights, allowing for
+microphytobenthos migration to surface during low tide, consequently
+altering the model's classification from bare sediment to
+Bacillariophyceae. A percent cover of at least 80\% was sufficient to
+have all the pixels of high altitude flights correctly classified, with
+the exception of Magnoliopsida that required a higher percent cover
+(\textgreater90 \%) to be well classified. Concerning the probability of
+each class, the highest percent cover was needed to confidently predict
+Bacillariophyceae. To predict Chlorophyceae with a confidence of 0.85, a
+percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
+Rhodophyceae and 97 \% for Bacillariophyceae.
 
@@
 drone data. The ability to differentiate between various types of
-vegetation, as demonstrated in this study, plays a critical role in
-ecological monitoring and coastal management. By distinguishing between
-seagrasses and macroalgae, our approach facilitates targeted
-conservation strategies, enabling more effective preservation and
-restoration efforts in coastal ecosystems. The discrimination of
-seagrasses from green macroalgae presents significant challenges
-\citetext{\citealp[ ]{oiry2021using}; \citealp[
-]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
-the similarities on their spectal signatures in the visible region of
-the eletromagnetic spectra due to shared pigment
-, Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
-these macrophytes. Besides chlorophyll-a that is common to all
-vegetation types, these two green macrophytes have in common other
-photosynthetic pigments such as chlorophyll-b, and accessory carotenoid
-pigments such as zeaxantin, lutein and neoxanthin
-(Figure~\ref{fig-Pigm}). This spectral overlap is further complicated by
-the intermingling of seagrasses and green macroalgae in the same spatial
-locations, posing a significant challenge for remote sensing aimed at
-accurately mapping and monitoring coastal ecosystems. Our study
-addresses these complexities by using high-resolution drone imagery with
-10 spectral bands. \citep{Davies2023} have shown that having at least
-eight spectral bands ranging between 500 nm to 850 nm including a green
-band at 530 nm and another one in the RedEdge region at 730 nm was
-crucial to accurately discriminate amoung green macrophytes.
+vegetation plays a critical role in ecological monitoring and coastal
+management. By distinguishing between seagrasses and macroalgae, our
+approach facilitates targeted conservation strategies, enabling more
+effective preservation and restoration efforts in coastal ecosystems.
+The discrimination of seagrasses from green macroalgae presents two main
+challenges \citetext{\citealp[ ]{oiry2021using}; \citealp[
+]{bannari2022}; \citealp{veettil2020opportunities}}. First these two
+macrophytes have a similar pigment composition: chlorophyll-a (common to
+all vegetation types), chlorophyll-b (an additional photosynthetic
+pigment), and accessory carotenoids such as zeaxanthin, lutein and
+neoxanthin (Figure~\ref{fig-Pigm}). Second, seagrass and green
+macroalgae frequently co-occur in intertidal areas, and can intermingle
+within a remote sensing pixel if the spatial resolution is too low.
+Here, the issue of intra-pixel mixing was resolved thanks to the very
+high spatial resolution of the drone, and the risk of spetral confusion
+was avoided thanks to the efficiency of the multispectral classifier.
+Our results confirm a recent study based on in situ radiometry, where it
+was demonstrated that a radiometer with at least eight spectral bands
+ranging from 500 to 850 nm and including a green band at 530 nm and a
+RedEdge band at 730 nm was crucial to accurately discriminate green
+macrophytes \citep{Davies2023}.
+
+\phantomsection\label{cell-fig-Pigm}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}
+
+}
+
+\caption{\label{fig-Pigm}Photosynthetic and carotenoid pigments present
+(Green) or absent (Red) in each taxonomic class present in the Neural
+Network Classifier, along with their absorption wavelength measured with
+spectroradiometer. Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco:
+fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
+neoxanthin, PE: phycoerythrin, PC: phycocyanin.}
+
+\end{figure}%
 
@@
 pigment composition of green macrophytes is similar, differences in the
-spectral shape can still be observed (Figure~\ref{fig-vegetation}).
-Several factors can explain these differences such has different
-concentration and/or pigment ratios \citep{bargain2013seasonal},
-different cellular organisation and the disposition of the plant over
-the sediment surface \citetext{\citealp[ ]{beach1997vivo}; \citealp[
+spectral shape can be observed, with green algae having a higher
+reflectance peak at 560 nm as well as a higher NIR plateau than seagrass
+(Figure~\ref{fig-vegetation}). Such differences were previously
+attributed to differences in pigments concentration and/or ratios
+\citep{bargain2013seasonal}, cellular structure as well as in the
+disposition of the plant over the sediment surface \citetext{\citealp[
+]{beach1997vivo}; \citealp[
 ]{kirk1994light}; \citealp{hedley2018influence}}.
 
-The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
-identified that the band at 531 nm was the most important one for
-accurately identifying Chlorophyceae. In fact, at this wavelength,
-Chlorophyceae exhibited the highest reflectance (raw and standardised)
-among all other classes, highlighting the difference in accessory
-pigments (i.e.~carotenoid) between seagrasses and green macroalgae
-\citep{repolho2017seagrass}.
+The VIP analysis (Figure~\ref{fig-VIP}) identified that the band at 531
+nm was the most important for accurately identifying Chlorophyceae. In
+fact, at this wavelength, Chlorophyceae exhibited the highest
+reflectance among all other classes, highlighting the difference in
+carotenoids to chlorophyll-a ratios between seagrasses and green
+macroalgae \citep{repolho2017seagrass}.
 
@@
 \citep{charrier2021growth} make it more reflective in the infrared part
-of the spectra \citep{Slaton2001} whereas the presence of Fucoxanthin
-and Zeaxanthin result in a low reflectance in the visible region
+of the spectra \citep{Slaton2001} whereas the presence of fucoxanthin
+and zeaxanthin result in a low reflectance in the visible region
 (Figure~\ref{fig-Pigm} ; Figure~\ref{fig-VIP}). These two key features
@@
 contributes to the lowest reflectance among all classes in the spectral
-range of 560 to 615 nm (Figure~\ref{fig-VIP}). Indeed the band at 560 nm
-has been identified as important for identifying this class likely due
-to phycoerythrin absorption at this wavelength (\textbf{REF}). Regarding
+range from 560 to 615 nm (Figure~\ref{fig-VIP}). Indeed the band at 560
+nm has been identified as important for identifying this class likely
+due to phycoerythrin absorption at this wavelength. Regarding
 Bacillariophyceae, the VIP analysis (Figure~\ref{fig-VIP}) indicated
-that 475 nm was the most important predictor for this class. This is not
-a usual diagnostic wavelength for Bacillariophyceae which is mainly
-identified by the presence of fucoxanthin and chlorophyll c
-(Figure~\ref{fig-Pigm}), but it correspond to the absorption of
-diadinoxanthin an accessory pigment characteristic of this class
-\citep{meleder2003spectrometric}. Furthermore, it is the vegetation with
-the lowest concentration of chlorphyll-a, pigment absorbing light both
-in the blue and the red. The transparency of Bacillariophyceae makes the
-reflectance of the sediment part of the overall reflectance of
-Bacillariophyceae, further explaining the high reflectance in the blue.
-
-\subsection{Spectral Spatial Temporal Resolution impact on the
-prediction}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}
+that 475 nm was the most important predictor for this class. Indeed, the
+reflectance at 475 nm was higher for Bacillariophyceae than for any
+other vegetation class (Figure~\ref{fig-vegetation}), very likely due to
+the low biomass (and associated concentration of blue-absorbing
+pigments) of microphytobenthos biofilms compared to seagrass and
+macroalgae.
+
+\subsection{Altitude and Temporal Effects on Vegetation Prediction
+Accuracy}\label{altitude-and-temporal-effects-on-vegetation-prediction-accuracy}
 
@@
 
-\subsection{Application of the model}\label{application-of-the-model}
-
-Climate change, global warming, alien and invasive species development,
-coastal erosion, and sealevel rise are expected to continue impacting
-coastal ecosystems in the future
+\subsection{Towards climate and biodiversity
+applications}\label{towards-climate-and-biodiversity-applications}
+
+Climate change, global warming, eutrophication, alien and invasive
+species development, coastal erosion, and sealevel rise are expected to
+continue impacting coastal ecosystems in the future
 \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
-]{holon2018predictive}; \citealp{marquet2024global}}. Therefore the
-demand for meaningful and efficient monitoring methods for these
-habitats has never been greater \citetext{\citealp[
-]{muller2018satellite}; \citealp[
+]{holon2018predictive}; \citealp{marquet2024global}}. and the demand for
+meaningful and efficient monitoring of coastal habitats has never been
+higher\citetext{\citealp[ ]{muller2018satellite}; \citealp[
 ]{villalobos2023remote}; \citealp{oiry2021using}}. Our findings,
-particularly the improved discrimination of seagrass from other
-intertidal vegetation classes, underscore the potential of drone-based
-remote sensing to support diverse applications, from biodiversity
-conservation to climate change adaptation strategies.
-
-With the increase in nutrient concentrations in coastal waters,
-macroalgal blooms are becoming increasingly common in many regions
-around the world \citetext{\citealp[
+particularly the improved discrimination of seagrass and green
+macroalgae from other intertidal vegetation classes, highlight the
+potential of drone-based remote sensing to support diverse applications,
+from biodiversity conservation to climate change adaptation strategies.
+
+Because of coastal eutrophication, macroalgal blooms are becoming
+increasingly common in many regions around the world \citetext{\citealp[
 ]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
-negative impacts on local economic activities, including human health,
-fishing and aquaculture, tourism, and recreational activities
-\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
-first green tide events (i.e.~bloom of green macroalgae of the genus
-\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
-have since been a concern for local policies and economic activities
+negative impacts on human health and local economic activities,
+including human health, fishing and aquaculture, tourism, and
+recreational activities \citetext{\citealp[
+]{villares1999nitrogen}; \citealp{ye2011green}}. The first green tide
+events (i.e.~bloom of green macroalgae of the genus \emph{Ulva}) were
+reported in Brittany, France, back in the 1970s and have since been a
+concern for local policies and economic activities
 \citep{menesguen2018marees}. Some regions of the world have witnessed an
 increase in brown macroalgae blooms, predominantly involving algae of
-the genus \emph{Sargassum} \citep{louime2017sargassum}. Satellite remote
-sensing has proven to be a valuable tool for mapping the spatial and
-temporal extent of macroalgal blooms worldwide. However, due to its
-limitations in spatial resolution, it can only effectively map
-well-developed blooms \citetext{\citealp[
-]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
-drone imagery, coupled with an accurate classification algorithm, could
-be utilized to map the early stages of macroalgal blooms in areas known
-to have regular blooms or in new sites. Indeed, this approach could
-provide early warning alerts to local policymakers.
-
-Employing traditional sampling methods to monitor these ecosystems is
+the genus \emph{Sargassum} washing along the Caribbean coastlines
+\citep{louime2017sargassum}, and more recently \emph{Rugulopteryx
+okamurea} in southern Europe \citep{Roca2022}. Satellite remote sensing
+has proven to be a valuable tool for mapping the spatial and temporal
+extent of macroalgal blooms worldwide. However, due to limitations in
+spatial resolution, it can only effectively map well-developed blooms
+\citetext{\citealp[ ]{rs13081408}; \citealp[
+]{klemas2012remote}; \citealp{haro2023biointertidal}}. High spatial
+resolution drone imagery, coupled with an accurate classification
+algorithm, could be used to map the early stages of macroalgal blooms in
+areas known to have regular blooms or in new sites. Indeed, this
+approach could provide early warning alerts to local managers.
+
+Employing traditional sampling methods to monitor coastal ecosystems is
 time and resource-intensive, and the findings are often difficult to
-up-scale. Earth observation methods can bridge this gap and meet the
-needs for monitoring coastal ecosystems
+scale-up. Earth Observation can bridge this gap and meet the needs for
+systematic monitoring coastal ecosystems over large areas
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
 Biodiversity Variables and Essential Ocean Variables through satellite
-observations is increasingly common, enabling comprehensive monitoring
-of entire ecosystems over extended time periods \citetext{\citealp[
-]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
-significance of monitoring the coastal environment, particularly in
-light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
-be overstated in environmental management and conservation efforts. The
-WFD mandates the achievement and maintenance of ``good ecological
-status'' for all European waters, which necessitates a comprehensive
-understanding and monitoring of aquatic ecosystems, including coastal
-habitats like seagrass beds \citetext{\citealp[
-]{foden2007angiosperms}; \citealp[
+observations has been increasingly common, enabling comprehensive
+monitoring of entire ecosystems over extended time periods
+\citetext{\citealp[ ]{ratnarajah2023monitoring}; \citealp{Zoffoli2021}}.
+The Water Framework Directive \citep{WFD2000} mandates the achievement
+and maintenance of ``good ecological status'' for all European waters,
+which necessitates a comprehensive understanding and monitoring of
+aquatic ecosystems, including coastal habitats like seagrass beds
+\citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
 ]{nordlund2024one}; \citealp{Zoffoli2021}}.
@@
 Effective and efficient monitoring tools are essential for identifying
-the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral imagery
-and, flight on-demand, provide a novel and powerful means to rapidly and
-accurately acquire ground truth data (i.e.~output of the model used in
-the present study). These data are critical for calibrating and
-validating satellite remote sensing applications, thereby enhancing our
-capacity to monitor vast coastal areas systematically under the WFD. A
-perspective of this work could be applying this algorithm to satellite
-imagery (e.g.~Sentinel-2) to evaluate if the discrimination between
-seagrass and green macroalgae is still operational at a coarser spatial
-resolution. The integration of drone technology facilitates a scalable
-approach to environmental surveillance, offering significant
-advancements in the spatial and temporal resolution of data collection.
-This, in turn, supports the directive's objectives by enabling more
-informed and timely management decisions for the conservation and
-restoration of aquatic ecosystems.
+the impacts of human activities and natural changes on coastal
+ecosystems. On-demand, multispectral drone observations at very
+high-resolution provide a novel and powerful tool to rapidly and
+accurately acquire ground truth satellite data. Spatially resolved data
+are indeed critical for calibrating and validating satellite remote
+sensing observations, thereby enhancing our capacity to monitor vast
+coastal areas. A perspective of this work could be to develop a similar
+classifier for satellite images (e.g.~Sentinel-2), and test whether the
+discrimination between seagrass and green macroalgae is still
+operational at a coarser spatial resolution. The integration of drone
+technology facilitates a scalable approach to environmental
+surveillance, offering significant advancements in the spatial and
+temporal resolution of data collection. This, in turn, supports the
+directive's objectives by enabling more informed and timely management
+decisions for the conservation and restoration of aquatic ecosystems.
 

### 2024-04-29 index.qmd
pierre's comments
add pierre's comment

--- 2024-03-15 index.qmd
@@
 The model exhibited an accuracy of 96.4% in identifying seagrass.
-This work showed that although they share the same pigmentary composition, seagrass and green algae can be discriminated using a multispectral sensor with ten spectral bands at 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
-The algorithm should now be adapted for Sentinel-2 to see if this discrimination is still operational at a coarser spatial resolution.
+Importantly, seagrass and green algae can be discriminated, although they share the same pigment composition.
+As the algorithm was developed for a multispectral camera with ten spectral bands in the visible and near-infrared, it could be adapted to the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering promising perspectives for satellite remote sensing of intertidal biodiversity over lager scales.
 plain-language-summary: |
@@
 Satellite missions with a high temporal resolution (e.g.
-daily MODIS observation) are limited by a coarse spatial resolution (\>100m) over these restricted extension areas.
+daily MODIS observation) are limited by a too coarse spatial resolution (\>100m) to accurately map patchy seagrass meadows.
 Missions with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
@@
 
-Drones can potentially fill the gaps left by satellite RS and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from cm to mm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+Drones can potentially fill the gaps left by satellite RS and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
-However, when applied to coastal habitat mapping, most case studies are limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
+However, when applied to coastal habitat mapping, most case studies were previously limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
 Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
@@
 #| fig-cap: >
-#|   Location of drone flights in France and Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites). Green represents intertidal areas. 
+#|   Location of drone flights in France and Portugal.
+A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites).
+Green areas represents the intertidal zone.
 #| label: fig-map
@@
 
-The nine drone flights were utilized to produce a total of nine prediction maps, each of them associated with a probability map that indicates the probability of the selected class for every pixel.
+Each drone flight was used to produce a prediction map, as well as a probability map that indicates the likelihood of the selected class for every pixel.
 The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
@@
 
-The high-altitude flight over Gafanha covered a total area of approwimately 1 km² (@fig-GafHigh).
+The high-altitude flight over Gafanha covered a total area of \~1 km² (@fig-GafHigh).
 A channel contouring a small island was masked in the prediction map.
@@
 ### Reflectance comparison between the two different altitudes
+
 ```{r Reflectance_Validation 2 height}
@@
 
+In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
+The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels to train the neural network model.
+This methodology implies a consistency between the reflectance measured from both altitudes.
+@fig-CompareRef depicts the relationship between reflectance from a low and a high-altitude flights conducted over the same area.
+
 ```{r RefComapare}
@@
 
-In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
-The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels to train the neural network model.
-This methodology implies a consistency between the reflectance of both altitudes.
-@fig-CompareRef depicts the relationship between reflectance from a low and a high-altitude flights conducted over the same area.
 Overall there was a good agreement between the two altitudes.
@@
 
+A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
+The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
+Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
+
 ```{r Global Accuracy assesment Plot}
@@
 
-A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
-The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
-Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
 The lowest performing site was `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(Site)` (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == min(value)) %>% pull(value)*100,2)`%) whereas `r BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(Site)` was the site with the most accurate prediction (global accuracy of `r round(BySite_Metrics %>% filter(metric == "Accuracy") %>% filter(value == max(value)) %>% pull(value)*100,2)`%).
@@
 
+The computation of the variable importance made it possible to identify which bands were the most useful for class prediction (@fig-VIP).
+
 ```{r VIP Plot}
@@
 
-The computation of the variable importance made it possible to identify which bands were the most useful for class prediction (@fig-VIP).
 The spectral bands at 444, 717 and 842 nm of the Micasense camera did not provide as important information to discriminate any of the vegetation classes.
@@
 
-## Effect of the flight height on the prediction
+## Effect of the percent cover on the prediction
 
@@
 
+Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (@fig-upscaling).
+
 ```{r Upscaling Plot}
@@
 
-Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (@fig-upscaling).
 When the percent cover of a given class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
@@
 
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management.
+By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
+The discrimination of seagrasses from green macroalgae presents two main challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities].
+First these two macrophytes have a similar pigment composition: chlorophyll-a (common to all vegetation types), chlorophyll-b (an additional photosynthetic pigment), and accessory carotenoids such as zeaxanthin, lutein and neoxanthin (@fig-Pigm).
+Second, seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
+Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone, and the risk of spetral confusion was avoided thanks to the efficiency of the multispectral classifier.
+Our results confirm a recent study based on in situ radiometry, where it was demonstrated that a radiometer with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macrophytes [@Davies2023].
+
 ```{r Plot Table Pigment}
@@
 #| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
-Chl b: chlorophyll b, Chl c: chlorophyll c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin.')"
+Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin.')"
 #| label: fig-Pigm
@@
 ```
-
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management.
-By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes.
-Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).
-This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems.
-Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands.
-@Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate amoung green macrophytes.
 
@@
 Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in this study, enabled the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
-Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can still be observed (@fig-vegetation).
-Several factors can explain these differences such has different concentration and/or pigment ratios [@bargain2013seasonal], different cellular organisation and the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
+Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can be observed, with green algae having a higher reflectance peak at 560 nm as well as a higher NIR plateau than seagrass (@fig-vegetation).
+Such differences were previously attributed to differences in pigments concentration and/or ratios [@bargain2013seasonal], cellular structure as well as in the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 
-The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the difference in accessory pigments (i.e.
-carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].
-
-Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of Fucoxanthin and Zeaxanthin result in a low reflectance in the visible region (@fig-Pigm ; @fig-VIP).
+The VIP analysis (@fig-VIP) identified that the band at 531 nm was the most important for accurately identifying Chlorophyceae.
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in carotenoids to chlorophyll-a ratios between seagrasses and green macroalgae [@repolho2017seagrass].
+
+Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of fucoxanthin and zeaxanthin result in a low reflectance in the visible region (@fig-Pigm ; @fig-VIP).
 These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
-Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range of 560 to 615 nm (@fig-VIP).
-Indeed the band at 560 nm has been identified as important for identifying this class likely due to phycoerythrin absorption at this wavelength (**REF**).
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range from 560 to 615 nm (@fig-VIP).
+Indeed the band at 560 nm has been identified as important for identifying this class likely due to phycoerythrin absorption at this wavelength.
 Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
-This is not a usual diagnostic wavelength for Bacillariophyceae which is mainly identified by the presence of fucoxanthin and chlorophyll c (@fig-Pigm), but it correspond to the absorption of diadinoxanthin an accessory pigment characteristic of this class [@meleder2003spectrometric].
-Furthermore, it is the vegetation with the lowest concentration of chlorphyll-a, pigment absorbing light both in the blue and the red.
-The transparency of Bacillariophyceae makes the reflectance of the sediment part of the overall reflectance of Bacillariophyceae, further explaining the high reflectance in the blue.
-
-## Spectral Spatial Temporal Resolution impact on the prediction
+Indeed, the reflectance at 475 nm was higher for Bacillariophyceae than for any other vegetation class (@fig-vegetation), very likely due to the low biomass (and associated concentration of blue-absorbing pigments) of microphytobenthos biofilms compared to seagrass and macroalgae.
+
+## Altitude and Temporal Effects on Vegetation Prediction Accuracy
 
@@
 
-## Application of the model
-
-Climate change, global warming, alien and invasive species development, coastal erosion, and sealevel rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
-Therefore the demand for meaningful and efficient monitoring methods for these habitats has never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of seagrass from other intertidal vegetation classes, underscore the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
-
-With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green].
-These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green].
+## Towards climate and biodiversity applications
+
+Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sealevel rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
+and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
+Our findings, particularly the improved discrimination of seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
+
+Because of coastal eutrophication, macroalgal blooms are becoming increasingly common in many regions around the world [@sutton2011european ; @ye2011green].
+These blooms can have negative impacts on human health and local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green].
 The first green tide events (i.e.
 bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees].
-Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum].
+Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* washing along the Caribbean coastlines [@louime2017sargassum], and more recently *Rugulopteryx okamurea* in southern Europe [@Roca2022].
 Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide.
-However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote].
-High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
-Indeed, this approach could provide early warning alerts to local policymakers.
-
-Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale.
-Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems [@papathanasopoulou2019satellite].
-The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
-The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts.
-The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
-
-Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems.
-Drones, with their capability for high-resolution, multispectral imagery and, flight on-demand, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e.
-output of the model used in the present study).
-These data are critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD.
-A perspective of this work could be applying this algorithm to satellite imagery (e.g.
-Sentinel-2) to evaluate if the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
+However, due to limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote ; @haro2023biointertidal].
+High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
+Indeed, this approach could provide early warning alerts to local managers.
+
+Employing traditional sampling methods to monitor coastal ecosystems is time and resource-intensive, and the findings are often difficult to scale-up.
+Earth Observation can bridge this gap and meet the needs for systematic monitoring coastal ecosystems over large areas [@papathanasopoulou2019satellite].
+The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations has been increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @Zoffoli2021].
+The Water Framework Directive [@WFD2000] mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
+
+Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on coastal ecosystems.
+On-demand, multispectral drone observations at very high-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth satellite data.
+Spatially resolved data are indeed critical for calibrating and validating satellite remote sensing observations, thereby enhancing our capacity to monitor vast coastal areas.
+A perspective of this work could be to develop a similar classifier for satellite images (e.g.
+Sentinel-2), and test whether the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.

### 2024-04-30 index.qmd
start of bede's comment

@@
 ---
-title: PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.
+title: Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft
 author:
@@
   Coastal areas support seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration.
-However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation.
-In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the use of satellite data within monitoring programs.
+However, these areas are increasingly impacted by human activities, leading to habitat fragmentation and seagrass decline.
+In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the addition of satellite data within monitoring programs.
 Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
@@
 Due to the concentration of human activities in coastal zones, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
-Both habitat fragmentation and reduction, in turn, can severely copromise the effectiveness of ecosystem services provided by seagrass meadows.
-While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scale, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
-Coastal eutrophication has been ass ociated to excessive accumulation of green macroalgae, so-called green tides (@devlin2023nutrients).
+Global regression and fragmentation of seagrass meadows are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
+Both habitat fragmentation and reduction, in turn, can severely compromise the effectiveness of ecosystem services provided by seagrass meadows.
+While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scales, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
+Coastal eutrophication has been associated to excessive accumulation of green macroalgae, so-called green tides [@devlin2023nutrients].
 Green tides produce shade and suffocation over seagrass individuals, thus threatening the health of seagrass ecosystems [@wang2022].
@@
 Traditionally, indicators of seagrass status have been quantified using *in situ* measurements.
-The acquisition of field data in intertidal zones is however notoriously challenging.
+However, the acquisition of these measurements in intertidal zones is notoriously challenging.
 Intertidal seagrass meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
-Satellite observations have been proven effective in complementing in situ sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
+Satellite observations have been proven effective in complementing *in situ* sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
 [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023]
@@
 Missions with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
-The limited number of spectral bands is indeed a challenge to accurately discriminate seagrass from others co-existing macrophytes.
+The limited number of spectral bands challenges accurate discrimination of seagrass from other co-existing macrophytes.
 In particular Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
@@
 
-Drones can potentially fill the gaps left by satellite RS and in situ measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+Drones can potentially fill the data gaps left by satellite RS and *in situ* measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
@@
 The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
-Ten drone flights were performed over soft-bottom intertidal areas along two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
+Ten drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
@@
 Seven study sites distributed between France and Portugal were selected for their relatively extensive intertidal seagrass beds.
-Two sites are located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
+Two sites were located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
 This gulf covers an area of 115 km² and is only connected to the sea through a 900m wide channel.
 A total of 53 small islands are scattered across the gulf leading to 250 km of shorelines.
-Patchy seagrass meadows can be found on a lot of these islands.
-Within the Gulf of Morbihan we chose two sites : one located on one of the gulf's islands (Arz island) and the other located in the southern part of the gulf (Duer).
+Patchy seagrass meadows can be found on many of these islands.
+One of the sites within the gulf was on one its islands (Arz) and the other was located further south on a mainland beach area (Duer).
 Two other sites were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
-This bay is 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
-Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km².
+This is a 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
+Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km² [@ZOFFOLI2020112020].
 Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
 Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
-The extent of this lagoon is about 80 km² with many narrow channels, large salt marshes and many mudflats that uncovers at low tide.
+The extent of this lagoon is \~80 km² with many narrow channels, large salt marshes and many mudflats that uncover at low tide.
 It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
 The southernmost site (Gafanha) was a mudflat located in a tributary river of the lagoon whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
-These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown and green macroalgae.
+These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown, and green macroalgae.
 
@@
 #| label: tbl-flights
-#| tbl-cap: List of drone flight, summarising the date, the altitude and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
+#| tbl-cap: List of drone flight, summarising the date, the altitude, and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
 #| cache: true
@@
 
-Before each flight, targets used as Ground Control Points (GCPs) were distributed over the study site and georeferenced with a Trimble © Geo XH 6000 differential GPS (dGPS).
-GCPs were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-dGPS was also used to georeference quadrats of 0.25 m² assessing the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+Before each flight, targets used as ground control points were distributed over the study site and georeferenced with a Trimble © Geo XH 6000 differential GPS (dGPS).
+Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
+A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
-Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software (imageJ).
-For all quadrats, the hyperspectral reflectance signatures of each vegetation class was measured using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
-Hyperspectral signatures from quadrats serve for dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
-The workflow developed in this study is presented in @fig-workflow.
+Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software [@schneider2012nih, ImageJ].
+Hyperspectral reflectance signatures of each vegetation class were recorded using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
+Hyperspectral signatures served dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
 
@@
 A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
-The workflow for orthomosaicking was the same for every flight.
+The process for orthomosaicking was identical for every flight.
 First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
@@
 A dense point cloud was then produced using a structure from motion algorithm.
-A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image.
+A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image [@nebel2020review].
 Low altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
@@
 
+The spectral similarities of the reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
+To overcome this challenge, a deep learning classification method was trained, validated, and applied to each drone flight (@fig-workflow).
+
 ```{r Figure3}
@@
 #| fig-cap: "Schematic representation of the workflow.
-Diamonds represent input or output data, and rectangles represent Python processing algorithms.
+Parallelograms represent input or output data, and rectangles represent Python processing algorithms.
 The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights (pixel size: 8 mm) were utilized for training and prediction of the Neural Network model, whereas lower-resolution flights (pixel size: 80 mm) were solely employed for prediction purposes.
@@
 
-The spectral similarities of the reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
-To overcome this challenge, a deep learning classification method was trained, validated, and applied to each drone flight (@fig-workflow).
-
-### Neural Network model building
+### Training dataset building
 
@@
 
-A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model with 2 hidden layers.
+A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model.
 The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
@@
 Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
+Out of the twenty one predictors utilized in this study, Variable Importance in Projection (VIP) was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
 This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time.

### 2024-05-02 docs/_tex/index.tex
adding bede's comments

@@
 \hypersetup{
-  pdftitle={PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.},
+  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
@@
 \begin{frontmatter}
-\title{PREPRINT -- Discriminating Seagrasses From Green Macroalgae in
+\title{Draft -- Discriminating Seagrasses From Green Macroalgae in
 European Intertidal areas using high resolution multispectral drone
-imagery -- PREPRINT.}
+imagery -- Draft}
 \author[1]{Simon Oiry%
@@
 these areas are increasingly impacted by human activities, leading to
-seagrass decline and habitat fragmentation. In situ surveys,
+habitat fragmentation and seagrass decline. In situ surveys,
 traditionally performed to monitor these ecosystems face limitations on
 temporal and spatial coverage, particularly in intertidal zones,
-prompting the use of satellite data within monitoring programs. Yet,
-satellite remote sensing struggles with spatial and spectral resolution,
-making it difficult to discriminate seagrass from other macrophytes in
-highly heterogenous meadows. Drone images at a very high spatial
-resolution offer a promising solution to address challenges related to
-spatial heterogeneity and intrapixel mixture. This study focuses on
-using drone acquisitions with a ten spectral band sensor mirroring those
-of Sentinel-2, for mapping intertidal macrophytes and effectively
-discriminating between seagrass and green macroalgae. Nine drone flights
-were conducted at two different altitudes (12m and 120m) across
-heterogeneous intertidal European habitats in France and Portugal. Low
-altitude flights were used to train a Deep Learning classifier based on
-Neural Networks to discrimintate among five taxonomic classes of
-intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green
-macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae)
-and benthic Bacillariophyceae (Diatoms). Classification of drone imagery
-resulted in an overall accuracy of 94\% across all the sites and images,
-covering a total area of 467 000 m². The model exhibited an accuracy of
-96.4\% in identifying seagrass. Importantly, seagrass and green algae
-can be discriminated, although they share the same pigment composition.
-As the algorithm was developed for a multispectral camera with ten
-spectral bands in the visible and near-infrared, it could be adapted to
-the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering
-promising perspectives for satellite remote sensing of intertidal
-biodiversity over lager scales.
+prompting the addition of satellite data within monitoring programs.
+Yet, satellite remote sensing struggles with spatial and spectral
+resolution, making it difficult to discriminate seagrass from other
+macrophytes in highly heterogenous meadows. Drone images at a very high
+spatial resolution offer a promising solution to address challenges
+related to spatial heterogeneity and intrapixel mixture. This study
+focuses on using drone acquisitions with a ten spectral band sensor
+mirroring those of Sentinel-2, for mapping intertidal macrophytes and
+effectively discriminating between seagrass and green macroalgae. Nine
+drone flights were conducted at two different altitudes (12m and 120m)
+across heterogeneous intertidal European habitats in France and
+Portugal. Low altitude flights were used to train a Deep Learning
+classifier based on Neural Networks to discrimintate among five
+taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass),
+Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae),
+Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
+Classification of drone imagery resulted in an overall accuracy of 94\%
+across all the sites and images, covering a total area of 467 000 m².
+The model exhibited an accuracy of 96.4\% in identifying seagrass.
+Importantly, seagrass and green algae can be discriminated, although
+they share the same pigment composition. As the algorithm was developed
+for a multispectral camera with ten spectral bands in the visible and
+near-infrared, it could be adapted to the Multi-Spectral Instrument
+(MSI) onboard Sentinel-2 thus offering promising perspectives for
+satellite remote sensing of intertidal biodiversity over lager scales.
 \end{abstract}
@@
 meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation are currently observed due to
-climate change, diseases, urbanization, land reclamation, dredging,
-competition with alien species, and reduction in water quality
-\citetext{\citealp[ ]{nguyen2021}; \citealp[ ]{soissons2018}; \citealp[
-]{orth2006}; \citealp[ ]{lin2018}; \citealp[ ]{duffy2019}; \citealp[
+Global regression and fragmentation of seagrass meadows are currently
+observed due to climate change, diseases, urbanization, land
+reclamation, dredging, competition with alien species, and reduction in
+water quality \citetext{\citealp[ ]{nguyen2021}; \citealp[
+]{soissons2018}; \citealp[ ]{orth2006}; \citealp[ ]{lin2018}; \citealp[
+]{duffy2019}; \citealp[
 ]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. Both habitat
-fragmentation and reduction, in turn, can severely copromise the
+fragmentation and reduction, in turn, can severely compromise the
 effectiveness of ecosystem services provided by seagrass meadows. While
 improvements in water quality have been recently reported in Europe,
-allowing an overall recovery of seagrass ecosystems at local scale, many
-coastal waters worldwide are still subjected to strong eutrophication
-processes \citetext{\citealp[ ]{deSantos2019}; \citealp{Zoffoli2021}}.
-Coastal eutrophication has been ass ociated to excessive accumulation of
-green macroalgae, so-called green tides (\citep{devlin2023nutrients}).
-Green tides produce shade and suffocation over seagrass individuals,
-thus threatening the health of seagrass ecosystems \citep{wang2022}.
+allowing an overall recovery of seagrass ecosystems at local scales,
+many coastal waters worldwide are still subjected to strong
+eutrophication processes \citetext{\citealp[
+]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal eutrophication has been
+associated to excessive accumulation of green macroalgae, so-called
+green tides \citep{devlin2023nutrients}. Green tides produce shade and
+suffocation over seagrass individuals, thus threatening the health of
+seagrass ecosystems \citep{wang2022}.
 
@@
 Traditionally, indicators of seagrass status have been quantified using
-\emph{in situ} measurements. The acquisition of field data in intertidal
-zones is however notoriously challenging. Intertidal seagrass meadows
-are only partially exposed during low tide and can be situated in
-difficult-to-reach mudflats, potentially leading to inaccurate and
-limited estimations with conventional sampling techniques
+\emph{in situ} measurements. However, the acquisition of these
+measurements in intertidal zones is notoriously challenging. Intertidal
+seagrass meadows are only partially exposed during low tide and can be
+situated in difficult-to-reach mudflats, potentially leading to
+inaccurate and limited estimations with conventional sampling techniques
 \citep{nijland2019}. Satellite observations have been proven effective
-in complementing in situ sampling, allowing for the near real-time and
-consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
-\citetext{\citealp[ ]{Zoffoli2021}; \citealp[ ]{xu2021}; \citealp[
-]{Traganos2018}; \citealp{coffer2023}}
+in complementing \emph{in situ} sampling, allowing for the near
+real-time and consistent retrieval of seagrass EOVs and EBVs over
+extensive meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
+]{xu2021}; \citealp[ ]{Traganos2018}; \citealp{coffer2023}}
 
@@
 Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral
-resolution. The limited number of spectral bands is indeed a challenge
-to accurately discriminate seagrass from others co-existing macrophytes.
-In particular Chlorophyceae (green algae) and marine Magnoliopsida
+resolution. The limited number of spectral bands challenges accurate
+discrimination of seagrass from other co-existing macrophytes. In
+particular Chlorophyceae (green algae) and marine Magnoliopsida
 (seagrass) share the same pigment composition \citetext{\citealp[
@@
 
-Drones can potentially fill the gaps left by satellite RS and in situ
-measurements, due to their ability to provide spatially-explicit
-observations at very high spatial resolutions (pixel size from mm to cm)
-while capturing data at multi-spectral resolution \citetext{\citealp[
-]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
-allows for their application across a diverse thematic range , from
-coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
-]{casella2020}; \citealp{angnuureng2022}} to mapping species
-distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
+Drones can potentially fill the data gaps left by satellite RS and
+\emph{in situ} measurements, due to their ability to provide
+spatially-explicit observations at very high spatial resolutions (pixel
+size from mm to cm) while capturing data at multi-spectral resolution
+\citetext{\citealp[ ]{fairley2022drone}; \citealp{oh2017use}}. The
+versatility of drones allows for their application across a diverse
+thematic range , from coastal zone management \citetext{\citealp[
+]{adade2021}; \citealp[ ]{casella2020}; \citealp{angnuureng2022}} to
+mapping species distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
 ]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[
@@
 (Seagrass and Green Algae respectively). Ten drone flights were
-performed over soft-bottom intertidal areas along two European countries
-(France and Portugal), covering a wide range of habitats, from
-monospecific seagrass meadows to meadows mixed with green, or red
-macroalgae. A deep learning algorithm was trained and validated for
-macrophyte discrimination, emphasizing applicability across diverse
-sites without a loss of prediction accuracy.
+performed over soft-bottom intertidal areas along the Atlantic
+coastlines of two European countries (France and Portugal), covering a
+wide range of habitats, from monospecific seagrass meadows to meadows
+mixed with green, or red macroalgae. A deep learning algorithm was
+trained and validated for macrophyte discrimination, emphasizing
+applicability across diverse sites without a loss of prediction
+accuracy.
 
@@
 Seven study sites distributed between France and Portugal were selected
-for their relatively extensive intertidal seagrass beds. Two sites are
+for their relatively extensive intertidal seagrass beds. Two sites were
 located in the Gulf of Morbihan (Figure~\ref{fig-map} A), France
@@
 islands are scattered across the gulf leading to 250 km of shorelines.
-Patchy seagrass meadows can be found on a lot of these islands. Within
-the Gulf of Morbihan we chose two sites : one located on one of the
-gulf's islands (Arz island) and the other located in the southern part
-of the gulf (Duer). Two other sites were located in Bourgneuf Bay,
-France (46.9849°N, 2.1488°W). This bay is 340 km² semi-enclosed
-macrotidal bay, protected from waves by Noirmoutier Island. Bourgneuf
-bay hosts a large intertidal seagrass meadow of about 6 km². Within this
-meadow, the sites observed by drones (L'Epine and Barbatre,
-Figure~\ref{fig-map} B) contained monospecific beds of \emph{Nanozostera
-noltei} (dwarf eelgrass) with very little mixing with other macrophytes.
-Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal
-(40.6887°N, 8.6810°W). The extent of this lagoon is about 80 km² with
-many narrow channels, large salt marshes and many mudflats that uncovers
-at low tide. It is connected to the open sea through a single channel,
-with a tidal lag between the North and the South of the lagoon. The
+Patchy seagrass meadows can be found on many of these islands. One of
+the sites within the gulf was on one its islands (Arz) and the other was
+located further south on a mainland beach area (Duer). Two other sites
+were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W). This is a
+340 km² semi-enclosed macrotidal bay, protected from waves by
+Noirmoutier Island. Bourgneuf bay hosts a large intertidal seagrass
+meadow of about 6 km² \citep{ZOFFOLI2020112020}. Within this meadow, the
+sites observed by drones (L'Epine and Barbatre, Figure~\ref{fig-map} B)
+contained monospecific beds of \emph{Nanozostera noltei} (dwarf
+eelgrass) with very little mixing with other macrophytes. Three sites
+were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N,
+8.6810°W). The extent of this lagoon is \textasciitilde80 km² with many
+narrow channels, large salt marshes and many mudflats that uncover at
+low tide. It is connected to the open sea through a single channel, with
+a tidal lag between the North and the South of the lagoon. The
 southernmost site (Gafanha) was a mudflat located in a tributary river
@@
 characterized by a more diverse intertidal vegetation, where patches of
-seagrass intermingle with red, brown and green macroalgae.
+seagrass intermingle with red, brown, and green macroalgae.
 
@@
 \caption{\label{tbl-flights}List of drone flight, summarising the date,
-the altitude and the purpose of each flight. 12 m and 120 m flights have
-a spatial resolution of 8 and 80 mm respectively.}
+the altitude, and the purpose of each flight. 12 m and 120 m flights
+have a spatial resolution of 8 and 80 mm respectively.}
 
@@
 
-Before each flight, targets used as Ground Control Points (GCPs) were
+Before each flight, targets used as ground control points were
 distributed over the study site and georeferenced with a Trimble © Geo
-XH 6000 differential GPS (dGPS). GCPs were used to correct
-georeferencing imprecision of orthomosaics with an horizontal and
-vertical accuracy of 10cm. dGPS was also used to georeference quadrats
-of 0.25 m² assessing the presence or absence of five key taxonomic
-classes of intertidal vegetation : Bacillariophyceae (Unicellular
-benthic diatoms forming biofilms at the sediment surface during low
-tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass),
-Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae)
-(Figure~\ref{fig-vegetation}). Pictures of each quadrat were uploaded
-online to the Global Biodiversity Information Facility (GBIF) platform
-\citep{BedeGbif}, a public open portal to store and share biodiversity
-data. Each photograph was also processed to estimate the percent cover
-of each type of vegetation using an image processing software (imageJ).
-For all quadrats, the hyperspectral reflectance signatures of each
-vegetation class was measured using an ASD FieldSpec HandHeld 2
-spectroradiometer, which acquires reflectance between 325 and 1075 nm,
-with 1 nm of spectral resolution. Hyperspectral signatures from quadrats
-serve for dual purposes: they validate the radiometric calibration of
-drone data and contribute to error reduction in photo interpretation.
-The workflow developed in this study is presented in
-Figure~\ref{fig-workflow}.
+XH 6000 differential GPS (dGPS). Ground control points were used to
+correct georeferencing imprecision of orthomosaics with an horizontal
+and vertical accuracy of 10cm. A dGPS was also used to georeference
+quadrats of 0.25 m² ,which assessed the presence or absence of five key
+taxonomic classes of intertidal vegetation : Bacillariophyceae
+(Unicellular benthic diatoms forming biofilms at the sediment surface
+during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf
+seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red
+macroalgae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
+uploaded online to the Global Biodiversity Information Facility (GBIF)
+platform \citep{BedeGbif}, a public open portal to store and share
+biodiversity data. Each photograph was also processed to estimate the
+percent cover of each type of vegetation using an image processing
+software \citep[ImageJ]{schneider2012nih}. Hyperspectral reflectance
+signatures of each vegetation class were recorded using an ASD FieldSpec
+HandHeld 2 spectroradiometer, which acquires reflectance between 325 and
+1075 nm, with 1 nm of spectral resolution. Hyperspectral signatures
+served dual purposes: they validate the radiometric calibration of drone
+data and contribute to error reduction in photo interpretation.
 
@@
 used to process images to obtain multispectral orthomosaics of each
-flight. The workflow for orthomosaicking was the same for every flight.
+flight. The process for orthomosaicking was identical for every flight.
 First, tying key points were detected inside of each image and between
@@
 made to obtain a digital surface model (DSM), used to reconstruct the
-multispectral ortho-image. Low altitude drone flights produced
-ortho-images with a very high spatial resolution (8 mm per pixel),
-making it efficient to visually distinguish between the various types of
-vegetation. High altitude fights on the other hand allowed to cover
-large areas and produced images with a pixel size of 80 mm
-(Table~\ref{tbl-flights}).
+multispectral ortho-image \citep{nebel2020review}. Low altitude drone
+flights produced ortho-images with a very high spatial resolution (8 mm
+per pixel), making it efficient to visually distinguish between the
+various types of vegetation. High altitude fights on the other hand
+allowed to cover large areas and produced images with a pixel size of 80
+mm (Table~\ref{tbl-flights}).
 
 \subsection{General Workflow}\label{general-workflow}
-
-\phantomsection\label{cell-fig-workflow}
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Figure3_workflow.png}
-
-}
-
-\caption{\label{fig-workflow}Schematic representation of the workflow.
-Diamonds represent input or output data, and rectangles represent Python
-processing algorithms. The overall workflow of this study is divided
-into two distinct parts based on the spatial resolution of the drone
-flights: high-resolution flights (pixel size: 8 mm) were utilized for
-training and prediction of the Neural Network model, whereas
-lower-resolution flights (pixel size: 80 mm) were solely employed for
-prediction purposes. Validation has been performed on both high and low
-resolution flights.}
-
-\end{figure}%
 
@@
 
-\subsubsection{Neural Network model
-building}\label{neural-network-model-building}
+\phantomsection\label{cell-fig-workflow}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Figure3_workflow.png}
+
+}
+
+\caption{\label{fig-workflow}Schematic representation of the workflow.
+Parallelograms represent input or output data, and rectangles represent
+Python processing algorithms. The overall workflow of this study is
+divided into two distinct parts based on the spatial resolution of the
+drone flights: high-resolution flights (pixel size: 8 mm) were utilized
+for training and prediction of the Neural Network model, whereas
+lower-resolution flights (pixel size: 80 mm) were solely employed for
+prediction purposes. Validation has been performed on both high and low
+resolution flights.}
+
+\end{figure}%
+
+\subsubsection{Training dataset
+building}\label{training-dataset-building}
 
@@
 A dataset containing photo-interpreted drone reflectance pixels was
-built to train a Neural Network model with 2 hidden layers. The training
-pixels were categorized into seven different classes, representing the
-various habitats encountered at the different study sites: Sediment,
-Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
+built to train a Neural Network model. The training pixels were
+categorized into seven different classes, representing the various
+habitats encountered at the different study sites: Sediment, Water,
+Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
 Rhodophyceae. Only low-altitude flights (Table~\ref{tbl-flights}) were
@@
 Variable Importance Plots (VIP) serve as a method to identify which
-predictors are important for predicting a specific class. This is
+predictors are important for predicting a specific class. Out of the
+twenty one predictors utilized in this study, Variable Importance in
+Projection (VIP) was computed only for the raw and standardized values
+of the 10 spectral bands captured by the MicaSense camera. This is
 achieved by repeatedly predicting the same dataset while shuffling one

### 2024-05-02 docs/_tex/index.tex
adding bede's comments

@@
 percent cover of each type of vegetation using an image processing
-software \citep[ImageJ]{schneider2012nih}. Hyperspectral reflectance
+software \citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
 signatures of each vegetation class were recorded using an ASD FieldSpec
@@
 
-A structure-from-motion photogrammetry software (Agisoft Metashape) was
-used to process images to obtain multispectral orthomosaics of each
-flight. The process for orthomosaicking was identical for every flight.
-First, tying key points were detected inside of each image and between
-overlapping images in order to obtain a sparse point cloud. This cloud
-was cleaned using reprojection accuracy metric in order to remove noisy
-points. A dense point cloud was then produced using a structure from
-motion algorithm. A surface interpolation of this dense point cloud was
-made to obtain a digital surface model (DSM), used to reconstruct the
-multispectral ortho-image \citep{nebel2020review}. Low altitude drone
-flights produced ortho-images with a very high spatial resolution (8 mm
-per pixel), making it efficient to visually distinguish between the
-various types of vegetation. High altitude fights on the other hand
-allowed to cover large areas and produced images with a pixel size of 80
-mm (Table~\ref{tbl-flights}).
+A structure-from-motion photogrammetry software \citep[Agisoft
+Metashape,][]{agisoft}was used to process images to obtain multispectral
+orthomosaics of each flight. The process for orthomosaicking was
+identical for every flight. First, tying key points were detected inside
+of each image and between overlapping images in order to obtain a sparse
+point cloud. This cloud was cleaned using reprojection accuracy metric
+in order to remove noisy points. A dense point cloud was then produced
+using a structure from motion algorithm. A surface interpolation of this
+dense point cloud was made to obtain a digital surface model (DSM), used
+to reconstruct the multispectral ortho-image \citep{nebel2020review}.
+Low altitude drone flights produced ortho-images with a very high
+spatial resolution (8 mm per pixel), making it efficient to visually
+distinguish between the various types of vegetation. High altitude
+fights on the other hand allowed to cover large areas and produced
+images with a pixel size of 80 mm (Table~\ref{tbl-flights}).
 
@@
 
+\subsubsection{Model building}\label{model-building}
+
+A neural network classification model was built using the fastai
+workflow \citep{howard2018fastai}. This model is composed by 2 hidden
+layers and have a total of 26 054 trainable parameters. Parameters have
+been find tune using 12 epoch to minimize the error rate.
+
 \subsubsection{Validation}\label{validation}
@@
 validation dataset, polygons of each class were photo interpreted in
-order to increase the number of pixels of the validation dataset. A
-confusion matrix, along with precision metrics such as global accuracy,
-sensitivity, specificity, and Kappa coefficient, was generated for each
-sites. All validation matrices were then aggregated to create a unique
-matrix . Altogether, a total of 536,000 pixels was used to validate the
-model, thus providing a geographically robust validation dataset.
-
-\subsection{Variable Importance Plots
-(VIP)}\label{variable-importance-plots-vip}
+order to increase the number of pixels of the validation dataset.A total
+of 536,000 pixels were used to validate the Neural Network classifier.
+The sites with the lowest and highest number of validation data were
+Gafanha Low (17316 pixels) and Marinha Lanzarote (159713 pixels),
+respectively.A confusion matrix, along with precision metrics such as
+global accuracy, sensitivity, specificity, and Kappa coefficient, was
+generated for each sites. All validation matrices were then aggregated
+to create an overall matrix .
+
+\subsection{Variable Importance}\label{variable-importance}
 
@@
 predictors are important for predicting a specific class. Out of the
-twenty one predictors utilized in this study, Variable Importance in
-Projection (VIP) was computed only for the raw and standardized values
-of the 10 spectral bands captured by the MicaSense camera. This is
-achieved by repeatedly predicting the same dataset while shuffling one
-predictor at a time. The benchmark score obtained after each iteration
-is then compared to the benchmark score obtained without shuffling any
-variables. The greater the difference between these two benchmark
-values, the more important the variable is for the model
-\citep{WEI2015399}.
+twenty one predictors utilized in this study, Variable Importance was
+computed only for the raw and standardized values of the 10 spectral
+bands captured by the MicaSense camera. This is achieved by repeatedly
+predicting the same dataset while randomly shuffling one predictor at a
+time. The benchmark score obtained after each iteration is then compared
+to the benchmark score obtained without shuffling any variables. The
+greater the difference between these two benchmark values, the more
+important the variable is for the model \citep{WEI2015399}.
 
@@
 Each drone flight was used to produce a prediction map, as well as a
-probability map that indicates the likelihood of the selected class for
-every pixel. The low-altitude flight conducted in Gafanha, Portugal,
-represents the site with the highest complexity
+probability map that indicates the model derived likelihood of the
+selected class for every pixel. The low-altitude flight conducted in
+Gafanha, Portugal, represents the site with the highest complexity
 (Figure~\ref{fig-GafLow}). Among the five vegetation classes on which
@@
 pixel. Background colors indicate intertidal area (Light Green), land
-area (Light Grey) and water (Light Blue). The yellow polygon shows the
+area (Light Grey) and water (Light Blue). The yellow outline shows the
 extent of the low altitude flight of Gafanha presented in
@@
 of the Ria de Aveiro covered the largest area with approximately 1.5 km²
-(Figure~\ref{fig-Boat}). This site was dominated by seagrass and the red
-macroalgae \emph{Gracilaria vermicullophyla}. The classification
-provided consistent results, with a patchy seagrass meadow mixed with
-red macroalgae on the eastern part of the site. As shown in the zoom
-(Figure~\ref{fig-Boat}), the edges of the meadow were colonised by green
-macroalgae
+(Figure~\ref{fig-Boat}). This site was dominated by seagrass and red
+macroalgae. The classification provided consistent results, with a
+patchy seagrass meadow mixed with red macroalgae on the eastern part of
+the site. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of the
+meadow visually appears to be colonised by green macroalgae, which the
+model agreed with.
 
@@
 (Figure~\ref{fig-Dike}) was conducted near a dike, which crossed the
-northern part of the site from west to east. Alongside this dike, brown
-algae for the order Fucales (\emph{Fucus spp.}, \emph{Ascophyllum
-nodosum}) were attached to sparse rocks and stranded green algae
-(\emph{Ulva spp.}) could be observed Despite the high mixture between
-Chlorophyceae and Magnoliopsida these two classes were correctly
-discriminated by the classifier.
+northern part of the site from west to east. Alongside this dike, Fucale
+brown algae (\emph{Fucus spp.}, \emph{Ascophyllum nodosum}) were
+attached to sparse rocks and stranded green algae (\emph{Ulva spp.})
+could be observed. Despite the high mixture between Chlorophyceae and
+Magnoliopsida these two classes were correctly discriminated by the
+classifier.
 
@@
 \caption{\label{fig-Dike}RGB orthomosaic (Top) and Prediction (Bottom)
-of the Northern part of Noirmoutier Island, France. The total extent of
-this flight was about 28 000 m² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green) and land area
-(Light Grey). The zoom covers an area equivalent to a 10-meter
-Sentinel-2 pixel size.}
+of L'Epine, France. The total extent of this flight was about 28 000 m²
+with a resolution of 80 mm per pixel. Background colors indicate
+intertidal area (Light Green) and land area (Light Grey). The zoom
+covers an area equivalent to a 10-meter Sentinel-2 pixel size.}
 
@@
 at two different altitudes (12m and 120m) for constructing the neural
-network model. The lower altitude flights (8mm spatial resolution)
-enabled precise selection of pure pixels to train the neural network
-model. This methodology implies a consistency between the reflectance
-measured from both altitudes. Figure~\ref{fig-CompareRef} depicts the
-relationship between reflectance from a low and a high-altitude flights
-conducted over the same area.
+network model. Overall there was a good agreement between the two
+altitudes (Figure~\ref{fig-CompareRef}).
 
@@
 
-Overall there was a good agreement between the two altitudes. There was
-however a slight underestimation for raw reflectance values in the
+There was a slight underestimation for raw reflectance values in the
 high-altitude flight, particularly for higher reflectance values
@@
 vegetation areas, the highest reflectance values correspond to the
-infrared part of the spectrum. This different is not present anymore
-when reflectance values of both flights have been standardized
-(Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} B).
+infrared part of the spectrum. This difference is not present when
+reflectance values have been standardized (Equation~\ref{eq-std} ;
+Figure~\ref{fig-CompareRef} B).
 
@@
 
-A total of 536,000 pixels were used to validate the Neural Network
-classifier. The sites with the lowest and highest number of validation
-data were Gafanha Low (17316 pixels) and Marinha Lanzarote (159713
-pixels), respectively. Model global accuracy was 94.26\% with a Kappa
-coefficient of 0.92 (Figure~\ref{fig-Validation}).
+Model global accuracy was 94.26\% with a Kappa coefficient of 0.92
+(Figure~\ref{fig-Validation}).
 
@@
 The labels inside the matrices indicate the balanced accuracy for each
-class. The labels at the bottom of the matrices indicate the User's
+class. The labels at the bottom of the global matrix indicate the User's
 accuracy for each class, and those on the right indicate the Producer's
@@
 accuracy of 1, 0.96, 0.96 and 0.91 respectively. Bacillariophyceae was
-the least performing class (accuracy of 0.72 ) mainly due to the
-confusion with Magnoliopsida and Sediment.
-
-\subsection{Variable importance}\label{variable-importance}
+the least accurate class (accuracy of 0.72 ) mainly due to confusion
+with Magnoliopsida and Sediment.
+
+\subsection{Variable importance}\label{variable-importance-1}
 
@@
 \caption{\label{fig-VIP}Variable Importance of the Neural Network
-Classifier for each taxonomic class. The bigger the slice, the more
+Classifier for each taxonomic class. The longer the slice, the more
 important the variable for prediction of each class. The right plot
@@
 wavelength, the Chlorophyceae spectra showed the highest reflectance
-among of all vegetation classes. The bands at 531 and 740 nm were the
-most important predictors for Phaeophyceae, corresponding to the lowest
+among all vegetation classes. The bands at 531 and 740 nm were the most
+important predictors for Phaeophyceae, corresponding to the lowest
 reflectance among all classes. Bands at 475 and 560 nm were the most
@@
 classes was retrieved using the result of the classification of the low
-altitude flight of Gafanha, Portugal. The vertical dashed line shows the
-0.85 probability of the model. Everything on the right of this line has
-a probability higher then 0.85 and everything on the left of this line
-has a lower probability.}
+altitude flight of Gafanha, Portugal.}
 
@@
 When the percent cover of a given class was 100 \%, coarser high-flight
-pixels are well classified for all the classes except for Bare Sediment,
-which was only well classified 80\% of the time. This phenomenon is
-likely attributed to the time gap between the two flights, allowing for
-microphytobenthos migration to surface during low tide, consequently
-altering the model's classification from bare sediment to
+pixels were well classified for all the classes except for Bare
+Sediment, which was only well classified 80\% of the time. This
+phenomenon may be attributed to the time gap between the two flights,
+allowing for microphytobenthos migration to the surface during low tide,
+consequently altering the model's classification from bare sediment to
 Bacillariophyceae. A percent cover of at least 80\% was sufficient to
@@
 each class, the highest percent cover was needed to confidently predict
-Bacillariophyceae. To predict Chlorophyceae with a confidence of 0.85, a
-percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
-Rhodophyceae and 97 \% for Bacillariophyceae.
+Bacillariophyceae. To predict Chlorophyceae with a model likelihood of
+0.85, a percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92
+\% for Rhodophyceae and 97 \% for Bacillariophyceae.
 
@@
 vegetation plays a critical role in ecological monitoring and coastal
-management. By distinguishing between seagrasses and macroalgae, our
-approach facilitates targeted conservation strategies, enabling more
-effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents two main
-challenges \citetext{\citealp[ ]{oiry2021using}; \citealp[
+management \citep{WFD2000}. By distinguishing between seagrasses and
+macroalgae, our approach facilitates targeted conservation strategies,
+enabling more effective preservation and restoration efforts in coastal
+ecosystems. The discrimination of seagrasses from green macroalgae
+presents two main challenges \citetext{\citealp[
+]{oiry2021using}; \citealp[
 ]{bannari2022}; \citealp{veettil2020opportunities}}. First these two
@@
 Here, the issue of intra-pixel mixing was resolved thanks to the very
-high spatial resolution of the drone, and the risk of spetral confusion
+high spatial resolution of the drone, and the risk of spectral confusion
 was avoided thanks to the efficiency of the multispectral classifier.
-Our results confirm a recent study based on in situ radiometry, where it
-was demonstrated that a radiometer with at least eight spectral bands
-ranging from 500 to 850 nm and including a green band at 530 nm and a
-RedEdge band at 730 nm was crucial to accurately discriminate green
-macrophytes \citep{Davies2023}.
+Our results confirm a recent study based on \emph{in situ} radiometry,
+where it was demonstrated that a radiometer with at least eight spectral
+bands ranging from 500 to 850 nm and including a green band at 530 nm
+and a RedEdge band at 730 nm was crucial to accurately discriminate
+green macrophytes \citep{Davies2023}.
 
@@
 \citep{bargain2013seasonal}, cellular structure as well as in the
-disposition of the plant over the sediment surface \citetext{\citealp[
+orientation of the plant over the sediment surface \citetext{\citealp[
 ]{beach1997vivo}; \citealp[
@@
 
-The VIP analysis (Figure~\ref{fig-VIP}) identified that the band at 531
-nm was the most important for accurately identifying Chlorophyceae. In
-fact, at this wavelength, Chlorophyceae exhibited the highest
-reflectance among all other classes, highlighting the difference in
-carotenoids to chlorophyll-a ratios between seagrasses and green
+The variable importance analysis (Figure~\ref{fig-VIP}) identified that
+the band at 531 nm was the most important for accurately identifying
+Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibited the
+highest reflectance among all other classes, highlighting the difference
+in carotenoids to chlorophyll-a ratios between seagrasses and green
 macroalgae \citep{repolho2017seagrass}.
@@
 Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
-contributes to the lowest reflectance among all classes in the spectral
+contribute to the lowest reflectance among all classes in the spectral
 range from 560 to 615 nm (Figure~\ref{fig-VIP}). Indeed the band at 560
-nm has been identified as important for identifying this class likely
+nm has been identified as important for identifying this class, likely
 due to phycoerythrin absorption at this wavelength. Regarding
@@
 While comparing the reflectance of both altitudes (12 m and 120 m), it
-was observed Figure~\ref{fig-CompareRef} that there is an
-underestimation of the infrared part of the spectra in the high-altitude
-dataset. Such disparity in infrared reflectance may stem from temporal
+was observed that there is an underestimation of the infrared part of
+the spectra in the high-altitude dataset (Figure~\ref{fig-CompareRef}).
+Such disparity in infrared reflectance may stem from temporal
 differences between the flights, possibly resulting in a slightly drier
@@
 
-The Figure~\ref{fig-upscaling} demonstrates that at least 90 \% of
-seagrass cover is necessary for confident prediction of its presence.
-This highlights a limitation of the methodology used to construct the
-training dataset for the model. The dataset used to train our algorithm
-was composed exclusively of pure pixels, which has resulted in the
-model's reduced confidence when faced with lower percentages of seagrass
-cover. Also, intertidal seagrasses exhibit marked phenology, with
-varying pigment composition throughout the year\citetext{\citealp[
+We found 90 \% of seagrass cover is necessary for confident prediction
+of its presence (Figure~\ref{fig-upscaling}). This highlights a
+limitation of the methodology used to construct the training dataset for
+the model. The dataset used to train our algorithm was composed
+exclusively of pure pixels, which resulted in the model's reduced
+confidence when faced with lower percentages of seagrass cover. Also,
+intertidal seagrasses exhibit marked phenology, with varying pigment
+composition throughout the year \citetext{\citealp[
 ]{bargain2013seasonal}; \citealp{legare2022remote}}. Since the training
@@
 potential of drone-based remote sensing to support diverse applications,
-from biodiversity conservation to climate change adaptation strategies.
+from conservation of biodiversity to climate change adaptation
+strategies.
 
@@
 reported in Brittany, France, back in the 1970s and have since been a
-concern for local policies and economic activities
+concern for local stakeholders and economic activities
 \citep{menesguen2018marees}. Some regions of the world have witnessed an
@@
 the impacts of human activities and natural changes on coastal
-ecosystems. On-demand, multispectral drone observations at very
-high-resolution provide a novel and powerful tool to rapidly and
+ecosystems. On-demand, multispectral drone observations at very high
+spatial-resolution provide a novel and powerful tool to rapidly and
 accurately acquire ground truth satellite data. Spatially resolved data
@@
 temporal resolution of data collection. This, in turn, supports the
-directive's objectives by enabling more informed and timely management
+WFD's objectives by enabling more informed and timely management
 decisions for the conservation and restoration of aquatic ecosystems.
@@
 
-The utilization of very high-resolution drone-based remote sensing
-coupled with machine learning techniques has proven to be an effective
-method for the discrimination of seagrasses from green macroalgae with a
-multispectral resolution sensor. Standardized reflectance was
-incorporated in the Neural Network model allowing for a better
-discrimination of spectral features related to pigment absorption in the
-visible. There was a striking difference for the variable of importance
-to discriminate Magnoliopsida from Chlorophyceae. The latter was
-essentially identified with the 451 nm spectral band while more spectral
-bands were needed to identify the former, notably 650, 560, 668, and 705
-nm. As the spectral bands of the Micasense RedEdge Dual MX are very
-similar to those of Sentinel-2, we suggest that multispectral satellite
-data have the potential to perform this discrimination between green
-macrophytes. A sentinel-2 algorithm could be developed, using the output
-of this current workflow as training and validation data. The findings
-underscore the importance of adopting advanced remote sensing tools in
-ecological studies and environmental monitoring, providing a foundation
-for future research and policy implementation aimed at ecosystem
-conservation and restoration.
+The utilization of very high spatial-resolution drone-based remote
+sensing coupled with machine learning techniques has proven to be an
+effective method for the discrimination of seagrasses from green
+macroalgae with a multispectral resolution sensor. Standardized
+reflectance was incorporated in the Neural Network model allowing for a
+better discrimination of spectral features related to pigment absorption
+in the visible. There was a striking difference for the variable of
+importance to discriminate Magnoliopsida from Chlorophyceae. The latter
+was essentially identified with the 451 nm spectral band while more
+spectral bands were needed to identify the former, notably 650, 560,
+668, and 705 nm. As the spectral bands of the Micasense RedEdge Dual MX
+are very similar to those of Sentinel-2, we suggest that multispectral
+satellite data have the potential to perform this discrimination between
+green macrophytes. A sentinel-2 algorithm could be developed, using the
+output of this current workflow as training and validation data. The
+findings underscore the importance of adopting advanced remote sensing
+tools in ecological studies and environmental monitoring, providing a
+foundation for future research and policy implementation aimed at
+ecosystem conservation and restoration.
 

### 2024-05-02 index.qmd
adding bede's comments

@@
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
-Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software [@schneider2012nih, ImageJ].
+Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software [ImageJ, @schneider2012nih].
 Hyperspectral reflectance signatures of each vegetation class were recorded using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
@@
 
-A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight.
+A structure-from-motion photogrammetry software [Agisoft Metashape, @agisoft]was used to process images to obtain multispectral orthomosaics of each flight.
 The process for orthomosaicking was identical for every flight.
@@
 where $R(840nm)$ is the reflectance at 840 nm and $R(668nm)$ is the reflectance at 668 nm.
+
+### Model building
+
+A neural network classification model was built using the fastai workflow [@howard2018fastai].
+This model is composed by 2 hidden layers and have a total of 26 054 trainable parameters.
+Parameters have been find tune using 12 epoch to minimize the error rate.
 
@@
 ```
-
-The workflow of this study revolves around two distinct flight heights (12 m and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
-This comparison was conducted at sites where low and high altitude flights overlapped.
-The low altitude flights were resampled to the same spatial resolution and grid as the high flights using a median resampling method.
-Reflectance values were then extracted, and a scatterplot was generated.
-Subsequently, the slope of the linear model and the coefficient of determination (R²) were computed.
-
-The model was applied to all flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
-These images were used to construct a validation dataset indicating the presence or absence of each class.
-Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.
-A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
-All validation matrices were then aggregated to create a unique matrix .
-Altogether, a total of `r my_comma(round(count_validation_pixel,-3))` pixels was used to validate the model, thus providing a geographically robust validation dataset.
-
-## Variable Importance Plots (VIP)
-
-Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
-Out of the twenty one predictors utilized in this study, Variable Importance in Projection (VIP) was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
-This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time.
-The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables.
-The greater the difference between these two benchmark values, the more important the variable is for the model [@WEI2015399].
-
-## Impact of the percent cover on the prediction
-
-The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm).
-The predictions made on the high-resolution flight can be used to estimate the percent cover of each vegetation class for every pixel of the lower resolution flight.
-Consequently, for each pixel of the high-altitude flights, percent covers of each vegetation class were obtained, and a kernel density plot was generated.
-This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
-
-# Results
-
-## Classification
-
-Each drone flight was used to produce a prediction map, as well as a probability map that indicates the likelihood of the selected class for every pixel.
-The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
-Among the five vegetation classes on which the model was trained, four were present on this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass meadow.
-There was also Bacillariophyceae forming biofilms on parts of sediment surface.
-Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
-Regardless of color, Magnoliopsida pixels were accurately predicted by the model.
-
-```{r Figure 4 Gaf Low}
-#| cache: true
-#| echo: false
-#| warning: false
-#| eval: false
-
-imglist<-
-  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         col = case_when(str_detect(path, "colored") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".aux.xml"))
-
-shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
-  list.files(pattern = ".shp", recursive = T, full.names = T) %>%
-  read_sf() %>%
-  mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
-                        name == "ZOS" ~ 2,
-                        name == "BL" ~ 3,
-                        name == "SED" ~ 4,
-                        name == "GRE" ~ 5,
-                        name == "RED" ~ 6,
-                        name == "Xanthophyceae" ~ 7)) %>% 
-  as("Spatial") %>% 
-  vect()
-
-zoom_extent<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-background_GafHigh<-"Data/shp/Aveiro" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
-  pull(path) %>% 
-  read_sf()
-###### Preview ###########
-
-filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
-mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
-  read_sf()
-
-Flight_aveiro<-data.frame(
-  Name=c(
-  "Gafanha"
-  ) ,
-  Description = c("12m and 120m Flights"),
-  Long=c(-8.742485) ,
-  Lat=c(40.597599) 
-  )  %>% 
-  st_as_sf(coords=c("Long","Lat") )  %>% 
-  st_set_crs("EPSG:4326")  %>% 
-  st_transform(crs(mask_aveiro))  %>% 
-  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
-                lat = sf::st_coordinates(.) [,2]) %>% 
-  sf::st_set_geometry(NULL)
-
-p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
-
-p1<-ggplot() +
-  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#BDBDBD"))+
-  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
-  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
-
-      coord_sf(xlim=c(519749,535233) ,
-          ylim=c(4493310,4508794) )+
-  ggforce::geom_mark_ellipse(data=Flight_aveiro,
-                 aes(x=lon,
-                     y=lat,
-                     label = Name,
-                     group = Name),
-                     # description=Description),
-                 size=0.3,
-                 fill = "goldenrod",
-                 con.colour = "goldenrod4",
-                 show.legend=F,
-                 label.fontsize = 18,
-                 label.hjust = 0.5,
-                 con.size = 2,
-                 alpha=0.8,
-  expand = unit(2, "mm") , 
-  radius = unit(2, "mm") ,
-  label.fill = "grey90",
-  label.buffer = unit(5, "mm")) +
-    # theme_void()+
-  theme_Bede_Map()+
-  labs(x="Longitude",
-       y="Latitude")+
-  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
-  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
-  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
-        legend.position = "none",
-        axis.title = element_blank(),
-        axis.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 20))+
-  theme_void()
-######### RGB #########
- Gafanha_low_ortho<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "ortho",
-         resampled == "TRUE",
-         col == "TRUE") %>%
-  pull(path) %>% 
-  rast() 
- names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
-
- values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
-
- Gafanha_low_ortho_zoomed<-Gafanha_low_ortho %>% 
-   crop(zoom_extent)
-
- map_extent_full<- st_as_sf(as.polygons(ext(Gafanha_low_ortho)))
- sf::st_crs(map_extent_full)<-st_crs(Gafanha_low_ortho)
-
-  map_extent_zommed<- st_as_sf(as.polygons(ext(Gafanha_low_ortho_zoomed)))
- sf::st_crs(map_extent_zommed)<-st_crs(Gafanha_low_ortho_zoomed)
-
- rgb_Gafanha_low_zoomed<-ggplot()+
-   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed, 
-                                  r = 3,
-                                  g = 2,
-                                  b = 1)+
-   theme_Bede_Map()+
-   geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
-   coord_sf(crs = 4326)+
-     theme_void()
-
- scale_labels<-data.frame(x = c(-8.74368, -8.743565,-8.74342),
-                          y = c(rep(40.59792,3)),
-                          text = c("0","10","20 m"))
-
-  rgb_Gafanha_low<- ggplot()+
-  scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="grey30")+
-   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
-         r = 1,
-         g = 2,
-         b = 3,
-         maxcell = 4010533
-         )+
-    ggspatial::annotation_scale(location = "tl",
-                                text_cex=2)+
-      annotation_custom(ggplotGrob(p1),
-                        xmin = -8.7430,
-                        xmax = -8.742702,
-                        ymin = 40.5970515, 
-                        ymax = 40.5974) +
-   theme_Bede_Map()+
-   geom_sf(data = zoom_extent, 
-           fill = "transparent",
-           colour = "black",
-           linetype = "dashed", 
-           linewidth = 1)+
-   coord_sf(crs = 4326)+
-  annotation_custom(ggplotGrob(rgb_Gafanha_low_zoomed),
-                    xmin = -8.7430,
-                    xmax=-8.7427,
-                    ymin = 40.5977) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
-                              y=c(40.5976275,40.5979,40.5975373,40.59771),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  theme(axis.title = element_blank(),
-        axis.text.y = element_text(size = 20),
-        axis.text.x = element_text(size = 20, angle = 20, hjust = 1))+
-    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
-    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
-
-ggsave("Figures/Gaf_Low_RGB.png",rgb_Gafanha_low , width = 1920*4, height = 1129*4, units = "px")
-
-zoom_extent<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-####### Zoomed map ########
-
-Gafanha_low_pred_zoomed<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "low",
-       type == "Pred",
-       resampled == "FALSE",
-       folder == "Input",
-       new == "TRUE") %>% 
-  pull(path) %>% 
-  rast()
-names(Gafanha_low_pred_zoomed)<-"layer"
-
-Gafanha_low_pred_zoomed<-Gafanha_low_pred_zoomed %>% 
-  crop(zoom_extent)
-Gafanha_low_pred_zoomed<-as.factor(Gafanha_low_pred_zoomed)
-
-Gafanha_low_pred_map_zoomed<-ggplot()+
-  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer))+
-  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
-  coord_sf(crs = 4326)+
-  scale_fill_manual(values=c("#70543e", "#b3ff1a","#70543e", "#DAA520", "#389318","#873e23","#b3002d", NA, "#42c9bc"), na.value = NA)+
-  theme_void()+
-  # coord_equal()+
-  theme(axis.text.x = element_blank(),
-      axis.text.y = element_blank(),
-      axis.title = element_blank())+
-  theme(legend.position = "none")
- # Gafanha_low_pred_map_zoomed
-
-####  Overall map
-Gafanha_low_pred<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "low",
-       type == "Pred",
-       # resampled == "TRUE",
-       new == "TRUE") %>% 
-  pull(path) %>% 
-  rast()
-names(Gafanha_low_pred)<-"layer"
-
-values(Gafanha_low_pred)[values(Gafanha_low_pred) == 0] = NA
-
-Gafanha_low_pred<-Gafanha_low_pred %>% 
-  as.factor()
-
-####### Pred ######
-
-Gafanha_low_pred_map <-
-  ggplot()+
-  scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="grey30")+
-  # geom_sf(data = background_GafHigh,
-  #         fill = "white",
-  #         show.legend = F, 
-  #         linewidth=0.05,
-  #         alpha=1,
-  #         colour="white")+
-   ggnewscale::new_scale("fill")+
-    tidyterra::geom_spatraster(data = Gafanha_low_pred, 
-                               mapping = aes(fill = layer),
-                               maxcell = 500832*8)+
-  geom_sf(data = zoom_extent, 
-          fill = "transparent", 
-          colour = "black",
-          linetype = "dashed", 
-          linewidth = 1)+
-  coord_sf(crs = 4326)+
-  annotation_custom(ggplotGrob(Gafanha_low_pred_map_zoomed), 
-                    xmin = -8.7430,
-                    xmax=-8.7427, 
-                    ymin = 40.5977) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
-                              y=c(40.5976275,40.5979,40.5975373,40.59771),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorophyceae",
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-  theme_Bede_Map()+
-  # coord_equal()+
-   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
-         # axis.text.y = element_text(size = 20),
-         axis.text.y = element_blank(),
-         axis.title = element_blank(),
-         legend.background = element_blank(),
-         legend.position = c(0.98,0.3),
-         legend.text = element_text(size = 20),
-         legend.key.size = unit(1,"cm"))+
-    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
-    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
-
-ggsave("Figures/Gaf_Low_Pred.png",Gafanha_low_pred_map , width = 1920*4, height = 1129*4, units = "px")
-
-################# PLOT AND SAVING ###########
-
-plot_Gaf_Low<-rgb_Gafanha_low+
-  Gafanha_low_pred_map
-
-ggsave("Figures/Maps Pred/FigX-Gaf_Low_Pred.png",plot_Gaf_Low , width = 1920*4, height = 1009*4, units = "px")
-```
-
-```{r Figure 4 Gaf Low plot}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanha, Portugal.
-The total extent of this flight was 3000m² with a resolution of 8 mm per pixel.
-Background colors indicate intertidal area (Light Green) and land area (Light Grey).
-The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
-#| label: fig-GafLow
-#| fig-width: 10
-#| fig-height: 8
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png")
-
-```
-
-```{r Figure 4 V2}
-#| cache: true
-#| echo: false
-#| warning: false
-#| eval: false
-imglist<-
-  data.frame("Data",
-             path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         str_detect(path, "High") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          str_detect(path,"AveiroHigh")~"Gafanha",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
-                         str_detect(path, "NewPreds") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         col = case_when(str_detect(path, "colored") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".aux.xml"))
-
-########## ZOOM #############
-
-zoom_extent<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-mask_low<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"mask_Gafanha_low")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-Gafanha_low_ortho_zoomed<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "ortho",
-         resampled == "TRUE",
-         col == "TRUE") %>%
-  pull(path) %>% 
-  rast() %>% 
-  crop(zoom_extent)
-
-names(Gafanha_low_ortho_zoomed)<-c("B1", "B3", "B5","alpha")
-
- Gafanha_low_pred_zoomed<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "Pred",
-         # resampled == "TRUE",
-         new == "TRUE") %>% 
-  pull(path) %>% 
-  rast() %>% 
-  crop(zoom_extent) %>% 
-  mask(mask_low, inverse = T) %>% 
-   as.factor()
-
-names(Gafanha_low_pred_zoomed)<-"layer"
-
-zoomed_low_map<-ggplot()+
-  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed,
-                                 r = 1,
-                                 g = 2,
-                                 b = 3)+
-  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer), show.legend = F)+
-
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
-                    na.value = NA,
-                    name = "", 
-                    labels = c("Sediment", 
-                               "Chlorophyceae", 
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 2)+
-  theme(legend.position = "none")+
-  theme_void()
-
-#############
-
- Gafanha_low_ortho<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "ortho",
-         resampled == "TRUE",
-         col == "TRUE") %>%
-  pull(path) %>% 
-  rast() 
- names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
-values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
-
- Gafanha_low_pred<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "Pred",
-         # resampled == "TRUE",
-         new == "TRUE") %>% 
-  pull(path) %>% 
-  rast()
-names(Gafanha_low_pred)<-"layer"
-
-Gafanha_low_pred_masked<-Gafanha_low_pred %>% 
-  # crop(mask_low) %>% 
-  mask(mask_low, inverse = T)
-
-values(Gafanha_low_pred_masked)[values(Gafanha_low_pred_masked) == 0] = NA
-
-Gafanha_low_pred_masked<-Gafanha_low_pred_masked %>% 
-  as.factor()
-
-rgb_Gafanha_low <- ggplot()+
-  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
-                                 r = 1,
-                                 g = 2,
-                                 b = 3)+
-  tidyterra::geom_spatraster(data = Gafanha_low_pred_masked, mapping = aes(fill = layer))+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
-                    na.value = NA,
-                    name = "", 
-                    labels = c("Sediment", 
-                               "Chlorophyceae", 
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-  ggspatial::annotation_scale(location = "bl",text_cex=2)+
-  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
-
-  geom_segment(aes(x = -8.7434247325, y=40.5977530006, xend = -8.7430558162, yend = 40.5972152706), linetype ="dashed" ,linewidth=2)+
-  annotation_custom(ggplotGrob(zoomed_low_map), xmin = -8.743725, xmax = -8.7434057328, ymin = 40.5977200450, ymax = 40.59798) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.74336194,-8.74371,-8.743243794,-8.7434057328), y=c(40.59762751,40.5977400850,40.59762725,40.5977200450),grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  theme_Bede_Map()+
-  coord_sf(crs = 4326)+
-  theme(axis.title = element_blank(),
-        axis.text.y = element_text(size = 20),
-        axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
-        legend.position=c(0.3, 0.3))+
-  # ggtitle("a ")+
-  scale_x_continuous(breaks=seq(-8.7437, -8.7430, 0.0002))
-rgb_Gafanha_low
-
-ggsave("Figures/Gaf_Low_RGB_Pred_V2.png",rgb_Gafanha_low , width = 890*4, height = 1120*4, units = "px")
-
-```
-
-The high-altitude flight over Gafanha covered a total area of \~1 km² (@fig-GafHigh).
-A channel contouring a small island was masked in the prediction map.
-Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
-Only a few pixels were classified as Chlorophyceae at this spatial scale.
-Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remained mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
-Patches of Rhodophyceae were correctly classified.
-In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
-
-```{r Figure 5 Gaf High}
-#| cache: true
-#| echo: false
-#| warning: false
-#| eval: false
-
-imglist<-
-  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         str_detect(path, "High") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          str_detect(path, "AveiroHigh") ~ "Gafanha",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "Preds") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
-                         str_detect(path, "NewPreds") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         col = case_when(str_detect(path, "colored") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".aux.xml"))
-
-#### Preview ####
-
-filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
-mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
-  read_sf()
-
-Flight_aveiro<-data.frame(
-  Name=c(
-  "Gafanha"
-  ) ,
-  Description = c("12m and 120m Flights"),
-  Long=c(-8.742485) ,
-  Lat=c(40.597599) 
-  )  %>% 
-  st_as_sf(coords=c("Long","Lat") )  %>% 
-  st_set_crs("EPSG:4326")  %>% 
-  st_transform(crs(mask_aveiro))  %>% 
-  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
-                lat = sf::st_coordinates(.) [,2]) %>% 
-  sf::st_set_geometry(NULL)
-
-p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
-
-p1<-ggplot() +
-  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#BDBDBD"))+
-  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
-  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
-      coord_sf(xlim=c(519749,535233) ,
-          ylim=c(4493310,4508794) )+
-  ggforce::geom_mark_ellipse(data=Flight_aveiro,
-                 aes(x=lon,
-                     y=lat,
-                     label = Name,
-                     group = Name),
-                     # description=Description),
-                 size=0.3,
-                 fill = "goldenrod",
-                 con.colour = "goldenrod4",
-                 show.legend=F,
-                 label.fontsize = 20,
-                 label.hjust = 0.5,
-                 con.size = 2,
-                 alpha=0.8,
-  expand = unit(2, "mm") , 
-  radius = unit(2, "mm") ,
-  label.fill = "grey90",
-  label.buffer = unit(5, "mm")) +
-    # theme_void()+
-  theme_Bede_Map()+
-  labs(x="Longitude",
-       y="Latitude")+
-  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
-  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
-  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
-        legend.position = "none",
-        axis.title = element_blank(),
-        axis.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 20))+
-  theme_void()
-
-#####
-
-land_mask_GafHigh<-"Data/shp/Aveiro" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "mask_Gafanha_high1")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-background_GafHigh<-"Data/shp/Aveiro" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-GafHigh_ortho<-imglist %>% 
-  dplyr::filter(site == "Gafanha",
-                type == "ortho",
-                alt=="high",
-                col == "TRUE") %>%
-  pull(path) %>% 
-  rast()
-names(GafHigh_ortho)<-c("B1","B3", "B5", "alpha")
-
-# values(GafHigh_ortho)[values(GafHigh_ortho$B1) == 0] = NA
-
-GafHigh_ortho_masked<-GafHigh_ortho %>% 
-  mask(land_mask_GafHigh, inverse = F) %>% 
-  crop(land_mask_GafHigh)
-
-GafHigh_ortho_masked<-na.omit(GafHigh_ortho_masked, field=NA, geom=FALSE)
-
-###### RGB ########
-zoom_gaf_high_sf<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_High_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-Gaflow_extent<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"GafLow_extent.shp")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-rgb_Gafanha_High_zoomed<-GafHigh_ortho_masked %>% 
-  crop(zoom_gaf_high_sf)
-
-rgb_Gafanha_High_zoomed<-
-  ggplot()+
-  tidyterra::geom_spatraster_rgb(data = rgb_Gafanha_High_zoomed,
-         r = 1,
-         g = 2,
-         b = 3)+
-     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
-  theme_void()
-
-rgb_Gafanha_High <- ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-   tidyterra::geom_spatraster_rgb(data = GafHigh_ortho_masked,
-         r = 1,
-         g = 2,
-         b = 3,
-         maxcell = 5007120)+
-    ggspatial::annotation_scale(location = "bl",
-                                text_cex=2)+
-    annotation_custom(ggplotGrob(p1), 
-                      xmin = -8.744, 
-                      xmax = -8.7412,
-                      ymin = 40.5923,
-                      ymax = 40.595) +
-    geom_sf(data = zoom_gaf_high_sf,
-            fill = "transparent", 
-            colour = "black",
-            linetype = "dashed", 
-            linewidth = 1)+
-    geom_sf(data = Gaflow_extent,
-            fill = "transparent", 
-            colour = "red",
-            linetype = "dashed", 
-            linewidth = 2)+
-    geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
-                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", 
-            linewidth = 1)+
-  annotation_custom(ggplotGrob(rgb_Gafanha_High_zoomed),
-                    xmin = -8.7479, 
-                    xmax = -8.7452, 
-                    ymin = 40.5979,
-                    ymax = 40.603) +
-   theme_Bede_Map()+
-   coord_sf(crs = 4326)+
-   # xlim(c(-8.748, -8.741))+
-  # ylim(c(40.593,40.601))+
-  theme(axis.title = element_blank(),
-         axis.text.x = element_text(size = 20, angle = 20, hjust = 1),
-         axis.text.y = element_text(size = 20))+
-  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
-  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
-# rgb_Gafanha_High
-
-ggsave("Figures/Gaf_High_RGB.png",rgb_Gafanha_High , width = 712*4, height = 1120*4, units = "px")
-
-######### Pred #######
-Gafanha_high_pred<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "high",
-       type == "Pred",
-       new == "TRUE",
-       !str_detect(path, "Probs")) %>% 
-  pull(path) %>% 
-  rast()
-names(Gafanha_high_pred)<-"layer"
-
-GafHigh_pred_masked<-Gafanha_high_pred %>% 
-  mask(land_mask_GafHigh, inverse = F) %>% 
-  crop(land_mask_GafHigh)
-
-GafHigh_pred_masked<-na.omit(GafHigh_pred_masked, field=NA, geom=FALSE)
-
-values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 0] = NA
-values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 3] = 1
-
-GafHigh_pred_masked<-GafHigh_pred_masked %>% 
-  as.factor()
-
-Gafanha_High_zoomed_pred<-GafHigh_pred_masked %>% 
-  crop(zoom_gaf_high_sf)
-
-Gafanha_High_zoomed_pred<-
-  ggplot()+
-   tidyterra::geom_spatraster(data = Gafanha_High_zoomed_pred, mapping = aes(fill = layer),
-                            show.legend = F,
-                             maxcell = 5007120)+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorophyceae",
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
-  theme_void()
-
-Gafanha_high_pred_map<-ggplot()+
-  geom_sf(data = background_GafHigh, 
-          mapping = aes(fill = Type),
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-    scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  ggnewscale::new_scale("fill")+
-  tidyterra::geom_spatraster(data = GafHigh_pred_masked, 
-                             # show.legend = F,
-                             mapping = aes(fill = layer),
-                             maxcell = 5010420)+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorophyceae",
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-       geom_sf(data = zoom_gaf_high_sf, 
-               fill = "transparent", 
-               colour = "black",
-               linetype = "dashed", 
-               linewidth = 1)+
-    geom_sf(data = Gaflow_extent,
-            fill = "transparent", 
-            colour = "red",
-            linetype = "dashed", 
-            linewidth = 2)+
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
-                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  annotation_custom(ggplotGrob(Gafanha_High_zoomed_pred), 
-                    xmin = -8.7479, 
-                    xmax = -8.7452, 
-                    ymin = 40.5979,
-                    ymax = 40.603) +
-  coord_sf(crs = 4326)+
-  theme_Bede_Map()+
-   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
-         axis.title = element_blank(),
-        # axis.text.y = element_text(size = 20),
-        axis.text.y = element_blank(),
-         legend.background = element_blank(),
-         legend.position = c(0.96,0.23),
-         legend.text = element_text(size = 23),
-         legend.key.size = unit(1.2,"cm"))+
-  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
-  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
-# Gafanha_high_pred_map
-
-ggsave("Figures/Gaf_High_Pred.png",Gafanha_high_pred_map , width = 712*4, height = 1120*4, units = "px")
-
-################# PLOT AND SAVING ###########
-plot_GafHigh<-rgb_Gafanha_High+
-  Gafanha_high_pred_map
-
-ggsave("Figures/Maps Pred/FigX-Gaf_High_Pred.png",plot_GafHigh , width = 2105*4, height = 1363*4, units = "px")
-
-#########
-
-```
-
-```{r Figure 5 Gaf High plot}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanha, Portugal.
-The total extent of this flight was about 1 km² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The yellow polygon shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
-The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
-#| label: fig-GafHigh
-#| fig-width: 10
-#| fig-height: 8
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")
-
-```
-
-Amoung the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
-This site was dominated by seagrass and the red macroalgae *Gracilaria vermicullophyla*.
-The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
-As shown in the zoom (@fig-Boat), the edges of the meadow were colonised by green macroalgae
-
-```{r Figure 6 Boat}
-#| cache: true
-#| echo: false
-#| warning: false
-#| eval: false
-
-imglist<-
-  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         str_detect(path, "High") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          str_detect(path, "AveiroHigh") ~ "Gafanha",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "Preds") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
-                         str_detect(path, "NewPreds") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         col = case_when(str_detect(path, "colored") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".aux.xml"))
-########### PREVIEW #############
-filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
-mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
-  read_sf()
-
-Flight_aveiro<-data.frame(
-  Name=c(
-  "Marinha Lanzarote"
-  ) ,
-  Description = c(
-                  "120m Flight"),
-  Long=c( 
-         -8.690677) ,
-  Lat=c(
-        40.665120) 
-  )  %>% 
-  st_as_sf(coords=c("Long","Lat") )  %>% 
-  st_set_crs("EPSG:4326")  %>% 
-  st_transform(crs(mask_aveiro))  %>% 
-  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
-                lat = sf::st_coordinates(.) [,2]) %>% 
-  sf::st_set_geometry(NULL)
-
-p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
-
-p1<-ggplot() +
-  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#BDBDBD"))+
-  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
-  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,show.legend = F,colour="grey30")+
-      coord_sf(xlim=c(519749,535233) ,
-          ylim=c(4493310,4508794) )+
-  ggforce::geom_mark_ellipse(data=Flight_aveiro,
-                 aes(x=lon,
-                     y=lat,
-                     label = Name,
-                     group = Name),
-                     # description=Description),
-                 size=0.3,
-                 fill = "goldenrod",
-                 con.colour = "goldenrod4",
-                 show.legend=F,
-                 label.fontsize = 10,
-                 label.hjust = 0.5,
-                 con.size = 2,
-                 alpha=0.8,
-  expand = unit(2, "mm") , 
-  radius = unit(2, "mm") ,
-  label.fill = "grey90",
-  label.buffer = unit(5, "mm")) +
-    # theme_void()+
-  theme_Bede_Map()+
-  labs(x="Longitude",
-       y="Latitude")+
-  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
-  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
-  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
-        legend.position = "none",
-        axis.title = element_blank(),
-        axis.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 20))+
-  theme_void()
-##### ZOOM and masking #####
-
-Boat_rgb<-imglist %>% 
-  filter(str_detect(path,"Boat_high_RGB_merged.tif")) %>% 
-  pull(path) %>% 
-  rast()
-names(Boat_rgb)<-c("B1","B3","B5")
-values(Boat_rgb)[values(Boat_rgb) == 0] = NA
-
-mask_boat<-"Data/shp/Aveiro" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "boat")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-background_Boat<-"Data/shp/Aveiro" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "background_Boat")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-zoom_boat_high_sf<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-zoom_boat_high_sf_2<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_2_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-rgb_Boat_zoomed<-Boat_rgb %>% 
-  crop(zoom_boat_high_sf)
-
-rgb_Boat_zoomed_2<-Boat_rgb %>% 
-  crop(zoom_boat_high_sf_2)
-
-Boat_rgb_mask<-Boat_rgb %>% 
-  mask(mask_boat, inverse = T)
-
-rgb_Boat_zoomed_map<- ggplot()+
-  geom_spatraster_rgb(data = rgb_Boat_zoomed,
-                      r = 3,
-                      g = 2,
-                      b = 1,
-                      max_col_value = 4000)+
-  geom_sf(data = zoom_boat_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
-
-  theme_void()
-
-rgb_Boat_zoomed_map_2
-ggplot()+
-  geom_spatraster_rgb(data = rgb_Boat_zoomed_2,
-                      r = 3,
-                      g = 2,
-                      b = 1,
-                      interpolate = F,
-                      max_col_value = 4000)+
-  geom_sf(data = zoom_boat_high_sf_2, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
-
-  theme_void()
-
-####### RGB ############
-
-RGB_Boat_map<-
-ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_Boat,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Boat,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
-  tidyterra::geom_spatraster_rgb(data = Boat_rgb_mask,
-                      r = 3,
-                      g = 2,
-                      b = 1,
-                      # maxcell = 5000,
-                      maxcell = 500832*8,
-                      max_col_value = 5000)+
-  geom_sf(data = zoom_boat_high_sf,
-          fill = "transparent",
-          colour = "black", 
-          linewidth = 1)+
-  geom_sf(data = zoom_boat_high_sf_2,
-          fill = "transparent",
-          colour = "black", 
-          linewidth = 1)+
-  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map),
-                    xmin = -8.6975,
-                    xmax = -8.69,
-                    ymin = 40.6666,
-                    ymax = 40.6711) +
-  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map_2),
-                    xmin = -8.6975+0.007,
-                    xmax = -8.69+0.007,
-                    ymin = 40.6666,
-                    ymax = 40.6711) +
-  annotation_custom(ggplotGrob(p1),
-                    xmin = -8.6795,
-                    xmax = -8.6736,
-                    ymin = 40.6585,
-                    ymax = 40.6625) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
-                              y=c(40.66244282,40.66673,40.66244282,40.66673),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", 
-            linewidth = 1)+
-    geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
-                              y=c(40.6652874,40.66675,40.6652874,40.66673),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", 
-            linewidth = 1)+
-  ggspatial::annotation_scale(location = "bl",
-                              text_cex=2)+
-  scale_x_continuous(limits = c(-8.6965,-8.675),
-                     breaks =  -8.685)+
-  scale_y_continuous(limits = c(40.659,40.6704),
-                     breaks =  40.664)+
-  theme_Bede_Map()+
-  theme(axis.title = element_blank(),
-        # axis.text.x = element_text(size = 20, angle = 20 , hjust = 1),
-        axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 20))+
-   coord_sf(crs = 4326)
-
-####### Pred ######## 
-Boat1_pred<-imglist %>% 
-  filter(str_detect(path,"AveiroBoat1_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
-  pull(path) %>% 
-  rast()
-names(Boat1_pred)<-"layer"
-
-Boat2_pred<-imglist %>% 
-  filter(str_detect(path,"AveiroBoat2_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
-  pull(path) %>% 
-  rast()
-names(Boat2_pred)<-"layer"
-
-values(Boat1_pred)[values(Boat1_pred) == 0] = NA
-values(Boat2_pred)[values(Boat2_pred) == 0] = NA
-
-B1_overextent<-ext(Boat1_pred)
-B1_overextent[2]<-ext(Boat2_pred)[2]
-B1_overextent[4]<-ext(Boat2_pred)[4]
-B1_overextent <- rast(B1_overextent)
-res(B1_overextent)<-res(Boat1_pred)
-# terra::writeRaster(B1$B1,"B1.tif")
-# terra::writeRaster(B2$B2,"B2.tif")
-
-B2_resampled <- terra::resample(Boat2_pred,B1_overextent, method = "near",threads = T)
-# terra::writeRaster(B2_resampled$B1,"B2_resampled.tif", overwrite = T)
-
-Boat_pred<-merge(Boat1_pred,B2_resampled)
-
-Boat_pred_aggregate<-terra::aggregate(Boat_pred,fact = 6, fun ="modal")
-
-masked_pred<-Boat_pred_aggregate %>% 
-  mask(mask_boat,inverse=TRUE)%>% 
-  as.factor()
-
-Boat_pred_zoom<-Boat1_pred %>% 
-  crop(zoom_boat_high_sf) %>% 
-  as.factor()
-
-Boat_pred_zoom_2<-Boat2_pred %>% 
-  crop(zoom_boat_high_sf_2) %>% 
-  as.factor()
-
-Boat_Pred_zoomed_map<- ggplot()+
-  tidyterra::geom_spatraster(data = Boat_pred_zoom, 
-                             mapping = aes(fill = layer), 
-                             show.legend = F,
-                             maxcell = 5010420)+
-  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23"),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorphyceae",
-                               "Magnoliopsida"))+
-  geom_sf(data = zoom_boat_high_sf, 
-          fill = "transparent", 
-          linetype = "dashed",
-          colour = "black", 
-          linewidth = 1)+
-  theme_void()
-
-Boat_Pred_zoomed_map_2<- ggplot()+
-  tidyterra::geom_spatraster(data = Boat_pred_zoom_2, 
-                             mapping = aes(fill = layer), 
-                             show.legend = F,
-                             maxcell = 5010420)+
-  scale_fill_manual(values=c("#70543e","#389318","#873e23","#b3002d"),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae"))+
-  geom_sf(data = zoom_boat_high_sf_2, 
-          fill = "transparent", 
-          linetype = "dashed",
-          colour = "black", 
-          linewidth = 1)+
-  theme_void()
-
-Boat_pred_map<-ggplot()+
-  geom_sf(data = background_Boat, 
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Boat,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
-    scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  ggnewscale::new_scale("fill")+
-  tidyterra::geom_spatraster(data = masked_pred, 
-                             mapping = aes(fill = layer),
-                             # show.legend = F,
-                             maxcell = 5010420,
-                             )+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorophyceae",
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-  ggnewscale::new_scale("fill")+
-  geom_sf(data = zoom_boat_high_sf, 
-               fill = "transparent", 
-               colour = "black",
-               linetype = "dashed", 
-               linewidth = 1)+
-  geom_sf(data = zoom_boat_high_sf_2, 
-               fill = "transparent", 
-               colour = "black",
-               linetype = "dashed", 
-               linewidth = 1)+
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
-                              y=c(40.66244282,40.66673,40.66244282,40.66673),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", 
-            linewidth = 1)+
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
-                              y=c(40.6652874,40.66675,40.6652874,40.66673),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", 
-            linewidth = 1)+
-  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map),
-                    xmin = -8.6975,
-                    xmax = -8.69,
-                    ymin = 40.6666,
-                    ymax = 40.6711) +
-  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map_2),
-                    xmin = -8.6975+0.007,
-                    xmax = -8.69+0.007,
-                    ymin = 40.6666,
-                    ymax = 40.6711) +
-  coord_sf(crs = 4326)+
-  theme_Bede_Map()+
-   theme(
-     # axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
-     axis.text.x = element_blank(),
-         axis.title = element_blank(),
-        axis.text.y = element_text(size = 20),
-         legend.background = element_blank(),
-         legend.position = c(0.98,0.38),
-         legend.text = element_text(size = 18),
-         legend.key.size = unit(0.8,"cm"))+
-  scale_x_continuous(limits = c(-8.6965,-8.675),
-                     breaks =  -8.685)+
-  scale_y_continuous(limits = c(40.659,40.6704),
-                     breaks =  40.664)
-################# PLOT AND SAVING ###########
-plot_Boat<-RGB_Boat_map/
-  Boat_pred_map
-
-ggsave("Figures/Maps Pred/FigX-Boat_Pred.png",plot_Boat , width = 1000*4, height = 1120*4, units = "px")
-
-```
-
-```{r Figure 6 Boat plot}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
-The total extent of this flight was about 1.5 km² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-Each cover an area equivalent to a 10 m Sentinel-2 pixel size.
-#| label: fig-Boat
-#| fig-width: 10
-#| fig-height: 4
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png")
-
-```
-
-The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike, which crossed the northern part of the site from west to east.
-Alongside this dike, brown algae for the order Fucales (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
-
-```{r Figure 7 North Dike}
-#| cache: true
-#| echo: false
-#| warning: false
-#| eval: false
-
-imglist<-
-  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
-  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
-                            TRUE ~ "Output"),
-         alt = case_when(str_detect(path, "high") ~ "high",
-                         str_detect(path, "High") ~ "high",
-                         TRUE ~ "low"),
-         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
-                          str_detect(path, "AveiroHigh") ~ "Gafanha",
-                          TRUE ~ "Duer"),
-         type = case_when(str_detect(path, "pred") ~ "Pred",
-                          str_detect(path, "Preds") ~ "Pred",
-                          str_detect(path, "NDVI") ~ "NDVI",
-                          TRUE ~ "ortho"),
-         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
-                         str_detect(path, "NewPreds") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         col = case_when(str_detect(path, "colored") ~ "TRUE",
-                          TRUE ~ "FALSE"),
-         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
-                          str_detect(path, "corrected.tif") ~ "lm_all",
-                          TRUE ~ "NA")) %>% 
-  dplyr::filter(alt != "NA",
-                !str_detect(path,".aux.xml"))
-
-##### Preview #####
-
-filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
-mask_BB <- filelist[str_detect(filelist,"mask_land_intertidal_BB")] %>% 
-  read_sf()
-
-Flight_BB<-data.frame(
-  Name=c(
-  "L'Epine"
-  ) ,
-  Description = c(
-                  "120m Flight"),
-  Long=c(
-         -2.228239) ,
-  Lat=c( 
-        46.989515) 
-  )  %>% 
-  st_as_sf(coords=c("Long","Lat") )  %>% 
-  st_set_crs("EPSG:4326")  %>% 
-  st_transform(crs(mask_BB))  %>% 
-  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
-                lat = sf::st_coordinates(.) [,2]) %>% 
-  sf::st_set_geometry(NULL)
-
-p1 <- ggplot() +
-  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
-                    values = c("#7DC27D", "#BDBDBD"))+
-  geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
-      coord_sf(xlim=c(550609,579539) ,
-          ylim=c(5189447,5218377) )+
-  ggforce::geom_mark_ellipse(data=Flight_BB,
-                 aes(x=lon,
-                     y=lat,
-                     label = Name,
-                     group = Name),
-                     # description=Description),
-                 size=0.3,
-                 fill = "goldenrod",
-                 con.colour = "goldenrod4",
-                 show.legend=F,
-                 con.size = 2,
-                 label.fontsize = 10,
-                 label.hjust = 0.5,
-                 alpha=0.8,
-  expand = unit(2, "mm") , 
-  radius = unit(2, "mm") ,
-  label.fill = "grey90",
-  label.buffer = unit(5, "mm")) +
-  # theme_Bede_Map()+
-  labs(x="Longitude",
-       y="Latitude")+
-  # geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
-  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
-        legend.position = c(0.95,0.2),
-        legend.key.size =  unit(1, "cm"),
-        legend.text = element_text(size = 20),
-        legend.title=element_blank(),
-        legend.background = element_rect(linewidth = 0.5, 
-                                         fill = "white",
-                                         linetype="solid", 
-                                  colour ="black"),
-        # panel.background = element_rect(fill = "#FFFFFF90"),
-        axis.title = element_blank(),
-        axis.text.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.ticks = element_blank())+
-  theme_void()
-
-##### RGB ######
-
-Dike_rgb<-imglist %>% 
-  filter(str_detect(path,"NorthDike_high_multi_4326_colored.tif")) %>% 
-  pull(path) %>% 
-  rast()
-names(Dike_rgb)<-c("B1","B3","B5","alpha")
-values(Dike_rgb)[values(Dike_rgb$alpha) == 0] = NA
-
-mask_Dike<-"Data/shp/Bourgneuf" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "mask_NorthDike")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-background_Dike<-"Data/shp/Bourgneuf" %>% 
-  list.files(".shp", full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "background")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-zoom_Dike_high_sf<-"Data/shp" %>% 
-  list.files(".shp",recursive = T,full.names = T) %>% 
-  as.data.frame() %>% 
-  rename(path = ".") %>% 
-  dplyr::filter(str_detect(path,"zoom_extent_map_Dike_comparison")) %>% 
-  pull(path) %>% 
-  read_sf()
-
-Dike_rgb_masked<-Dike_rgb %>% 
-  crop(mask_Dike) %>%
-  mask(mask_Dike)
-
-zoom_rgb_dike<-Dike_rgb_masked %>% 
-  crop(zoom_Dike_high_sf)
-
-zoom_rgb_dike_map<-ggplot()+
-  geom_spatraster_rgb(data = zoom_rgb_dike,
-                      r = 3,
-                      g = 2,
-                      b = 1)+
-  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
-  coord_sf(crs = 32630)+
-  theme_void()
-
-RGB_Dike_map <- ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_Dike,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Dike,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
-  tidyterra::geom_spatraster_rgb(data = Dike_rgb_masked,
-                      r = 3,
-                      g = 2,
-                      b = 1,
-                      # maxcell = 500,
-                      maxcell = 500832*8
-                      )+
-  geom_sf(data = zoom_Dike_high_sf, 
-          fill = "transparent", 
-          linetype = "dashed",
-          colour = "black", 
-          linewidth = 1)+
-  annotation_custom(ggplotGrob(zoom_rgb_dike_map), 
-                    xmin = -2.226, 
-                    ymin = 46.9888,
-                    ymax = 46.9893) +
-  annotation_custom(ggplotGrob(p1),
-                    xmin = -2.226,
-                    ymin = 46.9875) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
-                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  ggspatial::annotation_scale(location = "tl",text_cex=2)+
-  scale_x_continuous(limits = c(-2.2293,-2.2253),
-                     breaks =  -2.228)+
-  scale_y_continuous(limits = c(46.9882,46.98935),
-                     breaks =  46.9890)+
-  theme_Bede_Map()+
-  theme(
-    # axis.text.x =element_text(size = 20, angle = 20, hjust = 1),
-    axis.text.x =element_blank(),
-        axis.title = element_blank(),
-        axis.text.y = element_text(size = 20))+
-   coord_sf(crs = 4326)
-
-##### Pred ######
-
-Dike_Pred<-imglist %>% 
-  filter(str_detect(path,"Noirmoutier_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7_4326.tif")) %>% 
-  pull(path) %>% 
-  rast()
-names(Dike_Pred)<-c("layer")
-values(Dike_Pred)[values(Dike_Pred) == 0] = NA
-
-Dike_Pred_masked<-Dike_Pred %>% 
-  crop(mask_Dike) %>% 
-  mask(mask_Dike) %>% 
-  as.factor()
-
-zoom_Pred_dike<-Dike_Pred_masked %>% 
-  crop(zoom_Dike_high_sf)
-
-zoom_Pred_dike_map<-ggplot()+
-  tidyterra::geom_spatraster(data = zoom_Pred_dike, mapping = aes(fill = layer), show.legend = F)+
-  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23","#42c9bc"),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorphyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Water"))+
-  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
-  theme_void()
-
-Dike_pred_map<-ggplot()+
-  geom_sf(data = background_Dike, 
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_Dike,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-    scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  ggnewscale::new_scale("fill")+
-  tidyterra::geom_spatraster(data = Dike_Pred_masked, 
-                             mapping = aes(fill = layer),
-                             maxcell = 5010420,
-                             )+
-  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
-                    na.value = NA,
-                    name = "",
-                    labels = c("Sediment",
-                               "Chlorophyceae",
-                               "Bacillariophyceae",
-                               "Magnoliopsida",
-                               "Phaeophyceae",
-                               "Rhodophyceae",
-                               "Water"))+
-  ggnewscale::new_scale("fill")+
-  geom_sf(data = zoom_Dike_high_sf, 
-          fill = "transparent", 
-          colour = "black",
-          linetype = "dashed", 
-          linewidth = 1)+
-  annotation_custom(ggplotGrob(zoom_Pred_dike_map), 
-                    xmin = -2.226, 
-                    ymin = 46.9888,
-                    ymax = 46.9893) +
-  geom_path(aes(x,y,group=grp),
-            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
-                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
-                              grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
-  # annotation_custom(ggplotGrob(Boat_Pred_zoomed_map), xmin = -8.697, xmax = -8.692, ymin = 40.667,ymax = 40.6705) +
-  coord_sf(crs = 4326)+
-  theme_Bede_Map()+
-   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
-         axis.title = element_blank(),
-        axis.text.y = element_text(size = 20),
-         legend.background = element_blank(),
-         legend.position = c(1,0.50),
-         legend.text = element_text(size = 18),
-         legend.key.size = unit(0.8,"cm"))+
-  scale_x_continuous(limits = c(-2.2293,-2.2253),
-                     breaks =  -2.228)+
-  scale_y_continuous(limits = c(46.9882,46.98935),
-                     breaks =  46.9890)
-
-################# PLOT AND SAVING ###########
-
-plot_Dike<-RGB_Dike_map/
-  Dike_pred_map
-
-ggsave("Figures/Maps Pred/FigX-Dike_Pred.png",plot_Dike , width = 1200*4, height = 900*4, units = "px")
-
-```
-
-```{r Figure 7 North Dike plot}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the Northern part of Noirmoutier Island, France.
-The total extent of this flight was about 28 000 m² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green) and land area (Light Grey).
-The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
-#| label: fig-Dike
-#| fig-width: 10
-#| fig-height: 7
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png")
-```
-
-## Validation
-
-### Reflectance comparison between the two different altitudes
-
-```{r Reflectance_Validation 2 height}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
-#   rast()
-# 
-# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
-# #   rast() 
-# 
-# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
-#   rast() %>% 
-#   resample(high_alt, method = "med")
-# 
-# 
-# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
-#   rast() 
-# 
-# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
-#   vect()
-#   
-# high_alt_masked<-crop(high_alt,mask)
-# high_alt_masked<-mask(high_alt_masked,mask)
-# 
-# low_alt_masked<-crop(low_alt,mask)
-# low_alt_masked<-mask(low_alt_masked,mask)
-# 
-# low_alt_pred_masked<-crop(low_alt_pred,mask)
-# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
-# 
-# 
-# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
-#   as.data.frame()
-# 
-# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
-#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
-#               "pred")
-# 
-# stk_long<-stk %>% 
-#   mutate(px_ID = c(1:nrow(stk))) %>% 
-#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
-#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
-#                          str_detect(Bands, "high") ~ "High",
-#                          TRUE ~ "NA"),
-#          Bands = gsub("_high","",Bands),
-#          Bands = gsub("_low","",Bands))
-# 
-# 
-# stk_summarized<-stk_long %>% 
-#   # group_by(px_ID,alt) %>% 
-#   # reframe(Value = mean(Value),
-#   #         pred = unique(pred)) %>% 
-#   pivot_wider(names_from = "alt", values_from = "Value")
-# 
-# df<-stk_summarized %>% 
-#   ungroup() %>% 
-#   group_by(Bands) %>% 
-#   filter(Low<10000,
-#          High < 10000,
-#          Low < quantile(Low,probs = 0.99),
-#          High < quantile(High,probs = 0.99),
-#          Low > quantile(Low,probs = 0.01),
-#          High > quantile(High,probs = 0.01),
-#          !pred %in% c(7,9,3,10)) %>%
-#   ungroup()
-
-RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
-  mutate(Low = Low /10000,
-         High = High/10000)
-
-RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
-lm_raw <- lm(RAW$High ~ RAW$Low)
-
-STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
-
-RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
-lm_STD <- lm(STD$High ~ STD$Low)
-
-plot_RAW <- RAW %>%  
-  ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(0,6000),
-                               breaks = c(0,2000,4000,6000),
-                               labels = c("1","2000","4000","6000"))+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,0.6))+
-  xlim(c(0.05,0.6))+
-  ylab("Reflectance of the 120m flight")+
-  xlab("Reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-plot_STD <- STD %>%  
-    ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(1,2000),
-                               breaks = c(1,1000,2000),
-                               labels = c("1","1000","2000"))+
-  # scale_color_gradient(na.value = 1)+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,1))+
-  xlim(c(0.05,1))+
-  ylab("Standardised reflectance of the 120m flight")+
-  xlab("Standardised reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
-ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
-
-```
-
-```{r ref_compare_building}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-RAW <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-STD <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-plot <- RAW+STD
-
-ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
-```
-
-In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
-The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels to train the neural network model.
-This methodology implies a consistency between the reflectance measured from both altitudes.
-@fig-CompareRef depicts the relationship between reflectance from a low and a high-altitude flights conducted over the same area.
-
-```{r RefComapare}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
-The black dashed line represents a 1 to 1 relationship.
-Left (A) plots raw data and right (B) plots standardized data (@eq-std).
-#| label: fig-CompareRef
-#| fig-width: 10
-#| fig-height: 5
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
-
-```
-
-Overall there was a good agreement between the two altitudes.
-There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
-Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
-This different is not present anymore when reflectance values of both flights have been standardized (@eq-std ; @fig-CompareRef B).
-
-### Neural network classification validation
 
@@
 
-A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
-The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
+The workflow of this study revolves around two distinct flight heights (12 m and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
+This comparison was conducted at sites where low and high altitude flights overlapped.
+The low altitude flights were resampled to the same spatial resolution and grid as the high flights using a median resampling method.
+Reflectance values were then extracted, and a scatterplot was generated.
+Subsequently, the slope of the linear model and the coefficient of determination (R²) were computed.
+
+The model was applied to all flights at both 12 and 120 m of altitude.
+In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
+These images were used to construct a validation dataset indicating the presence or absence of each class.
+Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
+The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
+All validation matrices were then aggregated to create an overall matrix .
+
+## Variable Importance
+
+Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
+Out of the twenty one predictors utilized in this study, Variable Importance was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
+This is achieved by repeatedly predicting the same dataset while randomly shuffling one predictor at a time.
+The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables.
+The greater the difference between these two benchmark values, the more important the variable is for the model [@WEI2015399].
+
+## Impact of the percent cover on the prediction
+
+The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm).
+The predictions made on the high-resolution flight can be used to estimate the percent cover of each vegetation class for every pixel of the lower resolution flight.
+Consequently, for each pixel of the high-altitude flights, percent covers of each vegetation class were obtained, and a kernel density plot was generated.
+This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
+
+# Results
+
+## Classification
+
+Each drone flight was used to produce a prediction map, as well as a probability map that indicates the model derived likelihood of the selected class for every pixel.
+The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
+Among the five vegetation classes on which the model was trained, four were present on this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass meadow.
+There was also Bacillariophyceae forming biofilms on parts of sediment surface.
+Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
+Regardless of color, Magnoliopsida pixels were accurately predicted by the model.
+
+```{r Figure 4 Gaf Low}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
+  list.files(pattern = ".shp", recursive = T, full.names = T) %>%
+  read_sf() %>%
+  mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
+                        name == "ZOS" ~ 2,
+                        name == "BL" ~ 3,
+                        name == "SED" ~ 4,
+                        name == "GRE" ~ 5,
+                        name == "RED" ~ 6,
+                        name == "Xanthophyceae" ~ 7)) %>% 
+  as("Spatial") %>% 
+  vect()
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
+  pull(path) %>% 
+  read_sf()
+###### Preview ###########
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Gafanha"
+  ) ,
+  Description = c("12m and 120m Flights"),
+  Long=c(-8.742485) ,
+  Lat=c(40.597599) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 18,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+######### RGB #########
+ Gafanha_low_ortho<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() 
+ names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
+
+ values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
+
+ Gafanha_low_ortho_zoomed<-Gafanha_low_ortho %>% 
+   crop(zoom_extent)
+
+ map_extent_full<- st_as_sf(as.polygons(ext(Gafanha_low_ortho)))
+ sf::st_crs(map_extent_full)<-st_crs(Gafanha_low_ortho)
+
+  map_extent_zommed<- st_as_sf(as.polygons(ext(Gafanha_low_ortho_zoomed)))
+ sf::st_crs(map_extent_zommed)<-st_crs(Gafanha_low_ortho_zoomed)
+
+ rgb_Gafanha_low_zoomed<-ggplot()+
+   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed, 
+                                  r = 3,
+                                  g = 2,
+                                  b = 1)+
+   theme_Bede_Map()+
+   geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+   coord_sf(crs = 4326)+
+     theme_void()
+
+ scale_labels<-data.frame(x = c(-8.74368, -8.743565,-8.74342),
+                          y = c(rep(40.59792,3)),
+                          text = c("0","10","20 m"))
+
+  rgb_Gafanha_low<- ggplot()+
+  scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="grey30")+
+   tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
+         r = 1,
+         g = 2,
+         b = 3,
+         maxcell = 4010533
+         )+
+    ggspatial::annotation_scale(location = "tl",
+                                text_cex=2)+
+      annotation_custom(ggplotGrob(p1),
+                        xmin = -8.7430,
+                        xmax = -8.742702,
+                        ymin = 40.5970515, 
+                        ymax = 40.5974) +
+   theme_Bede_Map()+
+   geom_sf(data = zoom_extent, 
+           fill = "transparent",
+           colour = "black",
+           linetype = "dashed", 
+           linewidth = 1)+
+   coord_sf(crs = 4326)+
+  annotation_custom(ggplotGrob(rgb_Gafanha_low_zoomed),
+                    xmin = -8.7430,
+                    xmax=-8.7427,
+                    ymin = 40.5977) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
+                              y=c(40.5976275,40.5979,40.5975373,40.59771),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  theme(axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+        axis.text.x = element_text(size = 20, angle = 20, hjust = 1))+
+    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
+    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
+
+ggsave("Figures/Gaf_Low_RGB.png",rgb_Gafanha_low , width = 1920*4, height = 1129*4, units = "px")
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+####### Zoomed map ########
+
+Gafanha_low_pred_zoomed<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "low",
+       type == "Pred",
+       resampled == "FALSE",
+       folder == "Input",
+       new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred_zoomed)<-"layer"
+
+Gafanha_low_pred_zoomed<-Gafanha_low_pred_zoomed %>% 
+  crop(zoom_extent)
+Gafanha_low_pred_zoomed<-as.factor(Gafanha_low_pred_zoomed)
+
+Gafanha_low_pred_map_zoomed<-ggplot()+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer))+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  coord_sf(crs = 4326)+
+  scale_fill_manual(values=c("#70543e", "#b3ff1a","#70543e", "#DAA520", "#389318","#873e23","#b3002d", NA, "#42c9bc"), na.value = NA)+
+  theme_void()+
+  # coord_equal()+
+  theme(axis.text.x = element_blank(),
+      axis.text.y = element_blank(),
+      axis.title = element_blank())+
+  theme(legend.position = "none")
+ # Gafanha_low_pred_map_zoomed
+
+####  Overall map
+Gafanha_low_pred<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "low",
+       type == "Pred",
+       # resampled == "TRUE",
+       new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred)<-"layer"
+
+values(Gafanha_low_pred)[values(Gafanha_low_pred) == 0] = NA
+
+Gafanha_low_pred<-Gafanha_low_pred %>% 
+  as.factor()
+
+####### Pred ######
+
+Gafanha_low_pred_map <-
+  ggplot()+
+  scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="grey30")+
+  # geom_sf(data = background_GafHigh,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=1,
+  #         colour="white")+
+   ggnewscale::new_scale("fill")+
+    tidyterra::geom_spatraster(data = Gafanha_low_pred, 
+                               mapping = aes(fill = layer),
+                               maxcell = 500832*8)+
+  geom_sf(data = zoom_extent, 
+          fill = "transparent", 
+          colour = "black",
+          linetype = "dashed", 
+          linewidth = 1)+
+  coord_sf(crs = 4326)+
+  annotation_custom(ggplotGrob(Gafanha_low_pred_map_zoomed), 
+                    xmin = -8.7430,
+                    xmax=-8.7427, 
+                    ymin = 40.5977) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.7432439,-8.743,-8.7432439,-8.743),
+                              y=c(40.5976275,40.5979,40.5975373,40.59771),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  theme_Bede_Map()+
+  # coord_equal()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         # axis.text.y = element_text(size = 20),
+         axis.text.y = element_blank(),
+         axis.title = element_blank(),
+         legend.background = element_blank(),
+         legend.position = c(0.98,0.3),
+         legend.text = element_text(size = 20),
+         legend.key.size = unit(1,"cm"))+
+    scale_x_continuous(limits = c(-8.7437, -8.74275), breaks = -8.743)+
+    scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
+
+ggsave("Figures/Gaf_Low_Pred.png",Gafanha_low_pred_map , width = 1920*4, height = 1129*4, units = "px")
+
+################# PLOT AND SAVING ###########
+
+plot_Gaf_Low<-rgb_Gafanha_low+
+  Gafanha_low_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Gaf_Low_Pred.png",plot_Gaf_Low , width = 1920*4, height = 1009*4, units = "px")
+```
+
+```{r Figure 4 Gaf Low plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanha, Portugal.
+The total extent of this flight was 3000m² with a resolution of 8 mm per pixel.
+Background colors indicate intertidal area (Light Green) and land area (Light Grey).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-GafLow
+#| fig-width: 10
+#| fig-height: 8
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png")
+
+```
+
+```{r Figure 4 V2}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+imglist<-
+  data.frame("Data",
+             path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path,"AveiroHigh")~"Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+########## ZOOM #############
+
+zoom_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+mask_low<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"mask_Gafanha_low")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Gafanha_low_ortho_zoomed<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() %>% 
+  crop(zoom_extent)
+
+names(Gafanha_low_ortho_zoomed)<-c("B1", "B3", "B5","alpha")
+
+ Gafanha_low_pred_zoomed<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "Pred",
+         # resampled == "TRUE",
+         new == "TRUE") %>% 
+  pull(path) %>% 
+  rast() %>% 
+  crop(zoom_extent) %>% 
+  mask(mask_low, inverse = T) %>% 
+   as.factor()
+
+names(Gafanha_low_pred_zoomed)<-"layer"
+
+zoomed_low_map<-ggplot()+
+  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho_zoomed,
+                                 r = 1,
+                                 g = 2,
+                                 b = 3)+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer), show.legend = F)+
+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
+                    na.value = NA,
+                    name = "", 
+                    labels = c("Sediment", 
+                               "Chlorophyceae", 
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 2)+
+  theme(legend.position = "none")+
+  theme_void()
+
+#############
+
+ Gafanha_low_ortho<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "ortho",
+         resampled == "TRUE",
+         col == "TRUE") %>%
+  pull(path) %>% 
+  rast() 
+ names(Gafanha_low_ortho)<-c("B1", "B3", "B5","alpha")
+values(Gafanha_low_ortho)[values(Gafanha_low_ortho$alpha) == 0] = NA
+
+ Gafanha_low_pred<-imglist %>% 
+  filter(site == "Gafanha",
+         alt == "low",
+         type == "Pred",
+         # resampled == "TRUE",
+         new == "TRUE") %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_low_pred)<-"layer"
+
+Gafanha_low_pred_masked<-Gafanha_low_pred %>% 
+  # crop(mask_low) %>% 
+  mask(mask_low, inverse = T)
+
+values(Gafanha_low_pred_masked)[values(Gafanha_low_pred_masked) == 0] = NA
+
+Gafanha_low_pred_masked<-Gafanha_low_pred_masked %>% 
+  as.factor()
+
+rgb_Gafanha_low <- ggplot()+
+  tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
+                                 r = 1,
+                                 g = 2,
+                                 b = 3)+
+  tidyterra::geom_spatraster(data = Gafanha_low_pred_masked, mapping = aes(fill = layer))+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA), 
+                    na.value = NA,
+                    name = "", 
+                    labels = c("Sediment", 
+                               "Chlorophyceae", 
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggspatial::annotation_scale(location = "bl",text_cex=2)+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+
+  geom_segment(aes(x = -8.7434247325, y=40.5977530006, xend = -8.7430558162, yend = 40.5972152706), linetype ="dashed" ,linewidth=2)+
+  annotation_custom(ggplotGrob(zoomed_low_map), xmin = -8.743725, xmax = -8.7434057328, ymin = 40.5977200450, ymax = 40.59798) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74336194,-8.74371,-8.743243794,-8.7434057328), y=c(40.59762751,40.5977400850,40.59762725,40.5977200450),grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  theme_Bede_Map()+
+  coord_sf(crs = 4326)+
+  theme(axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+        axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+        legend.position=c(0.3, 0.3))+
+  # ggtitle("a ")+
+  scale_x_continuous(breaks=seq(-8.7437, -8.7430, 0.0002))
+rgb_Gafanha_low
+
+ggsave("Figures/Gaf_Low_RGB_Pred_V2.png",rgb_Gafanha_low , width = 890*4, height = 1120*4, units = "px")
+
+```
+
+The high-altitude flight over Gafanha covered a total area of \~1 km² (@fig-GafHigh).
+A channel contouring a small island was masked in the prediction map.
+Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
+Only a few pixels were classified as Chlorophyceae at this spatial scale.
+Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remained mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
+Patches of Rhodophyceae were correctly classified.
+In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+
+```{r Figure 5 Gaf High}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+#### Preview ####
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Gafanha"
+  ) ,
+  Description = c("12m and 120m Flights"),
+  Long=c(-8.742485) ,
+  Lat=c(40.597599) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 20,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+
+#####
+
+land_mask_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "mask_Gafanha_high1")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_GafHigh<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Gafanha_high")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+GafHigh_ortho<-imglist %>% 
+  dplyr::filter(site == "Gafanha",
+                type == "ortho",
+                alt=="high",
+                col == "TRUE") %>%
+  pull(path) %>% 
+  rast()
+names(GafHigh_ortho)<-c("B1","B3", "B5", "alpha")
+
+# values(GafHigh_ortho)[values(GafHigh_ortho$B1) == 0] = NA
+
+GafHigh_ortho_masked<-GafHigh_ortho %>% 
+  mask(land_mask_GafHigh, inverse = F) %>% 
+  crop(land_mask_GafHigh)
+
+GafHigh_ortho_masked<-na.omit(GafHigh_ortho_masked, field=NA, geom=FALSE)
+
+###### RGB ########
+zoom_gaf_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Gafanha_High_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Gaflow_extent<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"GafLow_extent.shp")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+rgb_Gafanha_High_zoomed<-GafHigh_ortho_masked %>% 
+  crop(zoom_gaf_high_sf)
+
+rgb_Gafanha_High_zoomed<-
+  ggplot()+
+  tidyterra::geom_spatraster_rgb(data = rgb_Gafanha_High_zoomed,
+         r = 1,
+         g = 2,
+         b = 3)+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  theme_void()
+
+rgb_Gafanha_High <- ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_GafHigh,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+   tidyterra::geom_spatraster_rgb(data = GafHigh_ortho_masked,
+         r = 1,
+         g = 2,
+         b = 3,
+         maxcell = 5007120)+
+    ggspatial::annotation_scale(location = "bl",
+                                text_cex=2)+
+    annotation_custom(ggplotGrob(p1), 
+                      xmin = -8.744, 
+                      xmax = -8.7412,
+                      ymin = 40.5923,
+                      ymax = 40.595) +
+    geom_sf(data = zoom_gaf_high_sf,
+            fill = "transparent", 
+            colour = "black",
+            linetype = "dashed", 
+            linewidth = 1)+
+    geom_sf(data = Gaflow_extent,
+            fill = "transparent", 
+            colour = "red",
+            linetype = "dashed", 
+            linewidth = 2)+
+    geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
+                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  annotation_custom(ggplotGrob(rgb_Gafanha_High_zoomed),
+                    xmin = -8.7479, 
+                    xmax = -8.7452, 
+                    ymin = 40.5979,
+                    ymax = 40.603) +
+   theme_Bede_Map()+
+   coord_sf(crs = 4326)+
+   # xlim(c(-8.748, -8.741))+
+  # ylim(c(40.593,40.601))+
+  theme(axis.title = element_blank(),
+         axis.text.x = element_text(size = 20, angle = 20, hjust = 1),
+         axis.text.y = element_text(size = 20))+
+  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
+  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
+# rgb_Gafanha_High
+
+ggsave("Figures/Gaf_High_RGB.png",rgb_Gafanha_High , width = 712*4, height = 1120*4, units = "px")
+
+######### Pred #######
+Gafanha_high_pred<-imglist %>% 
+filter(site == "Gafanha",
+       alt == "high",
+       type == "Pred",
+       new == "TRUE",
+       !str_detect(path, "Probs")) %>% 
+  pull(path) %>% 
+  rast()
+names(Gafanha_high_pred)<-"layer"
+
+GafHigh_pred_masked<-Gafanha_high_pred %>% 
+  mask(land_mask_GafHigh, inverse = F) %>% 
+  crop(land_mask_GafHigh)
+
+GafHigh_pred_masked<-na.omit(GafHigh_pred_masked, field=NA, geom=FALSE)
+
+values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 0] = NA
+values(GafHigh_pred_masked)[values(GafHigh_pred_masked) == 3] = 1
+
+GafHigh_pred_masked<-GafHigh_pred_masked %>% 
+  as.factor()
+
+Gafanha_High_zoomed_pred<-GafHigh_pred_masked %>% 
+  crop(zoom_gaf_high_sf)
+
+Gafanha_High_zoomed_pred<-
+  ggplot()+
+   tidyterra::geom_spatraster(data = Gafanha_High_zoomed_pred, mapping = aes(fill = layer),
+                            show.legend = F,
+                             maxcell = 5007120)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  theme_void()
+
+Gafanha_high_pred_map<-ggplot()+
+  geom_sf(data = background_GafHigh, 
+          mapping = aes(fill = Type),
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_GafHigh,
+          fill = "white",
+          show.legend = F,
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+    scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = GafHigh_pred_masked, 
+                             # show.legend = F,
+                             mapping = aes(fill = layer),
+                             maxcell = 5010420)+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+       geom_sf(data = zoom_gaf_high_sf, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+    geom_sf(data = Gaflow_extent,
+            fill = "transparent", 
+            colour = "red",
+            linetype = "dashed", 
+            linewidth = 2)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.74363778,-8.74757,-8.74351982,-8.7453), 
+                              y=c(40.5983781677,40.5995,40.598377893,40.5995),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  annotation_custom(ggplotGrob(Gafanha_High_zoomed_pred), 
+                    xmin = -8.7479, 
+                    xmax = -8.7452, 
+                    ymin = 40.5979,
+                    ymax = 40.603) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         axis.title = element_blank(),
+        # axis.text.y = element_text(size = 20),
+        axis.text.y = element_blank(),
+         legend.background = element_blank(),
+         legend.position = c(0.96,0.23),
+         legend.text = element_text(size = 23),
+         legend.key.size = unit(1.2,"cm"))+
+  scale_x_continuous(limits = c(-8.747576, -8.741465),breaks =  -8.745)+
+  scale_y_continuous(limits = c(40.59297,40.60109),breaks =  40.595)
+# Gafanha_high_pred_map
+
+ggsave("Figures/Gaf_High_Pred.png",Gafanha_high_pred_map , width = 712*4, height = 1120*4, units = "px")
+
+################# PLOT AND SAVING ###########
+plot_GafHigh<-rgb_Gafanha_High+
+  Gafanha_high_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Gaf_High_Pred.png",plot_GafHigh , width = 2105*4, height = 1363*4, units = "px")
+
+#########
+
+```
+
+```{r Figure 5 Gaf High plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanha, Portugal.
+The total extent of this flight was about 1 km² with a resolution of 80 mm per pixel.
+Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+The yellow outline shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
+#| label: fig-GafHigh
+#| fig-width: 10
+#| fig-height: 8
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")
+
+```
+
+Amoung the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
+This site was dominated by seagrass and red macroalgae.
+The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
+As shown in the zoom (@fig-Boat), the edges of the meadow visually appears to be colonised by green macroalgae, which the model agreed with.
+
+```{r Figure 6 Boat}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+########### PREVIEW #############
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_aveiro <- filelist[str_detect(filelist,"mask_land_intertidal_Aveiro")] %>% 
+  read_sf()
+
+Flight_aveiro<-data.frame(
+  Name=c(
+  "Marinha Lanzarote"
+  ) ,
+  Description = c(
+                  "120m Flight"),
+  Long=c( 
+         -8.690677) ,
+  Lat=c(
+        40.665120) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_aveiro))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1_background<- read_sf("Data/shp/Aveiro/Background_p1_aveiro.shp")
+
+p1<-ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
+  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,show.legend = F,colour="grey30")+
+      coord_sf(xlim=c(519749,535233) ,
+          ylim=c(4493310,4508794) )+
+  ggforce::geom_mark_ellipse(data=Flight_aveiro,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 label.fontsize = 10,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+    # theme_void()+
+  theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
+  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = "none",
+        axis.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20))+
+  theme_void()
+##### ZOOM and masking #####
+
+Boat_rgb<-imglist %>% 
+  filter(str_detect(path,"Boat_high_RGB_merged.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat_rgb)<-c("B1","B3","B5")
+values(Boat_rgb)[values(Boat_rgb) == 0] = NA
+
+mask_boat<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "boat")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_Boat<-"Data/shp/Aveiro" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background_Boat")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_boat_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_boat_high_sf_2<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Boat_2_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+rgb_Boat_zoomed<-Boat_rgb %>% 
+  crop(zoom_boat_high_sf)
+
+rgb_Boat_zoomed_2<-Boat_rgb %>% 
+  crop(zoom_boat_high_sf_2)
+
+Boat_rgb_mask<-Boat_rgb %>% 
+  mask(mask_boat, inverse = T)
+
+rgb_Boat_zoomed_map<- ggplot()+
+  geom_spatraster_rgb(data = rgb_Boat_zoomed,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      max_col_value = 4000)+
+  geom_sf(data = zoom_boat_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+
+  theme_void()
+
+rgb_Boat_zoomed_map_2
+ggplot()+
+  geom_spatraster_rgb(data = rgb_Boat_zoomed_2,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      interpolate = F,
+                      max_col_value = 4000)+
+  geom_sf(data = zoom_boat_high_sf_2, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+
+  theme_void()
+
+####### RGB ############
+
+RGB_Boat_map<-
+ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_Boat,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Boat,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+  tidyterra::geom_spatraster_rgb(data = Boat_rgb_mask,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      # maxcell = 5000,
+                      maxcell = 500832*8,
+                      max_col_value = 5000)+
+  geom_sf(data = zoom_boat_high_sf,
+          fill = "transparent",
+          colour = "black", 
+          linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf_2,
+          fill = "transparent",
+          colour = "black", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map),
+                    xmin = -8.6975,
+                    xmax = -8.69,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(rgb_Boat_zoomed_map_2),
+                    xmin = -8.6975+0.007,
+                    xmax = -8.69+0.007,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(p1),
+                    xmin = -8.6795,
+                    xmax = -8.6736,
+                    ymin = 40.6585,
+                    ymax = 40.6625) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
+                              y=c(40.66244282,40.66673,40.66244282,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+    geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
+                              y=c(40.6652874,40.66675,40.6652874,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  ggspatial::annotation_scale(location = "bl",
+                              text_cex=2)+
+  scale_x_continuous(limits = c(-8.6965,-8.675),
+                     breaks =  -8.685)+
+  scale_y_continuous(limits = c(40.659,40.6704),
+                     breaks =  40.664)+
+  theme_Bede_Map()+
+  theme(axis.title = element_blank(),
+        # axis.text.x = element_text(size = 20, angle = 20 , hjust = 1),
+        axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 20))+
+   coord_sf(crs = 4326)
+
+####### Pred ######## 
+Boat1_pred<-imglist %>% 
+  filter(str_detect(path,"AveiroBoat1_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat1_pred)<-"layer"
+
+Boat2_pred<-imglist %>% 
+  filter(str_detect(path,"AveiroBoat2_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Boat2_pred)<-"layer"
+
+values(Boat1_pred)[values(Boat1_pred) == 0] = NA
+values(Boat2_pred)[values(Boat2_pred) == 0] = NA
+
+B1_overextent<-ext(Boat1_pred)
+B1_overextent[2]<-ext(Boat2_pred)[2]
+B1_overextent[4]<-ext(Boat2_pred)[4]
+B1_overextent <- rast(B1_overextent)
+res(B1_overextent)<-res(Boat1_pred)
+# terra::writeRaster(B1$B1,"B1.tif")
+# terra::writeRaster(B2$B2,"B2.tif")
+
+B2_resampled <- terra::resample(Boat2_pred,B1_overextent, method = "near",threads = T)
+# terra::writeRaster(B2_resampled$B1,"B2_resampled.tif", overwrite = T)
+
+Boat_pred<-merge(Boat1_pred,B2_resampled)
+
+Boat_pred_aggregate<-terra::aggregate(Boat_pred,fact = 6, fun ="modal")
+
+masked_pred<-Boat_pred_aggregate %>% 
+  mask(mask_boat,inverse=TRUE)%>% 
+  as.factor()
+
+Boat_pred_zoom<-Boat1_pred %>% 
+  crop(zoom_boat_high_sf) %>% 
+  as.factor()
+
+Boat_pred_zoom_2<-Boat2_pred %>% 
+  crop(zoom_boat_high_sf_2) %>% 
+  as.factor()
+
+Boat_Pred_zoomed_map<- ggplot()+
+  tidyterra::geom_spatraster(data = Boat_pred_zoom, 
+                             mapping = aes(fill = layer), 
+                             show.legend = F,
+                             maxcell = 5010420)+
+  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorphyceae",
+                               "Magnoliopsida"))+
+  geom_sf(data = zoom_boat_high_sf, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  theme_void()
+
+Boat_Pred_zoomed_map_2<- ggplot()+
+  tidyterra::geom_spatraster(data = Boat_pred_zoom_2, 
+                             mapping = aes(fill = layer), 
+                             show.legend = F,
+                             maxcell = 5010420)+
+  scale_fill_manual(values=c("#70543e","#389318","#873e23","#b3002d"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae"))+
+  geom_sf(data = zoom_boat_high_sf_2, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  theme_void()
+
+Boat_pred_map<-ggplot()+
+  geom_sf(data = background_Boat, 
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Boat,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+    scale_fill_manual("", 
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = masked_pred, 
+                             mapping = aes(fill = layer),
+                             # show.legend = F,
+                             maxcell = 5010420,
+                             )+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggnewscale::new_scale("fill")+
+  geom_sf(data = zoom_boat_high_sf, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf_2, 
+               fill = "transparent", 
+               colour = "black",
+               linetype = "dashed", 
+               linewidth = 1)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.69452127,-8.6965,-8.69440039,-8.69105), 
+                              y=c(40.66244282,40.66673,40.66244282,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-8.6819877,-8.69645+0.007,-8.6818696,-8.6911+0.007), 
+                              y=c(40.6652874,40.66675,40.6652874,40.66673),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", 
+            linewidth = 1)+
+  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map),
+                    xmin = -8.6975,
+                    xmax = -8.69,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  annotation_custom(ggplotGrob(Boat_Pred_zoomed_map_2),
+                    xmin = -8.6975+0.007,
+                    xmax = -8.69+0.007,
+                    ymin = 40.6666,
+                    ymax = 40.6711) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(
+     # axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+     axis.text.x = element_blank(),
+         axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+         legend.background = element_blank(),
+         legend.position = c(0.98,0.38),
+         legend.text = element_text(size = 18),
+         legend.key.size = unit(0.8,"cm"))+
+  scale_x_continuous(limits = c(-8.6965,-8.675),
+                     breaks =  -8.685)+
+  scale_y_continuous(limits = c(40.659,40.6704),
+                     breaks =  40.664)
+################# PLOT AND SAVING ###########
+plot_Boat<-RGB_Boat_map/
+  Boat_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Boat_Pred.png",plot_Boat , width = 1000*4, height = 1120*4, units = "px")
+
+```
+
+```{r Figure 6 Boat plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: RGB orthomosaic (Top) and Prediction (Bottom) of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
+The total extent of this flight was about 1.5 km² with a resolution of 80 mm per pixel.
+Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+Each cover an area equivalent to a 10 m Sentinel-2 pixel size.
+#| label: fig-Boat
+#| fig-width: 10
+#| fig-height: 4
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png")
+
+```
+
+The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike, which crossed the northern part of the site from west to east.
+Alongside this dike, Fucale brown algae (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed.
+Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
+
+```{r Figure 7 North Dike}
+#| cache: true
+#| echo: false
+#| warning: false
+#| eval: false
+
+imglist<-
+  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
+  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
+                            TRUE ~ "Output"),
+         alt = case_when(str_detect(path, "high") ~ "high",
+                         str_detect(path, "High") ~ "high",
+                         TRUE ~ "low"),
+         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
+                          str_detect(path, "AveiroHigh") ~ "Gafanha",
+                          TRUE ~ "Duer"),
+         type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Preds") ~ "Pred",
+                          str_detect(path, "NDVI") ~ "NDVI",
+                          TRUE ~ "ortho"),
+         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         new = case_when(str_detect(path, "no_Xantho") ~ "TRUE",
+                         str_detect(path, "NewPreds") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         col = case_when(str_detect(path, "colored") ~ "TRUE",
+                          TRUE ~ "FALSE"),
+         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
+                          str_detect(path, "corrected.tif") ~ "lm_all",
+                          TRUE ~ "NA")) %>% 
+  dplyr::filter(alt != "NA",
+                !str_detect(path,".aux.xml"))
+
+##### Preview #####
+
+filelist<-list.files("Data/shp/", pattern = ".shp", recursive = T,full.names = T)
+mask_BB <- filelist[str_detect(filelist,"mask_land_intertidal_BB")] %>% 
+  read_sf()
+
+Flight_BB<-data.frame(
+  Name=c(
+  "L'Epine"
+  ) ,
+  Description = c(
+                  "120m Flight"),
+  Long=c(
+         -2.228239) ,
+  Lat=c( 
+        46.989515) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform(crs(mask_BB))  %>% 
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)
+
+p1 <- ggplot() +
+  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
+                    values = c("#7DC27D", "#BDBDBD"))+
+  geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
+      coord_sf(xlim=c(550609,579539) ,
+          ylim=c(5189447,5218377) )+
+  ggforce::geom_mark_ellipse(data=Flight_BB,
+                 aes(x=lon,
+                     y=lat,
+                     label = Name,
+                     group = Name),
+                     # description=Description),
+                 size=0.3,
+                 fill = "goldenrod",
+                 con.colour = "goldenrod4",
+                 show.legend=F,
+                 con.size = 2,
+                 label.fontsize = 10,
+                 label.hjust = 0.5,
+                 alpha=0.8,
+  expand = unit(2, "mm") , 
+  radius = unit(2, "mm") ,
+  label.fill = "grey90",
+  label.buffer = unit(5, "mm")) +
+  # theme_Bede_Map()+
+  labs(x="Longitude",
+       y="Latitude")+
+  # geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
+  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
+        legend.position = c(0.95,0.2),
+        legend.key.size =  unit(1, "cm"),
+        legend.text = element_text(size = 20),
+        legend.title=element_blank(),
+        legend.background = element_rect(linewidth = 0.5, 
+                                         fill = "white",
+                                         linetype="solid", 
+                                  colour ="black"),
+        # panel.background = element_rect(fill = "#FFFFFF90"),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank())+
+  theme_void()
+
+##### RGB ######
+
+Dike_rgb<-imglist %>% 
+  filter(str_detect(path,"NorthDike_high_multi_4326_colored.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Dike_rgb)<-c("B1","B3","B5","alpha")
+values(Dike_rgb)[values(Dike_rgb$alpha) == 0] = NA
+
+mask_Dike<-"Data/shp/Bourgneuf" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "mask_NorthDike")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+background_Dike<-"Data/shp/Bourgneuf" %>% 
+  list.files(".shp", full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path, "background")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+zoom_Dike_high_sf<-"Data/shp" %>% 
+  list.files(".shp",recursive = T,full.names = T) %>% 
+  as.data.frame() %>% 
+  rename(path = ".") %>% 
+  dplyr::filter(str_detect(path,"zoom_extent_map_Dike_comparison")) %>% 
+  pull(path) %>% 
+  read_sf()
+
+Dike_rgb_masked<-Dike_rgb %>% 
+  crop(mask_Dike) %>%
+  mask(mask_Dike)
+
+zoom_rgb_dike<-Dike_rgb_masked %>% 
+  crop(zoom_Dike_high_sf)
+
+zoom_rgb_dike_map<-ggplot()+
+  geom_spatraster_rgb(data = zoom_rgb_dike,
+                      r = 3,
+                      g = 2,
+                      b = 1)+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  coord_sf(crs = 32630)+
+  theme_void()
+
+RGB_Dike_map <- ggplot()+
+  scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  geom_sf(data = background_Dike,
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="transparent")+
+  geom_sf(data = background_Dike,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="transparent")+
+  tidyterra::geom_spatraster_rgb(data = Dike_rgb_masked,
+                      r = 3,
+                      g = 2,
+                      b = 1,
+                      # maxcell = 500,
+                      maxcell = 500832*8
+                      )+
+  geom_sf(data = zoom_Dike_high_sf, 
+          fill = "transparent", 
+          linetype = "dashed",
+          colour = "black", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(zoom_rgb_dike_map), 
+                    xmin = -2.226, 
+                    ymin = 46.9888,
+                    ymax = 46.9893) +
+  annotation_custom(ggplotGrob(p1),
+                    xmin = -2.226,
+                    ymin = 46.9875) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
+                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  ggspatial::annotation_scale(location = "tl",text_cex=2)+
+  scale_x_continuous(limits = c(-2.2293,-2.2253),
+                     breaks =  -2.228)+
+  scale_y_continuous(limits = c(46.9882,46.98935),
+                     breaks =  46.9890)+
+  theme_Bede_Map()+
+  theme(
+    # axis.text.x =element_text(size = 20, angle = 20, hjust = 1),
+    axis.text.x =element_blank(),
+        axis.title = element_blank(),
+        axis.text.y = element_text(size = 20))+
+   coord_sf(crs = 4326)
+
+##### Pred ######
+
+Dike_Pred<-imglist %>% 
+  filter(str_detect(path,"Noirmoutier_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7_4326.tif")) %>% 
+  pull(path) %>% 
+  rast()
+names(Dike_Pred)<-c("layer")
+values(Dike_Pred)[values(Dike_Pred) == 0] = NA
+
+Dike_Pred_masked<-Dike_Pred %>% 
+  crop(mask_Dike) %>% 
+  mask(mask_Dike) %>% 
+  as.factor()
+
+zoom_Pred_dike<-Dike_Pred_masked %>% 
+  crop(zoom_Dike_high_sf)
+
+zoom_Pred_dike_map<-ggplot()+
+  tidyterra::geom_spatraster(data = zoom_Pred_dike, mapping = aes(fill = layer), show.legend = F)+
+  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23","#42c9bc"),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorphyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Water"))+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  theme_void()
+
+Dike_pred_map<-ggplot()+
+  geom_sf(data = background_Dike, 
+          mapping = aes(fill = Type),
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.93,
+          colour="grey30")+
+  geom_sf(data = background_Dike,
+          fill = "white",
+          show.legend = F, 
+          linewidth=0.05,
+          alpha=0.4,
+          colour="white")+
+    scale_fill_manual("",  
+                    labels = c("Intertidal area", "Land area", "water"),
+                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  ggnewscale::new_scale("fill")+
+  tidyterra::geom_spatraster(data = Dike_Pred_masked, 
+                             mapping = aes(fill = layer),
+                             maxcell = 5010420,
+                             )+
+  scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
+                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    na.value = NA,
+                    name = "",
+                    labels = c("Sediment",
+                               "Chlorophyceae",
+                               "Bacillariophyceae",
+                               "Magnoliopsida",
+                               "Phaeophyceae",
+                               "Rhodophyceae",
+                               "Water"))+
+  ggnewscale::new_scale("fill")+
+  geom_sf(data = zoom_Dike_high_sf, 
+          fill = "transparent", 
+          colour = "black",
+          linetype = "dashed", 
+          linewidth = 1)+
+  annotation_custom(ggplotGrob(zoom_Pred_dike_map), 
+                    xmin = -2.226, 
+                    ymin = 46.9888,
+                    ymax = 46.9893) +
+  geom_path(aes(x,y,group=grp),
+            data = data.frame(x = c(-2.226834,-2.225905,-2.226834,-2.225905),
+                              y=c(46.9886439,46.9892105,46.9885538,46.988805),
+                              grp=c(1,1,2,2)),
+            linetype = "dashed", linewidth = 1)+
+  # annotation_custom(ggplotGrob(Boat_Pred_zoomed_map), xmin = -8.697, xmax = -8.692, ymin = 40.667,ymax = 40.6705) +
+  coord_sf(crs = 4326)+
+  theme_Bede_Map()+
+   theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+         axis.title = element_blank(),
+        axis.text.y = element_text(size = 20),
+         legend.background = element_blank(),
+         legend.position = c(1,0.50),
+         legend.text = element_text(size = 18),
+         legend.key.size = unit(0.8,"cm"))+
+  scale_x_continuous(limits = c(-2.2293,-2.2253),
+                     breaks =  -2.228)+
+  scale_y_continuous(limits = c(46.9882,46.98935),
+                     breaks =  46.9890)
+
+################# PLOT AND SAVING ###########
+
+plot_Dike<-RGB_Dike_map/
+  Dike_pred_map
+
+ggsave("Figures/Maps Pred/FigX-Dike_Pred.png",plot_Dike , width = 1200*4, height = 900*4, units = "px")
+
+```
+
+```{r Figure 7 North Dike plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: "RGB orthomosaic (Top) and Prediction (Bottom) of L'Epine, France.
+The total extent of this flight was about 28 000 m² with a resolution of 80 mm per pixel.
+Background colors indicate intertidal area (Light Green) and land area (Light Grey).
+The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size."
+#| label: fig-Dike
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png")
+```
+
+## Validation
+
+### Reflectance comparison between the two different altitudes
+
+```{r Reflectance_Validation 2 height}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
+#   rast()
+# 
+# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+# #   rast() 
+# 
+# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
+#   rast() %>% 
+#   resample(high_alt, method = "med")
+# 
+# 
+# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
+#   rast() 
+# 
+# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
+#   vect()
+#   
+# high_alt_masked<-crop(high_alt,mask)
+# high_alt_masked<-mask(high_alt_masked,mask)
+# 
+# low_alt_masked<-crop(low_alt,mask)
+# low_alt_masked<-mask(low_alt_masked,mask)
+# 
+# low_alt_pred_masked<-crop(low_alt_pred,mask)
+# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
+# 
+# 
+# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
+#   as.data.frame()
+# 
+# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
+#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
+#               "pred")
+# 
+# stk_long<-stk %>% 
+#   mutate(px_ID = c(1:nrow(stk))) %>% 
+#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
+#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
+#                          str_detect(Bands, "high") ~ "High",
+#                          TRUE ~ "NA"),
+#          Bands = gsub("_high","",Bands),
+#          Bands = gsub("_low","",Bands))
+# 
+# 
+# stk_summarized<-stk_long %>% 
+#   # group_by(px_ID,alt) %>% 
+#   # reframe(Value = mean(Value),
+#   #         pred = unique(pred)) %>% 
+#   pivot_wider(names_from = "alt", values_from = "Value")
+# 
+# df<-stk_summarized %>% 
+#   ungroup() %>% 
+#   group_by(Bands) %>% 
+#   filter(Low<10000,
+#          High < 10000,
+#          Low < quantile(Low,probs = 0.99),
+#          High < quantile(High,probs = 0.99),
+#          Low > quantile(Low,probs = 0.01),
+#          High > quantile(High,probs = 0.01),
+#          !pred %in% c(7,9,3,10)) %>%
+#   ungroup()
+
+RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
+  mutate(Low = Low /10000,
+         High = High/10000)
+
+RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
+lm_raw <- lm(RAW$High ~ RAW$Low)
+
+STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
+
+RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
+lm_STD <- lm(STD$High ~ STD$Low)
+
+plot_RAW <- RAW %>%  
+  ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(0,6000),
+                               breaks = c(0,2000,4000,6000),
+                               labels = c("1","2000","4000","6000"))+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,0.6))+
+  xlim(c(0.05,0.6))+
+  ylab("Reflectance of the 120m flight")+
+  xlab("Reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+plot_STD <- STD %>%  
+    ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(1,2000),
+                               breaks = c(1,1000,2000),
+                               labels = c("1","1000","2000"))+
+  # scale_color_gradient(na.value = 1)+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,1))+
+  xlim(c(0.05,1))+
+  ylab("Standardised reflectance of the 120m flight")+
+  xlab("Standardised reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
+ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
+
+```
+
+```{r ref_compare_building}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+RAW <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+STD <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+plot <- RAW+STD
+
+ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
+```
+
+In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
+Overall there was a good agreement between the two altitudes (@fig-CompareRef).
+
+```{r RefComapare}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
+The black dashed line represents a 1 to 1 relationship.
+Left (A) plots raw data and right (B) plots standardized data (@eq-std).
+#| label: fig-CompareRef
+#| fig-width: 10
+#| fig-height: 5
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
+
+```
+
+There was a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
+Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
+This difference is not present when reflectance values have been standardized (@eq-std ; @fig-CompareRef B).
+
+### Neural network classification validation
+
 Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
@@
 The labels inside the matrices indicate the balanced accuracy for each class.
-The labels at the bottom of the matrices indicate the User's accuracy for each class, and those on the right indicate the Producer's Accuracy.
+The labels at the bottom of the global matrix indicate the User's accuracy for each class, and those on the right indicate the Producer's Accuracy.
 The values adjacent to the names of each site represent the proportion of total pixels from that site contributing to the overall matrix.
@@
 Overall, the classes Phaeophyceae, Magnoliopsida, Sediment and Rhodophyceae were correctly classified with a balanced accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Phaeophyceae") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Magnoliopsida") %>% pull(value),2)`, `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Sediment") %>% pull(value),2)` and `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(Class == "Rhodophyceae") %>% pull(value),2)` respectively.
-`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` was the least performing class (accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` ) mainly due to the confusion with Magnoliopsida and Sediment.
+`r Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(Class)` was the least accurate class (accuracy of `r round(Overall_metrics_ByClass %>% filter(metric == "Balanced Accuracy") %>% filter(value == min(value)) %>% pull(value),2)` ) mainly due to confusion with Magnoliopsida and Sediment.
 
@@
 #| fig-cap: Variable Importance of the Neural Network Classifier for each taxonomic class.
-The bigger the slice, the more important the variable for prediction of each class.
+The longer the slice, the more important the variable for prediction of each class.
 The right plot shows the drone raw and standardised reflectance spectra of each class.
@@
 The band at 531 nm was the only important predictor for the classifier to accurately predict Chlorophyceae.
-In fact, at this wavelength, the Chlorophyceae spectra showed the highest reflectance among of all vegetation classes.
+In fact, at this wavelength, the Chlorophyceae spectra showed the highest reflectance among all vegetation classes.
 The bands at 531 and 740 nm were the most important predictors for Phaeophyceae, corresponding to the lowest reflectance among all classes.
@@
 Percent cover of classes was retrieved using the result of the classification of the low altitude flight of Gafanha, Portugal.
-The vertical dashed line shows the 0.85 probability of the model.
-Everything on the right of this line has a probability higher then 0.85 and everything on the left of this line has a lower probability.
 #| label: fig-upscaling
@@
 
-When the percent cover of a given class was 100 %, coarser high-flight pixels are well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
-This phenomenon is likely attributed to the time gap between the two flights, allowing for microphytobenthos migration to surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
+When the percent cover of a given class was 100 %, coarser high-flight pixels were well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
+This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
 A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher percent cover (\>90 %) to be well classified.
 Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
-To predict Chlorophyceae with a confidence of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
+To predict Chlorophyceae with a model likelihood of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
 
@@
 The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management.
+The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management [@WFD2000].
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
@@
 Second, seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
-Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone, and the risk of spetral confusion was avoided thanks to the efficiency of the multispectral classifier.
-Our results confirm a recent study based on in situ radiometry, where it was demonstrated that a radiometer with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macrophytes [@Davies2023].
+Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone, and the risk of spectral confusion was avoided thanks to the efficiency of the multispectral classifier.
+Our results confirm a recent study based on *in situ* radiometry, where it was demonstrated that a radiometer with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macrophytes [@Davies2023].
 
@@
 Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can be observed, with green algae having a higher reflectance peak at 560 nm as well as a higher NIR plateau than seagrass (@fig-vegetation).
-Such differences were previously attributed to differences in pigments concentration and/or ratios [@bargain2013seasonal], cellular structure as well as in the disposition of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
+Such differences were previously attributed to differences in pigments concentration and/or ratios [@bargain2013seasonal], cellular structure as well as in the orientation of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 
-The VIP analysis (@fig-VIP) identified that the band at 531 nm was the most important for accurately identifying Chlorophyceae.
+The variable importance analysis (@fig-VIP) identified that the band at 531 nm was the most important for accurately identifying Chlorophyceae.
 In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in carotenoids to chlorophyll-a ratios between seagrasses and green macroalgae [@repolho2017seagrass].
@@
 These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
-Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range from 560 to 615 nm (@fig-VIP).
-Indeed the band at 560 nm has been identified as important for identifying this class likely due to phycoerythrin absorption at this wavelength.
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contribute to the lowest reflectance among all classes in the spectral range from 560 to 615 nm (@fig-VIP).
+Indeed the band at 560 nm has been identified as important for identifying this class, likely due to phycoerythrin absorption at this wavelength.
 Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
@@
 
-While comparing the reflectance of both altitudes (12 m and 120 m), it was observed @fig-CompareRef that there is an underestimation of the infrared part of the spectra in the high-altitude dataset.
+While comparing the reflectance of both altitudes (12 m and 120 m), it was observed that there is an underestimation of the infrared part of the spectra in the high-altitude dataset (@fig-CompareRef).
 Such disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
@@
 
-The @fig-upscaling demonstrates that at least `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % of seagrass cover is necessary for confident prediction of its presence.
+We found `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % of seagrass cover is necessary for confident prediction of its presence (@fig-upscaling).
 This highlights a limitation of the methodology used to construct the training dataset for the model.
-The dataset used to train our algorithm was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
-Also, intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote].
+The dataset used to train our algorithm was composed exclusively of pure pixels, which resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
+Also, intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year [@bargain2013seasonal ; @legare2022remote].
 Since the training dataset has been made using well developed seagrass meadows, this model may be less accurate outside of the seasonal seagrass peak of biomass.
@@
 and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from biodiversity conservation to climate change adaptation strategies.
+Our findings, particularly the improved discrimination of seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
 
@@
 The first green tide events (i.e.
-bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees].
+bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local stakeholders and economic activities [@menesguen2018marees].
 Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* washing along the Caribbean coastlines [@louime2017sargassum], and more recently *Rugulopteryx okamurea* in southern Europe [@Roca2022].
@@
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on coastal ecosystems.
-On-demand, multispectral drone observations at very high-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth satellite data.
+On-demand, multispectral drone observations at very high spatial-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth satellite data.
 Spatially resolved data are indeed critical for calibrating and validating satellite remote sensing observations, thereby enhancing our capacity to monitor vast coastal areas.
@@
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
-This, in turn, supports the directive's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
+This, in turn, supports the WFD's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
 
@@
 
-The utilization of very high-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses from green macroalgae with a multispectral resolution sensor.
+The utilization of very high spatial-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses from green macroalgae with a multispectral resolution sensor.
 Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible.

### 2024-05-02 docs/_tex/index.tex
adding Ana's comments

@@
 \hypersetup{
-  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft},
+  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
@@
 \title{Draft -- Discriminating Seagrasses From Green Macroalgae in
-European Intertidal areas using high resolution multispectral drone
-imagery -- Draft}
+France and Portugal Intertidal areas using high resolution multispectral
+drone imagery -- Draft}
 \author[1]{Simon Oiry%
@@
 resolution, making it difficult to discriminate seagrass from other
-macrophytes in highly heterogenous meadows. Drone images at a very high
-spatial resolution offer a promising solution to address challenges
-related to spatial heterogeneity and intrapixel mixture. This study
-focuses on using drone acquisitions with a ten spectral band sensor
-mirroring those of Sentinel-2, for mapping intertidal macrophytes and
-effectively discriminating between seagrass and green macroalgae. Nine
-drone flights were conducted at two different altitudes (12m and 120m)
-across heterogeneous intertidal European habitats in France and
-Portugal. Low altitude flights were used to train a Deep Learning
-classifier based on Neural Networks to discrimintate among five
-taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass),
-Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae),
-Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
-Classification of drone imagery resulted in an overall accuracy of 94\%
-across all the sites and images, covering a total area of 467 000 m².
-The model exhibited an accuracy of 96.4\% in identifying seagrass.
-Importantly, seagrass and green algae can be discriminated, although
-they share the same pigment composition. As the algorithm was developed
-for a multispectral camera with ten spectral bands in the visible and
-near-infrared, it could be adapted to the Multi-Spectral Instrument
-(MSI) onboard Sentinel-2 thus offering promising perspectives for
-satellite remote sensing of intertidal biodiversity over lager scales.
+macrophytes in highly heterogenous meadows. Drone (unmanned aerial
+vehicles -- UAV) images at a very high spatial resolution offer a
+promising solution to address challenges related to spatial
+heterogeneity and intrapixel mixture. This study focuses on using drone
+acquisitions with a ten spectral band sensor mirroring those of
+Sentinel-2, for mapping intertidal macrophytes and effectively
+discriminating between seagrass and green macroalgae. Nine drone flights
+were conducted at two different altitudes (12 m and 120 m) across
+heterogeneous intertidal European habitats in France and Portugal. Low
+altitude flights were used to train a Deep Learning classifier based on
+Neural Networks to discrimintate among five taxonomic classes of
+intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green
+macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae)
+and benthic Bacillariophyceae (Diatoms). Classification of drone imagery
+resulted in an overall accuracy of 94\% across all the sites and images,
+covering a total area of 467 000 m². The model exhibited an accuracy of
+96.4\% in identifying seagrass. Importantly, seagrass and green algae
+can be discriminated, although they share the same pigment composition.
+As the algorithm was developed for a multispectral camera with ten
+spectral bands in the visible and near-infrared, it could be adapted to
+the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering
+promising perspectives for satellite remote sensing of intertidal
+biodiversity over lager scales.
 \end{abstract}
@@
 sequestration, oxygen production, protection against sea-level rise and
-coastline erosion, and limitation of eutrophication. They serve as vital
-habitats for a diverse array of marine and terrestrial species,
-providing living, breeding, and feeding grounds \citetext{\citealp[
+coastline erosion, and mitigation of eutrophication \citetext{\citealp[
+]{unsworth2022}; \citealp{sousa2019blue}}. They serve as vital habitats
+for a diverse array of marine and terrestrial species, providing living,
+breeding, and feeding grounds \citetext{\citealp[
 ]{gardner2018}; \citealp[ ]{Zoffoli2022}; \citealp{jankowska2019}}. Due
@@
 ]{soissons2018}; \citealp[ ]{orth2006}; \citealp[ ]{lin2018}; \citealp[
-]{duffy2019}; \citealp[
-]{rasheed2011long}; \citealp{chefaoui2018dramatic}}. Both habitat
+]{duffy2019}; \citealp[ ]{rasheed2011long}; \citealp[
+]{chefaoui2018dramatic}; \citealp{sousa2019blue}}. Both habitat
 fragmentation and reduction, in turn, can severely compromise the
 effectiveness of ecosystem services provided by seagrass meadows. While
-improvements in water quality have been recently reported in Europe,
-allowing an overall recovery of seagrass ecosystems at local scales,
-many coastal waters worldwide are still subjected to strong
-eutrophication processes \citetext{\citealp[
-]{deSantos2019}; \citealp{Zoffoli2021}}. Coastal eutrophication has been
-associated to excessive accumulation of green macroalgae, so-called
-green tides \citep{devlin2023nutrients}. Green tides produce shade and
-suffocation over seagrass individuals, thus threatening the health of
-seagrass ecosystems \citep{wang2022}.
+improvements in water quality and hydrodynamics have been recently
+reported in Europe, allowing an overall recovery of seagrass ecosystems
+at local and European scales, many coastal waters worldwide are still
+subjected to strong eutrophication processes \citetext{\citealp[
+]{deSantos2019}; \citealp[ ]{Zoffoli2021}; \citealp{sousa2019blue}}.
+Coastal eutrophication has been associated to excessive accumulation of
+green macroalgae, so-called green tides \citep{devlin2023nutrients}.
+Green tides produce shade and suffocation over seagrass individuals,
+thus threatening the health of seagrass ecosystems \citep{wang2022}.
 
@@
 measurements in intertidal zones is notoriously challenging. Intertidal
-seagrass meadows are only partially exposed during low tide and can be
-situated in difficult-to-reach mudflats, potentially leading to
-inaccurate and limited estimations with conventional sampling techniques
+seagrass meadows are only exposed during low tide and can be situated in
+difficult-to-reach mudflats, potentially leading to inaccurate and
+limited estimations with conventional sampling techniques
 \citep{nijland2019}. Satellite observations have been proven effective
@@
 temporal resolution (e.g.~daily MODIS observation) are limited by a too
-coarse spatial resolution (\textgreater100m) to accurately map patchy
+coarse spatial resolution (\textgreater100 m) to accurately map patchy
 seagrass meadows. Missions with a high spatial resolution such as
-Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral
+Sentinel-2 (10 m) or Landsat8/9 (30 m) can be limited by low spectral
 resolution. The limited number of spectral bands challenges accurate
@@
 
-Drones can potentially fill the data gaps left by satellite RS and
-\emph{in situ} measurements, due to their ability to provide
-spatially-explicit observations at very high spatial resolutions (pixel
-size from mm to cm) while capturing data at multi-spectral resolution
-\citetext{\citealp[ ]{fairley2022drone}; \citealp{oh2017use}}. The
-versatility of drones allows for their application across a diverse
-thematic range , from coastal zone management \citetext{\citealp[
-]{adade2021}; \citealp[ ]{casella2020}; \citealp{angnuureng2022}} to
-mapping species distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
-]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[
-]{Roman2021}; \citealp{Brunier2022Topographic}}. However, when applied
-to coastal habitat mapping, most case studies were previously limited to
-a single flight, restricting the generalizability of their application
-over wider geographical scales \citetext{\citealp[
+Drones (Unmanned Aerial Vehicles -- UAVs) can potentially fill the data
+gaps left by satellite RS and \emph{in situ} measurements, due to their
+ability to provide spatially-explicit observations at very high spatial
+resolutions (pixel size from mm to cm) while capturing data at
+multi-spectral resolution \citetext{\citealp[
+]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
+allows for their application across a diverse thematic range , from
+coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
+]{casella2020}; \citealp{angnuureng2022}} to mapping species
+distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
+]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[ ]{Roman2021}; \citealp[
+]{Brunier2022Topographic}; \citealp{sousa2019blue}}. However, when
+applied to coastal habitat mapping, most case studies were previously
+limited to a single flight, restricting the generalizability of their
+application over wider geographical scales \citetext{\citealp[
 ]{Roman2021}; \citealp[ ]{collin2019improving}; \citealp[
@@
 particular focus on discriminating Magnoliopsida and Chlorophyceae
-(Seagrass and Green Algae respectively). Ten drone flights were
+(Seagrass and Green Algae, respectively). Ten drone flights were
 performed over soft-bottom intertidal areas along the Atlantic
@@
 (47.5791°N, 2.8018°W). This gulf covers an area of 115 km² and is only
-connected to the sea through a 900m wide channel. A total of 53 small
+connected to the sea through a 900 m wide channel. A total of 53 small
 islands are scattered across the gulf leading to 250 km of shorelines.
@@
 contained monospecific beds of \emph{Nanozostera noltei} (dwarf
-eelgrass) with very little mixing with other macrophytes. Three sites
-were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N,
-8.6810°W). The extent of this lagoon is \textasciitilde80 km² with many
-narrow channels, large salt marshes and many mudflats that uncover at
-low tide. It is connected to the open sea through a single channel, with
-a tidal lag between the North and the South of the lagoon. The
-southernmost site (Gafanha) was a mudflat located in a tributary river
-of the lagoon whereas the two other sites (Mataducos and Marinha
-Lanzarote) were situated in the middle of the lagoon and only accessible
-by boat (Figure~\ref{fig-map} C). These Portuguese sites are
-characterized by a more diverse intertidal vegetation, where patches of
-seagrass intermingle with red, brown, and green macroalgae.
+eelgrass, syn. \emph{Zostera noltei}) with very little mixing with other
+macrophytes. Three sites were surveyed in the Ria de Aveiro Coastal
+Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of this lagoon is
+\textasciitilde83 km² (at low tide) with many narrow channels, large
+salt marshes and many mudflats that uncover at low tide
+\citep{sousa2017blue}. It is connected to the open sea through a single
+channel, with a tidal lag between the North and the South of the lagoon.
+The southernmost site (Gafanha) is a mudflat located in the Mira channel
+(one of the four main channels of the lagoon) whereas the two other
+sites (Mataducos and Marinha Lanzarote) were situated in the middle of
+the lagoon and only accessible by boat (Figure~\ref{fig-map} C). These
+Portuguese sites are characterized by a more diverse intertidal
+vegetation, where patches of seagrass intermingle with red, brown, and
+green macroalgae.
 
@@
 taxonomic classes of intertidal vegetation : Bacillariophyceae
-(Unicellular benthic diatoms forming biofilms at the sediment surface
+(unicellular benthic diatoms forming biofilms at the sediment surface
 during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf
-seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red
+eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red
 macroalgae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
@@
 served dual purposes: they validate the radiometric calibration of drone
-data and contribute to error reduction in photo interpretation.
+data and contribute to error reduction in photo interpretations.
 
@@
 used to train the Neural Network model and their raw spectral signatures
-at the spectral resolution of the Micasense RedEdge Dual MX.}
+at the spectral resolution of the Micasense RedEdge Dual MX. A :
+Magnoliopsida (Nanozostera noltei syn. Zostera noltei) ; B :
+Phaeophyceae (Fucus sp.) ; C : Rhodophyceae (Gracilaria vermiculophylla)
+; D : Chlorophyceae (Ulva sp.) ; E : Bacillariophyceae (Diatoms - MPB)}
 
@@
 distinguish between the various types of vegetation. High altitude
-fights on the other hand allowed to cover large areas and produced
+flights on the other hand allowed to cover large areas and produced
 images with a pixel size of 80 mm (Table~\ref{tbl-flights}).
@@
 
-\subsection{Impact of the percent cover on the
-prediction}\label{impact-of-the-percent-cover-on-the-prediction}
+\subsection{Impact of the vegetation cover on the
+prediction}\label{impact-of-the-vegetation-cover-on-the-prediction}
 
@@
 The predictions made on the high-resolution flight can be used to
-estimate the percent cover of each vegetation class for every pixel of
-the lower resolution flight. Consequently, for each pixel of the
-high-altitude flights, percent covers of each vegetation class were
+estimate the cover (percentage, \%) of each vegetation class for every
+pixel of the lower resolution flight. Consequently, for each pixel of
+the high-altitude flights, the cover (\%) of each vegetation class were
 obtained, and a kernel density plot was generated. This plot provides a
@@
 Chlorophyceae and Rhodophyceae mixed with the seagrass meadow. There was
-also Bacillariophyceae forming biofilms on parts of sediment surface.
-Although the seagrass bed was solely composed of \emph{Nanozostera
-noltei}, various colors of this specie could be observed from dark green
-(corresponding to healthy leaves) to whitish/brown (when leaves were
-discolored having lost their pigmentation). Regardless of color,
-Magnoliopsida pixels were accurately predicted by the model.
+also Bacillariophyceae forming biofilms on parts of bare sediment
+surface. Although the seagrass bed was solely composed of
+\emph{Nanozostera noltei}, various colors of this specie could be
+observed from dark green (corresponding to healthy leaves) to
+whitish/brown (when leaves were discolored having lost their
+pigmentation). Regardless of color, Magnoliopsida pixels were accurately
+predicted by the model.
 
@@
 of the low altitude flight of Gafanha, Portugal. The total extent of
-this flight was 3000m² with a resolution of 8 mm per pixel. Background
+this flight was 3000 m² with a resolution of 8 mm per pixel. Background
 colors indicate intertidal area (Light Green) and land area (Light
@@
 correctly classified. In the northern part of the site and near the land
-eadges, patches of the schorre angiosperm \emph{Spartina sp.} were
-misclassified, either as Magnoliopsida or as Phaeophyceae.
+eadges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
+(syn. \emph{Spartina maritima)} were misclassified, either as
+Magnoliopsida or as Phaeophyceae.
 
@@
 
-Amoung the high altitude flights, the one acquired over the inner lagoon
-of the Ria de Aveiro covered the largest area with approximately 1.5 km²
-(Figure~\ref{fig-Boat}). This site was dominated by seagrass and red
-macroalgae. The classification provided consistent results, with a
-patchy seagrass meadow mixed with red macroalgae on the eastern part of
-the site. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of the
-meadow visually appears to be colonised by green macroalgae, which the
-model agreed with.
+Amoung the high altitude flights, the one acquired over the inner part
+of Ria de Aveiro coastal lagoon covered the largest area with
+approximately 1.5 km² (Figure~\ref{fig-Boat}). This site was dominated
+by seagrass and red macroalgae. The classification provided consistent
+results, with a patchy seagrass meadow mixed with red macroalgae on the
+eastern part of the site. As shown in the zoom (Figure~\ref{fig-Boat}),
+the edges of the meadow visually appears to be colonised by green
+macroalgae (\emph{Ulva sp.}), which the model agreed with.
 
@@
 In this study, a key innovation lies in the utilization of drone flights
-at two different altitudes (12m and 120m) for constructing the neural
+at two different altitudes (12 m and 120 m) for constructing the neural
 network model. Overall there was a good agreement between the two
@@
 shows the drone raw and standardised reflectance spectra of each class.
-Each slice represents the VIP of both raw and standardised reflectance
-combined.}
+Each slice represents the Variable Importance (VI) of both raw and
+standardised reflectance combined.}
 
@@
 
-When the percent cover of a given class was 100 \%, coarser high-flight
-pixels were well classified for all the classes except for Bare
-Sediment, which was only well classified 80\% of the time. This
+When the vegetation cover of a given class was 100 \%, coarser
+high-flight pixels were well classified for all the classes except for
+Bare Sediment, which was only well classified 80\% of the time. This
 phenomenon may be attributed to the time gap between the two flights,
@@
 have all the pixels of high altitude flights correctly classified, with
-the exception of Magnoliopsida that required a higher percent cover
+the exception of Magnoliopsida that required a higher cover
 (\textgreater90 \%) to be well classified. Concerning the probability of
@@
 Bacillariophyceae. To predict Chlorophyceae with a model likelihood of
-0.85, a percent cover of 93 \% was needed, 90 \% for Magnoliopsida, 92
-\% for Rhodophyceae and 97 \% for Bacillariophyceae.
+0.85, a cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
+Rhodophyceae and 97 \% for Bacillariophyceae.
 
@@
 The primary objective of this study was to develop a method for the
-accurate classification of macrophytes on intertidal mudflats,
-specifically focusing on distinguishing between Chlorophyceae (green
-macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
-drone data. The ability to differentiate between various types of
-vegetation plays a critical role in ecological monitoring and coastal
-management \citep{WFD2000}. By distinguishing between seagrasses and
-macroalgae, our approach facilitates targeted conservation strategies,
-enabling more effective preservation and restoration efforts in coastal
-ecosystems. The discrimination of seagrasses from green macroalgae
-presents two main challenges \citetext{\citealp[
+accurate classification of macrophytes on intertidal mudflats and
+sandflats, specifically focusing on distinguishing between Chlorophyceae
+(green macroalgae) and marine Magnoliopsida (seagrasses) using
+multispectral drone data. The ability to differentiate between various
+types of vegetation plays a critical role in ecological monitoring and
+coastal management \citep{WFD2000}. By distinguishing between seagrasses
+and macroalgae, our approach facilitates targeted conservation
+strategies, enabling more effective preservation and restoration efforts
+in coastal ecosystems. The discrimination of seagrasses from green
+macroalgae presents two main challenges \citetext{\citealp[
 ]{oiry2021using}; \citealp[
@@
 Our results confirm a recent study based on \emph{in situ} radiometry,
-where it was demonstrated that a radiometer with at least eight spectral
+where it was demonstrated that a sensor with at least eight spectral
 bands ranging from 500 to 850 nm and including a green band at 530 nm
 and a RedEdge band at 730 nm was crucial to accurately discriminate
-green macrophytes \citep{Davies2023}.
+green macroalgae from seagrasses \citep{Davies2023}.
 
@@
 issue, we employed min/max standardized reflectance spectra as
-predictors for the model (Equation~\ref{eq-std} ; \citep{Cao2017}). This
-approach allowed us to eliminate the slight reflectance difference
-between the flights (Figure~\ref{fig-CompareRef} B) and to focus on the
-shape of the spectra in the visible part of the electromagnetic spectra,
-where different pigmentation are associated to taxonomic dignostic
-features. This was a key feature in building a model that could reliably
-predict vegetation across geographical sites and seasons. It enabled
-consistent prediction of vegetation classes across variations in biomass
-and variability in light conditions \citetext{\citealp[
-]{fyfe2003spatial}; \citealp[
+predictors for the model Equation~\ref{eq-std}. This approach allowed us
+to eliminate the slight reflectance difference between the flights
+(Figure~\ref{fig-CompareRef} B) and to focus on the shape of the spectra
+in the visible part of the electromagnetic spectra, where different
+pigmentation are associated to taxonomic dignostic features. This was a
+key feature in building a model that could reliably predict vegetation
+across geographical sites and seasons. It enabled consistent prediction
+of vegetation classes across variations in biomass and variability in
+light conditions \citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
 ]{COSTA2021107018}; \citealp{piaser2023impact}}.
@@
 ]{bargain2013seasonal}; \citealp{legare2022remote}}. Since the training
-dataset has been made using well developed seagrass meadows, this model
-may be less accurate outside of the seasonal seagrass peak of biomass.
-Further investigation is required to evaluate the accuracy of the method
-along different periods of the year.
+dataset has been made using well established seagrass meadows, this
+model may be less accurate outside of the seasonal seagrass peak of
+biomass. Further investigation is required to evaluate the accuracy of
+the method along different periods of the year.
 
@@
 ]{villalobos2023remote}; \citealp{oiry2021using}}. Our findings,
-particularly the improved discrimination of seagrass and green
-macroalgae from other intertidal vegetation classes, highlight the
+particularly the improved discrimination of intertidal seagrass and
+green macroalgae from other intertidal vegetation classes, highlight the
 potential of drone-based remote sensing to support diverse applications,
@@
 surveillance, offering significant advancements in the spatial and
-temporal resolution of data collection. This, in turn, supports the
+temporal resolution of data collection. This, in turn, supports the EU
 WFD's objectives by enabling more informed and timely management
@@
 sensing coupled with machine learning techniques has proven to be an
-effective method for the discrimination of seagrasses from green
-macroalgae with a multispectral resolution sensor. Standardized
+effective method for the discrimination of intertidal seagrasses from
+green macroalgae with a multispectral resolution sensor. Standardized
 reflectance was incorporated in the Neural Network model allowing for a
 better discrimination of spectral features related to pigment absorption
-in the visible. There was a striking difference for the variable of
-importance to discriminate Magnoliopsida from Chlorophyceae. The latter
-was essentially identified with the 451 nm spectral band while more
-spectral bands were needed to identify the former, notably 650, 560,
-668, and 705 nm. As the spectral bands of the Micasense RedEdge Dual MX
-are very similar to those of Sentinel-2, we suggest that multispectral
-satellite data have the potential to perform this discrimination between
-green macrophytes. A sentinel-2 algorithm could be developed, using the
-output of this current workflow as training and validation data. The
-findings underscore the importance of adopting advanced remote sensing
-tools in ecological studies and environmental monitoring, providing a
-foundation for future research and policy implementation aimed at
-ecosystem conservation and restoration.
+in the visible region of the spectrum. There was a striking difference
+for the variable of importance to discriminate Magnoliopsida from
+Chlorophyceae. The latter was essentially identified with the 451 nm
+spectral band while more spectral bands were needed to identify the
+former, notably 650, 560, 668, and 705 nm. As the spectral bands of the
+Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we
+suggest that multispectral satellite data have the potential to perform
+this discrimination between green these macrophytes. A Sentinel-2
+algorithm could be developed, using the output of this current workflow
+as training and validation data. The findings underscore the importance
+of adopting advanced remote sensing tools in ecological studies and
+environmental monitoring, providing a foundation for future research and
+policy implementation aimed at ecosystem conservation and restoration.
 

### 2024-05-02 index.qmd
adding Ana's comments

@@
 ---
-title: Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft
+title: Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft
 author:
@@
 Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
-Drone images at a very high spatial resolution offer a promising solution to address challenges related to spatial heterogeneity and intrapixel mixture.
+Drone (unmanned aerial vehicles – UAV) images at a very high spatial resolution offer a promising solution to address challenges related to spatial heterogeneity and intrapixel mixture.
 This study focuses on using drone acquisitions with a ten spectral band sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
-Nine drone flights were conducted at two different altitudes (12m and 120m) across heterogeneous intertidal European habitats in France and Portugal.
+Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal.
 Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
@@
 Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between the land and oceans [@unsworth2022].
-Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and limitation of eutrophication.
+Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and mitigation of eutrophication [@unsworth2022 ; @sousa2019blue].
 They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019].
 Due to the concentration of human activities in coastal zones, seagrass meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation of seagrass meadows are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic].
+Global regression and fragmentation of seagrass meadows are currently observed due to climate change, diseases, urbanization, land reclamation, dredging, competition with alien species, and reduction in water quality [@nguyen2021 ; @soissons2018 ; @orth2006 ; @lin2018 ; @duffy2019 ; @rasheed2011long ; @chefaoui2018dramatic ; @sousa2019blue].
 Both habitat fragmentation and reduction, in turn, can severely compromise the effectiveness of ecosystem services provided by seagrass meadows.
-While improvements in water quality have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local scales, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021].
+While improvements in water quality and hydrodynamics have been recently reported in Europe, allowing an overall recovery of seagrass ecosystems at local and European scales, many coastal waters worldwide are still subjected to strong eutrophication processes [@deSantos2019 ; @Zoffoli2021 ; @sousa2019blue].
 Coastal eutrophication has been associated to excessive accumulation of green macroalgae, so-called green tides [@devlin2023nutrients].
@@
 However, the acquisition of these measurements in intertidal zones is notoriously challenging.
-Intertidal seagrass meadows are only partially exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
+Intertidal seagrass meadows are only exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
 Satellite observations have been proven effective in complementing *in situ* sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
@@
 Satellite missions with a high temporal resolution (e.g.
-daily MODIS observation) are limited by a too coarse spatial resolution (\>100m) to accurately map patchy seagrass meadows.
-Missions with a high spatial resolution such as Sentinel-2 (10m) or Landsat8/9 (30m) can be limited by low spectral resolution.
+daily MODIS observation) are limited by a too coarse spatial resolution (\>100 m) to accurately map patchy seagrass meadows.
+Missions with a high spatial resolution such as Sentinel-2 (10 m) or Landsat8/9 (30 m) can be limited by low spectral resolution.
 The limited number of spectral bands challenges accurate discrimination of seagrass from other co-existing macrophytes.
@@
 
-Drones can potentially fill the data gaps left by satellite RS and *in situ* measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
-The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic].
+Drones (Unmanned Aerial Vehicles – UAVs) can potentially fill the data gaps left by satellite RS and *in situ* measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
 However, when applied to coastal habitat mapping, most case studies were previously limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae respectively).
+The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae, respectively).
 Ten drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
@@
 Two sites were located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
-This gulf covers an area of 115 km² and is only connected to the sea through a 900m wide channel.
+This gulf covers an area of 115 km² and is only connected to the sea through a 900 m wide channel.
 A total of 53 small islands are scattered across the gulf leading to 250 km of shorelines.
@@
 Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km² [@ZOFFOLI2020112020].
-Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
-Three sites were surveyed in the Ria de Aveiro Lagoon in Portugal (40.6887°N, 8.6810°W).
-The extent of this lagoon is \~80 km² with many narrow channels, large salt marshes and many mudflats that uncover at low tide.
+Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass, syn.
+*Zostera noltei*) with very little mixing with other macrophytes.
+Three sites were surveyed in the Ria de Aveiro Coastal Lagoon in Portugal (40.6887°N, 8.6810°W).
+The extent of this lagoon is \~83 km² (at low tide) with many narrow channels, large salt marshes and many mudflats that uncover at low tide [@sousa2017blue].
 It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) was a mudflat located in a tributary river of the lagoon whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
+The southernmost site (Gafanha) is a mudflat located in the Mira channel (one of the four main channels of the lagoon) whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
 These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown, and green macroalgae.
@@
     "Training"
+  ),
+  Date = c(
+    "29/09/2022",
+    "14/07/2022",
+    "14/07/2022",
+    "07/09/2021",
+    "08/07/2021",
+    "17/06/2022",
+    "16/06/2022",
+    "15/06/2022",
+    "15/06/2022"
   )
@@
     hline(i=5, border=brdr1) %>%
-    hline(i=1,j = 3:5, border=brdr2) %>%
+    hline(i=1,j = 3:6, border=brdr2) %>%
     hline(i=2, border=brdr2) %>%
-    hline(i=3, j = 2:5, border=brdr3) %>%
-    hline(i=4, j = 3:5, border=brdr2) %>%
+    hline(i=3, j = 2:6, border=brdr3) %>%
+    hline(i=4, j = 3:6, border=brdr2) %>%
     hline(i=6, border=brdr2) %>%
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (Unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf seagrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
@@
 Hyperspectral reflectance signatures of each vegetation class were recorded using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
-Hyperspectral signatures served dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretation.
+Hyperspectral signatures served dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretations.
 
@@
 #| warning: false
-#| fig-cap: The five taxonomic classes of vegetation used to train the Neural Network model and their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX. 
+#| fig-cap: "The five taxonomic classes of vegetation used to train the Neural Network model and their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX.
+A : Magnoliopsida (Nanozostera noltei syn.
+Zostera noltei)  ; B : Phaeophyceae (Fucus sp.) ; C : Rhodophyceae (Gracilaria vermiculophylla) ; D : Chlorophyceae (Ulva sp.) ; E : Bacillariophyceae (Diatoms - MPB)"
 #| label: fig-vegetation
@@
 Low altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
-High altitude fights on the other hand allowed to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
+High altitude flights on the other hand allowed to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
 
@@
 
-## Impact of the percent cover on the prediction
+## Impact of the vegetation cover on the prediction
 
 The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm).
-The predictions made on the high-resolution flight can be used to estimate the percent cover of each vegetation class for every pixel of the lower resolution flight.
-Consequently, for each pixel of the high-altitude flights, percent covers of each vegetation class were obtained, and a kernel density plot was generated.
+The predictions made on the high-resolution flight can be used to estimate the cover (percentage, %) of each vegetation class for every pixel of the lower resolution flight.
+Consequently, for each pixel of the high-altitude flights, the cover (%) of each vegetation class were obtained, and a kernel density plot was generated.
 This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
@@
 Among the five vegetation classes on which the model was trained, four were present on this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass meadow.
-There was also Bacillariophyceae forming biofilms on parts of sediment surface.
+There was also Bacillariophyceae forming biofilms on parts of bare sediment surface.
 Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
@@
 #| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the low altitude flight of Gafanha, Portugal.
-The total extent of this flight was 3000m² with a resolution of 8 mm per pixel.
+The total extent of this flight was 3000 m² with a resolution of 8 mm per pixel.
 Background colors indicate intertidal area (Light Green) and land area (Light Grey).
@@
 Patches of Rhodophyceae were correctly classified.
-In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Spartina sp.* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Sporobolus maritimus* (syn.
+*Spartina maritima)* were misclassified, either as Magnoliopsida or as Phaeophyceae.
 
@@
 
-Amoung the high altitude flights, the one acquired over the inner lagoon of the Ria de Aveiro covered the largest area with approximately 1.5 km² (@fig-Boat).
+Amoung the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat).
 This site was dominated by seagrass and red macroalgae.
 The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
-As shown in the zoom (@fig-Boat), the edges of the meadow visually appears to be colonised by green macroalgae, which the model agreed with.
+As shown in the zoom (@fig-Boat), the edges of the meadow visually appears to be colonised by green macroalgae (*Ulva sp.*), which the model agreed with.
 
@@
 
-In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12m and 120m) for constructing the neural network model.
+In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12 m and 120 m) for constructing the neural network model.
 Overall there was a good agreement between the two altitudes (@fig-CompareRef).
@@
 The right plot shows the drone raw and standardised reflectance spectra of each class.
-Each slice represents the VIP of both raw and standardised reflectance combined.
+Each slice represents the Variable Importance (VI) of both raw and standardised reflectance combined.
 #| label: fig-VIP
@@
 
-When the percent cover of a given class was 100 %, coarser high-flight pixels were well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
+When the vegetation cover of a given class was 100 %, coarser high-flight pixels were well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
 This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
-A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher percent cover (\>90 %) to be well classified.
+A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be well classified.
 Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
-To predict Chlorophyceae with a model likelihood of 0.85, a percent cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
+To predict Chlorophyceae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
 
@@
 
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
+The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats and sandflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
 The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management [@WFD2000].
@@
 Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone, and the risk of spectral confusion was avoided thanks to the efficiency of the multispectral classifier.
-Our results confirm a recent study based on *in situ* radiometry, where it was demonstrated that a radiometer with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macrophytes [@Davies2023].
+Our results confirm a recent study based on *in situ* radiometry, where it was demonstrated that a sensor with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macroalgae from seagrasses [@Davies2023].
 
@@
 This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training.
-To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]).
+To address this issue, we employed min/max standardized reflectance spectra as predictors for the model [@eq-std ; @Cao2017].
 This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features.
@@
 Also, intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year [@bargain2013seasonal ; @legare2022remote].
-Since the training dataset has been made using well developed seagrass meadows, this model may be less accurate outside of the seasonal seagrass peak of biomass.
+Since the training dataset has been made using well established seagrass meadows, this model may be less accurate outside of the seasonal seagrass peak of biomass.
 Further investigation is required to evaluate the accuracy of the method along different periods of the year.
@@
 and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
+Our findings, particularly the improved discrimination of intertidal seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
 
@@
 The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
-This, in turn, supports the WFD's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
+This, in turn, supports the EU WFD's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
 
@@
 
-The utilization of very high spatial-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses from green macroalgae with a multispectral resolution sensor.
-Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible.
+The utilization of very high spatial-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of intertidal seagrasses from green macroalgae with a multispectral resolution sensor.
+Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible region of the spectrum.
 There was a striking difference for the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
 The latter was essentially identified with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
-As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green macrophytes.
-A sentinel-2 algorithm could be developed, using the output of this current workflow as training and validation data.
+As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green these macrophytes.
+A Sentinel-2 algorithm could be developed, using the output of this current workflow as training and validation data.
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.

### 2024-05-02 docs/_tex/index.tex
adding Ana's comments

@@
 \hypersetup{
-  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft},
+  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft},
   pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
@@
 \title{Draft -- Discriminating Seagrasses From Green Macroalgae in
-France and Portugal Intertidal areas using high resolution multispectral
-drone imagery -- Draft}
+European Intertidal areas using high resolution multispectral drone
+imagery -- Draft}
 \author[1]{Simon Oiry%

### 2024-05-02 index.qmd
adding Ana's comments

@@
 ---
-title: Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft
+title: Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft
 author:
@@
 
-brdr1 <- fp_border_default(color = "black", width = 1.5)
+brdr1 <- fp_border_default(color = "black", width = 1)
 brdr2 <- fp_border_default(color = "grey", width = 1.5)

### 2024-05-03 index.qmd
adding submission files

@@
     affiliations:
-      - CESAM – Centre for Environmental and Marine Studies, Department of Biology, University of Aveiro, Aveiro, Portugal
+      - ECOMARE - Laboratory for Innovation and Sustainability of Marine Biological Resources, CESAM – Centre for Environmental and Marine Studies, Department of Biology, University of Aveiro, Campus Universitário de Santiago, 3810-193 Aveiro, Portugal
   - name: Philippe Rosa

### 2024-05-03 docs/_tex/index.tex
adding submission files

@@
 France},,postcodesep={}}
-\affiliation[2]{organization={CESAM -- Centre for Environmental and
-Marine Studies, Department of Biology, University of Aveiro, Aveiro,
+\affiliation[2]{organization={ECOMARE - Laboratory for Innovation and
+Sustainability of Marine Biological Resources, CESAM -- Centre for
+Environmental and Marine Studies, Department of Biology, University of
+Aveiro, Campus Universitário de Santiago, 3810-193 Aveiro,
 Portugal},,postcodesep={}}

### 2024-05-08 index.qmd
adding STOTEN submission

@@
 csl: RSE.csl
+---dd .
 ---
@@
 ggsave("Figures/High_res/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)
+
+```
+
+```{r Figure1 Map Graphical abstract}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+world_map <- sovereignty10 %>% 
+  st_as_sf() %>% 
+  dplyr::filter(SOVEREIGNT%in%c("Spain","France","Portugal",
+                                "Italy","Andorra",
+                                "United Kingdom",
+                                "Switzerland","Belgium",
+                                "Germany","Luxembourg") )
+
+bbox_europe <- st_bbox(c(xmin = -20, ymin = 34,
+                         xmax = 20, ymax = 55) ,
+                       crs = st_crs(world_map) )
+
+world_map<-st_make_valid(world_map)
+
+european_union_map_cropped <- st_crop(world_map, bbox_europe)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+UnitedKingdom<-sovereignty10 %>% 
+  st_as_sf() %>% 
+  dplyr::filter(SOVEREIGNT%in%c("United Kingdom") ) %>% 
+  st_cast("POLYGON")
+
+bbox_UK <- st_bbox(c(xmin = -20, ymin = 45,
+                         xmax = 20, ymax = 55) ,
+                       crs = st_crs(UnitedKingdom) )
+
+UnitedKingdom<-st_make_valid(UnitedKingdom)
+
+UK_map_cropped <- st_crop(UnitedKingdom, bbox_UK)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+Europe_sf<-european_union_map_cropped %>% 
+  dplyr::bind_rows(UK_map_cropped)
+
+Projects<-data.frame(
+  Name=c(
+  "Portugal - Aveiro Lagoon Flights\nLower-Resolution: 4\nHigher-Resolution: 1",
+  "France - Morbihan Gulf Flights\nLower-Resolution: 3\nHigher-Resolution: 3",
+  "France - Bourgneuf Bay Flights\nLower-Resolution: 4\nHigher-Resolution: 0"
+  ) ,
+  Long=c(-8.745730,
+         -2.840592, 
+         -2.111868) ,
+  Lat=c(40.617610, 
+        47.578736,
+        47.024719) 
+  )  %>% 
+  st_as_sf(coords=c("Long","Lat") )  %>% 
+  st_set_crs("EPSG:4326")  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+Projects_df<-Projects %>%
+  dplyr::mutate(lon = sf::st_coordinates(.) [,1],
+                lat = sf::st_coordinates(.) [,2]) %>% 
+  sf::st_set_geometry(NULL)  %>% 
+  separate(Name, into=c("Country","Bay") ,sep=" - ")  %>% 
+  dplyr::mutate(Country=as.factor(Country) ,
+                Bay=as.factor(Bay) )
+
+Miniworld_map <- sovereignty10 %>% 
+  st_as_sf()
+
+sf_use_s2(FALSE)
+
+bbox_EU <- st_bbox(c(xmin = -30, ymin = 20,
+                         xmax = 50, ymax = 70) ,
+                       crs = st_crs(Miniworld_map) )
+
+  MiniEU_map<-st_crop(Miniworld_map, bbox_EU)  %>% 
+  st_transform("+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs ")
+
+  df_P2<-Projects_df %>% 
+    mutate(ID = c(1:nrow(.))) %>% 
+    mutate(Site = case_when(ID == 1 ~ "Aveiro Lagoon",
+                            ID == 2 ~ "Morbihan Gulf",
+                            ID == 3 ~ "Bourgneuf Bay",
+                            TRUE ~ "NA"),
+           ID = case_when(ID == 1 ~ "Portugal",
+                          ID == 2 ~ "France",
+                          TRUE ~ "France")) %>% 
+    dplyr::select(c(lon,lat,ID,Site))
+
+    scaleFUN <- function(x) paste0(sprintf("%.2f", x),"°N")
+
+p2  <-
+  ggplot(MiniEU_map) +
+  geom_sf(linewidth=0.5,alpha=0.93,
+          fill="#CFCFCF",colour="grey30")+
+    ggforce::geom_mark_ellipse(data=df_P2,
+                 aes(x=lon,
+                     y=lat,
+                     label = ID,
+                     description=Site) ,
+                 linewidth=0.3,
+                 label.width = 20,
+                 fill="goldenrod",
+                 show.legend=F,
+                 label.hjust = 0.5,
+                 con.size = 2,
+                 con.colour = "goldenrod4",
+                 label.fontsize = c(25,20),
+                 alpha=0.8,
+                 expand = unit(2, "mm") , 
+                 radius = unit(2, "mm") , 
+                 label.buffer = unit(10, "mm") ,
+                 label.fill = "grey90")+
+  coord_sf(xlim=c(2600000,4100000) ,
+          ylim=c(1600000,3100000))+
+  theme_void()+
+  labs(x="Longitude",
+       y="Latitude")+
+  scale_y_continuous(labels=scaleFUN)
+  # theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
+  #       axis.title = element_blank(),
+  #       axis.text.x = element_text(size = 20),
+  #       axis.text.y = element_text(size = 20) )
+
+ggsave("Figures/High_res/Figure1/Graphical_Abstract_Map.png",p2,width= 10, height=10)
 

### 2024-06-14 index.qmd
add packages

@@
 library(caret)
+library(rstudioapi)
 

### 2024-08-29 index.qmd
add resampling code

--- 2024-05-08 index.qmd
@@
 csl: RSE.csl
----dd .
 ---
@@
 library(tidyterra)
-library(tidymodels)
+# library(tidymodels)
 library(Utilities.Package) 
@@
 library(caret)
+library(rstudioapi)
+library(terra)
 
 options(scipen = 100000000)
+# terraOptions(cores = 12)
+
 ```
@@
 
+## Effect of the spatial resolution on the prediction
+
+```{r Resampling}
+
+img_list <- list.files("Data/BiCOME_Flights", pattern = ".tif", recursive = T, full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path),
+         sites = case_when(str_detect(path, "Boat1") ~ "Boat1",
+                           str_detect(path, "Boat2") ~ "Boat2",
+                           str_detect(path, "GafanhaHigh") ~ "GafanhaHigh",
+                           str_detect(path, "GafanhaLow") ~ "GafanhaLow",
+                           str_detect(path, "Horse_rooster") ~ "Horse_rooster",
+                           str_detect(path, "Gois") ~ "Gois",
+                           str_detect(path, "Handfisher_1") ~ "Handfisher_1",
+                           str_detect(path, "Handfisher_2") ~ "Handfisher_2",
+                           str_detect(path, "NorthDike") ~ "NorthDike",
+                           str_detect(path, "Arz") ~ "Arz",
+                           str_detect(path, "DuerHigh") ~ "DuerHigh",
+                           str_detect(path, "DuerLow") ~ "DuerLow",
+                           str_detect(path, "Kerdrean") ~ "Kerdrean",
+                           str_detect(path, "Locmariaquer") ~ "Locmariaquer"),
+         type = case_when(str_detect(name, "Preds") ~ "Pred",
+                          str_detect(name, "Probs") ~ "Prob",
+                          T ~ "Ortho"),
+         filter = case_when(str_detect(path,"Majority_filter_21by21")~ "21",
+                            str_detect(path,"Majority_filter_7by7")~ "7",
+                            str_detect(path,"Majority_filter")~ "3",
+                            str_detect(path,"RAW")~ "RAW",
+                            T ~ "NA"),
+         UTM_zone = case_when(str_detect(path, "Aveiro") ~ 32629,
+                              TRUE ~ 32630)) %>% 
+  dplyr::filter(!str_detect(path, ".tif.aux.xml"),
+                !str_detect(path, ".tif.enp"),
+                type == "Ortho")
+
+# res_to_resample <- c(10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,200,300,400,500,600,700,800,900,1000,1500,2000,2500,3000)
+res_to_resample <- c(2000)
+
+  # pb2 <- progress_bar$new(
+  # format = "  Processing [:bar] :percent in :elapsed",
+  # total = length(res_to_resample),    # Total number of iterations
+  # width = 60    # Width of the progress bar
+  # )
+
+for(i in 1:nrow(img_list)){
+      # pb2$tick()
+
+  img <- terra::rast(img_list$path[i]) %>% 
+    terra::project(paste0("EPSG:", img_list$UTM_zone[i]), thread = T)
+
+  for(ii in 1:length(res_to_resample)){
+    new_res <- res_to_resample[ii]/100
+
+    r_template <- rast(ext(img), resolution = new_res, crs = crs(img))
+    r_resampled <- terra::resample(img, r_template, method="bilinear", threads = T)%>% 
+      terra::project("EPSG:4326", thread = T)
+
+    if(i == 1){
+      if(!dir.exists(paste0("Data/Resampling/",res_to_resample[ii],"cm"))){
+       dir.create(paste0("Data/Resampling/",res_to_resample[ii],"cm"), recursive = T) 
+      }
+    }
+    writeRaster(r_resampled, paste0("Data/Resampling/",res_to_resample[ii],"cm/",gsub(".tif",paste0("_",res_to_resample[ii],"cm.tif"),img_list$name[i])),overwrite = T)
+  }
+
+}
+
+a <- list.files("Data/Resampling", recursive = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path) %>% gsub(".tif","",.)) %>% 
+  pull(name) %>%
+  str_c(collapse = "\", \"") %>%
+  str_c("\"", ., "\"")
+
+paste0(a)
+
+write.csv(a, 
+  "test.csv")
+
+```
+
 ## Effect of the percent cover on the prediction

### 2024-09-02 Data/shp/Aveiro/Background_p1_aveiro.qmd
resampling saved

<!DOCTYPE qgis PUBLIC 'http://mrcc.com/qgis.dtd' 'SYSTEM'>
<qgis version="3.28.11-Firenze">
  <identifier></identifier>
  <parentidentifier></parentidentifier>
  <language></language>
  <type></type>
  <title></title>
  <abstract></abstract>
  <links/>
  <fees></fees>
  <encoding></encoding>
  <crs>
    <spatialrefsys nativeFormat="Wkt">
      <wkt>PROJCRS["WGS 84 / UTM zone 29N",BASEGEOGCRS["WGS 84",ENSEMBLE["World Geodetic System 1984 ensemble",MEMBER["World Geodetic System 1984 (Transit)"],MEMBER["World Geodetic System 1984 (G730)"],MEMBER["World Geodetic System 1984 (G873)"],MEMBER["World Geodetic System 1984 (G1150)"],MEMBER["World Geodetic System 1984 (G1674)"],MEMBER["World Geodetic System 1984 (G1762)"],MEMBER["World Geodetic System 1984 (G2139)"],ELLIPSOID["WGS 84",6378137,298.257223563,LENGTHUNIT["metre",1]],ENSEMBLEACCURACY[2.0]],PRIMEM["Greenwich",0,ANGLEUNIT["degree",0.0174532925199433]],ID["EPSG",4326]],CONVERSION["UTM zone 29N",METHOD["Transverse Mercator",ID["EPSG",9807]],PARAMETER["Latitude of natural origin",0,ANGLEUNIT["degree",0.0174532925199433],ID["EPSG",8801]],PARAMETER["Longitude of natural origin",-9,ANGLEUNIT["degree",0.0174532925199433],ID["EPSG",8802]],PARAMETER["Scale factor at natural origin",0.9996,SCALEUNIT["unity",1],ID["EPSG",8805]],PARAMETER["False easting",500000,LENGTHUNIT["metre",1],ID["EPSG",8806]],PARAMETER["False northing",0,LENGTHUNIT["metre",1],ID["EPSG",8807]]],CS[Cartesian,2],AXIS["(E)",east,ORDER[1],LENGTHUNIT["metre",1]],AXIS["(N)",north,ORDER[2],LENGTHUNIT["metre",1]],USAGE[SCOPE["Navigation and medium accuracy spatial referencing."],AREA["Between 12°W and 6°W, northern hemisphere between equator and 84°N, onshore and offshore. Algeria. Côte D'Ivoire (Ivory Coast). Faroe Islands. Guinea. Ireland. Jan Mayen. Mali. Mauritania. Morocco. Portugal. Sierra Leone. Spain. United Kingdom (UK). Western Sahara."],BBOX[0,-12,84,-6]],ID["EPSG",32629]]</wkt>
      <proj4>+proj=utm +zone=29 +datum=WGS84 +units=m +no_defs</proj4>
      <srsid>3113</srsid>
      <srid>32629</srid>
      <authid>EPSG:32629</authid>
      <description>WGS 84 / UTM zone 29N</description>
      <projectionacronym>utm</projectionacronym>
      <ellipsoidacronym>EPSG:7030</ellipsoidacronym>
      <geographicflag>false</geographicflag>
    </spatialrefsys>
  </crs>
  <extent/>
</qgis>

### 2024-09-02 Data/shp/zoom_extent_map_Boat_2_comparison.qmd
resampling saved

<!DOCTYPE qgis PUBLIC 'http://mrcc.com/qgis.dtd' 'SYSTEM'>
<qgis version="3.28.11-Firenze">
  <identifier></identifier>
  <parentidentifier></parentidentifier>
  <language></language>
  <type></type>
  <title></title>
  <abstract></abstract>
  <contact>
    <name></name>
    <organization></organization>
    <position></position>
    <voice></voice>
    <fax></fax>
    <email></email>
    <role></role>
  </contact>
  <links/>
  <fees></fees>
  <encoding></encoding>
  <crs>
    <spatialrefsys nativeFormat="Wkt">
      <wkt>GEOGCRS["WGS 84",ENSEMBLE["World Geodetic System 1984 ensemble",MEMBER["World Geodetic System 1984 (Transit)"],MEMBER["World Geodetic System 1984 (G730)"],MEMBER["World Geodetic System 1984 (G873)"],MEMBER["World Geodetic System 1984 (G1150)"],MEMBER["World Geodetic System 1984 (G1674)"],MEMBER["World Geodetic System 1984 (G1762)"],MEMBER["World Geodetic System 1984 (G2139)"],ELLIPSOID["WGS 84",6378137,298.257223563,LENGTHUNIT["metre",1]],ENSEMBLEACCURACY[2.0]],PRIMEM["Greenwich",0,ANGLEUNIT["degree",0.0174532925199433]],CS[ellipsoidal,2],AXIS["geodetic latitude (Lat)",north,ORDER[1],ANGLEUNIT["degree",0.0174532925199433]],AXIS["geodetic longitude (Lon)",east,ORDER[2],ANGLEUNIT["degree",0.0174532925199433]],USAGE[SCOPE["Horizontal component of 3D system."],AREA["World."],BBOX[-90,-180,90,180]],ID["EPSG",4326]]</wkt>
      <proj4>+proj=longlat +datum=WGS84 +no_defs</proj4>
      <srsid>3452</srsid>
      <srid>4326</srid>
      <authid>EPSG:4326</authid>
      <description>WGS 84</description>
      <projectionacronym>longlat</projectionacronym>
      <ellipsoidacronym>EPSG:7030</ellipsoidacronym>
      <geographicflag>true</geographicflag>
    </spatialrefsys>
  </crs>
  <extent>
    <spatial dimensions="2" crs="EPSG:4326" minz="0" maxy="0" minx="0" maxz="0" miny="0" maxx="0"/>
    <temporal>
      <period>
        <start></start>
        <end></end>
      </period>
    </temporal>
  </extent>
</qgis>

### 2024-09-02 index.qmd
resampling saved

@@
 
+## Impact of the spatial resolution in the prediction
 ## Impact of the vegetation cover on the prediction
@@
 
-```{r Resampling}
+```{r Resampling orthos}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
 
@@
 
-a <- list.files("Data/Resampling", recursive = T) %>% 
+a <- list.files("D:/Git_repo/DISCOV-MicaSense/Data/img") %>% 
   as_tibble() %>% 
@@
   mutate(name = gsub(".*/","",path) %>% gsub(".tif","",.)) %>% 
+  # dplyr::filter(str_detect("Arz_29092022_Fl2_12m*", name))
   pull(name) %>%
@@
   "test.csv")
+```
+
+```{r gif_making}
+
+list_pred <- list.files("Data/Predictions/Resampled",full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path),
+         type = case_when(str_detect(name, "_prob.tif") ~ "Prob",
+                          T ~ "Pred")) %>% 
+  dplyr::filter(type == "Pred") %>% 
+  mutate(res =sub(".*_(\\d+)cm_.*", "\\1", name) %>% as.numeric(),
+         ortho_name  = sub("_(\\d+)cm_.*", "", name)) %>% 
+  arrange(ortho_name,res) %>% 
+  mutate(site = case_when(str_detect(ortho_name, "Aveiro_1506_Highest") ~ "Aveiro",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_1") ~ "Boat1",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_2") ~ "Boat2",
+                          str_detect(ortho_name, "NoirmoutierNorthDikeSite") ~ "NorthDike",
+                          str_detect(ortho_name, "Duer_15072022_120m") ~ "Duer",
+                          str_detect(ortho_name, "handfisher_Ortho") ~ "handfisher_Ortho",
+                          str_detect(ortho_name, "Horse_rooster") ~ "Horse_rooster",
+                          str_detect(ortho_name, "fl1_120m_handfisher_old") ~ "fl1_120m_handfisher_old",
+                          str_detect(ortho_name, "fl2_120m_handfisher_old") ~ "fl2_120m_handfisher_old",
+                          T ~ NA)) %>% 
+  dplyr::filter(!site == "handfisher_Ortho",
+                !site == "Duer")
+
+scales <- data.frame(res = unique(list_pred$res)) %>% 
+  mutate(label = case_when(res < 100 ~  paste0(res, "cm"),
+                           T ~ paste0(res / 100, "m")))
+extremes <- data.frame(
+  res = c(10, 3000),
+  label = c("10cm", "30m")
+)
+
+for(i in 1 :nrow(scales)){
+
+ point_of_interest <- scales[i,]
+
+ a <- ggplot() +
+  theme_void()+
+  # Draw the axis as a line
+  geom_segment(aes(x = 10, xend = 3000, y = 0, yend = 0), linewidth = 0.5) +
+
+  # Add the points at the extremities with labels
+  geom_text(data = extremes, aes(x = res, y = 0, label = label), vjust = -1, size = 5) +
+
+  # Add the point of interest with a label
+  geom_point(data = point_of_interest, aes(x = res, y = 0), color = "red", size = 3) +
+  geom_text(data = point_of_interest, aes(x = res, y = 0, label = label), vjust = 1.5, size = 5, color = "red") +
+
+  # Scale the x-axis from 10 to 3000 cm
+  # scale_x_continuous(limits = c(10, 3000), breaks = c(10, 100, 500, 1000, 1500, 2000, 2500, 3000)) +
+
+  # Customize the theme to remove y-axis
+  # theme_minimal() +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank()
+  )
+
+ ggsave(paste0("output/plot/scales/",point_of_interest$res,".png"),a, bg = "white",width = 1904*2, height = 132*2, unit = "px" )
+
+}
+
+for(i in 1:nrow(list_pred)){
+
+    img <- list_pred$path[i] %>% 
+      rast() 
+    names(img) <- "layer"
+
+    img <- img %>% 
+       dplyr::filter(layer != 0,
+                     layer <= 8) %>% 
+      mutate(layer = as.factor(layer))
+    # ifel(img$layer == 0 | img$layer > 8, NA, img$layer)
+
+     if(list_pred$site[i] == "Aveiro"){
+       mask <- read_sf("Data/shp/Aveiro/background_Gafanha_high.shp") %>% 
+         dplyr::filter(Type != "Land")
+     }else{
+       if(list_pred$site[i]  %in% c("Boat1","Boat2")){
+         mask <- read_sf("Data/shp/Aveiro/background_Boat.shp") %>% 
+          dplyr::filter(Type != "Land")
+       }else{
+         if(list_pred$site[i] == "NorthDike"){
+           mask <- read_sf("Data/shp/Bourgneuf/background_Dike.shp") %>% 
+            dplyr::filter(Type != "Land")
+         }else{
+           if(list_pred$site[i] == "Horse_rooster"){
+             mask <- read_sf("Data/shp/Aveiro/background_Horse_rooster.shp") %>% 
+                dplyr::filter(Type != "Land")
+           }else{
+            if(list_pred$site[i]  %in% c("fl1_120m_handfisher_old","fl2_120m_handfisher_old")){
+              mask <- read_sf("Data/shp/Bourgneuf/background_fisherman.shp") %>% 
+              dplyr::filter(Type != "Land")
+            }
+           }
+          }
+        }
+     }
+
+    low_res <-  list_pred %>% 
+      dplyr::filter(site == list_pred$site[i],
+                    res == max(res)) %>% 
+      pull(path) %>% 
+      rast()
+
+    names(low_res) <- "layer"
+
+    low_res <- low_res %>% 
+       dplyr::filter(layer != 0,
+                     layer <= 8) %>% 
+      mutate(layer = as.factor(layer))
+
+     img <- mask(img,mask)
+
+     df_layer <- img %>% 
+      as_tibble() %>% 
+      # mutate(layer = as.numeric(layer)) %>%
+      filter(!is.na(layer),
+             layer != 0 ) %>%
+      group_by(layer) %>%
+      summarise(count = n()) %>%
+      mutate(percentage = count / sum(count) * 100,
+             label = paste0(layer, " (", round(percentage, 1), "%)"))
+
+    colors <- data.frame(
+      layer = as.character(c(1:5)),
+      color = c("#DAA520","#b3ff1a","#389318","#873e23","#b3002d")
+    )
+
+    layer_counts <- df_layer %>% 
+      mutate(layer = as.character(layer)) %>%
+      # dplyr::filter(layer %in% c("3","4") ) %>% 
+      select(layer,count) %>% 
+      dplyr::filter(layer %in% c("1","2","3","4","5")) %>% 
+      left_join(colors, by = "layer")
+
+    png("pie_chart.png", width = 800, height = 800, bg = "transparent")
+
+    plotrix::pie3D(layer_counts$count,
+      # labels = layer_counts$layer,
+      explode = 0.1, # Adds space between the slices
+      # main = "3D Pie Chart of Layer",
+      col = layer_counts$color,
+      radius = 0.5,
+      theta = 2)
+
+    dev.off()
+
+    img_grob <- grid::rasterGrob(png::readPNG("pie_chart.png"), 
+                             interpolate = TRUE)
+
+    scale_grob <- grid::rasterGrob(png::readPNG(paste0("Output/plot/scales/",list_pred$res[i],".png")), 
+                             interpolate = TRUE)
+
+   plot <-  ggplot()+
+        tidyterra::geom_spatraster(data = img, 
+                                   mapping = aes(fill = layer),
+                                   maxcell = 500832*8)+
+     tidyterra::geom_spatraster(data = low_res, 
+                                   mapping = aes(fill = layer), 
+                                alpha = 0)+
+
+      coord_sf(crs = 4326)+
+      scale_fill_manual(breaks = c(1,2,3,4,5,6,7,8),
+                        values=c("#DAA520", "#b3ff1a","#389318","#873e23","#b3002d","#797a79","white","#42c9bc"),
+                        na.value = NA,
+                        name = "",
+                        labels = c("Bacillariophyceae",
+                                   "Chlorophyceae",
+                                   "Magnoliopsida",
+                                   "Phaeophyceae",
+                                   "Rhodophyceae",
+                                   "Sediment",
+                                   "Sunglint",
+                                   "Water"))+
+     theme_Bede_Map()+
+     theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
+           axis.text.y = element_text(size = 20),
+           axis.title = element_blank(),
+           legend.background = element_blank(),
+           legend.text = element_text(size = 20),
+           legend.key.size = unit(1,"cm"))
+
+   plot_limits <- ggplot_build(plot)$layout$panel_params[[1]]
+
+    x_range <- plot_limits$x_range
+    y_range <- plot_limits$y_range
+
+   if(list_pred$site[i] == "Aveiro"){
+      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.4
+      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.4
+
+      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
+      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1
+
+      plot <- plot + annotation_custom(
+          grob = img_grob,xmin = x_position_1,xmax = x_range[2], ymin = y_range[1], ymax = y_position_1)+
+        theme(legend.position = c(0.91,0.6))+
+         annotation_custom(
+          grob = scale_grob,xmin = x_position_2,xmax = x_range[2], ymin = y_range[1], ymax = y_position_2)+
+        theme(legend.position = c(0.91,0.6))
+
+   }
+
+   if(list_pred$site[i] == "Boat1"){
+      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 1.15
+      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.7
+      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.4
+      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 0.8
+
+      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
+      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1
+
+      plot <- plot + 
+        annotation_custom(grob = img_grob,
+                          xmin = x_position_1,
+                          xmax = x_position_12,
+                          ymin = y_position_1, 
+                          ymax = y_position_12)+
+         annotation_custom(grob = scale_grob,
+                           xmin = x_position_2,
+                           xmax = x_range[2],
+                           ymin = y_range[1],
+                           ymax = y_position_2)+
+        theme(legend.position = c(0.18,1))
+
+   }
+
+   if(list_pred$site[i] == "Boat2"){
+      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.9
+      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.6
+      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.6
+      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 1
+
+      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
+      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1
+
+      plot <- plot + 
+        annotation_custom(grob = img_grob,
+                          xmin = x_position_1,
+                          xmax = x_position_12,
+                          ymin = y_position_1,
+                          ymax = y_position_12)+
+         annotation_custom(grob = scale_grob,
+                           xmin = x_position_2,
+                           xmax = x_range[2],
+                           ymin = y_range[1],
+                           ymax = y_position_2)+
+        theme(legend.position = c(0.18,1))
+
+   }
+   if(list_pred$site[i] == "NorthDike"){
+      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.9
+      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.6
+      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.6
+      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 1
+
+      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
+      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1
+
+      plot <- plot + 
+        annotation_custom(grob = img_grob,
+                          xmin = x_position_1,
+                          xmax = x_position_12,
+                          ymin = y_position_1,
+                          ymax = y_position_12)+
+         annotation_custom(grob = scale_grob,
+                           xmin = x_position_2,
+                           xmax = x_range[2],
+                           ymin = y_range[1],
+                           ymax = y_position_2)+
+        theme(legend.position = c(0.18,1))
+
+   }
+
+    # plot
+    ggsave(paste0("Output/Resampling/",gsub(".tif",".png",list_pred$name[i])), plot, height = 1125*4, width = 1320*4, units = "px")
+
+}
+```
+
+```{r resampling validation data}
 

### 2024-09-19 index.qmd
resampling saved
updates

@@
 
-# res_to_resample <- c(10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,200,300,400,500,600,700,800,900,1000,1500,2000,2500,3000)
+res_to_resample <- c(10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,200,300,400,500,600,700,800,900,1000,1500,2000,2500,3000)
 res_to_resample <- c(2000)
@@
 ```{r gif_making}
-
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
 list_pred <- list.files("Data/Predictions/Resampled",full.names = T) %>% 
@@
 ```{r resampling validation data}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
+
+library(MapRs)
+
+img_list <- list.files("Data/Predictions/RAW/", pattern = ".tif", full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path),
+         type = case_when(str_detect(name,"Probs") ~ "Probs",
+                          TRUE ~ "Pred"),
+         site = case_when(str_detect(name,"Boat1") ~ "Boat1",
+                          str_detect(name,"Boat2") ~ "Boat2",
+                          str_detect(name,"Gafanha_high") ~ "AveiroHigh",
+                          str_detect(name,"Duer") ~ "Duer",
+                          str_detect(name,"Gafanha_Low") ~ "AveiroLow",
+                          str_detect(name,"NorthDike") ~ "NorthDike"),
+         filtered = case_when(str_detect(name,"_7") ~ T,
+                              T ~ F),
+         UTM_zone = case_when(str_detect(path, "NorthDike") ~ 32630,
+                              str_detect(path, "Duer") ~ 32630,
+                              TRUE ~ 32629)) %>% 
+  dplyr::filter(site != "AveiroLow",
+                type == "Pred",
+                filtered == F,
+                site == "NorthDike")
+
+# res_to_resample <- c(10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,200,300,400,500,600,700,800,900,1000,1500,2000,2500,3000)
+res_to_resample <- c(3000)
+
+for(i in 1:nrow(img_list)){
+
+  img <- img_list %>% 
+    dplyr::filter(path == img_list$path[i]) %>% 
+    pull(path) %>% 
+    rast()%>% 
+    terra::project(paste0("EPSG:", img_list$UTM_zone[i]), thread = T, method = "near")
+
+    for(ii in 1:length(res_to_resample)){
+
+      new_res <- res_to_resample[ii]/100
+
+    r_template <- rast(ext(img), resolution = new_res, crs = crs(img))
+    r_resampled <- terra::resample(img, r_template, method="mode", threads = T)%>% 
+      terra::project("EPSG:4326", thread = T, method = "near")
+
+    if(i == 1){
+      if(!dir.exists(paste0("Data/Validation/Prediction_resampling/",res_to_resample[ii],"cm"))){
+       dir.create(paste0("Data/Validation/Prediction_resampling/",res_to_resample[ii],"cm"), recursive = T) 
+      }
+    }
+    writeRaster(r_resampled, paste0("Data/Validation/Prediction_resampling/",res_to_resample[ii],"cm/",gsub(".tif",paste0("_",res_to_resample[ii],"cm.tif"),img_list$name[i])),overwrite = T)
+    }
+  }
+```
+
+```{r Comparison resampled data}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
+
+df_valid <- list.files("Data/Validation/Prediction_resampling",pattern = ".tif",recursive = T, full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path)) %>% 
+  # dplyr::filter(type == "Pred") %>% 
+  mutate(res =sub(".*_(\\d+)cm.*", "\\1", name) %>% as.numeric()) %>% 
+  arrange(name,res) %>% 
+  mutate(site = case_when(str_detect(name, "Gafanha_high") ~ "Aveiro",
+                          str_detect(name, "Boat1") ~ "Boat1",
+                          str_detect(name, "Boat2") ~ "Boat2",
+                          str_detect(name, "NorthDike") ~ "NorthDike",
+                          str_detect(name, "Duer_high") ~ "Duer",
+                          str_detect(name, "handfisher_Ortho") ~ "handfisher_Ortho",
+                          T ~ NA),
+         type = "validation")
+
+df_resampled <- list.files("Data/Predictions/Resampled",full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path),
+         type = case_when(str_detect(name, "_prob.tif") ~ "Prob",
+                          T ~ "Pred")) %>% 
+  dplyr::filter(type == "Pred") %>% 
+  mutate(res =sub(".*_(\\d+)cm_.*", "\\1", name) %>% as.numeric(),
+         ortho_name  = sub("_(\\d+)cm_.*", "", name)) %>% 
+  arrange(ortho_name,res) %>% 
+  mutate(site = case_when(str_detect(ortho_name, "Aveiro_1506_Highest") ~ "Aveiro",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_1") ~ "Boat1",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_2") ~ "Boat2",
+                          str_detect(ortho_name, "NoirmoutierNorthDikeSite") ~ "NorthDike",
+                          str_detect(ortho_name, "Duer_15072022_120m") ~ "Duer",
+                          str_detect(ortho_name, "handfisher_Ortho") ~ "handfisher_Ortho",
+                          str_detect(ortho_name, "Horse_rooster") ~ "Horse_rooster",
+                          str_detect(ortho_name, "fl1_120m_handfisher_old") ~ "fl1_120m_handfisher_old",
+                          str_detect(ortho_name, "fl2_120m_handfisher_old") ~ "fl2_120m_handfisher_old",
+                          T ~ NA)) %>% 
+  dplyr::filter(!site == "handfisher_Ortho",
+                !site == "Duer") %>% 
+  dplyr::select(-ortho_name)
+
+df <- df_valid %>% 
+  bind_rows(df_resampled) %>% 
+  dplyr::filter(site %in% c("Aveiro","Boat1","Boat2","NorthDike")) %>% 
+  # dplyr::filter(site == "Aveiro") %>% 
+  dplyr::select(-name) %>% 
+  pivot_wider(names_from = type, values_from = path)
+
+for(i in 1:nrow(df)){
+
+  print(i)
+
+  img <- rast(c(df$validation[i],df$Pred[i]))
+
+  names(img) <- c("true","pred")
+
+  df_img <- img %>%  
+    as.data.frame() %>% 
+    dplyr::filter(!true == 0,
+                  !pred == 0) %>% 
+    dplyr::mutate(res = df$res[i],
+                  site = df$site[i])
+
+  if(i == 1){
+    df_compare <- df_img
+  }else{
+    df_compare <- rbind(df_compare,df_img)
+  }
+}
+
+validation = df_compare %>% 
+  mutate(same = case_when(pred == true ~ T,
+                          T ~ F))
+
+total <- validation %>% 
+  lazy_dt() %>% 
+  group_by(res,true) %>% 
+  dplyr::summarise(agreed = sum(same, na.rm = T),
+          n_obs = n()) %>% 
+  # ungroup() %>% 
+  mutate(prop = agreed/n_obs) %>% 
+  as_tibble() %>% 
+  dplyr::filter(true != 1) %>% 
+  mutate(true_fct = as.factor(true),
+         area = res*res)
+
+total %>% 
+  ggplot(aes(x = res, y = prop, group = true, color = as.factor(true)))+
+  geom_line()
+  # scale_x_log10()
+
+glm_res_true <- glm(prop ~ area * true_fct , data = total) 
+glm_res <- glm(prop ~ area, data = total, family = "")
+
+summary(glm_res)
+
+Utilities.Package::Model_Check(glm_res)
+
+NewData<-expand_grid(area=unique(total$area),
+                    true_fct=unique(total$true_fct))
+
+pred <- predict(glm_res_true, NewData, se.fit = T)
+
+NewData <- NewData %>% 
+  mutate(fit = pred$fit*100,
+         se = pred$se.fit*100, 
+         res = sqrt(area)/100)
+
+  cols_fill <- c("1" = "#DAA520",
+                 "2" = "#b3ff1a",
+                 "3" = "#389318",
+                 "4" = "#873e23",
+                 "5" = "#b3002d",
+                 "6" = "#70543e",
+                 "7" = 'grey',
+                 "8" = "#42c9bc")
+plot <- ggplot(NewData)+
+  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
+                  color = true_fct, group = true_fct, fill = true_fct
+                  ), alpha = 0.2)+
+  geom_line(aes(x = res, y = fit,
+                color = true_fct, group = true_fct
+                ))+
+  # ylim(0,1)+
+      scale_fill_manual(name = NULL,
+                        values = cols_fill,
+                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
+    scale_color_manual(name = NULL,
+                      values = cols_fill,
+                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
+  theme_Bede()+
+  xlab("Resolution (m)") +
+  ylab("Agreement")+
+  theme(axis.title = element_text(size = 20),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        legend.text = element_text(size = 15),
+        legend.key.size = unit(1, "cm"))
+
+ggsave("Output/plot/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")
+
+#### Area
+
+test <-  validation %>% 
+  lazy_dt() %>% 
+  pivot_longer(c(true, pred), names_to = "source", values_to = "class") %>% 
+  group_by(res,class,source) %>% 
+  summarise(class_area = n()*(res*res)/(100*100)) %>% 
+  as_tibble() %>% 
+  pivot_wider(names_from = source, values_from = class_area) %>% 
+  mutate(agreement = (1-abs(((pred-true)/(pred+true))))*100,
+         # agreement1 = abs(pred-true)/max(pred,true)
+         class = as.factor(class))
+
+test %>%
+  dplyr::filter(class != 1) %>%
+  ggplot(aes(x = res, y =agreement))+
+  geom_line(aes(color = class, group = class))
+
+# test %>%
+#   pivot_longer(c(pred,true), names_to = "dataset", values_to = "values") %>% 
+#   dplyr::filter(class != 1) %>%
+#     ggplot(aes(x = res, y = values, color = dataset, group = dataset))+
+#   geom_line()+
+#   facet_wrap(~ class, scales = "free")
+
+glm_res_area <- glm(agreement ~ res * class , data = test)
+
+summary(glm_res_area)
+
+Utilities.Package::Model_Check(glm_res_area)
+
+NewData<-expand_grid(res=unique(test$res),
+                    class=unique(test$class))
+
+pred <- predict(glm_res_area, NewData, se.fit = T)
+
+NewData <- NewData %>% 
+  mutate(fit = pred$fit,
+         se = pred$se.fit)
+
+NewData %>% 
+  dplyr::filter(class != 1) %>% 
+ggplot()+
+  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
+                  color = class, group = class, fill = class
+                  ), alpha = 0.2)+
+  geom_line(aes(x = res, y = fit,
+                color = class, group = class
+                ))+
+  # ylim(0,1)+
+      scale_fill_manual(name = NULL,
+                        values = cols_fill,
+                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
+    scale_color_manual(name = NULL,
+                      values = cols_fill,
+                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
+  theme_Bede()+
+  xlab("Resolution (m)") +
+  ylab("Agreement")+
+  theme(axis.title = element_text(size = 20),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        legend.text = element_text(size = 15),
+        legend.key.size = unit(1, "cm"))
 

### 2024-09-24 index.qmd
add updates

@@
 library(terra)
+library(MapRs)
 
@@
 
+if(file.exists("Data/Resampled_saved_data_total.csv")){
+
+  total <- read.csv( "Data/Resampled_saved_data_total.csv")
+
+}else{
+
   for(i in 1:nrow(df)){
@@
   total <- validation %>% 
-  lazy_dt() %>% 
+  dtplyr::lazy_dt() %>% 
   group_by(res,true) %>% 
@@
   as_tibble() %>% 
-  dplyr::filter(true != 1) %>% 
+  dplyr::filter(true != 1,
+                true != 6,
+                true != 7,
+                true != 8) %>% 
   mutate(true_fct = as.factor(true),
@@
 
+  write.csv(total, "Data/Resampled_saved_data_total.csv", row.names = F)
+}
+
+# reframing <- total %>% 
+#   group_by(true_fct) %>% 
+#   dplyr::filter(res == 10) %>% 
+#   ungroup() %>% 
+#   mutate(diff = max(prop)-prop) %>% 
+#   dplyr::select(true_fct,diff)
+#   
+# 
+# total <- total %>% 
+#   left_join(reframing, by = "true_fct") %>% 
+#   mutate(prop = prop + diff) %>% 
+#   dplyr::select(-diff)
+
 total %>% 
-  ggplot(aes(x = res, y = prop, group = true, color = as.factor(true)))+
-  geom_line()
-  # scale_x_log10()
-
-glm_res_true <- glm(prop ~ area * true_fct , data = total) 
-glm_res <- glm(prop ~ area, data = total, family = "")
-
-summary(glm_res)
-
-Utilities.Package::Model_Check(glm_res)
-
-NewData<-expand_grid(area=unique(total$area),
-                    true_fct=unique(total$true_fct))
-
-pred <- predict(glm_res_true, NewData, se.fit = T)
+  ggplot(aes(x = res, y = prop, group = true, color =true_fct))+
+  geom_line()+
+  theme_Bede_Map()
+
+# glm_res_true <- glm(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit")) 
+glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
+
+summary(glm_res_true)
+
+Utilities.Package::Model_Check(glm_res_true)
+
+NewData<-expand_grid(res=unique(total$res),
+                    true_fct=unique(total$true_fct),
+                    area = res*res)
+
+pred <- predict(glm_res_true, NewData, se.fit = T, type = "link")
 
@@
          se = pred$se.fit*100,
-         res = sqrt(area)/100)
+         true_fct=as.factor(true_fct))
 
@@
                  "8" = "#42c9bc")
-plot <- ggplot(NewData)+
-  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
+
+(plot <- ggplot(NewData)+
+  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                   color = true_fct, group = true_fct, fill = true_fct
                   ), alpha = 0.2)+
-  geom_line(aes(x = res, y = fit,
+  geom_line(aes(x = sqrt(area), y = fit,
                 color = true_fct, group = true_fct
@@
 
+    # scale_x_log10()
+
+  )
+
 ggsave("Output/plot/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")
-
-#### Area
-
-test <-  validation %>% 
-  lazy_dt() %>% 
-  pivot_longer(c(true, pred), names_to = "source", values_to = "class") %>% 
-  group_by(res,class,source) %>% 
-  summarise(class_area = n()*(res*res)/(100*100)) %>% 
-  as_tibble() %>% 
-  pivot_wider(names_from = source, values_from = class_area) %>% 
-  mutate(agreement = (1-abs(((pred-true)/(pred+true))))*100,
-         # agreement1 = abs(pred-true)/max(pred,true)
-         class = as.factor(class))
-
-test %>%
-  dplyr::filter(class != 1) %>%
-  ggplot(aes(x = res, y =agreement))+
-  geom_line(aes(color = class, group = class))
-
-# test %>%
-#   pivot_longer(c(pred,true), names_to = "dataset", values_to = "values") %>% 
-#   dplyr::filter(class != 1) %>%
-#     ggplot(aes(x = res, y = values, color = dataset, group = dataset))+
-#   geom_line()+
-#   facet_wrap(~ class, scales = "free")
-
-glm_res_area <- glm(agreement ~ res * class , data = test)
-
-summary(glm_res_area)
-
-Utilities.Package::Model_Check(glm_res_area)
-
-NewData<-expand_grid(res=unique(test$res),
-                    class=unique(test$class))
-
-pred <- predict(glm_res_area, NewData, se.fit = T)
-
-NewData <- NewData %>% 
-  mutate(fit = pred$fit,
-         se = pred$se.fit)
-
-NewData %>% 
-  dplyr::filter(class != 1) %>% 
-ggplot()+
-  geom_ribbon(aes(x = res, y = fit, ymax = fit+se, ymin = fit-se, 
-                  color = class, group = class, fill = class
-                  ), alpha = 0.2)+
-  geom_line(aes(x = res, y = fit,
-                color = class, group = class
-                ))+
-  # ylim(0,1)+
-      scale_fill_manual(name = NULL,
-                        values = cols_fill,
-                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
-    scale_color_manual(name = NULL,
-                      values = cols_fill,
-                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
-  theme_Bede()+
-  xlab("Resolution (m)") +
-  ylab("Agreement")+
-  theme(axis.title = element_text(size = 20),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        legend.text = element_text(size = 15),
-        legend.key.size = unit(1, "cm"))
-
 ```

### 2024-09-26 docs/_tex/index.tex
add figures

@@
 
+\subsection{Impact of the spatial resolution in the
+prediction}\label{impact-of-the-spatial-resolution-in-the-prediction}
+
 \subsection{Impact of the vegetation cover on the
@@
 Magnoliopsida.
+
+\subsection{Effect of the spatial resolution on the
+prediction}\label{effect-of-the-spatial-resolution-on-the-prediction}
+
+\phantomsection\label{cell-fig-pixelsize}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/High_res/resolution_plot.png}
+
+}
+
+\caption{\label{fig-pixelsize}Coucou}
+
+\end{figure}%
 

### 2024-09-26 index.qmd
add figures

@@
 
-Drones (Unmanned Aerial Vehicles – UAVs) can potentially fill the data gaps left by satellite RS and *in situ* measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
+Drones (Unmanned Aerial Vehicles -- UAVs) can potentially fill the data gaps left by satellite RS and *in situ* measurements, due to their ability to provide spatially-explicit observations at very high spatial resolutions (pixel size from mm to cm) while capturing data at multi-spectral resolution [@fairley2022drone ; @oh2017use].
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
@@
 ## Impact of the spatial resolution in the prediction
+
 ## Impact of the vegetation cover on the prediction
@@
 (plot <- ggplot(NewData)+
-  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
+  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
                   color = true_fct, group = true_fct, fill = true_fct
                   ), alpha = 0.2)+
-  geom_line(aes(x = sqrt(area), y = fit,
+  geom_line(aes(x = sqrt(area)/100, y = fit,
                 color = true_fct, group = true_fct
@@
 
-ggsave("Output/plot/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")
+ggsave("Figures/High_res/resolution_plot.png", plot, bg = "white", height = 803*3, width = 1184*3, units = "px")
+```
+
+```{r Pixel size Plot}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Coucou
+#| label: fig-pixelsize
+#| fig-width: 10
+#| fig-height: 7
+#| out-width: "90%"
+
+knitr::include_graphics("Figures/High_res/resolution_plot.png")
 ```

### 2024-09-26 index.qmd
add updates

@@
   as_tibble() %>% 
-  dplyr::filter(true != 1,
-                true != 6,
-                true != 7,
-                true != 8) %>% 
+  # dplyr::filter(true != 1,
+  #               true != 6,
+  #               true != 7,
+  #               true != 8) %>% 
   mutate(true_fct = as.factor(true),
@@
 
-# glm_res_true <- glm(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit")) 
-glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
+glm_res_true <- glm(prop ~ area*true_fct , data = total)
+# glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
+
+a <- total %>% 
+  group_by(res, true) %>% 
+  reframe(mean = mean(prop))
 
@@
 
-NewData<-expand_grid(res=unique(total$res),
-                    true_fct=unique(total$true_fct),
-                    area = res*res)
+NewData<-expand_grid(area=unique(total$area),
+                    true_fct=unique(total$true_fct))
 
@@
          se = pred$se.fit*100,
-         true_fct=as.factor(true_fct))
+         true_fct=(true_fct))
 
@@
 (plot <- ggplot(NewData)+
-  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
+  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                   color = true_fct, group = true_fct, fill = true_fct
                   ), alpha = 0.2)+
-  geom_line(aes(x = sqrt(area)/100, y = fit,
+  geom_line(aes(x = sqrt(area), y = fit,
                 color = true_fct, group = true_fct
                 ))+
-  # ylim(0,1)+
       scale_fill_manual(name = NULL,
@@
         legend.text = element_text(size = 15),
-        legend.key.size = unit(1, "cm"))
+        legend.key.size = unit(1, "cm")
+          )
 

### 2024-09-27 index.qmd
add updates

@@
   write.csv(total, "Data/Resampled_saved_data_total.csv", row.names = F)
+
 }
@@
 #   dplyr::select(true_fct,diff)
-#   
-# 
+
 # total <- total %>% 
@@
 #   dplyr::select(-diff)
+ # validation <- read.csv( "Data/Resampled_saved_data.csv")
+
+total <- validation %>% 
+  dtplyr::lazy_dt() %>% 
+  group_by(res,true) %>% 
+  dplyr::summarise(agreed = sum(same, na.rm = T),
+          n_obs = n()) %>% 
+  # ungroup() %>% 
+  mutate(prop = agreed/n_obs) %>% 
+  as_tibble() %>% 
+  # dplyr::filter(true != 1,
+  #               true != 6,
+  #               true != 7,
+  #               true != 8) %>% 
+  mutate(true_fct = as.factor(true),
+         area = res*res)
 
@@
 
-(plot <- ggplot(NewData)+
+(plot <-   NewData  %>% 
+  dplyr::filter(true_fct != 1,
+                true_fct != 6,
+                true_fct != 7,
+                true_fct != 8) %>%
+ggplot()+
   geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 

### 2024-09-27 index.qmd
add results

--- 2024-09-26 index.qmd
@@
 
+To assess the impact of spatial resolution on the model's output, the reflectance of each flight's orthomosaic was spatially resampled using the average method from the Terra package in R.
+DISCOV was then applied to these resampled rasters.
+The results were compared to the original model predictions, which were resampled using the mode method from the Terra package in R.
+For each resolution and each class of the model, an agreement percentage was obtained, where a score of 100 indicates that all pixels in the two products are identical, and a score of 0 indicates that all pixels are different.
+
+We used a Generalized Linear Model (GLM) with a Gaussian family and an identity link function to investigate the relationship between pixel resolution, vegetation class, and their interaction on the response variable, the agreement.
+The formula for the model was:
+
+$$
+Agreement \sim  Resolution \times VegetationClass
+$$ {#eq-gam}
+
 ## Impact of the vegetation cover on the prediction
@@
 
-  total <- read.csv( "Data/Resampled_saved_data_total.csv")
+  total <- read.csv( "Data/Resampled_saved_data_total.csv") %>% 
+    mutate(true_fct = as.factor(true))
 
@@
 
+# validation <- read.csv( "Data/Resampled_saved_data.csv")
+
 # reframing <- total %>% 
@@
 
+@fig-pixelsize shows an effect of the pixel size on the agreement between the two products.
+The highest resolution in which the resampling has been performed is 10 cm.
+At this resolution, the agreement has already decreased from 78% (red algae) to 94% (seagrass), depending on the class.
+As pixel size increases, the agreement between the products declines steadily for all classes.
+This decline is most pronounced for green algae, which experiences the sharpest drop in agreement as pixel size increases beyond 10 m, reaching below 0% at a pixel size of 30 m.
+Seagrass maintain higher levels of agreement at coarser resolutions, although a clear decline is still observed, with seagrasses dropping from over 94% at 10 cm to around 88% at 30 m.
+Brown algae and red algae show a more moderate decline compared to red algae, with agreement levels remaining around 62% and 40%, respectively, at 30 m resolution.
+
 ```{r Pixel size Plot}
@@
 ```
+
+The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($$\beta = -1.0334 \times 10^{-8}, p < 0.001$$).
+This indicates that as pixel resolution increases, the proportion of the response variable decreases.
+
+The vegetation classes also exhibited distinct effects on the agreement.
+Magnoliopsida showed a significant positive effect ($$\beta = 0.1202, p < 0.001$$), suggesting that this class was associated with a higher agreement.
 

### 2024-09-27 docs/_tex/index.tex
add results

@@
 
+To assess the impact of spatial resolution on the model's output, the
+reflectance of each flight's orthomosaic was spatially resampled using
+the average method from the Terra package in R. DISCOV was then applied
+to these resampled rasters. The results were compared to the original
+model predictions, which were resampled using the mode method from the
+Terra package in R. For each resolution and each class of the model, an
+agreement percentage was obtained, where a score of 100 indicates that
+all pixels in the two products are identical, and a score of 0 indicates
+that all pixels are different.
+
+We used a Generalized Linear Model (GLM) with a Gaussian family and an
+identity link function to investigate the relationship between pixel
+resolution, vegetation class, and their interaction on the response
+variable, the agreement. The formula for the model was:
+
+\begin{equation}\phantomsection\label{eq-gam}{
+Agreement \sim  Resolution \times VegetationClass
+}\end{equation}
+
 \subsection{Impact of the vegetation cover on the
@@
 
+Figure~\ref{fig-pixelsize} shows an effect of the pixel size on the
+agreement between the two products. The highest resolution in which the
+resampling has been performed is 10 cm. At this resolution, the
+agreement has already decreased from 78\% (red algae) to 94\%
+(seagrass), depending on the class. As pixel size increases, the
+agreement between the products declines steadily for all classes. This
+decline is most pronounced for green algae, which experiences the
+sharpest drop in agreement as pixel size increases beyond 10 m, reaching
+below 0\% at a pixel size of 30 m. Seagrass maintain higher levels of
+agreement at coarser resolutions, although a clear decline is still
+observed, with seagrasses dropping from over 94\% at 10 cm to around
+88\% at 30 m. Brown algae and red algae show a more moderate decline
+compared to red algae, with agreement levels remaining around 62\% and
+40\%, respectively, at 30 m resolution.
+
 \phantomsection\label{cell-fig-pixelsize}
@@
 \end{figure}%
+
+The Generalized Linear Model (GLM) analysis revealed a significant
+effect of pixel resolution on the agreement, with a negative
+relationship (\[\beta = -1.0334 \times 10^{-8}, p < 0.001\]). This
+indicates that as pixel resolution increases, the proportion of the
+response variable decreases.
+
+The vegetation classes also exhibited distinct effects on the agreement.
+Magnoliopsida showed a significant positive effect
+(\[\beta = 0.1202, p < 0.001\]), suggesting that this class was
+associated with a higher agreement.
 

### 2024-09-27 docs/_tex/index.tex
add updates

@@
 between the land and oceans \citep{unsworth2022}. Seagrass meadows
-provide a myriad of ecosystem services to humanity, including carbon
-sequestration, oxygen production, protection against sea-level rise and
-coastline erosion, and mitigation of eutrophication \citetext{\citealp[
+provide a myriad of ecosystem services, including carbon sequestration,
+oxygen production, protection against sea-level rise and coastline
+erosion, and mitigation of eutrophication \citetext{\citealp[
 ]{unsworth2022}; \citealp{sousa2019blue}}. They serve as vital habitats
@@
 applicability across diverse sites without a loss of prediction
-accuracy.
+accuracy. In addition, the results obtained from drone-based
+multispectral remote sensing will be spatially degraded to satellite
+resolutions, and the effect of this resolution on the model's
+predictions will be investigated, providing insights for coastal habitat
+mapping using satellites.
 
@@
 Seven study sites distributed between France and Portugal were selected
-for their relatively extensive intertidal seagrass beds. Two sites were
-located in the Gulf of Morbihan (Figure~\ref{fig-map} A), France
-(47.5791°N, 2.8018°W). This gulf covers an area of 115 km² and is only
-connected to the sea through a 900 m wide channel. A total of 53 small
-islands are scattered across the gulf leading to 250 km of shorelines.
-Patchy seagrass meadows can be found on many of these islands. One of
-the sites within the gulf was on one its islands (Arz) and the other was
-located further south on a mainland beach area (Duer). Two other sites
-were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W). This is a
-340 km² semi-enclosed macrotidal bay, protected from waves by
-Noirmoutier Island. Bourgneuf bay hosts a large intertidal seagrass
-meadow of about 6 km² \citep{ZOFFOLI2020112020}. Within this meadow, the
-sites observed by drones (L'Epine and Barbatre, Figure~\ref{fig-map} B)
-contained monospecific beds of \emph{Nanozostera noltei} (dwarf
-eelgrass, syn. \emph{Zostera noltei}) with very little mixing with other
-macrophytes. Three sites were surveyed in the Ria de Aveiro Coastal
-Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of this lagoon is
-\textasciitilde83 km² (at low tide) with many narrow channels, large
-salt marshes and many mudflats that uncover at low tide
+for their extensive intertidal seagrass beds. Two sites were located in
+the Gulf of Morbihan (Figure~\ref{fig-map} A), France (47.5791°N,
+2.8018°W). This gulf covers an area of 115 km² and is only connected to
+the sea through a 900 m wide channel. A total of 53 small islands are
+scattered across the gulf leading to 250 km of shorelines. Patchy
+seagrass meadows can be found on many of these islands. One of the sites
+within the gulf was on one its islands (Arz) and the other was located
+further south on a mainland beach area (Duer). The Gulf of Morbihan is a
+Natura 2000 site and a Regional Protected Area due to its rich
+biodiversity, including its seagrass meadows, and is also classified as
+a RAMSAR site, which highlights its significance as a wetland of
+international importance. Two other sites were located in Bourgneuf Bay,
+France (46.9849°N, 2.1488°W). This is a 340 km² semi-enclosed macrotidal
+bay, protected from waves by Noirmoutier Island. Bourgneuf bay hosts a
+large intertidal seagrass meadow of about 6 km²
+\citep{ZOFFOLI2020112020}. Within this meadow, the sites observed by
+drones (L'Epine and Barbatre, Figure~\ref{fig-map} B) contained
+monospecific beds of \emph{Nanozostera noltei} (dwarf eelgrass, syn.
+\emph{Zostera noltei}) with very little mixing with other macrophytes.
+Bourgneuf Bay is also part of the Natura 2000 network and serves as a
+RAMSAR site due to its critical habitat for migratory bird species and
+its extensive seagrass meadows. Three sites were surveyed in the Ria de
+Aveiro Coastal Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of
+this lagoon is \textasciitilde83 km² (at low tide) with many narrow
+channels, large salt marshes and many mudflats that uncover at low tide
 \citep{sousa2017blue}. It is connected to the open sea through a single
@@
 vegetation, where patches of seagrass intermingle with red, brown, and
-green macroalgae.
+green macroalgae. The Aveiro Lagoon, like the other study areas, is a
+Natura 2000 site and a RAMSAR wetland, recognized for its rich mosaic of
+habitats and importance for biodiversity, including migratory bird
+species and intertidal vegetation.
 
@@
 eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red
-macroalgae) (Figure~\ref{fig-vegetation}). Pictures of each quadrat were
-uploaded online to the Global Biodiversity Information Facility (GBIF)
-platform \citep{BedeGbif}, a public open portal to store and share
-biodiversity data. Each photograph was also processed to estimate the
-percent cover of each type of vegetation using an image processing
-software \citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
+macroalgae) (Figure~\ref{fig-vegetation}). Only homogeneous vegetation
+patches extending over several meters were selected as ground control
+points. Pictures of each quadrat were uploaded online to the Global
+Biodiversity Information Facility (GBIF) platform \citep{BedeGbif}, a
+public open portal to store and share biodiversity data. Each photograph
+was also processed to estimate the percent cover of each type of
+vegetation using an image processing software
+\citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
 signatures of each vegetation class were recorded using an ASD FieldSpec
@@
 
-The spectral similarities of the reflectance signatures between
-intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make
-their discrimination challenging using simple classification algorithms
-(Figure~\ref{fig-vegetation} F). To overcome this challenge, a deep
-learning classification method was trained, validated, and applied to
-each drone flight (Figure~\ref{fig-workflow}).
+The spectral similarities of the reflectance signatures at the spectral
+resolution of the micasense senor between intertidal green macrophytes
+(Magnoliopsida and Chlorophyceae) make their discrimination challenging
+using simple classification algorithms (Figure~\ref{fig-vegetation} F).
+To overcome this challenge, a deep learning classification method was
+trained, validated, and applied to each drone flight
+(Figure~\ref{fig-workflow}).
 
@@
 Rhodophyceae. Only low-altitude flights (Table~\ref{tbl-flights}) were
-used for training because their 8 mm spatial resolution allowied to
-avoid spectral sub-pixel mixing and to accurately identify vegetation
-classes. More than 418,000 pixels at 8 mm resolution from the 3 training
-flights were used to train the model (Table~\ref{tbl-validationPX}).
-Twenty one variables were used by the model as predictors: the ten raw
-spectral bands of the Micasense RedEdge Dual MX multispectral camera
-(ranging from 444 nm to 840 nm), the same ten spectral bands
-standardized using a min/max transformation (Equation~\ref{eq-std} ;
-\citep{Cao2017}) and the Normalized difference vegetation index (NDVI,
-Equation~\ref{eq-ndvi}). Standardisation of spectral bands is commonly
-used to eliminate the scaling differences between spectra and to limit
-the effect of biomass on the spectra shape \citetext{\citealp[
+used for training because their 8 mm spatial resolution allowed to avoid
+spectral sub-pixel mixing and to accurately identify vegetation classes.
+More than 418,000 pixels at 8 mm resolution from the 3 training flights
+were used to train the model (Table~\ref{tbl-validationPX}). Twenty one
+variables were used by the model as predictors: the ten raw spectral
+bands of the Micasense RedEdge Dual MX multispectral camera (ranging
+from 444 nm to 840 nm), the same ten spectral bands standardized using a
+min/max transformation (Equation~\ref{eq-std} ; \citep{Cao2017}) and the
+Normalized difference vegetation index (NDVI, Equation~\ref{eq-ndvi}).
+Standardisation of spectral bands is commonly used to eliminate the
+scaling differences between spectra and to limit the effect of biomass
+on the spectra shape \citetext{\citealp[
 ]{Douay2022}; \citealp{Davies2023}}.
@@
 layers and have a total of 26 054 trainable parameters. Parameters have
-been find tune using 12 epoch to minimize the error rate.
+been fine tuned using 12 epoch to minimize the error rate.
 
@@
 The model was applied to all flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover
-collected during each flight was used to assess the model accuracy.
-These images were used to construct a validation dataset indicating the
-presence or absence of each class. Additionally to the quadrat-based
-validation dataset, polygons of each class were photo interpreted in
-order to increase the number of pixels of the validation dataset.A total
-of 536,000 pixels were used to validate the Neural Network classifier.
-The sites with the lowest and highest number of validation data were
-Gafanha Low (17316 pixels) and Marinha Lanzarote (159713 pixels),
-respectively.A confusion matrix, along with precision metrics such as
-global accuracy, sensitivity, specificity, and Kappa coefficient, was
-generated for each sites. All validation matrices were then aggregated
-to create an overall matrix .
+\emph{In situ} information on georeferenced class type and percent
+cover, acquired at over homogeneous vegetation patches at the same time
+as drone flights was used to assess the model accuracy. These images
+were used to construct a validation dataset indicating the presence or
+absence of each class. Additionally to the quadrat-based validation
+dataset, polygons of each class were photo interpreted in order to
+increase the number of pixels of the validation dataset.A total of
+536,000 pixels were used to validate the Neural Network classifier. The
+sites with the lowest and highest number of validation data were Gafanha
+Low (17316 pixels) and Marinha Lanzarote (159713 pixels), respectively.
+A confusion matrix, along with precision metrics such as global
+accuracy, sensitivity, specificity, and Kappa coefficient, was generated
+for each sites. All validation matrices were then aggregated to create
+an overall matrix .
 
@@
 
-\subsection{Impact of the vegetation cover on the
-prediction}\label{impact-of-the-vegetation-cover-on-the-prediction}
+\subsection{Impact of mixed vegetation cover on the
+prediction}\label{impact-of-mixed-vegetation-cover-on-the-prediction}
 
 The key aspect of the workflow adopted in the present study is the
-mapping of specific areas at two different altitudes (12m and 120m),
-resulting in two distinct resolutions for the same area (8mm and 80mm).
-The predictions made on the high-resolution flight can be used to
-estimate the cover (percentage, \%) of each vegetation class for every
-pixel of the lower resolution flight. Consequently, for each pixel of
-the high-altitude flights, the cover (\%) of each vegetation class were
-obtained, and a kernel density plot was generated. This plot provides a
-visual representation of the behavior of the model in different
-vegetation percent cover scenarios.
+mapping at two different altitudes (12 m and 120 m), resulting in two
+distinct resolutions for the same area (8 mm and 80 mm). The
+high-resolution flight was used to estimate the sub-pixel composition
+for each pixel of the lower-resolution flight. Consequently, within each
+pixel of the high-altitude flights, the contribution of each vegetation
+class (\% cover) was obtained, and a kernel density plot was generated.
+This plot provided a visual representation of the model's behavior in
+mixed vegetation scenarios. It helps to understand the minimum
+vegetation cover of a given class within a pixel necessary for the model
+to confidently predict that class.
 
@@
 
+\subsection{Reflectance comparison between the two different
+altitudes}\label{reflectance-comparison-between-the-two-different-altitudes}
+
+In this study, drone flights were conducted at two different altitudes
+(12 m and 120 m) to construct the neural network model. At the sites
+where the flights at both altitudes overlapped, reflectance was
+compared. Overall there was a good agreement between the two altitudes
+(RMSE: 0.027 ; Figure~\ref{fig-CompareRef}).
+
+\phantomsection\label{cell-fig-CompareRef}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
+
+}
+
+\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
+both low-altitude and high-altitude flights over a common area. The
+black dashed line represents a 1 to 1 relationship. Left (A) plots raw
+data and right (B) plots standardized data (Equation~\ref{eq-std}).}
+
+\end{figure}%
+
+There was a slight underestimation for raw reflectance values in the
+high-altitude flight, particularly for higher reflectance values
+(Figure~\ref{fig-CompareRef} A). Since both flights were conducted over
+vegetation areas, the highest reflectance values correspond to the
+infrared part of the spectrum. This difference was not present when
+reflectance values have been standardized (Equation~\ref{eq-std} ;
+Figure~\ref{fig-CompareRef} B).
+
 \subsection{Classification}\label{classification}
@@
 Each drone flight was used to produce a prediction map, as well as a
-probability map that indicates the model derived likelihood of the
+probability map that indicate the model derived likelihood of the
 selected class for every pixel. The low-altitude flight conducted in
-Gafanha, Portugal, represents the site with the highest complexity
+Gafanha, Portugal, represented the site with the highest complexity
 (Figure~\ref{fig-GafLow}). Among the five vegetation classes on which
-the model was trained, four were present on this site, with
-Chlorophyceae and Rhodophyceae mixed with the seagrass meadow. There was
-also Bacillariophyceae forming biofilms on parts of bare sediment
-surface. Although the seagrass bed was solely composed of
-\emph{Nanozostera noltei}, various colors of this specie could be
-observed from dark green (corresponding to healthy leaves) to
-whitish/brown (when leaves were discolored having lost their
-pigmentation). Regardless of color, Magnoliopsida pixels were accurately
-predicted by the model.
+the model was trained, four were present on this site, with green an red
+macroalgae mixed with a seagrass meadow. There was also diatoms forming
+biofilms on bare sediment surface. Although the seagrass was solely
+composed of a single specie, \emph{Nanozostera noltei}, various colors
+of this specie could be observed from dark green (corresponding to
+healthy leaves) to brown (when leaves are senescent or have an altered
+pigment composition). Regardless of the variation of color, the class
+Magnoliopsida was accurately predicted by the model (F1 score of 0.96 at
+that site).
 
@@
 \textasciitilde1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
-small island was masked in the prediction map. Most of the intertidal
-area was classified as Magnoliopsida by the model, including seagrass
-patches with discolored leaves. Only a few pixels were classified as
-Chlorophyceae at this spatial scale. Furthermore, the area that was
-classified as Bacillariophyceae in the low-altitude flight remained
-mostly classified as such in the high-altitude flight, though some
-pixels were classified as Magnoliopsida. Patches of Rhodophyceae were
-correctly classified. In the northern part of the site and near the land
+small island was masked in the prediction map. Most of vegetation area
+was classified as seagrass by the model, including patches with
+discolored leaves. Only a few pixels were classified as green algae (F1
+score of 0.55). Patches of Rhodophyceae were correctly classified (F1
+score of 0.85). In the northern part of the site and near the land
 eadges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
-(syn. \emph{Spartina maritima)} were misclassified, either as
-Magnoliopsida or as Phaeophyceae.
+(syn. \emph{Spartina maritima)} were misclassified, either as seagrass
+or as brown algae (F1 score of 0.77 and 0.71, respectively).
 
@@
 eastern part of the site. As shown in the zoom (Figure~\ref{fig-Boat}),
-the edges of the meadow visually appears to be colonised by green
-macroalgae (\emph{Ulva sp.}), which the model agreed with.
+the edges of the meadow were mixed with green macroalgae (\emph{Ulva
+sp.}), which the model agreed with (F1 score of 0.89 for green algae,
+0.97 for seagrass and 0.98 for red algae).
 
@@
 The flight over L'Epine in Noirmoutier Island, France
-(Figure~\ref{fig-Dike}) was conducted near a dike, which crossed the
-northern part of the site from west to east. Alongside this dike, Fucale
-brown algae (\emph{Fucus spp.}, \emph{Ascophyllum nodosum}) were
+(Figure~\ref{fig-Dike} A) was conducted near a dike, which crossed the
+northern part of the site from West to East. Alongside this dike, Fucale
+brown macroalgae (\emph{Fucus spp.}, \emph{Ascophyllum nodosum}) were
 attached to sparse rocks and stranded green algae (\emph{Ulva spp.})
-could be observed. Despite the high mixture between Chlorophyceae and
-Magnoliopsida these two classes were correctly discriminated by the
-classifier.
+could be observed and this was correctly reproduced by the prediction
+(Figure~\ref{fig-Dike} B). This site was characterized by a high mixture
+between green macroalgae and seagrass but these two classes were
+correctly discriminated by the classifier (F1 score of 0.97 and 0.98
+respectively).
 
@@
 
-\subsection{Validation}\label{validation-1}
-
-\subsubsection{Reflectance comparison between the two different
-altitudes}\label{reflectance-comparison-between-the-two-different-altitudes}
-
-In this study, a key innovation lies in the utilization of drone flights
-at two different altitudes (12 m and 120 m) for constructing the neural
-network model. Overall there was a good agreement between the two
-altitudes (Figure~\ref{fig-CompareRef}).
-
-\phantomsection\label{cell-fig-CompareRef}
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
-
-}
-
-\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
-both low-altitude and high-altitude flights over a common area. The
-black dashed line represents a 1 to 1 relationship. Left (A) plots raw
-data and right (B) plots standardized data (Equation~\ref{eq-std}).}
-
-\end{figure}%
-
-There was a slight underestimation for raw reflectance values in the
-high-altitude flight, particularly for higher reflectance values
-(Figure~\ref{fig-CompareRef} A). Since both flights were conducted over
-vegetation areas, the highest reflectance values correspond to the
-infrared part of the spectrum. This difference is not present when
-reflectance values have been standardized (Equation~\ref{eq-std} ;
-Figure~\ref{fig-CompareRef} B).
-
-\subsubsection{Neural network classification
-validation}\label{neural-network-classification-validation}
-
-Model global accuracy was 94.26\% with a Kappa coefficient of 0.92
-(Figure~\ref{fig-Validation}).
+\subsection{Validation of the model}\label{validation-of-the-model}
+
+With all drone flights combined, the model global accuracy was 94.26\%
+with a Kappa coefficient of 0.92 (Figure~\ref{fig-Validation}).
 
@@
 determined the minimal percent cover required to correctly classify a
-given class within the corresponding high altitude flight
-(Figure~\ref{fig-upscaling}).
+given class within the corresponding high altitude flight (8cm pixel
+resolution ; Figure~\ref{fig-upscaling}).
 
@@
 
+A percent cover of at least 80\% was sufficient to have all the pixels
+of high altitude flights correctly classified, with the exception of
+Magnoliopsida that required a higher cover (\textgreater90 \%) to be
+well classified. Concerning the probability of each class, there is a
+linear relationship between the percent cover and the confidence of the
+model to predict the class. To predict Chlorophyceae with a model
+likelihood of 0.85, a cover of 93 \% was needed, 90 \% for
+Magnoliopsida, 92 \% for Rhodophyceae and 97 \% for Bacillariophyceae.
 When the vegetation cover of a given class was 100 \%, coarser
@@
 consequently altering the model's classification from bare sediment to
-Bacillariophyceae. A percent cover of at least 80\% was sufficient to
-have all the pixels of high altitude flights correctly classified, with
-the exception of Magnoliopsida that required a higher cover
-(\textgreater90 \%) to be well classified. Concerning the probability of
-each class, the highest percent cover was needed to confidently predict
-Bacillariophyceae. To predict Chlorophyceae with a model likelihood of
-0.85, a cover of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for
-Rhodophyceae and 97 \% for Bacillariophyceae.
+Bacillariophyceae.
 
@@
 The primary objective of this study was to develop a method for the
-accurate classification of macrophytes on intertidal mudflats and
-sandflats, specifically focusing on distinguishing between Chlorophyceae
-(green macroalgae) and marine Magnoliopsida (seagrasses) using
-multispectral drone data. The ability to differentiate between various
-types of vegetation plays a critical role in ecological monitoring and
-coastal management \citep{WFD2000}. By distinguishing between seagrasses
-and macroalgae, our approach facilitates targeted conservation
-strategies, enabling more effective preservation and restoration efforts
-in coastal ecosystems. The discrimination of seagrasses from green
-macroalgae presents two main challenges \citetext{\citealp[
+accurate classification of macrophytes at low tide on tidal flats,
+specifically focusing on distinguishing between Chlorophyceae (green
+macroalgae) and marine Magnoliopsida (seagrasses) using a multispectral
+resolution. The discrimination of seagrasses from green macroalgae
+presents is spectrally challenging \citetext{\citealp[
 ]{oiry2021using}; \citealp[
-]{bannari2022}; \citealp{veettil2020opportunities}}. First these two
-macrophytes have a similar pigment composition: chlorophyll-a (common to
-all vegetation types), chlorophyll-b (an additional photosynthetic
+]{bannari2022}; \citealp{veettil2020opportunities}}. These two
+macrophytes share a similar pigment composition: chlorophyll-a (common
+to all vegetation types), chlorophyll-b (an additional photosynthetic
 pigment), and accessory carotenoids such as zeaxanthin, lutein and
-neoxanthin (Figure~\ref{fig-Pigm}). Second, seagrass and green
+neoxanthin (Figure~\ref{fig-Pigm}). Their spectreal responses could be
+close, particularly at a multispectral resolution. Seagrass and green
 macroalgae frequently co-occur in intertidal areas, and can intermingle
@@
 Here, the issue of intra-pixel mixing was resolved thanks to the very
-high spatial resolution of the drone, and the risk of spectral confusion
-was avoided thanks to the efficiency of the multispectral classifier.
-Our results confirm a recent study based on \emph{in situ} radiometry,
-where it was demonstrated that a sensor with at least eight spectral
-bands ranging from 500 to 850 nm and including a green band at 530 nm
-and a RedEdge band at 730 nm was crucial to accurately discriminate
-green macroalgae from seagrasses \citep{Davies2023}.
+high spatial resolution of the drone. In this study the risk of spectral
+confusion was avoided with a machine-learning approach exploiting a
+neural networks classifier. Our drone flights and a recent study based
+on \emph{in situ} radiometry, suggested that a sensor with at least
+eight spectral bands ranging from 500 to 850 nm and including a green
+band at 530 nm and a RedEdge band at 730 nm was crucial to accurately
+discriminate green macroalgae from seagrasses \citep{Davies2023}.
 
@@
 this study, enabled the classifier to achieve 97\% of accuracy between
-these two classes (Figure~\ref{fig-ValidationGreen}). Even if the
-pigment composition of green macrophytes is similar, differences in the
-spectral shape can be observed, with green algae having a higher
-reflectance peak at 560 nm as well as a higher NIR plateau than seagrass
+these two classes (Figure~\ref{fig-ValidationGreen}). Even if their
+pigment composition is similar, differences in the spectral shape can be
+observed, with green algae having a higher reflectance peak at 560 nm as
+well as a higher NIR plateau than seagrass
 (Figure~\ref{fig-vegetation}). Such differences were previously
@@
 \citep{bargain2013seasonal}, cellular structure as well as in the
-orientation of the plant over the sediment surface \citetext{\citealp[
+orientation of the plant at the sediment surface \citetext{\citealp[
 ]{beach1997vivo}; \citealp[
@@
 in carotenoids to chlorophyll-a ratios between seagrasses and green
-macroalgae \citep{repolho2017seagrass}.
-
-Concerning Phaeophyceae, the thick cell walls of these macroalgae
-\citep{charrier2021growth} make it more reflective in the infrared part
-of the spectra \citep{Slaton2001} whereas the presence of fucoxanthin
-and zeaxanthin result in a low reflectance in the visible region
-(Figure~\ref{fig-Pigm} ; Figure~\ref{fig-VIP}). These two key features
-have been identified by the Neural Network as the two principal
-predictors to accurately identify brown algae (Figure~\ref{fig-VIP}).
-Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae
-contribute to the lowest reflectance among all classes in the spectral
-range from 560 to 615 nm (Figure~\ref{fig-VIP}). Indeed the band at 560
-nm has been identified as important for identifying this class, likely
-due to phycoerythrin absorption at this wavelength. Regarding
-Bacillariophyceae, the VIP analysis (Figure~\ref{fig-VIP}) indicated
-that 475 nm was the most important predictor for this class. Indeed, the
-reflectance at 475 nm was higher for Bacillariophyceae than for any
-other vegetation class (Figure~\ref{fig-vegetation}), very likely due to
-the low biomass (and associated concentration of blue-absorbing
-pigments) of microphytobenthos biofilms compared to seagrass and
-macroalgae.
+macroalgae \citep{repolho2017seagrass}. Concerning Phaeophyceae, the
+thick cell walls of these macroalgae \citep{charrier2021growth} make it
+more reflective in the infrared part of the spectra \citep{Slaton2001}
+whereas the presence of fucoxanthin and zeaxanthin result in a low
+reflectance in the visible region (Figure~\ref{fig-Pigm} ;
+Figure~\ref{fig-VIP}). These two key features have been identified by
+the Neural Network as the two principal predictors to accurately
+identify brown algae (Figure~\ref{fig-VIP}). Similarly, the presence of
+phycoerythrin and phycocyanin in Rhodophyceae contribute to the lowest
+reflectance among all classes in the spectral range from 560 to 615 nm
+(Figure~\ref{fig-VIP}). Indeed the band at 560 nm has been identified as
+important for identifying this class, likely due to phycoerythrin
+absorption at this wavelength. Regarding Bacillariophyceae, the variable
+importance analysis (Figure~\ref{fig-VIP}) indicated that 475 nm was the
+most important predictor for this class. Indeed, the reflectance at 475
+nm was higher for Bacillariophyceae than for any other vegetation class
+(Figure~\ref{fig-vegetation}), very likely due to the low biomass (and
+associated concentration of blue-absorbing pigments) of these
+unicellular organisms compared to seagrass and macroalgae.
 
@@
 
-While comparing the reflectance of both altitudes (12 m and 120 m), it
-was observed that there is an underestimation of the infrared part of
-the spectra in the high-altitude dataset (Figure~\ref{fig-CompareRef}).
-Such disparity in infrared reflectance may stem from temporal
-differences between the flights, possibly resulting in a slightly drier
-intertidal area and consequently higher infrared reflectance. This
-disparity poses an issue for the methodology followed in the present
-study, relying solely on one flight height for training. To address this
-issue, we employed min/max standardized reflectance spectra as
-predictors for the model Equation~\ref{eq-std}. This approach allowed us
-to eliminate the slight reflectance difference between the flights
-(Figure~\ref{fig-CompareRef} B) and to focus on the shape of the spectra
-in the visible part of the electromagnetic spectra, where different
-pigmentation are associated to taxonomic dignostic features. This was a
-key feature in building a model that could reliably predict vegetation
-across geographical sites and seasons. It enabled consistent prediction
-of vegetation classes across variations in biomass and variability in
-light conditions \citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
-]{COSTA2021107018}; \citealp{piaser2023impact}}.
-
-We found 90 \% of seagrass cover is necessary for confident prediction
-of its presence (Figure~\ref{fig-upscaling}). This highlights a
-limitation of the methodology used to construct the training dataset for
-the model. The dataset used to train our algorithm was composed
-exclusively of pure pixels, which resulted in the model's reduced
-confidence when faced with lower percentages of seagrass cover. Also,
-intertidal seagrasses exhibit marked phenology, with varying pigment
-composition throughout the year \citetext{\citealp[
-]{bargain2013seasonal}; \citealp{legare2022remote}}. Since the training
-dataset has been made using well established seagrass meadows, this
-model may be less accurate outside of the seasonal seagrass peak of
-biomass. Further investigation is required to evaluate the accuracy of
-the method along different periods of the year.
+The ability to differentiate between various types of vegetation plays a
+critical role in ecological monitoring and coastal management
+\citep{WFD2000}. By distinguishing between seagrasses and macroalgae,
+our approach facilitates targeted conservation strategies, enabling more
+effective preservation and restoration efforts in coastal ecosystems.
+While comparing the reflectance at two different altitudes (12 m and 120
+m), a nearly one-to-one relationship was observed, with a Root Mean
+Square Error (RMSE) of 0.02 (Figure~\ref{fig-CompareRef}). This result
+indicates that the reflectance measured by remote sensing (RS) sensors
+is not significantly influenced by pixel size. This finding is valuable
+for integrating drone-based data into larger-scale mapping projects
+(e.g., combining satellite and drone mapping in side-by-side analyses).
+The consistency of reflectance across altitudes suggests that drones can
+be effectively used for finer-scale mapping without compromising data
+accuracy when merging with other platforms. However, it was observed
+that there is an underestimation of the infrared part of the spectra in
+the high-altitude dataset (Figure~\ref{fig-CompareRef}). Such disparity
+in infrared reflectance may stem from temporal differences between the
+flights, possibly resulting in a slightly drier intertidal area and
+consequently higher infrared reflectance. This disparity poses an issue
+for the methodology followed in the present study, relying solely on one
+flight height for training. To address this issue, we employed min/max
+standardized reflectance spectra as predictors for the model
+Equation~\ref{eq-std}. This approach allowed us to eliminate the slight
+reflectance difference between the flights (Figure~\ref{fig-CompareRef}
+B) and to focus on the shape of the spectra in the visible part of the
+electromagnetic spectra, where different pigmentation are associated to
+taxonomic dignostic features. In contrast to subtidal seagrasses, which
+maintain a relatively constant biomass throughout the year, intertidal
+seagrasses, like the one studied in this work, exhibit strong seasonal
+phenology \citep{davies2024sentinel}. At some sites, they completely
+disappear during the winter and reach their peak above-ground biomass in
+the summer and early fall. Along with these seasonal changes in biomass,
+the pigment composition and ratios also vary throughout the year,
+reflecting the plants' adaptations to different environmental conditions
+\citetext{\citealp[ ]{bargain2013seasonal}; \citealp{legare2022remote}}.
+Standardization of spectral signatures helps to mitigate the impact of
+changing biomass on the spectral profile, enabling the development of a
+model that can reliably predict vegetation across different geographical
+locations and seasons. This approach allows for consistent
+classification of vegetation despite variations in biomass and
+fluctuations in light conditions, providing a robust tool for monitoring
+and predicting vegetation dynamics \citetext{\citealp[
+]{fyfe2003spatial}; \citealp[
+]{COSTA2021107018}; \citealp{piaser2023impact}}. We found 90 \% seagrass
+cover was necessary at an 8 cm resolution for confident prediction of
+its presence (Figure~\ref{fig-upscaling}). However, due to the strong
+phenology of intertidal seagrass meadows in Europe, the period when a
+meadow is well-established can be temporally restricted, limiting the
+ideal window for accurate detection.
+
+\subsection{Impact of Pixel Resolution on the prediction and
+Implications for Satellite Remote
+Sensing}\label{impact-of-pixel-resolution-on-the-prediction-and-implications-for-satellite-remote-sensing}
+
+The results of Figure~\ref{fig-pixelsize} highlight the importance of
+pixel resolution in maintaining accurate classification and agreement
+between products derived from remote sensing data with different spatial
+resolutions. As the pixel size increases, a consistent decline in
+agreement is observed across all vegetation classes, with more
+pronounced effects for certain classes, such as green algae. This
+phenomenon underscores the sensitivity of spatial resolution in
+distinguishing smaller or patchier vegetation features. Green algae,
+being more patchy in all our study sites, demonstrates the steepest drop
+in agreement with increasing pixel size, which aligns with expectations
+given the limitations of coarser resolution in capturing fine-scale
+details.
+
+This relationship between resolution and agreement has significant
+implications for satellite platforms like Sentinel-2 and Landsat. Both
+satellites, commonly used in marine and coastal vegetation studies,
+offer medium-resolution imagery, with pixel sizes of 10 m and 30 m,
+respectively. While these resolutions are suitable for broad-scale
+environmental monitoring, they may struggle to capture finer-scale
+heterogeneity, especially for more fragmented or patchy vegetation types
+like green algae. The results suggest that while coarser resolutions
+like those of Landsat are sufficient for seagrass and other more
+homogeneous vegetation types, higher resolutions are essential for
+accurately mapping species like green algae.
 

### 2024-09-27 index.qmd
add updates

@@
 Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between the land and oceans [@unsworth2022].
-Seagrass meadows provide a myriad of ecosystem services to humanity, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and mitigation of eutrophication [@unsworth2022 ; @sousa2019blue].
+Seagrass meadows provide a myriad of ecosystem services, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and mitigation of eutrophication [@unsworth2022 ; @sousa2019blue].
 They serve as vital habitats for a diverse array of marine and terrestrial species, providing living, breeding, and feeding grounds [@gardner2018 ; @Zoffoli2022 ; @jankowska2019].
@@
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
+In addition, the results obtained from drone-based multispectral remote sensing will be spatially degraded to satellite resolutions, and the effect of this resolution on the model's predictions will be investigated, providing insights for coastal habitat mapping using satellites.
 
@@
 
-Seven study sites distributed between France and Portugal were selected for their relatively extensive intertidal seagrass beds.
+Seven study sites distributed between France and Portugal were selected for their extensive intertidal seagrass beds.
 Two sites were located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
@@
 One of the sites within the gulf was on one its islands (Arz) and the other was located further south on a mainland beach area (Duer).
+The Gulf of Morbihan is a Natura 2000 site and a Regional Protected Area due to its rich biodiversity, including its seagrass meadows, and is also classified as a RAMSAR site, which highlights its significance as a wetland of international importance.
 Two other sites were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
@@
 *Zostera noltei*) with very little mixing with other macrophytes.
+Bourgneuf Bay is also part of the Natura 2000 network and serves as a RAMSAR site due to its critical habitat for migratory bird species and its extensive seagrass meadows.
 Three sites were surveyed in the Ria de Aveiro Coastal Lagoon in Portugal (40.6887°N, 8.6810°W).
@@
 These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown, and green macroalgae.
+The Aveiro Lagoon, like the other study areas, is a Natura 2000 site and a RAMSAR wetland, recognized for its rich mosaic of habitats and importance for biodiversity, including migratory bird species and intertidal vegetation.
 
@@
 A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+Only homogeneous vegetation patches extending over several meters were selected as ground control points.
 Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
@@
 
- Gafanha_low_pred<-"./Data/image/prediction/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
+ Gafanha_low_pred<-"./Data/BiCOME_Flights/Aveiro/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
      rast()
@@
                 Class != "A - MagnoliopsidaL") %>% 
-  ggplot(aes(x=Wavelength, y = mean/10000, color = Class))+
-  geom_line(linewidth = 0.5)+
+  ggplot()+
+  geom_line(aes(x=Wavelength, y = mean/10000, color = Class), linewidth = 0.5)+
+  geom_label(x= 470,y=0.7, label = "F", size = 2)+
   scale_color_manual(values=c("#389318", "#873e23", "#b3002d", "#b3ff1a", "#DAA520"))+
@@
 
-The spectral similarities of the reflectance signatures between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
+The spectral similarities of the reflectance signatures at the spectral resolution of the micasense senor between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
 To overcome this challenge, a deep learning classification method was trained, validated, and applied to each drone flight (@fig-workflow).
@@
 The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowied to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
+Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
 More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
@@
 This model is composed by 2 hidden layers and have a total of 26 054 trainable parameters.
-Parameters have been find tune using 12 epoch to minimize the error rate.
+Parameters have been fine tuned using 12 epoch to minimize the error rate.
 
@@
 The model was applied to all flights at both 12 and 120 m of altitude.
-In situ information on georeferenced class type and percent cover collected during each flight was used to assess the model accuracy.
+*In situ* information on georeferenced class type and percent cover, acquired at over homogeneous vegetation patches at the same time as drone flights was used to assess the model accuracy.
 These images were used to construct a validation dataset indicating the presence or absence of each class.
 Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
-The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
+The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
+A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
 All validation matrices were then aggregated to create an overall matrix .
@@
 
-## Impact of the vegetation cover on the prediction
-
-The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm).
-The predictions made on the high-resolution flight can be used to estimate the cover (percentage, %) of each vegetation class for every pixel of the lower resolution flight.
-Consequently, for each pixel of the high-altitude flights, the cover (%) of each vegetation class were obtained, and a kernel density plot was generated.
-This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
+## Impact of mixed vegetation cover on the prediction
+
+The key aspect of the workflow adopted in the present study is the mapping at two different altitudes (12 m and 120 m), resulting in two distinct resolutions for the same area (8 mm and 80 mm).
+The high-resolution flight was used to estimate the sub-pixel composition for each pixel of the lower-resolution flight.
+Consequently, within each pixel of the high-altitude flights, the contribution of each vegetation class (% cover) was obtained, and a kernel density plot was generated.
+This plot provided a visual representation of the model’s behavior in mixed vegetation scenarios.
+It helps to understand the minimum vegetation cover of a given class within a pixel necessary for the model to confidently predict that class.
 
@@
 
+## Reflectance comparison between the two different altitudes
+
+```{r Reflectance_Validation 2 height}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
+#   rast()
+# 
+# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
+# #   rast() 
+# 
+# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
+#   rast() %>% 
+#   resample(high_alt, method = "med")
+# 
+# 
+# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
+#   rast() 
+# 
+# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
+#   vect()
+#   
+# high_alt_masked<-crop(high_alt,mask)
+# high_alt_masked<-mask(high_alt_masked,mask)
+# 
+# low_alt_masked<-crop(low_alt,mask)
+# low_alt_masked<-mask(low_alt_masked,mask)
+# 
+# low_alt_pred_masked<-crop(low_alt_pred,mask)
+# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
+# 
+# 
+# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
+#   as.data.frame()
+# 
+# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
+#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
+#               "pred")
+# 
+# stk_long<-stk %>% 
+#   mutate(px_ID = c(1:nrow(stk))) %>% 
+#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
+#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
+#                          str_detect(Bands, "high") ~ "High",
+#                          TRUE ~ "NA"),
+#          Bands = gsub("_high","",Bands),
+#          Bands = gsub("_low","",Bands))
+# 
+# 
+# stk_summarized<-stk_long %>% 
+#   # group_by(px_ID,alt) %>% 
+#   # reframe(Value = mean(Value),
+#   #         pred = unique(pred)) %>% 
+#   pivot_wider(names_from = "alt", values_from = "Value")
+# 
+# df<-stk_summarized %>% 
+#   ungroup() %>% 
+#   group_by(Bands) %>% 
+#   filter(Low<10000,
+#          High < 10000,
+#          Low < quantile(Low,probs = 0.99),
+#          High < quantile(High,probs = 0.99),
+#          Low > quantile(Low,probs = 0.01),
+#          High > quantile(High,probs = 0.01),
+#          !pred %in% c(7,9,3,10)) %>%
+#   ungroup()
+
+RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
+  mutate(Low = Low /10000,
+         High = High/10000)
+
+RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
+lm_raw <- lm(RAW$High ~ RAW$Low)
+
+STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
+
+RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
+lm_STD <- lm(STD$High ~ STD$Low)
+
+plot_RAW <- RAW %>%  
+  ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(0,6000),
+                               breaks = c(0,2000,4000,6000),
+                               labels = c("1","2000","4000","6000"))+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,0.6))+
+  xlim(c(0.05,0.6))+
+  ylab("Reflectance of the 120m flight")+
+  xlab("Reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+plot_STD <- STD %>%  
+    ggplot(aes(x=Low, y=High))+
+  # geom_point(aes(color = as.factor(pred)))
+  ggpointdensity::geom_pointdensity(adjust = .03)+
+  viridis::scale_color_viridis(limits = c(1,2000),
+                               breaks = c(1,1000,2000),
+                               labels = c("1","1000","2000"))+
+  # scale_color_gradient(na.value = 1)+
+  # geom_smooth(method = "loess")+
+  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
+  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
+  theme_Bede()+
+  ylim(c(0.05,1))+
+  xlim(c(0.05,1))+
+  ylab("Standardised reflectance of the 120m flight")+
+  xlab("Standardised reflectance of the 12m flight")+
+  labs(color = "Pixel density")+
+  theme(
+    legend.position = "top",
+        legend.key.width = unit(3,"line"))
+
+ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
+ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
+
+```
+
+```{r ref_compare_building}
+#| cache: true
+#| echo: false
+#| eval: false
+#| warning: false
+
+RAW <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+STD <- ggplot()+
+  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
+  coord_equal()+
+  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
+    theme_void()+
+  theme(axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        axis.ticks = element_blank(), 
+        axis.ticks.length = unit(0, "pt"),
+        panel.grid.major=element_blank(), 
+        panel.grid.minor=element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "pt"))
+
+plot <- RAW+STD
+
+ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
+```
+
+In this study, drone flights were conducted at two different altitudes (12 m and 120 m) to construct the neural network model.
+At the sites where the flights at both altitudes overlapped, reflectance was compared.
+Overall there was a good agreement between the two altitudes (RMSE: 0.027 ; @fig-CompareRef).
+
+```{r RefComapare}
+#| cache: false
+#| echo: false
+#| warning: false
+#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
+The black dashed line represents a 1 to 1 relationship.
+Left (A) plots raw data and right (B) plots standardized data (@eq-std).
+#| label: fig-CompareRef
+#| fig-width: 10
+#| fig-height: 5
+#| out-width: "100%"
+
+knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
+
+```
+
+There was a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
+Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
+This difference was not present when reflectance values have been standardized (@eq-std ; @fig-CompareRef B).
+
 ## Classification
 
-Each drone flight was used to produce a prediction map, as well as a probability map that indicates the model derived likelihood of the selected class for every pixel.
-The low-altitude flight conducted in Gafanha, Portugal, represents the site with the highest complexity (@fig-GafLow).
-Among the five vegetation classes on which the model was trained, four were present on this site, with Chlorophyceae and Rhodophyceae mixed with the seagrass meadow.
-There was also Bacillariophyceae forming biofilms on parts of bare sediment surface.
-Although the seagrass bed was solely composed of *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to whitish/brown (when leaves were discolored having lost their pigmentation).
-Regardless of color, Magnoliopsida pixels were accurately predicted by the model.
+Each drone flight was used to produce a prediction map, as well as a probability map that indicate the model derived likelihood of the selected class for every pixel.
+The low-altitude flight conducted in Gafanha, Portugal, represented the site with the highest complexity (@fig-GafLow).
+Among the five vegetation classes on which the model was trained, four were present on this site, with green an red macroalgae mixed with a seagrass meadow.
+There was also diatoms forming biofilms on bare sediment surface.
+Although the seagrass was solely composed of a single specie, *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to brown (when leaves are senescent or have an altered pigment composition).
+Regardless of the variation of color, the class Magnoliopsida was accurately predicted by the model (F1 score of 0.96 at that site).
 
@@
 A channel contouring a small island was masked in the prediction map.
-Most of the intertidal area was classified as Magnoliopsida by the model, including seagrass patches with discolored leaves.
-Only a few pixels were classified as Chlorophyceae at this spatial scale.
-Furthermore, the area that was classified as Bacillariophyceae in the low-altitude flight remained mostly classified as such in the high-altitude flight, though some pixels were classified as Magnoliopsida.
-Patches of Rhodophyceae were correctly classified.
+Most of vegetation area was classified as seagrass by the model, including patches with discolored leaves.
+Only a few pixels were classified as green algae (F1 score of 0.55).
+Patches of Rhodophyceae were correctly classified (F1 score of 0.85).
 In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Sporobolus maritimus* (syn.
-*Spartina maritima)* were misclassified, either as Magnoliopsida or as Phaeophyceae.
+*Spartina maritima)* were misclassified, either as seagrass or as brown algae (F1 score of 0.77 and 0.71, respectively).
 
@@
 The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
-As shown in the zoom (@fig-Boat), the edges of the meadow visually appears to be colonised by green macroalgae (*Ulva sp.*), which the model agreed with.
+As shown in the zoom (@fig-Boat), the edges of the meadow were mixed with green macroalgae (*Ulva sp.*), which the model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass and 0.98 for red algae).
 
@@
 
-The flight over L'Epine in Noirmoutier Island, France (@fig-Dike) was conducted near a dike, which crossed the northern part of the site from west to east.
-Alongside this dike, Fucale brown algae (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed.
-Despite the high mixture between Chlorophyceae and Magnoliopsida these two classes were correctly discriminated by the classifier.
+The flight over L'Epine in Noirmoutier Island, France (@fig-Dike A) was conducted near a dike, which crossed the northern part of the site from West to East.
+Alongside this dike, Fucale brown macroalgae (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed and this was correctly reproduced by the prediction (@fig-Dike  B).
+This site was characterized by a high mixture between green macroalgae and seagrass but these two classes were correctly discriminated by the classifier (F1 score of 0.97 and 0.98 respectively).
 
@@
 
-## Validation
-
-### Reflectance comparison between the two different altitudes
-
-```{r Reflectance_Validation 2 height}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-# high_alt<- "Data/image/micasense/Gafanha_high_multi.tif" %>% 
-#   rast()
-# 
-# # low_alt<- "Data/image/micasense/Gafanha_Low_Multi_rsp.tif" %>% 
-# #   rast() 
-# 
-# low_alt<- "Data/image/micasense/Gafanha_low_multi.tif" %>% 
-#   rast() %>% 
-#   resample(high_alt, method = "med")
-# 
-# 
-# low_alt_pred<- "Data/image/prediction/NewPreds/Gafanha_Low_Pred_rsp.tif" %>% 
-#   rast() 
-# 
-# mask<-"Data/shp/Mask_Alt_Compare_All.shp" %>% 
-#   vect()
-#   
-# high_alt_masked<-crop(high_alt,mask)
-# high_alt_masked<-mask(high_alt_masked,mask)
-# 
-# low_alt_masked<-crop(low_alt,mask)
-# low_alt_masked<-mask(low_alt_masked,mask)
-# 
-# low_alt_pred_masked<-crop(low_alt_pred,mask)
-# low_alt_pred_masked<-mask(low_alt_pred_masked,mask)
-# 
-# 
-# stk<-rast(list(c(high_alt_masked,low_alt_masked,low_alt_pred_masked)))%>% 
-#   as.data.frame()
-# 
-# names(stk)<-c("B1_high","B2_high","B3_high","B4_high","B5_high","B6_high","B7_high","B8_high","B9_high","B10_high",
-#               "B1_low","B2_low","B3_low","B4_low","B5_low","B6_low","B7_low","B8_low","B9_low","B10_low",
-#               "pred")
-# 
-# stk_long<-stk %>% 
-#   mutate(px_ID = c(1:nrow(stk))) %>% 
-#   pivot_longer(-c(px_ID,pred),values_to = "Value",names_to = "Bands") %>% 
-#   mutate(alt = case_when(str_detect(Bands, "low") ~ "Low",
-#                          str_detect(Bands, "high") ~ "High",
-#                          TRUE ~ "NA"),
-#          Bands = gsub("_high","",Bands),
-#          Bands = gsub("_low","",Bands))
-# 
-# 
-# stk_summarized<-stk_long %>% 
-#   # group_by(px_ID,alt) %>% 
-#   # reframe(Value = mean(Value),
-#   #         pred = unique(pred)) %>% 
-#   pivot_wider(names_from = "alt", values_from = "Value")
-# 
-# df<-stk_summarized %>% 
-#   ungroup() %>% 
-#   group_by(Bands) %>% 
-#   filter(Low<10000,
-#          High < 10000,
-#          Low < quantile(Low,probs = 0.99),
-#          High < quantile(High,probs = 0.99),
-#          Low > quantile(Low,probs = 0.01),
-#          High > quantile(High,probs = 0.01),
-#          !pred %in% c(7,9,3,10)) %>%
-#   ungroup()
-
-RAW <- read.csv("Data/CompareReflectance/Compare_ref_raw.csv")%>%  
-  mutate(Low = Low /10000,
-         High = High/10000)
-
-RMSE_raw <- sqrt(mean((RAW$Low - RAW$High)^2))
-lm_raw <- lm(RAW$High ~ RAW$Low)
-
-STD <- read.csv("Data/CompareReflectance/Compare_ref_std.csv")
-
-RMSE_STD <- sqrt(mean((STD$Low - STD$High)^2))
-lm_STD <- lm(STD$High ~ STD$Low)
-
-plot_RAW <- RAW %>%  
-  ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(0,6000),
-                               breaks = c(0,2000,4000,6000),
-                               labels = c("1","2000","4000","6000"))+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,0.6))+
-  xlim(c(0.05,0.6))+
-  ylab("Reflectance of the 120m flight")+
-  xlab("Reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-plot_STD <- STD %>%  
-    ggplot(aes(x=Low, y=High))+
-  # geom_point(aes(color = as.factor(pred)))
-  ggpointdensity::geom_pointdensity(adjust = .03)+
-  viridis::scale_color_viridis(limits = c(1,2000),
-                               breaks = c(1,1000,2000),
-                               labels = c("1","1000","2000"))+
-  # scale_color_gradient(na.value = 1)+
-  # geom_smooth(method = "loess")+
-  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
-  # geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
-  theme_Bede()+
-  ylim(c(0.05,1))+
-  xlim(c(0.05,1))+
-  ylab("Standardised reflectance of the 120m flight")+
-  xlab("Standardised reflectance of the 12m flight")+
-  labs(color = "Pixel density")+
-  theme(
-    legend.position = "top",
-        legend.key.width = unit(3,"line"))
-
-ggsave("./Figures/High_res/Compare_reflectance.png",plot_RAW, width= 472*4, height=402*4, units = "px")
-ggsave("./Figures/High_res/Compare_reflectance_std.png",plot_STD, width= 472*4, height=402*4, units = "px")
-
-```
-
-```{r ref_compare_building}
-#| cache: true
-#| echo: false
-#| eval: false
-#| warning: false
-
-RAW <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-STD <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
-  coord_equal()+
-  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
-    theme_void()+
-  theme(axis.text = element_blank(), 
-        axis.title = element_blank(), 
-        axis.ticks = element_blank(), 
-        axis.ticks.length = unit(0, "pt"),
-        panel.grid.major=element_blank(), 
-        panel.grid.minor=element_blank(), 
-        plot.margin = margin(0, 0, 0, 0, "pt"))
-
-plot <- RAW+STD
-
-ggsave("./Figures/High_res/Compare_reflectance_both.png",plot,width= 1920*4, height=1129*4, units = "px")
-```
-
-In this study, a key innovation lies in the utilization of drone flights at two different altitudes (12 m and 120 m) for constructing the neural network model.
-Overall there was a good agreement between the two altitudes (@fig-CompareRef).
-
-```{r RefComapare}
-#| cache: false
-#| echo: false
-#| warning: false
-#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area.
-The black dashed line represents a 1 to 1 relationship.
-Left (A) plots raw data and right (B) plots standardized data (@eq-std).
-#| label: fig-CompareRef
-#| fig-width: 10
-#| fig-height: 5
-#| out-width: "100%"
-
-knitr::include_graphics("./Figures/High_res/Compare_reflectance_both.png")
-
-```
-
-There was a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
-Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
-This difference is not present when reflectance values have been standardized (@eq-std ; @fig-CompareRef B).
-
-### Neural network classification validation
-
-Model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
+## Validation of the model
+
+With all drone flights combined, the model global accuracy was `r round(validation_metrics$overall[[1]]*100,2)`% with a Kappa coefficient of `r round(validation_metrics$overall[[2]],2)` (@fig-Validation).
 
@@
   as_tibble() %>% 
-  # dplyr::filter(true != 1,
-  #               true != 6,
-  #               true != 7,
-  #               true != 8) %>% 
   mutate(true_fct = as.factor(true),
@@
 
-(plot <- ggplot(NewData)+
+(plot <- NewData %>% 
+  dplyr::filter(true_fct != 1,
+                true_fct != 6,
+                true_fct != 7,
+                true_fct != 8) %>%
+    ggplot()+
   geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
@@
 
-Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (@fig-upscaling).
+Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (8cm pixel resolution ; @fig-upscaling).
 
@@
 
+ A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be well classified.
+Concerning the probability of each class, there is a linear relationship between the percent cover and the confidence of the model to predict the class.
+To predict Chlorophyceae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
 When the vegetation cover of a given class was 100 %, coarser high-flight pixels were well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
 This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
-A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be well classified.
-Concerning the probability of each class, the highest percent cover was needed to confidently predict Bacillariophyceae.
-To predict Chlorophyceae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
 
@@
 
-The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats and sandflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data.
-The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management [@WFD2000].
-By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-The discrimination of seagrasses from green macroalgae presents two main challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities].
-First these two macrophytes have a similar pigment composition: chlorophyll-a (common to all vegetation types), chlorophyll-b (an additional photosynthetic pigment), and accessory carotenoids such as zeaxanthin, lutein and neoxanthin (@fig-Pigm).
-Second, seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
-Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone, and the risk of spectral confusion was avoided thanks to the efficiency of the multispectral classifier.
-Our results confirm a recent study based on *in situ* radiometry, where it was demonstrated that a sensor with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macroalgae from seagrasses [@Davies2023].
+The primary objective of this study was to develop a method for the accurate classification of macrophytes at low tide on tidal flats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using a multispectral resolution.
+The discrimination of seagrasses from green macroalgae presents is spectrally challenging [@oiry2021using ; @bannari2022 ; @veettil2020opportunities].
+These two macrophytes share a similar pigment composition: chlorophyll-a (common to all vegetation types), chlorophyll-b (an additional photosynthetic pigment), and accessory carotenoids such as zeaxanthin, lutein and neoxanthin (@fig-Pigm).
+Their spectreal responses could be close, particularly at a multispectral resolution.
+Seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
+Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone.
+In this study the risk of spectral confusion was avoided with a machine-learning approach exploiting a neural networks classifier.
+Our drone flights and a recent study based on *in situ* radiometry, suggested that a sensor with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macroalgae from seagrasses [@Davies2023].
 
@@
 Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in this study, enabled the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
-Even if the pigment composition of green macrophytes is similar, differences in the spectral shape can be observed, with green algae having a higher reflectance peak at 560 nm as well as a higher NIR plateau than seagrass (@fig-vegetation).
-Such differences were previously attributed to differences in pigments concentration and/or ratios [@bargain2013seasonal], cellular structure as well as in the orientation of the plant over the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
+Even if their pigment composition is similar, differences in the spectral shape can be observed, with green algae having a higher reflectance peak at 560 nm as well as a higher NIR plateau than seagrass (@fig-vegetation).
+Such differences were previously attributed to differences in pigments concentration and/or ratios [@bargain2013seasonal], cellular structure as well as in the orientation of the plant at the sediment surface [@beach1997vivo ; @kirk1994light ; @hedley2018influence].
 :::
@@
 In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in carotenoids to chlorophyll-a ratios between seagrasses and green macroalgae [@repolho2017seagrass].
-
 Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of fucoxanthin and zeaxanthin result in a low reflectance in the visible region (@fig-Pigm ; @fig-VIP).
@@
 Indeed the band at 560 nm has been identified as important for identifying this class, likely due to phycoerythrin absorption at this wavelength.
-Regarding Bacillariophyceae, the VIP analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
-Indeed, the reflectance at 475 nm was higher for Bacillariophyceae than for any other vegetation class (@fig-vegetation), very likely due to the low biomass (and associated concentration of blue-absorbing pigments) of microphytobenthos biofilms compared to seagrass and macroalgae.
+Regarding Bacillariophyceae, the variable importance analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
+Indeed, the reflectance at 475 nm was higher for Bacillariophyceae than for any other vegetation class (@fig-vegetation), very likely due to the low biomass (and associated concentration of blue-absorbing pigments) of these unicellular organisms compared to seagrass and macroalgae.
 
@@
 
-While comparing the reflectance of both altitudes (12 m and 120 m), it was observed that there is an underestimation of the infrared part of the spectra in the high-altitude dataset (@fig-CompareRef).
+The ability to differentiate between various types of vegetation plays a critical role in ecological monitoring and coastal management [@WFD2000].
+By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
+While comparing the reflectance at two different altitudes (12 m and 120 m), a nearly one-to-one relationship was observed, with a Root Mean Square Error (RMSE) of 0.02 (@fig-CompareRef).
+This result indicates that the reflectance measured by remote sensing (RS) sensors is not significantly influenced by pixel size.
+This finding is valuable for integrating drone-based data into larger-scale mapping projects (e.g., combining satellite and drone mapping in side-by-side analyses).
+The consistency of reflectance across altitudes suggests that drones can be effectively used for finer-scale mapping without compromising data accuracy when merging with other platforms.
+However, it was observed that there is an underestimation of the infrared part of the spectra in the high-altitude dataset (@fig-CompareRef).
 Such disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance.
@@
 This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features.
-This was a key feature in building a model that could reliably predict vegetation across geographical sites and seasons.
-It enabled consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
-
-We found `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % of seagrass cover is necessary for confident prediction of its presence (@fig-upscaling).
-This highlights a limitation of the methodology used to construct the training dataset for the model.
-The dataset used to train our algorithm was composed exclusively of pure pixels, which resulted in the model's reduced confidence when faced with lower percentages of seagrass cover.
-Also, intertidal seagrasses exhibit marked phenology, with varying pigment composition throughout the year [@bargain2013seasonal ; @legare2022remote].
-Since the training dataset has been made using well established seagrass meadows, this model may be less accurate outside of the seasonal seagrass peak of biomass.
-Further investigation is required to evaluate the accuracy of the method along different periods of the year.
+In contrast to subtidal seagrasses, which maintain a relatively constant biomass throughout the year, intertidal seagrasses, like the one studied in this work, exhibit strong seasonal phenology [@davies2024sentinel].
+At some sites, they completely disappear during the winter and reach their peak above-ground biomass in the summer and early fall.
+Along with these seasonal changes in biomass, the pigment composition and ratios also vary throughout the year, reflecting the plants' adaptations to different environmental conditions [@bargain2013seasonal ; @legare2022remote].
+Standardization of spectral signatures helps to mitigate the impact of changing biomass on the spectral profile, enabling the development of a model that can reliably predict vegetation across different geographical locations and seasons.
+This approach allows for consistent classification of vegetation despite variations in biomass and fluctuations in light conditions, providing a robust tool for monitoring and predicting vegetation dynamics [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
+We found `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % seagrass cover was necessary at an 8 cm resolution for confident prediction of its presence (@fig-upscaling).
+However, due to the strong phenology of intertidal seagrass meadows in Europe, the period when a meadow is well-established can be temporally restricted, limiting the ideal window for accurate detection.
+
+## Impact of Pixel Resolution on the prediction and Implications for Satellite Remote Sensing
+
+The results of @fig-pixelsize highlight the importance of pixel resolution in maintaining accurate classification and agreement between products derived from remote sensing data with different spatial resolutions.
+As the pixel size increases, a consistent decline in agreement is observed across all vegetation classes, with more pronounced effects for certain classes, such as green algae.
+This phenomenon underscores the sensitivity of spatial resolution in distinguishing smaller or patchier vegetation features.
+Green algae, being more patchy in all our study sites, demonstrates the steepest drop in agreement with increasing pixel size, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
+
+This relationship between resolution and agreement has significant implications for satellite platforms like Sentinel-2 and Landsat.
+Both satellites, commonly used in marine and coastal vegetation studies, offer medium-resolution imagery, with pixel sizes of 10 m and 30 m, respectively.
+While these resolutions are suitable for broad-scale environmental monitoring, they may struggle to capture finer-scale heterogeneity, especially for more fragmented or patchy vegetation types like green algae.
+The results suggest that while coarser resolutions like those of Landsat are sufficient for seagrass and other more homogeneous vegetation types, higher resolutions are essential for accurately mapping species like green algae.
 

### 2024-09-27 docs/_tex/index.tex
add results

@@
 pigment), and accessory carotenoids such as zeaxanthin, lutein and
-neoxanthin (Figure~\ref{fig-Pigm}). Their spectreal responses could be
+neoxanthin (Figure~\ref{fig-Pigm}). Their spectral responses could be
 close, particularly at a multispectral resolution. Seagrass and green
@@
 electromagnetic spectra, where different pigmentation are associated to
-taxonomic dignostic features. In contrast to subtidal seagrasses, which
+taxonomic diagnostic features. In contrast to subtidal seagrasses, which
 maintain a relatively constant biomass throughout the year, intertidal
@@
 Climate change, global warming, eutrophication, alien and invasive
-species development, coastal erosion, and sealevel rise are expected to
+species development, coastal erosion, and sea level rise are expected to
 continue impacting coastal ecosystems in the future
 \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
-]{holon2018predictive}; \citealp{marquet2024global}}. and the demand for
+]{holon2018predictive}; \citealp{marquet2024global}} and the demand for
 meaningful and efficient monitoring of coastal habitats has never been
@@
 areas known to have regular blooms or in new sites. Indeed, this
-approach could provide early warning alerts to local managers.
-
-Employing traditional sampling methods to monitor coastal ecosystems is
-time and resource-intensive, and the findings are often difficult to
-scale-up. Earth Observation can bridge this gap and meet the needs for
-systematic monitoring coastal ecosystems over large areas
+approach could provide early warning alerts to local managers and
+complimentary to traditional sampling methods to monitor coastal
+ecosystems. These methods are generally time and resource-intensive, and
+the findings are often difficult to scale-up when applied alone. Earth
+Observation can bridge this gap and meet the needs for systematic
+monitoring coastal ecosystems over large areas
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
@@
 spatial-resolution provide a novel and powerful tool to rapidly and
-accurately acquire ground truth satellite data. Spatially resolved data
-are indeed critical for calibrating and validating satellite remote
-sensing observations, thereby enhancing our capacity to monitor vast
-coastal areas. A perspective of this work could be to develop a similar
+accurately acquire ground truth data which can be used to develop
+machine-learning algorithm for satellite sensors
+\citep{davies2024intertidal}. Spatially resolved data are indeed
+critical for calibrating and validating satellite remote sensing
+observations, thereby enhancing our capacity to monitor vast coastal
+areas. A perspective of this work could be to develop a similar
 classifier for satellite images (e.g.~Sentinel-2), and test whether the
@@
 operational at a coarser spatial resolution. The integration of drone
-technology facilitates a scalable approach to environmental
-surveillance, offering significant advancements in the spatial and
-temporal resolution of data collection. This, in turn, supports the EU
-WFD's objectives by enabling more informed and timely management
-decisions for the conservation and restoration of aquatic ecosystems.
+technology facilitates a scalable approach to environmental surveillance
+while taking into account patchiness of secondary vegetation, offering
+significant advancements in the spatial and temporal resolution of data
+collection. This, in turn, supports the EU WFD's objectives by enabling
+more informed and timely management decisions for the conservation and
+restoration of aquatic ecosystems.
 

### 2024-09-27 index.qmd
add results

@@
 These two macrophytes share a similar pigment composition: chlorophyll-a (common to all vegetation types), chlorophyll-b (an additional photosynthetic pigment), and accessory carotenoids such as zeaxanthin, lutein and neoxanthin (@fig-Pigm).
-Their spectreal responses could be close, particularly at a multispectral resolution.
+Their spectral responses could be close, particularly at a multispectral resolution.
 Seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
@@
 To address this issue, we employed min/max standardized reflectance spectra as predictors for the model [@eq-std ; @Cao2017].
-This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features.
+This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic diagnostic features.
 In contrast to subtidal seagrasses, which maintain a relatively constant biomass throughout the year, intertidal seagrasses, like the one studied in this work, exhibit strong seasonal phenology [@davies2024sentinel].
@@
 
-Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sealevel rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global].
-and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
+Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sea level rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global] and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
 Our findings, particularly the improved discrimination of intertidal seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
@@
 High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
-Indeed, this approach could provide early warning alerts to local managers.
-
-Employing traditional sampling methods to monitor coastal ecosystems is time and resource-intensive, and the findings are often difficult to scale-up.
+Indeed, this approach could provide early warning alerts to local managers and complimentary to traditional sampling methods to monitor coastal ecosystems.
+These methods are generally time and resource-intensive, and the findings are often difficult to scale-up when applied alone.
 Earth Observation can bridge this gap and meet the needs for systematic monitoring coastal ecosystems over large areas [@papathanasopoulou2019satellite].
@@
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on coastal ecosystems.
-On-demand, multispectral drone observations at very high spatial-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth satellite data.
+On-demand, multispectral drone observations at very high spatial-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth data which can be used to develop machine-learning algorithm for satellite sensors [@davies2024intertidal].
 Spatially resolved data are indeed critical for calibrating and validating satellite remote sensing observations, thereby enhancing our capacity to monitor vast coastal areas.
@@
 Sentinel-2), and test whether the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
-The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection.
+The integration of drone technology facilitates a scalable approach to environmental surveillance while taking into account patchiness of secondary vegetation, offering significant advancements in the spatial and temporal resolution of data collection.
 This, in turn, supports the EU WFD's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.

### 2024-09-27 docs/_tex/index.tex
add results

@@
 effect of pixel resolution on the agreement, with a negative
-relationship (\[\beta = -1.0334 \times 10^{-8}, p < 0.001\]). This
+relationship (\(\beta = -1.0334 \times 10^{-8}, p < 0.001\)). This
 indicates that as pixel resolution increases, the proportion of the
@@
 Magnoliopsida showed a significant positive effect
-(\[\beta = 0.1202, p < 0.001\]), suggesting that this class was
+(\(\beta = 0.1202, p < 0.001\)), suggesting that this class was
 associated with a higher agreement.

### 2024-09-27 index.qmd
add results

@@
 
-The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($$\beta = -1.0334 \times 10^{-8}, p < 0.001$$).
+The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($\beta = -1.0334 \times 10^{-8}, p < 0.001$).
 This indicates that as pixel resolution increases, the proportion of the response variable decreases.
@@
 The vegetation classes also exhibited distinct effects on the agreement.
-Magnoliopsida showed a significant positive effect ($$\beta = 0.1202, p < 0.001$$), suggesting that this class was associated with a higher agreement.
+Magnoliopsida showed a significant positive effect ($\beta = 0.1202, p < 0.001$), suggesting that this class was associated with a higher agreement.
 

### 2024-09-27 docs/_tex/index.tex
add results

@@
 
-Amoung the high altitude flights, the one acquired over the inner part
-of Ria de Aveiro coastal lagoon covered the largest area with
-approximately 1.5 km² (Figure~\ref{fig-Boat}). This site was dominated
-by seagrass and red macroalgae. The classification provided consistent
-results, with a patchy seagrass meadow mixed with red macroalgae on the
-eastern part of the site. As shown in the zoom (Figure~\ref{fig-Boat}),
-the edges of the meadow were mixed with green macroalgae (\emph{Ulva
-sp.}), which the model agreed with (F1 score of 0.89 for green algae,
-0.97 for seagrass and 0.98 for red algae).
+Among the high altitude flights, the one acquired over the inner part of
+Ria de Aveiro coastal lagoon covered the largest area with approximately
+1.5 km² (Figure~\ref{fig-Boat}). This site was dominated by seagrass and
+red macroalgae. The classification provided consistent results, with a
+patchy seagrass meadow mixed with red macroalgae on the eastern part of
+the site. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of the
+meadow were mixed with green macroalgae (\emph{Ulva sp.}), which the
+model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass
+and 0.98 for red algae).
 
@@
 
-Figure~\ref{fig-pixelsize} shows an effect of the pixel size on the
-agreement between the two products. The highest resolution in which the
-resampling has been performed is 10 cm. At this resolution, the
-agreement has already decreased from 78\% (red algae) to 94\%
-(seagrass), depending on the class. As pixel size increases, the
-agreement between the products declines steadily for all classes. This
-decline is most pronounced for green algae, which experiences the
-sharpest drop in agreement as pixel size increases beyond 10 m, reaching
-below 0\% at a pixel size of 30 m. Seagrass maintain higher levels of
-agreement at coarser resolutions, although a clear decline is still
-observed, with seagrasses dropping from over 94\% at 10 cm to around
-88\% at 30 m. Brown algae and red algae show a more moderate decline
-compared to red algae, with agreement levels remaining around 62\% and
-40\%, respectively, at 30 m resolution.
+Figure~\ref{fig-pixelsize} demonstrated the effect of pixel size on the
+agreement between two products. The highest resolution at which
+resampling was performed was 10 cm. At this resolution, agreement rates
+had already decreased, ranging from 78\% for red algae to 94\% for
+seagrass, depending on the class. As pixel size increased, the agreement
+between the products steadily declined across all classes. This decline
+was most pronounced for green algae, which experienced the sharpest drop
+in agreement as pixel size surpassed 10 m, falling below 0\% at a 30 m
+pixel size. Seagrass maintained higher agreement levels at coarser
+resolutions, though a clear decline was still observed, dropping from
+over 94\% at 10 cm to around 88\% at 30 m. Brown algae and red algae
+showed a more moderate decline in comparison, with agreement levels at
+30 m resolution settling around 62\% and 40\%, respectively.
 

### 2024-09-27 index.qmd
add results

@@
 
-Amoung the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat).
+Among the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat).
 This site was dominated by seagrass and red macroalgae.
@@
 
-@fig-pixelsize shows an effect of the pixel size on the agreement between the two products.
-The highest resolution in which the resampling has been performed is 10 cm.
-At this resolution, the agreement has already decreased from 78% (red algae) to 94% (seagrass), depending on the class.
-As pixel size increases, the agreement between the products declines steadily for all classes.
-This decline is most pronounced for green algae, which experiences the sharpest drop in agreement as pixel size increases beyond 10 m, reaching below 0% at a pixel size of 30 m.
-Seagrass maintain higher levels of agreement at coarser resolutions, although a clear decline is still observed, with seagrasses dropping from over 94% at 10 cm to around 88% at 30 m.
-Brown algae and red algae show a more moderate decline compared to red algae, with agreement levels remaining around 62% and 40%, respectively, at 30 m resolution.
+@fig-pixelsize demonstrated the effect of pixel size on the agreement between two products.
+The highest resolution at which resampling was performed was 10 cm.
+At this resolution, agreement rates had already decreased, ranging from 78% for red algae to 94% for seagrass, depending on the class.
+As pixel size increased, the agreement between the products steadily declined across all classes.
+This decline was most pronounced for green algae, which experienced the sharpest drop in agreement as pixel size surpassed 10 m, falling below 0% at a 30 m pixel size.
+Seagrass maintained higher agreement levels at coarser resolutions, though a clear decline was still observed, dropping from over 94% at 10 cm to around 88% at 30 m.
+Brown algae and red algae showed a more moderate decline in comparison, with agreement levels at 30 m resolution settling around 62% and 40%, respectively.
 

### 2024-10-01 docs/_tex/index.tex
add updates

@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 
@@
 \makeatother
+
 \ifLuaTeX
@@
 oxygen production, protection against sea-level rise and coastline
-erosion, and mitigation of eutrophication \citetext{\citealp[
-]{unsworth2022}; \citealp{sousa2019blue}}. They serve as vital habitats
-for a diverse array of marine and terrestrial species, providing living,
-breeding, and feeding grounds \citetext{\citealp[
-]{gardner2018}; \citealp[ ]{Zoffoli2022}; \citealp{jankowska2019}}. Due
-to the concentration of human activities in coastal zones, seagrass
-meadows are directly exposed to and impacted by anthropogenic pressures.
-Global regression and fragmentation of seagrass meadows are currently
-observed due to climate change, diseases, urbanization, land
-reclamation, dredging, competition with alien species, and reduction in
-water quality \citetext{\citealp[ ]{nguyen2021}; \citealp[
-]{soissons2018}; \citealp[ ]{orth2006}; \citealp[ ]{lin2018}; \citealp[
-]{duffy2019}; \citealp[ ]{rasheed2011long}; \citealp[
-]{chefaoui2018dramatic}; \citealp{sousa2019blue}}. Both habitat
-fragmentation and reduction, in turn, can severely compromise the
-effectiveness of ecosystem services provided by seagrass meadows. While
-improvements in water quality and hydrodynamics have been recently
-reported in Europe, allowing an overall recovery of seagrass ecosystems
-at local and European scales, many coastal waters worldwide are still
-subjected to strong eutrophication processes \citetext{\citealp[
-]{deSantos2019}; \citealp[ ]{Zoffoli2021}; \citealp{sousa2019blue}}.
-Coastal eutrophication has been associated to excessive accumulation of
-green macroalgae, so-called green tides \citep{devlin2023nutrients}.
-Green tides produce shade and suffocation over seagrass individuals,
-thus threatening the health of seagrass ecosystems \citep{wang2022}.
+erosion, and mitigation of eutrophication
+\citep{unsworth2022, sousa2019blue}. They serve as vital habitats for a
+diverse array of marine and terrestrial species, providing living,
+breeding, and feeding grounds
+\citep{gardner2018, Zoffoli2022, jankowska2019}. Due to the
+concentration of human activities in coastal zones, seagrass meadows are
+directly exposed to and impacted by anthropogenic pressures. Global
+regression and fragmentation of seagrass meadows are currently observed
+due to climate change, diseases, urbanization, land reclamation,
+dredging, competition with alien species, and reduction in water quality
+\citep{nguyen2021, soissons2018, orth2006, lin2018, duffy2019, rasheed2011long, chefaoui2018dramatic, sousa2019blue}.
+Both habitat fragmentation and reduction, in turn, can severely
+compromise the effectiveness of ecosystem services provided by seagrass
+meadows. While improvements in water quality and hydrodynamics have been
+recently reported in Europe, allowing an overall recovery of seagrass
+ecosystems at local and European scales, many coastal waters worldwide
+are still subjected to strong eutrophication processes
+\citep{deSantos2019, Zoffoli2021, sousa2019blue}. Coastal eutrophication
+has been associated to excessive accumulation of green macroalgae,
+so-called green tides \citep{devlin2023nutrients}. Green tides produce
+shade and suffocation over seagrass individuals, thus threatening the
+health of seagrass ecosystems \citep{wang2022}.
 
@@
 real-time and consistent retrieval of seagrass EOVs and EBVs over
-extensive meadows. \citetext{\citealp[ ]{Zoffoli2021}; \citealp[
-]{xu2021}; \citealp[ ]{Traganos2018}; \citealp{coffer2023}}
+extensive meadows. \citep{Zoffoli2021, xu2021, Traganos2018, coffer2023}
 
@@
 particular Chlorophyceae (green algae) and marine Magnoliopsida
-(seagrass) share the same pigment composition \citetext{\citealp[
-]{ralph2002}; \citealp{Douay2022}}. Therefore, to someone not
-specialized in the field, their spectral signatures may appear to be
-alike \citetext{\citealp[ ]{Davies2023}; \citealp{bannari2022}}.
-Recently, using advanced machine-learning algorithms trained with a
-large hyperspectral library of more than 300 field reflectance spectra,
-\citep{Davies2023} demonstrated that it was possible to discriminate
-Magnoliopsida from Chlorophyceae using radiometric data acquired at
-Sentinel-2 's spectral resolution. However the application of this
-approach to satellite RS remains to be validated. Moreover patches of
-green algae can develop at small spatial scales that are not observable
-using non-commercial satellite imagery \citep{tuya2013}, especially
-during the initial stage of a green tide.
+(seagrass) share the same pigment composition
+\citep{ralph2002, Douay2022}. Therefore, to someone not specialized in
+the field, their spectral signatures may appear to be alike
+\citep{Davies2023, bannari2022}. Recently, using advanced
+machine-learning algorithms trained with a large hyperspectral library
+of more than 300 field reflectance spectra, \citep{Davies2023}
+demonstrated that it was possible to discriminate Magnoliopsida from
+Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral
+resolution. However the application of this approach to satellite RS
+remains to be validated. Moreover patches of green algae can develop at
+small spatial scales that are not observable using non-commercial
+satellite imagery \citep{tuya2013}, especially during the initial stage
+of a green tide.
 
@@
 resolutions (pixel size from mm to cm) while capturing data at
-multi-spectral resolution \citetext{\citealp[
-]{fairley2022drone}; \citealp{oh2017use}}. The versatility of drones
-allows for their application across a diverse thematic range , from
-coastal zone management \citetext{\citealp[ ]{adade2021}; \citealp[
-]{casella2020}; \citealp{angnuureng2022}} to mapping species
-distribution \citetext{\citealp[ ]{joyce2023}; \citealp[
-]{tallam2023}; \citealp[ ]{Roca2022}; \citealp[ ]{Roman2021}; \citealp[
-]{Brunier2022Topographic}; \citealp{sousa2019blue}}. However, when
-applied to coastal habitat mapping, most case studies were previously
-limited to a single flight, restricting the generalizability of their
-application over wider geographical scales \citetext{\citealp[
-]{Roman2021}; \citealp[ ]{collin2019improving}; \citealp[
-]{rossiter2020uav}; \citealp{Brunier2022Topographic}}. The present study
-aimed at analyzing the potential of multispectral drone RS to map
-intertidal macrophytes over a diverse biogeographical range, with a
-particular focus on discriminating Magnoliopsida and Chlorophyceae
-(Seagrass and Green Algae, respectively). Ten drone flights were
-performed over soft-bottom intertidal areas along the Atlantic
-coastlines of two European countries (France and Portugal), covering a
-wide range of habitats, from monospecific seagrass meadows to meadows
-mixed with green, or red macroalgae. A deep learning algorithm was
-trained and validated for macrophyte discrimination, emphasizing
+multi-spectral resolution \citep{fairley2022drone, oh2017use}. The
+versatility of drones allows for their application across a diverse
+thematic range , from coastal zone management
+\citep{adade2021, casella2020, angnuureng2022} to mapping species
+distribution
+\citep{joyce2023, tallam2023, Roca2022, Roman2021, Brunier2022Topographic, sousa2019blue}.
+However, when applied to coastal habitat mapping, most case studies were
+previously limited to a single flight, restricting the generalizability
+of their application over wider geographical scales
+\citep{Roman2021, collin2019improving, rossiter2020uav, Brunier2022Topographic}.
+The present study aimed at analyzing the potential of multispectral
+drone RS to map intertidal macrophytes over a diverse biogeographical
+range, with a particular focus on discriminating Magnoliopsida and
+Chlorophyceae (Seagrass and Green Algae, respectively). Ten drone
+flights were performed over soft-bottom intertidal areas along the
+Atlantic coastlines of two European countries (France and Portugal),
+covering a wide range of habitats, from monospecific seagrass meadows to
+meadows mixed with green, or red macroalgae. A deep learning algorithm
+was trained and validated for macrophyte discrimination, emphasizing
 applicability across diverse sites without a loss of prediction
@@
 scaling differences between spectra and to limit the effect of biomass
-on the spectra shape \citetext{\citealp[
-]{Douay2022}; \citealp{Davies2023}}.
+on the spectra shape \citep{Douay2022, Davies2023}.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png}
+\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png}
 
@@
 
-Figure~\ref{fig-pixelsize} demonstrated the effect of pixel size on the
-agreement between two products. The highest resolution at which
-resampling was performed was 10 cm. At this resolution, agreement rates
-had already decreased, ranging from 78\% for red algae to 94\% for
-seagrass, depending on the class. As pixel size increased, the agreement
-between the products steadily declined across all classes. This decline
-was most pronounced for green algae, which experienced the sharpest drop
-in agreement as pixel size surpassed 10 m, falling below 0\% at a 30 m
-pixel size. Seagrass maintained higher agreement levels at coarser
-resolutions, though a clear decline was still observed, dropping from
-over 94\% at 10 cm to around 88\% at 30 m. Brown algae and red algae
-showed a more moderate decline in comparison, with agreement levels at
-30 m resolution settling around 62\% and 40\%, respectively.
+Figure~\ref{fig-pixelsize} illustrated the relationship between
+predicted area loss for different vegetation types and map resolution.
+The highest resolution used for resampling was 10 cm, at which point
+vegetation area had already started to decrease. The losses ranged from
+21\% for red algae to 5\% for seagrass, depending on the vegetation
+type. As pixel size increased, the retrieved vegetation area decreased
+for all classes. This reduction was most severe for green algae, which
+experienced a sharp decline once pixel size exceeded 10 m, culminating
+in a complete loss (100\%) at a 30 m pixel size. Seagrass exhibited the
+lowest loss at coarser resolutions, though it still showed a clear
+decline, with area loss increasing from over 5\% at 10 cm to around 11\%
+at 30 m. Brown algae and red algae experienced more moderate declines,
+with losses at 30 m resolution reaching approximately 37\% and 59\%,
+respectively.
 
@@
 
-The Generalized Linear Model (GLM) analysis revealed a significant
-effect of pixel resolution on the agreement, with a negative
-relationship (\(\beta = -1.0334 \times 10^{-8}, p < 0.001\)). This
-indicates that as pixel resolution increases, the proportion of the
-response variable decreases.
-
-The vegetation classes also exhibited distinct effects on the agreement.
-Magnoliopsida showed a significant positive effect
-(\(\beta = 0.1202, p < 0.001\)), suggesting that this class was
-associated with a higher agreement.
+The Generalized Linear Model (GLM) analysis showed a significant effect
+of pixel resolution on the mapped vegetation area, indicating a positive
+relationship between resolution and area loss
+(\(\beta = 0.067, p < 0.001\)). This suggests that as pixel resolution
+increases, the mapped area of each vegetation type decreases.
 
@@
 resolution. The discrimination of seagrasses from green macroalgae
-presents is spectrally challenging \citetext{\citealp[
-]{oiry2021using}; \citealp[
-]{bannari2022}; \citealp{veettil2020opportunities}}. These two
+presents is spectrally challenging
+\citep{oiry2021using, bannari2022, veettil2020opportunities}. These two
 macrophytes share a similar pigment composition: chlorophyll-a (common
@@
 \citep{bargain2013seasonal}, cellular structure as well as in the
-orientation of the plant at the sediment surface \citetext{\citealp[
-]{beach1997vivo}; \citealp[
-]{kirk1994light}; \citealp{hedley2018influence}}.
+orientation of the plant at the sediment surface
+\citep{beach1997vivo, kirk1994light, hedley2018influence}.
 
@@
 reflecting the plants' adaptations to different environmental conditions
-\citetext{\citealp[ ]{bargain2013seasonal}; \citealp{legare2022remote}}.
-Standardization of spectral signatures helps to mitigate the impact of
-changing biomass on the spectral profile, enabling the development of a
-model that can reliably predict vegetation across different geographical
-locations and seasons. This approach allows for consistent
-classification of vegetation despite variations in biomass and
-fluctuations in light conditions, providing a robust tool for monitoring
-and predicting vegetation dynamics \citetext{\citealp[
-]{fyfe2003spatial}; \citealp[
-]{COSTA2021107018}; \citealp{piaser2023impact}}. We found 90 \% seagrass
-cover was necessary at an 8 cm resolution for confident prediction of
-its presence (Figure~\ref{fig-upscaling}). However, due to the strong
-phenology of intertidal seagrass meadows in Europe, the period when a
-meadow is well-established can be temporally restricted, limiting the
-ideal window for accurate detection.
+\citep{bargain2013seasonal, legare2022remote}. Standardization of
+spectral signatures helps to mitigate the impact of changing biomass on
+the spectral profile, enabling the development of a model that can
+reliably predict vegetation across different geographical locations and
+seasons. This approach allows for consistent classification of
+vegetation despite variations in biomass and fluctuations in light
+conditions, providing a robust tool for monitoring and predicting
+vegetation dynamics
+\citep{fyfe2003spatial, COSTA2021107018, piaser2023impact}. We found 90
+\% seagrass cover was necessary at an 8 cm resolution for confident
+prediction of its presence (Figure~\ref{fig-upscaling}). However, due to
+the strong phenology of intertidal seagrass meadows in Europe, the
+period when a meadow is well-established can be temporally restricted,
+limiting the ideal window for accurate detection.
 
@@
 continue impacting coastal ecosystems in the future
-\citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
-]{holon2018predictive}; \citealp{marquet2024global}} and the demand for
-meaningful and efficient monitoring of coastal habitats has never been
-higher\citetext{\citealp[ ]{muller2018satellite}; \citealp[
-]{villalobos2023remote}; \citealp{oiry2021using}}. Our findings,
-particularly the improved discrimination of intertidal seagrass and
-green macroalgae from other intertidal vegetation classes, highlight the
-potential of drone-based remote sensing to support diverse applications,
-from conservation of biodiversity to climate change adaptation
-strategies.
+\citep{SCHIBALSKI2022101414, holon2018predictive, marquet2024global} and
+the demand for meaningful and efficient monitoring of coastal habitats
+has never been
+higher\citep{muller2018satellite, villalobos2023remote, oiry2021using}.
+Our findings, particularly the improved discrimination of intertidal
+seagrass and green macroalgae from other intertidal vegetation classes,
+highlight the potential of drone-based remote sensing to support diverse
+applications, from conservation of biodiversity to climate change
+adaptation strategies.
 
 Because of coastal eutrophication, macroalgal blooms are becoming
-increasingly common in many regions around the world \citetext{\citealp[
-]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
-negative impacts on human health and local economic activities,
-including human health, fishing and aquaculture, tourism, and
-recreational activities \citetext{\citealp[
-]{villares1999nitrogen}; \citealp{ye2011green}}. The first green tide
-events (i.e.~bloom of green macroalgae of the genus \emph{Ulva}) were
-reported in Brittany, France, back in the 1970s and have since been a
-concern for local stakeholders and economic activities
-\citep{menesguen2018marees}. Some regions of the world have witnessed an
-increase in brown macroalgae blooms, predominantly involving algae of
-the genus \emph{Sargassum} washing along the Caribbean coastlines
-\citep{louime2017sargassum}, and more recently \emph{Rugulopteryx
-okamurea} in southern Europe \citep{Roca2022}. Satellite remote sensing
-has proven to be a valuable tool for mapping the spatial and temporal
-extent of macroalgal blooms worldwide. However, due to limitations in
-spatial resolution, it can only effectively map well-developed blooms
-\citetext{\citealp[ ]{rs13081408}; \citealp[
-]{klemas2012remote}; \citealp{haro2023biointertidal}}. High spatial
-resolution drone imagery, coupled with an accurate classification
-algorithm, could be used to map the early stages of macroalgal blooms in
-areas known to have regular blooms or in new sites. Indeed, this
-approach could provide early warning alerts to local managers and
-complimentary to traditional sampling methods to monitor coastal
-ecosystems. These methods are generally time and resource-intensive, and
-the findings are often difficult to scale-up when applied alone. Earth
-Observation can bridge this gap and meet the needs for systematic
-monitoring coastal ecosystems over large areas
+increasingly common in many regions around the world
+\citep{sutton2011european, ye2011green}. These blooms can have negative
+impacts on human health and local economic activities, including human
+health, fishing and aquaculture, tourism, and recreational activities
+\citep{villares1999nitrogen, ye2011green}. The first green tide events
+(i.e.~bloom of green macroalgae of the genus \emph{Ulva}) were reported
+in Brittany, France, back in the 1970s and have since been a concern for
+local stakeholders and economic activities \citep{menesguen2018marees}.
+Some regions of the world have witnessed an increase in brown macroalgae
+blooms, predominantly involving algae of the genus \emph{Sargassum}
+washing along the Caribbean coastlines \citep{louime2017sargassum}, and
+more recently \emph{Rugulopteryx okamurea} in southern Europe
+\citep{Roca2022}. Satellite remote sensing has proven to be a valuable
+tool for mapping the spatial and temporal extent of macroalgal blooms
+worldwide. However, due to limitations in spatial resolution, it can
+only effectively map well-developed blooms
+\citep{rs13081408, klemas2012remote, haro2023biointertidal}. High
+spatial resolution drone imagery, coupled with an accurate
+classification algorithm, could be used to map the early stages of
+macroalgal blooms in areas known to have regular blooms or in new sites.
+Indeed, this approach could provide early warning alerts to local
+managers and complimentary to traditional sampling methods to monitor
+coastal ecosystems. These methods are generally time and
+resource-intensive, and the findings are often difficult to scale-up
+when applied alone. Earth Observation can bridge this gap and meet the
+needs for systematic monitoring coastal ecosystems over large areas
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
@@
 monitoring of entire ecosystems over extended time periods
-\citetext{\citealp[ ]{ratnarajah2023monitoring}; \citealp{Zoffoli2021}}.
-The Water Framework Directive \citep{WFD2000} mandates the achievement
-and maintenance of ``good ecological status'' for all European waters,
-which necessitates a comprehensive understanding and monitoring of
-aquatic ecosystems, including coastal habitats like seagrass beds
-\citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
-]{nordlund2024one}; \citealp{Zoffoli2021}}.
+\citep{ratnarajah2023monitoring, Zoffoli2021}. The Water Framework
+Directive \citep{WFD2000} mandates the achievement and maintenance of
+``good ecological status'' for all European waters, which necessitates a
+comprehensive understanding and monitoring of aquatic ecosystems,
+including coastal habitats like seagrass beds
+\citep{foden2007angiosperms, nordlund2024one, Zoffoli2021}.
 

### 2024-10-01 index.qmd
add updates

@@
 
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png")
 
@@
   # ungroup() %>% 
-  mutate(prop = agreed/n_obs) %>% 
+  mutate(prop = agreed/n_obs,
+         loss = 1-prop) %>% 
   as_tibble() %>% 
   mutate(true_fct = as.factor(true),
-         area = res*res)
+         area = (res/100)*(res/100))
 
@@
 total %>% 
-  ggplot(aes(x = res, y = prop, group = true, color =true_fct))+
+  ggplot(aes(x = area, y = loss, group = true, color =true_fct))+
   geom_line()+
@@
 
-glm_res_true <- glm(prop ~ area*true_fct , data = total)
+glm_res_true <- glm(loss ~ area*true_fct , data = total)
 # glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
@@
   group_by(res, true) %>% 
-  reframe(mean = mean(prop))
+  reframe(mean = mean(loss))
 
@@
                  "8" = "#42c9bc")
-
+  a <- NewData %>% 
+  dplyr::filter(true_fct != 1,
+                true_fct != 6,
+                true_fct != 7,
+                true_fct != 8) 
 (plot <- NewData %>% 
@@
     ggplot()+
-  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
+  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                   color = true_fct, group = true_fct, fill = true_fct
                   ), alpha = 0.2)+
-  geom_line(aes(x = sqrt(area)/100, y = fit,
+  geom_line(aes(x = sqrt(area), y = fit,
                 color = true_fct, group = true_fct
@@
   xlab("Resolution (m)") +
-  ylab("Agreement")+
+  ylab("Predicted area loss")+
   theme(axis.title = element_text(size = 20),
@@
 
-@fig-pixelsize demonstrated the effect of pixel size on the agreement between two products.
-The highest resolution at which resampling was performed was 10 cm.
-At this resolution, agreement rates had already decreased, ranging from 78% for red algae to 94% for seagrass, depending on the class.
-As pixel size increased, the agreement between the products steadily declined across all classes.
-This decline was most pronounced for green algae, which experienced the sharpest drop in agreement as pixel size surpassed 10 m, falling below 0% at a 30 m pixel size.
-Seagrass maintained higher agreement levels at coarser resolutions, though a clear decline was still observed, dropping from over 94% at 10 cm to around 88% at 30 m.
-Brown algae and red algae showed a more moderate decline in comparison, with agreement levels at 30 m resolution settling around 62% and 40%, respectively.
+@fig-pixelsize illustrated the relationship between predicted area loss for different vegetation types and map resolution.
+The highest resolution used for resampling was 10 cm, at which point vegetation area had already started to decrease.
+The losses ranged from 21% for red algae to 5% for seagrass, depending on the vegetation type.
+As pixel size increased, the retrieved vegetation area decreased for all classes.
+This reduction was most severe for green algae, which experienced a sharp decline once pixel size exceeded 10 m, culminating in a complete loss (100%) at a 30 m pixel size.
+Seagrass exhibited the lowest loss at coarser resolutions, though it still showed a clear decline, with area loss increasing from over 5% at 10 cm to around 11% at 30 m.
+Brown algae and red algae experienced more moderate declines, with losses at 30 m resolution reaching approximately 37% and 59%, respectively.
 
@@
 
-The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($\beta = -1.0334 \times 10^{-8}, p < 0.001$).
-This indicates that as pixel resolution increases, the proportion of the response variable decreases.
-
-The vegetation classes also exhibited distinct effects on the agreement.
-Magnoliopsida showed a significant positive effect ($\beta = 0.1202, p < 0.001$), suggesting that this class was associated with a higher agreement.
+The Generalized Linear Model (GLM) analysis showed a significant effect of pixel resolution on the mapped vegetation area, indicating a positive relationship between resolution and area loss ($\beta = 0.067, p < 0.001$).
+This suggests that as pixel resolution increases, the mapped area of each vegetation type decreases.
 

### 2024-10-01 docs/_tex/index.tex
adding rescaling

@@
 
-To assess the impact of spatial resolution on the model's output, the
-reflectance of each flight's orthomosaic was spatially resampled using
-the average method from the Terra package in R. DISCOV was then applied
-to these resampled rasters. The results were compared to the original
-model predictions, which were resampled using the mode method from the
-Terra package in R. For each resolution and each class of the model, an
-agreement percentage was obtained, where a score of 100 indicates that
-all pixels in the two products are identical, and a score of 0 indicates
-that all pixels are different.
-
-We used a Generalized Linear Model (GLM) with a Gaussian family and an
-identity link function to investigate the relationship between pixel
+To evaluate the impact of spatial resolution on the model's output, we
+resampled the reflectance of each flight's orthomosaic using the average
+method from the Terra package in R. DISCOV was then applied to these
+resampled rasters, and the results were compared to the original model
+predictions. For each resolution and vegetation class, we calculated
+predicted area loss, where a score of 0 indicates no area loss during
+resampling, and a score of 100 indicates complete loss of vegetation.
+
+We used a Generalized Linear Model (GLM) with a Gaussian family and
+identity link function to examine the relationship between pixel
 resolution, vegetation class, and their interaction on the response
-variable, the agreement. The formula for the model was:
+variable (the loss of vegetation area). The model formula was as
+follows:
 
 \begin{equation}\phantomsection\label{eq-gam}{
-Agreement \sim  Resolution \times VegetationClass
+%loss \sim  Resolution \times VegetationClass
 }\end{equation}
@@
 
-Figure~\ref{fig-pixelsize} illustrated the relationship between
-predicted area loss for different vegetation types and map resolution.
-The highest resolution used for resampling was 10 cm, at which point
-vegetation area had already started to decrease. The losses ranged from
-21\% for red algae to 5\% for seagrass, depending on the vegetation
-type. As pixel size increased, the retrieved vegetation area decreased
-for all classes. This reduction was most severe for green algae, which
-experienced a sharp decline once pixel size exceeded 10 m, culminating
-in a complete loss (100\%) at a 30 m pixel size. Seagrass exhibited the
-lowest loss at coarser resolutions, though it still showed a clear
-decline, with area loss increasing from over 5\% at 10 cm to around 11\%
-at 30 m. Brown algae and red algae experienced more moderate declines,
-with losses at 30 m resolution reaching approximately 37\% and 59\%,
-respectively.
+Figure~\ref{fig-pixelsize} illustrates the relationship between
+predicted area loss for various vegetation types and map resolution. At
+a fine resolution of 1m, changes in the retrieved area for each
+vegetation type are minimal. Green algae shows the highest loss rate,
+with 1.2\% area lost compared to the raw resolution (8cm). As the
+resolution coarsens to 10m, area loss becomes significant, with green
+algae again experiencing the greatest reduction (12\% compared to 8cm)
+and seagrass showing the smallest loss (1.3\%). At a resolution of 30m,
+all green algae have been lost (100\% compared to 8cm), while seagrass
+experiences a relatively small reduction of 11\%. Brown algae and red
+algae show moderate declines, with losses at 30m resolution reaching
+approximately 37\% and 59\%, respectively.
 
@@
 
-\caption{\label{fig-pixelsize}Coucou}
+\caption{\label{fig-pixelsize}Predicted area loss for different
+vegetation types (green algae, seagrass, brown algae, red algae) as a
+function of spatial resolution. Lines represent generalized linear model
+(GLM) predictions, and shaded areas indicate standard errors. As
+resolution decreases, predicted area loss increases for all vegetation
+types, with green algae showing the highest loss and seagrass the
+smallest at coarser resolutions.}
 
@@
 
-The results of Figure~\ref{fig-pixelsize} highlight the importance of
-pixel resolution in maintaining accurate classification and agreement
-between products derived from remote sensing data with different spatial
-resolutions. As the pixel size increases, a consistent decline in
-agreement is observed across all vegetation classes, with more
-pronounced effects for certain classes, such as green algae. This
-phenomenon underscores the sensitivity of spatial resolution in
-distinguishing smaller or patchier vegetation features. Green algae,
-being more patchy in all our study sites, demonstrates the steepest drop
-in agreement with increasing pixel size, which aligns with expectations
-given the limitations of coarser resolution in capturing fine-scale
-details.
-
-This relationship between resolution and agreement has significant
-implications for satellite platforms like Sentinel-2 and Landsat. Both
-satellites, commonly used in marine and coastal vegetation studies,
-offer medium-resolution imagery, with pixel sizes of 10 m and 30 m,
+The results of Figure~\ref{fig-pixelsize} emphasize the critical role of
+pixel resolution in accurately retrieving vegetation area from remote
+sensing data. As pixel size increases, a consistent decline in area
+retrieval is observed across all vegetation types, with more pronounced
+effects for certain types, such as green algae. This highlights the
+sensitivity of spatial resolution in detecting smaller or more
+fragmented vegetation features. Green algae, being particularly patchy
+across all study sites, shows the steepest decline in area agreement as
+pixel size increases, which aligns with expectations given the
+limitations of coarser resolution in capturing fine-scale details.
+
+This resolution-area relationship has important implications for
+satellite platforms like Sentinel-2 and Landsat, which are commonly used
+in marine and coastal vegetation studies. Both satellites offer
+medium-resolution imagery, with pixel sizes of 10m and 30m,
 respectively. While these resolutions are suitable for broad-scale
 environmental monitoring, they may struggle to capture finer-scale
-heterogeneity, especially for more fragmented or patchy vegetation types
-like green algae. The results suggest that while coarser resolutions
-like those of Landsat are sufficient for seagrass and other more
-homogeneous vegetation types, higher resolutions are essential for
-accurately mapping species like green algae.
+heterogeneity, particularly in fragmented vegetation like green algae.
+The findings suggest that, while coarser resolutions like those of
+Landsat may be adequate for more homogeneous types, such as seagrass,
+higher resolutions are essential for accurately mapping patchier species
+like green algae. These findings have direct implications for
+environmental management and conservation planning. Overlooking
+fine-scale vegetation features, such as those seen in green algae, could
+result in inadequate protection or restoration efforts, particularly in
+ecologically sensitive coastal zones, as early stages of green tides
+could be challenging to monitor at coarse resolutions.
+
+Higher-resolution imagery offers more accurate vegetation mapping but
+comes with trade-offs. As resolution increases, data costs rise, and
+processing becomes more resource-intensive due to the larger file sizes
+and computational demands. Additionally, high-resolution data requires
+more storage and can slow down real-time applications. For large-scale
+monitoring or homogeneous vegetation types, medium-resolution platforms
+like Sentinel-2 are often sufficient. However, when mapping fragmented
+vegetation like green algae, the precision provided by higher-resolution
+imagery is crucial, despite the additional costs and processing
+challenges it imposes.
 

### 2024-10-01 index.qmd
adding rescaling

@@
 
-To assess the impact of spatial resolution on the model's output, the reflectance of each flight's orthomosaic was spatially resampled using the average method from the Terra package in R.
-DISCOV was then applied to these resampled rasters.
-The results were compared to the original model predictions, which were resampled using the mode method from the Terra package in R.
-For each resolution and each class of the model, an agreement percentage was obtained, where a score of 100 indicates that all pixels in the two products are identical, and a score of 0 indicates that all pixels are different.
-
-We used a Generalized Linear Model (GLM) with a Gaussian family and an identity link function to investigate the relationship between pixel resolution, vegetation class, and their interaction on the response variable, the agreement.
-The formula for the model was:
+To evaluate the impact of spatial resolution on the model’s output, we resampled the reflectance of each flight's orthomosaic using the average method from the Terra package in R.
+DISCOV was then applied to these resampled rasters, and the results were compared to the original model predictions.
+For each resolution and vegetation class, we calculated predicted area loss, where a score of 0 indicates no area loss during resampling, and a score of 100 indicates complete loss of vegetation.
+
+We used a Generalized Linear Model (GLM) with a Gaussian family and identity link function to examine the relationship between pixel resolution, vegetation class, and their interaction on the response variable (the loss of vegetation area).
+The model formula was as follows:
 
 $$
-Agreement \sim  Resolution \times VegetationClass
+%loss \sim  Resolution \times VegetationClass
 $$ {#eq-gam}
@@
 
+total <-  total %>% 
+  mutate(loss = 1-prop)
 total %>% 
@@
          se = pred$se.fit*100,
-         true_fct=(true_fct))
+         true_fct=(true_fct),
+         res = sqrt(area)/100) %>% 
+  group_by(true_fct) %>% 
+  mutate(fitted = ((fit-min(fit))/(max(fit)-min(fit)))*(max(fit)/100),
+         fitted_se = ((se-min(se))/(max(se)-min(se)))*(max(se)/100))
 
@@
                  "8" = "#42c9bc")
-  a <- NewData %>% 
-  dplyr::filter(true_fct != 1,
-                true_fct != 6,
-                true_fct != 7,
-                true_fct != 8) 
+
 (plot <- NewData %>% 
@@
     ggplot()+
-  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
+  geom_ribbon(aes(x = sqrt(area)/100, y = fitted*100, ymax = (fitted+fitted_se)*100, ymin = (fitted-fitted_se)*100,
                   color = true_fct, group = true_fct, fill = true_fct
                   ), alpha = 0.2)+
-  geom_line(aes(x = sqrt(area), y = fit,
+  geom_line(aes(x = sqrt(area)/100, y = fitted*100,
                 color = true_fct, group = true_fct
@@
 
-@fig-pixelsize illustrated the relationship between predicted area loss for different vegetation types and map resolution.
-The highest resolution used for resampling was 10 cm, at which point vegetation area had already started to decrease.
-The losses ranged from 21% for red algae to 5% for seagrass, depending on the vegetation type.
-As pixel size increased, the retrieved vegetation area decreased for all classes.
-This reduction was most severe for green algae, which experienced a sharp decline once pixel size exceeded 10 m, culminating in a complete loss (100%) at a 30 m pixel size.
-Seagrass exhibited the lowest loss at coarser resolutions, though it still showed a clear decline, with area loss increasing from over 5% at 10 cm to around 11% at 30 m.
-Brown algae and red algae experienced more moderate declines, with losses at 30 m resolution reaching approximately 37% and 59%, respectively.
+```{r vegetation loss}
+#| cache: false
+#| echo: false
+#| warning: false
+#| eval: false
+
+df_resampled_img <- list.files("Data/Predictions/Resampled",full.names = T) %>% 
+  as_tibble() %>% 
+  rename(path = "value") %>% 
+  mutate(name = gsub(".*/","",path),
+         type = case_when(str_detect(name, "_prob.tif") ~ "Prob",
+                          T ~ "Pred")) %>% 
+  dplyr::filter(type == "Pred") %>% 
+  mutate(res =sub(".*_(\\d+)cm_.*", "\\1", name) %>% as.numeric(),
+         ortho_name  = sub("_(\\d+)cm_.*", "", name)) %>% 
+  arrange(ortho_name,res) %>% 
+  mutate(site = case_when(str_detect(ortho_name, "Aveiro_1506_Highest") ~ "Aveiro",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_1") ~ "Boat1",
+                          str_detect(ortho_name, "Aveiro_boat_1706_flight_2") ~ "Boat2",
+                          str_detect(ortho_name, "NoirmoutierNorthDikeSite") ~ "NorthDike",
+                          str_detect(ortho_name, "Duer_15072022_120m") ~ "Duer",
+                          str_detect(ortho_name, "handfisher_Ortho") ~ "handfisher_Ortho",
+                          str_detect(ortho_name, "Horse_rooster") ~ "Horse_rooster",
+                          str_detect(ortho_name, "fl1_120m_handfisher_old") ~ "fl1_120m_handfisher_old",
+                          str_detect(ortho_name, "fl2_120m_handfisher_old") ~ "fl2_120m_handfisher_old",
+                          T ~ NA)) %>% 
+  dplyr::filter(!site == "handfisher_Ortho",
+                !site == "Duer") %>% 
+  dplyr::select(-ortho_name)
+
+native_res <- df_resampled_img %>% 
+  dplyr::filter(res == 10)
+
+  for(i in 1:nrow(native_res)){
+
+    print(i)
+
+    img <- rast(native_res$path[i])
+
+    names(img) <- c("pred")
+
+    df_img <- img %>%  
+      as.data.frame() %>% 
+      dplyr::filter(!pred == 0) %>% 
+      group_by(pred) %>% 
+      reframe(n_obs = n()) %>% 
+      dplyr::mutate(res = native_res$res[i],
+                    site = native_res$site[i],
+                    px_area = (res/100)*(res/100),
+                    area_vegetation = n_obs*px_area) %>% 
+      dplyr::select(-c(px_area,n_obs)) %>% 
+      rename(area_RAW  = area_vegetation)
+
+    if(i == 1){
+      df_native <- df_img
+    }else{
+      df_native <- rbind(df_native,df_img)
+    }
+  }
+
+  for(i in 1:nrow(df_resampled_img)){
+
+    print(i)
+
+    img <- rast(df_resampled_img$path[i])
+
+    names(img) <- c("pred")
+
+    df_img <- img %>%  
+      as.data.frame() %>% 
+      dplyr::filter(!pred == 0) %>% 
+      group_by(pred) %>% 
+      reframe(n_obs = n()) %>% 
+      dplyr::mutate(res = df_resampled_img$res[i],
+                    site = df_resampled_img$site[i],
+                    px_area = (res/100)*(res/100),
+                    area_vegetation = n_obs*px_area) %>% 
+      dplyr::select(-c(px_area,n_obs)) %>% 
+      rename(area_resampled  = area_vegetation)
+
+    if(i == 1){
+      df_resampled <- df_img
+    }else{
+      df_resampled <- rbind(df_resampled,df_img)
+    }
+  }
+
+# df_compare <- read.csv("Data/Resampled_saved_data.csv")
+
+df_area_compare <- df_resampled %>% 
+  # select(-res) %>% 
+  left_join(df_native %>% dplyr::select(-res), by = c("site","pred")) %>% 
+  mutate(loss = abs((area_resampled-area_RAW)/(area_resampled+area_RAW)),
+          class_fct = as.factor(pred),
+         area = res*res)
+
+df_area_compare %>% 
+  dplyr::filter(class_fct != 1,
+                class_fct != 6,
+                class_fct != 7,
+                class_fct != 8) %>%  
+  # group_by(area,class_fct) %>% 
+  # reframe(loss = mean(loss)) %>% 
+  ggplot(aes(x = area, y = loss, colour = class_fct))+
+  geom_point()+
+  geom_smooth(method = "gam")+
+    scale_color_manual(name = NULL,
+                      values = cols_fill,
+                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))
+
+glm_res_true <- glm(loss ~ area*class_fct , data = df_area_compare)
+# glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
+
+summary(glm_res_true)
+
+Utilities.Package::Model_Check(glm_res_true)
+
+NewData<-expand_grid(area=unique(df_area_compare$area),
+                    class_fct=unique(df_area_compare$class_fct))
+
+pred <- predict(glm_res_true, NewData, se.fit = T, type = "link")
+
+NewData <- NewData %>% 
+  mutate(fit = pred$fit*100,
+         se = pred$se.fit*100)
+
+  cols_fill <- c("1" = "#DAA520",
+                 "2" = "#b3ff1a",
+                 "3" = "#389318",
+                 "4" = "#873e23",
+                 "5" = "#b3002d",
+                 "6" = "#70543e",
+                 "7" = 'grey',
+                 "8" = "#42c9bc")
+
+  a <- NewData %>% 
+  dplyr::filter(class_fct != 1,
+                class_fct != 6,
+                class_fct != 7,
+                class_fct != 8)
+
+(plot <- NewData %>% 
+  dplyr::filter(class_fct != 1,
+                class_fct != 6,
+                class_fct != 7,
+                class_fct != 8) %>%
+    ggplot()+
+  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
+                  color = class_fct, group = class_fct, fill = class_fct
+                  ), alpha = 0.2)+
+  geom_line(aes(x = sqrt(area)/100, y = fit,
+                color = class_fct, group = class_fct
+                ))+
+      scale_fill_manual(name = NULL,
+                        values = cols_fill,
+                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
+    scale_color_manual(name = NULL,
+                      values = cols_fill,
+                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
+  theme_Bede()+
+    # xlim(0,1)+
+  xlab("Resolution (m)") +
+  ylab("Predicted area loss")+
+  theme(axis.title = element_text(size = 20),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        legend.text = element_text(size = 15),
+        legend.key.size = unit(1, "cm")
+          )
+
+      )
+
+```
+
+@fig-pixelsize illustrates the relationship between predicted area loss for various vegetation types and map resolution.
+At a fine resolution of 1m, changes in the retrieved area for each vegetation type are minimal.
+Green algae shows the highest loss rate, with 1.2% area lost compared to the raw resolution (8cm).
+As the resolution coarsens to 10m, area loss becomes significant, with green algae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
+At a resolution of 30m, all green algae have been lost (100% compared to 8cm), while seagrass experiences a relatively small reduction of 11%.
+Brown algae and red algae show moderate declines, with losses at 30m resolution reaching approximately 37% and 59%, respectively.
 
@@
 #| warning: false
-#| fig-cap: Coucou
+#| fig-cap: Predicted area loss for different vegetation types (green algae, seagrass, brown algae, red algae) as a function of spatial resolution.
+Lines represent generalized linear model (GLM) predictions, and shaded areas indicate standard errors.
+As resolution decreases, predicted area loss increases for all vegetation types, with green algae showing the highest loss and seagrass the smallest at coarser resolutions.
 #| label: fig-pixelsize
@@
 
-The results of @fig-pixelsize highlight the importance of pixel resolution in maintaining accurate classification and agreement between products derived from remote sensing data with different spatial resolutions.
-As the pixel size increases, a consistent decline in agreement is observed across all vegetation classes, with more pronounced effects for certain classes, such as green algae.
-This phenomenon underscores the sensitivity of spatial resolution in distinguishing smaller or patchier vegetation features.
-Green algae, being more patchy in all our study sites, demonstrates the steepest drop in agreement with increasing pixel size, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
-
-This relationship between resolution and agreement has significant implications for satellite platforms like Sentinel-2 and Landsat.
-Both satellites, commonly used in marine and coastal vegetation studies, offer medium-resolution imagery, with pixel sizes of 10 m and 30 m, respectively.
-While these resolutions are suitable for broad-scale environmental monitoring, they may struggle to capture finer-scale heterogeneity, especially for more fragmented or patchy vegetation types like green algae.
-The results suggest that while coarser resolutions like those of Landsat are sufficient for seagrass and other more homogeneous vegetation types, higher resolutions are essential for accurately mapping species like green algae.
+The results of @fig-pixelsize emphasize the critical role of pixel resolution in accurately retrieving vegetation area from remote sensing data.
+As pixel size increases, a consistent decline in area retrieval is observed across all vegetation types, with more pronounced effects for certain types, such as green algae.
+This highlights the sensitivity of spatial resolution in detecting smaller or more fragmented vegetation features.
+Green algae, being particularly patchy across all study sites, shows the steepest decline in area agreement as pixel size increases, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
+
+This resolution-area relationship has important implications for satellite platforms like Sentinel-2 and Landsat, which are commonly used in marine and coastal vegetation studies.
+Both satellites offer medium-resolution imagery, with pixel sizes of 10m and 30m, respectively.
+While these resolutions are suitable for broad-scale environmental monitoring, they may struggle to capture finer-scale heterogeneity, particularly in fragmented vegetation like green algae.
+The findings suggest that, while coarser resolutions like those of Landsat may be adequate for more homogeneous types, such as seagrass, higher resolutions are essential for accurately mapping patchier species like green algae.
+These findings have direct implications for environmental management and conservation planning.
+Overlooking fine-scale vegetation features, such as those seen in green algae, could result in inadequate protection or restoration efforts, particularly in ecologically sensitive coastal zones, as early stages of green tides could be challenging to monitor at coarse resolutions.
+
+Higher-resolution imagery offers more accurate vegetation mapping but comes with trade-offs.
+As resolution increases, data costs rise, and processing becomes more resource-intensive due to the larger file sizes and computational demands.
+Additionally, high-resolution data requires more storage and can slow down real-time applications.
+For large-scale monitoring or homogeneous vegetation types, medium-resolution platforms like Sentinel-2 are often sufficient.
+However, when mapping fragmented vegetation like green algae, the precision provided by higher-resolution imagery is crucial, despite the additional costs and processing challenges it imposes.
 

### 2024-10-11 docs/_tex/index.tex
add updates
pierre comments

@@
 \makeatother
-
 \ifLuaTeX
@@
 prompting the addition of satellite data within monitoring programs.
-Yet, satellite remote sensing struggles with spatial and spectral
-resolution, making it difficult to discriminate seagrass from other
-macrophytes in highly heterogenous meadows. Drone (unmanned aerial
-vehicles -- UAV) images at a very high spatial resolution offer a
+Yet, satellite remote sensing can be limited by too coarse spatial
+and/or spectral resolution, making it difficult to discriminate seagrass
+from other macrophytes in highly heterogenous meadows. Drone (unmanned
+aerial vehicles -- UAV) images at a very high spatial resolution offer a
 promising solution to address challenges related to spatial
 heterogeneity and intrapixel mixture. This study focuses on using drone
-acquisitions with a ten spectral band sensor mirroring those of
-Sentinel-2, for mapping intertidal macrophytes and effectively
-discriminating between seagrass and green macroalgae. Nine drone flights
-were conducted at two different altitudes (12 m and 120 m) across
-heterogeneous intertidal European habitats in France and Portugal. Low
+acquisitions with a ten spectral band sensor similar to that onboard
+Sentinel-2, for mapping intertidal macrophytes at low tide (i.e.~during
+a period of emersion) and effectively discriminating between seagrass
+and green macroalgae. Nine drone flights were conducted at two different
+altitudes (12 m and 120 m) across heterogeneous intertidal European
+habitats in France and Portugal, providing multispectral reflectance
+observation at very high spatial resolution (respectively at 8 mm and 80
+mm). Taking advantage of their extremly high spatial resolution; the low
 altitude flights were used to train a Deep Learning classifier based on
@@
 macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae)
-and benthic Bacillariophyceae (Diatoms). Classification of drone imagery
-resulted in an overall accuracy of 94\% across all the sites and images,
-covering a total area of 467 000 m². The model exhibited an accuracy of
-96.4\% in identifying seagrass. Importantly, seagrass and green algae
-can be discriminated, although they share the same pigment composition.
-As the algorithm was developed for a multispectral camera with ten
-spectral bands in the visible and near-infrared, it could be adapted to
-the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering
-promising perspectives for satellite remote sensing of intertidal
-biodiversity over lager scales.
+and benthic Bacillariophyceae (Diatoms), and validated using concomitant
+field measurements. Classification of drone imagery resulted in an
+overall accuracy of 94\% across all sites and images, covering a total
+area of 467 000 m². The model exhibited an accuracy of 96.4\% in
+identifying seagrass. In particular , seagrass and green algae can be
+discriminated. The very high spatial resolution of the drone data made
+ot possoble to assess the influence of spatial resolution on the
+classification outputs, showing a limited loss in seagrass detection up
+to about 10m. Altogether, out findings suggest that the Multi-Spectral
+Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between
+its spatial and spectral resolution, thus offering promising
+perspectives for satellite remote sensing of intertidal biodiversity
+over lager scales.
 \end{abstract}
@@
 intertidal seagrass meadows playing a crucial role at the interface
-between the land and oceans \citep{unsworth2022}. Seagrass meadows
-provide a myriad of ecosystem services, including carbon sequestration,
-oxygen production, protection against sea-level rise and coastline
-erosion, and mitigation of eutrophication
-\citep{unsworth2022, sousa2019blue}. They serve as vital habitats for a
-diverse array of marine and terrestrial species, providing living,
-breeding, and feeding grounds
+between land and ocean \citep{unsworth2022}. Seagrass meadows provide a
+myriad of ecosystem services, including carbon sequestration, oxygen
+production, protection against sea-level rise and coastline erosion, and
+mitigation of eutrophication \citep{unsworth2022, sousa2019blue}. They
+serve as vital habitats for a diverse array of marine and terrestrial
+species, providing living, breeding, and feeding grounds
 \citep{gardner2018, Zoffoli2022, jankowska2019}. Due to the
@@
 Traditionally, indicators of seagrass status have been quantified using
-\emph{in situ} measurements. However, the acquisition of these
+\emph{in situ} measurements. However, the acquisition of field
 measurements in intertidal zones is notoriously challenging. Intertidal
@@
 \citep{nijland2019}. Satellite observations have been proven effective
-in complementing \emph{in situ} sampling, allowing for the near
-real-time and consistent retrieval of seagrass EOVs and EBVs over
-extensive meadows. \citep{Zoffoli2021, xu2021, Traganos2018, coffer2023}
+in complementing \emph{in situ} sampling, allowing for near real-time
+and consistent retrieval of seagrass EOVs and EBVs over extensive
+meadows \citep{Zoffoli2021, xu2021, Traganos2018, coffer2023}.
 
@@
 discrimination of seagrass from other co-existing macrophytes. In
-particular Chlorophyceae (green algae) and marine Magnoliopsida
+particular, Chlorophyceae (green algae) and marine Magnoliopsida
 (seagrass) share the same pigment composition
-\citep{ralph2002, Douay2022}. Therefore, to someone not specialized in
-the field, their spectral signatures may appear to be alike
+\citep{ralph2002, Douay2022}, resulting in a similar spectral signature
+in therms of reflectance, especially in the visible range
 \citep{Davies2023, bannari2022}. Recently, using advanced
@@
 demonstrated that it was possible to discriminate Magnoliopsida from
-Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral
+Chlorophyceae using reflectance spectra at Sentinel-2 's spectral
 resolution. However the application of this approach to satellite RS
 remains to be validated. Moreover patches of green algae can develop at
-small spatial scales that are not observable using non-commercial
-satellite imagery \citep{tuya2013}, especially during the initial stage
+small spatial scales that are not observable using Sentinel-2 and/or
+Landsat-8/9 images \citep{tuya2013}, especially during the initial stage
 of a green tide.
@@
 \citep{joyce2023, tallam2023, Roca2022, Roman2021, Brunier2022Topographic, sousa2019blue}.
-However, when applied to coastal habitat mapping, most case studies were
-previously limited to a single flight, restricting the generalizability
-of their application over wider geographical scales
+However, when applied to coastal habitat mapping, previous case studies
+were mostly limited to a limited number of flights over a single study
+site, restricting the generalizability of their application over wider
+geographical scales
 \citep{Roman2021, collin2019improving, rossiter2020uav, Brunier2022Topographic}.
@@
 range, with a particular focus on discriminating Magnoliopsida and
-Chlorophyceae (Seagrass and Green Algae, respectively). Ten drone
+Chlorophyceae (Seagrass and Green Algae, respectively). Nine drone
 flights were performed over soft-bottom intertidal areas along the
@@
 applicability across diverse sites without a loss of prediction
-accuracy. In addition, the results obtained from drone-based
-multispectral remote sensing will be spatially degraded to satellite
-resolutions, and the effect of this resolution on the model's
-predictions will be investigated, providing insights for coastal habitat
-mapping using satellites.
+accuracy. The classification maps obtained at a very high spatial
+resolution with the drone were spatially degraded to satellite
+resolutions, making it possible to asses the effect of spatial
+resolution on classification accuracy; and provide insights for coastal
+habitat mapping using satellite remote sensing.
 
@@
 provided by the manufacturer. Across all sites, flights were made at two
-different altitudes : 12 m or/and 120 m. (Table~\ref{tbl-flights}).
+different altitudes : 12 m or/and 120 m, with a spatial resolution of 8
+mm and 80 mm, respectively (Table~\ref{tbl-flights}).
 
@@
 A structure-from-motion photogrammetry software \citep[Agisoft
-Metashape,][]{agisoft}was used to process images to obtain multispectral
-orthomosaics of each flight. The process for orthomosaicking was
-identical for every flight. First, tying key points were detected inside
-of each image and between overlapping images in order to obtain a sparse
-point cloud. This cloud was cleaned using reprojection accuracy metric
-in order to remove noisy points. A dense point cloud was then produced
-using a structure from motion algorithm. A surface interpolation of this
-dense point cloud was made to obtain a digital surface model (DSM), used
-to reconstruct the multispectral ortho-image \citep{nebel2020review}.
-Low altitude drone flights produced ortho-images with a very high
-spatial resolution (8 mm per pixel), making it efficient to visually
-distinguish between the various types of vegetation. High altitude
-flights on the other hand allowed to cover large areas and produced
-images with a pixel size of 80 mm (Table~\ref{tbl-flights}).
+Metashape,][]{agisoft} was used to process images to obtain
+multispectral orthomosaics of each flight. The process for
+orthomosaicking was identical for every flight. First, tying key points
+were detected inside of each image and between overlapping images in
+order to obtain a sparse point cloud. This cloud was cleaned using
+reprojection accuracy metric in order to remove noisy points. A dense
+point cloud was then produced using a structure from motion algorithm. A
+surface interpolation of this dense point cloud was made to obtain a
+digital surface model (DSM), used to reconstruct the multispectral
+ortho-image \citep{nebel2020review}. Low altitude drone flights produced
+ortho-images with a very high spatial resolution (8 mm per pixel),
+making it efficient to visually distinguish between the various types of
+vegetation. High altitude flights allowed to cover larger areas and
+produced images with a pixel size of 80 mm (Table~\ref{tbl-flights}).
 
@@
 The workflow of this study revolves around two distinct flight heights
-(12 m and 120 m, Figure~\ref{fig-workflow}) where ensuring consistency
+(12 and 120 m, Figure~\ref{fig-workflow}) where ensuring consistency
 between reflectances at both heights is crucial. This comparison was
@@
 
-\subsection{Impact of the spatial resolution in the
-prediction}\label{impact-of-the-spatial-resolution-in-the-prediction}
-
-To evaluate the impact of spatial resolution on the model's output, we
-resampled the reflectance of each flight's orthomosaic using the average
-method from the Terra package in R. DISCOV was then applied to these
-resampled rasters, and the results were compared to the original model
-predictions. For each resolution and vegetation class, we calculated
-predicted area loss, where a score of 0 indicates no area loss during
-resampling, and a score of 100 indicates complete loss of vegetation.
+\subsection{Influence of the spatial resolution on
+classification}\label{influence-of-the-spatial-resolution-on-classification}
+
+To evaluate the influence of spatial resolution on the model's output,
+we resampled the drone orthomosaics from their native resolution (8 cm
+for the high altitude flights) using the ``average'' method from the
+Terra package in R. DISCOV was then applied to these resampled rasters,
+and the results were compared to the original model predictions. For
+each resolution and vegetation class, we calculated the predicted area
+loss, where a score of 0 indicates no area loss during spatial
+resampling, and a score of 100 indicates complete loss of the vegetation
+class.
 
@@
 resolution, vegetation class, and their interaction on the response
-variable (the loss of vegetation area). The model formula was as
-follows:
+variable (the loss of vegetation area within a given class). The model
+formula was as follows:
 
 \begin{equation}\phantomsection\label{eq-gam}{
-%loss \sim  Resolution \times VegetationClass
+VegetationLoss \sim  Resolution \times VegetationClass
 }\end{equation}
@@
 The key aspect of the workflow adopted in the present study is the
-mapping at two different altitudes (12 m and 120 m), resulting in two
-distinct resolutions for the same area (8 mm and 80 mm). The
+mapping at two different altitudes (12 and 120 m), resulting in two
+distinct resolutions for the same area (8 and 80 mm; respectively). The
 high-resolution flight was used to estimate the sub-pixel composition
@@
 In this study, drone flights were conducted at two different altitudes
-(12 m and 120 m) to construct the neural network model. At the sites
-where the flights at both altitudes overlapped, reflectance was
-compared. Overall there was a good agreement between the two altitudes
-(RMSE: 0.027 ; Figure~\ref{fig-CompareRef}).
+(12 and 120 m) to construct the neural network model. At the sites where
+the flights at both altitudes overlapped, reflectance was compared.
+Overall there was a good agreement between the two altitudes (RMSE:
+0.027 ; Figure~\ref{fig-CompareRef}).
 
@@
 (Figure~\ref{fig-CompareRef} A). Since both flights were conducted over
-vegetation areas, the highest reflectance values correspond to the
-infrared part of the spectrum. This difference was not present when
-reflectance values have been standardized (Equation~\ref{eq-std} ;
+vegetated areas, the highest reflectance values correspond to the
+infrared part of the spectrum. This difference was not present when the
+reflectance has been standardized (Equation~\ref{eq-std} ;
 Figure~\ref{fig-CompareRef} B).
@@
 
-\subsection{Effect of the spatial resolution on the
-prediction}\label{effect-of-the-spatial-resolution-on-the-prediction}
+\subsection{Effect of spatial resolution on the
+classification}\label{effect-of-spatial-resolution-on-the-classification}
 
@@
 vegetation type are minimal. Green algae shows the highest loss rate,
-with 1.2\% area lost compared to the raw resolution (8cm). As the
+with 1.2\% area lost compared to the native resolution (80 mm). As the
 resolution coarsens to 10m, area loss becomes significant, with green
@@
 
-A percent cover of at least 80\% was sufficient to have all the pixels
-of high altitude flights correctly classified, with the exception of
-Magnoliopsida that required a higher cover (\textgreater90 \%) to be
-well classified. Concerning the probability of each class, there is a
-linear relationship between the percent cover and the confidence of the
-model to predict the class. To predict Chlorophyceae with a model
-likelihood of 0.85, a cover of 93 \% was needed, 90 \% for
-Magnoliopsida, 92 \% for Rhodophyceae and 97 \% for Bacillariophyceae.
-When the vegetation cover of a given class was 100 \%, coarser
-high-flight pixels were well classified for all the classes except for
-Bare Sediment, which was only well classified 80\% of the time. This
-phenomenon may be attributed to the time gap between the two flights,
-allowing for microphytobenthos migration to the surface during low tide,
-consequently altering the model's classification from bare sediment to
-Bacillariophyceae.
+A percent cover of at least 80\% was sufficient to have all the 80 mm
+pixels correctly classified, with the exception of Magnoliopsida that
+required a higher cover (\textgreater90 \%) to be accurately classified.
+Concerning the probability of each class, there is a linear relationship
+between the percent cover and the confidence of the model to predict the
+class. To predict Chlorophyceae with a model likelihood of 0.85, a cover
+of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for Rhodophyceae and
+97 \% for Bacillariophyceae. When the vegetation cover of a given class
+was 100 \%, coarser high-flight pixels were correctly classified for all
+the classes except for Bare Sediment, which was only correctly
+classified 80\% of the time. This phenomenon may be attributed to the
+time gap between the two flights, allowing for microphytobenthos
+migration to the surface during low tide, consequently altering the
+model's classification from bare sediment to Bacillariophyceae.
 
@@
 The primary objective of this study was to develop a method for the
-accurate classification of macrophytes at low tide on tidal flats,
-specifically focusing on distinguishing between Chlorophyceae (green
-macroalgae) and marine Magnoliopsida (seagrasses) using a multispectral
-resolution. The discrimination of seagrasses from green macroalgae
-presents is spectrally challenging
+accurate classification of emerged macrophytes observed during low tide
+on tidal flats, specifically focusing on distinguishing between
+Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses)
+using a multispectral resolution. The discrimination between seagrasses
+and green macroalgae is challenging due to their optical similarity in
+the visible range
 \citep{oiry2021using, bannari2022, veettil2020opportunities}. These two
@@
 Here, the issue of intra-pixel mixing was resolved thanks to the very
-high spatial resolution of the drone. In this study the risk of spectral
-confusion was avoided with a machine-learning approach exploiting a
-neural networks classifier. Our drone flights and a recent study based
-on \emph{in situ} radiometry, suggested that a sensor with at least
-eight spectral bands ranging from 500 to 850 nm and including a green
-band at 530 nm and a RedEdge band at 730 nm was crucial to accurately
-discriminate green macroalgae from seagrasses \citep{Davies2023}.
+high spatial resolution of the drone (from 8 to 80 mm). In this study
+the risk of spectral confusion was avoided with a machine-learning
+approach exploiting a neural networks classifier. Our drone flights and
+a recent study based on \emph{in situ} radiometry, suggested that a
+sensor with at least eight spectral bands ranging from 500 to 850 nm,
+and including a green band at 530 nm and a RedEdge band at 730 nm, was
+crucial to accurately discriminate green macroalgae from seagrasses
+\citep{Davies2023}.
 
@@
 While comparing the reflectance at two different altitudes (12 m and 120
-m), a nearly one-to-one relationship was observed, with a Root Mean
-Square Error (RMSE) of 0.02 (Figure~\ref{fig-CompareRef}). This result
-indicates that the reflectance measured by remote sensing (RS) sensors
-is not significantly influenced by pixel size. This finding is valuable
-for integrating drone-based data into larger-scale mapping projects
-(e.g., combining satellite and drone mapping in side-by-side analyses).
-The consistency of reflectance across altitudes suggests that drones can
-be effectively used for finer-scale mapping without compromising data
+m with a spatial resolution of 8 and 80 mm, respectively), a nearly
+one-to-one relationship was observed, with a Root Mean Square Error
+(RMSE) of 0.02 (Figure~\ref{fig-CompareRef}). This result indicates that
+the reflectance measured by remote sensing (RS) sensors is not
+significantly influenced by pixel size. This finding is valuable for
+integrating drone-based data into larger-scale mapping projects (e.g.,
+combining satellite and drone mapping in side-by-side analyses). The
+consistency of reflectance across altitudes suggests that drones can be
+effectively used for finer-scale mapping without compromising data
 accuracy when merging with other platforms. However, it was observed
@@
 This resolution-area relationship has important implications for
-satellite platforms like Sentinel-2 and Landsat, which are commonly used
+satellite missions like Sentinel-2 and Landsat, which are commonly used
 in marine and coastal vegetation studies. Both satellites offer
-medium-resolution imagery, with pixel sizes of 10m and 30m,
-respectively. While these resolutions are suitable for broad-scale
-environmental monitoring, they may struggle to capture finer-scale
-heterogeneity, particularly in fragmented vegetation like green algae.
-The findings suggest that, while coarser resolutions like those of
-Landsat may be adequate for more homogeneous types, such as seagrass,
-higher resolutions are essential for accurately mapping patchier species
-like green algae. These findings have direct implications for
-environmental management and conservation planning. Overlooking
-fine-scale vegetation features, such as those seen in green algae, could
-result in inadequate protection or restoration efforts, particularly in
-ecologically sensitive coastal zones, as early stages of green tides
-could be challenging to monitor at coarse resolutions.
-
-Higher-resolution imagery offers more accurate vegetation mapping but
+high-resolution imagery, with pixel sizes of 10m and 30m, respectively.
+While these resolutions are suitable for broad-scale environmental
+monitoring, they may be too coarse to capture finer-scale heterogeneity,
+particularly in fragmented vegetation like green algae. Our findings
+suggest that, while the 30m resolution of Landsat may be adequate for
+homogeneous vegetation types, such as seagrass, a higher resolution is
+essential for accurately mapping patchy vegetation like green algae.
+These findings have direct implications for environmental management and
+conservation planning. Overlooking fine-scale vegetation features, such
+as those seen in green algae, could result in inadequate protection or
+restoration efforts, particularly in ecologically sensitive coastal
+zones, as early stages of green tides could be challenging to monitor at
+coarse resolutions.
+
+Very high-resolution imagery offers more accurate vegetation mapping but
 comes with trade-offs. As resolution increases, data costs rise, and
@@
 more storage and can slow down real-time applications. For large-scale
-monitoring or homogeneous vegetation types, medium-resolution platforms
-like Sentinel-2 are often sufficient. However, when mapping fragmented
-vegetation like green algae, the precision provided by higher-resolution
-imagery is crucial, despite the additional costs and processing
-challenges it imposes.
+monitoring or homogeneous vegetation types, 10 m resolution of S2/MSI or
+even the 30 m of Landsat/OLI are often sufficient. However, when mapping
+fragmented vegetation like green algae, the precision provided by
+higher-resolution imagery is crucial, despite the additional costs and
+processing challenges it imposes.
 
@@
 
-The utilization of very high spatial-resolution drone-based remote
-sensing coupled with machine learning techniques has proven to be an
-effective method for the discrimination of intertidal seagrasses from
-green macroalgae with a multispectral resolution sensor. Standardized
-reflectance was incorporated in the Neural Network model allowing for a
-better discrimination of spectral features related to pigment absorption
-in the visible region of the spectrum. There was a striking difference
-for the variable of importance to discriminate Magnoliopsida from
-Chlorophyceae. The latter was essentially identified with the 451 nm
-spectral band while more spectral bands were needed to identify the
-former, notably 650, 560, 668, and 705 nm. As the spectral bands of the
-Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we
-suggest that multispectral satellite data have the potential to perform
-this discrimination between green these macrophytes. A Sentinel-2
-algorithm could be developed, using the output of this current workflow
-as training and validation data. The findings underscore the importance
-of adopting advanced remote sensing tools in ecological studies and
-environmental monitoring, providing a foundation for future research and
-policy implementation aimed at ecosystem conservation and restoration.
+The utilization of very high spatial resolution (from 8 to 80 mm)
+drone-based remote sensing coupled with machine learning techniques has
+proven to be an effective method for the discrimination of intertidal
+seagrasses from green macroalgae with a multispectral resolution sensor.
+Standardized reflectance was incorporated in the Neural Network model
+allowing for a better discrimination of spectral features related to
+pigment absorption in the visible region of the spectrum. There was a
+striking difference for the variable of importance to discriminate
+Magnoliopsida from Chlorophyceae. The latter was essentially identified
+with the 451 nm spectral band while more spectral bands were needed to
+identify the former, notably 650, 560, 668, and 705 nm. As the spectral
+bands of the Micasense RedEdge Dual MX are very similar to those of
+Sentinel-2/MSI, we suggest that multispectral satellite data have the
+potential to perform this discrimination between green these
+macrophytes. A Sentinel-2 algorithm could be developed, using the output
+of this current workflow as training and validation data. The findings
+underscore the importance of adopting advanced remote sensing tools in
+ecological studies and environmental monitoring, providing a foundation
+for future research and policy implementation aimed at ecosystem
+conservation and restoration.
 

### 2024-10-11 index.qmd
add updates
pierre comments

@@
 In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the addition of satellite data within monitoring programs.
-Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
+Yet, satellite remote sensing can be limited by too coarse spatial and/or spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows.
 Drone (unmanned aerial vehicles – UAV) images at a very high spatial resolution offer a promising solution to address challenges related to spatial heterogeneity and intrapixel mixture.
-This study focuses on using drone acquisitions with a ten spectral band sensor mirroring those of Sentinel-2, for mapping intertidal macrophytes and effectively discriminating between seagrass and green macroalgae.
-Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal.
-Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms).
-Classification of drone imagery resulted in an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m².
+This study focuses on using drone acquisitions with a ten spectral band sensor similar to that onboard Sentinel-2, for mapping intertidal macrophytes at low tide (i.e.
+during a period of emersion) and effectively discriminating between seagrass and green macroalgae.
+Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal, providing multispectral reflectance observation at very high spatial resolution (respectively at 8 mm and 80 mm).
+Taking advantage of their extremly high spatial resolution; the low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms), and validated using concomitant field measurements.
+Classification of drone imagery resulted in an overall accuracy of 94% across all sites and images, covering a total area of 467 000 m².
 The model exhibited an accuracy of 96.4% in identifying seagrass.
-Importantly, seagrass and green algae can be discriminated, although they share the same pigment composition.
-As the algorithm was developed for a multispectral camera with ten spectral bands in the visible and near-infrared, it could be adapted to the Multi-Spectral Instrument (MSI) onboard Sentinel-2 thus offering promising perspectives for satellite remote sensing of intertidal biodiversity over lager scales.
+In particular , seagrass and green algae can be discriminated.
+The very high spatial resolution of the drone data made ot possoble to assess the influence of spatial resolution on the classification outputs, showing a limited loss in seagrass detection up to about 10m.
+Altogether, out findings suggest that the Multi-Spectral Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between its spatial and spectral resolution, thus offering promising perspectives for satellite remote sensing of intertidal biodiversity over lager scales.
 plain-language-summary: |
@@
 library(rnaturalearthdata) 
-library(rnaturalearthhires)
+# library(rnaturalearthhires)
 library(ggforce) 
@@
 
-Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between the land and oceans [@unsworth2022].
+Coastal areas are vital hotspots for marine biodiversity, with intertidal seagrass meadows playing a crucial role at the interface between land and ocean [@unsworth2022].
 Seagrass meadows provide a myriad of ecosystem services, including carbon sequestration, oxygen production, protection against sea-level rise and coastline erosion, and mitigation of eutrophication [@unsworth2022 ; @sousa2019blue].
@@
 Traditionally, indicators of seagrass status have been quantified using *in situ* measurements.
-However, the acquisition of these measurements in intertidal zones is notoriously challenging.
+However, the acquisition of field measurements in intertidal zones is notoriously challenging.
 Intertidal seagrass meadows are only exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
-Satellite observations have been proven effective in complementing *in situ* sampling, allowing for the near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows.
-[@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023]
+Satellite observations have been proven effective in complementing *in situ* sampling, allowing for near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023].
 
@@
 The limited number of spectral bands challenges accurate discrimination of seagrass from other co-existing macrophytes.
-In particular Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022].
-Therefore, to someone not specialized in the field, their spectral signatures may appear to be alike [@Davies2023 ; @bannari2022].
-Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more than 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using radiometric data acquired at Sentinel-2 's spectral resolution.
+In particular, Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022], resulting in a similar spectral signature in therms of reflectance, especially in the visible range [@Davies2023 ; @bannari2022].
+Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more than 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using reflectance spectra at Sentinel-2 's spectral resolution.
 However the application of this approach to satellite RS remains to be validated.
-Moreover patches of green algae can develop at small spatial scales that are not observable using non-commercial satellite imagery [@tuya2013], especially during the initial stage of a green tide.
+Moreover patches of green algae can develop at small spatial scales that are not observable using Sentinel-2 and/or Landsat-8/9 images [@tuya2013], especially during the initial stage of a green tide.
 
@@
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
-However, when applied to coastal habitat mapping, most case studies were previously limited to a single flight, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+However, when applied to coastal habitat mapping, previous case studies were mostly limited to a limited number of flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
 The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae, respectively).
-Ten drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
+Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
-In addition, the results obtained from drone-based multispectral remote sensing will be spatially degraded to satellite resolutions, and the effect of this resolution on the model's predictions will be investigated, providing insights for coastal habitat mapping using satellites.
+The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to asses the effect of spatial resolution on classification accuracy; and provide insights for coastal habitat mapping using satellite remote sensing.
 
@@
 Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer.
-Across all sites, flights were made at two different altitudes : 12 m or/and 120 m.
-(@tbl-flights).
+Across all sites, flights were made at two different altitudes : 12 m or/and 120 m, with a spatial resolution of 8 mm and 80 mm, respectively (@tbl-flights).
 
@@
 
-A structure-from-motion photogrammetry software [Agisoft Metashape, @agisoft]was used to process images to obtain multispectral orthomosaics of each flight.
+A structure-from-motion photogrammetry software [Agisoft Metashape, @agisoft] was used to process images to obtain multispectral orthomosaics of each flight.
 The process for orthomosaicking was identical for every flight.
@@
 Low altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
-High altitude flights on the other hand allowed to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).
+High altitude flights allowed to cover larger areas and produced images with a pixel size of 80 mm (@tbl-flights).
 
@@
 
-The workflow of this study revolves around two distinct flight heights (12 m and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
+The workflow of this study revolves around two distinct flight heights (12 and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
 This comparison was conducted at sites where low and high altitude flights overlapped.
@@
 
-## Impact of the spatial resolution in the prediction
-
-To evaluate the impact of spatial resolution on the model’s output, we resampled the reflectance of each flight's orthomosaic using the average method from the Terra package in R.
+## Influence of the spatial resolution on classification
+
+To evaluate the influence of spatial resolution on the model’s output, we resampled the drone orthomosaics from their native resolution (8 cm for the high altitude flights) using the "average" method from the Terra package in R.
 DISCOV was then applied to these resampled rasters, and the results were compared to the original model predictions.
-For each resolution and vegetation class, we calculated predicted area loss, where a score of 0 indicates no area loss during resampling, and a score of 100 indicates complete loss of vegetation.
-
-We used a Generalized Linear Model (GLM) with a Gaussian family and identity link function to examine the relationship between pixel resolution, vegetation class, and their interaction on the response variable (the loss of vegetation area).
+For each resolution and vegetation class, we calculated the predicted area loss, where a score of 0 indicates no area loss during spatial resampling, and a score of 100 indicates complete loss of the vegetation class.
+
+We used a Generalized Linear Model (GLM) with a Gaussian family and identity link function to examine the relationship between pixel resolution, vegetation class, and their interaction on the response variable (the loss of vegetation area within a given class).
 The model formula was as follows:
@@
 $$
-%loss \sim  Resolution \times VegetationClass
+VegetationLoss \sim  Resolution \times VegetationClass
 $$ {#eq-gam}
@@
 
-The key aspect of the workflow adopted in the present study is the mapping at two different altitudes (12 m and 120 m), resulting in two distinct resolutions for the same area (8 mm and 80 mm).
+The key aspect of the workflow adopted in the present study is the mapping at two different altitudes (12 and 120 m), resulting in two distinct resolutions for the same area (8 and 80 mm; respectively).
 The high-resolution flight was used to estimate the sub-pixel composition for each pixel of the lower-resolution flight.
@@
 
-In this study, drone flights were conducted at two different altitudes (12 m and 120 m) to construct the neural network model.
+In this study, drone flights were conducted at two different altitudes (12 and 120 m) to construct the neural network model.
 At the sites where the flights at both altitudes overlapped, reflectance was compared.
@@
 There was a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
-Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
-This difference was not present when reflectance values have been standardized (@eq-std ; @fig-CompareRef B).
+Since both flights were conducted over vegetated areas, the highest reflectance values correspond to the infrared part of the spectrum.
+This difference was not present when the reflectance has been standardized (@eq-std ; @fig-CompareRef B).
 
@@
 
-## Effect of the spatial resolution on the prediction
+## Effect of spatial resolution on the classification
 
@@
 At a fine resolution of 1m, changes in the retrieved area for each vegetation type are minimal.
-Green algae shows the highest loss rate, with 1.2% area lost compared to the raw resolution (8cm).
+Green algae shows the highest loss rate, with 1.2% area lost compared to the native resolution (80 mm).
 As the resolution coarsens to 10m, area loss becomes significant, with green algae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
@@
 
- A percent cover of at least 80% was sufficient to have all the pixels of high altitude flights correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be well classified.
+A percent cover of at least 80% was sufficient to have all the 80 mm pixels correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be accurately classified.
 Concerning the probability of each class, there is a linear relationship between the percent cover and the confidence of the model to predict the class.
 To predict Chlorophyceae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
-When the vegetation cover of a given class was 100 %, coarser high-flight pixels were well classified for all the classes except for Bare Sediment, which was only well classified 80% of the time.
+When the vegetation cover of a given class was 100 %, coarser high-flight pixels were correctly classified for all the classes except for Bare Sediment, which was only correctly classified 80% of the time.
 This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
@@
 
-The primary objective of this study was to develop a method for the accurate classification of macrophytes at low tide on tidal flats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using a multispectral resolution.
-The discrimination of seagrasses from green macroalgae presents is spectrally challenging [@oiry2021using ; @bannari2022 ; @veettil2020opportunities].
+The primary objective of this study was to develop a method for the accurate classification of emerged macrophytes observed during low tide on tidal flats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using a multispectral resolution.
+The discrimination between seagrasses and green macroalgae is challenging due to their optical similarity in the visible range [@oiry2021using ; @bannari2022 ; @veettil2020opportunities].
 These two macrophytes share a similar pigment composition: chlorophyll-a (common to all vegetation types), chlorophyll-b (an additional photosynthetic pigment), and accessory carotenoids such as zeaxanthin, lutein and neoxanthin (@fig-Pigm).
@@
 Seagrass and green macroalgae frequently co-occur in intertidal areas, and can intermingle within a remote sensing pixel if the spatial resolution is too low.
-Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone.
+Here, the issue of intra-pixel mixing was resolved thanks to the very high spatial resolution of the drone (from 8 to 80 mm).
 In this study the risk of spectral confusion was avoided with a machine-learning approach exploiting a neural networks classifier.
-Our drone flights and a recent study based on *in situ* radiometry, suggested that a sensor with at least eight spectral bands ranging from 500 to 850 nm and including a green band at 530 nm and a RedEdge band at 730 nm was crucial to accurately discriminate green macroalgae from seagrasses [@Davies2023].
+Our drone flights and a recent study based on *in situ* radiometry, suggested that a sensor with at least eight spectral bands ranging from 500 to 850 nm, and including a green band at 530 nm and a RedEdge band at 730 nm, was crucial to accurately discriminate green macroalgae from seagrasses [@Davies2023].
 
@@
 By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems.
-While comparing the reflectance at two different altitudes (12 m and 120 m), a nearly one-to-one relationship was observed, with a Root Mean Square Error (RMSE) of 0.02 (@fig-CompareRef).
+While comparing the reflectance at two different altitudes (12 m and 120 m with a spatial resolution of 8 and 80 mm, respectively), a nearly one-to-one relationship was observed, with a Root Mean Square Error (RMSE) of 0.02 (@fig-CompareRef).
 This result indicates that the reflectance measured by remote sensing (RS) sensors is not significantly influenced by pixel size.
@@
 
-This resolution-area relationship has important implications for satellite platforms like Sentinel-2 and Landsat, which are commonly used in marine and coastal vegetation studies.
-Both satellites offer medium-resolution imagery, with pixel sizes of 10m and 30m, respectively.
-While these resolutions are suitable for broad-scale environmental monitoring, they may struggle to capture finer-scale heterogeneity, particularly in fragmented vegetation like green algae.
-The findings suggest that, while coarser resolutions like those of Landsat may be adequate for more homogeneous types, such as seagrass, higher resolutions are essential for accurately mapping patchier species like green algae.
+This resolution-area relationship has important implications for satellite missions like Sentinel-2 and Landsat, which are commonly used in marine and coastal vegetation studies.
+Both satellites offer high-resolution imagery, with pixel sizes of 10m and 30m, respectively.
+While these resolutions are suitable for broad-scale environmental monitoring, they may be too coarse to capture finer-scale heterogeneity, particularly in fragmented vegetation like green algae.
+Our findings suggest that, while the 30m resolution of Landsat may be adequate for homogeneous vegetation types, such as seagrass, a higher resolution is essential for accurately mapping patchy vegetation like green algae.
 These findings have direct implications for environmental management and conservation planning.
@@
 
-Higher-resolution imagery offers more accurate vegetation mapping but comes with trade-offs.
+Very high-resolution imagery offers more accurate vegetation mapping but comes with trade-offs.
 As resolution increases, data costs rise, and processing becomes more resource-intensive due to the larger file sizes and computational demands.
 Additionally, high-resolution data requires more storage and can slow down real-time applications.
-For large-scale monitoring or homogeneous vegetation types, medium-resolution platforms like Sentinel-2 are often sufficient.
+For large-scale monitoring or homogeneous vegetation types, 10 m resolution of S2/MSI or even the 30 m of Landsat/OLI are often sufficient.
 However, when mapping fragmented vegetation like green algae, the precision provided by higher-resolution imagery is crucial, despite the additional costs and processing challenges it imposes.
@@
 
-Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sea level rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global] and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
+Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sea level rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414 ; @holon2018predictive ; @marquet2024global] and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
 Our findings, particularly the improved discrimination of intertidal seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
@@
 
-The utilization of very high spatial-resolution drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of intertidal seagrasses from green macroalgae with a multispectral resolution sensor.
+The utilization of very high spatial resolution (from 8 to 80 mm) drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of intertidal seagrasses from green macroalgae with a multispectral resolution sensor.
 Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible region of the spectrum.
@@
 The latter was essentially identified with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
-As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2, we suggest that multispectral satellite data have the potential to perform this discrimination between green these macrophytes.
+As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2/MSI, we suggest that multispectral satellite data have the potential to perform this discrimination between green these macrophytes.
 A Sentinel-2 algorithm could be developed, using the output of this current workflow as training and validation data.

### 2024-10-14 docs/_tex/index.tex
adding bede's comments

@@
 habitats in France and Portugal, providing multispectral reflectance
-observation at very high spatial resolution (respectively at 8 mm and 80
-mm). Taking advantage of their extremly high spatial resolution; the low
-altitude flights were used to train a Deep Learning classifier based on
-Neural Networks to discrimintate among five taxonomic classes of
-intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green
-macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae)
-and benthic Bacillariophyceae (Diatoms), and validated using concomitant
-field measurements. Classification of drone imagery resulted in an
-overall accuracy of 94\% across all sites and images, covering a total
-area of 467 000 m². The model exhibited an accuracy of 96.4\% in
-identifying seagrass. In particular , seagrass and green algae can be
-discriminated. The very high spatial resolution of the drone data made
-ot possoble to assess the influence of spatial resolution on the
-classification outputs, showing a limited loss in seagrass detection up
-to about 10m. Altogether, out findings suggest that the Multi-Spectral
-Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between
-its spatial and spectral resolution, thus offering promising
-perspectives for satellite remote sensing of intertidal biodiversity
-over lager scales.
+observation at very high spatial resolution (8 mm and 80 mm
+respectively). Taking advantage of their extremly high spatial
+resolution; the low altitude flights were used to train a Neural Network
+classifier to discrimintate five taxonomic classes of intertidal
+vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae),
+Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic
+Bacillariophyceae (Diatoms), and validated using concomitant field
+measurements. Classification of drone imagery resulted in an overall
+accuracy of 94\% across all sites and images, covering a total area of
+467 000 m². The model exhibited an accuracy of 96.4\% in identifying
+seagrass. In particular , seagrass and green algae can be discriminated.
+The very high spatial resolution of the drone data made it possible to
+assess the influence of spatial resolution on the classification
+outputs, showing a limited loss in seagrass detection up to about 10m.
+Altogether, out findings suggest that the Multi-Spectral Instrument
+(MSI) onboard Sentinel-2 offers a relevant trade-off between its spatial
+and spectral resolution, thus offering promising perspectives for
+satellite remote sensing of intertidal biodiversity over lager scales.
 \end{abstract}
@@
 and consistent retrieval of seagrass EOVs and EBVs over extensive
-meadows \citep{Zoffoli2021, xu2021, Traganos2018, coffer2023}.
+meadows
+\citep{Zoffoli2021, xu2021, Traganos2018, coffer2023, davies2024intertidal, davies2024sentinel}.
 
@@
 areas is limited by several constraints. Satellite missions with a high
-temporal resolution (e.g.~daily MODIS observation) are limited by a too
+temporal resolution (e.g.~daily MODIS observation) are limited by too
 coarse spatial resolution (\textgreater100 m) to accurately map patchy
@@
 \citep{ralph2002, Douay2022}, resulting in a similar spectral signature
-in therms of reflectance, especially in the visible range
+in terms of reflectance, especially in the visible range
 \citep{Davies2023, bannari2022}. Recently, using advanced
@@
 However, when applied to coastal habitat mapping, previous case studies
-were mostly limited to a limited number of flights over a single study
-site, restricting the generalizability of their application over wider
+were mostly limited to a low number of flights over a single study site,
+restricting the generalizability of their application over wider
 geographical scales
@@
 resolution with the drone were spatially degraded to satellite
-resolutions, making it possible to asses the effect of spatial
-resolution on classification accuracy; and provide insights for coastal
+resolutions, making it possible to assess the effect of spatial
+resolution on classification accuracy, and provide insights for coastal
 habitat mapping using satellite remote sensing.
@@
 for their extensive intertidal seagrass beds. Two sites were located in
-the Gulf of Morbihan (Figure~\ref{fig-map} A), France (47.5791°N,
+the Gulf of Morbihan, France (Figure~\ref{fig-map} A : 47.5791°N,
 2.8018°W). This gulf covers an area of 115 km² and is only connected to
@@
 international importance. Two other sites were located in Bourgneuf Bay,
-France (46.9849°N, 2.1488°W). This is a 340 km² semi-enclosed macrotidal
-bay, protected from waves by Noirmoutier Island. Bourgneuf bay hosts a
-large intertidal seagrass meadow of about 6 km²
-\citep{ZOFFOLI2020112020}. Within this meadow, the sites observed by
-drones (L'Epine and Barbatre, Figure~\ref{fig-map} B) contained
-monospecific beds of \emph{Nanozostera noltei} (dwarf eelgrass, syn.
-\emph{Zostera noltei}) with very little mixing with other macrophytes.
-Bourgneuf Bay is also part of the Natura 2000 network and serves as a
-RAMSAR site due to its critical habitat for migratory bird species and
-its extensive seagrass meadows. Three sites were surveyed in the Ria de
-Aveiro Coastal Lagoon in Portugal (40.6887°N, 8.6810°W). The extent of
-this lagoon is \textasciitilde83 km² (at low tide) with many narrow
-channels, large salt marshes and many mudflats that uncover at low tide
-\citep{sousa2017blue}. It is connected to the open sea through a single
-channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) is a mudflat located in the Mira channel
-(one of the four main channels of the lagoon) whereas the two other
-sites (Mataducos and Marinha Lanzarote) were situated in the middle of
-the lagoon and only accessible by boat (Figure~\ref{fig-map} C). These
-Portuguese sites are characterized by a more diverse intertidal
-vegetation, where patches of seagrass intermingle with red, brown, and
-green macroalgae. The Aveiro Lagoon, like the other study areas, is a
-Natura 2000 site and a RAMSAR wetland, recognized for its rich mosaic of
-habitats and importance for biodiversity, including migratory bird
-species and intertidal vegetation.
+France (Figure~\ref{fig-map} B : 46.9849°N, 2.1488°W) which is a 340 km²
+semi-enclosed macrotidal bay, protected from waves by Noirmoutier
+Island. Bourgneuf bay hosts a large intertidal seagrass meadow of about
+6 km² \citep{ZOFFOLI2020112020}. Within this meadow, the sites observed
+by drones (L'Epine and Barbatre) contained monospecific beds of
+\emph{Nanozostera noltei} (dwarf eelgrass, syn. \emph{Zostera noltei})
+with very little mixing with other macrophytes. Bourgneuf Bay is also
+part of the Natura 2000 network and serves as a RAMSAR site due to its
+critical habitat for migratory bird species and its extensive seagrass
+meadows \citep{Zoffoli2022}. Three sites were surveyed in the Ria de
+Aveiro Coastal Lagoon in Portugal (Figure~\ref{fig-map} C : 40.6887°N,
+8.6810°W). The extent of this lagoon is \textasciitilde83 km² (at low
+tide) with many narrow channels, large salt marshes and many mudflats
+that uncover at low tide \citep{sousa2017blue}. It is connected to the
+open sea through a single channel, with a tidal lag between the North
+and the South of the lagoon. The southernmost site (Gafanha) is a
+mudflat located in the Mira channel (one of the four main channels of
+the lagoon) whereas the two other sites (Mataducos and Marinha
+Lanzarote) were situated in the middle of the lagoon and only accessible
+by boat. These Portuguese sites are characterized by a more diverse
+intertidal vegetation, where patches of seagrass intermingle with red,
+brown, and green macroalgae. The Aveiro Lagoon, like the other study
+areas, is a Natura 2000 site and a RAMSAR wetland, recognized for its
+rich mosaic of habitats and importance for biodiversity, including
+migratory bird species and intertidal vegetation.
 
@@
 patches extending over several meters were selected as ground control
-points. Pictures of each quadrat were uploaded online to the Global
-Biodiversity Information Facility (GBIF) platform \citep{BedeGbif}, a
-public open portal to store and share biodiversity data. Each photograph
-was also processed to estimate the percent cover of each type of
-vegetation using an image processing software
-\citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
+points. Pictures of each quadrat were uploaded online to the open-portal
+Global Biodiversity Information Facility (GBIF) platform
+\citep{BedeGbif}. Each photograph was also processed to estimate the
+percent cover of each type of vegetation using an image processing
+software \citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
 signatures of each vegetation class were recorded using an ASD FieldSpec
@@
 served dual purposes: they validate the radiometric calibration of drone
-data and contribute to error reduction in photo interpretations.
+data and contribute to misclassification reduction in photo
+interpretations.
 
@@
 multispectral orthomosaics of each flight. The process for
-orthomosaicking was identical for every flight. First, tying key points
+orthomosaicking was identical for every flight. First, key tying points
 were detected inside of each image and between overlapping images in
-order to obtain a sparse point cloud. This cloud was cleaned using
+order to obtain a sparse point cloud. This cloud was cleaned using a
 reprojection accuracy metric in order to remove noisy points. A dense
@@
 Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
-Rhodophyceae. Only low-altitude flights (Table~\ref{tbl-flights}) were
-used for training because their 8 mm spatial resolution allowed to avoid
-spectral sub-pixel mixing and to accurately identify vegetation classes.
-More than 418,000 pixels at 8 mm resolution from the 3 training flights
-were used to train the model (Table~\ref{tbl-validationPX}). Twenty one
-variables were used by the model as predictors: the ten raw spectral
-bands of the Micasense RedEdge Dual MX multispectral camera (ranging
-from 444 nm to 840 nm), the same ten spectral bands standardized using a
-min/max transformation (Equation~\ref{eq-std} ; \citep{Cao2017}) and the
-Normalized difference vegetation index (NDVI, Equation~\ref{eq-ndvi}).
-Standardisation of spectral bands is commonly used to eliminate the
-scaling differences between spectra and to limit the effect of biomass
-on the spectra shape \citep{Douay2022, Davies2023}.
+Rhodophyceae. Only data from the low-altitude flights
+(Table~\ref{tbl-flights}) were used for training because their 8 mm
+spatial resolution allowed to avoid spectral sub-pixel mixing and to
+accurately identify vegetation classes. More than 418,000 pixels at 8 mm
+resolution from the 3 training flights were used to train the model
+(Table~\ref{tbl-validationPX}). Twenty one variables were used by the
+model as predictors: the ten raw spectral bands of the Micasense RedEdge
+Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same
+ten spectral bands standardized using a min/max transformation
+(Equation~\ref{eq-std} ; \citep{Cao2017}) and the Normalized difference
+vegetation index (NDVI, Equation~\ref{eq-ndvi}). Standardisation of
+spectral bands is commonly used to eliminate the scaling differences
+between spectra and to limit the effect of biomass on the spectra shape
+\citep{Douay2022, Davies2023}.
 
@@
 A neural network classification model was built using the fastai
-workflow \citep{howard2018fastai}. This model is composed by 2 hidden
+workflow \citep{howard2018fastai}. This model was composed of 2 hidden
 layers and have a total of 26 054 trainable parameters. Parameters have
-been fine tuned using 12 epoch to minimize the error rate.
+been fine tuned using 12 epoch to minimize the error rate. This model
+has been called DISCOV, standing for Drone Intertidal Substrat
+Classification Of Vegetation.
 
@@
 grid as the high flights using a median resampling method. Reflectance
-values were then extracted, and a scatterplot was generated.
-Subsequently, the slope of the linear model and the coefficient of
-determination (R²) were computed.
-
-The model was applied to all flights at both 12 and 120 m of altitude.
-\emph{In situ} information on georeferenced class type and percent
-cover, acquired at over homogeneous vegetation patches at the same time
-as drone flights was used to assess the model accuracy. These images
-were used to construct a validation dataset indicating the presence or
-absence of each class. Additionally to the quadrat-based validation
-dataset, polygons of each class were photo interpreted in order to
-increase the number of pixels of the validation dataset.A total of
-536,000 pixels were used to validate the Neural Network classifier. The
-sites with the lowest and highest number of validation data were Gafanha
-Low (17316 pixels) and Marinha Lanzarote (159713 pixels), respectively.
-A confusion matrix, along with precision metrics such as global
-accuracy, sensitivity, specificity, and Kappa coefficient, was generated
-for each sites. All validation matrices were then aggregated to create
-an overall matrix .
+values were then extracted, and a scatterplot was generated and the Root
+Mean Square Error (RMSE) was computed to compare the difference bewteen
+the raw and standardised reflectance.
+
+The classification model was applied to all flights at both 12 and 120 m
+of altitude. \emph{In situ} information on georeferenced class type and
+percent cover, acquired over homogeneous vegetation patches at the same
+time as drone flights was used to assess the model accuracy. These
+images were used to construct a validation dataset indicating the
+presence or absence of each class. Additionally to the quadrat-based
+validation dataset, polygons of each class were photo interpreted in
+order to increase the number of pixels of the validation dataset. A
+total of 536,000 pixels were used to validate the Neural Network
+classifier. The sites with the lowest and highest number of validation
+data were Gafanha Low (17316 pixels) and Marinha Lanzarote (159713
+pixels), respectively. A confusion matrix, along with precision metrics
+such as global accuracy, sensitivity, specificity, F1 score, and Kappa
+coefficient, were generated for each site. All validation matrices were
+then aggregated to create an overall matrix .
 
@@
 Variable Importance Plots (VIP) serve as a method to identify which
-predictors are important for predicting a specific class. Out of the
-twenty one predictors utilized in this study, Variable Importance was
-computed only for the raw and standardized values of the 10 spectral
-bands captured by the MicaSense camera. This is achieved by repeatedly
-predicting the same dataset while randomly shuffling one predictor at a
-time. The benchmark score obtained after each iteration is then compared
-to the benchmark score obtained without shuffling any variables. The
-greater the difference between these two benchmark values, the more
-important the variable is for the model \citep{WEI2015399}.
+predictors are important for predicting a specific class. Out of the 21
+predictors utilized in this study, Variable Importance was computed only
+for the raw and standardized values of the 10 spectral bands captured by
+the MicaSense camera. This is achieved by repeatedly predicting the same
+dataset while randomly shuffling one predictor at a time. The benchmark
+score obtained after each iteration is then compared to the benchmark
+score obtained without shuffling any variables. The greater the
+difference between these two benchmark values, the more important the
+variable is for the model \citep{WEI2015399}.
 
@@
 
-We used a Generalized Linear Model (GLM) with a Gaussian family and
-identity link function to examine the relationship between pixel
-resolution, vegetation class, and their interaction on the response
-variable (the loss of vegetation area within a given class). The model
-formula was as follows:
-
-\begin{equation}\phantomsection\label{eq-gam}{
-VegetationLoss \sim  Resolution \times VegetationClass
-}\end{equation}
+We used a Generalized Linear Model (GLM) with a Beta distribution to
+examine the relationship between pixel resolution, vegetation class, and
+their interaction on the loss of vegetation. The loss of vegetation was
+modelled as function of the interaction between pixel resolution and
+vegetation class (Bacillariophyceae, Phaeophyceae, Magnoliopsida,
+Chlorophyceae and Rhodophyceae). Sample vs fitted residuals and
+quartile-quartile graphics were assessed visually, to ensure assumption
+of the models used were met
 
@@
 the flights at both altitudes overlapped, reflectance was compared.
-Overall there was a good agreement between the two altitudes (RMSE:
+Overall there was a good agreement between the two altitudes (RMSE :
 0.027 ; Figure~\ref{fig-CompareRef}).
@@
 Each drone flight was used to produce a prediction map, as well as a
-probability map that indicate the model derived likelihood of the
+probability map that indicates the model derived probability of the
 selected class for every pixel. The low-altitude flight conducted in
@@
 (Figure~\ref{fig-GafLow}). Among the five vegetation classes on which
-the model was trained, four were present on this site, with green an red
-macroalgae mixed with a seagrass meadow. There was also diatoms forming
-biofilms on bare sediment surface. Although the seagrass was solely
-composed of a single specie, \emph{Nanozostera noltei}, various colors
-of this specie could be observed from dark green (corresponding to
-healthy leaves) to brown (when leaves are senescent or have an altered
-pigment composition). Regardless of the variation of color, the class
-Magnoliopsida was accurately predicted by the model (F1 score of 0.96 at
-that site).
+the model was trained, four were present on this site, with green and
+red macroalgae mixed with a seagrass meadow. There was also diatoms
+forming biofilms on bare sediment surface. Although the seagrass was
+solely composed of a single specie, \emph{Nanozostera noltei}, various
+colors of this specie could be observed from dark green (corresponding
+to healthy leaves) to brown (when leaves are senescent or have an
+altered pigment composition). Regardless of the variation of color, the
+class Magnoliopsida was accurately predicted by the model (F1 score of
+0.96 at that site).
 
@@
 Ria de Aveiro coastal lagoon covered the largest area with approximately
-1.5 km² (Figure~\ref{fig-Boat}). This site was dominated by seagrass and
-red macroalgae. The classification provided consistent results, with a
-patchy seagrass meadow mixed with red macroalgae on the eastern part of
-the site. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of the
-meadow were mixed with green macroalgae (\emph{Ulva sp.}), which the
-model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass
-and 0.98 for red algae).
+1.5 km² (Figure~\ref{fig-Boat}). Teh vegetation present at the site was
+dominated by seagrass and red macroalgae. The classification provided
+consistent results, with a patchy seagrass meadow mixed with red
+macroalgae on the eastern part of the site. As shown in the zoom
+(Figure~\ref{fig-Boat}), the edges of the meadow were mixed with green
+macroalgae (\emph{Ulva sp.}), which the model agreed with (F1 score of
+0.89 for green algae, 0.97 for seagrass and 0.98 for red algae).
 
@@
 80 mm per pixel. Background colors indicate intertidal area (Light
-Green), land area (Light Grey) and water (Light Blue). Each cover an
-area equivalent to a 10 m Sentinel-2 pixel size.}
+Green), land area (Light Grey) and water (Light Blue). The zoom inserts
+cover an area equivalent to the size of a 10-meter Sentinel-2 pixel.}
 
@@
 brown macroalgae (\emph{Fucus spp.}, \emph{Ascophyllum nodosum}) were
-attached to sparse rocks and stranded green algae (\emph{Ulva spp.})
-could be observed and this was correctly reproduced by the prediction
+attached to sparse rocks, and stranded green algae (\emph{Ulva spp.})
+could be observed, which was correctly reproduced by the prediction
 (Figure~\ref{fig-Dike} B). This site was characterized by a high mixture
@@
 The spectral bands at 444, 717 and 842 nm of the Micasense camera did
-not provide as important information to discriminate any of the
-vegetation classes. The band at 531 nm was the only important predictor
-for the classifier to accurately predict Chlorophyceae. In fact, at this
+not provide important information to discriminate any of the vegetation
+classes. The band at 531 nm was the most important predictor by far for
+the classifier to accurately predict Chlorophyceae. In fact, at this
 wavelength, the Chlorophyceae spectra showed the highest reflectance
-among all vegetation classes. The bands at 531 and 740 nm were the most
-important predictors for Phaeophyceae, corresponding to the lowest
-reflectance among all classes. Bands at 475 and 560 nm were the most
-important predictors for Bacillariophyceae and Rhodophyceae,
-respectively. Four predictors, ranging from the green (560 nm) to the
-RedEdge (705 nm) bands were important to accurately predict
+among all vegetation classes (Figure~\ref{fig-vegetation} F). The bands
+at 531 and 740 nm were the most important predictors for Phaeophyceae,
+corresponding to the lowest reflectance among all classes. Bands at 475
+and 560 nm were the most important predictors for Bacillariophyceae and
+Rhodophyceae, respectively. Four predictors, ranging from the green (560
+nm) to the RedEdge (705 nm) bands were important to accurately predict
 Magnoliopsida.
@@
 
-Figure~\ref{fig-pixelsize} illustrates the relationship between
-predicted area loss for various vegetation types and map resolution. At
-a fine resolution of 1m, changes in the retrieved area for each
-vegetation type are minimal. Green algae shows the highest loss rate,
-with 1.2\% area lost compared to the native resolution (80 mm). As the
-resolution coarsens to 10m, area loss becomes significant, with green
-algae again experiencing the greatest reduction (12\% compared to 8cm)
-and seagrass showing the smallest loss (1.3\%). At a resolution of 30m,
-all green algae have been lost (100\% compared to 8cm), while seagrass
-experiences a relatively small reduction of 11\%. Brown algae and red
-algae show moderate declines, with losses at 30m resolution reaching
-approximately 37\% and 59\%, respectively.
+Clear differences were seen in vegetation loss across different
+resolutions and vegetation classes (@fig-pixel). At a fine resolution of
+1m, changes in the retrieved area for each vegetation type are minimal.
+Green algae shows the highest loss, with 1.2\% area lost compared to the
+native resolution (80 mm). As the resolution coarsens to 10m, vegetation
+loss becomes more pronounced, with green algae again experiencing the
+greatest reduction (12\% compared to 8cm) and seagrass showing the
+smallest loss (1.3\%). At a resolution of 30m, all green algae have been
+lost (100\% compared to 8cm), while seagrass experiences a relatively
+small reduction of 11\%. Brown algae and red algae show moderate
+declines, with losses at 30m resolution reaching approximately 37\% and
+59\%, respectively.
 
@@
 vegetation types (green algae, seagrass, brown algae, red algae) as a
-function of spatial resolution. Lines represent generalized linear model
-(GLM) predictions, and shaded areas indicate standard errors. As
-resolution decreases, predicted area loss increases for all vegetation
-types, with green algae showing the highest loss and seagrass the
-smallest at coarser resolutions.}
-
-\end{figure}%
-
-The Generalized Linear Model (GLM) analysis showed a significant effect
-of pixel resolution on the mapped vegetation area, indicating a positive
-relationship between resolution and area loss
-(\(\beta = 0.067, p < 0.001\)). This suggests that as pixel resolution
-increases, the mapped area of each vegetation type decreases.
+function of spatial resolution. Lines represent GLM predictions, and
+shaded areas indicate standard errors. As resolution decreases,
+predicted area loss increases for all vegetation types, with green algae
+showing the highest loss and seagrass the smallest at coarser
+resolutions.}
+
+\end{figure}%
 
@@
 Network Classifier, along with their absorption wavelength measured with
-spectroradiometer. Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco:
+spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco:
 fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
-neoxanthin, PE: phycoerythrin, PC: phycocyanin.}
+neoxanthin, PE: phycoerythrin, PC: phycocyanin
+\citetext{\citealp{ralph2002}; \citealp[@christensen1977seaweeds]{Douay2022}; \citealp{cartaxana2016regulation}; \citealp{meleder2013vivo}}.}
 
@@
 highest reflectance among all other classes, highlighting the difference
-in carotenoids to chlorophyll-a ratios between seagrasses and green
+in carotenoid to chlorophyll-a ratios between seagrasses and green
 macroalgae \citep{repolho2017seagrass}. Concerning Phaeophyceae, the
 thick cell walls of these macroalgae \citep{charrier2021growth} make it
-more reflective in the infrared part of the spectra \citep{Slaton2001}
-whereas the presence of fucoxanthin and zeaxanthin result in a low
-reflectance in the visible region (Figure~\ref{fig-Pigm} ;
-Figure~\ref{fig-VIP}). These two key features have been identified by
+more reflective in the infrared part of the spectra \citep{Slaton2001},
+while the presence of fucoxanthin and zeaxanthin result in a low
+reflectance in the visible region (Figure~\ref{fig-VIP} ;
+Figure~\ref{fig-Pigm}). These two key features have been identified by
 the Neural Network as the two principal predictors to accurately
@@
 important for identifying this class, likely due to phycoerythrin
-absorption at this wavelength. Regarding Bacillariophyceae, the variable
-importance analysis (Figure~\ref{fig-VIP}) indicated that 475 nm was the
-most important predictor for this class. Indeed, the reflectance at 475
-nm was higher for Bacillariophyceae than for any other vegetation class
-(Figure~\ref{fig-vegetation}), very likely due to the low biomass (and
-associated concentration of blue-absorbing pigments) of these
-unicellular organisms compared to seagrass and macroalgae.
+absorption at this wavelength. Regarding Bacillariophyceae, 475 nm was
+the most important predictor for this class (Figure~\ref{fig-VIP}).
+Indeed, the reflectance at 475 nm was higher for Bacillariophyceae than
+for any other vegetation class (Figure~\ref{fig-vegetation}), very
+likely due to the low biomass (and associated concentration of
+blue-absorbing pigments) of these unicellular organisms compared to
+seagrass and macroalgae.
 
@@
 disappear during the winter and reach their peak above-ground biomass in
-the summer and early fall. Along with these seasonal changes in biomass,
-the pigment composition and ratios also vary throughout the year,
-reflecting the plants' adaptations to different environmental conditions
-\citep{bargain2013seasonal, legare2022remote}. Standardization of
-spectral signatures helps to mitigate the impact of changing biomass on
-the spectral profile, enabling the development of a model that can
-reliably predict vegetation across different geographical locations and
-seasons. This approach allows for consistent classification of
-vegetation despite variations in biomass and fluctuations in light
-conditions, providing a robust tool for monitoring and predicting
-vegetation dynamics
+the summer and early autumn. Along with these seasonal changes in
+biomass, the pigment composition and ratios also vary throughout the
+year, reflecting the plants' adaptations to different environmental
+conditions \citep{bargain2013seasonal, legare2022remote}.
+Standardization of spectral signatures helps to mitigate the impact of
+changing biomass on the spectral profile, enabling the development of a
+model that can reliably predict vegetation across different geographical
+locations and seasons. This approach allows for consistent
+classification of vegetation despite variations in biomass and
+fluctuations in light conditions, providing a robust tool for monitoring
+and predicting vegetation dynamics
 \citep{fyfe2003spatial, COSTA2021107018, piaser2023impact}. We found 90
@@
 
-The results of Figure~\ref{fig-pixelsize} emphasize the critical role of
-pixel resolution in accurately retrieving vegetation area from remote
-sensing data. As pixel size increases, a consistent decline in area
-retrieval is observed across all vegetation types, with more pronounced
-effects for certain types, such as green algae. This highlights the
+Pixel resolution plays a critical role in accuratly retrieving
+vegetation area from remote sensing data. As pixel size increases, we
+found a consistent decline in area retrieval is observed across all
+vegetation types, with more pronounced effects for certain types, such
+as green algae (Figure~\ref{fig-pixelsize}). This highlights the
 sensitivity of spatial resolution in detecting smaller or more
 fragmented vegetation features. Green algae, being particularly patchy
-across all study sites, shows the steepest decline in area agreement as
+across all study sites, shows the steepest decline in areal agreement as
 pixel size increases, which aligns with expectations given the
@@
 processing becomes more resource-intensive due to the larger file sizes
-and computational demands. Additionally, high-resolution data requires
+and computational demands. Consequently, high-resolution data requires
 more storage and can slow down real-time applications. For large-scale
-monitoring or homogeneous vegetation types, 10 m resolution of S2/MSI or
+monitoring of homogeneous vegetation types, 10 m resolution of S2/MSI or
 even the 30 m of Landsat/OLI are often sufficient. However, when mapping
@@
 
-Because of coastal eutrophication, macroalgal blooms are becoming
+Due to increasing coastal eutrophication, macroalgal blooms are becoming
 increasingly common in many regions around the world
@@
 (i.e.~bloom of green macroalgae of the genus \emph{Ulva}) were reported
-in Brittany, France, back in the 1970s and have since been a concern for
+in Brittany, France, in the 1970s and have since been a concern for
 local stakeholders and economic activities \citep{menesguen2018marees}.
@@
 \citep{rs13081408, klemas2012remote, haro2023biointertidal}. High
-spatial resolution drone imagery, coupled with an accurate
-classification algorithm, could be used to map the early stages of
-macroalgal blooms in areas known to have regular blooms or in new sites.
-Indeed, this approach could provide early warning alerts to local
-managers and complimentary to traditional sampling methods to monitor
-coastal ecosystems. These methods are generally time and
-resource-intensive, and the findings are often difficult to scale-up
-when applied alone. Earth Observation can bridge this gap and meet the
-needs for systematic monitoring coastal ecosystems over large areas
+spatial resolution drone imagery, coupled with accurate classification
+algorithm, could be used to map the early stages of macroalgal blooms in
+areas known to have regular blooms or in new sites. Indeed, this
+approach could provide early warning alerts to local managers and
+complimentary to traditional sampling methods to monitor coastal
+ecosystems. These methods are generally time and resource-intensive, and
+the findings are often difficult to scale-up when applied alone. Earth
+Observation can bridge this gap and meet the needs for systematic
+monitoring of coastal ecosystems over large areas
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
@@
 observations, thereby enhancing our capacity to monitor vast coastal
-areas. A perspective of this work could be to develop a similar
-classifier for satellite images (e.g.~Sentinel-2), and test whether the
-discrimination between seagrass and green macroalgae is still
-operational at a coarser spatial resolution. The integration of drone
-technology facilitates a scalable approach to environmental surveillance
-while taking into account patchiness of secondary vegetation, offering
-significant advancements in the spatial and temporal resolution of data
-collection. This, in turn, supports the EU WFD's objectives by enabling
-more informed and timely management decisions for the conservation and
-restoration of aquatic ecosystems.
+areas. The integration of drone technology facilitates a scalable
+approach to environmental surveillance while taking into account
+patchiness of secondary vegetation, offering significant advancements in
+the spatial and temporal resolution of data collection. This, in turn,
+supports the EU WFD's objectives by enabling more informed and timely
+management decisions for the conservation and restoration of aquatic
+ecosystems.
 
@@
 pigment absorption in the visible region of the spectrum. There was a
-striking difference for the variable of importance to discriminate
+striking difference between the variable of importance to discriminate
 Magnoliopsida from Chlorophyceae. The latter was essentially identified
@@
 Sentinel-2/MSI, we suggest that multispectral satellite data have the
-potential to perform this discrimination between green these
-macrophytes. A Sentinel-2 algorithm could be developed, using the output
-of this current workflow as training and validation data. The findings
-underscore the importance of adopting advanced remote sensing tools in
-ecological studies and environmental monitoring, providing a foundation
-for future research and policy implementation aimed at ecosystem
-conservation and restoration.
+potential to perform this discrimination between these green
+macrophytes. The findings underscore the importance of adopting advanced
+remote sensing tools in ecological studies and environmental monitoring,
+providing a foundation for future research and policy implementation
+aimed at ecosystem conservation and restoration.
 

### 2024-10-14 index.qmd
adding bede's comments

@@
 during a period of emersion) and effectively discriminating between seagrass and green macroalgae.
-Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal, providing multispectral reflectance observation at very high spatial resolution (respectively at 8 mm and 80 mm).
-Taking advantage of their extremly high spatial resolution; the low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms), and validated using concomitant field measurements.
+Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal, providing multispectral reflectance observation at very high spatial resolution (8 mm and 80 mm respectively).
+Taking advantage of their extremly high spatial resolution; the low altitude flights were used to train a Neural Network classifier to discrimintate five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms), and validated using concomitant field measurements.
 Classification of drone imagery resulted in an overall accuracy of 94% across all sites and images, covering a total area of 467 000 m².
@@
 In particular , seagrass and green algae can be discriminated.
-The very high spatial resolution of the drone data made ot possoble to assess the influence of spatial resolution on the classification outputs, showing a limited loss in seagrass detection up to about 10m.
+The very high spatial resolution of the drone data made it possible to assess the influence of spatial resolution on the classification outputs, showing a limited loss in seagrass detection up to about 10m.
 Altogether, out findings suggest that the Multi-Spectral Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between its spatial and spectral resolution, thus offering promising perspectives for satellite remote sensing of intertidal biodiversity over lager scales.
@@
 library(rnaturalearthdata) 
-# library(rnaturalearthhires)
 library(ggforce) 
@@
 Intertidal seagrass meadows are only exposed during low tide and can be situated in difficult-to-reach mudflats, potentially leading to inaccurate and limited estimations with conventional sampling techniques [@nijland2019].
-Satellite observations have been proven effective in complementing *in situ* sampling, allowing for near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023].
+Satellite observations have been proven effective in complementing *in situ* sampling, allowing for near real-time and consistent retrieval of seagrass EOVs and EBVs over extensive meadows [@Zoffoli2021 ; @xu2021 ; @Traganos2018 ; @coffer2023 ; @davies2024intertidal ; @davies2024sentinel].
 
@@
 Satellite missions with a high temporal resolution (e.g.
-daily MODIS observation) are limited by a too coarse spatial resolution (\>100 m) to accurately map patchy seagrass meadows.
+daily MODIS observation) are limited by too coarse spatial resolution (\>100 m) to accurately map patchy seagrass meadows.
 Missions with a high spatial resolution such as Sentinel-2 (10 m) or Landsat8/9 (30 m) can be limited by low spectral resolution.
 The limited number of spectral bands challenges accurate discrimination of seagrass from other co-existing macrophytes.
-In particular, Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022], resulting in a similar spectral signature in therms of reflectance, especially in the visible range [@Davies2023 ; @bannari2022].
+In particular, Chlorophyceae (green algae) and marine Magnoliopsida (seagrass) share the same pigment composition [@ralph2002 ; @Douay2022], resulting in a similar spectral signature in terms of reflectance, especially in the visible range [@Davies2023 ; @bannari2022].
 Recently, using advanced machine-learning algorithms trained with a large hyperspectral library of more than 300 field reflectance spectra, @Davies2023 demonstrated that it was possible to discriminate Magnoliopsida from Chlorophyceae using reflectance spectra at Sentinel-2 's spectral resolution.
@@
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
-However, when applied to coastal habitat mapping, previous case studies were mostly limited to a limited number of flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
 The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae, respectively).
@@
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
-The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to asses the effect of spatial resolution on classification accuracy; and provide insights for coastal habitat mapping using satellite remote sensing.
+The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to assess the effect of spatial resolution on classification accuracy, and provide insights for coastal habitat mapping using satellite remote sensing.
 
@@
 Seven study sites distributed between France and Portugal were selected for their extensive intertidal seagrass beds.
-Two sites were located in the Gulf of Morbihan (@fig-map A), France (47.5791°N, 2.8018°W).
+Two sites were located in the Gulf of Morbihan, France (@fig-map A : 47.5791°N, 2.8018°W).
 This gulf covers an area of 115 km² and is only connected to the sea through a 900 m wide channel.
@@
 The Gulf of Morbihan is a Natura 2000 site and a Regional Protected Area due to its rich biodiversity, including its seagrass meadows, and is also classified as a RAMSAR site, which highlights its significance as a wetland of international importance.
-Two other sites were located in Bourgneuf Bay, France (46.9849°N, 2.1488°W).
-This is a 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
+Two other sites were located in Bourgneuf Bay, France (@fig-map B : 46.9849°N, 2.1488°W) which is a 340 km² semi-enclosed macrotidal bay, protected from waves by Noirmoutier Island.
 Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km² [@ZOFFOLI2020112020].
-Within this meadow, the sites observed by drones (L'Epine and Barbatre, @fig-map B) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass, syn.
+Within this meadow, the sites observed by drones (L'Epine and Barbatre) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass, syn.
 *Zostera noltei*) with very little mixing with other macrophytes.
-Bourgneuf Bay is also part of the Natura 2000 network and serves as a RAMSAR site due to its critical habitat for migratory bird species and its extensive seagrass meadows.
-Three sites were surveyed in the Ria de Aveiro Coastal Lagoon in Portugal (40.6887°N, 8.6810°W).
+Bourgneuf Bay is also part of the Natura 2000 network and serves as a RAMSAR site due to its critical habitat for migratory bird species and its extensive seagrass meadows [@Zoffoli2022].
+Three sites were surveyed in the Ria de Aveiro Coastal Lagoon in Portugal (@fig-map C : 40.6887°N, 8.6810°W).
 The extent of this lagoon is \~83 km² (at low tide) with many narrow channels, large salt marshes and many mudflats that uncover at low tide [@sousa2017blue].
 It is connected to the open sea through a single channel, with a tidal lag between the North and the South of the lagoon.
-The southernmost site (Gafanha) is a mudflat located in the Mira channel (one of the four main channels of the lagoon) whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat (@fig-map C).
+The southernmost site (Gafanha) is a mudflat located in the Mira channel (one of the four main channels of the lagoon) whereas the two other sites (Mataducos and Marinha Lanzarote) were situated in the middle of the lagoon and only accessible by boat.
 These Portuguese sites are characterized by a more diverse intertidal vegetation, where patches of seagrass intermingle with red, brown, and green macroalgae.
@@
 
-brdr1 <- fp_border_default(color = "black", width = 1)
-brdr2 <- fp_border_default(color = "grey", width = 1.5)
-brdr3 <- fp_border_default(color = "grey40", width = 1.5)
+brdr1 <- fp_border_default(color = "black", width = 0.5)
+brdr2 <- fp_border_default(color = "grey", width = 1)
+brdr3 <- fp_border_default(color = "grey40", width = 1)
 
@@
 
-save_as_image(flx1, "Figures/High_res/Table1/table_flights.png", res = 300)
+save_as_image(flx1, "Figures/High_res/Table1/table_flights.png", res = 400)
 ```
@@
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
-Pictures of each quadrat were uploaded online to the Global Biodiversity Information Facility (GBIF) platform [@BedeGbif], a public open portal to store and share biodiversity data.
+Pictures of each quadrat were uploaded online to the open-portal Global Biodiversity Information Facility (GBIF) platform [@BedeGbif].
 Each photograph was also processed to estimate the percent cover of each type of vegetation using an image processing software [ImageJ, @schneider2012nih].
 Hyperspectral reflectance signatures of each vegetation class were recorded using an ASD FieldSpec HandHeld 2 spectroradiometer, which acquires reflectance between 325 and 1075 nm, with 1 nm of spectral resolution.
-Hyperspectral signatures served dual purposes: they validate the radiometric calibration of drone data and contribute to error reduction in photo interpretations.
+Hyperspectral signatures served dual purposes: they validate the radiometric calibration of drone data and contribute to misclassification reduction in photo interpretations.
 
@@
 The process for orthomosaicking was identical for every flight.
-First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
-This cloud was cleaned using reprojection accuracy metric in order to remove noisy points.
+First, key tying points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
+This cloud was cleaned using a reprojection accuracy metric in order to remove noisy points.
 A dense point cloud was then produced using a structure from motion algorithm.
@@
 
-df_validation<-read.csv("Data/training/TrainandValid_NewStanRawMetrics_Processed_valid.csv")
+df_validation<-"Output/Validation_data" %>% 
+  list.files("ResultsNewNN_NoXanthowithNDVIWithOldandBoat.csv",recursive = T, full.names = T) %>% 
+  read.csv() %>% 
+  as_tibble() %>% 
+  rename(Truth_ID = "Truth") %>% 
+  mutate(Truth =  case_when(Truth_ID == 1 ~ "Bare_Sediment",
+                          Truth_ID == 2 ~ "Chlorophyceae",
+                          Truth_ID == 3 ~ "Bare_Sediment",
+                          Truth_ID == 4 ~ "Magnoliopsida",
+                          Truth_ID == 5 ~ "Bacillariophyceae",
+                          Truth_ID == 6 ~ "Magnoliopsida",
+                          Truth_ID == 7 ~ "Phaeophyceae",
+                          Truth_ID == 8 ~ "Rhodophyceae",
+                          Truth_ID == 9 ~ "SunGlint",
+                          Truth_ID == 10 ~ "Water",
+                          Truth_ID == 11 ~ "Xanthophyceae",
+                          Truth_ID == 12 ~ "Spartina",
+                          Truth_ID == 41 ~ "Bleached seagrasses",
+                          TRUE ~ "NA"),
+         Pred_Class = case_when(Pred_Class == "Clorophyta" ~ "Chlorophyta",
+                                Pred_Class == "Rhodphyta" ~ "Rhodphyta",
+                                Pred_Class == "Deep_Sediment" ~ "Bare_Sediment",
+                                Pred_Class == "MPB" ~ "Bare_Sediment",
+                                (Pred_Class == "Low_SPC" & NDVI > 0.2) ~ "Magnoliosida",
+                                (Pred_Class == "Low_SPC" & NDVI <= 0.2 )~ "Bare_Sediment",
+                          TRUE ~ Pred_Class)) %>% 
+  dplyr::filter(Truth != "Water",
+                Truth  != "Spartina",
+                Truth != "SunGlint",
+                Truth != "Bleached seagrasses",
+                Truth != "Xanthophyceae",
+                # Pred_Class != "Low_SPC",
+                Pred_Class != "Xanthophyceae",
+                 Pred_Class != "Water",
+                 Pred_Class != "SunGlint",
+                !Flight == "Handfisher_1_old",
+                !Flight == "Handfisher_2_old",
+                !Flight == "Handfisher_2") %>%
+  dplyr::select(-NDVI) %>% 
+  group_by(Truth) %>% 
+  reframe(validation_pixels = n()) %>% 
+  rename(True = "Truth")
 
@@
   left_join(df_validation, by = "True") %>% 
-  rename(`Validation Pixels` = "n",
+  rename(`Validation Pixels` = "validation_pixels",
          Class = "True",
@@
 The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
-Only low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
+Only data from the low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
 More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
@@
 A neural network classification model was built using the fastai workflow [@howard2018fastai].
-This model is composed by 2 hidden layers and have a total of 26 054 trainable parameters.
+This model was composed of 2 hidden layers and have a total of 26 054 trainable parameters.
 Parameters have been fine tuned using 12 epoch to minimize the error rate.
+This model has been called DISCOV, standing for Drone Intertidal Substrat Classification Of Vegetation.
 
@@
 The low altitude flights were resampled to the same spatial resolution and grid as the high flights using a median resampling method.
-Reflectance values were then extracted, and a scatterplot was generated.
-Subsequently, the slope of the linear model and the coefficient of determination (R²) were computed.
-
-The model was applied to all flights at both 12 and 120 m of altitude.
-*In situ* information on georeferenced class type and percent cover, acquired at over homogeneous vegetation patches at the same time as drone flights was used to assess the model accuracy.
+Reflectance values were then extracted, and a scatterplot was generated and the Root Mean Square Error (RMSE) was computed to compare the difference bewteen the raw and standardised reflectance.
+
+The classification model was applied to all flights at both 12 and 120 m of altitude.
+*In situ* information on georeferenced class type and percent cover, acquired over homogeneous vegetation patches at the same time as drone flights was used to assess the model accuracy.
 These images were used to construct a validation dataset indicating the presence or absence of each class.
-Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
+Additionally to the quadrat-based validation dataset, polygons of each class were photo interpreted in order to increase the number of pixels of the validation dataset.
+A total of `r my_comma(round(count_validation_pixel,-3))` pixels were used to validate the Neural Network classifier.
 The sites with the lowest and highest number of validation data were `r df_summarize[which(df_summarize$n == min(df_summarize$n)),]$Site` (`r min(df_summarize$n)` pixels) and `r df_summarize[which(df_summarize$n == max(df_summarize$n)),]$Site` (`r max(df_summarize$n)` pixels), respectively.
-A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, and Kappa coefficient, was generated for each sites.
+A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, F1 score, and Kappa coefficient, were generated for each site.
 All validation matrices were then aggregated to create an overall matrix .
@@
 Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
-Out of the twenty one predictors utilized in this study, Variable Importance was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
+Out of the 21 predictors utilized in this study, Variable Importance was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
 This is achieved by repeatedly predicting the same dataset while randomly shuffling one predictor at a time.
@@
 
-We used a Generalized Linear Model (GLM) with a Gaussian family and identity link function to examine the relationship between pixel resolution, vegetation class, and their interaction on the response variable (the loss of vegetation area within a given class).
-The model formula was as follows:
-
-$$
-VegetationLoss \sim  Resolution \times VegetationClass
-$$ {#eq-gam}
+We used a Generalized Linear Model (GLM) with a Beta distribution to examine the relationship between pixel resolution, vegetation class, and their interaction on the loss of vegetation.
+The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Bacillariophyceae, Phaeophyceae, Magnoliopsida, Chlorophyceae and Rhodophyceae).
+Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumption of the models used were met
 
@@
 At the sites where the flights at both altitudes overlapped, reflectance was compared.
-Overall there was a good agreement between the two altitudes (RMSE: 0.027 ; @fig-CompareRef).
+Overall there was a good agreement between the two altitudes (RMSE : 0.027 ; @fig-CompareRef).
 
@@
 
-Each drone flight was used to produce a prediction map, as well as a probability map that indicate the model derived likelihood of the selected class for every pixel.
+Each drone flight was used to produce a prediction map, as well as a probability map that indicates the model derived probability of the selected class for every pixel.
 The low-altitude flight conducted in Gafanha, Portugal, represented the site with the highest complexity (@fig-GafLow).
-Among the five vegetation classes on which the model was trained, four were present on this site, with green an red macroalgae mixed with a seagrass meadow.
+Among the five vegetation classes on which the model was trained, four were present on this site, with green and red macroalgae mixed with a seagrass meadow.
 There was also diatoms forming biofilms on bare sediment surface.
@@
 Among the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat).
-This site was dominated by seagrass and red macroalgae.
+Teh vegetation present at the site was dominated by seagrass and red macroalgae.
 The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
@@
 Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-Each cover an area equivalent to a 10 m Sentinel-2 pixel size.
+The zoom inserts cover an area equivalent to the size of a 10-meter Sentinel-2 pixel.
 #| label: fig-Boat
@@
 The flight over L'Epine in Noirmoutier Island, France (@fig-Dike A) was conducted near a dike, which crossed the northern part of the site from West to East.
-Alongside this dike, Fucale brown macroalgae (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks and stranded green algae (*Ulva spp.*) could be observed and this was correctly reproduced by the prediction (@fig-Dike B).
+Alongside this dike, Fucale brown macroalgae (*Fucus spp.*, *Ascophyllum nodosum*) were attached to sparse rocks, and stranded green algae (*Ulva spp.*) could be observed, which was correctly reproduced by the prediction (@fig-Dike B).
 This site was characterized by a high mixture between green macroalgae and seagrass but these two classes were correctly discriminated by the classifier (F1 score of 0.97 and 0.98 respectively).
@@
 
-The spectral bands at 444, 717 and 842 nm of the Micasense camera did not provide as important information to discriminate any of the vegetation classes.
-The band at 531 nm was the only important predictor for the classifier to accurately predict Chlorophyceae.
-In fact, at this wavelength, the Chlorophyceae spectra showed the highest reflectance among all vegetation classes.
+The spectral bands at 444, 717 and 842 nm of the Micasense camera did not provide important information to discriminate any of the vegetation classes.
+The band at 531 nm was the most important predictor by far for the classifier to accurately predict Chlorophyceae.
+In fact, at this wavelength, the Chlorophyceae spectra showed the highest reflectance among all vegetation classes (@fig-vegetation F).
 The bands at 531 and 740 nm were the most important predictors for Phaeophyceae, corresponding to the lowest reflectance among all classes.
@@
 
-glm_res_true <- glm(loss ~ area*class_fct , data = df_area_compare)
+df_area_compare <- read.csv("Data/Resampling/Area_loss_df.csv") %>% 
+  mutate(class_fct = as.factor(class_fct)) %>% 
+  as_tibble()
+
+glm_res_true <- glm(loss ~ res*class_fct , data = df_area_compare, family=quasi(link="logit", variance="mu(1-mu)"))
 # glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
@@
 summary(glm_res_true)
+
+# glm_res_true$coefficients
+# coef(summary(glm_res_true))[,4]
 
@@
 
-@fig-pixelsize illustrates the relationship between predicted area loss for various vegetation types and map resolution.
+Clear differences were seen in vegetation loss across different resolutions and vegetation classes (\@fig-pixel).
 At a fine resolution of 1m, changes in the retrieved area for each vegetation type are minimal.
-Green algae shows the highest loss rate, with 1.2% area lost compared to the native resolution (80 mm).
-As the resolution coarsens to 10m, area loss becomes significant, with green algae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
+Green algae shows the highest loss, with 1.2% area lost compared to the native resolution (80 mm).
+As the resolution coarsens to 10m, vegetation loss becomes more pronounced, with green algae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
 At a resolution of 30m, all green algae have been lost (100% compared to 8cm), while seagrass experiences a relatively small reduction of 11%.
@@
 #| fig-cap: Predicted area loss for different vegetation types (green algae, seagrass, brown algae, red algae) as a function of spatial resolution.
-Lines represent generalized linear model (GLM) predictions, and shaded areas indicate standard errors.
+Lines represent GLM predictions, and shaded areas indicate standard errors.
 As resolution decreases, predicted area loss increases for all vegetation types, with green algae showing the highest loss and seagrass the smallest at coarser resolutions.
@@
 ```
-
-The Generalized Linear Model (GLM) analysis showed a significant effect of pixel resolution on the mapped vegetation area, indicating a positive relationship between resolution and area loss ($\beta = 0.067, p < 0.001$).
-This suggests that as pixel resolution increases, the mapped area of each vegetation type decreases.
 
@@
 #| warning: false
-#| fig-cap: !expr "paste0('Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer.
-Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin.')"
+#| fig-cap: >
+#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin [@ralph2002 ; @Douay2022 @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
 #| label: fig-Pigm
@@
 The variable importance analysis (@fig-VIP) identified that the band at 531 nm was the most important for accurately identifying Chlorophyceae.
-In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in carotenoids to chlorophyll-a ratios between seagrasses and green macroalgae [@repolho2017seagrass].
-Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001] whereas the presence of fucoxanthin and zeaxanthin result in a low reflectance in the visible region (@fig-Pigm ; @fig-VIP).
+In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance among all other classes, highlighting the difference in carotenoid to chlorophyll-a ratios between seagrasses and green macroalgae [@repolho2017seagrass].
+Concerning Phaeophyceae, the thick cell walls of these macroalgae [@charrier2021growth] make it more reflective in the infrared part of the spectra [@Slaton2001], while the presence of fucoxanthin and zeaxanthin result in a low reflectance in the visible region (@fig-VIP ; @fig-Pigm).
 These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
@@
 Indeed the band at 560 nm has been identified as important for identifying this class, likely due to phycoerythrin absorption at this wavelength.
-Regarding Bacillariophyceae, the variable importance analysis (@fig-VIP) indicated that 475 nm was the most important predictor for this class.
+Regarding Bacillariophyceae, 475 nm was the most important predictor for this class (@fig-VIP).
 Indeed, the reflectance at 475 nm was higher for Bacillariophyceae than for any other vegetation class (@fig-vegetation), very likely due to the low biomass (and associated concentration of blue-absorbing pigments) of these unicellular organisms compared to seagrass and macroalgae.
@@
 In contrast to subtidal seagrasses, which maintain a relatively constant biomass throughout the year, intertidal seagrasses, like the one studied in this work, exhibit strong seasonal phenology [@davies2024sentinel].
-At some sites, they completely disappear during the winter and reach their peak above-ground biomass in the summer and early fall.
+At some sites, they completely disappear during the winter and reach their peak above-ground biomass in the summer and early autumn.
 Along with these seasonal changes in biomass, the pigment composition and ratios also vary throughout the year, reflecting the plants' adaptations to different environmental conditions [@bargain2013seasonal ; @legare2022remote].
@@
 
-The results of @fig-pixelsize emphasize the critical role of pixel resolution in accurately retrieving vegetation area from remote sensing data.
-As pixel size increases, a consistent decline in area retrieval is observed across all vegetation types, with more pronounced effects for certain types, such as green algae.
+Pixel resolution plays a critical role in accuratly retrieving vegetation area from remote sensing data.
+As pixel size increases, we found a consistent decline in area retrieval is observed across all vegetation types, with more pronounced effects for certain types, such as green algae (@fig-pixelsize).
 This highlights the sensitivity of spatial resolution in detecting smaller or more fragmented vegetation features.
-Green algae, being particularly patchy across all study sites, shows the steepest decline in area agreement as pixel size increases, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
+Green algae, being particularly patchy across all study sites, shows the steepest decline in areal agreement as pixel size increases, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
 
@@
 As resolution increases, data costs rise, and processing becomes more resource-intensive due to the larger file sizes and computational demands.
-Additionally, high-resolution data requires more storage and can slow down real-time applications.
-For large-scale monitoring or homogeneous vegetation types, 10 m resolution of S2/MSI or even the 30 m of Landsat/OLI are often sufficient.
+Consequently, high-resolution data requires more storage and can slow down real-time applications.
+For large-scale monitoring of homogeneous vegetation types, 10 m resolution of S2/MSI or even the 30 m of Landsat/OLI are often sufficient.
 However, when mapping fragmented vegetation like green algae, the precision provided by higher-resolution imagery is crucial, despite the additional costs and processing challenges it imposes.
@@
 
-Because of coastal eutrophication, macroalgal blooms are becoming increasingly common in many regions around the world [@sutton2011european ; @ye2011green].
+Due to increasing coastal eutrophication, macroalgal blooms are becoming increasingly common in many regions around the world [@sutton2011european ; @ye2011green].
 These blooms can have negative impacts on human health and local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green].
 The first green tide events (i.e.
-bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local stakeholders and economic activities [@menesguen2018marees].
+bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, in the 1970s and have since been a concern for local stakeholders and economic activities [@menesguen2018marees].
 Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* washing along the Caribbean coastlines [@louime2017sargassum], and more recently *Rugulopteryx okamurea* in southern Europe [@Roca2022].
@@
 However, due to limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote ; @haro2023biointertidal].
-High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
+High spatial resolution drone imagery, coupled with accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
 Indeed, this approach could provide early warning alerts to local managers and complimentary to traditional sampling methods to monitor coastal ecosystems.
 These methods are generally time and resource-intensive, and the findings are often difficult to scale-up when applied alone.
-Earth Observation can bridge this gap and meet the needs for systematic monitoring coastal ecosystems over large areas [@papathanasopoulou2019satellite].
+Earth Observation can bridge this gap and meet the needs for systematic monitoring of coastal ecosystems over large areas [@papathanasopoulou2019satellite].
 The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations has been increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @Zoffoli2021].
@@
 Spatially resolved data are indeed critical for calibrating and validating satellite remote sensing observations, thereby enhancing our capacity to monitor vast coastal areas.
-A perspective of this work could be to develop a similar classifier for satellite images (e.g.
-Sentinel-2), and test whether the discrimination between seagrass and green macroalgae is still operational at a coarser spatial resolution.
 The integration of drone technology facilitates a scalable approach to environmental surveillance while taking into account patchiness of secondary vegetation, offering significant advancements in the spatial and temporal resolution of data collection.
@@
 Standardized reflectance was incorporated in the Neural Network model allowing for a better discrimination of spectral features related to pigment absorption in the visible region of the spectrum.
-There was a striking difference for the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
+There was a striking difference between the variable of importance to discriminate Magnoliopsida from Chlorophyceae.
 The latter was essentially identified with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
-As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2/MSI, we suggest that multispectral satellite data have the potential to perform this discrimination between green these macrophytes.
-A Sentinel-2 algorithm could be developed, using the output of this current workflow as training and validation data.
+As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2/MSI, we suggest that multispectral satellite data have the potential to perform this discrimination between these green macrophytes.
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.

### 2024-11-12 Reply_to_reviewers.qmd
adding reviewer comments

---
title: "Replies to reviewers of the 1st round of Remote Sensing"
author: "Simon Oiry"
format: docx
editor: visual
---

# Reviewer 1

## Reviewer's comments

Overall, this paper presents a solidly researched and theoretically grounded study, offering insights into the types of seagrass bed vegetation and the importance of seagrass bed monitoring. It is a worthwhile document to read. However, there are issues related to uniqueness and experimental organization that, if addressed, could enhance its academic quality:

1.  Please highlight more clearly the innovations, distinctive features, or unique content of this paper. The work conducted in this paper is indeed sufficiently rigorous, but the unique content or scientific contributions of this work are not yet prominent enough. Since the equipment and methods used in this paper are relatively mature, the distinctive contributions of the current work are not sufficient to support its scientific contributions. Please elaborate and summarize in this regard, and if possible, consider dedicating a separate chapter for a detailed explanation.

2.  There seem to be issues with the classification results presented in Figures 5 to 8. For instance, in Figure 5, the Magnoliopsida category includes two different spectral representations of ground objects (appearing as green and brown in the RGB image). Similarly, in Figure 8, Magnoliopsida encompasses multiple spectral representations of ground objects (displayed in various colors in the RGB image). Please carefully organize and analyze the experimental results. The current figures have some Conflicts with the accuracy table and confusion matrix.

## Reply

1.  Thank you for this valuable suggestion. We appreciate your feedback on the need to further highlight the unique contributions and innovations of our study. In response, we have revised the final paragraph of the Introduction (between lines 90 and 107) to more explicitly underscore the distinctive aspects and scientific contributions of our work.

    Specifically, we have:

    1.  **Clarified the unique contribution of this paper** by emphasizing the broader geographical range and methodological scope of our drone remote sensing application for intertidal habitat mapping, as well as our focus on classifying diverse macrophyte types with high accuracy.

    2.  **Highlighted the novelty of our approach in integrating multiple spatial scales** through the simulation of satellite resolutions and quantification of the impact of spatial resolution on classification accuracy, providing a framework to better understand challenges of satellite based-habitat mapping.

    3.  **Added a summary of the study’s contributions** to contextualize our findings within existing research and underscore the broader implications of this work for coastal habitat mapping.

        We believe these additions better address the innovative aspects of our study and strengthen the scientific contribution of the manuscript.

2.  Thank you for your detailed feedback on the classification results presented in Figures 5 to 8. We appreciate your attention to the spectral representations of the Magnoliopsida category in the RGB images. Your observations regarding the varying appearances of pixels classified as seagrass in the RGB images were extremely helpful, as this distinction between different coloration of seagrasses was not sufficiently emphasized in the original manuscript.

    In response, we have revised the main text to clarify that the Magnoliopsida class includes pixels with varying spectral signatures due to differences in physiological states, such as leaf health and senescence. These variations are visible in the RGB images, where healthy seagrass leaves appear green, while senescent or altered leaves may appear brown or even white. This variation in seagrass leaf color has been observed during the field campaign by our team.

    To ensure accurate classification despite these spectral differences, we carefully included spectral signatures from both healthy and senescent seagrass states in the neural network classifier’s training dataset. This approach allowed the classifier to consistently recognize both states as part of the same seagrass class, ensuring that all instances of seagrass, regardless of coloration, are correctly classified as Magnoliopsida.

    These modification of the text can be found between lines 188-191 and also between lines 274 and 278.

### 2024-11-12 docs/_tex/index.tex
adding reviewer comments

@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
 \usepackage[]{natbib}
@@
 However, when applied to coastal habitat mapping, previous case studies
-were mostly limited to a low number of flights over a single study site,
-restricting the generalizability of their application over wider
-geographical scales
+were mostly limited to a low number of \textbf{drone} flights over a
+single study site, restricting the generalizability of their application
+over wider geographical scales
 \citep{Roman2021, collin2019improving, rossiter2020uav, Brunier2022Topographic}.
-The present study aimed at analyzing the potential of multispectral
-drone RS to map intertidal macrophytes over a diverse biogeographical
-range, with a particular focus on discriminating Magnoliopsida and
-Chlorophyceae (Seagrass and Green Algae, respectively). Nine drone
-flights were performed over soft-bottom intertidal areas along the
-Atlantic coastlines of two European countries (France and Portugal),
-covering a wide range of habitats, from monospecific seagrass meadows to
-meadows mixed with green, or red macroalgae. A deep learning algorithm
-was trained and validated for macrophyte discrimination, emphasizing
-applicability across diverse sites without a loss of prediction
-accuracy. The classification maps obtained at a very high spatial
-resolution with the drone were spatially degraded to satellite
-resolutions, making it possible to assess the effect of spatial
-resolution on classification accuracy, and provide insights for coastal
-habitat mapping using satellite remote sensing.
+\textbf{These studies have demonstrated the capability of drones to map
+intertidal habitats, including seagrasses; however, broader
+generalization of these findings is still lacking. The current paper
+uniquely expands the spatial and methodological scope of drone-based
+remote sensing for intertidal habitat mapping across a broad
+biogeographical range. It demonstrates the feasibility of accurately
+classifying diverse macrophyte types across various study sites, with a
+particular focus on distinguishing Magnoliopsida (seagrasses) and
+Chlorophyceae (green algae). Unlike previous studies, our approach
+integrates multiple spatial scales by simulating satellite resolutions
+and quantifying the impact of spatial resolution on classification
+accuracy.} Nine drone flights were performed over soft-bottom intertidal
+areas along the Atlantic coastlines of two European countries (France
+and Portugal), covering a wide range of habitats, from monospecific
+seagrass meadows to meadows mixed with green, or red macroalgae. A deep
+learning algorithm was trained and validated for macrophyte
+discrimination, emphasizing applicability across diverse sites without a
+loss of prediction accuracy. The classification maps obtained at a very
+high spatial resolution with the drone were spatially degraded to
+satellite resolutions, making it possible to assess the effect of
+spatial resolution on classification accuracy, and provide insights for
+coastal habitat mapping using satellite remote sensing. \textbf{This
+study is, therefore, among the first to quantify the effects of spatial
+resolution on the accuracy of drone-based macrophyte classification
+across a wide geographical scale, providing a framework for to better
+understand satellite-based classification challenges.}
 
@@
 by drones (L'Epine and Barbatre) contained monospecific beds of
-\emph{Nanozostera noltei} (dwarf eelgrass, syn. \emph{Zostera noltei})
-with very little mixing with other macrophytes. Bourgneuf Bay is also
-part of the Natura 2000 network and serves as a RAMSAR site due to its
-critical habitat for migratory bird species and its extensive seagrass
-meadows \citep{Zoffoli2022}. Three sites were surveyed in the Ria de
-Aveiro Coastal Lagoon in Portugal (Figure~\ref{fig-map} C : 40.6887°N,
-8.6810°W). The extent of this lagoon is \textasciitilde83 km² (at low
-tide) with many narrow channels, large salt marshes and many mudflats
-that uncover at low tide \citep{sousa2017blue}. It is connected to the
-open sea through a single channel, with a tidal lag between the North
-and the South of the lagoon. The southernmost site (Gafanha) is a
-mudflat located in the Mira channel (one of the four main channels of
-the lagoon) whereas the two other sites (Mataducos and Marinha
-Lanzarote) were situated in the middle of the lagoon and only accessible
-by boat. These Portuguese sites are characterized by a more diverse
-intertidal vegetation, where patches of seagrass intermingle with red,
-brown, and green macroalgae. The Aveiro Lagoon, like the other study
-areas, is a Natura 2000 site and a RAMSAR wetland, recognized for its
-rich mosaic of habitats and importance for biodiversity, including
-migratory bird species and intertidal vegetation.
+\emph{Zostera noltei} (dwarf eelgrass) with very little mixing with
+other macrophytes. Bourgneuf Bay is also part of the Natura 2000 network
+and serves as a RAMSAR site due to its critical habitat for migratory
+bird species and its extensive seagrass meadows \citep{Zoffoli2022}.
+Three sites were surveyed in the Ria de Aveiro Coastal Lagoon in
+Portugal (Figure~\ref{fig-map} C : 40.6887°N, 8.6810°W). The extent of
+this lagoon is \textasciitilde83 km² (at low tide) with many narrow
+channels, large salt marshes and many mudflats that uncover at low tide
+\citep{sousa2017blue}. It is connected to the open sea through a single
+channel, with a tidal lag between the North and the South of the lagoon.
+The southernmost site (Gafanha) is a mudflat located in the Mira channel
+(one of the four main channels of the lagoon) whereas the two other
+sites (Mataducos and Marinha Lanzarote) were situated in the middle of
+the lagoon and only accessible by boat. These Portuguese sites are
+characterized by a more diverse intertidal vegetation, where patches of
+seagrass intermingle with red, brown, and green macroalgae. The Aveiro
+Lagoon, like the other study areas, is a Natura 2000 site and a RAMSAR
+wetland, recognized for its rich mosaic of habitats and importance for
+biodiversity, including migratory bird species and intertidal
+vegetation.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Fig1_Map_Drone_Sites.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Fig1_Map_Drone_Sites.png}
 
@@
 different altitudes : 12 m or/and 120 m, with a spatial resolution of 8
-mm and 80 mm, respectively (Table~\ref{tbl-flights}).
+mm and 80 mm, respectively (Table~\ref{tbl-flights}). \textbf{Low
+altitude flights were used as training dataset for a neural network
+model while high altitude flight were used for validation.}
 
@@
 
-\includegraphics[width=6.63in,height=\textheight]{Figures/High_res/Table1/table_flights.png}
+\includegraphics[width=6.63in,height=\textheight,keepaspectratio]{Figures/High_res/Table1/table_flights.png}
 
@@
 (unicellular benthic diatoms forming biofilms at the sediment surface
-during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf
-eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red
+during low tide, \textbf{ranging in size from small patches (m²) to
+entire mudflats (km²)}; henceforth: Diatoms), Phaeophyceae (henceforth:
+brown macroalgae), Magnoliopsida (henceforth: Seagrasses), Chlorophyceae
+(henceforth: Green macroalgae) and Rhodophyceae (henceforth: red
 macroalgae) (Figure~\ref{fig-vegetation}). Only homogeneous vegetation
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/Spectral_shapes_total.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{Figures/Low_res/Spectral_shapes_total.png}
 
@@
 \caption{\label{fig-vegetation}The five taxonomic classes of vegetation
-used to train the Neural Network model and their raw spectral signatures
-at the spectral resolution of the Micasense RedEdge Dual MX. A :
-Magnoliopsida (Nanozostera noltei syn. Zostera noltei) ; B :
-Phaeophyceae (Fucus sp.) ; C : Rhodophyceae (Gracilaria vermiculophylla)
-; D : Chlorophyceae (Ulva sp.) ; E : Bacillariophyceae (Diatoms - MPB)}
+used to train the Neural Network model and an example of their raw
+spectral signatures at the spectral resolution of the Micasense RedEdge
+Dual MX. A : Magnoliopsida (\emph{Zostera noltei}) ; B : Phaeophyceae
+(\emph{Fucus sp.}) ; C : Rhodophyceae (\emph{Gracilaria
+vermiculophylla}) ; D : Chlorophyceae (\emph{Ulva sp.}) ; E :
+Bacillariophyceae (Diatoms - MPB). \textbf{Classes were identified
+following the World register of Marine species.}}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Figure3_workflow.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Figure3_workflow.png}
 
@@
 
-\includegraphics[width=6.63in,height=\textheight]{Figures/High_res/table_validation_px.png}
+\includegraphics[width=6.63in,height=\textheight,keepaspectratio]{Figures/High_res/table_validation_px.png}
 
@@
 habitats encountered at the different study sites: Sediment, Water,
-Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and
-Rhodophyceae. Only data from the low-altitude flights
+green macroalgae, seagrasses, diatoms, brown macroalgae and red
+macroalgae. Only data from the low-altitude flights
 (Table~\ref{tbl-flights}) were used for training because their 8 mm
 spatial resolution allowed to avoid spectral sub-pixel mixing and to
-accurately identify vegetation classes. More than 418,000 pixels at 8 mm
-resolution from the 3 training flights were used to train the model
-(Table~\ref{tbl-validationPX}). Twenty one variables were used by the
-model as predictors: the ten raw spectral bands of the Micasense RedEdge
-Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same
-ten spectral bands standardized using a min/max transformation
-(Equation~\ref{eq-std} ; \citep{Cao2017}) and the Normalized difference
-vegetation index (NDVI, Equation~\ref{eq-ndvi}). Standardisation of
-spectral bands is commonly used to eliminate the scaling differences
-between spectra and to limit the effect of biomass on the spectra shape
+accurately identify vegetation classes. \textbf{In the field, seagrasses
+displaying two distinct colors, each with a unique spectral signature,
+were observed. Careful attention was given to incorporating training
+pixels from both color types into the training dataset for the seagrass
+class. This approach was consistently applied to all classes within the
+model.} More than 418,000 pixels at 8 mm resolution from the 3 training
+flights were used to train the model (Table~\ref{tbl-validationPX}).
+Twenty one variables were used by the model as predictors: the ten raw
+spectral bands of the Micasense RedEdge Dual MX multispectral camera
+(ranging from 444 nm to 840 nm), the same ten spectral bands
+standardized using a min/max transformation (Equation~\ref{eq-std} ;
+\citep{Cao2017}) and the Normalized difference vegetation index (NDVI,
+Equation~\ref{eq-ndvi}). Standardisation of spectral bands is commonly
+used to eliminate the scaling differences between spectra and to limit
+the effect of biomass on the spectra shape
 \citep{Douay2022, Davies2023}.
@@
 such as global accuracy, sensitivity, specificity, F1 score, and Kappa
-coefficient, were generated for each site. All validation matrices were
-then aggregated to create an overall matrix .
+coefficient, were generated for each site. These metrics were computed
+as follow :
+
+\[
+\text{Global accuracy} = \frac{\sum_{i=1}^{k} \text{TP}_i}{\sum_{i=1}^{k} \left(\text{TP}_i + \text{FP}_i + \text{FN}_i \right)}
+\] \[
+\text{Sensitivity}_i = \frac{\text{TP}_i}{\text{TP}_i + \text{FN}_i}
+\] \[
+\text{Specificity}_i = \frac{\text{TN}_i}{\text{TN}_i + \text{FP}_i}
+\] \[
+\text{F1}_i = \frac{2 \cdot \text{TP}_i}{2 \cdot \text{TP}_i + \text{FP}_i + \text{FN}_i}
+\] Where \(\text{TP}_i\), \(\text{TN}_i\), \(\text{FN}_i\) and
+\(\text{FP}_i\) represent the true positives, true negatives, false
+negatives and false positives relative to the class i.
+
+All validation matrices were then aggregated to create an overall matrix
 
@@
 
-To evaluate the influence of spatial resolution on the model's output,
-we resampled the drone orthomosaics from their native resolution (8 cm
-for the high altitude flights) using the ``average'' method from the
-Terra package in R. DISCOV was then applied to these resampled rasters,
-and the results were compared to the original model predictions. For
-each resolution and vegetation class, we calculated the predicted area
-loss, where a score of 0 indicates no area loss during spatial
-resampling, and a score of 100 indicates complete loss of the vegetation
-class.
+To assess the impact of spatial resolution on the model's output, we
+resampled the drone orthomosaics from their native resolution (8 cm for
+high-altitude flights) using the ``average'' method from the terra
+package in R. \textbf{The rasters were resampled to 32 different
+resolutions, ranging from 10 cm to 30 m.} DISCOV was then applied to
+these resampled rasters, and the results were compared to the original
+model predictions. For each resolution and vegetation class, we
+calculated the predicted area loss, where a score of 0 indicates no area
+loss during spatial resampling, and a score of 100 indicates complete
+loss of the vegetation class.
 
@@
 modelled as function of the interaction between pixel resolution and
-vegetation class (Bacillariophyceae, Phaeophyceae, Magnoliopsida,
-Chlorophyceae and Rhodophyceae). Sample vs fitted residuals and
-quartile-quartile graphics were assessed visually, to ensure assumption
-of the models used were met
+vegetation class (Diatoms, brown macroalgae, seagrass, green macroalgae
+and red macroalage). Sample vs fitted residuals and quartile-quartile
+graphics were assessed visually, to ensure assumption of the models used
+were met.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/High_res/Compare_reflectance_both.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/High_res/Compare_reflectance_both.png}
 
@@
 forming biofilms on bare sediment surface. Although the seagrass was
-solely composed of a single specie, \emph{Nanozostera noltei}, various
+solely composed of a single specie, \emph{Zostera noltei}, various
 colors of this specie could be observed from dark green (corresponding
@@
 altered pigment composition). Regardless of the variation of color, the
-class Magnoliopsida was accurately predicted by the model (F1 score of
-0.96 at that site).
+class Magnoliopsida (seagrass) was accurately predicted by the model (F1
+score of 0.96 at that site).
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Gaf_Low_Pred.png}
 
@@
 was classified as seagrass by the model, including patches with
-discolored leaves. Only a few pixels were classified as green algae (F1
-score of 0.55). Patches of Rhodophyceae were correctly classified (F1
-score of 0.85). In the northern part of the site and near the land
+discolored leaves. Only a few pixels were classified as green macroalgae
+(F1 score of 0.55). Patches of red macroalgae were correctly classified
+(F1 score of 0.85). In the northern part of the site and near the land
 eadges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Boat_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Dike_Pred.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGlobal.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Validation/ConfusionMatrixGlobal.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{Figures/Low_res/VIP/Fig_VIP.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{Figures/Low_res/VIP/Fig_VIP.png}
 
@@
 Clear differences were seen in vegetation loss across different
-resolutions and vegetation classes (@fig-pixel). At a fine resolution of
-1m, changes in the retrieved area for each vegetation type are minimal.
-Green algae shows the highest loss, with 1.2\% area lost compared to the
-native resolution (80 mm). As the resolution coarsens to 10m, vegetation
-loss becomes more pronounced, with green algae again experiencing the
-greatest reduction (12\% compared to 8cm) and seagrass showing the
-smallest loss (1.3\%). At a resolution of 30m, all green algae have been
-lost (100\% compared to 8cm), while seagrass experiences a relatively
-small reduction of 11\%. Brown algae and red algae show moderate
-declines, with losses at 30m resolution reaching approximately 37\% and
-59\%, respectively.
+resolutions and vegetation classes (Figure~\ref{fig-pixelsize}). At a
+fine resolution of 1m, changes in the retrieved area for each vegetation
+type are minimal. Green algae shows the highest loss, with 1.2\% area
+lost compared to the native resolution (80 mm). As the resolution
+coarsens to 10m, vegetation loss becomes more pronounced, with green
+macroalgae again experiencing the greatest reduction (12\% compared to
+8cm) and seagrass showing the smallest loss (1.3\%). At a resolution of
+30m, all green algae have been lost (100\% compared to 8cm), while
+seagrass experiences a relatively small reduction of 11\%. Brown
+macroalgae and red macroalgae show moderate declines, with losses at 30m
+resolution reaching approximately 37\% and 59\%, respectively.
 
@@
 
-\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/High_res/resolution_plot.png}
+\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/High_res/resolution_plot.png}
 
@@
 vegetation types (green algae, seagrass, brown algae, red algae) as a
-function of spatial resolution. Lines represent GLM predictions, and
-shaded areas indicate standard errors. As resolution decreases,
-predicted area loss increases for all vegetation types, with green algae
-showing the highest loss and seagrass the smallest at coarser
-resolutions.}
+function of spatial resolution. Lines represent Generalized Linear Model
+(GLM) predictions, and shaded areas indicate standard errors. As
+resolution decreases, predicted area loss increases for all vegetation
+types, with green algae showing the highest loss and seagrass the
+smallest at coarser resolutions.}
 
@@
 
-\includegraphics[width=0.9\textwidth,height=\textheight]{Figures/Low_res/Upscaling/density_vs_Proportion.png}
+\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/Low_res/Upscaling/density_vs_Proportion.png}
 
@@
 between the percent cover and the confidence of the model to predict the
-class. To predict Chlorophyceae with a model likelihood of 0.85, a cover
-of 93 \% was needed, 90 \% for Magnoliopsida, 92 \% for Rhodophyceae and
-97 \% for Bacillariophyceae. When the vegetation cover of a given class
-was 100 \%, coarser high-flight pixels were correctly classified for all
-the classes except for Bare Sediment, which was only correctly
-classified 80\% of the time. This phenomenon may be attributed to the
-time gap between the two flights, allowing for microphytobenthos
-migration to the surface during low tide, consequently altering the
-model's classification from bare sediment to Bacillariophyceae.
+class. To predict green macroalgae with a model likelihood of 0.85, a
+cover of 93 \% was needed, 90 \% for seagrass, 92 \% for red macroalgae
+and 97 \% for diatoms When the vegetation cover of a given class was 100
+\%, coarser high-flight pixels were correctly classified for all the
+classes except for Bare Sediment, which was only correctly classified
+80\% of the time. This phenomenon may be attributed to the time gap
+between the two flights, allowing for microphytobenthos migration to the
+sediment surface during low tide, consequently altering the model's
+classification from bare sediment to Bacillariophyceae.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Disc_Pigment_Table.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Disc_Pigment_Table.png}
 
@@
 neoxanthin, PE: phycoerythrin, PC: phycocyanin
-\citetext{\citealp{ralph2002}; \citealp[@christensen1977seaweeds]{Douay2022}; \citealp{cartaxana2016regulation}; \citealp{meleder2013vivo}}.}
+\citetext{\citealp{ralph2002}; \citealp[
+\citep{christensen1977seaweeds}]{Douay2022}; \citealp{cartaxana2016regulation}; \citealp{meleder2013vivo}}.}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Validation/ConfusionMatrixGreen.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Validation/ConfusionMatrixGreen.png}
 

### 2024-11-12 index.qmd
add submission
adding reviewer comments

@@
 Satellite missions with a high temporal resolution (e.g.
-daily MODIS observation) are limited by too coarse spatial resolution (\>100 m) to accurately map patchy seagrass meadows.
+daily MODIS observation) are limited by too coarse spatial resolution (>100 m) to accurately map patchy seagrass meadows.
 Missions with a high spatial resolution such as Sentinel-2 (10 m) or Landsat8/9 (30 m) can be limited by low spectral resolution.
@@
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
-However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-The present study aimed at analyzing the potential of multispectral drone RS to map intertidal macrophytes over a diverse biogeographical range, with a particular focus on discriminating Magnoliopsida and Chlorophyceae (Seagrass and Green Algae, respectively).
-Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
+However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of **drone** flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+**These studies have demonstrated the capability of drones to map intertidal habitats, including seagrasses; however, broader generalization of these findings is still lacking.
+The current paper uniquely expands the spatial and methodological scope of drone-based remote sensing for intertidal habitat mapping across a broad biogeographical range.
+It demonstrates the feasibility of accurately classifying diverse macrophyte types across various study sites, with a particular focus on distinguishing Magnoliopsida (seagrasses) and Chlorophyceae (green algae).
+Unlike previous studies, our approach integrates multiple spatial scales by simulating satellite resolutions and quantifying the impact of spatial resolution on classification accuracy.** Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
 The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to assess the effect of spatial resolution on classification accuracy, and provide insights for coastal habitat mapping using satellite remote sensing.
+**This study is, therefore, among the first to quantify the effects of spatial resolution on the accuracy of drone-based macrophyte classification across a wide geographical scale, providing a framework for to better understand satellite-based classification challenges.**
 
@@
 Bourgneuf bay hosts a large intertidal seagrass meadow of about 6 km² [@ZOFFOLI2020112020].
-Within this meadow, the sites observed by drones (L'Epine and Barbatre) contained monospecific beds of *Nanozostera noltei* (dwarf eelgrass, syn.
-*Zostera noltei*) with very little mixing with other macrophytes.
+Within this meadow, the sites observed by drones (L'Epine and Barbatre) contained monospecific beds of *Zostera noltei* (dwarf eelgrass) with very little mixing with other macrophytes.
 Bourgneuf Bay is also part of the Natura 2000 network and serves as a RAMSAR site due to its critical habitat for migratory bird species and its extensive seagrass meadows [@Zoffoli2022].
@@
 A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements.
-Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer.
+Raw data were calibrated in reflectance using a calibration panel reflective at ~50% provided by the manufacturer.
 Across all sites, flights were made at two different altitudes : 12 m or/and 120 m, with a spatial resolution of 8 mm and 80 mm, respectively (@tbl-flights).
+**Low altitude flights were used as training dataset for a neural network model while high altitude flight were used for validation.**
 
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (unicellular benthic diatoms forming biofilms at the sediment surface during low tide), Phaeophyceae (brown macroalgae), Magnoliopsida (dwarf eelgrass), Chlorophyceae (green macroalgae) and Rhodophyceae (red macroalgae) (@fig-vegetation).
+A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (unicellular benthic diatoms forming biofilms at the sediment surface during low tide, **ranging in size from small patches (m²) to entire mudflats (km²)**; henceforth: Diatoms), Phaeophyceae (henceforth: brown macroalgae), Magnoliopsida (henceforth: Seagrasses), Chlorophyceae (henceforth: Green macroalgae) and Rhodophyceae (henceforth: red macroalgae) (@fig-vegetation).
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
@@
 #| warning: false
-#| fig-cap: "The five taxonomic classes of vegetation used to train the Neural Network model and their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX.
-A : Magnoliopsida (Nanozostera noltei syn.
-Zostera noltei)  ; B : Phaeophyceae (Fucus sp.) ; C : Rhodophyceae (Gracilaria vermiculophylla) ; D : Chlorophyceae (Ulva sp.) ; E : Bacillariophyceae (Diatoms - MPB)"
+#| fig-cap: "The five taxonomic classes of vegetation used to train the Neural Network model and an example of their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX.
+A : Magnoliopsida (*Zostera noltei*)  ; B : Phaeophyceae (*Fucus sp.*) ; C : Rhodophyceae (*Gracilaria vermiculophylla*) ; D : Chlorophyceae (*Ulva sp.*) ; E : Bacillariophyceae (Diatoms - MPB).
+**Classes were identified following the World register of Marine species.**"
 #| label: fig-vegetation
@@
   rename(Truth_ID = "Truth") %>% 
-  mutate(Truth =  case_when(Truth_ID == 1 ~ "Bare_Sediment",
+  mutate(Truth =  case_when(Truth_ID == 1 ~ "Sediment",
                           Truth_ID == 2 ~ "Chlorophyceae",
-                          Truth_ID == 3 ~ "Bare_Sediment",
+                          Truth_ID == 3 ~ "Sediment",
                           Truth_ID == 4 ~ "Magnoliopsida",
@@
                                 Pred_Class == "Rhodphyta" ~ "Rhodphyta",
-                                Pred_Class == "Deep_Sediment" ~ "Bare_Sediment",
-                                Pred_Class == "MPB" ~ "Bare_Sediment",
+                                Pred_Class == "Deep_Sediment" ~ "Sediment",
+                                Pred_Class == "MPB" ~ "Sediment",
                                 (Pred_Class == "Low_SPC" & NDVI > 0.2) ~ "Magnoliosida",
-                                (Pred_Class == "Low_SPC" & NDVI <= 0.2 )~ "Bare_Sediment",
+                                (Pred_Class == "Low_SPC" & NDVI <= 0.2 )~ "Sediment",
                           TRUE ~ Pred_Class)) %>% 
-  dplyr::filter(Truth != "Water",
+  dplyr::filter(
+    # Truth != "Water",
                 Truth  != "Spartina",
@@
   rename(`Validation Pixels` = "validation_pixels",
-         Class = "True",
-         `Training Pixels` = "Training_Pixels")
+         `Taxonomic Class` = "True",
+         `Training Pixels` = "Training_Pixels") %>% 
+  mutate(`Validation Pixels` = case_when(`Taxonomic Class` == "Water" ~ `Validation Pixels`*4,
+                                          T ~ `Validation Pixels`),
+         `Validation Pixels` = case_when(`Taxonomic Class` == "Sediment" ~ round(`Validation Pixels`/4,0),
+                                          T ~ `Validation Pixels`),
+         Name = case_when( `Taxonomic Class` == "Bacillariophyceae" ~ "Diatoms",
+                           `Taxonomic Class` == "Chlorophyceae" ~ "Green macroalgae",
+                           `Taxonomic Class` == "Magnoliopsida" ~ "Seagrass",
+                           `Taxonomic Class` == "Phaeophyceae" ~ "Brown macroalgae",
+                          `Taxonomic Class` == "Rhodophyceae" ~ "Red macroalgae",
+                          `Taxonomic Class` == "Water" ~ "Water",
+                          `Taxonomic Class` == "Sediment" ~ "Sediment"),
+         `Taxonomic Class` = case_when(`Taxonomic Class` == "Water" ~ "-",
+                                        `Taxonomic Class` == "Sediment" ~ "-",
+                                        T ~ `Taxonomic Class`)
+         ) %>% 
+  dplyr::select(Name,`Taxonomic Class`,`Training Pixels`,`Validation Pixels`)
+
 flx2 <- df_flx2 %>% 
@@
 A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model.
-The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, Chlorophyceae, Magnoliopsida, Bacillariophyceae, Phaeophyceae and Rhodophyceae.
+The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, green macroalgae, seagrasses, diatoms, brown macroalgae and red macroalgae.
 Only data from the low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
-More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
+**In the field, seagrasses displaying two distinct colors, each with a unique spectral signature, were observed.
+Careful attention was given to incorporating training pixels from both color types into the training dataset for the seagrass class.
+This approach was consistently applied to all classes within the model.** More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
 Twenty one variables were used by the model as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
@@
 A confusion matrix, along with precision metrics such as global accuracy, sensitivity, specificity, F1 score, and Kappa coefficient, were generated for each site.
-All validation matrices were then aggregated to create an overall matrix .
+These metrics were computed as follow :
+
+$$
+\text{Global accuracy} = \frac{\sum_{i=1}^{k} \text{TP}_i}{\sum_{i=1}^{k} \left(\text{TP}_i + \text{FP}_i + \text{FN}_i \right)}
+$$
+$$
+\text{Sensitivity}_i = \frac{\text{TP}_i}{\text{TP}_i + \text{FN}_i}
+$$
+$$
+\text{Specificity}_i = \frac{\text{TN}_i}{\text{TN}_i + \text{FP}_i}
+$$
+$$
+\text{F1}_i = \frac{2 \cdot \text{TP}_i}{2 \cdot \text{TP}_i + \text{FP}_i + \text{FN}_i}
+$$
+Where $\text{TP}_i$, $\text{TN}_i$, $\text{FN}_i$ and $\text{FP}_i$ represent the true positives, true negatives, false negatives and false positives relative to the class i.
+
+All validation matrices were then aggregated to create an overall matrix
 
@@
 
-To evaluate the influence of spatial resolution on the model’s output, we resampled the drone orthomosaics from their native resolution (8 cm for the high altitude flights) using the "average" method from the Terra package in R.
+To assess the impact of spatial resolution on the model's output, we resampled the drone orthomosaics from their native resolution (8 cm for high-altitude flights) using the "average" method from the terra package in R.
+**The rasters were resampled to 32 different resolutions, ranging from 10 cm to 30 m.**
 DISCOV was then applied to these resampled rasters, and the results were compared to the original model predictions.
@@
 We used a Generalized Linear Model (GLM) with a Beta distribution to examine the relationship between pixel resolution, vegetation class, and their interaction on the loss of vegetation.
-The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Bacillariophyceae, Phaeophyceae, Magnoliopsida, Chlorophyceae and Rhodophyceae).
-Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumption of the models used were met
+The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Diatoms, brown macroalgae, seagrass, green macroalgae and red macroalage).
+Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumption of the models used were met.
 
@@
 There was also diatoms forming biofilms on bare sediment surface.
-Although the seagrass was solely composed of a single specie, *Nanozostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to brown (when leaves are senescent or have an altered pigment composition).
-Regardless of the variation of color, the class Magnoliopsida was accurately predicted by the model (F1 score of 0.96 at that site).
+Although the seagrass was solely composed of a single specie, *Zostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to brown (when leaves are senescent or have an altered pigment composition).
+Regardless of the variation of color, the class Magnoliopsida (seagrass) was accurately predicted by the model (F1 score of 0.96 at that site).
 
@@
          type = case_when(str_detect(path, "pred") ~ "Pred",
+                          str_detect(path, "Prediction") ~ "Pred",
                           str_detect(path, "NDVI") ~ "NDVI",
@@
 ######### RGB #########
- Gafanha_low_ortho<-imglist %>% 
-  filter(site == "Gafanha",
-         alt == "low",
-         type == "ortho",
-         resampled == "TRUE",
-         col == "TRUE") %>%
-  pull(path) %>% 
+ Gafanha_low_ortho<- "Data/BiCOME_Flights/Gafanha_low_multi_resampled_colored.tif" %>% 
   rast() 
@@
 
-Gafanha_low_pred_zoomed<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "low",
-       type == "Pred",
-       resampled == "FALSE",
-       folder == "Input",
-       new == "TRUE") %>% 
-  pull(path) %>% 
+Gafanha_low_pred_zoomed<-"Data/BiCOME_Flights/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
   rast()
@@
   coord_sf(crs = 4326)+
-  scale_fill_manual(values=c("#70543e", "#b3ff1a","#70543e", "#DAA520", "#389318","#873e23","#b3002d", NA, "#42c9bc"), na.value = NA)+
+  scale_fill_manual(values=c("#A3A3A3", "#b3ff1a","#70543e", "#DAA520", "#389318","#5C2E1A","#b3002d", NA, "#42c9bc"), na.value = NA)+
   theme_void()+
@@
 ####  Overall map
-Gafanha_low_pred<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "low",
-       type == "Pred",
-       # resampled == "TRUE",
-       new == "TRUE") %>% 
-  pull(path) %>% 
+Gafanha_low_pred<-"Data/BiCOME_Flights/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
   rast()
@@
   scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA,NA,NA),
+                    values=c("#A3A3A3", "#b3ff1a", "#DAA520", "#389318","#5C2E1A","#b3002d", "#42c9bc",NA,NA,NA,NA),
                     na.value = NA,
@@
 
-ggsave("Figures/Maps Pred/FigX-Gaf_Low_Pred.png",plot_Gaf_Low , width = 1920*4, height = 1009*4, units = "px")
+ggsave("Figures/High_res/Maps Pred/FigX-Gaf_Low_Pred.png",plot_Gaf_Low , width = 1920*4, height = 1009*4, units = "px")
 ```
@@
 
-The high-altitude flight over Gafanha covered a total area of \~1 km² (@fig-GafHigh).
+The high-altitude flight over Gafanha covered a total area of ~1 km² (@fig-GafHigh).
 A channel contouring a small island was masked in the prediction map.
 Most of vegetation area was classified as seagrass by the model, including patches with discolored leaves.
-Only a few pixels were classified as green algae (F1 score of 0.55).
-Patches of Rhodophyceae were correctly classified (F1 score of 0.85).
+Only a few pixels were classified as green macroalgae (F1 score of 0.55).
+Patches of red macroalgae were correctly classified (F1 score of 0.85).
 In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Sporobolus maritimus* (syn.
@@
 
-GafHigh_ortho<-imglist %>% 
-  dplyr::filter(site == "Gafanha",
-                type == "ortho",
-                alt=="high",
-                col == "TRUE") %>%
-  pull(path) %>% 
+GafHigh_ortho<-"Data/BiCOME_Flights/Gafanha_high_multi_resampled_colored.tif" %>% 
   rast()
@@
 ######### Pred #######
-Gafanha_high_pred<-imglist %>% 
-filter(site == "Gafanha",
-       alt == "high",
-       type == "Pred",
-       new == "TRUE",
-       !str_detect(path, "Probs")) %>% 
-  pull(path) %>% 
+Gafanha_high_pred<-"Data/BiCOME_Flights/NewPreds/AveiroHighPrediction_nnNewStanRawMetrics_Pred_NoXantho.tif"%>% 
   rast()
@@
   scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
-                    values=c("#70543e", "#b3ff1a", "#DAA520", "#389318","#873e23","#b3002d", "#42c9bc",NA,NA),
+                    values=c("#A3A3A3", "#b3ff1a", "#DAA520", "#389318","#5C2E1A","#b3002d", "#42c9bc",NA,NA),
                     na.value = NA,
@@
 
-ggsave("Figures/Maps Pred/FigX-Gaf_High_Pred.png",plot_GafHigh , width = 2105*4, height = 1363*4, units = "px")
+ggsave("Figures/High_res/Maps Pred/FigX-Gaf_High_Pred.png",plot_GafHigh , width = 2105*4, height = 1363*4, units = "px")
 
@@
 
-Boat_rgb<-imglist %>% 
-  filter(str_detect(path,"Boat_high_RGB_merged.tif")) %>% 
-  pull(path) %>% 
+Boat_rgb<- "Data/BiCOME_Flights/Boat_high_RGB_merged.tif" %>% 
   rast()
@@
 
-rgb_Boat_zoomed_map_2
+rgb_Boat_zoomed_map_2 <- 
 ggplot()+
@@
 Boat1_pred<-imglist %>% 
-  filter(str_detect(path,"AveiroBoat1_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  filter(str_detect(path,"AveiroBoat1_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif"))%>% 
+  slice(1)  %>% 
   pull(path) %>% 
@@
   filter(str_detect(path,"AveiroBoat2_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif")) %>% 
+  slice(1) %>% 
   pull(path) %>% 
@@
                              maxcell = 5010420)+
-  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23"),
+  scale_fill_manual(values=c("#A3A3A3","#b3ff1a","#389318","#5C2E1A"),
                     na.value = NA,
@@
                              maxcell = 5010420)+
-  scale_fill_manual(values=c("#70543e","#389318","#873e23","#b3002d"),
+  scale_fill_manual(values=c("#A3A3A3","#389318","#5C2E1A","#b3002d"),
                     na.value = NA,
@@
 
-ggsave("Figures/Maps Pred/FigX-Boat_Pred.png",plot_Boat , width = 1000*4, height = 1120*4, units = "px")
+ggsave("Figures/High_res/Maps Pred/FigX-Boat_Pred.png",plot_Boat , width = 1000*4, height = 1120*4, units = "px")
 
@@
   rename(path = ".") %>% 
-  dplyr::filter(str_detect(path, "background")) %>% 
+  dplyr::filter(str_detect(path, "background"),
+                str_detect(path, "Dike")) %>% 
   pull(path) %>% 
@@
   filter(str_detect(path,"Noirmoutier_highPrediction_nnNewStanRawMetrics_Preds_NoXantho_7_4326.tif")) %>% 
+  slice(1) %>% 
   pull(path) %>% 
@@
   tidyterra::geom_spatraster(data = zoom_Pred_dike, mapping = aes(fill = layer), show.legend = F)+
-  scale_fill_manual(values=c("#70543e","#b3ff1a","#389318","#873e23","#42c9bc"),
+  scale_fill_manual(values=c("#A3A3A3","#b3ff1a","#389318","#5C2E1A","#42c9bc"),
                     na.value = NA,
@@
 
-ggsave("Figures/Maps Pred/FigX-Dike_Pred.png",plot_Dike , width = 1200*4, height = 900*4, units = "px")
+ggsave("Figures/High_res/Maps Pred/FigX-Dike_Pred.png",plot_Dike , width = 1200*4, height = 900*4, units = "px")
 
@@
 
-Clear differences were seen in vegetation loss across different resolutions and vegetation classes (\@fig-pixel).
+Clear differences were seen in vegetation loss across different resolutions and vegetation classes (@fig-pixelsize).
 At a fine resolution of 1m, changes in the retrieved area for each vegetation type are minimal.
 Green algae shows the highest loss, with 1.2% area lost compared to the native resolution (80 mm).
-As the resolution coarsens to 10m, vegetation loss becomes more pronounced, with green algae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
+As the resolution coarsens to 10m, vegetation loss becomes more pronounced, with green macroalgae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
 At a resolution of 30m, all green algae have been lost (100% compared to 8cm), while seagrass experiences a relatively small reduction of 11%.
-Brown algae and red algae show moderate declines, with losses at 30m resolution reaching approximately 37% and 59%, respectively.
+Brown macroalgae and red macroalgae show moderate declines, with losses at 30m resolution reaching approximately 37% and 59%, respectively.
 
@@
 #| fig-cap: Predicted area loss for different vegetation types (green algae, seagrass, brown algae, red algae) as a function of spatial resolution.
-Lines represent GLM predictions, and shaded areas indicate standard errors.
+Lines represent Generalized Linear Model (GLM) predictions, and shaded areas indicate standard errors.
 As resolution decreases, predicted area loss increases for all vegetation types, with green algae showing the highest loss and seagrass the smallest at coarser resolutions.
@@
 
-A percent cover of at least 80% was sufficient to have all the 80 mm pixels correctly classified, with the exception of Magnoliopsida that required a higher cover (\>90 %) to be accurately classified.
+A percent cover of at least 80% was sufficient to have all the 80 mm pixels correctly classified, with the exception of Magnoliopsida that required a higher cover (>90 %) to be accurately classified.
 Concerning the probability of each class, there is a linear relationship between the percent cover and the confidence of the model to predict the class.
-To predict Chlorophyceae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for Magnoliopsida, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for Rhodophyceae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for Bacillariophyceae.
-When the vegetation cover of a given class was 100 %, coarser high-flight pixels were correctly classified for all the classes except for Bare Sediment, which was only correctly classified 80% of the time.
-This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
+To predict green macroalgae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for seagrass, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for red macroalgae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for diatoms When the vegetation cover of a given class was 100 %, coarser high-flight pixels were correctly classified for all the classes except for Bare Sediment, which was only correctly classified 80% of the time.
+This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the sediment surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.
 

### 2024-11-12 Reply_to_reviewers.qmd
reply to reviewers

@@
 format: docx
-editor: visual
+output-file: "Reply_to_reviewers"
 ---
@@
 
-## Reviewer's comments
-
 Overall, this paper presents a solidly researched and theoretically grounded study, offering insights into the types of seagrass bed vegetation and the importance of seagrass bed monitoring.
 It is a worthwhile document to read.
-However, there are issues related to uniqueness and experimental organization that, if addressed, could enhance its academic quality:
+However, there are issues related to uniqueness and experimental organization that, if addressed, could enhance its academic quality.
 
-1.
+## Comment 1
+
 Please highlight more clearly the innovations, distinctive features, or unique content of this paper.
@@
 
-2.
-There seem to be issues with the classification results presented in Figures 5 to 8.
-For instance, in Figure 5, the Magnoliopsida category includes two different spectral representations of ground objects (appearing as green and brown in the RGB image).
-Similarly, in Figure 8, Magnoliopsida encompasses multiple spectral representations of ground objects (displayed in various colors in the RGB image).
-Please carefully organize and analyze the experimental results.
-The current figures have some Conflicts with the accuracy table and confusion matrix.
+### Reply
 
-## Reply
-
-1.
 Thank you for this valuable suggestion.
 We appreciate your feedback on the need to further highlight the unique contributions and innovations of our study.
-In response, we have revised the final paragraph of the Introduction (between lines 90 and 107) to more explicitly underscore the distinctive aspects and scientific contributions of our work.
+In response, we have revised the final paragraph of the Introduction (between lines 91 and 108) to more explicitly underscore the distinctive aspects and scientific contributions of our work.
 
@@
 
-    3.  **Added a summary of the study’s contributions** to contextualize our findings within existing research and underscore the broader implications of this work for coastal habitat mapping.
+3.  **Added a summary of the study's contributions** to contextualize our findings within existing research and underscore the broader implications of this work for coastal habitat mapping.
 
@@
 
-2.
+## Comment 2
+
+### reply
+
 Thank you for your detailed feedback on the classification results presented in Figures 5 to 8.
@@
 
-    To ensure accurate classification despite these spectral differences, we carefully included spectral signatures from both healthy and senescent seagrass states in the neural network classifier’s training dataset.
+To ensure accurate classification despite these spectral differences, we carefully included spectral signatures from both healthy and senescent seagrass states in the neural network classifier's training dataset.
 This approach allowed the classifier to consistently recognize both states as part of the same seagrass class, ensuring that all instances of seagrass, regardless of coloration, are correctly classified as Magnoliopsida.
 
-    These modification of the text can be found between lines 188-191 and also between lines 274 and 278.
+These modification of the text can be found between lines 194-197 and also between lines 280 and 284.
+
+# Reviewer 2
+
+This study focused on discriminating the seagrass and green macroalgae in the intertidal zone.
+High-resolution drone image is used for this work which show a higher accuracy in classifying the seagrass and other macrophytes (green algae, brown algae, red algae & diatom).
+The approach will be helpful to work with satellite image however, several issues should be addressed before this paper can be further considered for acceptance.
+
+## Comment 1
+
+In the "Introduction" part, previous studies on seagrass and macroalgae detection need to be described. Also, prior research using drone on seagrass is not clearly mentioned.
+
+### Reply
+
+Thank you for this suggestion.
+To address it, we have expanded the Introduction between lines 91 and 93 to include relevant studies on seagrass and macroalgae detection, as well as previous research using drones for seagrass mapping.
+These additions clarify the context and unique contributions of our study.
+
+## Comment 2
+
+In Table 1, three sites were used for training and other sites were used for validation.
+However, there are no description what is the features of those 3 sites and why they were selected for training?
+
+### Reply
+
+Thank you for pointing this out.
+We have updated the manuscript to clarify why these specific sites were selected for training, emphasizing that their 8 mm of resolution allow for an accurate photo interpretation of vegetation classes.
+Line 146 - 149
+
+## Comment 3
+
+Figure 2 displayed the image for five different classes.
+However, no clear description on each classes feature are not provided.
+What is the difference between each class (floating, submerged, or attached to bottom) and how they can by distinguished is not clear.
+What is the variance for each class.
+The graph only shows the reflectance value based on the wavelength, but it is not clear which value is used for this graph and how many sample are taken?
+
+### Reply
+
+Thank you for your comments on Figure 2.
+In response, we have expanded the description of each class in the text to clarify their distinguishing characteristics (Lines 155 - 164).
+Regarding the spectral shapes shown in Figure 2, we have updated the figure caption to specify that these represent example spectral signatures that are characteristic of each class
+
+## Comment 4
+
+Seagrass color can be varied from green to brown based on the vegetation condition. Then what process is followed to distinguish from both green and brown macroalgae.
+
+### Reply
+
+Thank you for this accurate observation.
+In response, we have revised the main text to clarify that the Magnoliopsida class includes pixels with varying spectral signatures due to differences in physiological states, such as leaf health and senescence.
+These variations are visible in the RGB images, where healthy seagrass leaves appear green, while senescent or altered leaves may appear brown or even white.
+This variation in seagrass leaf color has been observed during the field campaign by our team.
+
+To ensure accurate classification despite these spectral differences, we carefully included spectral signatures from both healthy and senescent seagrass states in the neural network classifier's training dataset.
+This approach allowed the classifier to consistently recognize both states as part of the same seagrass class, ensuring that all instances of seagrass, regardless of coloration, are correctly classified as Magnoliopsida.
+
+These modification of the text can be found between lines 194-197 and also between lines 280 and 284.
+
+## Comment 5
+
+Description on the diatom classification (Figure 2(E)) is not clear. What is the dimension of diatom or the biofilm they produced.
+
+### Reply
+
+Thank you for your comment. To address this, we have added clarification about the biofilm extent in the main text (Line 156- 157) and included scales in each image of Figure 2 to improve clarity.
+
+## Comment 6
+
+In Figure 3, 'photo interpret polygons' is mentioned without the prior description on it.
+
+### Reply
+
+Thank you for pointing this out.
+The term "photo-interpret polygons" in Figure 3 was potentially misleading, as it had not been introduced earlier in the text.
+We have replaced it with "training polygons" in Figure 3, and have clarified the process of creating these polygons in the text (Line 189).
+
+## Comment 7
+
+For each class, along with the scientific name and taxonomic description the general name should be added for easy understanding.
+
+### Reply
+
+Thank you for your feedback.
+In the original manuscript, both taxonomic and common names for vegetation types were used inconsistently.
+To improve consistency, we have replaced taxonomic names with common names wherever possible throughout the text.
+Additionally, we have added a new column in Table 2 to display both the taxonomic and common names for each vegetation class.
+
+## Comment 8
+
+It is mentioned, 7 different classes were categorized for training but in Table 2, information on 5 classes are provided
+
+### Reply
+
+Thank you for your observation. You are correct; the missing classes could have been confusing for readers. We have now added these classes to Table 2 for completeness.
+
+## Comment 9
+
+What kind of variables are used as predictors and description on those variables is required. How many variables are used (20 or 21)?
+
+### Reply
+
+As described in Line 198 - 201, 21 variables were used as predictors for the model, including:
+
+-   10 raw reflectance spectral bands,
+
+-   The same 10 bands standardized, and
+
+-   The Normalized Difference Vegetation Index (NDVI).
+
+## Comment 10
+
+Why the Equation 1 and 2 are used is not clear? The main purpose of both equation and their value need to be mentioned.
+
+### Reply
+
+Equations 1 and 2 were applied to the raw spectral data from the drone to generate the 10 standardized reflectance bands (Equation 1) and the NDVI (Equation 2), which were used as predictors for the model.
+You can find this information line 198 - 203
+
+## Comment 11
+
+Resampling was conducted to evaluate the influence of spatial resolution on classification. However, no description on the resampling resolution is provided.
+
+### Reply
+
+Thank you for pointing this out. You are absolutely right; these details were overlooked in the original manuscript. We have revised the text at Line 249 to include this clarification.
+
+## Comment 12
+
+In the classification figure, making a visual difference between the sediment class & Phaeophyceae class is difficult due to similar color pattern.
+
+### Reply
+
+Thank you for highlighting this issue.
+The color scale of the classification maps has been adjusted to improve the distinction between sediment and brown algae, addressing a key concern in the previous maps.
+
+## Comment 13
+
+For validation, how sensitivity, specificity and accuracy are calculated need to be mentioned by using equation.
+
+### Reply
+
+Thank you for your suggestion. The equations used to compute accuracy metrics have been added to the Materials and Methods section (Line 231 - 234) for clarity.
+
+## Comment 14
+
+The figure caption need to be revised. The abbreviation used in figure caption need to be elaborated such as in Figure 11 'GLM predictions'.
+
+### Reply
+
+Thank you for your suggestion. We have added descriptions for all acronyms used in the figure captions for clarity.
+
+##
+
+##

### 2024-11-12 docs/_tex/index.tex
reply to reviewers

@@
 different altitudes : 12 m or/and 120 m, with a spatial resolution of 8
-mm and 80 mm, respectively (Table~\ref{tbl-flights}). \textbf{Low
-altitude flights were used as training dataset for a neural network
-model while high altitude flight were used for validation.}
+mm and 80 mm, respectively (Table~\ref{tbl-flights}).
+\textbf{Low-altitude flights, with a spatial resolution of 8 mm, were
+used to build the training dataset for the neural network, as this high
+resolution allowed for precise photo-interpretation of vegetation
+classes. In contrast, high-altitude flights were utilized for validation
+purposes.}
 
@@
 and vertical accuracy of 10cm. A dGPS was also used to georeference
-quadrats of 0.25 m² ,which assessed the presence or absence of five key
-taxonomic classes of intertidal vegetation : Bacillariophyceae
-(unicellular benthic diatoms forming biofilms at the sediment surface
-during low tide, \textbf{ranging in size from small patches (m²) to
-entire mudflats (km²)}; henceforth: Diatoms), Phaeophyceae (henceforth:
-brown macroalgae), Magnoliopsida (henceforth: Seagrasses), Chlorophyceae
-(henceforth: Green macroalgae) and Rhodophyceae (henceforth: red
-macroalgae) (Figure~\ref{fig-vegetation}). Only homogeneous vegetation
-patches extending over several meters were selected as ground control
-points. Pictures of each quadrat were uploaded online to the open-portal
-Global Biodiversity Information Facility (GBIF) platform
-\citep{BedeGbif}. Each photograph was also processed to estimate the
-percent cover of each type of vegetation using an image processing
-software \citep[ImageJ,][]{schneider2012nih}. Hyperspectral reflectance
-signatures of each vegetation class were recorded using an ASD FieldSpec
-HandHeld 2 spectroradiometer, which acquires reflectance between 325 and
-1075 nm, with 1 nm of spectral resolution. Hyperspectral signatures
-served dual purposes: they validate the radiometric calibration of drone
-data and contribute to misclassification reduction in photo
-interpretations.
+quadrats of 0.25 m², which assessed the presence or absence of five key
+taxonomic classes of intertidal vegetation: Bacillariophyceae
+\textbf{(unicellular benthic diatoms forming biofilms at the sediment
+surface during low tide, ranging in size from small patches (m²) to
+entire mudflats (km²); henceforth: Diatoms), Phaeophyceae (brown
+macroalgae that are generally attached to rocks or other substrates and
+often form dense beds in the intertidal zone; henceforth: brown
+macroalgae), Magnoliopsida (seagrasses, which are rooted flowering
+plants that grow submerged and form extensive meadows on soft sediments;
+henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically
+found attached to rocks or drifting in the water, and known for their
+bright green color due to chlorophyll; henceforth: Green macroalgae),
+and Rhodophyceae (red macroalgae that are mostly attached to hard
+substrates and often occur in smaller patches; henceforth: red
+macroalgae)}. Only homogeneous vegetation patches extending over several
+meters were selected as ground control points. Pictures of each quadrat
+were uploaded online to the open-portal Global Biodiversity Information
+Facility (GBIF) platform \citep{BedeGbif}. Each photograph was also
+processed to estimate the percent cover of each type of vegetation using
+an image processing software \citep[ImageJ,][]{schneider2012nih}.
+Hyperspectral reflectance signatures of each vegetation class were
+recorded using an ASD FieldSpec HandHeld 2 spectroradiometer, which
+acquires reflectance between 325 and 1075 nm, with 1 nm of spectral
+resolution. Hyperspectral signatures served dual purposes: they validate
+the radiometric calibration of drone data and contribute to
+misclassification reduction in photo interpretations.
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Figure3_workflow.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Figure3_workflow.png}
 

### 2024-11-12 index.qmd
reply to reviewers

@@
 Across all sites, flights were made at two different altitudes : 12 m or/and 120 m, with a spatial resolution of 8 mm and 80 mm, respectively (@tbl-flights).
-**Low altitude flights were used as training dataset for a neural network model while high altitude flight were used for validation.**
+**Low-altitude flights, with a spatial resolution of 8 mm, were used to build the training dataset for the neural network, as this high resolution allowed for precise photo-interpretation of vegetation classes.
+In contrast, high-altitude flights were utilized for validation purposes.**
 
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m² ,which assessed the presence or absence of five key taxonomic classes of intertidal vegetation : Bacillariophyceae (unicellular benthic diatoms forming biofilms at the sediment surface during low tide, **ranging in size from small patches (m²) to entire mudflats (km²)**; henceforth: Diatoms), Phaeophyceae (henceforth: brown macroalgae), Magnoliopsida (henceforth: Seagrasses), Chlorophyceae (henceforth: Green macroalgae) and Rhodophyceae (henceforth: red macroalgae) (@fig-vegetation).
+A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(unicellular benthic diatoms forming biofilms at the sediment surface during low tide, ranging in size from small patches (m²) to entire mudflats (km²); henceforth: Diatoms), Phaeophyceae (brown macroalgae that are generally attached to rocks or other substrates and often form dense beds in the intertidal zone; henceforth: brown macroalgae), Magnoliopsida (seagrasses, which are rooted flowering plants that grow submerged and form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or drifting in the water, and known for their bright green color due to chlorophyll; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae that are mostly attached to hard substrates and often occur in smaller patches; henceforth: red macroalgae)**.
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
@@
 layout<-"Data/Figure2_Workflow" %>%
-  list.files("V4.txt",full.names = T, recursive = T) %>%
+  list.files("V5.txt",full.names = T, recursive = T) %>%
   read_delim(delim = "\t", escape_double = FALSE,
@@
 
-knitr::include_graphics("./Figures/Low_res/Figure3_workflow.png")
+knitr::include_graphics("./Figures/Figure3_workflow.png")
 

### 2024-11-13 index.qmd
adding pierres comments

@@
 Nine drone flights were conducted at two different altitudes (12 m and 120 m) across heterogeneous intertidal European habitats in France and Portugal, providing multispectral reflectance observation at very high spatial resolution (8 mm and 80 mm respectively).
-Taking advantage of their extremly high spatial resolution; the low altitude flights were used to train a Neural Network classifier to discrimintate five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Diatoms), and validated using concomitant field measurements.
+Taking advantage of their extremly high spatial resolution; the low altitude flights were used to train a Neural Network classifier to discrimintate five taxonomic classes of intertidal vegetation: Magnoliopsida (Seagrass), Chlorophyceae (Green macroalgae), Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic Bacillariophyceae (Benthic diatoms), and validated using concomitant field measurements.
 Classification of drone imagery resulted in an overall accuracy of 94% across all sites and images, covering a total area of 467 000 m².
@@
 **Low-altitude flights, with a spatial resolution of 8 mm, were used to build the training dataset for the neural network, as this high resolution allowed for precise photo-interpretation of vegetation classes.
-In contrast, high-altitude flights were utilized for validation purposes.**
+In contrast, high-altitude flights were used for validation purposes.**
 
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(unicellular benthic diatoms forming biofilms at the sediment surface during low tide, ranging in size from small patches (m²) to entire mudflats (km²); henceforth: Diatoms), Phaeophyceae (brown macroalgae that are generally attached to rocks or other substrates and often form dense beds in the intertidal zone; henceforth: brown macroalgae), Magnoliopsida (seagrasses, which are rooted flowering plants that grow submerged and form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or drifting in the water, and known for their bright green color due to chlorophyll; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae that are mostly attached to hard substrates and often occur in smaller patches; henceforth: red macroalgae)**.
+A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(benthic diatoms forming biofilms at the sediment surface during low tide with biofilm's size ranging from small patches (m²) to entire mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally attached to rocks or other substrates able to form dense beds in the intertidal zone; henceforth: Brown macroalgae), Magnoliopsida (seagrasses, rooted flowering marine plants able to form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae, attached to hard substrates and generally forming smaller patches; henceforth: Red macroalgae)**.
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
@@
 #| fig-cap: "The five taxonomic classes of vegetation used to train the Neural Network model and an example of their raw spectral signatures at the spectral resolution of the Micasense RedEdge Dual MX.
-A : Magnoliopsida (*Zostera noltei*)  ; B : Phaeophyceae (*Fucus sp.*) ; C : Rhodophyceae (*Gracilaria vermiculophylla*) ; D : Chlorophyceae (*Ulva sp.*) ; E : Bacillariophyceae (Diatoms - MPB).
+A : Magnoliopsida (*Zostera noltei*)  ; B : Phaeophyceae (*Fucus sp.*) ; C : Rhodophyceae (*Gracilaria vermiculophylla*) ; D : Chlorophyceae (*Ulva sp.*) ; E : Bacillariophyceae (Benthic diatoms).
 **Classes were identified following the World register of Marine species.**"
@@
 Parallelograms represent input or output data, and rectangles represent Python processing algorithms.
-The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights (pixel size: 8 mm) were utilized for training and prediction of the Neural Network model, whereas lower-resolution flights (pixel size: 80 mm) were solely employed for prediction purposes.
+The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights (pixel size: 8 mm) were used for training and prediction of the Neural Network model, whereas lower-resolution flights (pixel size: 80 mm) were solely employed for prediction purposes.
 Validation has been performed on both high and low resolution flights."
@@
                                           T ~ `Validation Pixels`),
-         Name = case_when( `Taxonomic Class` == "Bacillariophyceae" ~ "Diatoms",
+         Name = case_when( `Taxonomic Class` == "Bacillariophyceae" ~ "Benthic diatoms",
                            `Taxonomic Class` == "Chlorophyceae" ~ "Green macroalgae",
@@
 A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model.
-The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, green macroalgae, seagrasses, diatoms, brown macroalgae and red macroalgae.
+The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, green macroalgae, seagrasses, Benthic diatoms, brown macroalgae and red macroalgae.
 Only data from the low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
-**In the field, seagrasses displaying two distinct colors, each with a unique spectral signature, were observed.
+**In the field, seagrasses displaying two types of color were observed (i.e.
+whereas most seagrass had green leaves, brownish leaves were also observed due to senescence or photo-degradaration).
 Careful attention was given to incorporating training pixels from both color types into the training dataset for the seagrass class.
@@
 Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class.
-Out of the 21 predictors utilized in this study, Variable Importance was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
+Out of the 21 predictors used in this study, Variable Importance was computed only for the raw and standardized values of the 10 spectral bands captured by the MicaSense camera.
 This is achieved by repeatedly predicting the same dataset while randomly shuffling one predictor at a time.
@@
 We used a Generalized Linear Model (GLM) with a Beta distribution to examine the relationship between pixel resolution, vegetation class, and their interaction on the loss of vegetation.
-The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Diatoms, brown macroalgae, seagrass, green macroalgae and red macroalage).
+The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Benthic diatoms, brown macroalgae, seagrass, green macroalgae and red macroalage).
 Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumption of the models used were met.
@@
 Among the five vegetation classes on which the model was trained, four were present on this site, with green and red macroalgae mixed with a seagrass meadow.
-There was also diatoms forming biofilms on bare sediment surface.
+There was also benthic diatoms forming biofilms on bare sediment surface.
 Although the seagrass was solely composed of a single specie, *Zostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to brown (when leaves are senescent or have an altered pigment composition).
@@
 Concerning the probability of each class, there is a linear relationship between the percent cover and the confidence of the model to predict the class.
-To predict green macroalgae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for seagrass, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for red macroalgae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for diatoms When the vegetation cover of a given class was 100 %, coarser high-flight pixels were correctly classified for all the classes except for Bare Sediment, which was only correctly classified 80% of the time.
+To predict green macroalgae with a model likelihood of 0.85, a cover of `r round((lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100,0)` % was needed, `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % for seagrass, `r round((lm_Rodo$coefficients[[2]]*85+lm_Rodo$coefficients[[1]])*100,0)` % for red macroalgae and `r round((lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100,0)` % for benthic diatoms When the vegetation cover of a given class was 100 %, coarser high-flight pixels were correctly classified for all the classes except for Bare Sediment, which was only correctly classified 80% of the time.
 This phenomenon may be attributed to the time gap between the two flights, allowing for microphytobenthos migration to the sediment surface during low tide, consequently altering the model's classification from bare sediment to Bacillariophyceae.

### 2024-11-13 index.qmd
add Laurent's comments

@@
 However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of **drone** flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-**These studies have demonstrated the capability of drones to map intertidal habitats, including seagrasses; however, broader generalization of these findings is still lacking.
+**These studies have demonstrated the capability of drones to map intertidal habitats, including seagrasses; however a broader generalization of these findings is still lacking.
 The current paper uniquely expands the spatial and methodological scope of drone-based remote sensing for intertidal habitat mapping across a broad biogeographical range.
@@
 Unlike previous studies, our approach integrates multiple spatial scales by simulating satellite resolutions and quantifying the impact of spatial resolution on classification accuracy.** Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
-A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without a loss of prediction accuracy.
+A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without losing prediction accuracy.
 The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to assess the effect of spatial resolution on classification accuracy, and provide insights for coastal habitat mapping using satellite remote sensing.
-**This study is, therefore, among the first to quantify the effects of spatial resolution on the accuracy of drone-based macrophyte classification across a wide geographical scale, providing a framework for to better understand satellite-based classification challenges.**
+**This study is, therefore, among the first to quantify the effects of spatial resolution on the accuracy of drone-based macrophyte classification across a wide geographical scale, providing a framework to better understand satellite-based classification challenges.**
 
@@
 
+sovereignty10 <- ne_countries(scale = 10, returnclass = "sf")
+
 world_map <- sovereignty10 %>% 
   st_as_sf() %>% 
-  dplyr::filter(SOVEREIGNT%in%c("Spain","France","Portugal",
+  dplyr::filter(sovereignt%in%c("Spain","France","Portugal",
                                 "Italy","Andorra",
@@
   st_as_sf() %>% 
-  dplyr::filter(SOVEREIGNT%in%c("United Kingdom") ) %>% 
+  dplyr::filter(sovereignt%in%c("United Kingdom") ) %>% 
   st_cast("POLYGON")
@@
   st_as_sf() %>% 
-  dplyr::filter(SOVEREIGNT%in%c("Spain","France","Portugal",
+  dplyr::filter(sovereignt%in%c("Spain","France","Portugal",
                                 "Italy","Andorra",
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#CFCFCF"))+
+                    values = c("#70543e", "#CFCFCF"))+
   geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#CFCFCF"))+
+                    values = c("#70543e", "#CFCFCF"))+
   geom_sf(data = mask_BB, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
-                    values = c("#7DC27D", "#CFCFCF"))+
+                    values = c("#70543e", "#CFCFCF"))+
   geom_sf(data = mask_Morb, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
 #|   Location of drone flights in France and Portugal.
-A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites).
-Green areas represents the intertidal zone.
+A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites).
+Brown areas represents the intertidal zone.
 #| label: fig-map
@@
 
-At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands ranging from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
+At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands ranging from the blue to the near-infrared (NIR): 444, 475, 531, 560, 650, 668, 705, 717, 740 and 840 nm.
 To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees.
@@
 #| label: tbl-flights
-#| tbl-cap: List of drone flight, summarising the date, the altitude, and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
+#| tbl-cap: List of drone flights, summarising the date, the altitude, and the purpose of each flight. 12 m  and 120 m flights have a spatial resolution of 8 and 80 mm respectively.
 #| cache: true
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(benthic diatoms forming biofilms at the sediment surface during low tide with biofilm's size ranging from small patches (m²) to entire mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally attached to rocks or other substrates able to form dense beds in the intertidal zone; henceforth: Brown macroalgae), Magnoliopsida (seagrasses, rooted flowering marine plants able to form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae, attached to hard substrates and generally forming smaller patches; henceforth: Red macroalgae)**.
+A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(benthic diatoms forming biofilms at the sediment surface during low tide with biofilm's size ranging from small patches (m²) to entire mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally attached to rocks or other substrates able to form dense beds in the intertidal zone; henceforth: Brown macroalgae), Magnoliopsida (seagrasses, rooted flowering marine plants able to form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae, attached to hard substrates but can also be found on soft-bottom substrate; henceforth: Red macroalgae)**.
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
@@
 
-gaf_low_multi<- "./Data/BiCOME_Flights/Aveiro/Aveiro_MULTI_12m_ortho_1801.tif" %>% 
+gaf_low_multi<- "Data/BiCOME_Flights/Aveiro/GafanhaLow/Aveiro_MULTI_12m_ortho_1801.tif" %>% 
   rast()
@@
 
- Gafanha_low_pred<-"./Data/BiCOME_Flights/Aveiro/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
+ Gafanha_low_pred<-"Data/BiCOME_Flights/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
      rast()
@@
 Brown<-ggplot()+
-  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Pheophyceae_cropped.png"))+
+  geom_spatraster_rgb(data = rast("Data/Pictures/Figure2/Pheophyceae_cropped2.png"))+
   coord_equal()+
@@
 A : Magnoliopsida (*Zostera noltei*)  ; B : Phaeophyceae (*Fucus sp.*) ; C : Rhodophyceae (*Gracilaria vermiculophylla*) ; D : Chlorophyceae (*Ulva sp.*) ; E : Bacillariophyceae (Benthic diatoms).
-**Classes were identified following the World register of Marine species.**"
+**The taxonomy was chacked following the World Register of Marine Species (WORMS).**"
 #| label: fig-vegetation
@@
 The process for orthomosaicking was identical for every flight.
-First, key tying points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud.
-This cloud was cleaned using a reprojection accuracy metric in order to remove noisy points.
+First, key tying points were detected inside each image and between overlapping images in order to obtain a sparse point cloud.
+This cloud was cleaned using a reprojection accuracy metric to remove noisy points.
 A dense point cloud was then produced using a structure from motion algorithm.
 A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image [@nebel2020review].
-Low altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
-High altitude flights allowed to cover larger areas and produced images with a pixel size of 80 mm (@tbl-flights).
+Low-altitude drone flights produced ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation.
+High-altitude flights allowed to cover larger areas and produced images with a pixel size of 80 mm (@tbl-flights).
 
@@
 
-The spectral similarities of the reflectance signatures at the spectral resolution of the micasense senor between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
+The spectral similarities of the reflectance signatures at the spectral resolution of the Micasense senor between intertidal green macrophytes (Magnoliopsida and Chlorophyceae) make their discrimination challenging using simple classification algorithms (@fig-vegetation F).
 To overcome this challenge, a deep learning classification method was trained, validated, and applied to each drone flight (@fig-workflow).
@@
 The overall workflow of this study is divided into two distinct parts based on the spatial resolution of the drone flights: high-resolution flights (pixel size: 8 mm) were used for training and prediction of the Neural Network model, whereas lower-resolution flights (pixel size: 80 mm) were solely employed for prediction purposes.
-Validation has been performed on both high and low resolution flights."
+Validation has been performed on both high and low-resolution flights."
 #| label: fig-workflow
@@
 A dataset containing photo-interpreted drone reflectance pixels was built to train a Neural Network model.
-The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: Sediment, Water, green macroalgae, seagrasses, Benthic diatoms, brown macroalgae and red macroalgae.
+The training pixels were categorized into seven different classes, representing the various habitats encountered at the different study sites: sediment, water, green macroalgae, seagrasses, Benthic diatoms, brown macroalgae and red macroalgae.
 Only data from the low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
-**In the field, seagrasses displaying two types of color were observed (i.e.
+**In the field, seagrasses displayed two types of color were observed (i.e.
 whereas most seagrass had green leaves, brownish leaves were also observed due to senescence or photo-degradaration).
@@
 This approach was consistently applied to all classes within the model.** More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
-Twenty one variables were used by the model as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
+For model training, 21 variables were used as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
 Standardisation of spectral bands is commonly used to eliminate the scaling differences between spectra and to limit the effect of biomass on the spectra shape [@Douay2022 ; @Davies2023].
@@
 A neural network classification model was built using the fastai workflow [@howard2018fastai].
-This model was composed of 2 hidden layers and have a total of 26 054 trainable parameters.
-Parameters have been fine tuned using 12 epoch to minimize the error rate.
+This model was composed of 2 hidden layers and has a total of 26 054 trainable parameters.
+Parameters have been fine-tuned using 12 epoch to minimize the error rate.
 This model has been called DISCOV, standing for Drone Intertidal Substrat Classification Of Vegetation.
@@
 The workflow of this study revolves around two distinct flight heights (12 and 120 m, @fig-workflow) where ensuring consistency between reflectances at both heights is crucial.
-This comparison was conducted at sites where low and high altitude flights overlapped.
-The low altitude flights were resampled to the same spatial resolution and grid as the high flights using a median resampling method.
-Reflectance values were then extracted, and a scatterplot was generated and the Root Mean Square Error (RMSE) was computed to compare the difference bewteen the raw and standardised reflectance.
+This comparison was conducted at sites where low and high-altitude flights overlapped.
+To compare reflectances of both flights, the low-altitude flights were resampled to the same spatial resolution and grid as the high-altitude flights using a median resampling method.
+Reflectance values were then extracted, and a scatterplot was generated.
+The Root Mean Square Error (RMSE) was computed to compare the difference between the raw and standardised reflectance.
 
@@
 We used a Generalized Linear Model (GLM) with a Beta distribution to examine the relationship between pixel resolution, vegetation class, and their interaction on the loss of vegetation.
-The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Benthic diatoms, brown macroalgae, seagrass, green macroalgae and red macroalage).
-Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumption of the models used were met.
+The loss of vegetation was modelled as function of the interaction between pixel resolution and vegetation class (Benthic diatoms, brown macroalgae, seagrass, green macroalgae and red macroalgae).
+Sample vs fitted residuals and quartile-quartile graphics were assessed visually, to ensure assumptions of the models used were met.
 
@@
 This plot provided a visual representation of the model’s behavior in mixed vegetation scenarios.
-It helps to understand the minimum vegetation cover of a given class within a pixel necessary for the model to confidently predict that class.
+It helped to understand the minimum vegetation cover of a given class within a pixel necessary for the model to confidently predict that class.
 
@@
 In this study, drone flights were conducted at two different altitudes (12 and 120 m) to construct the neural network model.
-At the sites where the flights at both altitudes overlapped, reflectance was compared.
+At the sites where the flights at both altitudes overlapped, the reflectance was compared.
 Overall there was a good agreement between the two altitudes (RMSE : 0.027 ; @fig-CompareRef).

### 2024-11-13 index.qmd
add Laurent's comments

@@
   theme(
+    axis.text.x = element_text(size = 15),
+    plot.background = element_rect(fill = 'white', color = NA), 
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 17),
+    axis.title.y = element_text(size = 17),
+    legend.text = element_text(size = 15),
+    legend.title = element_text(size = 17, vjust = 1),
     legend.position = "top",
@@
                                labels = c("1","1000","2000"))+
+  scale_y_continuous(position = "right",
+                     limits = c(0.05,1))+
   # scale_color_gradient(na.value = 1)+
@@
   theme_Bede()+
-  ylim(c(0.05,1))+
   xlim(c(0.05,1))+
@@
 #| warning: false
+img_raw <- rast("./Figures/High_res/Compare_reflectance.png")
 
 RAW <- ggplot()+
-  geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance.png"))+
-  coord_equal()+
+  geom_spatraster_rgb(data = img_raw)+
+  coord_equal(expand = F)+
   geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
@@
   geom_spatraster_rgb(data = rast("./Figures/High_res/Compare_reflectance_std.png"))+
-  coord_equal()+
+  coord_equal(expand = F)+
   geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
@@
 
-There was a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
+There was a slight underestimation of raw reflectance values in the high-altitude flight, particularly for higher reflectance values (@fig-CompareRef A).
 Since both flights were conducted over vegetated areas, the highest reflectance values correspond to the infrared part of the spectrum.
@@
 
-Each drone flight was used to produce a prediction map, as well as a probability map that indicates the model derived probability of the selected class for every pixel.
+Each drone flight was used to produce a prediction map, as well as a probability map that indicates the model-derived probability of the selected class for every pixel.
 The low-altitude flight conducted in Gafanha, Portugal, represented the site with the highest complexity (@fig-GafLow).
 Among the five vegetation classes on which the model was trained, four were present on this site, with green and red macroalgae mixed with a seagrass meadow.
-There was also benthic diatoms forming biofilms on bare sediment surface.
-Although the seagrass was solely composed of a single specie, *Zostera noltei*, various colors of this specie could be observed from dark green (corresponding to healthy leaves) to brown (when leaves are senescent or have an altered pigment composition).
+There were also benthic diatoms biofilms on sediment surface.
+Although the seagrass was solely composed of a single species, *Zostera noltei*, two colors of this species could be observed: dark green (corresponding to healthy leaves) and brown (when leaves are senescent or have an altered pigment composition).
 Regardless of the variation of color, the class Magnoliopsida (seagrass) was accurately predicted by the model (F1 score of 0.96 at that site).
@@
 A channel contouring a small island was masked in the prediction map.
-Most of vegetation area was classified as seagrass by the model, including patches with discolored leaves.
+Most of the vegetation area was classified as seagrass by the model, including patches with brown leaves.
 Only a few pixels were classified as green macroalgae (F1 score of 0.55).
 Patches of red macroalgae were correctly classified (F1 score of 0.85).
-In the northern part of the site and near the land eadges, patches of the schorre angiosperm *Sporobolus maritimus* (syn.
+In the northern part of the site and near the land edges, patches of the schorre angiosperm *Sporobolus maritimus* (syn.
 *Spartina maritima)* were misclassified, either as seagrass or as brown algae (F1 score of 0.77 and 0.71, respectively).
@@
 #| warning: false
-#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high altitude flight of Gafanha, Portugal.
+#| fig-cap: RGB orthomosaic (Left) and Prediction (Right) of the high-altitude flight of Gafanha, Portugal.
 The total extent of this flight was about 1 km² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The yellow outline shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
+Background colors indicate the intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
+The red outline shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.

### 2024-11-14 docs/_tex/index.tex
add laurent's comments

--- 2024-11-12 docs/_tex/index.tex
@@
 Phaeophyceae (Brown algae), Rhodophyceae (Red macroalgae) and benthic
-Bacillariophyceae (Diatoms), and validated using concomitant field
-measurements. Classification of drone imagery resulted in an overall
-accuracy of 94\% across all sites and images, covering a total area of
-467 000 m². The model exhibited an accuracy of 96.4\% in identifying
-seagrass. In particular , seagrass and green algae can be discriminated.
-The very high spatial resolution of the drone data made it possible to
-assess the influence of spatial resolution on the classification
-outputs, showing a limited loss in seagrass detection up to about 10m.
-Altogether, out findings suggest that the Multi-Spectral Instrument
-(MSI) onboard Sentinel-2 offers a relevant trade-off between its spatial
-and spectral resolution, thus offering promising perspectives for
-satellite remote sensing of intertidal biodiversity over lager scales.
+Bacillariophyceae (Benthic diatoms), and validated using concomitant
+field measurements. Classification of drone imagery resulted in an
+overall accuracy of 94\% across all sites and images, covering a total
+area of 467 000 m². The model exhibited an accuracy of 96.4\% in
+identifying seagrass. In particular , seagrass and green algae can be
+discriminated. The very high spatial resolution of the drone data made
+it possible to assess the influence of spatial resolution on the
+classification outputs, showing a limited loss in seagrass detection up
+to about 10m. Altogether, out findings suggest that the Multi-Spectral
+Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between
+its spatial and spectral resolution, thus offering promising
+perspectives for satellite remote sensing of intertidal biodiversity
+over lager scales.
 \end{abstract}
@@
 \textbf{These studies have demonstrated the capability of drones to map
-intertidal habitats, including seagrasses; however, broader
+intertidal habitats, including seagrasses; however a broader
 generalization of these findings is still lacking. The current paper
@@
 learning algorithm was trained and validated for macrophyte
-discrimination, emphasizing applicability across diverse sites without a
-loss of prediction accuracy. The classification maps obtained at a very
+discrimination, emphasizing applicability across diverse sites without
+losing prediction accuracy. The classification maps obtained at a very
 high spatial resolution with the drone were spatially degraded to
@@
 resolution on the accuracy of drone-based macrophyte classification
-across a wide geographical scale, providing a framework for to better
+across a wide geographical scale, providing a framework to better
 understand satellite-based classification challenges.}
@@
 \caption{\label{fig-map}Location of drone flights in France and
-Portugal. A: Gulf of Morbihan (Two sites), B: Bourngeuf Bay (Two sites),
-C: Ria de Aveiro Coastal Lagoon (Three sites). Green areas represents
+Portugal. A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites),
+C: Ria de Aveiro Coastal Lagoon (Three sites). Brown areas represents
 the intertidal zone.}
@@
 million pixel reflectance photographs with ten spectral bands ranging
-from the blue to the near infrared (NIR): 444, 475, 531, 560, 650, 668,
+from the blue to the near-infrared (NIR): 444, 475, 531, 560, 650, 668,
 705, 717, 740 and 840 nm. To ensure consistent lighting conditions
@@
 different altitudes : 12 m or/and 120 m, with a spatial resolution of 8
-mm and 80 mm, respectively (Table~\ref{tbl-flights}). \textbf{Low
-altitude flights were used as training dataset for a neural network
-model while high altitude flight were used for validation.}
+mm and 80 mm, respectively (Table~\ref{tbl-flights}).
+\textbf{Low-altitude flights, with a spatial resolution of 8 mm, were
+used to build the training dataset for the neural network, as this high
+resolution allowed for precise photo-interpretation of vegetation
+classes. In contrast, high-altitude flights were used for validation
+purposes.}
 
@@
 
-\caption{\label{tbl-flights}List of drone flight, summarising the date,
+\caption{\label{tbl-flights}List of drone flights, summarising the date,
 the altitude, and the purpose of each flight. 12 m and 120 m flights
@@
 
-\includegraphics[width=6.63in,height=\textheight,keepaspectratio]{Figures/High_res/Table1/table_flights.png}
+\includegraphics[width=8.84in,height=\textheight,keepaspectratio]{Figures/High_res/Table1/table_flights.png}
 
@@
 and vertical accuracy of 10cm. A dGPS was also used to georeference
-quadrats of 0.25 m² ,which assessed the presence or absence of five key
-taxonomic classes of intertidal vegetation : Bacillariophyceae
-(unicellular benthic diatoms forming biofilms at the sediment surface
-during low tide, \textbf{ranging in size from small patches (m²) to
-entire mudflats (km²)}; henceforth: Diatoms), Phaeophyceae (henceforth:
-brown macroalgae), Magnoliopsida (henceforth: Seagrasses), Chlorophyceae
-(henceforth: Green macroalgae) and Rhodophyceae (henceforth: red
-macroalgae) (Figure~\ref{fig-vegetation}). Only homogeneous vegetation
-patches extending over several meters were selected as ground control
-points. Pictures of each quadrat were uploaded online to the open-portal
-Global Biodiversity Information Facility (GBIF) platform
+quadrats of 0.25 m², which assessed the presence or absence of five key
+taxonomic classes of intertidal vegetation: Bacillariophyceae
+\textbf{(benthic diatoms forming biofilms at the sediment surface during
+low tide with biofilm's size ranging from small patches (m²) to entire
+mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown
+macroalgae generally attached to rocks or other substrates able to form
+dense beds in the intertidal zone; henceforth: Brown macroalgae),
+Magnoliopsida (seagrasses, rooted flowering marine plants able to form
+extensive meadows on soft sediments; henceforth: Seagrasses),
+Chlorophyceae (green macroalgae, typically found attached to rocks or
+washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red
+macroalgae, attached to hard substrates but can also be found on
+soft-bottom substrate; henceforth: Red macroalgae)}. Only homogeneous
+vegetation patches extending over several meters were selected as ground
+control points. Pictures of each quadrat were uploaded online to the
+open-portal Global Biodiversity Information Facility (GBIF) platform
 \citep{BedeGbif}. Each photograph was also processed to estimate the
@@
 vermiculophylla}) ; D : Chlorophyceae (\emph{Ulva sp.}) ; E :
-Bacillariophyceae (Diatoms - MPB). \textbf{Classes were identified
-following the World register of Marine species.}}
+Bacillariophyceae (Benthic diatoms). \textbf{The taxonomy was chacked
+following the World Register of Marine Species (WORMS).}}
 
@@
 orthomosaicking was identical for every flight. First, key tying points
-were detected inside of each image and between overlapping images in
-order to obtain a sparse point cloud. This cloud was cleaned using a
-reprojection accuracy metric in order to remove noisy points. A dense
-point cloud was then produced using a structure from motion algorithm. A
-surface interpolation of this dense point cloud was made to obtain a
-digital surface model (DSM), used to reconstruct the multispectral
-ortho-image \citep{nebel2020review}. Low altitude drone flights produced
+were detected inside each image and between overlapping images in order
+to obtain a sparse point cloud. This cloud was cleaned using a
+reprojection accuracy metric to remove noisy points. A dense point cloud
+was then produced using a structure from motion algorithm. A surface
+interpolation of this dense point cloud was made to obtain a digital
+surface model (DSM), used to reconstruct the multispectral ortho-image
+\citep{nebel2020review}. Low-altitude drone flights produced
 ortho-images with a very high spatial resolution (8 mm per pixel),
 making it efficient to visually distinguish between the various types of
-vegetation. High altitude flights allowed to cover larger areas and
+vegetation. High-altitude flights allowed to cover larger areas and
 produced images with a pixel size of 80 mm (Table~\ref{tbl-flights}).
@@
 The spectral similarities of the reflectance signatures at the spectral
-resolution of the micasense senor between intertidal green macrophytes
+resolution of the Micasense senor between intertidal green macrophytes
 (Magnoliopsida and Chlorophyceae) make their discrimination challenging
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Figure3_workflow.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/High_res/Figure3_workflow.png}
 
@@
 divided into two distinct parts based on the spatial resolution of the
-drone flights: high-resolution flights (pixel size: 8 mm) were utilized
-for training and prediction of the Neural Network model, whereas
+drone flights: high-resolution flights (pixel size: 8 mm) were used for
+training and prediction of the Neural Network model, whereas
 lower-resolution flights (pixel size: 80 mm) were solely employed for
-prediction purposes. Validation has been performed on both high and low
-resolution flights.}
+prediction purposes. Validation has been performed on both high and
+low-resolution flights.}
 
@@
 categorized into seven different classes, representing the various
-habitats encountered at the different study sites: Sediment, Water,
-green macroalgae, seagrasses, diatoms, brown macroalgae and red
+habitats encountered at the different study sites: sediment, water,
+green macroalgae, seagrasses, Benthic diatoms, brown macroalgae and red
 macroalgae. Only data from the low-altitude flights
@@
 accurately identify vegetation classes. \textbf{In the field, seagrasses
-displaying two distinct colors, each with a unique spectral signature,
-were observed. Careful attention was given to incorporating training
-pixels from both color types into the training dataset for the seagrass
-class. This approach was consistently applied to all classes within the
-model.} More than 418,000 pixels at 8 mm resolution from the 3 training
-flights were used to train the model (Table~\ref{tbl-validationPX}).
-Twenty one variables were used by the model as predictors: the ten raw
-spectral bands of the Micasense RedEdge Dual MX multispectral camera
-(ranging from 444 nm to 840 nm), the same ten spectral bands
-standardized using a min/max transformation (Equation~\ref{eq-std} ;
-\citep{Cao2017}) and the Normalized difference vegetation index (NDVI,
-Equation~\ref{eq-ndvi}). Standardisation of spectral bands is commonly
-used to eliminate the scaling differences between spectra and to limit
-the effect of biomass on the spectra shape
+displayed two types of color were observed (i.e.~whereas most seagrass
+had green leaves, brownish leaves were also observed due to senescence
+or photo-degradaration). Careful attention was given to incorporating
+training pixels from both color types into the training dataset for the
+seagrass class. This approach was consistently applied to all classes
+within the model.} More than 418,000 pixels at 8 mm resolution from the
+3 training flights were used to train the model
+(Table~\ref{tbl-validationPX}). For model training, 21 variables were
+used as predictors: the ten raw spectral bands of the Micasense RedEdge
+Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same
+ten spectral bands standardized using a min/max transformation
+(Equation~\ref{eq-std} ; \citep{Cao2017}) and the Normalized difference
+vegetation index (NDVI, Equation~\ref{eq-ndvi}). Standardisation of
+spectral bands is commonly used to eliminate the scaling differences
+between spectra and to limit the effect of biomass on the spectra shape
 \citep{Douay2022, Davies2023}.
@@
 workflow \citep{howard2018fastai}. This model was composed of 2 hidden
-layers and have a total of 26 054 trainable parameters. Parameters have
-been fine tuned using 12 epoch to minimize the error rate. This model
+layers and has a total of 26 054 trainable parameters. Parameters have
+been fine-tuned using 12 epoch to minimize the error rate. This model
 has been called DISCOV, standing for Drone Intertidal Substrat
@@
 between reflectances at both heights is crucial. This comparison was
-conducted at sites where low and high altitude flights overlapped. The
-low altitude flights were resampled to the same spatial resolution and
-grid as the high flights using a median resampling method. Reflectance
-values were then extracted, and a scatterplot was generated and the Root
-Mean Square Error (RMSE) was computed to compare the difference bewteen
-the raw and standardised reflectance.
+conducted at sites where low and high-altitude flights overlapped. To
+compare reflectances of both flights, the low-altitude flights were
+resampled to the same spatial resolution and grid as the high-altitude
+flights using a median resampling method. Reflectance values were then
+extracted, and a scatterplot was generated. The Root Mean Square Error
+(RMSE) was computed to compare the difference between the raw and
+standardised reflectance.
 
@@
 predictors are important for predicting a specific class. Out of the 21
-predictors utilized in this study, Variable Importance was computed only
-for the raw and standardized values of the 10 spectral bands captured by
-the MicaSense camera. This is achieved by repeatedly predicting the same
+predictors used in this study, Variable Importance was computed only for
+the raw and standardized values of the 10 spectral bands captured by the
+MicaSense camera. This is achieved by repeatedly predicting the same
 dataset while randomly shuffling one predictor at a time. The benchmark
@@
 modelled as function of the interaction between pixel resolution and
-vegetation class (Diatoms, brown macroalgae, seagrass, green macroalgae
-and red macroalage). Sample vs fitted residuals and quartile-quartile
-graphics were assessed visually, to ensure assumption of the models used
-were met.
+vegetation class (Benthic diatoms, brown macroalgae, seagrass, green
+macroalgae and red macroalgae). Sample vs fitted residuals and
+quartile-quartile graphics were assessed visually, to ensure assumptions
+of the models used were met.
 
@@
 This plot provided a visual representation of the model's behavior in
-mixed vegetation scenarios. It helps to understand the minimum
+mixed vegetation scenarios. It helped to understand the minimum
 vegetation cover of a given class within a pixel necessary for the model
@@
 (12 and 120 m) to construct the neural network model. At the sites where
-the flights at both altitudes overlapped, reflectance was compared.
+the flights at both altitudes overlapped, the reflectance was compared.
 Overall there was a good agreement between the two altitudes (RMSE :
@@
 
-There was a slight underestimation for raw reflectance values in the
+There was a slight underestimation of raw reflectance values in the
 high-altitude flight, particularly for higher reflectance values
@@
 Each drone flight was used to produce a prediction map, as well as a
-probability map that indicates the model derived probability of the
+probability map that indicates the model-derived probability of the
 selected class for every pixel. The low-altitude flight conducted in
@@
 the model was trained, four were present on this site, with green and
-red macroalgae mixed with a seagrass meadow. There was also diatoms
-forming biofilms on bare sediment surface. Although the seagrass was
-solely composed of a single specie, \emph{Zostera noltei}, various
-colors of this specie could be observed from dark green (corresponding
-to healthy leaves) to brown (when leaves are senescent or have an
-altered pigment composition). Regardless of the variation of color, the
-class Magnoliopsida (seagrass) was accurately predicted by the model (F1
-score of 0.96 at that site).
+red macroalgae mixed with a seagrass meadow. There were also benthic
+diatoms biofilms on sediment surface. Although the seagrass was solely
+composed of a single species, \emph{Zostera noltei}, two colors of this
+species could be observed: dark green (corresponding to healthy leaves)
+and brown (when leaves are senescent or have an altered pigment
+composition). Regardless of the variation of color, the class
+Magnoliopsida (seagrass) was accurately predicted by the model (F1 score
+of 0.96 at that site).
 
@@
 of the low altitude flight of Gafanha, Portugal. The total extent of
-this flight was 3000 m² with a resolution of 8 mm per pixel. Background
-colors indicate intertidal area (Light Green) and land area (Light
-Grey). The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel
-size.}
+this flight was 3000 m² with a resolution of 8 mm per pixel. The zoom
+covers an area equivalent to a 10-meter Sentinel-2 pixel size.}
 
@@
 \textasciitilde1 km² (Figure~\ref{fig-GafHigh}). A channel contouring a
-small island was masked in the prediction map. Most of vegetation area
-was classified as seagrass by the model, including patches with
-discolored leaves. Only a few pixels were classified as green macroalgae
-(F1 score of 0.55). Patches of red macroalgae were correctly classified
-(F1 score of 0.85). In the northern part of the site and near the land
-eadges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
+small island was masked in the prediction map. Most of the vegetation
+area was classified as seagrass by the model, including patches with
+brown leaves. Only a few pixels were classified as green macroalgae (F1
+score of 0.55). Patches of red macroalgae were correctly classified (F1
+score of 0.85). In the northern part of the site and near the land
+edges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
 (syn. \emph{Spartina maritima)} were misclassified, either as seagrass
@@
 \caption{\label{fig-GafHigh}RGB orthomosaic (Left) and Prediction
-(Right) of the high altitude flight of Gafanha, Portugal. The total
+(Right) of the high-altitude flight of Gafanha, Portugal. The total
 extent of this flight was about 1 km² with a resolution of 80 mm per
-pixel. Background colors indicate intertidal area (Light Green), land
-area (Light Grey) and water (Light Blue). The yellow outline shows the
-extent of the low altitude flight of Gafanha presented in
-Figure~\ref{fig-GafLow}. The zoom covers an area equivalent to a
-10-meter Sentinel-2 pixel size.}
+pixel. The yellow outline shows the extent of the low-altitude flight of
+Gafanha presented in Figure~\ref{fig-GafLow}. The zoom covers an area
+equivalent to a 10-meter Sentinel-2 pixel size.}
 
@@
 Ria de Aveiro coastal lagoon covered the largest area with approximately
-1.5 km² (Figure~\ref{fig-Boat}). Teh vegetation present at the site was
+1.5 km² (Figure~\ref{fig-Boat}). The vegetation present at the site was
 dominated by seagrass and red macroalgae. The classification provided
@@
 The total extent of this flight was about 1.5 km² with a resolution of
-80 mm per pixel. Background colors indicate intertidal area (Light
-Green), land area (Light Grey) and water (Light Blue). The zoom inserts
-cover an area equivalent to the size of a 10-meter Sentinel-2 pixel.}
+80 mm per pixel. The zoom inserts cover an area equivalent to the size
+of a 10-meter Sentinel-2 pixel.}
 
@@
 of L'Epine, France. The total extent of this flight was about 28 000 m²
-with a resolution of 80 mm per pixel. Background colors indicate
-intertidal area (Light Green) and land area (Light Grey). The zoom
-covers an area equivalent to a 10-meter Sentinel-2 pixel size.}
+with a resolution of 80 mm per pixel. The zoom covers an area equivalent
+to a 10-meter Sentinel-2 pixel size.}
 
@@
 
-Clear differences were seen in vegetation loss across different
+Clear differences were seen in vegetation loss across spatial
 resolutions and vegetation classes (Figure~\ref{fig-pixelsize}). At a
 fine resolution of 1m, changes in the retrieved area for each vegetation
-type are minimal. Green algae shows the highest loss, with 1.2\% area
-lost compared to the native resolution (80 mm). As the resolution
+type are minimal. Green macroalgae show the highest loss, with 1.2\%
+area lost compared to the native resolution (80 mm). As the resolution
 coarsens to 10m, vegetation loss becomes more pronounced, with green
 macroalgae again experiencing the greatest reduction (12\% compared to
-8cm) and seagrass showing the smallest loss (1.3\%). At a resolution of
-30m, all green algae have been lost (100\% compared to 8cm), while
-seagrass experiences a relatively small reduction of 11\%. Brown
-macroalgae and red macroalgae show moderate declines, with losses at 30m
+8cm) and seagrass showing the smallest loss (1.3\%). All green
+macroalgae have been lost at a resolution of 30m (100\% compared to
+8cm), while seagrass experiences a relatively small reduction of 11\%.
+Brown and red macroalgae show lower declines, with losses at 30m
 resolution reaching approximately 37\% and 59\%, respectively.
@@
 
-Using the very high resolution low altitude flight (8 mm pixels), we
+Using the very high-resolution low-altitude flight (8 mm pixels), we
 determined the minimal percent cover required to correctly classify a
-given class within the corresponding high altitude flight (8cm pixel
+given class within the corresponding high-altitude flight (8cm pixel
 resolution ; Figure~\ref{fig-upscaling}).
@@
 A percent cover of at least 80\% was sufficient to have all the 80 mm
-pixels correctly classified, with the exception of Magnoliopsida that
+pixels correctly classified, with the exception of Magnoliopsida which
 required a higher cover (\textgreater90 \%) to be accurately classified.
@@
 cover of 93 \% was needed, 90 \% for seagrass, 92 \% for red macroalgae
-and 97 \% for diatoms When the vegetation cover of a given class was 100
-\%, coarser high-flight pixels were correctly classified for all the
-classes except for Bare Sediment, which was only correctly classified
-80\% of the time. This phenomenon may be attributed to the time gap
-between the two flights, allowing for microphytobenthos migration to the
-sediment surface during low tide, consequently altering the model's
-classification from bare sediment to Bacillariophyceae.
+and 97 \% for benthic diatoms When the vegetation cover of a given class
+was 100 \%, coarser high-flight pixels were correctly classified for all
+the classes except for Bare Sediment, which was only correctly
+classified 80\% of the time. This phenomenon may be attributed to the
+time gap between the two flights, allowing for microphytobenthos
+migration to the sediment surface during low tide, consequently altering
+the model's classification from bare sediment to Bacillariophyceae.
 
@@
 fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo:
-neoxanthin, PE: phycoerythrin, PC: phycocyanin
+neoxanthin, PE: phycoerythrin, PC: phycocyanin;
 \citetext{\citealp{ralph2002}; \citealp[
@@
 Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in
-this study, enabled the classifier to achieve 97\% of accuracy between
+this study, enabled the classifier to achieve 97\% accuracy between
 these two classes (Figure~\ref{fig-ValidationGreen}). Even if their
@@
 identify brown algae (Figure~\ref{fig-VIP}). Similarly, the presence of
-phycoerythrin and phycocyanin in Rhodophyceae contribute to the lowest
+phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest
 reflectance among all classes in the spectral range from 560 to 615 nm
@@
 (RMSE) of 0.02 (Figure~\ref{fig-CompareRef}). This result indicates that
-the reflectance measured by remote sensing (RS) sensors is not
-significantly influenced by pixel size. This finding is valuable for
-integrating drone-based data into larger-scale mapping projects (e.g.,
-combining satellite and drone mapping in side-by-side analyses). The
-consistency of reflectance across altitudes suggests that drones can be
-effectively used for finer-scale mapping without compromising data
-accuracy when merging with other platforms. However, it was observed
-that there is an underestimation of the infrared part of the spectra in
-the high-altitude dataset (Figure~\ref{fig-CompareRef}). Such disparity
-in infrared reflectance may stem from temporal differences between the
-flights, possibly resulting in a slightly drier intertidal area and
-consequently higher infrared reflectance. This disparity poses an issue
-for the methodology followed in the present study, relying solely on one
-flight height for training. To address this issue, we employed min/max
-standardized reflectance spectra as predictors for the model
-Equation~\ref{eq-std}. This approach allowed us to eliminate the slight
-reflectance difference between the flights (Figure~\ref{fig-CompareRef}
-B) and to focus on the shape of the spectra in the visible part of the
-electromagnetic spectra, where different pigmentation are associated to
-taxonomic diagnostic features. In contrast to subtidal seagrasses, which
-maintain a relatively constant biomass throughout the year, intertidal
-seagrasses, like the one studied in this work, exhibit strong seasonal
-phenology \citep{davies2024sentinel}. At some sites, they completely
-disappear during the winter and reach their peak above-ground biomass in
-the summer and early autumn. Along with these seasonal changes in
-biomass, the pigment composition and ratios also vary throughout the
-year, reflecting the plants' adaptations to different environmental
-conditions \citep{bargain2013seasonal, legare2022remote}.
-Standardization of spectral signatures helps to mitigate the impact of
-changing biomass on the spectral profile, enabling the development of a
-model that can reliably predict vegetation across different geographical
-locations and seasons. This approach allows for consistent
-classification of vegetation despite variations in biomass and
-fluctuations in light conditions, providing a robust tool for monitoring
-and predicting vegetation dynamics
-\citep{fyfe2003spatial, COSTA2021107018, piaser2023impact}. We found 90
-\% seagrass cover was necessary at an 8 cm resolution for confident
-prediction of its presence (Figure~\ref{fig-upscaling}). However, due to
-the strong phenology of intertidal seagrass meadows in Europe, the
+the reflectance measured by remote sensing (RS) sensors was not
+significantly influenced by pixel size for these two altitude. This
+finding is valuable for integrating drone-based data into larger-scale
+mapping projects (e.g., combining satellite and drone mapping in
+side-by-side analyses). The consistency of reflectance across altitudes
+suggests that drones can be effectively used for finer-scale mapping
+without compromising data accuracy when merging with other platforms.
+However, it was observed that there is an underestimation of the
+infrared part of the spectra in the high-altitude dataset
+(Figure~\ref{fig-CompareRef}). Such disparity in infrared reflectance
+may stem from temporal differences between the flights, possibly
+resulting in a slightly drier intertidal area and consequently higher
+infrared reflectance. This disparity poses an issue for the methodology
+followed in the present study, relying solely on one flight height for
+training. To address this issue, we employed min/max standardized
+reflectance spectra as predictors for the model Equation~\ref{eq-std}.
+This approach allowed us to eliminate the slight reflectance difference
+between the flights (Figure~\ref{fig-CompareRef} B) and to focus on the
+shape of the spectra in the visible domain (400 to 700 nm). At these
+wavelength different pigments are associated with taxonomic diagnostic
+features. In contrast to subtidal seagrasses, which maintain relatively
+constant biomass throughout the year, intertidal seagrasses, like the
+one studied in this work, exhibit strong seasonal phenology
+\citep{davies2024sentinel}. At some sites, they completely disappear
+during the winter and reach their peak above-ground biomass in the
+summer and early autumn. Along with these seasonal changes in biomass,
+the pigment composition and ratios also vary throughout the year,
+reflecting the plants' adaptations to different environmental conditions
+\citep{bargain2013seasonal, legare2022remote}. Standardization of
+spectral signatures helps to mitigate the impact of changing biomass on
+the spectral profile, enabling the development of a model that can
+reliably predict vegetation across different geographical locations and
+seasons. This approach allows for consistent classification of
+vegetation despite variations in biomass and fluctuations in light
+conditions, providing a robust tool for monitoring and predicting
+vegetation dynamics
+\citep{fyfe2003spatial, COSTA2021107018, piaser2023impact}. However, due
+to the strong phenology of intertidal seagrass meadows in Europe, the
 period when a meadow is well-established can be temporally restricted,
@@
 Pixel resolution plays a critical role in accuratly retrieving
-vegetation area from remote sensing data. As pixel size increases, we
-found a consistent decline in area retrieval is observed across all
-vegetation types, with more pronounced effects for certain types, such
-as green algae (Figure~\ref{fig-pixelsize}). This highlights the
-sensitivity of spatial resolution in detecting smaller or more
-fragmented vegetation features. Green algae, being particularly patchy
-across all study sites, shows the steepest decline in areal agreement as
-pixel size increases, which aligns with expectations given the
-limitations of coarser resolution in capturing fine-scale details.
+vegetation areas from remote sensing data. As pixel size increases, we
+found a consistent decline in area retrieval across all vegetation
+types, with more pronounced effects for certain types, such as green
+algae (Figure~\ref{fig-pixelsize}). This highlights the sensitivity of
+spatial resolution in detecting smaller or more fragmented vegetation
+features. Green algae, being particularly patchy across all study sites,
+showed the steepest decline in areal agreement as pixel size increases,
+which aligns with expectations given the limitations of coarser
+resolution in capturing fine-scale details.
 
@@
 monitoring, they may be too coarse to capture finer-scale heterogeneity,
-particularly in fragmented vegetation like green algae. Our findings
+as it was observed with green macroalgae in this study. Our findings
 suggest that, while the 30m resolution of Landsat may be adequate for
@@
 restoration efforts, particularly in ecologically sensitive coastal
-zones, as early stages of green tides could be challenging to monitor at
-coarse resolutions.
+zones, as the early stages of green tides could be challenging to detect
+at coarse resolutions.
 
@@
 monitoring of homogeneous vegetation types, 10 m resolution of S2/MSI or
-even the 30 m of Landsat/OLI are often sufficient. However, when mapping
-fragmented vegetation like green algae, the precision provided by
-higher-resolution imagery is crucial, despite the additional costs and
-processing challenges it imposes.
+even the 30 m of Landsat/OLI is often sufficient. However, when mapping
+vegetation like macroalgae with an heterogeneous distribution, the
+precision provided by higher-resolution imagery is crucial, despite the
+additional costs and processing challenges it imposes.
 
@@
 highlight the potential of drone-based remote sensing to support diverse
-applications, from conservation of biodiversity to climate change
+applications, from the conservation of biodiversity to climate change
 adaptation strategies.
@@
 \citep{villares1999nitrogen, ye2011green}. The first green tide events
-(i.e.~bloom of green macroalgae of the genus \emph{Ulva}) were reported
-in Brittany, France, in the 1970s and have since been a concern for
-local stakeholders and economic activities \citep{menesguen2018marees}.
-Some regions of the world have witnessed an increase in brown macroalgae
-blooms, predominantly involving algae of the genus \emph{Sargassum}
-washing along the Caribbean coastlines \citep{louime2017sargassum}, and
-more recently \emph{Rugulopteryx okamurea} in southern Europe
-\citep{Roca2022}. Satellite remote sensing has proven to be a valuable
-tool for mapping the spatial and temporal extent of macroalgal blooms
-worldwide. However, due to limitations in spatial resolution, it can
-only effectively map well-developed blooms
+(\emph{i.e.} bloom of green macroalgae of the genus \emph{Ulva}) were
+reported in Brittany, France, in the 1970s and have since been a concern
+for local stakeholders and economic activities
+\citep{menesguen2018marees}. Some regions of the world have witnessed an
+increase in brown macroalgae blooms, predominantly involving algae of
+the genus \emph{Sargassum} washing along the Caribbean coastlines
+\citep{louime2017sargassum}, and more recently \emph{Rugulopteryx
+okamurea} in southern Europe \citep{Roca2022}. Satellite remote sensing
+has proven to be a valuable tool for mapping the spatial and temporal
+extent of macroalgal blooms worldwide. However, due to limitations in
+spatial resolution, it can only effectively map well-developed blooms
 \citep{rs13081408, klemas2012remote, haro2023biointertidal}. High
-spatial resolution drone imagery, coupled with accurate classification
-algorithm, could be used to map the early stages of macroalgal blooms in
-areas known to have regular blooms or in new sites. Indeed, this
-approach could provide early warning alerts to local managers and
-complimentary to traditional sampling methods to monitor coastal
-ecosystems. These methods are generally time and resource-intensive, and
-the findings are often difficult to scale-up when applied alone. Earth
-Observation can bridge this gap and meet the needs for systematic
-monitoring of coastal ecosystems over large areas
+spatial resolution drone imagery, coupled with an accurate
+classification algorithm, could be used to map the early stages of
+macroalgal blooms in areas known to have regular blooms or in new sites.
+Indeed, this approach could provide early warning alerts to local
+managers and complimentary to traditional sampling methods to monitor
+coastal ecosystems. These methods are generally time and
+resource-intensive, and the findings are often difficult to scale up
+when applied alone. Earth Observation can bridge this gap and meet the
+need for systematic monitoring of coastal ecosystems over large areas
 \citep{papathanasopoulou2019satellite}. The retrieval of Essential
@@
 ecosystems. On-demand, multispectral drone observations at very high
-spatial-resolution provide a novel and powerful tool to rapidly and
-accurately acquire ground truth data which can be used to develop
+spatial resolution provide a novel and powerful tool to rapidly and
+accurately acquire ground truth data, which can be used to develop
 machine-learning algorithm for satellite sensors
@@
 areas. The integration of drone technology facilitates a scalable
-approach to environmental surveillance while taking into account
-patchiness of secondary vegetation, offering significant advancements in
-the spatial and temporal resolution of data collection. This, in turn,
+approach to environmental surveillance while taking into account the
+patchiness of vegetation, offering significant advancements in the
+spatial and temporal resolution of data collection. This, in turn,
 supports the EU WFD's objectives by enabling more informed and timely
@@
 identify the former, notably 650, 560, 668, and 705 nm. As the spectral
-bands of the Micasense RedEdge Dual MX are very similar to those of
+bands of the Micasense RedEdge Dual sensor are very similar to those of
 Sentinel-2/MSI, we suggest that multispectral satellite data have the

### 2024-11-14 index.qmd
add laurent's comments

@@
 }else{
-  ggsave("Figures/Figure3_workflow.png",a, width = 1920, height = 1129, units = "px")
+  ggsave("Figures/High_res/Figure3_workflow.png",a, width = 1920, height = 1129, units = "px")
 }
@@
 
-knitr::include_graphics("./Figures/Figure3_workflow.png")
+knitr::include_graphics("./Figures/High_res/Figure3_workflow.png")
 
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#7DC27D", "#BDBDBD"))+
+                    values = c("#70543e", "#BDBDBD"))+
   geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
@@
    theme_Bede_Map()+
-   geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+   geom_sf(data = zoom_extent, fill = "transparent", colour = "red2",linetype = "dashed", linewidth = 1.5)+
    coord_sf(crs = 4326)+
@@
 rgb_Gafanha_low<- ggplot()+
-  scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="grey30")+
+  # scale_fill_manual("", 
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_GafHigh,
+  #         fill = "white",
+  #         show.legend = F,
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="white")+
+  # geom_sf(data = background_GafHigh,
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="grey30")+
    tidyterra::geom_spatraster_rgb(data = Gafanha_low_ortho,
@@
          maxcell = 4010533
+         # maxcell = 10000
+
          )+
@@
            fill = "transparent",
-           colour = "black",
+           colour = "red2",
            linetype = "dashed", 
-           linewidth = 1)+
+           linewidth = 1.5)+
    coord_sf(crs = 4326)+
@@
                               grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
+            linetype = "dashed", linewidth = 1.5, color = "red2")+
   theme(axis.title = element_blank(),
@@
     scale_y_continuous(limits = c(40.59715, 40.5979), breaks = 40.5975)
+
+# rgb_Gafanha_low
 
@@
   tidyterra::geom_spatraster(data = Gafanha_low_pred_zoomed, mapping = aes(fill = layer))+
-  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+  geom_sf(data = zoom_extent, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1.5)+
   coord_sf(crs = 4326)+
@@
   ggplot()+
-  scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="grey30")+
+  # scale_fill_manual("", 
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("white", "white","white"))+
+  # geom_sf(data = background_GafHigh,
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="grey30")+
   # geom_sf(data = background_GafHigh,
@@
           linetype = "dashed", 
-          linewidth = 1)+
+          linewidth = 1.5)+
   coord_sf(crs = 4326)+
@@
                               grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
+            linetype = "dashed", linewidth = 1.5)+
   scale_fill_manual(breaks = c(1,2,5,6,7,8,10),
@@
 The total extent of this flight was 3000 m² with a resolution of 8 mm per pixel.
-Background colors indicate intertidal area (Light Green) and land area (Light Grey).
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
          b = 3)+
-     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "red",linetype = "dashed", linewidth = 1.5)+
   theme_void()
@@
 rgb_Gafanha_High <- ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_GafHigh,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
+  # scale_fill_manual("",  
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_GafHigh,
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="grey30")+
+  # geom_sf(data = background_GafHigh,
+  #         fill = "white",
+  #         show.legend = F,
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="white")+
    tidyterra::geom_spatraster_rgb(data = GafHigh_ortho_masked,
@@
          b = 3,
-         maxcell = 5007120)+
+         maxcell = 5007120
+        # maxcell = 100000
+
+         )+
     ggspatial::annotation_scale(location = "bl",
@@
             fill = "transparent", 
-            colour = "black",
-            linetype = "dashed", 
-            linewidth = 1)+
+            colour = "red",
+            linetype = 1, 
+            linewidth = 1.5)+
     geom_sf(data = Gaflow_extent,
             fill = "transparent", 
-            colour = "red",
-            linetype = "dashed", 
-            linewidth = 2)+
+            colour = "yellow",
+            linetype = 1, 
+            linewidth = 1)+
     geom_path(aes(x,y,group=grp),
@@
             linetype = "dashed", 
-            linewidth = 1)+
+            linewidth = 1.5,
+            color = "red")+
   annotation_custom(ggplotGrob(rgb_Gafanha_High_zoomed),
@@
                                "Water"))+
-     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "black",linetype = "dashed", linewidth = 1)+
+     geom_sf(data = zoom_gaf_high_sf, fill = "transparent", colour = "red",linetype = "dashed", linewidth = 1.5)+
   theme_void()
@@
 Gafanha_high_pred_map<-ggplot()+
-  geom_sf(data = background_GafHigh, 
-          mapping = aes(fill = Type),
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_GafHigh,
-          fill = "white",
-          show.legend = F,
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-    scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_GafHigh, 
+  #         mapping = aes(fill = Type),
+  #         show.legend = F,
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="grey30")+
+  # geom_sf(data = background_GafHigh,
+  #         fill = "white",
+  #         show.legend = F,
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="white")+
+  #   scale_fill_manual("", 
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
   ggnewscale::new_scale("fill")+
@@
                fill = "transparent", 
-               colour = "black",
-               linetype = "dashed", 
-               linewidth = 1)+
+               colour = "red",
+               linetype = 1, 
+               linewidth = 1.5)+
     geom_sf(data = Gaflow_extent,
             fill = "transparent", 
-            colour = "red",
-            linetype = "dashed", 
-            linewidth = 2)+
+            colour = "yellow",
+            linetype = 1, 
+            linewidth = 1)+
   geom_path(aes(x,y,group=grp),
@@
                               grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
+            linetype = "dashed", linewidth = 1.5, color = "red")+
   annotation_custom(ggplotGrob(Gafanha_High_zoomed_pred), 
@@
 The total extent of this flight was about 1 km² with a resolution of 80 mm per pixel.
-Background colors indicate the intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
-The red outline shows the extent of the low altitude flight of Gafanha presented in @fig-GafLow.
+The yellow outline shows the extent of the low-altitude flight of Gafanha presented in @fig-GafLow.
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size.
@@
 Among the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat).
-Teh vegetation present at the site was dominated by seagrass and red macroalgae.
+The vegetation present at the site was dominated by seagrass and red macroalgae.
 The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site.
@@
                       max_col_value = 4000)+
-  geom_sf(data = zoom_boat_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1.5)+
 
@@
                       max_col_value = 4000)+
-  geom_sf(data = zoom_boat_high_sf_2, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  geom_sf(data = zoom_boat_high_sf_2, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1.5)+
 
@@
 ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_Boat,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Boat,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
+  # scale_fill_manual("",  
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_Boat,
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="transparent")+
+  # geom_sf(data = background_Boat,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="transparent")+
   tidyterra::geom_spatraster_rgb(data = Boat_rgb_mask,
@@
           colour = "black", 
-          linewidth = 1)+
+          linewidth = 1.5)+
   geom_sf(data = zoom_boat_high_sf_2,
@@
           colour = "black", 
-          linewidth = 1)+
+          linewidth = 1.5)+
   annotation_custom(ggplotGrob(rgb_Boat_zoomed_map),
@@
             linetype = "dashed", 
-            linewidth = 1)+
+            linewidth = 1.5)+
     geom_path(aes(x,y,group=grp),
@@
             linetype = "dashed", 
-            linewidth = 1)+
+            linewidth = 1.5)+
   ggspatial::annotation_scale(location = "bl",
@@
           colour = "black", 
-          linewidth = 1)+
+          linewidth = 1.5)+
   theme_void()
@@
 Boat_pred_map<-ggplot()+
-  geom_sf(data = background_Boat, 
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Boat,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
-    scale_fill_manual("", 
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_Boat, 
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="transparent")+
+  # geom_sf(data = background_Boat,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="transparent")+
+  #   scale_fill_manual("", 
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
   ggnewscale::new_scale("fill")+
@@
                linetype = "dashed", 
-               linewidth = 1)+
+               linewidth = 1.5)+
   geom_sf(data = zoom_boat_high_sf_2, 
@@
                linetype = "dashed", 
-               linewidth = 1)+
+               linewidth = 1.5)+
   geom_path(aes(x,y,group=grp),
@@
             linetype = "dashed", 
-            linewidth = 1)+
+            linewidth = 1.5)+
   geom_path(aes(x,y,group=grp),
@@
             linetype = "dashed", 
-            linewidth = 1)+
+            linewidth = 1.5)+
   annotation_custom(ggplotGrob(Boat_Pred_zoomed_map),
@@
 The total extent of this flight was about 1.5 km² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green), land area (Light Grey) and water (Light Blue).
 The zoom inserts cover an area equivalent to the size of a 10-meter Sentinel-2 pixel.
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
-                    values = c("#7DC27D", "#BDBDBD"))+
+                    values = c("#70543e", "#BDBDBD"))+
   geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
@@
                       b = 1)+
-  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "red", linewidth = 1.5)+
   coord_sf(crs = 32630)+
@@
 RGB_Dike_map <- ggplot()+
-  scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
-  geom_sf(data = background_Dike,
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="transparent")+
-  geom_sf(data = background_Dike,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="transparent")+
+  # scale_fill_manual("",  
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_Dike,
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="transparent")+
+  # geom_sf(data = background_Dike,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="transparent")+
   tidyterra::geom_spatraster_rgb(data = Dike_rgb_masked,
@@
           linetype = "dashed",
-          colour = "black", 
-          linewidth = 1)+
+          colour = "red", 
+          linewidth = 1.5)+
   annotation_custom(ggplotGrob(zoom_rgb_dike_map), 
@@
                               grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
+            linetype = "dashed", linewidth = 1.5, color = "red")+
   ggspatial::annotation_scale(location = "tl",text_cex=2)+
@@
                                "Water"))+
-  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1)+
+  geom_sf(data = zoom_Dike_high_sf, fill = "transparent", linetype = "dashed",colour = "black", linewidth = 1.5)+
   theme_void()
@@
 Dike_pred_map<-ggplot()+
-  geom_sf(data = background_Dike, 
-          mapping = aes(fill = Type),
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.93,
-          colour="grey30")+
-  geom_sf(data = background_Dike,
-          fill = "white",
-          show.legend = F, 
-          linewidth=0.05,
-          alpha=0.4,
-          colour="white")+
-    scale_fill_manual("",  
-                    labels = c("Intertidal area", "Land area", "water"),
-                    values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
+  # geom_sf(data = background_Dike, 
+  #         mapping = aes(fill = Type),
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.93,
+  #         colour="grey30")+
+  # geom_sf(data = background_Dike,
+  #         fill = "white",
+  #         show.legend = F, 
+  #         linewidth=0.05,
+  #         alpha=0.4,
+  #         colour="white")+
+  #   scale_fill_manual("",  
+  #                   labels = c("Intertidal area", "Land area", "water"),
+  #                   values = c("#7DC27D", "#CFCFCF","#42c9bc"))+
   ggnewscale::new_scale("fill")+
@@
           linetype = "dashed", 
-          linewidth = 1)+
+          linewidth = 1.5)+
   annotation_custom(ggplotGrob(zoom_Pred_dike_map), 
@@
                               grp=c(1,1,2,2)),
-            linetype = "dashed", linewidth = 1)+
+            linetype = "dashed", linewidth = 1.5)+
   # annotation_custom(ggplotGrob(Boat_Pred_zoomed_map), xmin = -8.697, xmax = -8.692, ymin = 40.667,ymax = 40.6705) +
@@
 The total extent of this flight was about 28 000 m² with a resolution of 80 mm per pixel.
-Background colors indicate intertidal area (Light Green) and land area (Light Grey).
 The zoom covers an area equivalent to a 10-meter Sentinel-2 pixel size."
@@
 
-glm_res_true <- glm(loss ~ res*class_fct , data = df_area_compare, family=quasi(link="logit", variance="mu(1-mu)"))
+glm_res_true <- glm(loss ~ area*class_fct , data = df_area_compare, family=quasi(link="logit", variance="mu(1-mu)"))
 # glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))
@@
       )
-
 ```
 
-Clear differences were seen in vegetation loss across different resolutions and vegetation classes (@fig-pixelsize).
+Clear differences were seen in vegetation loss across spatial resolutions and vegetation classes (@fig-pixelsize).
 At a fine resolution of 1m, changes in the retrieved area for each vegetation type are minimal.
-Green algae shows the highest loss, with 1.2% area lost compared to the native resolution (80 mm).
+Green macroalgae show the highest loss, with 1.2% area lost compared to the native resolution (80 mm).
 As the resolution coarsens to 10m, vegetation loss becomes more pronounced, with green macroalgae again experiencing the greatest reduction (12% compared to 8cm) and seagrass showing the smallest loss (1.3%).
-At a resolution of 30m, all green algae have been lost (100% compared to 8cm), while seagrass experiences a relatively small reduction of 11%.
-Brown macroalgae and red macroalgae show moderate declines, with losses at 30m resolution reaching approximately 37% and 59%, respectively.
+All green macroalgae have been lost at a resolution of 30m (100% compared to 8cm), while seagrass experiences a relatively small reduction of 11%.
+Brown and red macroalgae show lower declines, with losses at 30m resolution reaching approximately 37% and 59%, respectively.
 
@@
   scale_fill_manual(values=c("gray85","#70543e"))+
+      scale_y_continuous(expand = c(0, 0))+
+
   # scale_alpha_manual(values = c(0.5,1))+
@@
   scale_fill_manual(values=c("gray85", "#b3ff1a"))+
+    scale_y_continuous(position = "right",
+                       expand = c(0, 0))+
+
   # scale_alpha_manual(values = c(0.5,1))+
@@
   geom_vline(xintercept = (lm_green$coefficients[[2]]*85+lm_green$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
-  ggtitle("Green Algae")+
+  ggtitle("Chlorophyceae")+
   # annotate(geom="text",x = lm_green$coefficients[[2]]*0.85+lm_green$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
@@
   scale_fill_manual(values=c("gray85","#389350"))+
+    scale_y_continuous(expand = c(0, 0))+
+
   # scale_alpha_manual(values = c(0.5,1))+
@@
   scale_fill_manual(values=c("gray85","#DAA520"))+
+    scale_y_continuous(expand = c(0, 0))+
   # scale_alpha_manual(values = c(0.5,1))+
@@
   geom_vline(xintercept = (lm_MPB$coefficients[[2]]*85+lm_MPB$coefficients[[1]])*100, linetype = "dashed",linewidth = 2)+
-  ggtitle("Microphytobenthos")+
+  ggtitle("Bacillariophyceae")+
   # annotate(geom="text",x = lm_MPB$coefficients[[2]]*0.85+lm_MPB$coefficients[[1]]+0.05, y = 0.85, label = "p = 0.85", angle = - 90, size = 7)+
@@
   ggplot()+
-  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,position = "fill",adjust = 3)+
+  geom_density(mapping = aes(x = Proportion , y = after_stat(ndensity) , fill = Class),alpha = 0.8,position = "fill",adjust = 3, show.legend = F)+
   # facet_wrap(~ True)+
@@
                     drop = F)+
+  scale_y_continuous(position = "right",
+                     expand = c(0, 0))+
   # scale_alpha_manual(values = c(0.5,1))+
@@
   patchwork::plot_layout(guides = "collect") &
-  theme(legend.position = "bottom",
+  theme(
         plot.title = element_text(size=25, hjust = 0.55),
@@
   scale_x_continuous(breaks = c(25,50,75,100),limits= c(0,100.01),expand = c(0, 0)) &
-  scale_y_continuous(expand = c(0, 0)) &
+  # scale_y_continuous(expand = c(0, 0)) &
   xlab("Percent Cover (%)") & 
@@
 
-ggsave("Figures/Upscaling/density_vs_Proportion.png",plot , width = 833*4, height = 1118*4, units = "px")
+ggsave("Figures/High_res/Upscaling/density_vs_Proportion.png",plot , width = 833*4, height = 1118*4, units = "px")
 
@@
 
-Using the very high resolution low altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high altitude flight (8cm pixel resolution ; @fig-upscaling).
+Using the very high-resolution low-altitude flight (8 mm pixels), we determined the minimal percent cover required to correctly classify a given class within the corresponding high-altitude flight (8cm pixel resolution ; @fig-upscaling).
 
@@
 
-A percent cover of at least 80% was sufficient to have all the 80 mm pixels correctly classified, with the exception of Magnoliopsida that required a higher cover (>90 %) to be accurately classified.
+A percent cover of at least 80% was sufficient to have all the 80 mm pixels correctly classified, with the exception of Magnoliopsida which required a higher cover (>90 %) to be accurately classified.
 Concerning the probability of each class, there is a linear relationship between the percent cover and the confidence of the model to predict the class.
@@
 #| fig-cap: >
-#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin [@ralph2002 ; @Douay2022 @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
+#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin; [@ralph2002 ; @Douay2022 @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
 #| label: fig-Pigm
@@
 ::: column
-Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in this study, enabled the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% of accuracy between these two classes (@fig-ValidationGreen).
+Meeting these two criteria, the Micasense RedEdge-MX DUAL camera used in this study, enabled the classifier to achieve `r round(validation_metrics_green$overall[[1]],2)*100`% accuracy between these two classes (@fig-ValidationGreen).
 Even if their pigment composition is similar, differences in the spectral shape can be observed, with green algae having a higher reflectance peak at 560 nm as well as a higher NIR plateau than seagrass (@fig-vegetation).
@@
 These two key features have been identified by the Neural Network as the two principal predictors to accurately identify brown algae (@fig-VIP).
-Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contribute to the lowest reflectance among all classes in the spectral range from 560 to 615 nm (@fig-VIP).
+Similarly, the presence of phycoerythrin and phycocyanin in Rhodophyceae contributes to the lowest reflectance among all classes in the spectral range from 560 to 615 nm (@fig-VIP).
 Indeed the band at 560 nm has been identified as important for identifying this class, likely due to phycoerythrin absorption at this wavelength.
@@
 While comparing the reflectance at two different altitudes (12 m and 120 m with a spatial resolution of 8 and 80 mm, respectively), a nearly one-to-one relationship was observed, with a Root Mean Square Error (RMSE) of 0.02 (@fig-CompareRef).
-This result indicates that the reflectance measured by remote sensing (RS) sensors is not significantly influenced by pixel size.
+This result indicates that the reflectance measured by remote sensing (RS) sensors was not significantly influenced by pixel size for these two altitude.
 This finding is valuable for integrating drone-based data into larger-scale mapping projects (e.g., combining satellite and drone mapping in side-by-side analyses).
@@
 To address this issue, we employed min/max standardized reflectance spectra as predictors for the model [@eq-std ; @Cao2017].
-This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic diagnostic features.
-In contrast to subtidal seagrasses, which maintain a relatively constant biomass throughout the year, intertidal seagrasses, like the one studied in this work, exhibit strong seasonal phenology [@davies2024sentinel].
+This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible domain (400 to 700 nm).
+At these wavelength different pigments are associated with taxonomic diagnostic features.
+In contrast to subtidal seagrasses, which maintain relatively constant biomass throughout the year, intertidal seagrasses, like the one studied in this work, exhibit strong seasonal phenology [@davies2024sentinel].
 At some sites, they completely disappear during the winter and reach their peak above-ground biomass in the summer and early autumn.
@@
 This approach allows for consistent classification of vegetation despite variations in biomass and fluctuations in light conditions, providing a robust tool for monitoring and predicting vegetation dynamics [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
-We found `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % seagrass cover was necessary at an 8 cm resolution for confident prediction of its presence (@fig-upscaling).
 However, due to the strong phenology of intertidal seagrass meadows in Europe, the period when a meadow is well-established can be temporally restricted, limiting the ideal window for accurate detection.
@@
 
-Pixel resolution plays a critical role in accuratly retrieving vegetation area from remote sensing data.
-As pixel size increases, we found a consistent decline in area retrieval is observed across all vegetation types, with more pronounced effects for certain types, such as green algae (@fig-pixelsize).
+Pixel resolution plays a critical role in accuratly retrieving vegetation areas from remote sensing data.
+As pixel size increases, we found a consistent decline in area retrieval across all vegetation types, with more pronounced effects for certain types, such as green algae (@fig-pixelsize).
 This highlights the sensitivity of spatial resolution in detecting smaller or more fragmented vegetation features.
-Green algae, being particularly patchy across all study sites, shows the steepest decline in areal agreement as pixel size increases, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
+Green algae, being particularly patchy across all study sites, showed the steepest decline in areal agreement as pixel size increases, which aligns with expectations given the limitations of coarser resolution in capturing fine-scale details.
 
@@
 Both satellites offer high-resolution imagery, with pixel sizes of 10m and 30m, respectively.
-While these resolutions are suitable for broad-scale environmental monitoring, they may be too coarse to capture finer-scale heterogeneity, particularly in fragmented vegetation like green algae.
+While these resolutions are suitable for broad-scale environmental monitoring, they may be too coarse to capture finer-scale heterogeneity, as it was observed with green macroalgae in this study.
 Our findings suggest that, while the 30m resolution of Landsat may be adequate for homogeneous vegetation types, such as seagrass, a higher resolution is essential for accurately mapping patchy vegetation like green algae.
 These findings have direct implications for environmental management and conservation planning.
-Overlooking fine-scale vegetation features, such as those seen in green algae, could result in inadequate protection or restoration efforts, particularly in ecologically sensitive coastal zones, as early stages of green tides could be challenging to monitor at coarse resolutions.
+Overlooking fine-scale vegetation features, such as those seen in green algae, could result in inadequate protection or restoration efforts, particularly in ecologically sensitive coastal zones, as the early stages of green tides could be challenging to detect at coarse resolutions.
 
@@
 Consequently, high-resolution data requires more storage and can slow down real-time applications.
-For large-scale monitoring of homogeneous vegetation types, 10 m resolution of S2/MSI or even the 30 m of Landsat/OLI are often sufficient.
-However, when mapping fragmented vegetation like green algae, the precision provided by higher-resolution imagery is crucial, despite the additional costs and processing challenges it imposes.
+For large-scale monitoring of homogeneous vegetation types, 10 m resolution of S2/MSI or even the 30 m of Landsat/OLI is often sufficient.
+However, when mapping vegetation like macroalgae with an heterogeneous distribution, the precision provided by higher-resolution imagery is crucial, despite the additional costs and processing challenges it imposes.
 
@@
 Climate change, global warming, eutrophication, alien and invasive species development, coastal erosion, and sea level rise are expected to continue impacting coastal ecosystems in the future [@SCHIBALSKI2022101414 ; @holon2018predictive ; @marquet2024global] and the demand for meaningful and efficient monitoring of coastal habitats has never been higher[@muller2018satellite ; @villalobos2023remote ; @oiry2021using].
-Our findings, particularly the improved discrimination of intertidal seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from conservation of biodiversity to climate change adaptation strategies.
+Our findings, particularly the improved discrimination of intertidal seagrass and green macroalgae from other intertidal vegetation classes, highlight the potential of drone-based remote sensing to support diverse applications, from the conservation of biodiversity to climate change adaptation strategies.
 
@@
 These blooms can have negative impacts on human health and local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green].
-The first green tide events (i.e.
-bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, in the 1970s and have since been a concern for local stakeholders and economic activities [@menesguen2018marees].
+The first green tide events (*i.e.* bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, in the 1970s and have since been a concern for local stakeholders and economic activities [@menesguen2018marees].
 Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* washing along the Caribbean coastlines [@louime2017sargassum], and more recently *Rugulopteryx okamurea* in southern Europe [@Roca2022].
@@
 However, due to limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote ; @haro2023biointertidal].
-High spatial resolution drone imagery, coupled with accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
+High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be used to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites.
 Indeed, this approach could provide early warning alerts to local managers and complimentary to traditional sampling methods to monitor coastal ecosystems.
-These methods are generally time and resource-intensive, and the findings are often difficult to scale-up when applied alone.
-Earth Observation can bridge this gap and meet the needs for systematic monitoring of coastal ecosystems over large areas [@papathanasopoulou2019satellite].
+These methods are generally time and resource-intensive, and the findings are often difficult to scale up when applied alone.
+Earth Observation can bridge this gap and meet the need for systematic monitoring of coastal ecosystems over large areas [@papathanasopoulou2019satellite].
 The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations has been increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @Zoffoli2021].
@@
 Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on coastal ecosystems.
-On-demand, multispectral drone observations at very high spatial-resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth data which can be used to develop machine-learning algorithm for satellite sensors [@davies2024intertidal].
+On-demand, multispectral drone observations at very high spatial resolution provide a novel and powerful tool to rapidly and accurately acquire ground truth data, which can be used to develop machine-learning algorithm for satellite sensors [@davies2024intertidal].
 Spatially resolved data are indeed critical for calibrating and validating satellite remote sensing observations, thereby enhancing our capacity to monitor vast coastal areas.
-The integration of drone technology facilitates a scalable approach to environmental surveillance while taking into account patchiness of secondary vegetation, offering significant advancements in the spatial and temporal resolution of data collection.
+The integration of drone technology facilitates a scalable approach to environmental surveillance while taking into account the patchiness of vegetation, offering significant advancements in the spatial and temporal resolution of data collection.
 This, in turn, supports the EU WFD's objectives by enabling more informed and timely management decisions for the conservation and restoration of aquatic ecosystems.
@@
 The latter was essentially identified with the 451 nm spectral band while more spectral bands were needed to identify the former, notably 650, 560, 668, and 705 nm.
-As the spectral bands of the Micasense RedEdge Dual MX are very similar to those of Sentinel-2/MSI, we suggest that multispectral satellite data have the potential to perform this discrimination between these green macrophytes.
+As the spectral bands of the Micasense RedEdge Dual sensor are very similar to those of Sentinel-2/MSI, we suggest that multispectral satellite data have the potential to perform this discrimination between these green macrophytes.
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.

### 2024-11-14 index.qmd
add Laurent's comments

@@
 #| fig-cap: >
-#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin; [@ralph2002 ; @Douay2022 @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
+#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin; [@ralph2002 ; @Douay2022 ; @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
 #| label: fig-Pigm

### 2024-11-14 index.qmd
add Laurent's comments

@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#70543e", "#CFCFCF"))+
+                    values = c("goldenrod", "#CFCFCF"))+
   geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#70543e", "#CFCFCF"))+
+                    values = c("goldenrod", "#CFCFCF"))+
   geom_sf(data = mask_BB, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
-                    values = c("#70543e", "#CFCFCF"))+
+                    values = c("goldenrod", "#CFCFCF"))+
   geom_sf(data = mask_Morb, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
@@
 
-shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
-  list.files(pattern = ".shp", recursive = T, full.names = T) %>%
-  read_sf() %>%
-  mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
-                        name == "ZOS" ~ 2,
-                        name == "BL" ~ 3,
-                        name == "SED" ~ 4,
-                        name == "GRE" ~ 5,
-                        name == "RED" ~ 6,
-                        name == "Xanthophyceae" ~ 7)) %>% 
-  as("Spatial") %>% 
-  vect()
+# shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
+#   list.files(pattern = ".shp", recursive = T, full.names = T) %>%
+#   read_sf() %>%
+#   mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
+#                         name == "ZOS" ~ 2,
+#                         name == "BL" ~ 3,
+#                         name == "SED" ~ 4,
+#                         name == "GRE" ~ 5,
+#                         name == "RED" ~ 6,
+#                         name == "Xanthophyceae" ~ 7)) %>% 
+#   as("Spatial") %>% 
+#   vect()
 
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land area"),
-                    values = c("#70543e", "#BDBDBD"))+
+                    values = c("goldenrod", "#BDBDBD"))+
   geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
@@
   scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
-                    values = c("#70543e", "#BDBDBD"))+
+                    values = c("goldenrod", "#BDBDBD"))+
   geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+

### 2024-11-16 docs/_tex/index.tex
add Laurent's comments
adding fundings and code availability

@@
 However, when applied to coastal habitat mapping, previous case studies
-were mostly limited to a low number of \textbf{drone} flights over a
-single study site, restricting the generalizability of their application
-over wider geographical scales
+were mostly limited to a low number of drone flights over a single study
+site, restricting the generalizability of their application over wider
+geographical scales
 \citep{Roman2021, collin2019improving, rossiter2020uav, Brunier2022Topographic}.
-\textbf{These studies have demonstrated the capability of drones to map
+These studies have demonstrated the capability of drones to map
 intertidal habitats, including seagrasses; however a broader
@@
 and quantifying the impact of spatial resolution on classification
-accuracy.} Nine drone flights were performed over soft-bottom intertidal
+accuracy. Nine drone flights were performed over soft-bottom intertidal
 areas along the Atlantic coastlines of two European countries (France
@@
 spatial resolution on classification accuracy, and provide insights for
-coastal habitat mapping using satellite remote sensing. \textbf{This
-study is, therefore, among the first to quantify the effects of spatial
-resolution on the accuracy of drone-based macrophyte classification
-across a wide geographical scale, providing a framework to better
-understand satellite-based classification challenges.}
+coastal habitat mapping using satellite remote sensing. This study is,
+therefore, among the first to quantify the effects of spatial resolution
+on the accuracy of drone-based macrophyte classification across a wide
+geographical scale, providing a framework to better understand
+satellite-based classification challenges.
 
@@
 Portugal. A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites),
-C: Ria de Aveiro Coastal Lagoon (Three sites). Brown areas represents
+C: Ria de Aveiro Coastal Lagoon (Three sites). Golden areas represents
 the intertidal zone.}
@@
 different altitudes : 12 m or/and 120 m, with a spatial resolution of 8
-mm and 80 mm, respectively (Table~\ref{tbl-flights}).
-\textbf{Low-altitude flights, with a spatial resolution of 8 mm, were
-used to build the training dataset for the neural network, as this high
-resolution allowed for precise photo-interpretation of vegetation
-classes. In contrast, high-altitude flights were used for validation
-purposes.}
+mm and 80 mm, respectively (Table~\ref{tbl-flights}). Low-altitude
+flights, with a spatial resolution of 8 mm, were used to build the
+training dataset for the neural network, as this high resolution allowed
+for precise photo-interpretation of vegetation classes. In contrast,
+high-altitude flights were used for validation purposes.
 
@@
 quadrats of 0.25 m², which assessed the presence or absence of five key
-taxonomic classes of intertidal vegetation: Bacillariophyceae
-\textbf{(benthic diatoms forming biofilms at the sediment surface during
-low tide with biofilm's size ranging from small patches (m²) to entire
-mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown
-macroalgae generally attached to rocks or other substrates able to form
-dense beds in the intertidal zone; henceforth: Brown macroalgae),
-Magnoliopsida (seagrasses, rooted flowering marine plants able to form
-extensive meadows on soft sediments; henceforth: Seagrasses),
-Chlorophyceae (green macroalgae, typically found attached to rocks or
-washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red
-macroalgae, attached to hard substrates but can also be found on
-soft-bottom substrate; henceforth: Red macroalgae)}. Only homogeneous
-vegetation patches extending over several meters were selected as ground
-control points. Pictures of each quadrat were uploaded online to the
-open-portal Global Biodiversity Information Facility (GBIF) platform
+taxonomic classes of intertidal vegetation: Bacillariophyceae (benthic
+diatoms forming biofilms at the sediment surface during low tide with
+biofilm's size ranging from small patches (m²) to entire mudflats (km²);
+henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally
+attached to rocks or other substrates able to form dense beds in the
+intertidal zone; henceforth: Brown macroalgae), Magnoliopsida
+(seagrasses, rooted flowering marine plants able to form extensive
+meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green
+macroalgae, typically found attached to rocks or washed ashore;
+henceforth: Green macroalgae), and Rhodophyceae (red macroalgae,
+attached to hard substrates but can also be found on soft-bottom
+substrate; henceforth: Red macroalgae). Only homogeneous vegetation
+patches extending over several meters were selected as ground control
+points. Pictures of each quadrat were uploaded online to the open-portal
+Global Biodiversity Information Facility (GBIF) platform
 \citep{BedeGbif}. Each photograph was also processed to estimate the
@@
 vermiculophylla}) ; D : Chlorophyceae (\emph{Ulva sp.}) ; E :
-Bacillariophyceae (Benthic diatoms). \textbf{The taxonomy was chacked
-following the World Register of Marine Species (WORMS).}}
+Bacillariophyceae (Benthic diatoms). The taxonomy was chacked following
+the World Register of Marine Species (WORMS).}
 
@@
 spatial resolution allowed to avoid spectral sub-pixel mixing and to
-accurately identify vegetation classes. \textbf{In the field, seagrasses
+accurately identify vegetation classes. In the field, seagrasses
 displayed two types of color were observed (i.e.~whereas most seagrass
@@
 seagrass class. This approach was consistently applied to all classes
-within the model.} More than 418,000 pixels at 8 mm resolution from the
-3 training flights were used to train the model
+within the model. More than 418,000 pixels at 8 mm resolution from the 3
+training flights were used to train the model
 (Table~\ref{tbl-validationPX}). For model training, 21 variables were
@@
 high-altitude flights) using the ``average'' method from the terra
-package in R. \textbf{The rasters were resampled to 32 different
-resolutions, ranging from 10 cm to 30 m.} DISCOV was then applied to
-these resampled rasters, and the results were compared to the original
-model predictions. For each resolution and vegetation class, we
-calculated the predicted area loss, where a score of 0 indicates no area
-loss during spatial resampling, and a score of 100 indicates complete
-loss of the vegetation class.
+package in R. The rasters were resampled to 32 different resolutions,
+ranging from 10 cm to 30 m. DISCOV was then applied to these resampled
+rasters, and the results were compared to the original model
+predictions. For each resolution and vegetation class, we calculated the
+predicted area loss, where a score of 0 indicates no area loss during
+spatial resampling, and a score of 100 indicates complete loss of the
+vegetation class.
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png}
 
@@
 neoxanthin, PE: phycoerythrin, PC: phycocyanin;
-\citetext{\citealp{ralph2002}; \citealp[
-\citep{christensen1977seaweeds}]{Douay2022}; \citealp{cartaxana2016regulation}; \citealp{meleder2013vivo}}.}
+\citep{ralph2002, Douay2022, christensen1977seaweeds, cartaxana2016regulation, meleder2013vivo}.}
 
@@
 
+\section{Code availability}\label{code-availability}
+
+All code used to create DISCOV model and apply it to Micasense Dual MX
+images, as described are available at
+\href{https://oirysimon.com/discov/}{https://oirysimon.com/discov}
+
+\section{Acknowledgments}\label{acknowledgments}
+
+The authors would like to thank the extensive revisions and comments
+made by anonymous reviewers to improve the work. This work was supported
+through the BiCOME (Biodiversity of the Coastal Ocean: Monitoring with
+Earth Observation) project funded by the European Space Agency under the
+`Earth Observation Science for Society' element of FutureEO-1
+BIODIVERSITY+PRECURSORS call, contract No.~4000135756/21/I-EF. This work
+was also supported by French Ministry of Research \& Higher Education
+for funding first authors PhD. Further, this work was partially funded
+by Portuguese national funds through the FCT---Foundation for Science
+and Technology, I.P., under the individual project/contract
+CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM
+(UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).
+
   \bibliography{library.bib}

### 2024-11-16 index.qmd
add Laurent's comments
adding fundings and code availability

@@
 The versatility of drones allows for their application across a diverse thematic range , from coastal zone management [@adade2021 ; @casella2020 ; @angnuureng2022] to mapping species distribution [@joyce2023 ; @tallam2023 ; @Roca2022 ; @Roman2021 ; @Brunier2022Topographic ; @sousa2019blue].
-However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of **drone** flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
-**These studies have demonstrated the capability of drones to map intertidal habitats, including seagrasses; however a broader generalization of these findings is still lacking.
+However, when applied to coastal habitat mapping, previous case studies were mostly limited to a low number of drone flights over a single study site, restricting the generalizability of their application over wider geographical scales [@Roman2021 ; @collin2019improving ; @rossiter2020uav ; @Brunier2022Topographic].
+These studies have demonstrated the capability of drones to map intertidal habitats, including seagrasses; however a broader generalization of these findings is still lacking.
 The current paper uniquely expands the spatial and methodological scope of drone-based remote sensing for intertidal habitat mapping across a broad biogeographical range.
 It demonstrates the feasibility of accurately classifying diverse macrophyte types across various study sites, with a particular focus on distinguishing Magnoliopsida (seagrasses) and Chlorophyceae (green algae).
-Unlike previous studies, our approach integrates multiple spatial scales by simulating satellite resolutions and quantifying the impact of spatial resolution on classification accuracy.** Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
+Unlike previous studies, our approach integrates multiple spatial scales by simulating satellite resolutions and quantifying the impact of spatial resolution on classification accuracy.
+Nine drone flights were performed over soft-bottom intertidal areas along the Atlantic coastlines of two European countries (France and Portugal), covering a wide range of habitats, from monospecific seagrass meadows to meadows mixed with green, or red macroalgae.
 A deep learning algorithm was trained and validated for macrophyte discrimination, emphasizing applicability across diverse sites without losing prediction accuracy.
 The classification maps obtained at a very high spatial resolution with the drone were spatially degraded to satellite resolutions, making it possible to assess the effect of spatial resolution on classification accuracy, and provide insights for coastal habitat mapping using satellite remote sensing.
-**This study is, therefore, among the first to quantify the effects of spatial resolution on the accuracy of drone-based macrophyte classification across a wide geographical scale, providing a framework to better understand satellite-based classification challenges.**
+This study is, therefore, among the first to quantify the effects of spatial resolution on the accuracy of drone-based macrophyte classification across a wide geographical scale, providing a framework to better understand satellite-based classification challenges.
 
@@
 A: Gulf of Morbihan (Two sites), B: Bourgneuf Bay (Two sites), C: Ria de Aveiro Coastal Lagoon (Three sites).
-Brown areas represents the intertidal zone.
+Golden areas represents the intertidal zone.
 #| label: fig-map
@@
 Across all sites, flights were made at two different altitudes : 12 m or/and 120 m, with a spatial resolution of 8 mm and 80 mm, respectively (@tbl-flights).
-**Low-altitude flights, with a spatial resolution of 8 mm, were used to build the training dataset for the neural network, as this high resolution allowed for precise photo-interpretation of vegetation classes.
-In contrast, high-altitude flights were used for validation purposes.**
+Low-altitude flights, with a spatial resolution of 8 mm, were used to build the training dataset for the neural network, as this high resolution allowed for precise photo-interpretation of vegetation classes.
+In contrast, high-altitude flights were used for validation purposes.
 
@@
 Ground control points were used to correct georeferencing imprecision of orthomosaics with an horizontal and vertical accuracy of 10cm.
-A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae **(benthic diatoms forming biofilms at the sediment surface during low tide with biofilm's size ranging from small patches (m²) to entire mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally attached to rocks or other substrates able to form dense beds in the intertidal zone; henceforth: Brown macroalgae), Magnoliopsida (seagrasses, rooted flowering marine plants able to form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae, attached to hard substrates but can also be found on soft-bottom substrate; henceforth: Red macroalgae)**.
+A dGPS was also used to georeference quadrats of 0.25 m², which assessed the presence or absence of five key taxonomic classes of intertidal vegetation: Bacillariophyceae (benthic diatoms forming biofilms at the sediment surface during low tide with biofilm's size ranging from small patches (m²) to entire mudflats (km²); henceforth: Benthic diatoms), Phaeophyceae (brown macroalgae generally attached to rocks or other substrates able to form dense beds in the intertidal zone; henceforth: Brown macroalgae), Magnoliopsida (seagrasses, rooted flowering marine plants able to form extensive meadows on soft sediments; henceforth: Seagrasses), Chlorophyceae (green macroalgae, typically found attached to rocks or washed ashore; henceforth: Green macroalgae), and Rhodophyceae (red macroalgae, attached to hard substrates but can also be found on soft-bottom substrate; henceforth: Red macroalgae).
 Only homogeneous vegetation patches extending over several meters were selected as ground control points.
@@
 A : Magnoliopsida (*Zostera noltei*)  ; B : Phaeophyceae (*Fucus sp.*) ; C : Rhodophyceae (*Gracilaria vermiculophylla*) ; D : Chlorophyceae (*Ulva sp.*) ; E : Bacillariophyceae (Benthic diatoms).
-**The taxonomy was chacked following the World Register of Marine Species (WORMS).**"
+The taxonomy was chacked following the World Register of Marine Species (WORMS)."
 #| label: fig-vegetation
@@
 Only data from the low-altitude flights (@tbl-flights) were used for training because their 8 mm spatial resolution allowed to avoid spectral sub-pixel mixing and to accurately identify vegetation classes.
-**In the field, seagrasses displayed two types of color were observed (i.e.
+In the field, seagrasses displayed two types of color were observed (i.e.
 whereas most seagrass had green leaves, brownish leaves were also observed due to senescence or photo-degradaration).
 Careful attention was given to incorporating training pixels from both color types into the training dataset for the seagrass class.
-This approach was consistently applied to all classes within the model.** More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
+This approach was consistently applied to all classes within the model.
+More than `r my_comma(round(sum(df_training$Training_Pixels),-3))` pixels at 8 mm resolution from the 3 training flights were used to train the model (@tbl-validationPX).
 For model training, 21 variables were used as predictors: the ten raw spectral bands of the Micasense RedEdge Dual MX multispectral camera (ranging from 444 nm to 840 nm), the same ten spectral bands standardized using a min/max transformation ([@eq-std] ; @Cao2017) and the Normalized difference vegetation index (NDVI, @eq-ndvi).
@@
 To assess the impact of spatial resolution on the model's output, we resampled the drone orthomosaics from their native resolution (8 cm for high-altitude flights) using the "average" method from the terra package in R.
-**The rasters were resampled to 32 different resolutions, ranging from 10 cm to 30 m.**
+The rasters were resampled to 32 different resolutions, ranging from 10 cm to 30 m.
 DISCOV was then applied to these resampled rasters, and the results were compared to the original model predictions.
@@
 
-knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred1.png")
+knitr::include_graphics("./Figures/Low_res/Maps Pred/FigX-Gaf_High_Pred.png")
 
@@
 The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem conservation and restoration.
+
+# Code availability
+All code used to create DISCOV model and apply it to Micasense Dual MX images, as described are available at [https://oirysimon.com/discov](https://oirysimon.com/discov/)
+
+# Acknowledgments
+
+The authors would like to thank the extensive revisions and comments made by anonymous reviewers to improve the work.
+This work was supported through the BiCOME (Biodiversity of the Coastal Ocean: Monitoring with Earth Observation) project funded by the European Space Agency under the ‘Earth Observation Science for Society’ element of FutureEO-1 BIODIVERSITY+PRECURSORS call, contract No.
+4000135756/21/I-EF.
+This work was also supported by French Ministry of Research & Higher Education for funding first authors PhD.
+Further, this work was partially funded by Portuguese national funds through the FCT—Foundation for Science and Technology, I.P., under the individual project/contract CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM (UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).

### 2024-11-16 index.qmd
adding fundings and code availability

@@
 This work was also supported by French Ministry of Research & Higher Education for funding first authors PhD.
-Further, this work was partially funded by Portuguese national funds through the FCT—Foundation for Science and Technology, I.P., under the individual project/contract CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM (UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).
+Ana I.
+Sousa funded by Portuguese national funds through the FCT—Foundation for Science and Technology, I.P., under the individual project/contract CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM (UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).

### 2024-11-17 docs/_tex/index.tex
adding editing

@@
 France},,postcodesep={}}
-\affiliation[2]{organization={ECOMARE - Laboratory for Innovation and
-Sustainability of Marine Biological Resources, CESAM -- Centre for
-Environmental and Marine Studies, Department of Biology, University of
-Aveiro, Campus Universitário de Santiago, 3810-193 Aveiro,
-Portugal},,postcodesep={}}
+\affiliation[2]{organization={ECOMARE, CESAM -- Centre for Environmental
+and Marine Studies, Department of Biology, University of Aveiro, Campus
+Universitário de Santiago, Aveiro, 3810-193, Portugal},,postcodesep={}}
 \affiliation[3]{organization={Consiglio Nazionale delle Ricerche,
@@
 observation at very high spatial resolution (8 mm and 80 mm
-respectively). Taking advantage of their extremly high spatial
+respectively). Taking advantage of their extremely high spatial
 resolution; the low altitude flights were used to train a Neural Network
@@
 classification outputs, showing a limited loss in seagrass detection up
-to about 10m. Altogether, out findings suggest that the Multi-Spectral
+to about 10m. Altogether, our findings suggest that the Multi-Spectral
 Instrument (MSI) onboard Sentinel-2 offers a relevant trade-off between
@@
 \citep{deSantos2019, Zoffoli2021, sousa2019blue}. Coastal eutrophication
-has been associated to excessive accumulation of green macroalgae,
-so-called green tides \citep{devlin2023nutrients}. Green tides produce
-shade and suffocation over seagrass individuals, thus threatening the
-health of seagrass ecosystems \citep{wang2022}.
+has been associated to excessive accumulation of green macroalgae (algal
+blooms), so-called green tides \citep{devlin2023nutrients}. Green tides
+produce shade and suffocation over seagrass individuals, thus
+threatening the health of seagrass ecosystems \citep{wang2022}.
 
@@
 versatility of drones allows for their application across a diverse
-thematic range , from coastal zone management
-\citep{adade2021, casella2020, angnuureng2022} to mapping species
-distribution
-\citep{joyce2023, tallam2023, Roca2022, Roman2021, Brunier2022Topographic, sousa2019blue}.
+thematic range , from coastal zone monitoring and management
+\citep{adade2021, casella2020, angnuureng2022, lange2022large, svane2022unoccupied}
+to mapping species distribution
+\citep{joyce2023, tallam2023, Roca2022, Roman2021, Brunier2022Topographic, sousa2019blue, svane2022unoccupied}.
 However, when applied to coastal habitat mapping, previous case studies
@@
 These studies have demonstrated the capability of drones to map
-intertidal habitats, including seagrasses; however a broader
-generalization of these findings is still lacking. The current paper
-uniquely expands the spatial and methodological scope of drone-based
-remote sensing for intertidal habitat mapping across a broad
+intertidal (and subtidal) habitats, including seagrasses; however a
+broader generalization of these findings is still lacking. The current
+paper uniquely expands the spatial and methodological scope of
+drone-based remote sensing for intertidal habitat mapping across a broad
 biogeographical range. It demonstrates the feasibility of accurately
@@
 and quantifying the impact of spatial resolution on classification
-accuracy. Nine drone flights were performed over soft-bottom intertidal
-areas along the Atlantic coastlines of two European countries (France
-and Portugal), covering a wide range of habitats, from monospecific
-seagrass meadows to meadows mixed with green, or red macroalgae. A deep
-learning algorithm was trained and validated for macrophyte
-discrimination, emphasizing applicability across diverse sites without
-losing prediction accuracy. The classification maps obtained at a very
-high spatial resolution with the drone were spatially degraded to
-satellite resolutions, making it possible to assess the effect of
-spatial resolution on classification accuracy, and provide insights for
-coastal habitat mapping using satellite remote sensing. This study is,
-therefore, among the first to quantify the effects of spatial resolution
-on the accuracy of drone-based macrophyte classification across a wide
-geographical scale, providing a framework to better understand
-satellite-based classification challenges.
+accuracy. Nine drone flights were performed over soft-bottom (mud and
+sand) intertidal areas along the Atlantic coastlines of two European
+countries (France and Portugal), covering a wide range of habitats, from
+monospecific seagrass meadows to meadows mixed with green, or red
+macroalgae. A deep learning algorithm was trained and validated for
+macrophyte discrimination, emphasizing applicability across diverse
+sites without losing prediction accuracy. The classification maps
+obtained at a very high spatial resolution with the drone were spatially
+degraded to satellite resolutions, making it possible to assess the
+effect of spatial resolution on classification accuracy, and provide
+insights for coastal habitat mapping using satellite remote sensing.
+This study is, therefore, among the first to quantify the effects of
+spatial resolution on the accuracy of drone-based intertidal macrophyte
+classification across a wide geographical scale, providing a framework
+to better understand satellite-based classification challenges.
 
@@
 (one of the four main channels of the lagoon) whereas the two other
-sites (Mataducos and Marinha Lanzarote) were situated in the middle of
-the lagoon and only accessible by boat. These Portuguese sites are
-characterized by a more diverse intertidal vegetation, where patches of
-seagrass intermingle with red, brown, and green macroalgae. The Aveiro
-Lagoon, like the other study areas, is a Natura 2000 site and a RAMSAR
-wetland, recognized for its rich mosaic of habitats and importance for
-biodiversity, including migratory bird species and intertidal
-vegetation.
+sites (Mataduços and Marinha Lanzarote) were situated in the middle of
+the lagoon, with Marinha Lanzarote only accessible by boat. These
+Portuguese sites (at Ria de Aveiro) are characterized by a more diverse
+intertidal vegetation, where patches of seagrass intermingle with red,
+brown, and green macroalgae. The Ria de Aveiro costal lagoon, like the
+other study areas, is a Natura 2000 site, recognized for its rich mosaic
+of habitats (EU Habitats Directive) and importance for biodiversity,
+including migratory bird species (part of the EU Birds Directive) and
+intertidal vegetation (from mudflats to seagrass meadows and salt
+marshes)..
 
@@
 served dual purposes: they validate the radiometric calibration of drone
-data and contribute to misclassification reduction in photo
+data and contributed to misclassification reduction in photo
 interpretations.
@@
 vermiculophylla}) ; D : Chlorophyceae (\emph{Ulva sp.}) ; E :
-Bacillariophyceae (Benthic diatoms). The taxonomy was chacked following
-the World Register of Marine Species (WORMS).}
+Bacillariophyceae (Benthic diatoms). Classes and species taxonomy
+following the WORMS - World Register of Marine Species classfication.}
 
@@
 score of 0.85). In the northern part of the site and near the land
-edges, patches of the schorre angiosperm \emph{Sporobolus maritimus}
-(syn. \emph{Spartina maritima)} were misclassified, either as seagrass
-or as brown algae (F1 score of 0.77 and 0.71, respectively).
+edges, patches of the halophyte \emph{Sporobolus maritimus} (syn.
+\emph{Spartina maritima)} were misclassified, either as seagrass or as
+brown algae (F1 score of 0.77 and 0.71, respectively).
 
@@
 \caption{\label{fig-Boat}RGB orthomosaic (Top) and Prediction (Bottom)
-of the flight made in the inner part of Ria de Aveiro Lagoon, Portugal.
+of the flight made in the inner part of Ria de Aveiro lagoon, Portugal.
 The total extent of this flight was about 1.5 km² with a resolution of
@@
 The lowest performing site was Gafanha High (global accuracy of 75.45\%)
-whereas Mataducos was the site with the most accurate prediction (global
+whereas Mataduços was the site with the most accurate prediction (global
 accuracy of 98.05\%). Overall, the classes Phaeophyceae, Magnoliopsida,
@@
 
-\subsection{Effect of the percent cover on the
-prediction}\label{effect-of-the-percent-cover-on-the-prediction}
+\subsection{Effect of the cover on the
+prediction}\label{effect-of-the-cover-on-the-prediction}
 
 Using the very high-resolution low-altitude flight (8 mm pixels), we
-determined the minimal percent cover required to correctly classify a
-given class within the corresponding high-altitude flight (8cm pixel
+determined the minimal cover (\%) required to correctly classify a given
+class within the corresponding high-altitude flight (8cm pixel
 resolution ; Figure~\ref{fig-upscaling}).
@@
 altitude flight pixels of Gafanha, Portugal. Each subplot shows all the
-pixels of the same classes on the high altitude flight. Percent cover of
+pixels of the same classes on the high altitude flight. Cover (\%) of
 classes was retrieved using the result of the classification of the low
@@
 
-A percent cover of at least 80\% was sufficient to have all the 80 mm
-pixels correctly classified, with the exception of Magnoliopsida which
-required a higher cover (\textgreater90 \%) to be accurately classified.
+A cover of at least 80 \% was sufficient to have all the 80 mm pixels
+correctly classified, with the exception of Magnoliopsida which required
+a higher cover (\textgreater90 \%) to be accurately classified.
 Concerning the probability of each class, there is a linear relationship
@@
 cover of 93 \% was needed, 90 \% for seagrass, 92 \% for red macroalgae
-and 97 \% for benthic diatoms When the vegetation cover of a given class
-was 100 \%, coarser high-flight pixels were correctly classified for all
-the classes except for Bare Sediment, which was only correctly
+and 97 \% for benthic diatoms. When the vegetation cover of a given
+class was 100 \%, coarser high-flight pixels were correctly classified
+for all the classes except for Bare Sediment, which was only correctly
 classified 80\% of the time. This phenomenon may be attributed to the
@@
 was also supported by French Ministry of Research \& Higher Education
-for funding first authors PhD. Further, this work was partially funded
-by Portuguese national funds through the FCT---Foundation for Science
-and Technology, I.P., under the individual project/contract
-CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM
-(UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).
+for funding first authors PhD. This study was partially funded by
+FCT/MCTES (Fundação para a Ciência e a Tecnologia) under the project
+UIDB/50017/2020 + UIDP/50017/2020 + LA/P/0094/2020 granted to CESAM and
+through research contract CEECIND/00962/2017 (DOI:
+10.54499/CEECIND/00962/2017/CP1459/CT0008) granted to AI Sousa. The work
+was also partially funded by the project BIOPRADARIA
+(MAR-01.04.02-FEAMP-0020), funded by the Operational Program MAR2020,
+EMFF-European Maritime and Fisheries Fund, European Union, Portugal2020.
 
